### 2020-07-05 paper.tex
Abstract

\documentclass[aps,prl,twocolumn,groupedaddress]{revtex4-1}
% \documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[colorlinks=true]{hyperref}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\eff}{ef\! f}
\newcommand{\fxnote}[1]{{\textbf{[#1]}}}

\newcommand{\todo}[1]{}

\ifpdf
% Ensure reproducible output
\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}
\hypersetup{
  pdfcreator={},
  pdfproducer={}
}
\fi

\begin{document}
\title{Coherent optical association of single molecules}
\author{Yichao Yu}
\email{yichaoyu@g.harvard.edu}
\author{Kenneth Wang}
\author{Jessie T. Zhang}
\author{Lewis Picard}
\author{William Cairncross}
\author{Kang-Kuen Ni}
\email{ni@chemistry.harvard.edu}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts, 02138, USA}

\date{\today}

\begin{abstract}
  We report coherent association of a single NaCs molecule in an optical tweezer
  through an optical Raman transition.
  By selecting a deeply bound intermediate state,
  we suppress the scattering loss during the transfer process.
  Starting from atoms in their relative motional ground state,
  we achieve optical transfer efficiency of $50 \%$ \todo{number}.
  The molecule we create have a zero-field binding energy of $770 \mathrm{MHz}$ \todo{number}
  and lifetime up to $1 \mathrm{ms}$ \todo{number}.
  We demonstrate that coherent creation of ground state single molecule is possible,
  even without Feshbach resonance or narrow optical transition.
\end{abstract}

% Coherent
% Intermediate state
% Motional state control
% Initial state preparation

\maketitle

\bibliography{paper}
\end{document}

### 2020-08-04 paper.tex
figure

@@
 
+% Introduction
+
+Trapped neutral molecules, assembled in an array of optical tweezers,
+are a promising platform to study quantum infoqrmation and quantum simulations.
+
+\begin{figure*}
+  \includegraphics[height=4.5cm]{fig1.pdf}
+  \caption{Optical creation of single molecule from single atoms in tweezer.
+    (A) Schematics of the Raman transition. \todo{more about the states involved}
+    (B) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
+    \todo{Field strength, power, polarization description (pi)}
+    (C) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
+    This power is smoothly ramped down and the down leg power ramped up over $10\mu s$ while
+    maintaining the total power of the tweezer.
+    \todo{to minimize heating?}
+    \label{f-setup}
+  }
+\end{figure*}
+
+\begin{figure*}
+  \includegraphics[height=4.5cm]{fig2.pdf}
+  \caption{
+    (A) Raman resonance from atomic state to molecular state, showing Fourier limited linewidth.
+    \todo{states, time}
+    (B) Rabi oscillation on resonance
+    \label{f-raman}}
+\end{figure*}
+
+\begin{figure*}
+  \includegraphics[height=4.5cm]{fig3.pdf}
+  \caption{
+    (A) Molecule lifetime in 15 mW of trap depth \todo{lifetime number}
+    (B) Two-body atom lifetime in 15 mW of trap depth \todo{lifetime number,
+      subtraction of single body, photoassociation rate}
+    \label{f-lifetime}}
+\end{figure*}
+
+% In this Letter, we demostrate that a single ground state molecule can be formed
+
 \bibliography{paper}

### 2020-08-13 paper.tex
early draft...

@@
 
-% In this Letter, we demostrate that a single ground state molecule can be formed
+In this Letter, we demostrate that a single ground electronic state molecule can be formed
+from two single optical tweezers by driving an optical Raman transition
+
+\todo{Previous result}
+\todo{talk about size mismatch, two step transfer/weakly bound molecule in intro}
+
+%% Preparation
+Our experiment begins by loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into an optical tweezer from a dual-species MOT\todo{cite na loading paper} into separate optical tweezers.
+The atoms are imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom during post selection.
+We then perform simutanious Raman sideband cooling (RSC) to cool both atoms into a single 3-dimentional motional ground state in the tweezers.
+After RSC, the Na tweezer is moved by sweeping the frequency on an acustical optical beam deflector (AOBD) to overlap with the Cs tweezer before smoothly ramping off so that the Na and Cs atoms are merged into the same tweezer \todo{cite}.
+The spin states for the Na and Cs atoms after RSC and during the merge process are $|F=2,m_F=2\rangle$ and $|F=4,m_F=4\rangle$ respectively.
+This states combination has a low scattering length of $...
+a_0$ which allows the two atoms to be merged into the same tweezer with minimum pertubation on each other and remains in their motional ground state after the merge.
+
+After preparing the Na and Cs atoms in the same tweezer in a single quantum state, we perform interaction shift spectroscopy using a Cs Raman transition to drive the Cs into the $|F=3,m_F=3\rangle$ state.
+The new spin state combination has a larger scattering length of $...
+a_0$ which generates a interaction shift of $...
+kHz$ in the tweezer.
+This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of relative motional ground state.
+The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer.
+
+%% Transfer scheme
+
+The optical transfer scheme we used is shown in figure \todo{}.
+We use an optical Raman transition to drive the system from the atomic initial state to a
+ground electronic molecular state.
+In order to reduce the size mismatch between the atomic and molecular states,
+we selected the first bound state for the 3322 spin state \todo{asymtopt to the 3322 threshold?} as our final state. \todo{move selection of intermediate state to intro?}.
+For similar reason, the natural choice for the intermediate excited molecular state is one
+with highly excited motional level.
+However, from our calculation (and experiment?), the smaller level space for high
+vibrational state and the smaller detuning from the atomic threshold increases the
+the scattering rate of the molecular state which causes a reduced Raman Rabi frequency
+to decoherence rate ratio and a lower transfer efficiency.
+Therefore, in our experiment, we selected the v=0 state as the intermediate state for our
+Raman transition.
+
+The pulse sequence for the experiment can be seen in figure ().
+Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal.
+After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simutaniously ramping up the power of a different frequency so that the total tweezer power remains unchanged.
+Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.
+The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition.
+Using the tweezer beam for the Raman transition also allow us to maximize the intensity of the Raman beams and minimize the transfer time.
+
+Figure () shows the geometry of the experiment setup.
+The B field which defines the quantization axis in the experiment is perpendicular to the tweezer axis.
+The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
+
+%% Prediction
+
+This excited state used in the Raman transition was measured in our previous experiment using PA to be at $288...
+GHz$ from our atomic state.
+The ground molecular state has not been observed previously in experimentally.
+Based on previous FB and interaction shift and 4422 bound state data.
+Theory prediction was at $770...
+MHz$.
+\todo{more, mention/cite Jeremy}
+
+%% Experiment condition/resonance
+
+\todo{Resonance observed at}
+\todo{FWHM of line}
+
+\todo{Rabi flopping}
+
+\todo{Scattering}
 

### 2020-08-14 paper.tex
still early draft...

@@
 Using the tweezer beam for the Raman transition also allow us to maximize the intensity of the Raman beams and minimize the transfer time.
+\todo{clarify coprop of Raman beam?}
 
 Figure () shows the geometry of the experiment setup.
-The B field which defines the quantization axis in the experiment is perpendicular to the tweezer axis.
+A $8.8\mathrm{G}$ B field was used to defines the quantization axis in the experiment and is applied perpendicular to the tweezer axis.
 The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
@@
 
-This excited state used in the Raman transition was measured in our previous experiment using PA to be at $288...
+This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288...
 GHz$ from our atomic state.
 The ground molecular state has not been observed previously in experimentally.
-Based on previous FB and interaction shift and 4422 bound state data.
+Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state.
 Theory prediction was at $770...
@@
 
-\todo{Resonance observed at}
-\todo{FWHM of line}
+We locate the Raman resonance for the atom to molecule transition at $770... MHz$ (figure \todo{}) with a $15 mW$ tweezer at $288... GHz$ which corresponds to a $... GHz$ single photon detuning.
+The background level of $...\%$ corresponds to the propability of preparing the two atoms in the relative motional ground state using interaction shift spectroscopy.
+When the atoms are transfered into molecule by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imagine step.
+\todo{more explanation of detection?}
+\todo{FWHM of line??}
 
-\todo{Rabi flopping}
+B field dependency $... kHz/G$ which agrees with theory prediction of $... kHz/G$.
+Dependency on tweezer power $... kHz/mW$, extrapulated to obtain the bare resonance at $0$ tweezer power to be at $... MHz$.
+
+After confirming the creating of the molecule via optical Raman transition, we proceed to verify the coherence of the process.
+This is done by fixing the Raman frequency on the resonance and scanned the pulse time.
+figure ...
+shows the observed Rabi oscillation between the atomic and molecular states.
+Fitting the data with a decaying Rabi oscillation suggests that $..\%$ of initial ground state atoms are transfered into the molecular state.
+
+\todo{Atomic lifetime}
+
+Combining the frequency and time scan allow us to accurately fit the parameters for the Raman transition.
+Raman Rabi frequency
+Molecular state lifetime.
+The result shows that the decoherence of the Rabi oscillation is caused by finite lifetime of the molecule in the tweezer.
+We can directly measure this by \todo{pulse sequence} (figure ...)...
+
+\todo{Lifetime}
+
+\todo{Fitting}
 

### 2020-08-18 paper.tex
Update on Overleaf.

@@
 \author{Kenneth Wang}
+\author{J. D. Hood}
+\author{Lewis Picard}
 \author{Jessie T. Zhang}
-\author{Lewis Picard}
 \author{William Cairncross}
+\author{Jeremy Hutson}
+\author{Till Rosenband}
 \author{Kang-Kuen Ni}
@@
 \begin{abstract}
-  We report coherent association of a single NaCs molecule in an optical tweezer
-  through an optical Raman transition.
-  By selecting a deeply bound intermediate state,
-  we suppress the scattering loss during the transfer process.
-  Starting from atoms in their relative motional ground state,
+  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
+  through an optical Raman transition without the use of a Feshbach resonance.
+Our scheme borrows transition dipole moment while reducing photon scattering by selecting a deeply bound electronic excited intermediate state.
+  Starting from two atoms in their relative motional ground state,
   we achieve optical transfer efficiency of $50 \%$ \todo{number}.
-  The molecule we create have a zero-field binding energy of $770 \mathrm{MHz}$ \todo{number}
-  and lifetime up to $1 \mathrm{ms}$ \todo{number}.
-  We demonstrate that coherent creation of ground state single molecule is possible,
-  even without Feshbach resonance or narrow optical transition.
+  The molecule has a (change to 8.8G) zero-field binding energy of $770 \mathrm{MHz}$ \todo{number}
+  and lifetime up to $1 \mathrm{ms}$ \todo{number}. (center of mass motional state population.)
+  %We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition. 
+  This  technique is general (does not rely on narrow excited state linewidth) and could allow a wider range of molecular species to be assembled atom-by-atom. 
 \end{abstract}
@@
 
-Trapped neutral molecules, assembled in an array of optical tweezers,
-are a promising platform to study quantum infoqrmation and quantum simulations.
+Trapped neutral molecules, assembled in an array of optical tweezers, are a promising platform to study quantum infoqrmation and quantum simulations.
+1.
+we want to have a diverse species to tailor to different applications.
+2.
+but so far all has been done with Feshbach association (before STIRAP), or in the case of Sr2, a narrow excited state.
+Previous work on near-threshold Raman transfer has been incoherent.
+(suggested referees: Florian Shreck and Immanual Bloch)
+
+In this Letter, we survey theoretically the best electronic intermediate state, detuning, etc that balance coupling/transfer efficiency and photon scattering to demonstrate coherent association of a electronic ground-state molecule from two atoms.
+Because the electronic excited state we used are generic in most diatomic molecules, this technique is general....
 
@@
 \end{figure*}
-
-In this Letter, we demostrate that a single ground electronic state molecule can be formed
-from two single optical tweezers by driving an optical Raman transition
 

### 2020-08-19 plot_raman_full.jl
Draft of all figures

@@ -1,0 +1,72 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+# using DataStructures
+# using LsqFit
+using LibArchive
+
+using DelimitedFiles
+
+const fname = joinpath(@__DIR__, "../damop-2020/20MHz_linewidth_c3SigmaOnly_3322_80kHzConfinement.csv.zst")
+const data = LibArchive.Reader(fname) do reader
+    LibArchive.support_format_raw(reader)
+    LibArchive.support_filter_all(reader)
+    LibArchive.next_header(reader)
+    readdlm(reader, ',', skipstart=1)
+end
+const prefix = joinpath(@__DIR__, "imgs", "raman_theory")
+
+figure()
+l1 = plot(data[:, 1], abs.(data[:, 2] ./ 2π / 1000), "C0",
+          label="\$\\Omega_{Raman}\$")
+l2 = plot(data[:, 1], abs.(data[:, 4] ./ 2π / 1000), "C1",
+          label="\$\\Gamma_{scatter}\$")
+ylabel("\$2\\pi\\cdot \\mathrm{kHz}\$")
+xlabel("One-Photon Detuning (GHz)")
+yscale("log")
+ylim([0.001, 10])
+grid()
+ax = gca()
+ax2 = ax.twinx()
+l3 = ax2.plot(data[:, 1], abs.(data[:, 2] ./ data[:, 4]), "C2",
+              label="\$\\frac{\\Omega_{Raman}}{\\Gamma_{scatter}}\$")
+ls = [l1; l2; l3]
+legend(ls, [l.get_label() for l in ls], fontsize="x-small",
+       loc="lower right", bbox_to_anchor=(1, 0.05))
+xlim([287500, 345000])
+yscale("log")
+ylim([0.1, 100])
+ax2.tick_params(axis="y", labelcolor="C2")
+# setp(ax2.get_yticklabels(), fontweight="bold")
+NaCsPlot.maybe_save("$(prefix)")
+
+# figure()
[…]

### 2020-08-24 paper.tex
Draft of all figures
process

@@
 
+\begin{figure*}
+  \includegraphics[height=4.5cm]{fig4.pdf}
+  \caption{Raman Rabi frequency vs detuning
+    \label{f-det}}
+\end{figure*}
+
 \todo{Previous result}
 \todo{talk about size mismatch, two step transfer/weakly bound molecule in intro}
+
+For atoms in the motional ground state in the tweezer, the average distance between the two atoms is $...$.
+However, for the ground rovibrational molecule, the bond length is only $...$.
+The size mismatch between the initial and final state causes a very small wavefunction overlap between the initial and final state, \todo{overlap is always 0, the accurate description here is the product of wavefunction overlap through any reasonable intermediate state, or the density-density correlation which serves as a reasonable estimate of the matrix element through different pathways} which poses the biggest challege for for coherent creation of the molecule.
+Because of this, it is necessary to use a intermediate state with a size in between the initial and final state and accomplish the transfer in two steps, each with improved wavefunction overlap.
+
+The traditional choice for such an intermediate state is a FB molecule \todo{cite our FB result}.
+However, the requirement of a suitable FB resonance limits its generality (e.g.
+non-magnetic atoms).
+Instead, we selected a weakly bound molecular state as the intermediate state and we use an optical Raman transition as the first step transfer.
+This approach relies on fewer special properties of the system and can be more generally applied to creating other molecules.
+Such a transfer using optical transition has been observed in previous experiments (\todo{cite}).
+However, they either require the use of a narrow optical transition which limits the generality or were driving the transition incoherently due to scattering.
+In this letter, we will present our result on coherent creation of a weakly bond molecule using only optical transition for the first time.
+
+Even with the first step transfer to a weakly bond molecular state, it is still a challenge to achieve high enough Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.
+For this reason, previous experiments also use weakly bond molecular excited states for the Raman transition.
+However, for a typical molecular potential, vibrationally excited states have a smaller spacing between neighboring states which limits the detuning for the Raman transition and increases the scattering.
+Moreover, there is also a significant scattering process from the excited atomic states due to the strong coupling with the weakly bond molecular ground state.
+Such scattering process is proportional to $1/\delta^2$ from the desociation threshold which is also much stronger for more weakly bound states.
+(combining these factors, confirm with figure 1 Rabi rate vs scattering rate calculation).
+Because of this, we use a deeply bound molecular excited state to drive the Raman transition.
+
+(mention scattering/lightshift depends on up/down matrix element ratio?)
+
+In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
+Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance.
+In additional to the confinement, this value is related to the interaction between the two atoms.
+States with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (add figure?).
+The increase in the coupling is proportional to (quote/cite Olive's equation?).
+For our system, among the stable spin combinations, 4422 and 3311 has a small scattering length of $\abs{a}=....$ respectively and 3322 has a large and negative scattering length.
+(interaction shift $\approx$ binding?)
 
@@
 We use an optical Raman transition to drive the system from the atomic initial state to a
-ground electronic molecular state.
-In order to reduce the size mismatch between the atomic and molecular states,
+ground electronic molecular state. In order to reduce the size mismatch between the atomic and molecular states,
 we selected the first bound state for the 3322 spin state \todo{asymtopt to the 3322 threshold?} as our final state. \todo{move selection of intermediate state to intro?}.
@@
 
+\todo{sm: STIRAP vs Raman}
+
 \bibliography{paper}

### 2020-08-27 paper.tex
results

@@
 When the atoms are transfered into molecule by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imagine step.
-\todo{more explanation of detection?}
-\todo{FWHM of line??}
 
-B field dependency $... kHz/G$ which agrees with theory prediction of $... kHz/G$.
-Dependency on tweezer power $... kHz/mW$, extrapulated to obtain the bare resonance at $0$ tweezer power to be at $... MHz$.
-
-After confirming the creating of the molecule via optical Raman transition, we proceed to verify the coherence of the process.
-This is done by fixing the Raman frequency on the resonance and scanned the pulse time.
+We observed the narrowest linewidth of $....
+kHz$ for the Raman resonance at a pulse time of $...
+ms$, which corresponds to a linewidth-pulsetime product of $...$.
+This is consistent with the expected value of $...$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent.
+In order to verify the coherence of the transfer directly, we fixed the Raman frequency on the resonance and scanned the pulse time.
 figure ...
@@
 
-\todo{Atomic lifetime}
+In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state.
+We also account for atomic state loss by measuring the single and two body lifetime for the atomic state (figure ...).
+The result suggests that our transfer has a Raman Rabi frequency of and the molecule we form has a lifetime of $...$.
+We can also directly verify this result by measuring the lifetime of the molecule directly.
+This is done by applying a reverse Raman pulse to dissociate the molecule back to atoms after a variable wait time.
+The result of the direct measurement shows a molecular lifetime consistent with our fitting of the Raman transition data.
 
-Combining the frequency and time scan allow us to accurately fit the parameters for the Raman transition.
-Raman Rabi frequency
-Molecular state lifetime.
-The result shows that the decoherence of the Rabi oscillation is caused by finite lifetime of the molecule in the tweezer.
-We can directly measure this by \todo{pulse sequence} (figure ...)...
+The molecule lifetime measured in the experiment is $...$ larger than the expected value of $...$ calculated from .....
+By measuring the lifetime for different tweezer powers, we observed a linear dependency of the lifetime (fig ...).
+This confirms that the short lifetime is mainly caused by scattering from the tweezer light rather than the intrinsic lifetime of the molecule itself.
+Additionally, we also measured the loss rate as a function of the tweezer frequency (fig ...) which shows only a very weak dependency for a $...x$ change in the detuning from the $v=0$ excited state.
+This result is significantly different from the $1/\delta^2$ dependency expected from off-resonant scattering and suggests that the main source of the scattering is due to a broadband process that is not directly related to the $v=0$ excited state.
 
-\todo{Lifetime}
+(ASE filter?)
 
-\todo{Fitting}
-
-\todo{Scattering}
+B field dependency $... kHz/G$ which agrees with theory prediction of $... kHz/G$.
+Dependency on tweezer power $... kHz/mW$, extrapulated to obtain the bare resonance at $0$ tweezer power to be at $... MHz$.
 

### 2020-08-28 paper.tex
Refinement

@@
 However, for the ground rovibrational molecule, the bond length is only $...$.
-The size mismatch between the initial and final state causes a very small wavefunction overlap between the initial and final state, \todo{overlap is always 0, the accurate description here is the product of wavefunction overlap through any reasonable intermediate state, or the density-density correlation which serves as a reasonable estimate of the matrix element through different pathways} which poses the biggest challege for for coherent creation of the molecule.
-Because of this, it is necessary to use a intermediate state with a size in between the initial and final state and accomplish the transfer in two steps, each with improved wavefunction overlap.
+The size mismatch between the initial and final state causes a very small wavefunction overlap between them, \todo{overlap is always 0, the accurate description here is the product of wavefunction overlap through any reasonable intermediate state, or the density-density correlation which serves as a reasonable estimate of the matrix element through different pathways} which poses the biggest challege for for coherent creation of the molecule.
+Because of this, it is necessary to use a intermediate state with a size in between the initial and final states and accomplish the transfer in two steps, each with improved wavefunction overlap.
 
@@
 
-Even with the first step transfer to a weakly bond molecular state, it is still a challenge to achieve high enough Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.
-For this reason, previous experiments also use weakly bond molecular excited states for the Raman transition.
-However, for a typical molecular potential, vibrationally excited states have a smaller spacing between neighboring states which limits the detuning for the Raman transition and increases the scattering.
-Moreover, there is also a significant scattering process from the excited atomic states due to the strong coupling with the weakly bond molecular ground state.
-Such scattering process is proportional to $1/\delta^2$ from the desociation threshold which is also much stronger for more weakly bound states.
-(combining these factors, confirm with figure 1 Rabi rate vs scattering rate calculation).
-Because of this, we use a deeply bound molecular excited state to drive the Raman transition.
+Even with the first step transfer to a weakly bond molecular state, it is still a challenge to achieve high Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.
+For this reason, previous experiments also use weakly bond molecular excited states in the Raman transition.
+However, this choice of state also increases the scattering during the transfer process for two reasons.
+Firstly, since for a typical molecular potential the spacing between states decreases with increasing vibrational levels,
+a weakly bond excited molecular state limits the effectiveness of scattering reduction by increasing the detuning for the Raman transition.
+Secondly, the weakly bound molecular ground state has a strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
+The rate of such scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold,
+which further increases the scattering rate for a weakly bond excited state.
+Based on these considerations, we calculated both the Raman Rabi frequency and the scattering rate at different detunings.
+As seen in figure (1....), despite a higher Raman Rabi frequency at the same detuning, the weakly bond state also has a much higher scattering rate
+and ultimately a smaller Rabi frequency to scattering at the optimal detuning. Based on this calculation, we use a deeply bound molecular excited state to drive the Raman transition.
 

### 2020-08-31 paper.tex
tweaks

@@
 
-\todo{Previous result}
-\todo{talk about size mismatch, two step transfer/weakly bound molecule in intro}
-
-For atoms in the motional ground state in the tweezer, the average distance between the two atoms is $...$.
-However, for the ground rovibrational molecule, the bond length is only $...$.
-The size mismatch between the initial and final state causes a very small wavefunction overlap between them, \todo{overlap is always 0, the accurate description here is the product of wavefunction overlap through any reasonable intermediate state, or the density-density correlation which serves as a reasonable estimate of the matrix element through different pathways} which poses the biggest challege for for coherent creation of the molecule.
-Because of this, it is necessary to use a intermediate state with a size in between the initial and final states and accomplish the transfer in two steps, each with improved wavefunction overlap.
+For atoms in the motional ground state in the tweezer,
+the average distance between the two atoms is about $1000a_0$.
+However, for the ground rovibrational molecule, the bond length is only around $4a_0$.
+The size mismatch between the initial and final states cause a very small coupling between them,
+which poses the biggest challege for for coherent creation of the molecule.
+Because of this, it is necessary to use an intermediate state
+with a size in between the initial and final states,
+and accomplish the transfer in two steps in order to increase the coupling.
 
 The traditional choice for such an intermediate state is a FB molecule \todo{cite our FB result}.
-However, the requirement of a suitable FB resonance limits its generality (e.g.
-non-magnetic atoms).
-Instead, we selected a weakly bound molecular state as the intermediate state and we use an optical Raman transition as the first step transfer.
-This approach relies on fewer special properties of the system and can be more generally applied to creating other molecules.
-Such a transfer using optical transition has been observed in previous experiments (\todo{cite}).
-However, they either require the use of a narrow optical transition which limits the generality or were driving the transition incoherently due to scattering.
-In this letter, we will present our result on coherent creation of a weakly bond molecule using only optical transition for the first time.
+However, the requirement of a suitable FB resonance limits its generality. \todo{e.g. non-magnetic atoms?}
+Instead, we selected a weakly bond molecular state as the intermediate state
+and we use an optical Raman transition as the first step transfer.
+This approach minimizes the reliance on system specific properties
+and can therefore be more generally applied to creating other molecules.
+Such a transfer using optical transition has been observed in previous experiments \todo{cite}.
+However, they either require the use of a narrow optical transition which limits the generality
+or were driving the transition incoherently due to scattering.
+In this letter, we will present our result on coherent creation of a weakly bond molecule
+using only optical transitions on a broad optical line for the first time.
 
-Even with the first step transfer to a weakly bond molecular state, it is still a challenge to achieve high Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.
-For this reason, previous experiments also use weakly bond molecular excited states in the Raman transition.
-However, this choice of state also increases the scattering during the transfer process for two reasons.
-Firstly, since for a typical molecular potential the spacing between states decreases with increasing vibrational levels,
-a weakly bond excited molecular state limits the effectiveness of scattering reduction by increasing the detuning for the Raman transition.
-Secondly, the weakly bound molecular ground state has a strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
-The rate of such scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold,
-which further increases the scattering rate for a weakly bond excited state.
-Based on these considerations, we calculated both the Raman Rabi frequency and the scattering rate at different detunings.
-As seen in figure (1....), despite a higher Raman Rabi frequency at the same detuning, the weakly bond state also has a much higher scattering rate
-and ultimately a smaller Rabi frequency to scattering at the optimal detuning. Based on this calculation, we use a deeply bound molecular excited state to drive the Raman transition.
+Even for the first step transfer to a weakly bond molecular state,
+it is still a challenge to achieve high Raman Rabi frequency to drive this transition
+due to the wavefunction size mismatch with the excited molecular state.
+For this reason, previous experiments also use weakly bond molecular excited states
+in the Raman transition.
+However, in additional to a higher Raman Rabi frequency,
+this choice of state also increases the scattering during the transfer process for two reasons.
+Firstly, since for a typical molecular potential the spacing between states
+decreases with increasing vibrational levels,
+a weakly bond excited molecular state limits maximum usable detuning
+and therefore the effectiveness of scattering reduction
+by increasing the detuning for the Raman transition.
+Secondly, due to size similarity, the weakly bound molecular ground state has a strong coupling
+with the atomic excited state which contributes significantly to the total scattering rate.
+The rate of such scattering process is proportional to $1/\delta_{thresh}^2$,
+where $\delta_{thresh}$ is the detuning from the dissociation threshold.
+This further increases the scattering rate for a weakly bond excited state.
+Based on these considerations, we calculated both the Raman Rabi frequency
+and the scattering rate at different detunings.
+As seen in figure (1....), despite a higher Raman Rabi frequency at the same detuning,
+the weakly bond state also has a much higher scattering rate
+and ultimately a smaller Rabi frequency to scattering at the optimal detuning.
+As a result, we use a deeply bound molecular excited state to drive the Raman transition.
 

### 2020-09-07 paper.tex
Update figures

@@
 \begin{figure*}
-  \includegraphics[height=4.5cm]{fig1.pdf}
+  \includegraphics[height=5cm]{fig1.pdf}
   \caption{Optical creation of single molecule from single atoms in tweezer.
@@
   \caption{
-    (A) Molecule lifetime in 15 mW of trap depth \todo{lifetime number}
-    (B) Two-body atom lifetime in 15 mW of trap depth \todo{lifetime number,
+    (A) Two-body atom lifetime in 15 mW of trap depth \todo{lifetime number,
       subtraction of single body, photoassociation rate}
+    (B) Molecule lifetime in 15 mW of trap depth \todo{lifetime number}
     \label{f-lifetime}}
@@
 As a result, we use a deeply bound molecular excited state to drive the Raman transition.
+
+(goes to SM?)
 

### 2020-09-07 plot_exp_data.jl

@@ -1,0 +1,333 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+include("../../experiments/nacs_202003/molecular_raman_model.jl")
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+
+const inames = ["nacs_202003/data/data_20200326_101325.mat",
+                "nacs_202003/data/data_20200326_223438.mat",
+                "nacs_202003/data/data_20200327_004910.mat",
+                "nacs_202003/data/data_20200330_033004.mat",
+                "nacs_202003/data/data_20200327_133537.mat",
+                "nacs_202003/data/data_20200330_201614.mat",
+                "nacs_202003/data/data_20200331_020659.mat",
+                "nacs_202004/data/data_20200401_060025.mat"]
+const datas = [NaCsData.load_striped_mat(joinpath(@__DIR__, "../../experiments/", iname)) for iname in inames]
+const maxcnts = [typemax(Int),
+                 typemax(Int),
+                 typemax(Int),
+                 typemax(Int),
+                 typemax(Int),
+                 typemax(Int),
+                 typemax(Int),
+                 typemax(Int)]
+const specs = [(593.0 .+ [-20; -6:2:6; 20], # 15 mW, 0.09 ms
+                522.7 .+ [-15; -4.5:1.5:4.5; 15], # 12 mW, 0.12 ms
+                447.5 .+ [-10; -3:0.6:3; 5], # 9 mW, 0.16 ms
+                369.5 .+ [-5; -2:0.5:2; 5], # 6 mW, 0.27 ms
+                287.5 .+ [-5; -0.6:0.15:0.6; 5], # 3 mW, 0.9 ms
+                ),
+               (593.0 .+ [-30; -7.5:1.5:7.5; 30], # 15 mW, 0.1 ms
[…]

### 2020-09-07 plot_raman.jl

@@ -1,0 +1,84 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+# using DataStructures
+# using LsqFit
+using LibArchive
+
+using DelimitedFiles
+
+const fname = joinpath(@__DIR__, "../damop-2020/20MHz_linewidth_c3SigmaOnly_3322_80kHzConfinement.csv.zst")
+const data = LibArchive.Reader(fname) do reader
+    LibArchive.support_format_raw(reader)
+    LibArchive.support_filter_all(reader)
+    LibArchive.next_header(reader)
+    readdlm(reader, ',', skipstart=1)
+end
+const prefix = joinpath(@__DIR__, "imgs", "raman")
+
+fig = figure(figsize=[1, 1] * 4.8)
+
+ax0 = fig.add_subplot(111)    # The big subplot
+ax0.spines["top"].set_color("none")
+ax0.spines["bottom"].set_color("none")
+ax0.spines["left"].set_color("none")
+ax0.spines["right"].set_color("none")
+ax0.tick_params(labelcolor="w", top="off", bottom="off", left="off", right="off")
+ylabel("\$\\Omega_{Raman}\$ and \$\\Gamma_{scatter}\$ (\$2\\pi\\cdot \\mathrm{kHz})\$", fontsize="small")
+ax0.get_yaxis().set_label_coords(-0.13, 0.5)
+ax0.tick_params(axis="x", length=0)
+ax0.tick_params(axis="y", length=0)
+tax0 = ax0.twinx()
+tax0.tick_params(labelcolor="w", top="off", bottom="off", left="off", right="off")
+tax0.tick_params(axis="x", length=0)
+tax0.tick_params(axis="y", length=0)
+ylabel("\$\\Omega_{Raman}/\\Gamma_{scatter}\$", fontsize="small", color="C2")
+
+ax1 = fig.add_subplot(211)
+plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ 2π / 1000), "C0",
[…]

### 2020-09-10 paper.tex
Update on Overleaf.

@@
 
-Trapped neutral molecules, assembled in an array of optical tweezers, are a promising platform to study quantum infoqrmation and quantum simulations.
-1.
+Trapped neutral molecules, assembled in an array of optical tweezers, are a promising platform to study quantum information and quantum simulation. (more detail to add here about applications?).
+
+Production of ultracold molecules in optical tweezers is challenging due to their internal degrees of freedom including rotation and vibration.
+In certain molecular species with relatively closed cycling transitions, direct laser cooling remains a viable option.
+However, for many species, including NaCs, the vibrational branching ratios are unfavorable, making direct laser cooling challenging.
+In these systems, a bottom-up approach of assembling the molecule from its constituent atoms has been demonstrated both in bulk gas and in optical tweezers.
+The challenge in a bottom-up approach is the vastly different length scales between the free atoms and a ground state molecule, leading to small coupling between them.
+For atoms in the motional ground state in the tweezer,
+the average distance between the two atoms is about $1000a_0$.
+However, for the ground rovibrational molecule, the bond length is only around $4a_0$. Because of this, it is necessary to use an intermediate state
+with a size in between the initial and final states,
+and accomplish the transfer in two steps in order to increase the coupling.
+
+The traditional choice for such an intermediate state is a weakly-bound Feshbach molecule, which can be coherently produced by ramping a magnetic field across the Feshbach resonance \todo{cite our FB result}.
+However, this requires a suitable Feshbach resonance, which limits the generality of this technique.
+An alternative approach uses a weakly bound ground electronic molecular state as the intermediate state (I'm wondering how we can distinguish this weakly bound molecular state from the weakly-bound Feshbach molecule state, we can maybe specify typcial binding energies?
+"most weakly bound state of the low field ground state electronic potential" maybe?), populated by an optical Raman transition, schematically shown in figure \todo{}.
+In this scheme, a pair of Raman beams is used to drive the unbound, but confined, atoms to a bound molecular state via an excited molecular state.
+This approach minimizes the reliance on system specific properties
+and can therefore be more generally applied to creating other molecules. Such a transfer using an optical transition has been observed in previous experiments \todo{cite}.
+However, they either require the use of a narrow optical transition which limits the generality
+or were driving the transition incoherently due to scattering.
+
+%the requirement of a suitable FB resonance limits its generality. \todo{e.g. non-magnetic atoms?}
+
+%The size mismatch between the initial and final states cause a very small coupling between them,
+%which poses the biggest challege for for coherent creation of the molecule.
+
+% 1.
 we want to have a diverse species to tailor to different applications.
@@
 
-In this Letter, we survey theoretically the best electronic intermediate state, detuning, etc that balance coupling/transfer efficiency and photon scattering to demonstrate coherent association of a electronic ground-state molecule from two atoms.
-Because the electronic excited state we used are generic in most diatomic molecules, this technique is general....
+In this Letter, we theoretically determine the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering.
+Using these parameters, we demonstrate coherent association of a electronic ground-state molecule from two atoms via an optical Raman transition in an optical tweezer.
+
+% Because the electronic excited state we used are generic in most diatomic molecules, this technique is general....
 
@@
 
-For atoms in the motional ground state in the tweezer,
-the average distance between the two atoms is about $1000a_0$.
-However, for the ground rovibrational molecule, the bond length is only around $4a_0$.
-The size mismatch between the initial and final states cause a very small coupling between them,
-which poses the biggest challege for for coherent creation of the molecule.
-Because of this, it is necessary to use an intermediate state
-with a size in between the initial and final states,
-and accomplish the transfer in two steps in order to increase the coupling.
+%In this letter, we will present our result on coherent creation of a weakly bond molecule
+%using only optical transitions on a broad optical line for the first time.
 
-The traditional choice for such an intermediate state is a FB molecule \todo{cite our FB result}.
-However, the requirement of a suitable FB resonance limits its generality. \todo{e.g. non-magnetic atoms?}
-Instead, we selected a weakly bond molecular state as the intermediate state
-and we use an optical Raman transition as the first step transfer.
-This approach minimizes the reliance on system specific properties
-and can therefore be more generally applied to creating other molecules.
-Such a transfer using optical transition has been observed in previous experiments \todo{cite}.
-However, they either require the use of a narrow optical transition which limits the generality
-or were driving the transition incoherently due to scattering.
-In this letter, we will present our result on coherent creation of a weakly bond molecule
-using only optical transitions on a broad optical line for the first time.
+%The optical transfer scheme we use is shown in figure \todo{}. To drive the atoms from
+% We use an optical Raman transition to drive the system from the atomic initial state to a ground electronic molecular state.
+In order to reduce the size mismatch between the atomic and molecular states, we selected the first bound state for the 3322 spin state \todo{asymtopt to the 3322 threshold?} as our final state.
+\todo{move selection of intermediate state to intro?}.
+For similar reason, the natural choice for the intermediate excited molecular state is one with highly excited motional level.However, from our calculation (and experiment?), the smaller level space for high vibrational state and the smaller detuning from the atomic threshold increases the scattering rate of the molecular state which causes a reduced Raman Rabi frequency to decoherence rate ratio and a lower transfer efficiency.
+Therefore, in our experiment, we selected the v=0 state as the intermediate state for our Raman transition.
 
-Even for the first step transfer to a weakly bond molecular state,
-it is still a challenge to achieve high Raman Rabi frequency to drive this transition
-due to the wavefunction size mismatch with the excited molecular state.
-For this reason, previous experiments also use weakly bond molecular excited states
-in the Raman transition.
-However, in additional to a higher Raman Rabi frequency,
-this choice of state also increases the scattering during the transfer process for two reasons.
+Even for this first step transfer to a weakly bound molecular state, it is still a challenge to achieve high Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.
+Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential.
+In additional to the confinement, this value is related to the interaction between the two atoms.
+For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (add figure?).
+The increase in the coupling is proportional to (quote/cite Olive's equation?).
+For our system, among the stable spin combinations, 4422 and 3311 has a small scattering length of $\abs{a}=....$ respectively and 3322 has a large and negative scattering length.
+(interaction shift $\approx$ binding?) Thus, we use the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination.
+
+In addition to the choice of initial state, the choice of the intermediate state also plays a role.
+Previous experiments use weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency.
+However, this choice of state also increases the scattering during the transfer process for two reasons.
 Firstly, since for a typical molecular potential the spacing between states
 decreases with increasing vibrational levels,
-a weakly bond excited molecular state limits maximum usable detuning
-and therefore the effectiveness of scattering reduction
-by increasing the detuning for the Raman transition.
-Secondly, due to size similarity, the weakly bound molecular ground state has a strong coupling
-with the atomic excited state which contributes significantly to the total scattering rate.
+a weakly bound excited molecular state limits maximum usable detuning and therefore the effectiveness of scattering reduction by increasing the detuning for the Raman transition.
+Secondly, due to size similarity, the weakly bound molecular ground state has a strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
 The rate of such scattering process is proportional to $1/\delta_{thresh}^2$,
-where $\delta_{thresh}$ is the detuning from the dissociation threshold.
-This further increases the scattering rate for a weakly bond excited state.
-Based on these considerations, we calculated both the Raman Rabi frequency
-and the scattering rate at different detunings.
-As seen in figure (1....), despite a higher Raman Rabi frequency at the same detuning,
-the weakly bond state also has a much higher scattering rate
-and ultimately a smaller Rabi frequency to scattering at the optimal detuning.
+where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
+% This further increases the scattering rate for a weakly bond excited state.
+Based on these considerations, we calculated both the Raman Rabi frequency and the scattering rate at different detunings.
+As seen in figure (1....), despite a higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states.
 As a result, we use a deeply bound molecular excited state to drive the Raman transition.
@@
 
-In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
-Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance.
-In additional to the confinement, this value is related to the interaction between the two atoms.
-States with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (add figure?).
-The increase in the coupling is proportional to (quote/cite Olive's equation?).
-For our system, among the stable spin combinations, 4422 and 3311 has a small scattering length of $\abs{a}=....$ respectively and 3322 has a large and negative scattering length.
-(interaction shift $\approx$ binding?)
+%In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
 
@@
 The atoms are imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom during post selection.
-We then perform simutanious Raman sideband cooling (RSC) to cool both atoms into a single 3-dimentional motional ground state in the tweezers.
-After RSC, the Na tweezer is moved by sweeping the frequency on an acustical optical beam deflector (AOBD) to overlap with the Cs tweezer before smoothly ramping off so that the Na and Cs atoms are merged into the same tweezer \todo{cite}.
+We then perform simultaneous Raman sideband cooling (RSC) to cool both atoms into the 3-dimensional motional ground state of their optical tweezers.
+After RSC, the Na tweezer is moved by sweeping the frequency on an acoustical optical beam deflector (AOBD) to overlap with the Cs tweezer before smoothly ramping off rso that the Na and Cs atoms are merged into the same tweezer \todo{cite}.
 The spin states for the Na and Cs atoms after RSC and during the merge process are $|F=2,m_F=2\rangle$ and $|F=4,m_F=4\rangle$ respectively.
 This states combination has a low scattering length of $...
-a_0$ which allows the two atoms to be merged into the same tweezer with minimum pertubation on each other and remains in their motional ground state after the merge.
+a_0$ which allows the two atoms to be merged into the same tweezer with minimum pertubation on each other and thus they remain in the motional ground state after the merge.
 
-After preparing the Na and Cs atoms in the same tweezer in a single quantum state, we perform interaction shift spectroscopy using a Cs Raman transition to drive the Cs into the $|F=3,m_F=3\rangle$ state.
+After preparing the Na and Cs atoms in the same tweezer in a single quantum state, we need to drive the atoms into the large scattering length 3322 hyperfine combination.
+To do this, we perform interaction shift spectroscopy using a Cs Raman transition to drive the Cs into the $|F=3,m_F=3\rangle$ state (Is this really "performing spectroscopy"?
+Or should we just say we drive a Raman transfer to flip the spin).
 The new spin state combination has a larger scattering length of $...
@@
 This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of relative motional ground state.
-The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer.
+
+%The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..
 
 %% Transfer scheme
-
-The optical transfer scheme we used is shown in figure \todo{}.
-We use an optical Raman transition to drive the system from the atomic initial state to a
-ground electronic molecular state. In order to reduce the size mismatch between the atomic and molecular states,
-we selected the first bound state for the 3322 spin state \todo{asymtopt to the 3322 threshold?} as our final state. \todo{move selection of intermediate state to intro?}.
-For similar reason, the natural choice for the intermediate excited molecular state is one
-with highly excited motional level.
-However, from our calculation (and experiment?), the smaller level space for high
-vibrational state and the smaller detuning from the atomic threshold increases the
-the scattering rate of the molecular state which causes a reduced Raman Rabi frequency
-to decoherence rate ratio and a lower transfer efficiency.
-Therefore, in our experiment, we selected the v=0 state as the intermediate state for our
-Raman transition.
-
-The pulse sequence for the experiment can be seen in figure ().
+After the atoms are prepared in the 3322 hyperfine combination, we then perform the Raman transfer.
+The pulse sequence for this step is shown in figure ().
 Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal.
+The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time.
 After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simutaniously ramping up the power of a different frequency so that the total tweezer power remains unchanged.
 Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.
-The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition.
-Using the tweezer beam for the Raman transition also allow us to maximize the intensity of the Raman beams and minimize the transfer time.
 \todo{clarify coprop of Raman beam?}
-
-Figure () shows the geometry of the experiment setup.
-A $8.8\mathrm{G}$ B field was used to defines the quantization axis in the experiment and is applied perpendicular to the tweezer axis.
-The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
-
-%% Prediction
-
-This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288...
-GHz$ from our atomic state.
-The ground molecular state has not been observed previously in experimentally.
-Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state.
-Theory prediction was at $770...
-MHz$.
-\todo{more, mention/cite Jeremy}
 
@@
 
-We locate the Raman resonance for the atom to molecule transition at $770... MHz$ (figure \todo{}) with a $15 mW$ tweezer at $288... GHz$ which corresponds to a $... GHz$ single photon detuning.
-The background level of $...\%$ corresponds to the propability of preparing the two atoms in the relative motional ground state using interaction shift spectroscopy.
-When the atoms are transfered into molecule by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imagine step.
-
+We locate the Raman resonance for the atom to molecule transition at $770...
+MHz$ (figure \todo{}) with a $15 mW$ tweezer at $288...
+GHz$ which corresponds to a $...
+GHz$ single photon detuning.
+(We can maybe add information about the prediction here?)
+The background level of $...\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state using interaction shift spectroscopy (can this be considered "interaction shift spectroscopy"?).
+When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imaging step.
 We observed the narrowest linewidth of $....
@@
 This result is significantly different from the $1/\delta^2$ dependency expected from off-resonant scattering and suggests that the main source of the scattering is due to a broadband process that is not directly related to the $v=0$ excited state.
+(ASE filter?)
 
-(ASE filter?)
+%%%% Maybe this following section about the B field can be relegated to a figure caption?
+% Figure () shows the geometry of the experiment setup.
+A $8.8\mathrm{G}$ B field was used to defines the quantization axis in the experiment and is applied perpendicular to the tweezer axis.
+The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
+
+%% Prediction
+
+%This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288...
+GHz$ from our atomic state.
+The ground molecular state has not been observed previously in experimentally.
+Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state.
+Theory prediction was at $770...
+MHz$.
+\todo{more, mention/cite Jeremy}
 

### 2020-09-14 paper.tex
Update on Overleaf.

@@
 Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal.
-The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time.
-After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simutaniously ramping up the power of a different frequency so that the total tweezer power remains unchanged.
+The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time (also minimize source of scattering).
+After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged.
 Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.

### 2020-09-16 paper.tex
Format/whitespace

@@
   and lifetime up to $1 \mathrm{ms}$ \todo{number}. (center of mass motional state population.)
-  %We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition.
+  % We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition.
   This  technique is general (does not rely on narrow excited state linewidth) and could allow a wider range of molecular species to be assembled atom-by-atom.
@@
 
-%the requirement of a suitable FB resonance limits its generality. \todo{e.g. non-magnetic atoms?}
+% the requirement of a suitable FB resonance limits its generality. \todo{e.g. non-magnetic atoms?}
 
-%The size mismatch between the initial and final states cause a very small coupling between them,
-%which poses the biggest challege for for coherent creation of the molecule.
+% The size mismatch between the initial and final states cause a very small coupling between them,
+% which poses the biggest challege for for coherent creation of the molecule.
 
@@
 
-%In this letter, we will present our result on coherent creation of a weakly bond molecule
-%using only optical transitions on a broad optical line for the first time.
+% In this letter, we will present our result on coherent creation of a weakly bond molecule
+% using only optical transitions on a broad optical line for the first time.
 
-%The optical transfer scheme we use is shown in figure \todo{}. To drive the atoms from
+% The optical transfer scheme we use is shown in figure \todo{}. To drive the atoms from
 % We use an optical Raman transition to drive the system from the atomic initial state to a ground electronic molecular state.
@@
 
-%In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
+% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
 
@@
 
-%The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..
+% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..
 
@@
 (We can maybe add information about the prediction here?)
+%% Prediction
+% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288...
+GHz$ from our atomic state.
+The ground molecular state has not been observed previously in experimentally.
+Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state.
+Theory prediction was at $770...
+MHz$.
+\todo{more, mention/cite Jeremy}
 The background level of $...\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state using interaction shift spectroscopy (can this be considered "interaction shift spectroscopy"?).
@@
 
-%% Prediction
-
-%This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288...
-GHz$ from our atomic state.
-The ground molecular state has not been observed previously in experimentally.
-Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state.
-Theory prediction was at $770...
-MHz$.
-\todo{more, mention/cite Jeremy}
-
 B field dependency $... kHz/G$ which agrees with theory prediction of $... kHz/G$.

### 2020-09-17 paper.tex
WIP: result analysis

@@
 
-In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state.
-We also account for atomic state loss by measuring the single and two body lifetime for the atomic state (figure ...).
-The result suggests that our transfer has a Raman Rabi frequency of and the molecule we form has a lifetime of $...$.
-We can also directly verify this result by measuring the lifetime of the molecule directly.
-This is done by applying a reverse Raman pulse to dissociate the molecule back to atoms after a variable wait time.
-The result of the direct measurement shows a molecular lifetime consistent with our fitting of the Raman transition data.
+In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state (figure 3...).
+The effect due to atomic state loss was taken into account by measuring the single and two body lifetime of the atoms directly (figure 3...).
+The fit shows that we have a Raman Rabi frequency of $...$.
+The molecule we form has a lifetime of $...$ which is the main limitation on the fidelity of the transfer.
+The molecule lifetime can be verified directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (figure 3...).
+The result shows a molecular lifetime consistent with our fitting of the Raman transition data.
+
+The ratio of molecule scattering rate and the Rabi frequency is larger than the theory prediction.
+In order to understand the origin of this discrepancy, we measured the dependency of the Raman resonance as a function of the tweezer power and frequency.
+The important results from the fits are resonance frequency (light shift), Raman Rabi frequency, atomic lifetime and molecular lifetime, each provide us information about a different combination of physical processes.
+
+First we look at the change in resonance frequency.
+As a function of the tweezer power, we observed a linear dependency on the resonance frequency caused by the differential light shift between the atomic and molecular state (figure ?).
+When we vary the tweezer frequency around the $v=0$ excited state, we can further observe a $1/\delta$ component and a background component that is constant for different detunings.
+The background is caused by coupling to all the other excited states that are further away which is not very important in this case.
+The $1/\delta$ component, however, is due to the coupling to the $v=0$ excited state and from equation (?) we know that this is mainly due to the coupling between the excited and ground molecular states.
+From this, we can calculate a down leg matrix element of $....$ which is similar to what we calculated from theory (ref/sm theory).
+(make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$, also $\Omega$ vs $\Omega'$ for the single leg vs cross coupling number).
+
+(talk about blue side?)
+
+The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change in the atomic wavefunction caused by the change in confinement.
+The up leg matrix element scales with the short length atomic wavefunction amplitude which is 0.375 for weakly interaction particles.
+However, due to the strong interaction between the two atoms, this approximation breaks down.
+Instead, theory calculation shows that the scaling is very well approximated by a power of 0.29 within the range of confinement in our experiment.
+Combined with the intensity factor of the Raman beams, the Raman Rabi frequency should scale with 1.29 power of the tweezer intensity, which agrees with our experimental result.
+Similar to the light shift, there is also a background component and a $v=0$ component in the Raman Rabi frequency.
+The $v=0$ component predicts a up leg Rabi frequency of $...$ which is consistent with theory.
+Unfortunately, the background Raman Rabi frequency cancels the Rabi frequency for red detuning Raman transition which is one of the factors that decreases our transfer efficiency.
+(need blue side?)
+
+% Parameters: Light shift, Rabi frequency, atomic scattering rate, molecular scattering rate
+% Variables: detuning, power
+% Changes: background, single line
 

### 2020-09-18 paper.tex
WIP: result analysis

@@
 
-% Parameters: Light shift, Rabi frequency, atomic scattering rate, molecular scattering rate
-% Variables: detuning, power
-% Changes: background, single line
+Next, we look at the atomic loss rate during the transfer process.
+The atomic loss rate scales as the tweezer intensity to the 2.58th power but shows little to no dependency on the tweezer frequency.
+The lack of frequency dependency suggests that most of the atomic loss are due to the coupling to states other than the $v=0$ one.
+After substracing 0.58 from the power scaling due to the change in the up leg matrix element, the loss rate is proportional to the tweezer power squared.
+This is an evidence that the loss is likely caused by a two photon scattering process rather than one photon scattering.
+The strong power scaling causes a faster than expected loss rate for the atom.
+However, the atomic scattering is contribution only a small fraction of the total scattering rate so this is not the limiting factor for the transfer.
 
-The molecule lifetime measured in the experiment is $...$ larger than the expected value of $...$ calculated from .....
-By measuring the lifetime for different tweezer powers, we observed a linear dependency of the lifetime (fig ...).
-This confirms that the short lifetime is mainly caused by scattering from the tweezer light rather than the intrinsic lifetime of the molecule itself.
-Additionally, we also measured the loss rate as a function of the tweezer frequency (fig ...) which shows only a very weak dependency for a $...x$ change in the detuning from the $v=0$ excited state.
-This result is significantly different from the $1/\delta^2$ dependency expected from off-resonant scattering and suggests that the main source of the scattering is due to a broadband process that is not directly related to the $v=0$ excited state.
-(ASE filter?)
+Finally, we fit the scaling for the molecular loss rate.
+We observed a dependency on the detuning that is consistent with $1/\delta^2$ suggesting that the loss is indeed mostly coming from the $v=0$ excited state.
+(preliminary) We observed a power scaling power of $\approx1.2$ which is closed to the prediction for a single photon scattering process.
+The excited state line width calculated from the scattering rate is $...(1 GHz?)$ which is much larger than the theory prediction of $10 MHz$ as well as the $20 MHz$ upper bound from our previous PA measurements (cite).
+
+(ASE filter)
 

### 2020-09-19 paper.tex
Update on Overleaf.

@@
 \begin{document}
-\title{Coherent optical association of single molecules}
+\title{Coherent optical association of a single molecule}
 \author{Yichao Yu}
@@
 
-Trapped neutral molecules, assembled in an array of optical tweezers, are a promising platform to study quantum information and quantum simulation. (more detail to add here about applications?).
+% 1.
+we want to have a diverse species to tailor to different applications including precision measurements and quantum engineering.
+2.
+for the technique of associating atoms to form molecules, but so far all has been done with Feshbach association (before STIRAP), or in the case of Sr2, a narrow excited state.
+Previous work on near-threshold Raman transfer has been incoherent.
+%(suggested referees: Florian Shreck and Immanual Bloch, Tanya, Deep Gupta, DeMille)
 
-Production of ultracold molecules in optical tweezers is challenging due to their internal degrees of freedom including rotation and vibration.
+%Trapped neutral molecules, assembled in an array of optical tweezers, are a promising platform to study quantum information and quantum simulation. (more detail to add here about applications?).
+
+Diverse species of fully quantum controlled  ultracod molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and the studies of ultracold chemistry.
+While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules  below 1~mK~\cite{Norrgard2016}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the associations of ultracold atoms.
+%(any place to cite  molecular ion work?)
+
+Such ultracold molecular associating takes advantage of the much developed cooling and trapping techniques for atoms  as a starting point.
+To overcome the challenges of small wavefunction overlap and the large release of binding energy of converting atoms to deeply-bound molecules, an established two-step approach have been taken to first associate atom pairs into weakly-bound molecules, then transfer the molecules from one internal state  to a desired rovibrational and electronic state~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
+So far, all of such association process  utilize a magnetic Feshbach scattering resonance.
+The only exception is Sr$_2$~\cite{Reinaudi2012,Stellmer2012} where narrow excited states are available and optical association can be driven.
+The requirement of a Feshbach resonance to enhance atom-to-molecule wavefunction overlap (and the narrow excited state) limits the   generality of the association technique to  more diverse species of molecules which are needed (or picked) for a desired application.
+
+Here, we demonstrate coherent association of an atom pair to a weakly bound molecules using an optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state.
+Our scheme is based on theoretically determined most suitable vibrational state of the electronic excited state $c^3\Sigma$ that balances coupling/transfer efficiency and photon scattering.
+Furthermore, to reduce technical requirements such as intensity stability, etc , we choose a initial and final state ...
+This approach is general and can be use to associate other molecular species or large molecules atom-by-atom.
+%electronic the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering.
+Using these parameters, we demonstrate coherent association of a electronic ground-state molecule from two atoms via an optical Raman transition in an optical tweezer.
+
+%Production of ultracold molecules in optical tweezers is challenging due to their internal degrees of freedom including rotation and vibration.
 In certain molecular species with relatively closed cycling transitions, direct laser cooling remains a viable option.
@@
 The challenge in a bottom-up approach is the vastly different length scales between the free atoms and a ground state molecule, leading to small coupling between them.
-For atoms in the motional ground state in the tweezer,
-the average distance between the two atoms is about $1000a_0$.
-However, for the ground rovibrational molecule, the bond length is only around $4a_0$. Because of this, it is necessary to use an intermediate state
-with a size in between the initial and final states,
-and accomplish the transfer in two steps in order to increase the coupling.
+For atoms in the motional ground state in the tweezer, the average distance between the two atoms is about $1000a_0$.
+However, for the ground rovibrational molecule, the bond length is only around $4a_0$.
+Because of this, it is necessary to use an intermediate state with a size in between the initial and final states, and accomplish the transfer in two steps in order to increase the coupling.
 
-The traditional choice for such an intermediate state is a weakly-bound Feshbach molecule, which can be coherently produced by ramping a magnetic field across the Feshbach resonance \todo{cite our FB result}.
+%The traditional choice for such an intermediate state is a weakly-bound Feshbach molecule, which can be coherently produced by ramping a magnetic field across the Feshbach resonance \todo{cite our FB result}.
 However, this requires a suitable Feshbach resonance, which limits the generality of this technique.
@@
 In this scheme, a pair of Raman beams is used to drive the unbound, but confined, atoms to a bound molecular state via an excited molecular state.
-This approach minimizes the reliance on system specific properties
-and can therefore be more generally applied to creating other molecules. Such a transfer using an optical transition has been observed in previous experiments \todo{cite}.
-However, they either require the use of a narrow optical transition which limits the generality
-or were driving the transition incoherently due to scattering.
+This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules.
+Such a transfer using an optical transition has been observed in previous experiments \todo{cite}.
+However, they either require the use of a narrow optical transition which limits the generality or were driving the transition incoherently due to scattering.
 
@@
 % The size mismatch between the initial and final states cause a very small coupling between them,
-% which poses the biggest challege for for coherent creation of the molecule.
-
-% 1.
-we want to have a diverse species to tailor to different applications.
-2.
-but so far all has been done with Feshbach association (before STIRAP), or in the case of Sr2, a narrow excited state.
-Previous work on near-threshold Raman transfer has been incoherent.
-(suggested referees: Florian Shreck and Immanual Bloch)
-
-In this Letter, we theoretically determine the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering.
-Using these parameters, we demonstrate coherent association of a electronic ground-state molecule from two atoms via an optical Raman transition in an optical tweezer.
+% which poses the biggest challenge for for coherent creation of the molecule.
 
@@
 
-Even for this first step transfer to a weakly bound molecular state, it is still a challenge to achieve high Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.
-Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential.
-In additional to the confinement, this value is related to the interaction between the two atoms.
-For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (add figure?).
-The increase in the coupling is proportional to (quote/cite Olive's equation?).
-For our system, among the stable spin combinations, 4422 and 3311 has a small scattering length of $\abs{a}=....$ respectively and 3322 has a large and negative scattering length.
-(interaction shift $\approx$ binding?) Thus, we use the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination.
-
-In addition to the choice of initial state, the choice of the intermediate state also plays a role.
+While optical Raman transfer of atoms to molecules utilizing an electronic excited state has been shown previously\todo{cite}.
+Those demonstrations were  incoherent  where the signal comes from loss of population (and therefore more like spectroscopy and the transferred molecules cannot be further utilized).
+The challenge lies at  achieve high enough Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.
  Previous experiments use weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency.
@@
 (mention scattering/lightshift depends on up/down matrix element ratio?)
+
+Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential.
+In additional to the confinement, this value is related to the interaction between the two atoms.
+For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (add figure?).
+The increase in the coupling is proportional to (quote/cite Olive's equation?).
+For our system, among the stable spin combinations, 4422 and 3311 has a small scattering length of $\abs{a}=....$ respectively and 3322 has a large and negative scattering length.
+(interaction shift $\approx$ binding?) Thus, we use the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination.
 
@@
 
-\bibliography{paper}
+%\bibliography{paper}
+\bibliography{master_ref}
+\bibliographystyle{apsrev4-2}
 \end{document}

### 2020-09-19 paper.tex
whitespace, regenerate pdf
Reference

@@
 
-Diverse species of fully quantum controlled  ultracod molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and the studies of ultracold chemistry.
+Diverse species of fully quantum controlled  ultracod molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan2017}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and the studies of ultracold chemistry.
 While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules  below 1~mK~\cite{Norrgard2016}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the associations of ultracold atoms.

### 2020-09-20 paper.tex
Update on Overleaf.

--- 2020-09-19 paper.tex
@@
 
-Diverse species of fully quantum controlled  ultracod molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and the studies of ultracold chemistry.
+Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan2017}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and studies of ultracold chemistry.
 While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules  below 1~mK~\cite{Norrgard2016}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the associations of ultracold atoms.
 %(any place to cite  molecular ion work?)
+% cite recent doyle group result on cooling symmetric top molecule? FOR SURE, and other laser cooling works and electro-optical-cooling! Citations are not complete. Add them as you see fit.
 
-Such ultracold molecular associating takes advantage of the much developed cooling and trapping techniques for atoms  as a starting point.
-To overcome the challenges of small wavefunction overlap and the large release of binding energy of converting atoms to deeply-bound molecules, an established two-step approach have been taken to first associate atom pairs into weakly-bound molecules, then transfer the molecules from one internal state  to a desired rovibrational and electronic state~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
-So far, all of such association process  utilize a magnetic Feshbach scattering resonance.
-The only exception is Sr$_2$~\cite{Reinaudi2012,Stellmer2012} where narrow excited states are available and optical association can be driven.
-The requirement of a Feshbach resonance to enhance atom-to-molecule wavefunction overlap (and the narrow excited state) limits the   generality of the association technique to  more diverse species of molecules which are needed (or picked) for a desired application.
+Such ultracold molecular association takes advantage of the much developed cooling and trapping techniques for atoms  as a starting point.
+To overcome the challenges of small wavefunction overlap and the large release of binding energy of converting atoms to deeply-bound molecules, a  two-step approach have been established to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from one internal state  to a desired rovibrational and electronic state~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
+So far, all of such association process  utilize a magnetic Feshbach scattering resonance and  apply to bialkali molecules.
+The only exception is Sr$_2$~\cite{Reinaudi2012,Stellmer2012} where narrow linewidth excited states are available and optical association can be driven.
+The requirement of a Feshbach resonance to enhance atom-to-molecule wavefunction overlap or the narrow excited state lines limits the generality of the association technique to more diverse molecular species.
 
-Here, we demonstrate coherent association of an atom pair to a weakly bound molecules using an optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state.
-Our scheme is based on theoretically determined most suitable vibrational state of the electronic excited state $c^3\Sigma$ that balances coupling/transfer efficiency and photon scattering.
+Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using an optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state.
+Our scheme is based on theoretically determined most suitable vibrational state of the electronic excited state $c^3\Sigma^+$ that balances transfer coupling and photon scattering.
 Furthermore, to reduce technical requirements such as intensity stability, etc , we choose a initial and final state ...
@@
 
-(goes to SM?)
+%(goes to SM?)
 
 (mention scattering/lightshift depends on up/down matrix element ratio?)
+
+In addition to the intermediate state, the choice of the initial and final states are critical for both fundamental and technical reasons.
+A key difference in molecular association via a Raman process compared to Raman transfer between hyperfine states in atoms is that the matrix elements between the ground states and the excited state are greatly unbalanced.
+In particular, the matrix element between the molecule state and the excited state, $ \Omega_m $ is much larger than the matrix element between the free atom state and the excited state, $ \Omega_a $.
+To understand the effect of this inbalance, we consider a 3 level model, and ignore the presence of multiple excited states.
+The Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$ depends on both matrix elements, but the scattering rate predominantly comes from the final molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth and $ \Delta $ is the single photon detuning.
+Assuming the power of each Raman beam is equal, there is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning.
+Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
+Thus, a small $ \Omega_m/\Omega_a $ ratio is desired to be able to drive this transition coherently.
+In addition to this fundamental reason, there is also a technical advantage for having a $ \Omega_m/\Omega_a $ ratio to be as small(?
+or big) as possible.
+The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $.
+The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser needs to be stabilized to better than the inverse of this ratio, $ \Omega_a/\Omega_m $, to fluctuate by less than a linewidth.
+This becomes technically easier when $ \Omega_m/\Omega_a $ is smaller.
+(for our choice of states, this mean intensity fluctuation of less than 1\% or 0.1\%.)
 

### 2020-09-20 paper.tex
whitespace, regenerate PDF
Update on Overleaf.

@@
 Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using an optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state.
-Our scheme is based on theoretically determined most suitable vibrational state of the electronic excited state $c^3\Sigma^+$ that balances transfer coupling and photon scattering.
+Our scheme is based on a theoretically determined  vibrational state of the electronic excited state $c^3\Sigma^+$ that has the best transfer Rabi coupling to photon scattering ratio.
 Furthermore, to reduce technical requirements such as intensity stability, etc , we choose a initial and final state ...
-This approach is general and can be use to associate other molecular species or large molecules atom-by-atom.
+The choice of the states is general and can be applied to associate other molecular species or large molecules atom-by-atom.
 %electronic the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering.
@@
 % This further increases the scattering rate for a weakly bond excited state.
-Based on these considerations, we calculated both the Raman Rabi frequency and the scattering rate at different detunings.
+Based on these considerations, we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM).
 As seen in figure (1....), despite a higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states.
 As a result, we use a deeply bound molecular excited state to drive the Raman transition.
+(mention the trend, also v=12 will work as similarly as v=0)
 

### 2020-09-20 paper.tex
Figure 1 and 2 captions

@@
   \caption{Optical creation of single molecule from single atoms in tweezer.
-    (A) Schematics of the Raman transition. \todo{more about the states involved}
-    (B) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
-    \todo{Field strength, power, polarization description (pi)}
-    (C) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
-    This power is smoothly ramped down and the down leg power ramped up over $10\mu s$ while
-    maintaining the total power of the tweezer.
-    \todo{to minimize heating?}
-    \label{f-setup}
+    (A) Schematics of the optical transition from an atom pair to a weakly bound molecule.
+    The initial state is the relative motional ground state between the two atoms
+    and the final state is the first molecular bound state.
+    The transition is driven by a pair of laser frequencies matching the binding energy
+    of the molecule.
+    The lasers are detuned from an excited molecular state in the $c^3\Sigma$ potential
+    by $\Delta$ in order to suppress the scattering during the transfer.
+    (B) Comparison between using a weakly bound and a deeply bound excited state
+    as intermediate state for the Raman transition.
+    The deeply bound excited state (upper half $v=0$) has a smaller Raman Rabi frequency ($\Omega_{Raman}$)
+    compared to the weakly bound excited state (lower half $v=63$) at a given detuning.
+    However, the scattering rate ($\Gamma_{scatter}$) is also much lower,
+    which results in a larger Raman Rabi frequency to scattering rate ratio.
+    (C) Enhancement of short range wavefunction.
+    The large scattering length for the $Na(2,2),Cs(3,3)$ state creates an interaction shift
+    comparable to the axial trapping frequency.
+    This causes a significant change in the relative wavefunction especially at short
+    intranuclear distance ($R$).
+    Compared to other spin states with weaker interaction,
+    the wavefunction at short distance ($R<100\mathrm{\AA}$) is significantly enhanced.
+    \label{f-theory}
   }
@@
   \caption{
-    (A) Raman resonance from atomic state to molecular state, showing Fourier limited linewidth.
+    (A) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
+    The tweezer and Raman beam is focused through an objective to define the location of the
+    atoms and molecule.
+    We use a bias B field of $B_0=8.8 G$ alone the tweezer polarization
+    to define the quantization axis.
+    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
+    (B) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
+    When driving the Raman transition, the up leg power is smoothly ramped down and
+    the down leg power ramped up over $10\mu s$ while maintaining the total power of the tweezer.
+    This minimizes the heating on the atoms due to power fluctuation while maximizes the time
+    with maximum Raman Rabi frequency when the up and down leg powers are equal.
+    (C) Raman resonance from atomic state to molecular state, showing Fourier limited linewidth.
     \todo{states, time}

### 2020-09-20 paper.tex
Update on Overleaf.

@@
 
-While optical Raman transfer of atoms to molecules utilizing an electronic excited state has been shown previously\todo{cite}.
-Those demonstrations were  incoherent  where the signal comes from loss of population (and therefore more like spectroscopy and the transferred molecules cannot be further utilized).
+While optical Raman transfer of atoms to molecules utilizing an electronic excited state has been shown previously\cite{Wynar2000,Rom2004}.
+Those demonstrations were  incoherent  where the signal shows resonance loss of population and the transferred molecules cannot be further utilized(need to improve).
 The challenge lies at  achieve high enough Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.

### 2020-09-21 paper.tex
Update on Overleaf.

@@
 Such ultracold molecular association takes advantage of the much developed cooling and trapping techniques for atoms  as a starting point.
-To overcome the challenges of small wavefunction overlap and the large release of binding energy of converting atoms to deeply-bound molecules, a  two-step approach have been established to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from one internal state  to a desired rovibrational and electronic state~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
-So far, all of such association process  utilize a magnetic Feshbach scattering resonance and  apply to bialkali molecules.
-The only exception is Sr$_2$~\cite{Reinaudi2012,Stellmer2012} where narrow linewidth excited states are available and optical association can be driven.
-The requirement of a Feshbach resonance to enhance atom-to-molecule wavefunction overlap or the narrow excited state lines limits the generality of the association technique to more diverse molecular species.
+To overcome the challenges of small wavefunction overlap and the large release of binding energy of converting atoms to deeply-bound molecules, a  two-step approach has been established to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
+So far, all of such association processes  utilized a magnetic Feshbach scattering resonance and have been applied to bialkali molecules.
+The only exception is Sr$_2$ where narrow linewidth excited states are available and optical association can be driven~\cite{Reinaudi2012,Stellmer2012}.
+The requirement of a Feshbach resonance to enhance atom-to-molecule wavefunction overlap or the narrow excited state lines limits the generality of the association technique.
+%to more diverse molecular species.
 
-Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using an optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state.
+Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state.
 Our scheme is based on a theoretically determined vibrational state of the electronic excited state $c^3\Sigma^+$ that has the best transfer Rabi coupling to photon scattering ratio.
-Furthermore, to reduce technical requirements such as intensity stability, etc , we choose a initial and final state ...
-The choice of the states is general and can be applied to associate other molecular species or large molecules atom-by-atom.
+To further increase this ratio and reduce technical requirements such as intensity stability, we choose an initial and final state where the matrix elements with the excited state are as balanced as possible.
+This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
+%The choice of the states is general and can be applied to associate other molecular species or large molecules atom-by-atom with full quantum state control.
+(also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules)) %This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules.
 %electronic the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering.
@@
 
+% In this letter, we will present our result on coherent creation of a weakly bond molecule
+% using only optical transitions on a broad optical line for the first time.
+
+% The optical transfer scheme we use is shown in figure \todo{}. To drive the atoms from
+% We use an optical Raman transition to drive the system from the atomic initial state to a ground electronic molecular state.
+In order to reduce the size mismatch between the atomic and molecular states, we selected the first bound state for the 3322 spin state \todo{asymtopt to the 3322 threshold?} as our final state.
+\todo{move selection of intermediate state to intro?}.
+For similar reason, the natural choice for the intermediate excited molecular state is one with highly excited motional level.However, from our calculation (and experiment?), the smaller level space for high vibrational state and the smaller detuning from the atomic threshold increases the scattering rate of the molecular state which causes a reduced Raman Rabi frequency to decoherence rate ratio and a lower transfer efficiency.
+Therefore, in our experiment, we selected the v=0 state as the intermediate state for our Raman transition.
+
+%While optical Raman transfers of atoms to molecules utilizing an electronic excited state have been shown previously, the transfers were incoherent  where the resulting molecules were lost~\cite{Wynar2000,Rom2004}.
+
+The challenge of optical Raman transfers of atoms to molecules lies with achieving a high enough Raman Rabi frequency  due to the wavefunction size mismatch with the excited molecular state.
+While pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, this choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
+%Previous experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency.
+However, this choice of state also increases the scattering during the transfer process for two reasons.
+In general, scattering can be reduce by detuning away from resonance. However, we are constrained by the multi-level of molecules. 
+Firstly, since for a typical molecular potential the spacing between states
+decreases with increasing vibrational levels,
+a weakly bound excited molecular state limits the maximum usable detuning and therefore the effectiveness of scattering reduction by increasing the detuning for the Raman transition.
+Secondly, due to size similarity(?), the weakly bound molecular ground state has a strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
+The rate of such a scattering process is larger for the weakly bound states, and is proportional to $1/\delta_{thresh}^2$,
+where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
+% This further increases the scattering rate for a weakly bond excited state.
+Based on these considerations, we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM).
+As seen in figure (1....), we found a distinct regime from what have been explored previously, namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering ratio is much higher as compared to a weakly bound intermediate state.
+As a result, we use a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) to drive the Raman transition.
+(mention the trend, also v=12 will work as similarly as v=0)
+
+%higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states.
+As a result, we use a deeply bound molecular excited state to drive the Raman transition.
+
+%(goes to SM?)
+
+(mention scattering/lightshift depends on up/down matrix element ratio?)
+
+In addition to the intermediate state, the choice of the initial and final states are critical for both fundamental and technical reasons.
+A key difference in molecular association via a Raman process compared to Raman transfer between hyperfine states in atoms is that the matrix elements between the ground states and the excited state are greatly unbalanced.
+In particular, the matrix element between the molecule state and the excited state, $ \Omega_m $ is much larger than the matrix element between the free atom state and the excited state, $ \Omega_a $.
+To understand the effect of this imbalance, we consider a 3 level model, and ignore the presence of multiple excited states.
+The Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$ depends on both matrix elements, but the scattering rate predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth and $ \Delta $ is the single photon detuning.
+We choose the power of the Raman beams to be equal (this gives the smallest scattering), there is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning.
+Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
+Thus, a small $ \Omega_m/\Omega_a $ ratio is desired to be able to drive this transition coherently at smaller detunings where the Raman Rabi frequency will be larger.
+In addition to this fundamental reason, there is also a technical advantage for having a $ \Omega_m/\Omega_a $ ratio to be as small( KW: I think small, but open question whether we should always talk about $\Omega_m/\Omega_a$ or $ \Omega_a/\Omega_m$, KN: maybe $ \Omega_a/\Omega_m$ is better because it sounds more natural that we want to make it large?
+but either way.) as possible.
+The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $.
+The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser needs to be stabilized to better than the inverse of this ratio, $ \Omega_a/\Omega_m $, to fluctuate by less than a linewidth.
+This becomes technically easier when $ \Omega_m/\Omega_a $ is smaller.
+%(for our choice of states, this mean intensity fluctuation of less than 1\% or 0.1\%. KW: I mentioned this in next paragraph, does it still need to be mentioned here?)
+
+This ratio can be made smaller by increasing the coupling of the atomic state with the excited molecular state.
+Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential.
+In additional to the confinement, this value is related to the interaction between the two atoms.
+For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (add figure?).
+The increase in the coupling is proportional to (quote/cite Olive's equation?).
+For our system, among the stable spin combinations, 4422 and 3311 both have small scattering lengths of $\abs{a_{4422}}= 30.4a_0, \abs{a_{3311}} = 13.7a_0 $ respectively and 3322 has a large and negative scattering length of $ \abs{a_{3322}} = 693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
+In addition to the increased atomic coupling, $ \Omega_a $, with the 3322 hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly this spin combination also has reduced coupling, $ \Omega_m $, with the excited state when compared with the 4422 and 3311 bound states.
+Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_m/\Omega_a$ ratio of about 20 instead of a ratio of about 300 with the 4422 or 3311 combinations.
+This more favorable ratio also relaxes the technical requirement of intensity stability of $0.3 \% $ for the 4422 combination compared to $ 5\% $ for the 3322 combination.
+Thus, we use the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination.
+(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
+
+% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
 \begin{figure*}
@@
 \end{figure*}
-
-% In this letter, we will present our result on coherent creation of a weakly bond molecule
-% using only optical transitions on a broad optical line for the first time.
-
-% The optical transfer scheme we use is shown in figure \todo{}. To drive the atoms from
-% We use an optical Raman transition to drive the system from the atomic initial state to a ground electronic molecular state.
-In order to reduce the size mismatch between the atomic and molecular states, we selected the first bound state for the 3322 spin state \todo{asymtopt to the 3322 threshold?} as our final state.
-\todo{move selection of intermediate state to intro?}.
-For similar reason, the natural choice for the intermediate excited molecular state is one with highly excited motional level.However, from our calculation (and experiment?), the smaller level space for high vibrational state and the smaller detuning from the atomic threshold increases the scattering rate of the molecular state which causes a reduced Raman Rabi frequency to decoherence rate ratio and a lower transfer efficiency.
-Therefore, in our experiment, we selected the v=0 state as the intermediate state for our Raman transition.
-
-While optical Raman transfer of atoms to molecules utilizing an electronic excited state has been shown previously\cite{Wynar2000,Rom2004}.
-Those demonstrations were  incoherent  where the signal shows resonance loss of population and the transferred molecules cannot be further utilized(need to improve).
-The challenge lies at  achieve high enough Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.
- Previous experiments use weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency.
-However, this choice of state also increases the scattering during the transfer process for two reasons.
-Firstly, since for a typical molecular potential the spacing between states
-decreases with increasing vibrational levels,
-a weakly bound excited molecular state limits maximum usable detuning and therefore the effectiveness of scattering reduction by increasing the detuning for the Raman transition.
-Secondly, due to size similarity, the weakly bound molecular ground state has a strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
-The rate of such scattering process is proportional to $1/\delta_{thresh}^2$,
-where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
-% This further increases the scattering rate for a weakly bond excited state.
-Based on these considerations, we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM).
-As seen in figure (1....), despite a higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states.
-As a result, we use a deeply bound molecular excited state to drive the Raman transition.
-(mention the trend, also v=12 will work as similarly as v=0)
-
-%(goes to SM?)
-
-(mention scattering/lightshift depends on up/down matrix element ratio?)
-
-In addition to the intermediate state, the choice of the initial and final states are critical for both fundamental and technical reasons.
-A key difference in molecular association via a Raman process compared to Raman transfer between hyperfine states in atoms is that the matrix elements between the ground states and the excited state are greatly unbalanced.
-In particular, the matrix element between the molecule state and the excited state, $ \Omega_m $ is much larger than the matrix element between the free atom state and the excited state, $ \Omega_a $.
-To understand the effect of this inbalance, we consider a 3 level model, and ignore the presence of multiple excited states.
-The Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$ depends on both matrix elements, but the scattering rate predominantly comes from the final molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth and $ \Delta $ is the single photon detuning.
-Assuming the power of each Raman beam is equal, there is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning.
-Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
-Thus, a small $ \Omega_m/\Omega_a $ ratio is desired to be able to drive this transition coherently.
-In addition to this fundamental reason, there is also a technical advantage for having a $ \Omega_m/\Omega_a $ ratio to be as small(?
-or big) as possible.
-The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $.
-The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser needs to be stabilized to better than the inverse of this ratio, $ \Omega_a/\Omega_m $, to fluctuate by less than a linewidth.
-This becomes technically easier when $ \Omega_m/\Omega_a $ is smaller.
-(for our choice of states, this mean intensity fluctuation of less than 1\% or 0.1\%.)
-
-Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential.
-In additional to the confinement, this value is related to the interaction between the two atoms.
-For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (add figure?).
-The increase in the coupling is proportional to (quote/cite Olive's equation?).
-For our system, among the stable spin combinations, 4422 and 3311 has a small scattering length of $\abs{a}=....$ respectively and 3322 has a large and negative scattering length.
-(interaction shift $\approx$ binding?) Thus, we use the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination.
-
-% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
 

### 2020-09-22 paper.tex
Update on Overleaf.

@@
 The requirement of a Feshbach resonance to enhance atom-to-molecule wavefunction overlap or the narrow excited state lines limits the generality of the association technique.
-%to more diverse molecular species.
+% to more diverse species.
 
 Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state.
+The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.
 Our scheme is based on a theoretically determined vibrational state of the electronic excited state $c^3\Sigma^+$ that has the best transfer Rabi coupling to photon scattering ratio.
@@
 This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
-%The choice of the states is general and can be applied to associate other molecular species or large molecules atom-by-atom with full quantum state control.
-(also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules)) %This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules.
+%(also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))
+
+%This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules.
 %electronic the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering.
@@
   \caption{Optical creation of single molecule from single atoms in tweezer.
-    (A) Schematics of the optical transition from an atom pair to a weakly bound molecule.
+    (A) (should label $v'=0$ and $v'=63$) Schematics of the optical transition from an atom pair to a weakly bound molecule.
     The initial state is the relative motional ground state between the two atoms
@@
 %While optical Raman transfers of atoms to molecules utilizing an electronic excited state have been shown previously, the transfers were incoherent  where the resulting molecules were lost~\cite{Wynar2000,Rom2004}.
+%For a given excited intermediate state,
+%This can be understood by using a three level model. 
+%However, we are constrained by the multi-level of molecules. 
+%A key difference in molecular association via a Raman process compared to Raman transfer between hyperfine states in atoms is that the matrix elements between the ground states and the excited state are greatly unbalanced.
+In particular, the matrix element between the molecule state and the excited state, $ \Omega_m $ is much larger than the matrix element between the free atom state and the excited state, $ \Omega_a $.
+To understand the effect of this imbalance, we consider a 3 level model, and ignore the presence of multiple excited states.
 
 The challenge of optical Raman transfers of atoms to molecules lies with achieving a high enough Raman Rabi frequency  due to the wavefunction size mismatch with the excited molecular state.
-While pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, this choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
-%Previous experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency.
-However, this choice of state also increases the scattering during the transfer process for two reasons.
-In general, scattering can be reduce by detuning away from resonance. However, we are constrained by the multi-level of molecules. 
-Firstly, since for a typical molecular potential the spacing between states
+While pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
+Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with a minimal lost is the first key task.
+
+In a simplified model of a three-level system (as shown in Fig.~\ref{f-theory}), the initial atomic state, an excited intermediate state, and the target weakly-bound molecular state in the ground electronic potential are coupled by two photons, $\Omega_a$ and $\Omega_m$.
+%(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
+The Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$ depends on both the matrix element between the atomic state and the excited state, $ \Omega_a  $ and the matrix element between the molecular state and the excited state, $ \Omega_m $.
+Unlike in atoms, the two matrix elements, $ \Omega_m$ and $ \Omega_a$ are greatly imbalanced.
+Since $ \Omega_m $ is generally much larger than $ \Omega_a $ due to the wavefunction mismatch between the atomic state and the excited molecular state, the scattering rate predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth and $ \Delta $ is the single photon detuning.
+We choose the power of the Raman beams to be equal (which gives the largest Raman Rabi rate), so there is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning.
+Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
+To ensure a coherent process, larger detuning is preferred, but if it's too large, the Raman Rabi rate may become too small.
+With the multiple excited vibrational states present in a molecular potential, the total scattering rates becomes a sum of the scattering rates over all the states.
+Since for a typical molecular potential the spacing between states
 decreases with increasing vibrational levels,
-a weakly bound excited molecular state limits the maximum usable detuning and therefore the effectiveness of scattering reduction by increasing the detuning for the Raman transition.
-Secondly, due to size similarity(?), the weakly bound molecular ground state has a strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
-The rate of such a scattering process is larger for the weakly bound states, and is proportional to $1/\delta_{thresh}^2$,
+a weakly bound excited molecular state limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning for the Raman transition.
+Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state has a strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
+The rate of such a scattering process is larger for weakly bound molecular excited states, and is proportional to $1/\delta_{thresh}^2$,
 where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
 % This further increases the scattering rate for a weakly bond excited state.
-Based on these considerations, we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM).
+Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus, 
+we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM).
 As seen in figure (1....), we found a distinct regime from what have been explored previously, namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering ratio is much higher as compared to a weakly bound intermediate state.
@@
 
-In addition to the intermediate state, the choice of the initial and final states are critical for both fundamental and technical reasons.
-A key difference in molecular association via a Raman process compared to Raman transfer between hyperfine states in atoms is that the matrix elements between the ground states and the excited state are greatly unbalanced.
-In particular, the matrix element between the molecule state and the excited state, $ \Omega_m $ is much larger than the matrix element between the free atom state and the excited state, $ \Omega_a $.
-To understand the effect of this imbalance, we consider a 3 level model, and ignore the presence of multiple excited states.
-The Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$ depends on both matrix elements, but the scattering rate predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth and $ \Delta $ is the single photon detuning.
-We choose the power of the Raman beams to be equal (this gives the smallest scattering), there is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning.
-Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
+%In addition to the intermediate state, the choice of the initial and final states are critical for both fundamental and technical reasons.
 Thus, a small $ \Omega_m/\Omega_a $ ratio is desired to be able to drive this transition coherently at smaller detunings where the Raman Rabi frequency will be larger.
@@
 
+In addition to the intermediate state, the choice of the initial and final states are critical for both fundamental and technical reasons.
+As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio.
+The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio.
 This ratio can be made smaller by increasing the coupling of the atomic state with the excited molecular state.
@@
 In addition to the increased atomic coupling, $ \Omega_a $, with the 3322 hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly this spin combination also has reduced coupling, $ \Omega_m $, with the excited state when compared with the 4422 and 3311 bound states.
-Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_m/\Omega_a$ ratio of about 20 instead of a ratio of about 300 with the 4422 or 3311 combinations.
-This more favorable ratio also relaxes the technical requirement of intensity stability of $0.3 \% $ for the 4422 combination compared to $ 5\% $ for the 3322 combination.
+Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the 4422 or 3311 combinations.
+In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement.
+The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $.
+The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser needs to be stabilized to better than the inverse of this ratio, $ \Omega_a/\Omega_m $, to fluctuate by less than a linewidth.
+Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
 Thus, we use the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination.

### 2020-09-23 paper.tex
More figure captions for the results plots

@@
     with maximum Raman Rabi frequency when the up and down leg powers are equal.
-    (C) Raman resonance from atomic state to molecular state, showing Fourier limited linewidth.
-    \todo{states, time}
-    (B) Rabi oscillation on resonance
+    (C) Raman resonance from atomic state $Na(2,2)\ Cs(3,3)$ to the first molecular bound state
+    using a $0.1\mathrm{ms}$ pulse.
+    The full width half maximum (FWHM) of $8.43(81) \mathrm{kHz}$ of the resonance
+    is consistent with the FWHM for a coherent $0.1\mathrm{ms}$ $8.0 \mathrm{kHz}$ $\pi$ pulse.
+    (D) Raman pulse time scan on resonance. A decaying Rabi oscillation can be observed
+    proving the coherence of the Raman transfer process.
     \label{f-raman}}
@@
   \caption{
-    (A) Two-body atom lifetime in 15 mW of trap depth \todo{lifetime number,
-      subtraction of single body, photoassociation rate}
-    (B) Molecule lifetime in 15 mW of trap depth \todo{lifetime number}
+    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
+    with loss on the atom and molecule state. The combined fit is used to determine
+    both the Raman Rabi frequency and the loss rates.
+    (B) \todo{inset?} Two-body atom lifetime in $15 \mathrm{mW}$ of trap depth caused by
+    off-resonance photoassociation.
+    This is used to improve the fitting of the Raman transfer data.
+    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
+    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
+    The lifetime of $...$ is consistent with that measured from the Raman transition data.
     \label{f-lifetime}}
@@
   \includegraphics[height=4.5cm]{fig4.pdf}
-  \caption{Raman Rabi frequency vs detuning
+  \caption{Raman transition parameters as a function of tweezer/Raman power and detuning.
+    (A) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\delta$ with an offset.
+    (B) Atom loss rate scales as $P_{tweezer}^{2.58}$ suggesting a two-photon scattering loss.
+    (C) Molecular loss rate scales closed to $P_{tweezer}$ and follows $1/\delta^2$
+    with additional detuning independent background loss rate.
+    This result controdicts the our previous measurement of excited state lifetime
+    suggesting that there are additional loss mechanism that is not taken into account.
     \label{f-det}}

### 2020-09-24 paper.tex
Update on Overleaf.

@@
 So far, all of such association processes  utilized a magnetic Feshbach scattering resonance and have been applied to bialkali molecules.
-The only exception is Sr$_2$ where narrow linewidth excited states are available and optical association can be driven~\cite{Reinaudi2012,Stellmer2012}.
-The requirement of a Feshbach resonance to enhance atom-to-molecule wavefunction overlap or the narrow excited state lines limits the generality of the association technique.
+The only exception is Sr$_2$ where narrow linewidth excited states are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012}.
+The requirement of a Feshbach resonance to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of the association technique.
 % to more diverse species.
 
-Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state.
+Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state, schematically shown in Fig.~\ref{f-theory}.
 The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.
-Our scheme is based on a theoretically determined vibrational state of the electronic excited state $c^3\Sigma^+$ that has the best transfer Rabi coupling to photon scattering ratio.
+Our scheme is based on using a theoretically determined vibrational state of the electronic excited state $c^3\Sigma^+$ that has the best transfer Rabi coupling to photon scattering ratio.
 To further increase this ratio and reduce technical requirements such as intensity stability, we choose an initial and final state where the matrix elements with the excited state are as balanced as possible.
-This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
+This approach minimizes the reliance on system specific properties and could therefore be applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
 %(also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))
@@
 
-The challenge of optical Raman transfers of atoms to molecules lies with achieving a high enough Raman Rabi frequency  due to the wavefunction size mismatch with the excited molecular state.
+The challenge of optical Raman association of molecules from atoms lies with achieving a high enough Raman Rabi frequency despite the wavefunction size mismatch between the atomic state and the excited molecular state.
 While pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
-Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with a minimal lost is the first key task.
+Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with minimal loss is the first key task.
 
-In a simplified model of a three-level system (as shown in Fig.~\ref{f-theory}), the initial atomic state, an excited intermediate state, and the target weakly-bound molecular state in the ground electronic potential are coupled by two photons, $\Omega_a$ and $\Omega_m$.
+In a simplified model of a three-level system (as shown in Fig.~\ref{f-theory}), we consider the initial atomic state, an excited intermediate state, and the target weakly-bound molecular state in the ground electronic potential.
+The initial atomic state and target weakly-bound state are coupled by two photons, $\Omega_a$ and $\Omega_m$ to the excited intermediate state, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
-The Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$ depends on both the matrix element between the atomic state and the excited state, $ \Omega_a  $ and the matrix element between the molecular state and the excited state, $ \Omega_m $.
-Unlike in atoms, the two matrix elements, $ \Omega_m$ and $ \Omega_a$ are greatly imbalanced.
-Since $ \Omega_m $ is generally much larger than $ \Omega_a $ due to the wavefunction mismatch between the atomic state and the excited molecular state, the scattering rate predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth and $ \Delta $ is the single photon detuning.
-We choose the power of the Raman beams to be equal (which gives the largest Raman Rabi rate), so there is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning.
+The Raman Rabi Rate for a detuned transfer, $ \Omega_a\Omega_m / 2\Delta$ depends on both of these matrix elements and the single photon detuning.
+Unlike for Raman transitions in atoms, the two matrix elements, $ \Omega_m$ and $ \Omega_a$ are greatly imbalanced.
+Since $ \Omega_m $ is generally much larger than $ \Omega_a $ due to the wavefunction mismatch between the atomic state and the excited molecular state, the scattering rate predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth.
+We choose the power of the Raman beams to be equal (which gives the largest Raman Rabi rate at a fixed total power), so there is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning.
 Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
-To ensure a coherent process, larger detuning is preferred, but if it's too large, the Raman Rabi rate may become too small.
-With the multiple excited vibrational states present in a molecular potential, the total scattering rates becomes a sum of the scattering rates over all the states.
-Since for a typical molecular potential the spacing between states
-decreases with increasing vibrational levels,
-a weakly bound excited molecular state limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning for the Raman transition.
-Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state has a strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
-The rate of such a scattering process is larger for weakly bound molecular excited states, and is proportional to $1/\delta_{thresh}^2$,
+To ensure a coherent process, larger detuning is preferred.
+
+With the multiple excited vibrational states present in a molecular potential, the total scattering rates becomes a sum of the scattering rates over all the states, and there are many possible intermediate states to choose from.
+To obtain the full picture, we perform a full calculation of the Raman Rabi frequency and scattering rate at different detunings (full result in SM).
+As shown in figure ~\ref{f-theory}, the ratio of the Raman Rabi rate to scattering rate can be made better for more deeply bound states compared to weakly bound states.
+For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus %Since for a typical molecular potential the spacing between states
+%decreases with increasing vibrational levels,
+%a weakly bound excited molecular state 
+limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
+Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state has strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
+The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$,
 where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
@@
 Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus, 
-we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM).
-As seen in figure (1....), we found a distinct regime from what have been explored previously, namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering ratio is much higher as compared to a weakly bound intermediate state.
+% we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in figure (1....), 
+we found a distinct optimal regime from what has been explored experimentally previously.
+Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state.
 As a result, we use a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) to drive the Raman transition.
@@
 
-In addition to the intermediate state, the choice of the initial and final states are critical for both fundamental and technical reasons.
+In addition to the intermediate state, the choice of the initial and final states is critical.
 As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio.
-The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio.
+The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the overall Raman Rabi Rate.
 This ratio can be made smaller by increasing the coupling of the atomic state with the excited molecular state.
 Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential.
-In additional to the confinement, this value is related to the interaction between the two atoms.
+In addition to the confinement, this value is related to the interaction between the two atoms.
 For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (add figure?).
@@
 Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the 4422 or 3311 combinations.
-In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement.
+In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation.
 The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $.
-The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser needs to be stabilized to better than the inverse of this ratio, $ \Omega_a/\Omega_m $, to fluctuate by less than a linewidth.
+The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth.
 Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.

### 2020-09-24 paper.tex
White space
Update on Overleaf.

@@
 
-In a simplified model of a three-level system (as shown in Fig.~\ref{f-theory}), we consider the initial atomic state, an excited intermediate state, and the target weakly-bound molecular state in the ground electronic potential.
+In a simplified model of a three-level system (as shown in Fig.~\ref{f-theory}), we consider the initial atomic state, the target weakly-bound molecular state coupled to an excited intermediate state, and the target weakly-bound molecular state in the ground electronic potential.
 The initial atomic state and target weakly-bound state are coupled by two photons, $\Omega_a$ and $\Omega_m$ to the excited intermediate state, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.

### 2020-09-24 plot_exp_data.jl
Include Raman fit in fig 3

@@ -188,6 +188,25 @@ const plot_time = linspace(0, 0.45, 1000)
 const plot_pa_time = linspace(0, 25, 1000)
 const plot_m_time = linspace(0, 0.32, 1000)
 
+figure()
+ratio_00, uncs_00 = get_ratio_val(data_nacs_00)
+v00 = model_2d(0, 0, param_1)
+errorbar([param_1[3]], [ratio_00], [uncs_00], fmt="C0.", label="0.00 ms")
+plot([plot_freq_lo, plot_freq_hi], [v00, v00], "C0-")
+NaCsPlot.plot_survival_data(data_nacs_05, fmt="C1.", label="0.05 ms")
+plot(plot_freq, model_2d.(0.05, plot_freq, (param_1,)), "C1")
+NaCsPlot.plot_survival_data(data_nacs_06, fmt="C2.", label="0.06 ms")
+plot(plot_freq, model_2d.(0.06, plot_freq, (param_2,)), "C2")
+NaCsPlot.plot_survival_data(data_nacs_10, fmt="C3.", label="0.10 ms")
+plot(plot_freq, model_2d.(0.10, plot_freq, (param_1,)), "C3")
+NaCsPlot.plot_survival_data(data_nacs_28, fmt="C4.", label="0.28 ms")
+plot(plot_freq, model_2d.(0.28, plot_freq, (param_1,)), "C4")
+legend(fontsize="x-small", loc="lower right")
+grid()
+xlabel("2-Photon Detuning (770XXX kHz)")
+ylabel("Two-body survival")
+NaCsPlot.maybe_save("$(prefix)_raman_det")
+
 # figure(figsize=[12.6, 11.2])
 
 # subplot(2, 2, 1)

### 2020-09-24 paper.tex
Update on Overleaf.

--- 2020-09-24 paper.tex
@@
 
-In a simplified model of a three-level system (as shown in Fig.~\ref{f-theory}), we consider the initial atomic state, an excited intermediate state, and the target weakly-bound molecular state in the ground electronic potential.
-The initial atomic state and target weakly-bound state are coupled by two photons, $\Omega_a$ and $\Omega_m$ to the excited intermediate state, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.
+In a simplified model of a three-level system (as shown in Fig.~\ref{f-theory}), we consider the initial atomic state, the target weakly-bound molecular state coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)

### 2020-09-24 paper.tex
Update on Overleaf.

@@
 
-The challenge of optical Raman association of molecules from atoms lies with achieving a high enough Raman Rabi frequency despite the wavefunction size mismatch between the atomic state and the excited molecular state.
+%The challenge of optical Raman association of molecules from atoms lies with achieving a high enough Raman Rabi frequency despite the wavefunction size mismatch between the atomic state and the excited molecular state.
 While pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
@@
 To ensure a coherent process, larger detuning is preferred.
+However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
+With the multiple excited vibrational states present in a molecular potential, the total scattering rates becomes a sum of the scattering rates over all the states, and there are many possible intermediate states to choose from.
 
-With the multiple excited vibrational states present in a molecular potential, the total scattering rates becomes a sum of the scattering rates over all the states, and there are many possible intermediate states to choose from.
 To obtain the full picture, we perform a full calculation of the Raman Rabi frequency and scattering rate at different detunings (full result in SM).

### 2020-09-24 paper.tex
Update on Overleaf.

@@
 While pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
-Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with minimal loss is the first key task.
+%Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with minimal loss is the first key task.
 
@@
 With the multiple excited vibrational states present in a molecular potential, the total scattering rates becomes a sum of the scattering rates over all the states, and there are many possible intermediate states to choose from.
+
+Pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, but such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
 

### 2020-09-24 paper.tex
Update on Overleaf.

@@
 
-Pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, but such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
+Pioneering experiments used weakly bound molecular excited states in the Raman transition to en Raman Rabi frequency, but such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
 

### 2020-09-24 paper.tex
Update on Overleaf.

@@
 
-Pioneering experiments used weakly bound molecular excited states in the Raman transition to en Raman Rabi frequency, but such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
+Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency, but such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
 

### 2020-09-24 paper.tex
Update on Overleaf.

@@
 Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency, but such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
+For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
+Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state has strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
+The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$,
+where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
 
@@
 As shown in figure ~\ref{f-theory}, the ratio of the Raman Rabi rate to scattering rate can be made better for more deeply bound states compared to weakly bound states.
-For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus %Since for a typical molecular potential the spacing between states
+%Since for a typical molecular potential the spacing between states
 %decreases with increasing vibrational levels,
 %a weakly bound excited molecular state
-limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
-Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state has strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
-The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$,
-where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
+
 % This further increases the scattering rate for a weakly bond excited state.

### 2020-09-24 paper.tex
Update on Overleaf.

@@
 However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
-With the multiple excited vibrational states present in a molecular potential, the total scattering rates becomes a sum of the scattering rates over all the states, and there are many possible intermediate states to choose from.
+With the multiple excited vibrational states present in a molecular potential, the total scattering rates and Rabi rates becomes a sum of the scattering rates and Rabi rates over all the states, and there are many possible intermediate states to choose from.
 
-Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency, but such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
+Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency.
+However, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
 For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
 Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state has strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
-The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$,
-where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
+The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold.
+(Should we also mention scattering of the atomic initial state too?
+This should affect the Raman process as well)
 
-To obtain the full picture, we perform a full calculation of the Raman Rabi frequency and scattering rate at different detunings (full result in SM).
+To obtain a complete picture, we perform a full calculation of the Raman Rabi frequency and scattering rate at different detunings (full result in SM).
 As shown in figure ~\ref{f-theory}, the ratio of the Raman Rabi rate to scattering rate can be made better for more deeply bound states compared to weakly bound states.
@@
 %a weakly bound excited molecular state
-
 % This further increases the scattering rate for a weakly bond excited state.
-Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
+%Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
 % we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in figure (1....),
-we found a distinct optimal regime from what has been explored experimentally previously.
+%we found a distinct optimal regime from what has been explored experimentally previously. 
 Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state.
-As a result, we use a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) to drive the Raman transition.
+As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) to drive the Raman transition.
 (mention the trend, also v=12 will work as similarly as v=0)
@@
 The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the overall Raman Rabi Rate.
-This ratio can be made smaller by increasing the coupling of the atomic state with the excited molecular state.
+This ratio can be made larger by increasing the coupling of the atomic state with the excited molecular state.
 Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential.
@@
 Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
-Thus, we use the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination.
+Thus, we choose the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination.
 (We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
@@
 %% Preparation
+To perform the Raman transfer, we use our apparatus described in our previous work~\cite{Liu2019}.
 Our experiment begins by loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into an optical tweezer from a dual-species MOT\todo{cite na loading paper} into separate optical tweezers.
@@
 After preparing the Na and Cs atoms in the same tweezer in a single quantum state, we need to drive the atoms into the large scattering length 3322 hyperfine combination.
-To do this, we perform interaction shift spectroscopy using a Cs Raman transition to drive the Cs into the $|F=3,m_F=3\rangle$ state (Is this really "performing spectroscopy"?
-Or should we just say we drive a Raman transfer to flip the spin).
-The new spin state combination has a larger scattering length of $...
-a_0$ which generates a interaction shift of $...
-kHz$ in the tweezer.
+To do this, we perform a spin flip taking into account the interaction shift~\cite{Hood2019} using a Cs Raman transition to drive the Cs atom into the $|F=3,m_F=3\rangle$ state.
+The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
 This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of relative motional ground state.
@@
 
-We locate the Raman resonance for the atom to molecule transition at $770...
+Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770...
 MHz$ (figure \todo{}) with a $15 mW$ tweezer at $288...

### 2020-09-24 plot_exp_data.jl
Shift detuning plot axis

@@ -188,22 +188,27 @@ const plot_time = linspace(0, 0.45, 1000)
 const plot_pa_time = linspace(0, 25, 1000)
 const plot_m_time = linspace(0, 0.32, 1000)
 
+const data_nacs_05′ = NaCsData.map_params((i, v)->v - param_1[3], data_nacs_05)
+const data_nacs_06′ = NaCsData.map_params((i, v)->v - param_1[3], data_nacs_06)
+const data_nacs_10′ = NaCsData.map_params((i, v)->v - param_1[3], data_nacs_10)
+const data_nacs_28′ = NaCsData.map_params((i, v)->v - param_1[3], data_nacs_28)
+
 figure()
 ratio_00, uncs_00 = get_ratio_val(data_nacs_00)
 v00 = model_2d(0, 0, param_1)
-errorbar([param_1[3]], [ratio_00], [uncs_00], fmt="C0.", label="0.00 ms")
-plot([plot_freq_lo, plot_freq_hi], [v00, v00], "C0-")
-NaCsPlot.plot_survival_data(data_nacs_05, fmt="C1.", label="0.05 ms")
-plot(plot_freq, model_2d.(0.05, plot_freq, (param_1,)), "C1")
-NaCsPlot.plot_survival_data(data_nacs_06, fmt="C2.", label="0.06 ms")
-plot(plot_freq, model_2d.(0.06, plot_freq, (param_2,)), "C2")
-NaCsPlot.plot_survival_data(data_nacs_10, fmt="C3.", label="0.10 ms")
-plot(plot_freq, model_2d.(0.10, plot_freq, (param_1,)), "C3")
-NaCsPlot.plot_survival_data(data_nacs_28, fmt="C4.", label="0.28 ms")
-plot(plot_freq, model_2d.(0.28, plot_freq, (param_1,)), "C4")
+errorbar([0.0], [ratio_00], [uncs_00], fmt="C0.", label="0.00 ms")
+plot([plot_freq_lo, plot_freq_hi] .- param_1[3], [v00, v00], "C0-")
+NaCsPlot.plot_survival_data(data_nacs_05′, fmt="C1.", label="0.05 ms")
+plot(plot_freq .- param_1[3], model_2d.(0.05, plot_freq, (param_1,)), "C1")
+NaCsPlot.plot_survival_data(data_nacs_06′, fmt="C2.", label="0.06 ms")
[…]

### 2020-09-24 paper.tex
Figure references

@@
 
-Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state, schematically shown in Fig.~\ref{f-theory}.
+Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state, schematically shown in Fig.~\ref{f-theory}A.
 The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.
@@
 
-In a simplified model of a three-level system (as shown in Fig.~\ref{f-theory}), we consider the initial atomic state, the target weakly-bound molecular state coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.
+In a simplified model of a three-level system (as shown in Fig.~\ref{f-theory}A), we consider the initial atomic state, the target weakly-bound molecular state coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
@@
 To obtain a complete picture, we perform a full calculation of the Raman Rabi frequency and scattering rate at different detunings (full result in SM).
-As shown in figure ~\ref{f-theory}, the ratio of the Raman Rabi rate to scattering rate can be made better for more deeply bound states compared to weakly bound states.
+As shown in Fig.~\ref{f-theory}B, the ratio of the Raman Rabi rate to scattering rate can be made better for more deeply bound states compared to weakly bound states.
 %Since for a typical molecular potential the spacing between states
@@
 %Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
-% we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in figure (1....),
+% we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in Fig.~\ref{f-theory}B,
 %we found a distinct optimal regime from what has been explored experimentally previously.
@@
 In addition to the confinement, this value is related to the interaction between the two atoms.
-For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (add figure?).
+For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}C).
 The increase in the coupling is proportional to (quote/cite Olive's equation?).
@@
 After the atoms are prepared in the 3322 hyperfine combination, we then perform the Raman transfer.
-The pulse sequence for this step is shown in figure ().
+The pulse sequence for this step is shown in Fig.~\ref{f-raman}B.
 Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal.
@@
 Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770...
-MHz$ (figure \todo{}) with a $15 mW$ tweezer at $288...
+MHz$ (Fig.~\ref{f-raman}C) with a $15 mW$ tweezer at $288...
 GHz$ which corresponds to a $...
@@
 In order to verify the coherence of the transfer directly, we fixed the Raman frequency on the resonance and scanned the pulse time.
-figure ...
-shows the observed Rabi oscillation between the atomic and molecular states.
+Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states.
 Fitting the data with a decaying Rabi oscillation suggests that $..\%$ of initial ground state atoms are transfered into the molecular state.
 
-In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state (figure 3...).
-The effect due to atomic state loss was taken into account by measuring the single and two body lifetime of the atoms directly (figure 3...).
+In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state (Fig.~\ref{f-lifetime}A).
+The effect due to atomic state loss was taken into account by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B).
 The fit shows that we have a Raman Rabi frequency of $...$.
 The molecule we form has a lifetime of $...$ which is the main limitation on the fidelity of the transfer.
-The molecule lifetime can be verified directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (figure 3...).
+The molecule lifetime can be verified directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C).
 The result shows a molecular lifetime consistent with our fitting of the Raman transition data.
@@
 First we look at the change in resonance frequency.
-As a function of the tweezer power, we observed a linear dependency on the resonance frequency caused by the differential light shift between the atomic and molecular state (figure ?).
+As a function of the tweezer power, we observed a linear dependency on the resonance frequency caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
 When we vary the tweezer frequency around the $v=0$ excited state, we can further observe a $1/\delta$ component and a background component that is constant for different detunings.
@@
 
-The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change in the atomic wavefunction caused by the change in confinement.
+The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change in the atomic wavefunction caused by the change in confinement (Fig.~\ref{f-det}?).
 The up leg matrix element scales with the short length atomic wavefunction amplitude which is 0.375 for weakly interaction particles.
@@
 
-Next, we look at the atomic loss rate during the transfer process.
+Next, we look at the atomic loss rate during the transfer process. (Fig.~\ref{f-det}?)
 The atomic loss rate scales as the tweezer intensity to the 2.58th power but shows little to no dependency on the tweezer frequency.
@@
 
-Finally, we fit the scaling for the molecular loss rate.
+Finally, we fit the scaling for the molecular loss rate. (Fig.~\ref{f-det}?)
 We observed a dependency on the detuning that is consistent with $1/\delta^2$ suggesting that the loss is indeed mostly coming from the $v=0$ excited state.

### 2020-09-30 paper.tex
Clean up, regenerate pdf
Update on Overleaf.

@@
   % We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition.
-  This technique is general (does not rely on narrow excited state linewidth) and could allow a wider range of molecular species to be assembled atom-by-atom.
+  This technique is general without relying on narrow excited state lines or Feshbach resonances and could allow a wider range of molecular species to be assembled atom-by-atom.
 \end{abstract}
@@
 Previous work on near-threshold Raman transfer has been incoherent.
-%(suggested referees: Florian Shreck and Immanual Bloch, Tanya, Deep Gupta, DeMille)
+% (suggested referees: Florian Shreck and Immanual Bloch, Tanya, Deep Gupta, DeMille)
 
-%Trapped neutral molecules, assembled in an array of optical tweezers, are a promising platform to study quantum information and quantum simulation. (more detail to add here about applications?).
+% Trapped neutral molecules, assembled in an array of optical tweezers, are a promising platform to study quantum information and quantum simulation. (more detail to add here about applications?).
 
-Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan2017}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and studies of ultracold chemistry.
-While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules  below 1~mK~\cite{Norrgard2016}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the associations of ultracold atoms.
-%(any place to cite  molecular ion work?)
+Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan2017}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111}.
+While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016, Mitra1366}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the association of ultracold atoms.
+% (any place to cite  molecular ion work?)
 % cite recent doyle group result on cooling symmetric top molecule? FOR SURE, and other laser cooling works and electro-optical-cooling! Citations are not complete. Add them as you see fit.
@@
 The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.
-Our scheme is based on using a theoretically determined vibrational state of the electronic excited state $c^3\Sigma^+$ that has the best transfer Rabi coupling to photon scattering ratio.
+Our scheme is based on using a theoretically determined vibrational state of the electronic excited state $c^3\Sigma^+$ that has the best raman Rabi frequency to photon scattering ratio.
 To further increase this ratio and reduce technical requirements such as intensity stability, we choose an initial and final state where the matrix elements with the excited state are as balanced as possible.
 This approach minimizes the reliance on system specific properties and could therefore be applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
-%(also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))
+% (also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))
 
-%This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules.
-%electronic the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering.
+% This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules.
+% electronic the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering.
 Using these parameters, we demonstrate coherent association of a electronic ground-state molecule from two atoms via an optical Raman transition in an optical tweezer.
 
-%Production of ultracold molecules in optical tweezers is challenging due to their internal degrees of freedom including rotation and vibration.
+% Production of ultracold molecules in optical tweezers is challenging due to their internal degrees of freedom including rotation and vibration.
 In certain molecular species with relatively closed cycling transitions, direct laser cooling remains a viable option.
@@
 
-%The traditional choice for such an intermediate state is a weakly-bound Feshbach molecule, which can be coherently produced by ramping a magnetic field across the Feshbach resonance \todo{cite our FB result}.
+% The traditional choice for such an intermediate state is a weakly-bound Feshbach molecule, which can be coherently produced by ramping a magnetic field across the Feshbach resonance \todo{cite our FB result}.
 However, this requires a suitable Feshbach resonance, which limits the generality of this technique.
@@
 
-%While optical Raman transfers of atoms to molecules utilizing an electronic excited state have been shown previously, the transfers were incoherent  where the resulting molecules were lost~\cite{Wynar2000,Rom2004}.
-%For a given excited intermediate state,
-%This can be understood by using a three level model.
-%However, we are constrained by the multi-level of molecules.
-%A key difference in molecular association via a Raman process compared to Raman transfer between hyperfine states in atoms is that the matrix elements between the ground states and the excited state are greatly unbalanced.
+% While optical Raman transfers of atoms to molecules utilizing an electronic excited state have been shown previously, the transfers were incoherent  where the resulting molecules were lost~\cite{Wynar2000,Rom2004}.
+% For a given excited intermediate state,
+% This can be understood by using a three level model.
+% However, we are constrained by the multi-level of molecules.
+% A key difference in molecular association via a Raman process compared to Raman transfer between hyperfine states in atoms is that the matrix elements between the ground states and the excited state are greatly unbalanced.
 In particular, the matrix element between the molecule state and the excited state, $ \Omega_m $ is much larger than the matrix element between the free atom state and the excited state, $ \Omega_a $.
@@
 
-%The challenge of optical Raman association of molecules from atoms lies with achieving a high enough Raman Rabi frequency despite the wavefunction size mismatch between the atomic state and the excited molecular state.
+% The challenge of optical Raman association of molecules from atoms lies with achieving a high enough Raman Rabi frequency despite the wavefunction size mismatch between the atomic state and the excited molecular state.
 While pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
-%Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with minimal loss is the first key task.
+% Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with minimal loss is the first key task.
 
-In a simplified model of a three-level system (as shown in Fig.~\ref{f-theory}A), we consider the initial atomic state, the target weakly-bound molecular state coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.
+The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
-The Raman Rabi Rate for a detuned transfer, $ \Omega_a\Omega_m / 2\Delta$ depends on both of these matrix elements and the single photon detuning.
-Unlike for Raman transitions in atoms, the two matrix elements, $ \Omega_m$ and $ \Omega_a$ are greatly imbalanced.
-Since $ \Omega_m $ is generally much larger than $ \Omega_a $ due to the wavefunction mismatch between the atomic state and the excited molecular state, the scattering rate predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth.
-We choose the power of the Raman beams to be equal (which gives the largest Raman Rabi rate at a fixed total power), so there is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning.
+The transfer Raman Rabi Rate is $ \Omega_a\Omega_m / 2\Delta$~\cite{Wineland2003}. %, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}. 
+Unlike for Raman transitions in atoms, the two matrix elements here, $ \Omega_m$ and $ \Omega_a$, are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $ 
+due to the small wavefunction overlap between the atomic state and the excited molecular state.
+The scattering rate therefore predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth.
+Because the energy difference of the atomic and the weakly bound states are small ($<$1~GHz) comparing to $\Delta$, the power of the Raman beams are chosen to be equal to gives the largest Raman Rabi rate at a fixed total power.) There is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning.
 Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
@@
 However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
-With the multiple excited vibrational states present in a molecular potential, the total scattering rates and Rabi rates becomes a sum of the scattering rates and Rabi rates over all the states, and there are many possible intermediate states to choose from.
+With the multiple excited vibrational states present in a molecular potential, the total scattering rates and Rabi rates become a sum of the scattering rates and Rabi rates over all the states.
+There are also many possible intermediate states to choose from.
 
@@
 For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
-Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state has strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
-The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold.
-(Should we also mention scattering of the atomic initial state too?
-This should affect the Raman process as well)
+Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
+The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can also be made smaller by detuning away from the dissociation threshold.
+%(Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
 
@@
 %Since for a typical molecular potential the spacing between states
-%decreases with increasing vibrational levels,
-%a weakly bound excited molecular state
+% decreases with increasing vibrational levels,
+% a weakly bound excited molecular state
 % This further increases the scattering rate for a weakly bond excited state.
-%Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
+% Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
 % we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in Fig.~\ref{f-theory}B,
-%we found a distinct optimal regime from what has been explored experimentally previously.
+% we found a distinct optimal regime from what has been explored experimentally previously.
 Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state.
@@
 
-%higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states.
+% higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states.
 As a result, we use a deeply bound molecular excited state to drive the Raman transition.
 
-%(goes to SM?)
+% (goes to SM?)
 
-(mention scattering/lightshift depends on up/down matrix element ratio?)
+%(mention scattering/lightshift depends on up/down matrix element ratio?)
 
-%In addition to the intermediate state, the choice of the initial and final states are critical for both fundamental and technical reasons.
+% In addition to the intermediate state, the choice of the initial and final states are critical for both fundamental and technical reasons.
 Thus, a small $ \Omega_m/\Omega_a $ ratio is desired to be able to drive this transition coherently at smaller detunings where the Raman Rabi frequency will be larger.
@@
 This becomes technically easier when $ \Omega_m/\Omega_a $ is smaller.
-%(for our choice of states, this mean intensity fluctuation of less than 1\% or 0.1\%. KW: I mentioned this in next paragraph, does it still need to be mentioned here?)
+% (for our choice of states, this mean intensity fluctuation of less than 1\% or 0.1\%. KW: I mentioned this in next paragraph, does it still need to be mentioned here?)
 
@@
 As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio.
-The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the overall Raman Rabi Rate.
+The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate.
 This ratio can be made larger by increasing the coupling of the atomic state with the excited molecular state.
@@
 The increase in the coupling is proportional to (quote/cite Olive's equation?).
-For our system, among the stable spin combinations, 4422 and 3311 both have small scattering lengths of $\abs{a_{4422}}= 30.4a_0, \abs{a_{3311}} = 13.7a_0 $ respectively and 3322 has a large and negative scattering length of $ \abs{a_{3322}} = 693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
-In addition to the increased atomic coupling, $ \Omega_a $, with the 3322 hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly this spin combination also has reduced coupling, $ \Omega_m $, with the excited state when compared with the 4422 and 3311 bound states.
+For our system, among the stable spin combinations, 4422 and 3311 both have small scattering lengths of $ a_{4422}= 30.4a_0, a_{3311} = 13.7a_0 $ respectively, but the 3332 combination has a large and negative scattering length of $ a_{3322} = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
+In addition to the increased atomic coupling, $ \Omega_a $, with the 3322 hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly in the 3322 spin combinationn also has reduced coupling, $ \Omega_m $, with the excited state when compared with the 4422 and 3311 bound states.
 Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the 4422 or 3311 combinations.
@@
 The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $.
-The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth.
-Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
+The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth.
+Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
 Thus, we choose the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination.
@@
 To perform the Raman transfer, we use our apparatus described in our previous work~\cite{Liu2019}.
-Our experiment begins by loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into an optical tweezer from a dual-species MOT\todo{cite na loading paper} into separate optical tweezers.
-The atoms are imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom during post selection.
+Our experiment begins by stochastically loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into an optical tweezer from a dual-species MOT\todo{cite na loading paper} into separate optical tweezers.
+The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom in order to perform post selection.
 We then perform simultaneous Raman sideband cooling (RSC) to cool both atoms into the 3-dimensional motional ground state of their optical tweezers.
-After RSC, the Na tweezer is moved by sweeping the frequency on an acoustical optical beam deflector (AOBD) to overlap with the Cs tweezer before smoothly ramping off rso that the Na and Cs atoms are merged into the same tweezer \todo{cite}.
-The spin states for the Na and Cs atoms after RSC and during the merge process are $|F=2,m_F=2\rangle$ and $|F=4,m_F=4\rangle$ respectively.
-This states combination has a low scattering length of $...
-a_0$ which allows the two atoms to be merged into the same tweezer with minimum pertubation on each other and thus they remain in the motional ground state after the merge.
+After RSC, the Na tweezer is moved by sweeping the frequency on an acoustical optical beam deflector (AOBD) to overlap with the Cs tweezer before smoothly ramping off, so that the Na and Cs atoms are merged into the same tweezer~\cite{Liu2019}.
+The spin states for the Na and Cs atoms after RSC and during the merge process are $|F=2,m_F=2\rangle_{Na}$ and $|F=4,m_F=4\rangle_{Cs}$ respectively.
+This states combination has a low scattering length, which allows the two atoms to be merged into the same tweezer with minimum pertubation on each other and thus they remain in the motional ground state after the merge.
 
 After preparing the Na and Cs atoms in the same tweezer in a single quantum state, we need to drive the atoms into the large scattering length 3322 hyperfine combination.
-To do this, we perform a spin flip taking into account the interaction shift~\cite{Hood2019} using a Cs Raman transition to drive the Cs atom into the $|F=3,m_F=3\rangle$ state.
+To do this, we perform a spin flip taking into account the interaction shift~\cite{Hood2019} using a Cs Raman transition to drive the Cs atom into the $|F=3,m_F=3\rangle_{Cs}$ state.
 The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
-This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of relative motional ground state.
+This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.
 
@@
 Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal.
+In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse.
 The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time (also minimize source of scattering).
@@
 Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.
-\todo{clarify coprop of Raman beam?}
+%\todo{clarify coprop of Raman beam?}
 
@@
 \todo{more, mention/cite Jeremy}
-The background level of $...\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state using interaction shift spectroscopy (can this be considered "interaction shift spectroscopy"?).
+The background level of $...\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
 When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imaging step.
@@
 This is consistent with the expected value of $...$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent.
-In order to verify the coherence of the transfer directly, we fixed the Raman frequency on the resonance and scanned the pulse time.
+In order to verify the coherence of the transfer directly, we fix the Raman frequency on resonance and scan the pulse time.
 Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states.
-Fitting the data with a decaying Rabi oscillation suggests that $..\%$ of initial ground state atoms are transfered into the molecular state.
+Fitting the data with a decaying Rabi oscillation suggests that $..\%$ of initial ground state atoms are transferred into the molecular state.
 
 In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state (Fig.~\ref{f-lifetime}A).
-The effect due to atomic state loss was taken into account by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B).
+We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B).
 The fit shows that we have a Raman Rabi frequency of $...$.
@@
 The molecule lifetime can be verified directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C).
-The result shows a molecular lifetime consistent with our fitting of the Raman transition data.
+The result shows a molecular lifetime consistent with our fitting of the decaying Rabi oscillation.
 
-The ratio of molecule scattering rate and the Rabi frequency is larger than the theory prediction.
-In order to understand the origin of this discrepancy, we measured the dependency of the Raman resonance as a function of the tweezer power and frequency.
-The important results from the fits are resonance frequency (light shift), Raman Rabi frequency, atomic lifetime and molecular lifetime, each provide us information about a different combination of physical processes.
+The ratio of molecule scattering rate to the Rabi frequency is larger than the theory prediction.
+In order to understand the origin of this discrepancy, we measured the dependency of the Raman resonance (what does dependence of the Raman resonance mean?
+Do you just mean we measured molecule formation as a function of all these parameters?) as a function of the tweezer power and single photon frequency.
+The important results from the fits are the 2 photon resonance frequency (light shift), Raman Rabi frequency, atomic lifetime and molecular lifetime.
+Each of these quantities provide us with information about a different combination of physical processes.
 
 First we look at the change in resonance frequency.
-As a function of the tweezer power, we observed a linear dependency on the resonance frequency caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
-When we vary the tweezer frequency around the $v=0$ excited state, we can further observe a $1/\delta$ component and a background component that is constant for different detunings.
-The background is caused by coupling to all the other excited states that are further away which is not very important in this case.
-The $1/\delta$ component, however, is due to the coupling to the $v=0$ excited state and from equation (?) we know that this is mainly due to the coupling between the excited and ground molecular states.
-From this, we can calculate a down leg matrix element of $....$ which is similar to what we calculated from theory (ref/sm theory).
+As a function of the tweezer power, we observe a linear dependency on the resonance frequency caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
+When we vary the tweezer frequency around the $v=0$ excited state, we can further observe a $1/\delta$ component and a background component that is constant for different detunings in the experimentally explored region.
+The background is caused by coupling to other excited states that are further away in energy.
+%which is not very important in this case.
+% The $1/\delta$ component, however, is due to the coupling to the $v=0$ excited state and from equation (?) we know that the light shift is mainly due to the coupling between the excited and ground molecular states.
+The $1/\delta$ component, however, is predominantly due to the coupling between the molecular state and the $ v =0 $ excited state.
+From this measurement, we can calculate a matrix element between the molecular state and the excited state, $ \Omega_m$, of $....$ which is similar to what we calculated from theory (ref/sm theory).
 (make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$, also $\Omega$ vs $\Omega'$ for the single leg vs cross coupling number).
+% what's the take away of this paragraph with respect to the mystery that is setup in the previous paragraph of having a larger scattering rate to rabi frequency ratio than expected?
 
@@
 
+Next, we discuss the dependencies of the Raman Rabi frequency.
 The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change in the atomic wavefunction caused by the change in confinement (Fig.~\ref{f-det}?).
-The up leg matrix element scales with the short length atomic wavefunction amplitude which is 0.375 for weakly interaction particles.
+The atomic matrix element, $\Omega_a$, is proportional to the the short range atomic wavefunction amplitude, which scales as $ P^{0.375} $ for weakly interacting particles.
 However, due to the strong interaction between the two atoms, this approximation breaks down.
-Instead, theory calculation shows that the scaling is very well approximated by a power of 0.29 within the range of confinement in our experiment.
-Combined with the intensity factor of the Raman beams, the Raman Rabi frequency should scale with 1.29 power of the tweezer intensity, which agrees with our experimental result.
+Instead, theory calculation shows that the scaling is very well approximated by $ P^{0.29} $ within the range of confinement in our experiment.
+Combined with the intensity factor, the Raman Rabi frequency should scale with $P^{1.29}$, which agrees with our experimental result.
 Similar to the light shift, there is also a background component and a $v=0$ component in the Raman Rabi frequency.
@@
 (need blue side?)
+% I think we should include some takeaway from this paragraph as well, otherwise it may not be clear what the point is.
+Maybe something like, "Based on these analyses, the Rabi frequencies agree with theory.
+Thus, the high scattering rate to raman rabi frequency ratio is caused by larger than expected scattering, which we discuss next"
 
 Next, we look at the atomic loss rate during the transfer process. (Fig.~\ref{f-det}?)
-The atomic loss rate scales as the tweezer intensity to the 2.58th power but shows little to no dependency on the tweezer frequency.
-The lack of frequency dependency suggests that most of the atomic loss are due to the coupling to states other than the $v=0$ one.
-After substracing 0.58 from the power scaling due to the change in the up leg matrix element, the loss rate is proportional to the tweezer power squared.
-This is an evidence that the loss is likely caused by a two photon scattering process rather than one photon scattering.
+The atomic loss rate scales as $P^{2.58}$ but shows little to no dependency on the tweezer frequency.
+The lack of frequency dependency suggests that most of the atomic loss are due to the coupling to states other than $v=0$.
+After subtracting 0.58 from the power scaling due to the effect of confinement on the square of the atomic matrix element, the loss rate is proportional to $P^2$.
+This is evidence that the loss is likely caused by a two photon scattering process rather than one photon scattering.
 The strong power scaling causes a faster than expected loss rate for the atom.
-However, the atomic scattering is contribution only a small fraction of the total scattering rate so this is not the limiting factor for the transfer.
+However, the atomic scattering rate contributes only a small fraction of the total scattering rate so this is not the limiting factor for the transfer.
 
 Finally, we fit the scaling for the molecular loss rate. (Fig.~\ref{f-det}?)
-We observed a dependency on the detuning that is consistent with $1/\delta^2$ suggesting that the loss is indeed mostly coming from the $v=0$ excited state.
+We observed a dependency on the detuning that is consistent with $1/\delta^2$ suggesting that the loss is indeed mostly coming from the $v=0$ excited state (but this is only true at certain single photon detunings?).
 (preliminary) We observed a power scaling power of $\approx1.2$ which is closed to the prediction for a single photon scattering process.
@@
 
-%\bibliography{paper}
 \bibliography{master_ref}

### 2020-09-30 paper.tex
Clean up, regenerate PDF, update some numbers

@@
     Molecule survival is detected by dissociating back to atoms using a second Raman transition.
-    The lifetime of $...$ is consistent with that measured from the Raman transition data.
+    The lifetime is consistent with the $84.9(49) \mathrm{\mu s}$
+    measured from the Raman transition data.
     \label{f-lifetime}}
@@
 
-Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770...
-MHz$ (Fig.~\ref{f-raman}C) with a $15 mW$ tweezer at $288...
-GHz$ which corresponds to a $...
-GHz$ single photon detuning.
+Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) \mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 mW$ tweezer at $288560 GHz$ which corresponds to a $145 GHz$ single photon detuning.
 (We can maybe add information about the prediction here?)
 %% Prediction
-% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288...
-GHz$ from our atomic state.
+% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state.
 The ground molecular state has not been observed previously in experimentally.
 Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state.
-Theory prediction was at $770...
-MHz$.
+Theory prediction was at $770.1 MHz$.
 \todo{more, mention/cite Jeremy}
-The background level of $...\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
+The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
 When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imaging step.
-We observed the narrowest linewidth of $....
-kHz$ for the Raman resonance at a pulse time of $...
-ms$, which corresponds to a linewidth-pulsetime product of $...$.
-This is consistent with the expected value of $...$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent.
+We observed the narrowest linewidth of $8.43(81) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.1 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.843(81)$.
+This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent.
 In order to verify the coherence of the transfer directly, we fix the Raman frequency on resonance and scan the pulse time.
 Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states.
-Fitting the data with a decaying Rabi oscillation suggests that $..\%$ of initial ground state atoms are transferred into the molecular state.
+Fitting the data with a decaying Rabi oscillation suggests that $63\%$ of initial ground state atoms are transferred into the molecular state.
 
@@
 The fit shows that we have a Raman Rabi frequency of $...$.
-The molecule we form has a lifetime of $...$ which is the main limitation on the fidelity of the transfer.
+The molecule we form has a lifetime of $84.9(49) \mathrm{\mu s}$ which is the main limitation on the fidelity of the transfer.
 The molecule lifetime can be verified directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C).

### 2020-10-02 paper.tex
Update on Overleaf.

@@
   This technique is general without relying on narrow excited state lines or Feshbach resonances and could allow a wider range of molecular species to be assembled atom-by-atom.
+\textcolor{blue}{Yichao, can you update numbers in the abstract?
+also, can you update affiliations in the author list, Jeremy is Durham and Jon is Purdue}
 \end{abstract}
@@
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
-The transfer Raman Rabi Rate is $ \Omega_a\Omega_m / 2\Delta$~\cite{Wineland2003}. %, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}.
+The transfer Raman Rabi Rate is $ \Omega_a\Omega_m / 2\Delta$ accompanied by a photon scattering rate of $\Gamma_e \Omega / 4\Delta^2$...(sum of i terms\textcolor{red}{KW: I was intending to only mention the sum over terms at the end when we exit the 3 level system.})\textcolor{blue}{check factor of 2.
+KW: The 2 in the denominator is including cross coupling.
+4 without cross coupling.
+Since cross coupling is mentioned later, maybe leave this with 4?}, where $ \Gamma_e $ is the excited state linewidth~\cite{Wineland2003}.
+%, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}.
 Unlike for Raman transitions in atoms, the two matrix elements here, $ \Omega_m$ and $ \Omega_a$, are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
@@
 The scattering rate therefore predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth.
-Because the energy difference of the atomic and the weakly bound states are small ($<$1~GHz) comparing to $\Delta$, the power of the Raman beams are chosen to be equal to gives the largest Raman Rabi rate at a fixed total power.) There is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning.
-Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
-To ensure a coherent process, larger detuning is preferred.
-However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
+\textcolor{blue}{(blue text can potentially be moved to footnote) Furthermore, because the energy difference of the atomic and the weakly bound states are small ($<$1~GHz) comparing to $\Delta$, the power of the Raman beams are chosen to be equal to gives the largest Raman Rabi rate at a fixed total power.
+%There is
+An additional factor of 2 is included in the scattering rate because the molecular state scatters off of both Raman beams at roughly the same single photon detuning.
+} Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
+To ensure a coherent process, larger detuning is preferred while achieving a realistic Raman Rabi frequency.
+%However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
 With the multiple excited vibrational states present in a molecular potential, the total scattering rates and Rabi rates become a sum of the scattering rates and Rabi rates over all the states.
-There are also many possible intermediate states to choose from.
+%There are also many possible intermediate states to choose from.
 
-Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency.
-However, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
-For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
-Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
+Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
+However, such choice of state suffers from strong scattering of the nearby atomic excited state to render it incoherent, resulting in molecule loss.
+The scattering  is  proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can  be made smaller by detuning away from the dissociation threshold.
+
+ %For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
+%Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
 The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can also be made smaller by detuning away from the dissociation threshold.
@@
 
-To obtain a complete picture, we perform a full calculation of the Raman Rabi frequency and scattering rate at different detunings (full result in SM).
-As shown in Fig.~\ref{f-theory}B, the ratio of the Raman Rabi rate to scattering rate can be made better for more deeply bound states compared to weakly bound states.
+To find the optimal excited intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma$ excited molecular state potential (full result in SM)~\cite{Liu2017} \textcolor{red}{KW: I have only done the calculations with c3Sigma only, cause the b3Pi is highly spin orbit coupled, and not necessarily trustworthy where we are.
+I can also include a citation to the paper with that potential?}.
+As shown in Fig.~\ref{f-theory}B, the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency.
 %Since for a typical molecular potential the spacing between states
@@
 % we found a distinct optimal regime from what has been explored experimentally previously.
-Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state.
-As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) to drive the Raman transition.
-(mention the trend, also v=12 will work as similarly as v=0)
+%Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state. 
+As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) as an intermediate state to drive the Raman transition.
+%(mention the trend, also v=12 will work as similarly as v=0)
 
@@
 The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser needs to be stabilized to better than the inverse of this ratio, $ \Omega_a/\Omega_m $, to fluctuate by less than a linewidth.
-This becomes technically easier when $ \Omega_m/\Omega_a $ is smaller.
+This becomes technically easier wh So en $ \Omega_m/\Omega_a $ is smaller.
 % (for our choice of states, this mean intensity fluctuation of less than 1\% or 0.1\%. KW: I mentioned this in next paragraph, does it still need to be mentioned here?)
 
-In addition to the intermediate state, the choice of the initial and final states is critical.
+\textcolor{blue}{Main point here.
+Small $\Omega_a/\Omega_m$ ratio can be compensated by larger detuning, but Stark shift is problematic.} \textcolor{red}{KW: I agree Stark shift limitation is definitely pretty problematic, but I would also argue that larger detuning may not be able to save the day, because of the many vibrational states in a molecular potential, the lower Raman rabi frequency which results from detuning farther and possibly running into other limitations if you have to do that, such as the background off resonant scattering rate from near threshold states or technical background scattering.} \textcolor{blue}{yes, I agree.
+I want to layout the structure ....
+motivate for the better ratio first, than talk about choosing the state.} \textcolor{red}{KW: Okay, got it.
+Makes sense.
+}
+In addition to the intermediate state, the choice of the initial and final states is also critical.
 As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio.
@@
 For our system, among the stable spin combinations, 4422 and 3311 both have small scattering lengths of $ a_{4422}= 30.4a_0, a_{3311} = 13.7a_0 $ respectively, but the 3332 combination has a large and negative scattering length of $ a_{3322} = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
-In addition to the increased atomic coupling, $ \Omega_a $, with the 3322 hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly in the 3322 spin combinationn also has reduced coupling, $ \Omega_m $, with the excited state when compared with the 4422 and 3311 bound states.
+In addition to the increased atomic coupling, $ \Omega_a $, with the 3322 hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly in the 3322 spin combination also has reduced coupling, $ \Omega_m $, with the excited state when compared with the 4422 and 3311 bound states.
 Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the 4422 or 3311 combinations.
@@
 The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $.
-The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth.
+\textcolor{red}{KW: Can also include similar footnote here about cross coupling?
+The 2 in the denominator is assuming cross coupling and equal powers.} The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process.
 Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
@@
 % In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
-\begin{figure*}
+\begin{figure*}[ht!]
   \includegraphics[height=4.5cm]{fig2.pdf}
@@
     \label{f-raman}}
-\end{figure*}
-
-\begin{figure*}
-  \includegraphics[height=4.5cm]{fig3.pdf}
-  \caption{
-    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
-    with loss on the atom and molecule state. The combined fit is used to determine
-    both the Raman Rabi frequency and the loss rates.
-    (B) \todo{inset?} Two-body atom lifetime in $15 \mathrm{mW}$ of trap depth caused by
-    off-resonance photoassociation.
-    This is used to improve the fitting of the Raman transfer data.
-    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
-    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
-    The lifetime is consistent with the $84.9(49) \mathrm{\mu s}$
-    measured from the Raman transition data.
-    \label{f-lifetime}}
-\end{figure*}
-
-\begin{figure*}
-  \includegraphics[height=4.5cm]{fig4.pdf}
-  \caption{Raman transition parameters as a function of tweezer/Raman power and detuning.
-    (A) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\delta$ with an offset.
-    (B) Atom loss rate scales as $P_{tweezer}^{2.58}$ suggesting a two-photon scattering loss.
-    (C) Molecular loss rate scales closed to $P_{tweezer}$ and follows $1/\delta^2$
-    with additional detuning independent background loss rate.
-    This result controdicts the our previous measurement of excited state lifetime
-    suggesting that there are additional loss mechanism that is not taken into account.
-    \label{f-det}}
 \end{figure*}
@@
 Fitting the data with a decaying Rabi oscillation suggests that $63\%$ of initial ground state atoms are transferred into the molecular state.
+
+\begin{figure*}
+  \includegraphics[height=4.5cm]{fig3.pdf}
+  \caption{
+    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
+    with loss on the atom and molecule state. The combined fit is used to determine
+    both the Raman Rabi frequency and the loss rates.
+    (B) \todo{inset?} Two-body atom lifetime in $15 \mathrm{mW}$ of trap depth caused by
+    off-resonance photoassociation.
+    This is used to improve the fitting of the Raman transfer data.
+    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
+    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
+    The lifetime is consistent with the $84.9(49) \mathrm{\mu s}$
+    measured from the Raman transition data.
+    \label{f-lifetime}}
+\end{figure*}
 
@@
 
+\begin{figure*}
+  \includegraphics[height=4.5cm]{fig4.pdf}
+  \caption{Raman transition parameters as a function of tweezer/Raman power and detuning.
+    (A) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\delta$ with an offset.
+    (B) Atom loss rate scales as $P_{tweezer}^{2.58}$ suggesting a two-photon scattering loss.
+    (C) Molecular loss rate scales closed to $P_{tweezer}$ and follows $1/\delta^2$
+    with additional detuning independent background loss rate.
+    This result controdicts the our previous measurement of excited state lifetime
+    suggesting that there are additional loss mechanism that is not taken into account.
+    \label{f-det}}
+\end{figure*}
+
 Finally, we fit the scaling for the molecular loss rate. (Fig.~\ref{f-det}?)

### 2020-10-02 plot_raman.jl
v prime

@@ -47,7 +47,7 @@ plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ 2π / 1000), "C0",
      label="\$\\Omega_{Raman}\$")
 plot(data[:, 1] .- 288625.081, abs.(data[:, 4] ./ 2π / 1000), "C1",
      label="\$\\Gamma_{scatter}\$")
-text(-32, 2.5, "v=0", fontsize="small")
+text(-32, 2.5, "v'=0", fontsize="small")
 ylim([0, 30])
 grid()
 tax1 = ax1.twinx()
@@ -66,7 +66,7 @@ l1 = plot(data[:, 1] .- 351271.53, abs.(data[:, 2] ./ 2π / 1000), "C0",
           label="\$\\Omega_{Raman}\$")
 l2 = plot(data[:, 1] .- 351271.53, abs.(data[:, 4] ./ 2π / 1000), "C1",
           label="\$\\Gamma_{scatter}\$")
-text(-32, 130, "v=63", fontsize="small")
+text(-32, 130, "v'=63", fontsize="small")
 xlabel("One-Photon Detuning (GHz)")
 ylim([0, 596])
 grid()

### 2020-10-03 paper.tex
White space, regenerate PDF
Update on Overleaf.
Remove done todo
Mention ASE filter

@@
   \caption{Optical creation of single molecule from single atoms in tweezer.
-    (A) (should label $v'=0$ and $v'=63$) Schematics of the optical transition from an atom pair to a weakly bound molecule.
+    (A) Schematics of the optical transition from an atom pair to a weakly bound molecule.
     The initial state is the relative motional ground state between the two atoms
@@
 
- %For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
+% For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
 %Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
 The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can also be made smaller by detuning away from the dissociation threshold.
-%(Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
+% (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
 
@@
 % we found a distinct optimal regime from what has been explored experimentally previously.
-%Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state. 
+% Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state.
 As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) as an intermediate state to drive the Raman transition.
@@
 
-%(mention scattering/lightshift depends on up/down matrix element ratio?)
+% (mention scattering/lightshift depends on up/down matrix element ratio?)
 
@@
 In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse.
-The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time (also minimize source of scattering).
+The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time.
 After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged.
 Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.
-%\todo{clarify coprop of Raman beam?}
+In additional to reducing the number of laser beams during the Raman transition,
+we also found the spectral purity of the laser to be critical for achieving a higher
+transfer efficiency. The tweezer and Raman beams are generated by amplifying a $1037 \mathrm{nm}$
+external cavity diode laser (ECDL) with a Raman fiber amplifier,
+which produces a broad band amplified spontaneous emission (ASE),
+in addtional to the desired frequency, and increases the scattering rate due to coupline to
+other excited states.
+We use a bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the
+laser spectrum and found it reduces the scattering rate by at least a factor of $2$
+for certain tweezer detuning.
 
@@
 \end{document}
+
+% ASE in caption for figure 4 and when mentioning the setup ahead of time
+% figure 4
+
+% ? SM?

### 2020-10-05 plot_exp_data.jl
Update figure 2 and 3

@@ -14,51 +14,31 @@ using PyPlot
 using DataStructures
 using LsqFit
 
-const inames = ["nacs_202003/data/data_20200326_101325.mat",
-                "nacs_202003/data/data_20200326_223438.mat",
-                "nacs_202003/data/data_20200327_004910.mat",
-                "nacs_202003/data/data_20200330_033004.mat",
-                "nacs_202003/data/data_20200327_133537.mat",
-                "nacs_202003/data/data_20200330_201614.mat",
-                "nacs_202003/data/data_20200331_020659.mat",
-                "nacs_202004/data/data_20200401_060025.mat"]
+const inames = ["nacs_202010/data/data_20201001_203322.mat",
+                "nacs_202010/data/data_20201002_203848.mat",
+                "nacs_202010/data/data_20201002_085901.mat",
+                "nacs_202010/data/data_20201003_102015.mat"]
 const datas = [NaCsData.load_striped_mat(joinpath(@__DIR__, "../../experiments/", iname)) for iname in inames]
 const maxcnts = [typemax(Int),
                  typemax(Int),
                  typemax(Int),
-                 typemax(Int),
-                 typemax(Int),
-                 typemax(Int),
-                 typemax(Int),
                  typemax(Int)]
-const specs = [(593.0 .+ [-20; -6:2:6; 20], # 15 mW, 0.09 ms
-                522.7 .+ [-15; -4.5:1.5:4.5; 15], # 12 mW, 0.12 ms
-                447.5 .+ [-10; -3:0.6:3; 5], # 9 mW, 0.16 ms
-                369.5 .+ [-5; -2:0.5:2; 5], # 6 mW, 0.27 ms
-                287.5 .+ [-5; -0.6:0.15:0.6; 5], # 3 mW, 0.9 ms
+const specs = [[0; [0.02, 0.04, 0.07, 0.085, 0.10, 0.13, 0.145, 0.16,
+                    0.175, 0.19, 0.22, 0.25, 0.28, 0.31, 0.34, 0.37,
+                    0.40, 0.43, 0.46, 0.49] .* 1.6 .- 0.01], # 15 mW, 770.5704 MHz
[…]

### 2020-10-05 plot_exp_data.jl
2d plot for reference

@@ -342,93 +342,21 @@ xlabel("Molecule Hold Time (ms)")
 ylabel("Two-body survival")
 NaCsPlot.maybe_save("$(prefix)_norm_m_t")
 
-NaCsPlot.maybe_show()
+const img_freq = param_1[3] .+ linspace(-20, 20, 201)
+const img_time = linspace(0, 0.5, 201)
+const mol_2d = [model_2d(t, f, param_1, molecule=true) .* scale_1
+                for f in img_freq, t in img_time]
 
-
-
-exit()
-#!/usr/bin/julia
-
-
-
-
-
-figure(figsize=[12.6, 11.2])
-
-subplot(2, 2, 1)
-ratio_00, uncs_00 = get_ratio_val(data_nacs_00)
-v00 = model_2d(0, 0, param_2)
-errorbar([param_2[3]], [ratio_00], [uncs_00], fmt="C0.", label="0.00 ms")
-plot([plot_freq_lo, plot_freq_hi], [v00, v00], "C0-")
-NaCsPlot.plot_survival_data(data_nacs_25, fmt="C1.", label="0.25 ms")
-plot(plot_freq, model_2d.(0.25, plot_freq, (param_2,)), "C1")
-NaCsPlot.plot_survival_data(data_nacs_12, fmt="C2.", label="0.12 ms")
-plot(plot_freq, model_2d.(0.12, plot_freq, (param_2,)), "C2")
-legend(fontsize="x-small", loc="lower right")
-ylim([0, ylim()[2]])
+figure()
+imshow(mol_2d, aspect="auto", interpolation="none", origin="lower",
+       extent=[img_time[1] - step(img_time) / 2, img_time[end] + step(img_time) / 2,
+               img_freq[1] - step(img_freq) / 2 - param_1[3],
+               img_freq[end] + step(img_freq) / 2 - param_1[3]])
+xlabel("Raman time (ms)")
+ylabel("Detuning from resonance (kHz)")
+title("Molecule Population")
 grid()
-xlabel("2-Photon Detuning (770XXX kHz)")
-ylabel("Two-body survival")
-title("288895 GHz, 15 mW")
-
-subplot(2, 2, 2)
-NaCsPlot.plot_survival_data(data_nacs_t, fmt="C0.", label="770.5704 MHz")
-plot(plot_time, model_2d.(plot_time, 570.4, (param_1,)), "C0")
[…]

### 2020-10-05 paper.tex
... remove notes
Update Fig 2 and 3 descriptions

@@
     (C) Raman resonance from atomic state $Na(2,2)\ Cs(3,3)$ to the first molecular bound state
-    using a $0.1\mathrm{ms}$ pulse.
-    The full width half maximum (FWHM) of $8.43(81) \mathrm{kHz}$ of the resonance
-    is consistent with the FWHM for a coherent $0.1\mathrm{ms}$ $8.0 \mathrm{kHz}$ $\pi$ pulse.
+    using a $0.12\mathrm{ms}$ pulse.
+    The full width half maximum (FWHM) of $7.56(82) \mathrm{kHz}$ of the resonance
+    is consistent with the FWHM for a coherent $0.12\mathrm{ms}$ $\pi$ pulse $6.7 \mathrm{kHz}$.
     (D) Raman pulse time scan on resonance. A decaying Rabi oscillation can be observed
@@
 When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imaging step.
-We observed the narrowest linewidth of $8.43(81) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.1 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.843(81)$.
+We observed the narrowest linewidth of $7.56(82) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.12 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.907(98)$.
 This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent.
@@
 Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states.
-Fitting the data with a decaying Rabi oscillation suggests that $63\%$ of initial ground state atoms are transferred into the molecular state.
+Fitting the data with a decaying Rabi oscillation suggests that $69\%$ of initial ground state atoms are transferred into the molecular state.
 
@@
     Molecule survival is detected by dissociating back to atoms using a second Raman transition.
-    The lifetime is consistent with the $84.9(49) \mathrm{\mu s}$
+    The lifetime is consistent with the $0.204(13) \mathrm{ms}$
     measured from the Raman transition data.
+    The oscillation in the survival is the result of the interference
+    between the two Raman pulses with incomplete transfer.
     \label{f-lifetime}}
@@
 We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B).
-The fit shows that we have a Raman Rabi frequency of $...$.
-The molecule we form has a lifetime of $84.9(49) \mathrm{\mu s}$ which is the main limitation on the fidelity of the transfer.
+The fit shows that we have a Raman Rabi frequency of $2\pi\times3.282(42) \mathrm{kHz}$.
+The molecule we form has a lifetime of $0.204(13) \mathrm{ms}$ which is the main limitation on the fidelity of the transfer.
 The molecule lifetime can be verified directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C).
@@
 
-(ASE filter)
-
 %%%% Maybe this following section about the B field can be relegated to a figure caption?
@@
 \end{document}
-
-% ASE in caption for figure 4 and when mentioning the setup ahead of time
-% figure 4
-
-% ? SM?

### 2020-10-05 plot_exp_data.jl

@@ -339,7 +339,7 @@ text(0.218, 0.07 * scale_ramsey,
 xlim([0, 0.9])
 grid()
 xlabel("Molecule Hold Time (ms)")
-ylabel("Two-body survival")
+ylabel("Molecule survival")
 NaCsPlot.maybe_save("$(prefix)_norm_m_t")
 
 const img_freq = param_1[3] .+ linspace(-20, 20, 201)

### 2020-10-08 paper.tex
Update text for figure 4

@@
     as intermediate state for the Raman transition.
-    The deeply bound excited state (upper half $v=0$) has a smaller Raman Rabi frequency ($\Omega_{Raman}$)
-    compared to the weakly bound excited state (lower half $v=63$) at a given detuning.
+    The deeply bound excited state (upper half $v'=0$) has a smaller Raman Rabi frequency ($\Omega_{Raman}$)
+    compared to the weakly bound excited state (lower half $v'=63$) at a given detuning.
     However, the scattering rate ($\Gamma_{scatter}$) is also much lower,
@@
 For similar reason, the natural choice for the intermediate excited molecular state is one with highly excited motional level.However, from our calculation (and experiment?), the smaller level space for high vibrational state and the smaller detuning from the atomic threshold increases the scattering rate of the molecular state which causes a reduced Raman Rabi frequency to decoherence rate ratio and a lower transfer efficiency.
-Therefore, in our experiment, we selected the v=0 state as the intermediate state for our Raman transition.
+Therefore, in our experiment, we selected the v'=0 state as the intermediate state for our Raman transition.
 
@@
 As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) as an intermediate state to drive the Raman transition.
-%(mention the trend, also v=12 will work as similarly as v=0)
+%(mention the trend, also v'=12 will work as similarly as v'=0)
 
@@
 
-The ratio of molecule scattering rate to the Rabi frequency is larger than the theory prediction.
-In order to understand the origin of this discrepancy, we measured the dependency of the Raman resonance (what does dependence of the Raman resonance mean?
-Do you just mean we measured molecule formation as a function of all these parameters?) as a function of the tweezer power and single photon frequency.
-The important results from the fits are the 2 photon resonance frequency (light shift), Raman Rabi frequency, atomic lifetime and molecular lifetime.
-Each of these quantities provide us with information about a different combination of physical processes.
+The ratio of molecule scattering rate to the Rabi frequency is larger than the theory prediction
+by more than a factor of $10$.
+Based on the calculation above, if this comes from the coupling to the $v'=0$ excited state,
+it can be either due to a high ratio of $\Omega_m / \Omega_a$ or a large $\Gamma_e$.
+Additionally, coupling to other excited states can also adds an offset to both the Raman
+Rabi frequency and the scattering rate which can affect the scattering rate
+to Rabi frequency ratio.
+
+In order to verify whether any one of these known sources are the origin of the discrepancy,
+we measured the Raman resonance as a function of the tweezer power and single photon frequency.
+The important results from the fits are the 2 photon resonance frequency (light shift),
+Raman Rabi frequency, atomic lifetime and molecular lifetime.
+Each of these quantities provide us with information about a different combination
+of physical processes and the detuning dependency of them allows us
+to distinguish the contribution from the $v'=0$ excited states and other states.
 
 First we look at the change in resonance frequency.
-As a function of the tweezer power, we observe a linear dependency on the resonance frequency caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
-When we vary the tweezer frequency around the $v=0$ excited state, we can further observe a $1/\delta$ component and a background component that is constant for different detunings in the experimentally explored region.
+As a function of the tweezer power, we observe a linear dependency on the resonance frequency
+caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
+When we vary the tweezer frequency around the $v'=0$ excited state,
+we can further observe a $1/\delta$ component and a constant component
+in the experimentally explored region.
 The background is caused by coupling to other excited states that are further away in energy.
-%which is not very important in this case.
-% The $1/\delta$ component, however, is due to the coupling to the $v=0$ excited state and from equation (?) we know that the light shift is mainly due to the coupling between the excited and ground molecular states.
-The $1/\delta$ component, however, is predominantly due to the coupling between the molecular state and the $ v =0 $ excited state.
-From this measurement, we can calculate a matrix element between the molecular state and the excited state, $ \Omega_m$, of $....$ which is similar to what we calculated from theory (ref/sm theory).
-(make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$, also $\Omega$ vs $\Omega'$ for the single leg vs cross coupling number).
-% what's the take away of this paragraph with respect to the mystery that is setup in the previous paragraph of having a larger scattering rate to rabi frequency ratio than expected?
+The $1/\delta$ component, however, is predominantly due to the coupling between
+the molecular state and the $v'=0$ excited state.
+From this measurement, we can calculate a matrix element between the molecular state and
+the excited state, $\Omega_m$, of $2\pi\times89.40(17) \mathrm{MHz}/\sqrt{\mathrm{mW}}$
+or $2\pi\times346.24(65) \mathrm{MHz}$ for the $15 \mathrm{mW}$ tweezer power used above.
+This number is about $3$ times larger than the value of
+$2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ \todo{ref/sm theory}.
+\todo{make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$,
+  also $\Omega$ vs $\Omega'$ for the single leg vs cross coupling number.}
 
-(talk about blue side?)
+In order to calculate the matrix element ratio,
+next we discuss the dependencies of the Raman Rabi frequency.
+The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change
+in the atomic wavefunction caused by the change in confinement (Fig.~\ref{f-det}B).
+The atomic matrix element, $\Omega_a$,
+is proportional to the the short range atomic wavefunction amplitude,
+which scales as $P^{0.375}$ for weakly interacting particles.
+However, due to the strong interaction between the two atoms, this approximation breaks down.
+Instead, theory calculation shows that the scaling is very well approximated by $P^{0.29}$
+within the range of confinement in our experiment.
+Combined with the intensity factor, the Raman Rabi frequency should scale with $P^{1.29}$,
+which agrees with our experimental result.
+Similar to the light shift, there is also an offset and
+a $v'=0$ component in the Raman Rabi frequency.
+Based on the $v'=0$ component and the $\Omega_m$ measured above,
+we measured a up leg Rabi frequency of $...$, or $...$ at $15 \mathrm{mW}$ tweezer power.
+This gives a Rabi frequency, and therefore matrix element, ratio of $...$,
+which is in fact better than the theory prediction of $...$
+and should not cause the scattering from the $v'=0$ state to be higher than expected.
 
-Next, we discuss the dependencies of the Raman Rabi frequency.
-The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change in the atomic wavefunction caused by the change in confinement (Fig.~\ref{f-det}?).
-The atomic matrix element, $\Omega_a$, is proportional to the the short range atomic wavefunction amplitude, which scales as $ P^{0.375} $ for weakly interacting particles.
-However, due to the strong interaction between the two atoms, this approximation breaks down.
-Instead, theory calculation shows that the scaling is very well approximated by $ P^{0.29} $ within the range of confinement in our experiment.
-Combined with the intensity factor, the Raman Rabi frequency should scale with $P^{1.29}$, which agrees with our experimental result.
-Similar to the light shift, there is also a background component and a $v=0$ component in the Raman Rabi frequency.
-The $v=0$ component predicts a up leg Rabi frequency of $...$ which is consistent with theory.
-Unfortunately, the background Raman Rabi frequency cancels the Rabi frequency for red detuning Raman transition which is one of the factors that decreases our transfer efficiency.
-(need blue side?)
-% I think we should include some takeaway from this paragraph as well, otherwise it may not be clear what the point is.
-Maybe something like, "Based on these analyses, the Rabi frequencies agree with theory.
-Thus, the high scattering rate to raman rabi frequency ratio is caused by larger than expected scattering, which we discuss next"
-
-Next, we look at the atomic loss rate during the transfer process. (Fig.~\ref{f-det}?)
-The atomic loss rate scales as $P^{2.58}$ but shows little to no dependency on the tweezer frequency.
-The lack of frequency dependency suggests that most of the atomic loss are due to the coupling to states other than $v=0$.
-After subtracting 0.58 from the power scaling due to the effect of confinement on the square of the atomic matrix element, the loss rate is proportional to $P^2$.
-This is evidence that the loss is likely caused by a two photon scattering process rather than one photon scattering.
-The strong power scaling causes a faster than expected loss rate for the atom.
-However, the atomic scattering rate contributes only a small fraction of the total scattering rate so this is not the limiting factor for the transfer.
+Unfortunately, the offset in the Raman Rabi frequency fit cancels
+the Rabi frequency for red detuning Raman transition and reduces it by about $...\times$
+at the current detuning. However, this difference is not enough to explain
+the difference we observed in the experiment.
+The same offset will increase the Rabi frequency for blue detuning
+but we have observed additional excited states at slightly higher frequencies
+which prevent the blue side of the transition to be usuable for Raman transition.
 
@@
   \includegraphics[height=4.5cm]{fig4.pdf}
-  \caption{Raman transition parameters as a function of tweezer/Raman power and detuning.
-    (A) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\delta$ with an offset.
-    (B) Atom loss rate scales as $P_{tweezer}^{2.58}$ suggesting a two-photon scattering loss.
-    (C) Molecular loss rate scales closed to $P_{tweezer}$ and follows $1/\delta^2$
-    with additional detuning independent background loss rate.
-    This result controdicts the our previous measurement of excited state lifetime
-    suggesting that there are additional loss mechanism that is not taken into account.
+  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
+    (A) The light shift of the Raman resonance scales as $P_{tweezer}$
+    and follows $1/\delta$ with an offset.
+    (B) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\delta$ with an offset.
+    From these results we can confirm the theory prediction of
+    the atom-molecule matrix element ratio.
+    (C) Atomic scattering rate scales as $P_{tweezer}^{2.58}$,
+    this is consistent with a two photon scattering process.
+    We have not measured a clear dependency of the loss rate on the tweezer detuning.
     \label{f-det}}
@@
 
-Finally, we fit the scaling for the molecular loss rate. (Fig.~\ref{f-det}?)
-We observed a dependency on the detuning that is consistent with $1/\delta^2$ suggesting that the loss is indeed mostly coming from the $v=0$ excited state (but this is only true at certain single photon detunings?).
-(preliminary) We observed a power scaling power of $\approx1.2$ which is closed to the prediction for a single photon scattering process.
-The excited state line width calculated from the scattering rate is $...(1 GHz?)$ which is much larger than the theory prediction of $10 MHz$ as well as the $20 MHz$ upper bound from our previous PA measurements (cite).
+Based on our previous measurements of the excited state using photoassociation (PA) spectroscopy,
+the linewidth of the $v'=0$ excited state is no larger than $50 \mathrm{MHz}$.
+This suggests that the excited state linewidth should not cause a stronger than expected
+scattering from $v'=0$ state either.
+
+These results suggests that the decoherence or loss we observed during the the Raman transition
+comes from either a higher than expected background scattering rate
+or a different intrinsic or technical source that we have not accounted for.
+As mentioned above, we have observed significant improvment in the coherence time
+by filtering out most of the ASE from the laser suggesting the spectral purity of
+the laser is a significant source of scattering.
+Although we have good control on the total power of the tweezer and Raman beam to stabilize
+the light shift on the transition, the power ratio of the two frequencies within the beam
+is not yet controlled as tightly and may result in a residual resonance fluctuation.
+Finally, Fig.~\ref{f-det}C shows the two-body scattering rate for the atomic initial state.
+The scattering rate scales as $P_{tweezer}^{2.58}$ which is inconsistent with
+the prediction based on single photon scattering process.
+Although the absolute scattering rate is much lower than the total decoherence rate
+and we have not been able to observe a dependency on the detuning in order to
+verify if the scattering process is related to the $v'=0$ state, the power scaling
+strongly suggests the existence of a unknown two photon scattering process.
 
@@
 The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
-
 B field dependency $... kHz/G$ which agrees with theory prediction of $... kHz/G$.

### 2020-10-08 paper.tex
Update number

@@
 Based on our previous measurements of the excited state using photoassociation (PA) spectroscopy,
-the linewidth of the $v'=0$ excited state is no larger than $50 \mathrm{MHz}$.
+the linewidth of the $v'=0$ excited state is no larger than $20 \mathrm{MHz}$.
 This suggests that the excited state linewidth should not cause a stronger than expected

### 2020-10-08 paper.tex
Update on Overleaf.

@@
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
-The transfer Raman Rabi Rate is $ \Omega_a\Omega_m / 2\Delta$ accompanied by a photon scattering rate of $\Gamma_e \Omega / 4\Delta^2$...(sum of i terms\textcolor{red}{KW: I was intending to only mention the sum over terms at the end when we exit the 3 level system.})\textcolor{blue}{check factor of 2.
+The transfer Raman Rabi Rate is $ \Omega_a\Omega_m / 2\Delta$ accompanied by a photon scattering rate of $\Gamma_e \Omega^2 / 4\Delta^2$...(sum of i terms\textcolor{red}{KW: I was intending to only mention the sum over terms at the end when we exit the 3 level system.})\textcolor{blue}{check factor of 2.
 KW: The 2 in the denominator is including cross coupling.
@@
 
-\textcolor{blue}{Main point here.
+%\textcolor{blue}{Main point here.
 Small $\Omega_a/\Omega_m$ ratio can be compensated by larger detuning, but Stark shift is problematic.} \textcolor{red}{KW: I agree Stark shift limitation is definitely pretty problematic, but I would also argue that larger detuning may not be able to save the day, because of the many vibrational states in a molecular potential, the lower Raman rabi frequency which results from detuning farther and possibly running into other limitations if you have to do that, such as the background off resonant scattering rate from near threshold states or technical background scattering.} \textcolor{blue}{yes, I agree.
@@
 }
-In addition to the intermediate state, the choice of the initial and final states is also critical.
+%In addition to the intermediate state, the choice of the initial and final states is also critical. 
 As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio.
 The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate.
-This ratio can be made larger by increasing the coupling of the atomic state with the excited molecular state.
+In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation.
+The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $.
+\textcolor{red}{KW: Can also include similar footnote here about cross coupling?
+The 2 in the denominator is assuming cross coupling and equal powers.} The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process.
+The ratio, $ \Omega_a/\Omega_m $ can be changed through the choice of initial and final states.
+In particular, it can be made larger by increasing the coupling of the atomic state with the excited molecular state.
 Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential.
@@
 Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the 4422 or 3311 combinations.
-In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation.
-The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $.
-\textcolor{red}{KW: Can also include similar footnote here about cross coupling?
-The 2 in the denominator is assuming cross coupling and equal powers.} The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process.
-Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
+%Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.  
 Thus, we choose the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination.

### 2020-10-09 plot_raman.jl
Remove ghost text from the figure...

@@ -31,15 +31,20 @@ ax0.spines["top"].set_color("none")
 ax0.spines["bottom"].set_color("none")
 ax0.spines["left"].set_color("none")
 ax0.spines["right"].set_color("none")
+ax0.set_xticks([])
+ax0.set_yticks([])
 ax0.tick_params(labelcolor="w", top="off", bottom="off", left="off", right="off")
 ylabel("\$\\Omega_{Raman}\$ and \$\\Gamma_{scatter}\$ (\$2\\pi\\cdot \\mathrm{kHz})\$", fontsize="small")
 ax0.get_yaxis().set_label_coords(-0.13, 0.5)
 ax0.tick_params(axis="x", length=0)
 ax0.tick_params(axis="y", length=0)
 tax0 = ax0.twinx()
+tax0.set_xticks([])
+tax0.set_yticks([])
 tax0.tick_params(labelcolor="w", top="off", bottom="off", left="off", right="off")
 tax0.tick_params(axis="x", length=0)
 tax0.tick_params(axis="y", length=0)
+tax0.get_yaxis().set_label_coords(1.118, 0.5)
 ylabel("\$\\Omega_{Raman}/\\Gamma_{scatter}\$", fontsize="small", color="C2")
 
 ax1 = fig.add_subplot(211)

### 2020-10-11 plot_res_scaling.jl
resonance scaling

@@ -1,0 +1,187 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival, get_plot_range
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+
+const freqs = [668.35 21 772.1367 0.0082
+               668.35 21 772.1376 0.0049
+               668.35 21 772.1172 0.0048
+               668.35 18 771.924 0.033
+               668.35 12 771.323 0.050
+
+               560 15 770.59417 0.00013
+               560 6 770.369081 0.000037
+               560 3 770.287276 0.000015
+
+               565 15 770.61656 0.00021
+               565 6 770.378274 0.000080
+               565 3 770.291891 0.000038
+
+               555 15 770.57744 0.00013
+               555 6 770.362165 0.000043
+               555 3 770.283665 0.000017
+
+               503 15 770.483553 0.000049
+               503 12 770.43248 0.00011
+               503 9 770.379505 0.000028
+               503 6 770.324463 0.000019
+               503 3 770.2648307 0.0000084
+
+               492 15 770.47571 0.00010
+               492 12 770.42599 0.00032
+               492 9 770.375007 0.000069
+               492 6 770.321355 0.000037
+               492 3 770.263402 0.000028
+
+               510 15 770.50117 0.00083
+               510 12 770.44659 0.00021
+               510 9 770.390205 0.000079
+               510 6 770.331510 0.000057
+               510 3 770.258511 0.000023
+
+               605 15 770.76208 0.00027
+               605 12 770.65624 0.00046
+               605 9 770.54816 0.00058
+               605 6 770.437052 0.000072
+               605 3 770.321367 0.000038
+               ]
+
+function model_sqr(x, p)
+    return p[1] .+ (p[2] .+ p[3] .* x) .* x
+end
+
+broacast_array(f, x) = f(x)
+broacast_array(f, x::AbstractArray) = f.(x)
+
+# x: freq, power, idx
[…]

### 2020-10-11 plot_res_scaling.jl
update resonance scaling plot

@@ -53,6 +53,10 @@ const freqs = [668.35 21 772.1367 0.0082
                605 9 770.54816 0.00058
                605 6 770.437052 0.000072
                605 3 770.321367 0.000038
+
+               625 15 770.89410 0.00024
+               625 6 770.490130 0.000059
+               625 3 770.347812 0.000022
                ]
 
 function model_sqr(x, p)
@@ -166,11 +170,11 @@ for i in 1:length(powers_plot)
     power = powers_plot[i]
     plot1 = get_plot_data_power(data, fit1, model1, power)
     errorbar(plot1.x .+ 288000, (plot1.y .- fit1.param[1]) .* 1000,
-             plot1.unc .* 1000, fmt="C$(i - 1)s")
+             plot1.unc .* 1000, fmt="C$(i - 1).")
     plot(plot1.plotx .+ 288000, (plot1.ploty .- fit1.param[1]) .* 1000,
          "C$(i - 1)", label="$(power) mW")
 end
-xticks([288500, 288525, 288550, 288575, 288600])
+xticks([288500, 288530, 288560, 288590, 288620])
 # p: framan0, fpa0, offset, strength, bs...
 # text(560, 1700, ("\$f_{Raman0} + a\\cdot P\$\n" *
 #                  "  \$-\\dfrac{b}{f-f_{PA0}}\\cdot P\$"))

### 2020-10-11 plot_rabi_scaling.jl
rabi scaling

@@ -1,0 +1,149 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival, get_plot_range
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+
+const freqs = [560 15 3.282 0.042
+               560 6 1.182 0.033
+               560 3 0.488 0.015
+
+               503 15 2.073 0.051
+               503 9 1.074 0.036
+               503 6 0.680 0.022
+               503 3 0.2544 0.0077
+
+               605 15 6.39 0.15
+               605 6 1.985 0.043
+               605 3 0.845 0.042
+
+               625 15 8.35 0.25
+               625 6 2.513 0.036
+               625 3 0.996 0.029
+               ]
+
+function model_omega(x, p)
+    return p[1] .* x.^1.29
+end
+
+broacast_array(f, x) = f(x)
+broacast_array(f, x::AbstractArray) = f.(x)
+
+# x: freq, power
+# p: offset, strength
+function gen_model(fpa0)
+    function model(xs, p)
+        function real_model(x)
+            freq, power = x
+            offset, strength = p
+            p_omega = (offset - strength / (freq - fpa0),)
+            return model_omega(power, p_omega)
+        end
+        return broacast_array(real_model, xs)
+    end
+end
+
+function gen_data(data_in)
+    freq_ids = Dict{Float64,Int}()
+    xs = Tuple{Float64,Float64,Int}[]
+    ys = Float64[]
+    uncs = Float64[]
+    idmax = 0
+    for i in 1:size(data_in, 1)
+        freq = data_in[i, 1]
+        power = data_in[i, 2]
+        freq_id = get!(freq_ids, freq) do
+            idmax += 1
+            return idmax
+        end
+        push!(xs, (freq, power, freq_id))
+        push!(ys, data_in[i, 3])
+        push!(uncs, data_in[i, 4])
+    end
+    return (x=xs, y=ys, unc=uncs, freqs=collect(keys(freq_ids)))
+end
+
[…]

### 2020-10-11 plot_atomic_loss_scaling.jl
atomic loss scaling

@@ -1,0 +1,42 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival, get_plot_range
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+
+const rates = [15 32.5 3.1
+               6 2.77 0.27
+               3 0.573 0.078]
+
+function gen_power_model(pwr)
+    return function (x, p)
+        return p[1] .* x.^pwr
+    end
+end
+fit_gamma_a2 = fit_data(gen_power_model(2.58), rates[:, 1], rates[:, 2], rates[:, 3],
+                        [1.0]; plot_lo=2.7)
+@show fit_gamma_a2.uncs
+
+const prefix = joinpath(@__DIR__, "imgs", "atomic_loss_scaling")
+
+figure()
+errorbar(rates[:, 1], rates[:, 2], rates[:, 3], fmt="C0.")
+plot(fit_gamma_a2.plotx, fit_gamma_a2.ploty, "C0")
+xscale("log")
+yscale("log")
+grid()
+xticks([3, 4, 6, 8, 12], ["3", "4", "6", "8", "12"])
+yticks([1, 3, 10, 30], ["1", "3", "10", "30"])
+xlabel("Tweezer Power (mW)")
+ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$")
+NaCsPlot.maybe_save("$(prefix)")
+
+NaCsPlot.maybe_show()

### 2020-10-11 plot_rabi_scaling.jl
Consistent legend style and update figure 4

@@ -140,7 +140,7 @@ xticks([288500, 288530, 288560, 288590, 288620])
 # text(500, 5.0, ("\$\\left(a-\\dfrac{b}{f-705 GHz}\\right)\\cdot P^{1.29}\$"))
 # text(500, 2.8, ("\$a=$(fit1.uncs[1] * 1000)\$ Hz/mW\$^{1.29}\$\n" *
 #               "\$b=$(fit1.uncs[2])\$ kHz\$\\cdot\$GHz/mW\$^{1.29}\$"), fontsize="small")
-legend(fontsize="x-small")
+legend(loc="upper center", fontsize="small")
 grid()
 xlabel("Tweezer Frequency (GHz)")
 ylabel("\$\\Omega_{Raman} (2\\pi\\cdot \\mathrm{kHz})\$")

### 2020-10-11 plot_res_scaling.jl

@@ -182,7 +182,7 @@ xticks([288500, 288530, 288560, 288590, 288620])
 #                 "\$f_{PA0}=$(fit1.uncs[2] + 288000)\$ GHz\n" *
 #                 "\$a=$(fit1.uncs[3] * 1000)\$ kHz/mW\n" *
 #                 "\$b=$(fit1.uncs[4])\$ MHz\$\\cdot\$GHz/mW"), fontsize="small")
-legend(fontsize="small")
+legend(loc="upper center", fontsize="small")
 grid()
 xlabel("Tweezer Frequency (GHz)")
 ylabel("Light Shift (kHz)")

### 2020-10-11 paper.tex
white space, regenerate pdf
Update figure 4 legend
update numbers

@@
 % For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
-%Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
+% Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
 The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can also be made smaller by detuning away from the dissociation threshold.
@@
 
-%\textcolor{blue}{Main point here.
+% \textcolor{blue}{Main point here.
 Small $\Omega_a/\Omega_m$ ratio can be compensated by larger detuning, but Stark shift is problematic.} \textcolor{red}{KW: I agree Stark shift limitation is definitely pretty problematic, but I would also argue that larger detuning may not be able to save the day, because of the many vibrational states in a molecular potential, the lower Raman rabi frequency which results from detuning farther and possibly running into other limitations if you have to do that, such as the background off resonant scattering rate from near threshold states or technical background scattering.} \textcolor{blue}{yes, I agree.
@@
 }
-%In addition to the intermediate state, the choice of the initial and final states is also critical. 
+% In addition to the intermediate state, the choice of the initial and final states is also critical.
 As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio.
@@
 Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the 4422 or 3311 combinations.
-%Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.  
+% Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
 Thus, we choose the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination.
@@
 From this measurement, we can calculate a matrix element between the molecular state and
-the excited state, $\Omega_m$, of $2\pi\times89.40(17) \mathrm{MHz}/\sqrt{\mathrm{mW}}$
-or $2\pi\times346.24(65) \mathrm{MHz}$ for the $15 \mathrm{mW}$ tweezer power used above.
-This number is about $3$ times larger than the value of
+the excited state, $\Omega_m$, of $2\pi\times36.162(20) \mathrm{MHz}/\sqrt{\mathrm{mW}}$
+or $2\pi\times140.056(78) \mathrm{MHz}$ for the $15 \mathrm{mW}$ tweezer power used above.
+This number is consistent with the value of
 $2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ \todo{ref/sm theory}.
@@
 a $v'=0$ component in the Raman Rabi frequency.
-Based on the $v'=0$ component and the $\Omega_m$ measured above,
-we measured a up leg Rabi frequency of $...$, or $...$ at $15 \mathrm{mW}$ tweezer power.
-This gives a Rabi frequency, and therefore matrix element, ratio of $...$,
-which is in fact better than the theory prediction of $...$
+The $v'=0$ component of the Raman Rabi frequency is
+$2\pi\times161.8(22) \mathrm{Hz\cdot mW^{-1.29}}$,
+or $2\pi5.324(73)\mathrm{kHz}$ at $15 \mathrm{mW}$ tweezer power.
+Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
+$2\pi11.53(16)\mathrm{MHz}$.
+This gives a Rabi frequency, and therefore matrix element, ratio of $12.14(16)$,
+which is in fact better than the theory prediction of $23.7$
 and should not cause the scattering from the $v'=0$ state to be higher than expected.
@@
 Unfortunately, the offset in the Raman Rabi frequency fit cancels
-the Rabi frequency for red detuning Raman transition and reduces it by about $...\times$
+the Rabi frequency for red detuning Raman transition and reduces it by about $30\%$
 at the current detuning. However, this difference is not enough to explain
@@
     and follows $1/\delta$ with an offset.
+    The fit also includes a small term that is proportional to $P_{tweezer}^2$
+    which is caused by the effective magnetic field generated by the tweezer which is
+    perpendicular to the real magnetic field.
     (B) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\delta$ with an offset.

### 2020-10-11 paper.tex
A few more numbers

@@
   Starting from two atoms in their relative motional ground state,
-  we achieve optical transfer efficiency of $50 \%$ \todo{number}.
-  The molecule has a (change to 8.8G) zero-field binding energy of $770 \mathrm{MHz}$ \todo{number}
-  and lifetime up to $1 \mathrm{ms}$ \todo{number}. (center of mass motional state population.)
+  we achieve optical transfer efficiency of $69\%$.
+  The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8 \mathrm{G}$
+  and lifetime up to $1 \mathrm{ms}$ with more than $60\%$ of the molecule created in the
+  motional ground state.
   % We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition.
@@
 The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
-B field dependency $... kHz/G$ which agrees with theory prediction of $... kHz/G$.
-Dependency on tweezer power $... kHz/mW$, extrapulated to obtain the bare resonance at $0$ tweezer power to be at $... MHz$.
+B field dependency $42.17(24) kHz/G$ which agrees with theory prediction of $... kHz/G$.
 

### 2020-10-12 paper.tex
Update affiliation

@@
 \author{J. D. Hood}
+\altaffiliation{Department of Chemistry, Purdue University, West Lafayette, Indiana, 47907, USA}
 \author{Lewis Picard}
@@
 \author{Jeremy Hutson}
+\altaffiliation{Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
 \author{Till Rosenband}
@@
   This technique is general without relying on narrow excited state lines or Feshbach resonances and could allow a wider range of molecular species to be assembled atom-by-atom.
-\textcolor{blue}{Yichao, can you update numbers in the abstract?
-also, can you update affiliations in the author list, Jeremy is Durham and Jon is Purdue}
 \end{abstract}

### 2020-10-14 paper.tex
Clear notes
Update on Overleaf.

@@
   we achieve optical transfer efficiency of $69\%$.
-  The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8 \mathrm{G}$
-  and lifetime up to $1 \mathrm{ms}$ with more than $60\%$ of the molecule created in the
+  The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8~\mathrm{G}$
+  and lifetime up to $1 \mathrm{ms}$ \textcolor{blue}{(1~ms seems long here)} with more than $60\%$ of the molecule created in the
   motional ground state.
@@
 \end{abstract}
-
-% Coherent
-% Intermediate state
-% Motional state control
-% Initial state preparation
 

### 2020-10-14 paper.tex
Update author affiliation

@@
-\documentclass[aps,prl,twocolumn,groupedaddress]{revtex4-1}
+\documentclass[aps,prl,twocolumn,superscriptaddress]{revtex4-1}
 % \documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4-1}
@@
 
+\newcommand{\cuaphysics}{
+  \affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+  \affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
+  \affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
+}
+
 \begin{document}
@@
 \email{yichaoyu@g.harvard.edu}
+\cuaphysics
 \author{Kenneth Wang}
-\author{J. D. Hood}
-\altaffiliation{Department of Chemistry, Purdue University, West Lafayette, Indiana, 47907, USA}
-\author{Lewis Picard}
-\author{Jessie T. Zhang}
-\author{William Cairncross}
-\author{Jeremy Hutson}
-\altaffiliation{Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
+\cuaphysics
+\author{Jonathan~D.~Hood}
+\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indianna, 47906}
+\author{Lewis~R.~B.~Picard}
+\cuaphysics
+\author{Jessie~T.~Zhang}
+\cuaphysics
+\author{William~B.~Cairncross}
+\cuaphysics
+\author{Jeremy~M.~Hutson}
+\affiliation{Joint Quantum Centre Durham-Newcastle, Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
 \author{Till Rosenband}
-\author{Kang-Kuen Ni}
+\author{Kang-Kuen~Ni}
 \email{ni@chemistry.harvard.edu}
-\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts, 02138, USA}
-\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts, 02138, USA}
-\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts, 02138, USA}
+\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
 

### 2020-10-15 paper.tex
Update on Overleaf.

@@
 \usepackage[colorlinks=true]{hyperref}
+\usepackage{footmisc}
+\usepackage{braket}
 
@@
 \author{Till Rosenband}
+\cuaphysics
 \author{Kang-Kuen~Ni}
 \email{ni@chemistry.harvard.edu}
-\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
+\cuaphysics
+%\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
+%\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+%\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
 
@@
 
-Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state, schematically shown in Fig.~\ref{f-theory}A.
+Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}A, neither using a Feshbach resonance nor a narrow excited state.
 The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.
-Our scheme is based on using a theoretically determined vibrational state of the electronic excited state $c^3\Sigma^+$ that has the best raman Rabi frequency to photon scattering ratio.
+Our scheme is based on a choice of vibrational state of the electronic excited state $c^3\Sigma^+(\Omega = 1)$ that has the theoretical best raman Rabi frequency to photon scattering ratio.
 To further increase this ratio and reduce technical requirements such as intensity stability, we choose an initial and final state where the matrix elements with the excited state are as balanced as possible.
@@
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
-The transfer Raman Rabi Rate is $ \Omega_a\Omega_m / 2\Delta$ accompanied by a photon scattering rate of $\Gamma_e \Omega^2 / 4\Delta^2$...(sum of i terms\textcolor{red}{KW: I was intending to only mention the sum over terms at the end when we exit the 3 level system.})\textcolor{blue}{check factor of 2.
-KW: The 2 in the denominator is including cross coupling.
-4 without cross coupling.
-Since cross coupling is mentioned later, maybe leave this with 4?}, where $ \Gamma_e $ is the excited state linewidth~\cite{Wineland2003}.
-%, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}.
+The transfer Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate which is a sum of all coupling sources %of $\sum_{n=i} \Gamma_e \Omega_i^2 / 4\Delta^2 $,
+$\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth~\cite{Wineland2003}. %, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}.
 Unlike for Raman transitions in atoms, the two matrix elements here, $ \Omega_m$ and $ \Omega_a$, are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
-due to the small wavefunction overlap between the atomic state and the excited molecular state.
-The scattering rate therefore predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth.
-\textcolor{blue}{(blue text can potentially be moved to footnote) Furthermore, because the energy difference of the atomic and the weakly bound states are small ($<$1~GHz) comparing to $\Delta$, the power of the Raman beams are chosen to be equal to gives the largest Raman Rabi rate at a fixed total power.
-%There is
-  An additional factor of 2 is included in the scattering rate because the molecular state scatters off of both Raman beams at roughly the same single photon detuning.
-} Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
-To ensure a coherent process, larger detuning is preferred while achieving a realistic Raman Rabi frequency.
+due to the small wavefunction overlap between the atomic state and the excited molecular state, and the scattering is predominantly from the molecular state.
+Furthermore, the energy difference between the atomic and weakly bound state is small ($ < 1 \mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the molecular state can scatter off both beams at roughly the same single photon detuning.
+Thus, the scattering is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$ \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi Rate at a fixed total power.
+Thus, this results in an additional factor of 2 coming from scattering off 2 beams.}.
+The ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
+To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred.
 %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
-With the multiple excited vibrational states present in a molecular potential, the total scattering rates and Rabi rates become a sum of the scattering rates and Rabi rates over all the states.
+With the multiple excited vibrational states present in a molecular potential, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual states.
 %There are also many possible intermediate states to choose from.
@@
 However, such choice of state suffers from strong scattering of the nearby atomic excited state to render it incoherent, resulting in molecule loss.
-The scattering  is  proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can  be made smaller by detuning away from the dissociation threshold.
+This scattering is  proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can  be made smaller by detuning away from the dissociation threshold.
 
@@
 
-To find the optimal excited intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma$ excited molecular state potential (full result in SM)~\cite{Liu2017} \textcolor{red}{KW: I have only done the calculations with c3Sigma only, cause the b3Pi is highly spin orbit coupled, and not necessarily trustworthy where we are.
-I can also include a citation to the paper with that potential?}.
+To find the optimal excited intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential (full result in SM)~\cite{Liu2017, Grochola2011}.
 As shown in Fig.~\ref{f-theory}B, the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency.
@@
 % Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state.
-As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) as an intermediate state to drive the Raman transition.
+As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+(\Omega = 1)$) as an intermediate state to drive the Raman transition.
 %(mention the trend, also v'=12 will work as similarly as v'=0)
@@
 In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation.
-The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $.
-\textcolor{red}{KW: Can also include similar footnote here about cross coupling?
-The 2 in the denominator is assuming cross coupling and equal powers.} The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process.
+The position of the two photon resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift of both beams.}.
+The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process.
 The ratio, $ \Omega_a/\Omega_m $ can be changed through the choice of initial and final states.
@@
 The increase in the coupling is proportional to (quote/cite Olive's equation?).
-For our system, among the stable spin combinations, 4422 and 3311 both have small scattering lengths of $ a_{4422}= 30.4a_0, a_{3311} = 13.7a_0 $ respectively, but the 3332 combination has a large and negative scattering length of $ a_{3322} = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
-In addition to the increased atomic coupling, $ \Omega_a $, with the 3322 hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly in the 3322 spin combination also has reduced coupling, $ \Omega_m $, with the excited state when compared with the 4422 and 3311 bound states.
-Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the 4422 or 3311 combinations.
+For our system, we denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\text{Cs}}} = \ket{F=4,m_F=4}_{\text{Cs}}, \ket{\downarrow_{\text{Cs}}} = \ket{F=3,m_F=3}_{\text{Cs}}, \ket{\uparrow_{\text{Na}}} = \ket{F=2,m_F=2}_{\text{Na}}, $ and $ \ket{\downarrow_{\text{Na}}} = \ket{F=1,m_F=1}_{\text{Na}}$.
+Among the stable spin combinations, $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}} $ combination has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
+In addition to the increased atomic coupling, $ \Omega_a $, with the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly in this spin combination also has reduced coupling, $ \Omega_m $, with the excited state when compared with the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ bound states.
+Therefore, using an initial $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the other combinations.
 % Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
-Thus, we choose the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination.
-(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
+Thus, we choose the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination.
+%(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
 
@@
 After RSC, the Na tweezer is moved by sweeping the frequency on an acoustical optical beam deflector (AOBD) to overlap with the Cs tweezer before smoothly ramping off, so that the Na and Cs atoms are merged into the same tweezer~\cite{Liu2019}.
-The spin states for the Na and Cs atoms after RSC and during the merge process are $|F=2,m_F=2\rangle_{Na}$ and $|F=4,m_F=4\rangle_{Cs}$ respectively.
+The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $.
 This states combination has a low scattering length, which allows the two atoms to be merged into the same tweezer with minimum pertubation on each other and thus they remain in the motional ground state after the merge.
 
-After preparing the Na and Cs atoms in the same tweezer in a single quantum state, we need to drive the atoms into the large scattering length 3322 hyperfine combination.
-To do this, we perform a spin flip taking into account the interaction shift~\cite{Hood2019} using a Cs Raman transition to drive the Cs atom into the $|F=3,m_F=3\rangle_{Cs}$ state.
+After preparing the Na and Cs atoms in the same tweezer in a single quantum state, we need to drive the atoms into the large scattering length $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination.
+To do this, we perform a spin flip taking into account the interaction shift~\cite{Hood2019} using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\text{Cs}}}$ state.
 The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
@@
 %% Transfer scheme
-After the atoms are prepared in the 3322 hyperfine combination, we then perform the Raman transfer.
+After the atoms are prepared in the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $ hyperfine combination, we then perform the Raman transfer.
 The pulse sequence for this step is shown in Fig.~\ref{f-raman}B.
@@
 Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.
-In additional to reducing the number of laser beams during the Raman transition,
+In addition to reducing the number of laser beams during the Raman transition,
 we also found the spectral purity of the laser to be critical for achieving a higher
 transfer efficiency. The tweezer and Raman beams are generated by amplifying a $1037 \mathrm{nm}$
-external cavity diode laser (ECDL) with a Raman fiber amplifier,
-which produces a broad band amplified spontaneous emission (ASE),
-in addtional to the desired frequency, and increases the scattering rate due to coupline to
+external cavity diode laser (ECDL) with a fiber amplifier,
+which produces a broad band amplified spontaneous emission (ASE)
+in addition to the desired frequency. This increases the scattering rate due to coupling to
 other excited states.
-We use a bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the
+We use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the
 laser spectrum and found it reduces the scattering rate by at least a factor of $2$
-for certain tweezer detuning.
+for a particular single photon detuning.
 
@@
 it can be either due to a high ratio of $\Omega_m / \Omega_a$ or a large $\Gamma_e$.
-Additionally, coupling to other excited states can also adds an offset to both the Raman
+Additionally, coupling to other excited states can also add an offset to both the Raman
 Rabi frequency and the scattering rate which can affect the scattering rate
@@
 The background is caused by coupling to other excited states that are further away in energy.
-The $1/\delta$ component, however, is predominantly due to the coupling between
+The $1/\Delta$ component, however, is predominantly due to the coupling between
 the molecular state and the $v'=0$ excited state.
@@
 This number is consistent with the value of
-$2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ \todo{ref/sm theory}.
+$2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
 \todo{make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$,
@@
 
-In order to calculate the matrix element ratio,
-next we discuss the dependencies of the Raman Rabi frequency.
+In order to calculate the matrix element ratio, we now need to extract the matrix element between the atomic state and the excited molecular state, $ \Omega_a $.
+We do this by measuring the dependencies of the Raman Rabi frequency, which depends on both $\Omega_m$ and $\Omega_a$.
 The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change
@@
 Similar to the light shift, there is also an offset and
-a $v'=0$ component in the Raman Rabi frequency.
+a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$.
 The $v'=0$ component of the Raman Rabi frequency is
 $2\pi\times161.8(22) \mathrm{Hz\cdot mW^{-1.29}}$,
-or $2\pi5.324(73)\mathrm{kHz}$ at $15 \mathrm{mW}$ tweezer power.
+or $2\pi \times 5.324(73)\mathrm{kHz}$ at $15 \mathrm{mW}$ tweezer power.
 Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
-$2\pi11.53(16)\mathrm{MHz}$.
+$2\pi \times 11.53(16)\mathrm{MHz}$.
 This gives a Rabi frequency, and therefore matrix element, ratio of $12.14(16)$,
@@
 but we have observed additional excited states at slightly higher frequencies
-which prevent the blue side of the transition to be usuable for Raman transition.
+which prevent the blue side of the transition to be usable for the Raman transition.
 
@@
     (A) The light shift of the Raman resonance scales as $P_{tweezer}$
-    and follows $1/\delta$ with an offset.
+    and follows $1/\Delta$ with an offset.
     The fit also includes a small term that is proportional to $P_{tweezer}^2$
@@
     perpendicular to the real magnetic field.
-    (B) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\delta$ with an offset.
+    (B) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\Delta$ with an offset.
     From these results we can confirm the theory prediction of
@@
 Based on our previous measurements of the excited state using photoassociation (PA) spectroscopy,
-the linewidth of the $v'=0$ excited state is no larger than $20 \mathrm{MHz}$.
+the natural linewidth of the $v'=0$ excited state is no larger than $20 \mathrm{MHz}$.
 This suggests that the excited state linewidth should not cause a stronger than expected

### 2020-10-15 paper.tex
Update on Overleaf.

@@
 
-The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.
+The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)

### 2020-10-15 paper.tex
White space, regenerate PDF

@@
 \title{Coherent optical association of a single molecule}
-\author{Yichao Yu}
+\author{Yichao~Yu}
 \email{yichaoyu@g.harvard.edu}
-\cuaphysics
-\author{Kenneth Wang}
-\cuaphysics
+\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
+\author{Kenneth~Wang}
+\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
 \author{Jonathan~D.~Hood}
@@
 \author{Lewis~R.~B.~Picard}
-\cuaphysics
+\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
+
 \author{Jessie~T.~Zhang}
-\cuaphysics
+\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
+
 \author{William~B.~Cairncross}
-\cuaphysics
+\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
+
 \author{Jeremy~M.~Hutson}
@@
 \author{Till Rosenband}
-\cuaphysics
+\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
 \author{Kang-Kuen~Ni}
 \email{ni@chemistry.harvard.edu}
-\cuaphysics
-%\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
-%\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
-%\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
+\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
+
+% \affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
+% \affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+% \affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
 
@@
 
+In conclusion, we have formed a weakly bound NaCs molecule in an optical tweezer via an optical Raman transfer.
+A theoretical investigation including all excited states of $ c^3\Sigma^+(\Omega = 1)$ and coupled channel ground state wavefunctions indicated better transfer efficiency using a deeply bound intermediate state and the $ \ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}} } $ hyperfine state combination.
+Using these theoretical insights, we located the weakly bound state and coherently associated the atoms into the weakly bound molecule.
+Our transfer efficiency is limited by an unknown scattering source resulting in measured scattering rates over 10 times larger than theory predictions.
+Despite this limitation, the transfer efficiency may be further improved by increasing the $ \Omega_a/\Omega_m$ ratio by exploring the possibility of driving to more deeply bound states.
+There may also be a better choice of single photon detuning to increase the Raman Rabi frequency, since our location results in about 30\% cancellation of the Raman Rabi frequency due to an offset of unknown origin.
+(Do we want to mention also technical improvements as another way to potentially improve our signal?
+Though I guess that was mentioned directly in the paragraph above...) Nevertheless, our technique, with the right choice of parameters, can be used to form a more diverse set of molecular species, since it does not rely on a magnetic Feshbach resonance or a narrow excited state (More sentences here to discuss scientific outlook, but without repeating the introduction...?
+\textcolor{blue}{Yes, on topics related to single molecules for exciting science!!})
+
 \todo{sm: STIRAP vs Raman}

### 2020-10-16 paper.tex
Update on Overleaf.
remove duplicated affiliation string again...

@@
 
-\newcommand{\cuaphysics}{
-  \affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
-  \affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
-  \affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
+\newcommand{\harvardphysics}{\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}}
+\newcommand{\harvardccb}{\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}}
+\newcommand{\cua}{\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}}
+\newcommand{\gradstudent}{
+  \harvardphysics
+  \harvardccb
+  \cua
 }
@@
 \email{yichaoyu@g.harvard.edu}
-\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
+\gradstudent
 \author{Kenneth~Wang}
-\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
+\gradstudent
 \author{Jonathan~D.~Hood}
@@
 \author{Lewis~R.~B.~Picard}
-\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
-
+\gradstudent
 \author{Jessie~T.~Zhang}
-\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
-
+\gradstudent
 \author{William~B.~Cairncross}
-\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
-
+\harvardccb
+\harvardphysics
+\cua
 \author{Jeremy~M.~Hutson}
@@
 \author{Till Rosenband}
-\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+\harvardphysics
 \author{Kang-Kuen~Ni}
 \email{ni@chemistry.harvard.edu}
-\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
-\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
-
-% \affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
-% \affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
-% \affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
+\harvardccb
+\harvardphysics
+\cua
 

### 2020-10-16 paper.tex
Update on Overleaf.

@@
 
-Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan2017}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111}.
+Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan2017, PhysRevA.101.042504} \textcolor{red}{KW: added a citation here for some exotic atomic/molecular species for precision measurements.
+Can delete this text, if you think it's appropriate, or otherwise remove this reference.}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111}.
 While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016, Mitra1366}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the association of ultracold atoms.
@@
 In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation.
-The position of the two photon resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift of both beams.}.
+The position of the two photon resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.}.
 The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process.
@@
 (Do we want to mention also technical improvements as another way to potentially improve our signal?
-Though I guess that was mentioned directly in the paragraph above...) Nevertheless, our technique, with the right choice of parameters, can be used to form a more diverse set of molecular species, since it does not rely on a magnetic Feshbach resonance or a narrow excited state (More sentences here to discuss scientific outlook, but without repeating the introduction...?
-\textcolor{blue}{Yes, on topics related to single molecules for exciting science!!})
+Though I guess that was mentioned directly in the paragraph above...) Nevertheless, our technique, with the right choice of parameters, can be used to form a more diverse set of molecular species, since it does not rely on a magnetic Feshbach resonance or a narrow excited state.
+The formation of a weakly bound molecule is also a key step in forming rovibrational ground state molecules.
+Combined with real time rearrangement \cite{Barredo2016, Endres2016}, defect free arrays of highly controlled molecules can be formed in arbitrary geometries.
+These arrays are a promising and flexible platform for quantum simulation and quantum computing applications.
 

### 2020-10-19 paper.tex
Update on Overleaf.

@@
   motional ground state.
-  % We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition.
   This technique is general without relying on narrow excited state lines or Feshbach resonances and could allow a wider range of molecular species to be assembled atom-by-atom.
@@
 
-Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan2017, PhysRevA.101.042504} \textcolor{red}{KW: added a citation here for some exotic atomic/molecular species for precision measurements.
-Can delete this text, if you think it's appropriate, or otherwise remove this reference.}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111}.
+Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018, PhysRevLett.119.153001, hudson2011}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111}.
 While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016, Mitra1366}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the association of ultracold atoms.
 % (any place to cite  molecular ion work?)
-% cite recent doyle group result on cooling symmetric top molecule? FOR SURE, and other laser cooling works and electro-optical-cooling! Citations are not complete. Add them as you see fit.
+% Citations are not complete. Add them as you see fit.
 
@@
 So far, all of such association processes utilized a magnetic Feshbach scattering resonance and have been applied to bialkali molecules.
-The only exception is Sr$_2$ where narrow linewidth excited states are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012}.
-The requirement of a Feshbach resonance to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of the association technique.
+The only exceptions are Sr$_2$ where narrow linewidth excited states are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb where weakly bound molecules of a binding energy of a couple MHz exists~\cite{He331}.
+These requirements greatly limit the generality of previous association techniques.
+%The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques.
 % to more diverse species.
 
-Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}A, neither using a Feshbach resonance nor a narrow excited state.
+Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}A, neither using a Feshbach resonance, few MHz-level bound states, nor a narrow excited state.
 The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.
@@
 
-The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
+\textcolor{blue}{(need to make consistent concise terminology, excited state molecule, weakly bound molecule, molecular state, etc.
+call them  state 1, 2, 3?
+or revert back to call the intermediate state without mentioning molecule?).} The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
-The transfer Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate which is a sum of all coupling sources %of $\sum_{n=i} \Gamma_e \Omega_i^2 / 4\Delta^2 $,
-$\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth~\cite{Wineland2003}. %, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}.
-Unlike for Raman transitions in atoms, the two matrix elements here, $ \Omega_m$ and $ \Omega_a$, are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
-due to the small wavefunction overlap between the atomic state and the excited molecular state, and the scattering is predominantly from the molecular state.
-Furthermore, the energy difference between the atomic and weakly bound state is small ($ < 1 \mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the molecular state can scatter off both beams at roughly the same single photon detuning.
-Thus, the scattering is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$ \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi Rate at a fixed total power.
-Thus, this results in an additional factor of 2 coming from scattering off 2 beams.}.
-The ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
+The transfer Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate that is a sum of all coupling sources%, 
+%$\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
+~\cite{Wineland2003}. 
+Unlike for Raman transitions in atoms, the two coupling matrix elements here are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
+due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
+and therefore the scattering is predominantly from the molecular state.
+Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the molecular state can scatter off both beams roughly equally.
+Thus, the scattering is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi Rate at a fixed total power.
+Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
+The ratio between the Raman Rabi frequency and the scattering rate is therefore $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $.
+%, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
 To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred.
 %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
-With the multiple excited vibrational states present in a molecular potential, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual states.
-%There are also many possible intermediate states to choose from.
+With the multiple excited vibrational states present in a molecular potential as intermediate states, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual intermediate states.
+Furthermore, for a more complete calculation, we also need to account for the effects of the excited atomic continuum, which is particularly important for the target molecular state.
+\footnote{The sum of the squares of the wavefunction overlap between the weakly bound molecular state and all the excited intermediate states considered is only about 2\%, suggesting that there is significant matrix element between this weakly bound state and the excited atomic continuum.
+See supplementary information.} \textcolor{red}{(KW: I included a footnote here, but we can also consider putting this information into the main text?)}
 
-Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
-However, such choice of state suffers from strong scattering of the nearby atomic excited state to render it incoherent, resulting in molecule loss.
+Pioneering experiments used weakly-bound excited states as the intermediate state in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
+However, such choice of state suffers from strong scattering of the nearby excited atomic continuum to render it incoherent, resulting in molecule loss.
 This scattering is  proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can  be made smaller by detuning away from the dissociation threshold.
@@
 
-To find the optimal excited intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential (full result in SM)~\cite{Liu2017, Grochola2011}.
-As shown in Fig.~\ref{f-theory}B, the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency.
-%Since for a typical molecular potential the spacing between states
-% decreases with increasing vibrational levels,
-% a weakly bound excited molecular state
-% This further increases the scattering rate for a weakly bond excited state.
-% Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
-% we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in Fig.~\ref{f-theory}B,
-% we found a distinct optimal regime from what has been explored experimentally previously.
-% Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state.
-As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+(\Omega = 1)$) as an intermediate state to drive the Raman transition.
-%(mention the trend, also v'=12 will work as similarly as v'=0)
+To find the optimal intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011} and the continuum~\cite{Liu2017}.
+As shown in Fig.~\ref{f-theory}B (full result in SM), the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency.
+As a result, we choose %a deeply bound molecular excited state
+the $v'=0$ of $c^3\Sigma^+(\Omega = 1)$ as an intermediate state to drive the Raman transition. %(mention the trend, also v'=12 will work as similarly as v'=0)
 
@@
 % In addition to the intermediate state, the choice of the initial and final states is also critical.
-As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio.
+In addition to the intermediate state, choosing an initial and a final state for a large  $ \Omega_a/\Omega_m $ ratio would allow large Raman Rabi coupling at a given detuning.
+Furthermore, a larger ratio also relaxes the intensity stability requirement, because this is also the ratio between the Raman Rabi coupling and the AC Stark shift of the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2, with both beams at equal power, to account for the Stark shift caused by both beams.}.
+%and relax the intensity stability requirement due to the AC Stark shift of the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.}
+%As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio.
 The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate.
@@
 The ratio, $ \Omega_a/\Omega_m $ can be changed through the choice of initial and final states.
-In particular, it can be made larger by increasing the coupling of the atomic state with the excited molecular state.
-Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential.
-In addition to the confinement, this value is related to the interaction between the two atoms.
-For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}C).
-The increase in the coupling is proportional to (quote/cite Olive's equation?).
-For our system, we denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\text{Cs}}} = \ket{F=4,m_F=4}_{\text{Cs}}, \ket{\downarrow_{\text{Cs}}} = \ket{F=3,m_F=3}_{\text{Cs}}, \ket{\uparrow_{\text{Na}}} = \ket{F=2,m_F=2}_{\text{Na}}, $ and $ \ket{\downarrow_{\text{Na}}} = \ket{F=1,m_F=1}_{\text{Na}}$.
+%Because of the large atom and molecule wavefunction mismatch, choosing an initial atomic state that has more amplitude at smaller internuclear distance can increase the coupling $\Omega_a$.
+\textcolor{blue}{(the two sentences have the same idea.)}
+%it can be made larger by increasing the coupling of the atomic state with the excited molecular state. 
+Due to the small size of the intermediate state wavefunction, the coupling $\Omega_a$ is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential.
+To increase the amplitude within the molecular potential, one can increase the external confinement of atom pairs.
+Using a harmonic oscillator approximation, the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/8} $, where $ \omega_{\text{trap}} $ is the trap frequency.
+Alternatively, one can choose an atomic pair state with a large scattering length (positive or negative).
+For these states, the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}C).
+%The increase in the coupling is proportional to (quote/cite Olive's equation?).
+For our system of Na and Cs atoms, we chose  a  spin state combination $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}\equiv \ket{F=2,m_F=2}_{\text{Na}}\ket{F=3,m_F=3}_{\text{Cs}} $that has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0$~\cite{Hood2019}.
+We note that other stable spin combinations give smaller scattering lengths ($<~50~a_0$) \textcolor{blue}{(define arbitrarily).}
+%We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\text{Cs}}} = \ket{F=4,m_F=4}_{\text{Cs}}, \ket{\downarrow_{\text{Cs}}} = \ket{F=3,m_F=3}_{\text{Cs}}, \ket{\uparrow_{\text{Na}}} = \ket{F=2,m_F=2}_{\text{Na}}, $ and $ \ket{\downarrow_{\text{Na}}} = \ket{F=1,m_F=1}_{\text{Na}}$.
 Among the stable spin combinations, $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}} $ combination has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
-In addition to the increased atomic coupling, $ \Omega_a $, with the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly in this spin combination also has reduced coupling, $ \Omega_m $, with the excited state when compared with the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ bound states.
-Therefore, using an initial $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the other combinations.
+In addition to the increased atomic coupling, $ \Omega_a $, %with the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination, 
+coupled channel calculations show that the target molecular state that is predominantly in this spin combination also has reduced coupling, $ \Omega_m $, with the intermediate state when compared to bound states of the other stable spin combinations % $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ bound states.
+Therefore, using an initial $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the other combinations, and thus only an required intensity stability of 5\% instead of 0.3\%.
 % Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
-Thus, we choose the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination.
-%(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
+%Thus, we choose the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination.
+\textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
 
@@
 %% Preparation
-To perform the Raman transfer, we use our apparatus described in our previous work~\cite{Liu2019}.
-Our experiment begins by stochastically loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into an optical tweezer from a dual-species MOT\todo{cite na loading paper} into separate optical tweezers.
-The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom in order to perform post selection.
-We then perform simultaneous Raman sideband cooling (RSC) to cool both atoms into the 3-dimensional motional ground state of their optical tweezers.
-After RSC, the Na tweezer is moved by sweeping the frequency on an acoustical optical beam deflector (AOBD) to overlap with the Cs tweezer before smoothly ramping off, so that the Na and Cs atoms are merged into the same tweezer~\cite{Liu2019}.
-The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $.
-This states combination has a low scattering length, which allows the two atoms to be merged into the same tweezer with minimum pertubation on each other and thus they remain in the motional ground state after the merge.
+Experimentally, we first prepare two atoms in a well-defined external and internal quantum state using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}.
+In brief, the experimental cycle begins by  loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom stochastically into separate optical tweezers.
+The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom, which is compared to the image at the end of the experiment.
+Raman sideband cooling is then applied to cool both atoms simultaneous into the 3-dimensional motional ground state of their optical tweezers.
+After cooling, the Na and Cs atoms are in a spin state of $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}\equiv \ket{F=2,m_F=2}_{\text{Na}}\ket{F=4,m_F=4}_{\text{Cs}} $ %and are merged into the same tweezer~\cite{Liu2019}.
+%The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $.
+that has a low scattering length.
+The small two atom interaction allows the two atoms to be merged into the same tweezer with minimum pertubation  and remain in the motional ground state after the merge.
 
-After preparing the Na and Cs atoms in the same tweezer in a single quantum state, we need to drive the atoms into the large scattering length $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination.
-To do this, we perform a spin flip taking into account the interaction shift~\cite{Hood2019} using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\text{Cs}}}$ state.
+%After preparing the Na and Cs atoms in the same tweezer in a single quantum state, 
+Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7 kHz$ interaction shift~\cite{Hood2019}.
+%using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\text{Cs}}}$ state.
 The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
-This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.
-
+This spin flip selectively transfers atoms in the relative motion ground state \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}, and for the experiment reported here, this is 31\% of the initial population of two atoms loaded in separate optical tweezers.
 % The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..
@@
 %% Transfer scheme
-After the atoms are prepared in the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $ hyperfine combination, we then perform the Raman transfer.
-The pulse sequence for this step is shown in Fig.~\ref{f-raman}B.
-Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal.
-In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse.
+%After the atoms are prepared in the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $ hyperfine combination, we then perform the Raman transfer. 
+To perform Raman transfer of an atom pair to the targeted weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}A).
+The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to  maximize the Raman Rabi frequency and minimize the transfer time.
+%to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
+The pulse sequence is shown in Fig.~\ref{f-raman}B. %Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. 
+%In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse.
 The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time.
 After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged.
-Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.
-In addition to reducing the number of laser beams during the Raman transition,
-we also found the spectral purity of the laser to be critical for achieving a higher
-transfer efficiency. The tweezer and Raman beams are generated by amplifying a $1037 \mathrm{nm}$
-external cavity diode laser (ECDL) with a fiber amplifier,
-which produces a broad band amplified spontaneous emission (ASE)
-in addition to the desired frequency. This increases the scattering rate due to coupling to
-other excited states.
-We use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the
-laser spectrum and found it reduces the scattering rate by at least a factor of $2$
-for a particular single photon detuning.
+Both frequencies are kept on for a specified duration before the process is reversed and the tweezer returns to a single frequency.
+%In addition to reducing the number of laser beams during the Raman transition, 
+Furthermore, we use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to filter  the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
+We observed a reduction of the scattering rate by at least  a factor of $2$ \textcolor{blue}{(can we be more definite?)}
+(for a particular single photon detuning) due to the (xx dB?) suppression   of the broadband amplified spontaneous emission (ASE) from the laser that   couples to other excited states.
 
-%% Experiment condition/resonance
+%found the spectral purity of the laser for Raman beams to be critical for achieving a higher transfer efficiency. 
+%The tweezer/Raman beams are generated by a fiber amplifier seeded with a $1037 \mathrm{nm}$ external cavity diode laser. 
+%by amplifying a $1037 \mathrm{nm}$ external cavity diode laser (ECDL) with a fiber amplifier,
+%The diode laser produces the desired frequency on top of a broad band amplified spontaneous emission (ASE).
+We use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the laser spectrum and found it reduces the scattering rate by at least a factor of $2$
+%for a particular single photon detuning.
 
-Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) \mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 mW$ tweezer at $288560 GHz$ which corresponds to a $145 GHz$ single photon detuning.
-(We can maybe add information about the prediction here?)
-%% Prediction
-% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state.
-The ground molecular state has not been observed previously in experimentally.
-Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state.
-Theory prediction was at $770.1 MHz$.
-\todo{more, mention/cite Jeremy}
-The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
-When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imaging step.
-We observed the narrowest linewidth of $7.56(82) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.12 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.907(98)$.
-This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent.
-In order to verify the coherence of the transfer directly, we fix the Raman frequency on resonance and scan the pulse time.
-Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states.
-Fitting the data with a decaying Rabi oscillation suggests that $69\%$ of initial ground state atoms are transferred into the molecular state.
+%in addition to the desired frequency. This increases the scattering rate due to coupling to other excited states.
 
-\begin{figure*}
+\begin{figure*}[t!]
   \includegraphics[height=4.5cm]{fig3.pdf}
@@
 
+%% Experiment condition/resonance
+
+Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) \mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 mW$ tweezer at $288560 GHz$ which corresponds to a $145 GHz$ single photon detuning.
+(We can maybe add information about the prediction here?)
+%% Prediction
+% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state.
+The ground molecular state has not been observed previously in experimentally.
+Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state.
+Theory prediction was at $770.1 MHz$.
+\todo{more, mention/cite Jeremy}
+%The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state. 
+When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence.
+% directly detected by our imaging step.
+We observed the narrowest linewidth of $7.56(82) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.12 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.907(98)$.
+This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent.
+In order to verify the coherence of the transfer directly, we fix the Raman frequency on resonance and scan the pulse time.
+Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states.
+Fitting the data with a decaying Rabi oscillation suggests that $69\%$ of initial ground state atoms are transferred into the molecular state.
+
 In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state (Fig.~\ref{f-lifetime}A).
@@
 The molecule we form has a lifetime of $0.204(13) \mathrm{ms}$ which is the main limitation on the fidelity of the transfer.
-The molecule lifetime can be verified directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C).
+The molecule lifetime can be verified (or measured) directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C).
 The result shows a molecular lifetime consistent with our fitting of the decaying Rabi oscillation.
@@
 
+\begin{figure*}
+  \includegraphics[height=4.5cm]{fig4.pdf}
+  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
+    (A) The light shift of the Raman resonance scales as $P_{tweezer}$
+    and follows $1/\Delta$ with an offset.
+    The fit also includes a small term that is proportional to $P_{tweezer}^2$
+    which is caused by the effective magnetic field generated by the tweezer which is
+    perpendicular to the real magnetic field.
+    (B) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\Delta$ with an offset.
+    From these results we can confirm the theory prediction of
+    the atom-molecule matrix element ratio.
+    (C) Atomic scattering rate scales as $P_{tweezer}^{2.58}$,
+    this is consistent with a two photon scattering process.
+    We have not measured a clear dependency of the loss rate on the tweezer detuning.
+    \label{f-det}}
+\end{figure*}
+
 In order to calculate the matrix element ratio, we now need to extract the matrix element between the atomic state and the excited molecular state, $ \Omega_a $.
@@
 is proportional to the the short range atomic wavefunction amplitude,
-which scales as $P^{0.375}$ for weakly interacting particles.
+which scales as $P^{0.375}$ due to increasing density for weakly interacting particles.
 However, due to the strong interaction between the two atoms, this approximation breaks down.
-Instead, theory calculation shows that the scaling is very well approximated by $P^{0.29}$
+Instead, coupled-channel calculation shows that the scaling is very well approximated by $P^{0.29}$
 within the range of confinement in our experiment.
@@
 which prevent the blue side of the transition to be usable for the Raman transition.
-
-\begin{figure*}
-  \includegraphics[height=4.5cm]{fig4.pdf}
-  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
-    (A) The light shift of the Raman resonance scales as $P_{tweezer}$
-    and follows $1/\Delta$ with an offset.
-    The fit also includes a small term that is proportional to $P_{tweezer}^2$
-    which is caused by the effective magnetic field generated by the tweezer which is
-    perpendicular to the real magnetic field.
-    (B) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\Delta$ with an offset.
-    From these results we can confirm the theory prediction of
-    the atom-molecule matrix element ratio.
-    (C) Atomic scattering rate scales as $P_{tweezer}^{2.58}$,
-    this is consistent with a two photon scattering process.
-    We have not measured a clear dependency of the loss rate on the tweezer detuning.
-    \label{f-det}}
-\end{figure*}
 
@@
 
+\begin{acknowledgments}
+We would like to thank Bo Gao and Paul Julienne, Rosario (?) (anybody else) for discussion.
+This work is supported by the NSF~(PHY-1806595), the AFOSR~(FA9550-19-1-0089), ARO DURIP (W911NF1810194) and the Arnold and Mabel Beckman foundation.
+J.~T.~Z.
+is supported by a National Defense Science and Engineering Graduate Fellowship.
+W.~C.
+is supported by a Max Planck-Harvard Research Center for Quantum Optics fellowship.
+K.~W.
+is supported by an NSF GRFP fellowship.
+J.~M.~H.
+is supported by the U.K.
+Engineering and Physical Sciences Research Council (EPSRC) Grants No.\ EP/N007085/1, EP/P008275/1 and EP/P01058X/1.
+\end{acknowledgments}
+
 \bibliography{master_ref}

### 2020-10-19 paper.tex
White space, remove duplicated reference entry, regenerate PDF
Update on Overleaf.

@@
 These requirements greatly limit the generality of previous association techniques.
-%The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques.
+% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques.
 % to more diverse species.
@@
 
-\textcolor{blue}{(need to make consistent concise terminology, excited state molecule, weakly bound molecule, molecular state, etc.
-call them  state 1, 2, 3?
-or revert back to call the intermediate state without mentioning molecule?).} The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
+The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
 The transfer Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate that is a sum of all coupling sources%,
-%$\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
+% $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
 ~\cite{Wineland2003}.
@@
 due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
-and therefore the scattering is predominantly from the molecular state.
-Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the molecular state can scatter off both beams roughly equally.
-Thus, the scattering is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi Rate at a fixed total power.
+and therefore the scattering is predominantly from the target molecular state.
+Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally.
+Thus, the scattering is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power.
 Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
@@
 Furthermore, for a more complete calculation, we also need to account for the effects of the excited atomic continuum, which is particularly important for the target molecular state.
-\footnote{The sum of the squares of the wavefunction overlap between the weakly bound molecular state and all the excited intermediate states considered is only about 2\%, suggesting that there is significant matrix element between this weakly bound state and the excited atomic continuum.
-See supplementary information.} \textcolor{red}{(KW: I included a footnote here, but we can also consider putting this information into the main text?)}
+The sum of the squares of the wavefunction overlap between the target weakly-bound molecular state and all the excited molecular intermediate states considered is only about 2\%, suggesting that there is significant matrix element between the target molecular state and the excited atomic continuum.
+(See SM)
 
@@
 Furthermore, a larger ratio also relaxes the intensity stability requirement, because this is also the ratio between the Raman Rabi coupling and the AC Stark shift of the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2, with both beams at equal power, to account for the Stark shift caused by both beams.}.
-%and relax the intensity stability requirement due to the AC Stark shift of the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.}
-%As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio.
+% and relax the intensity stability requirement due to the AC Stark shift of the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.}
+% As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio.
 The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate.
@@
 The ratio, $ \Omega_a/\Omega_m $ can be changed through the choice of initial and final states.
-%Because of the large atom and molecule wavefunction mismatch, choosing an initial atomic state that has more amplitude at smaller internuclear distance can increase the coupling $\Omega_a$.
+% Because of the large atom and molecule wavefunction mismatch, choosing an initial atomic state that has more amplitude at smaller internuclear distance can increase the coupling $\Omega_a$.
 \textcolor{blue}{(the two sentences have the same idea.)}
-%it can be made larger by increasing the coupling of the atomic state with the excited molecular state. 
+% it can be made larger by increasing the coupling of the atomic state with the excited molecular state.
 Due to the small size of the intermediate state wavefunction, the coupling $\Omega_a$ is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential.
 To increase the amplitude within the molecular potential, one can increase the external confinement of atom pairs.
-Using a harmonic oscillator approximation, the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/8} $, where $ \omega_{\text{trap}} $ is the trap frequency.
+Using a harmonic oscillator approximation, the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $, where $ \omega_{\text{trap}} $ is the trap frequency.
 Alternatively, one can choose an atomic pair state with a large scattering length (positive or negative).
@@
 %The increase in the coupling is proportional to (quote/cite Olive's equation?).
-For our system of Na and Cs atoms, we chose  a  spin state combination $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}\equiv \ket{F=2,m_F=2}_{\text{Na}}\ket{F=3,m_F=3}_{\text{Cs}} $that has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0$~\cite{Hood2019}.
-We note that other stable spin combinations give smaller scattering lengths ($<~50~a_0$) \textcolor{blue}{(define arbitrarily).}
-%We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\text{Cs}}} = \ket{F=4,m_F=4}_{\text{Cs}}, \ket{\downarrow_{\text{Cs}}} = \ket{F=3,m_F=3}_{\text{Cs}}, \ket{\uparrow_{\text{Na}}} = \ket{F=2,m_F=2}_{\text{Na}}, $ and $ \ket{\downarrow_{\text{Na}}} = \ket{F=1,m_F=1}_{\text{Na}}$.
+For our system of Na and Cs atoms, we choose  a spin state combination $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}\equiv \ket{F=2,m_F=2}_{\text{Na}}\ket{F=3,m_F=3}_{\text{Cs}} $that has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0$~\cite{Hood2019}.
+We note that other stable spin combinations give smaller scattering lengths ($<~50~a_0$).
+% We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\text{Cs}}} = \ket{F=4,m_F=4}_{\text{Cs}}, \ket{\downarrow_{\text{Cs}}} = \ket{F=3,m_F=3}_{\text{Cs}}, \ket{\uparrow_{\text{Na}}} = \ket{F=2,m_F=2}_{\text{Na}}, $ and $ \ket{\downarrow_{\text{Na}}} = \ket{F=1,m_F=1}_{\text{Na}}$.
 Among the stable spin combinations, $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}} $ combination has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
@@
 % Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
-%Thus, we choose the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination.
+% Thus, we choose the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination.
 \textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
@@
 
-%After preparing the Na and Cs atoms in the same tweezer in a single quantum state, 
+% After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
 Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7 kHz$ interaction shift~\cite{Hood2019}.
@@
 %% Transfer scheme
-%After the atoms are prepared in the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $ hyperfine combination, we then perform the Raman transfer. 
-To perform Raman transfer of an atom pair to the targeted weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}A).
+% After the atoms are prepared in the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $ hyperfine combination, we then perform the Raman transfer.
+To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}A).
 The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time.
@@
 The pulse sequence is shown in Fig.~\ref{f-raman}B. %Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal.
-%In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse.
+% In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse.
 The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time.
@@
 Both frequencies are kept on for a specified duration before the process is reversed and the tweezer returns to a single frequency.
-%In addition to reducing the number of laser beams during the Raman transition, 
-Furthermore, we use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to filter  the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
-We observed a reduction of the scattering rate by at least  a factor of $2$ \textcolor{blue}{(can we be more definite?)}
-(for a particular single photon detuning) due to the (xx dB?) suppression   of the broadband amplified spontaneous emission (ASE) from the laser that   couples to other excited states.
+% In addition to reducing the number of laser beams during the Raman transition,
+Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50 ~\mathrm{GHz}$ to filter  the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
+We observed a reduction of the scattering rate by a factor of $2$ due to suppression of the broadband amplified spontaneous emission (ASE) from the laser that couples to other excited states.
 
-%found the spectral purity of the laser for Raman beams to be critical for achieving a higher transfer efficiency. 
-%The tweezer/Raman beams are generated by a fiber amplifier seeded with a $1037 \mathrm{nm}$ external cavity diode laser. 
-%by amplifying a $1037 \mathrm{nm}$ external cavity diode laser (ECDL) with a fiber amplifier,
-%The diode laser produces the desired frequency on top of a broad band amplified spontaneous emission (ASE).
+% found the spectral purity of the laser for Raman beams to be critical for achieving a higher transfer efficiency.
+% The tweezer/Raman beams are generated by a fiber amplifier seeded with a $1037 \mathrm{nm}$ external cavity diode laser.
+% by amplifying a $1037 \mathrm{nm}$ external cavity diode laser (ECDL) with a fiber amplifier,
+% The diode laser produces the desired frequency on top of a broad band amplified spontaneous emission (ASE).
 We use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the laser spectrum and found it reduces the scattering rate by at least a factor of $2$
-%for a particular single photon detuning.
+% for a particular single photon detuning.
 
-%in addition to the desired frequency. This increases the scattering rate due to coupling to other excited states.
+% in addition to the desired frequency. This increases the scattering rate due to coupling to other excited states.
 
@@
 
-Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) \mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 mW$ tweezer at $288560 GHz$ which corresponds to a $145 GHz$ single photon detuning.
-(We can maybe add information about the prediction here?)
+Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$ which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning.
+%(We can maybe add information about the prediction here?)
 %% Prediction
@@
 \todo{more, mention/cite Jeremy}
-%The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state. 
-When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence.
+% The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
+% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence.
 % directly detected by our imaging step.
+The molecular state is dark to the imaging step, so successful transfer of the atoms to the molecular state will be detected as loss of atoms in the post experiment image when compared to the initial image.
 We observed the narrowest linewidth of $7.56(82) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.12 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.907(98)$.
-This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent.
-In order to verify the coherence of the transfer directly, we fix the Raman frequency on resonance and scan the pulse time.
+This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is evidence of a coherent transfer.
+In order to verify the coherence of the transfer directly, we fix the two photon detuning on resonance and scan the pulse time.
 Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states.
@@
 
-In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state (Fig.~\ref{f-lifetime}A).
-We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B).
-The fit shows that we have a Raman Rabi frequency of $2\pi\times3.282(42) \mathrm{kHz}$.
-The molecule we form has a lifetime of $0.204(13) \mathrm{ms}$ which is the main limitation on the fidelity of the transfer.
-The molecule lifetime can be verified (or measured) directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C).
+In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the molecular state (Fig.~\ref{f-lifetime}A).
+We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B) without turning on the second frequency.
+The fit shows that we have a Raman Rabi frequency of $2\pi\times3.282(42) ~\mathrm{kHz}$.
+The molecule we form has a lifetime of $0.204(13) ~\mathrm{ms}$ which is the main limitation on the fidelity of the transfer.
+The molecule lifetime can be measured directly by preparing the molecule with a $\pi $ pulse and then using a second $\pi $ pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C).
 The result shows a molecular lifetime consistent with our fitting of the decaying Rabi oscillation.
 
-The ratio of molecule scattering rate to the Rabi frequency is larger than the theory prediction
-by more than a factor of $10$.
-Based on the calculation above, if this comes from the coupling to the $v'=0$ excited state,
-it can be either due to a high ratio of $\Omega_m / \Omega_a$ or a large $\Gamma_e$.
-Additionally, coupling to other excited states can also add an offset to both the Raman
-Rabi frequency and the scattering rate which can affect the scattering rate
-to Rabi frequency ratio.
+The ratio of the molecule scattering rate to the Rabi frequency is larger than the theory prediction by more than a factor of $10$.
+Based on the discussion above, if this discrepancy arises from the $v'=0$ excited state, it can be either due to a high ratio of $\Omega_m / \Omega_a$ or a large $\Gamma_e$.
+Additionally, coupling to other excited states can also add an offset to both the Raman Rabi frequency and the scattering rate which can affect the scattering rate to Rabi frequency ratio.
 
-In order to verify whether any one of these known sources are the origin of the discrepancy,
-we measured the Raman resonance as a function of the tweezer power and single photon frequency.
-The important results from the fits are the 2 photon resonance frequency (light shift),
-Raman Rabi frequency, atomic lifetime and molecular lifetime.
-Each of these quantities provide us with information about a different combination
-of physical processes and the detuning dependency of them allows us
-to distinguish the contribution from the $v'=0$ excited states and other states.
+In order to verify whether any one of these known sources are the origin of the discrepancy, we measured the Raman resonance as a function of the tweezer power and single photon frequency.
+These dependencies allow us to experimentally determine the matrix elements, $ \Omega_a $, $\Omega_m $ and how much of the scattering, Stark shift, or Raman Rabi frequency comes from the $ v' = 0$ intermediate state.
 
-First we look at the change in resonance frequency.
-As a function of the tweezer power, we observe a linear dependency on the resonance frequency
+% From these fits, we extract the 2 photon resonance frequency, Raman Rabi frequency, atomic lifetime and molecular lifetime.
+%Each of these quantities provide us with information about a different combination of physical processes and the detuning dependency of them allows us to distinguish the contribution from the $v'=0$ excited states and other states.
+
+First we look at the change in resonance frequency. As a function of the tweezer power, we observe the expected linear dependency on the resonance frequency
 caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
-When we vary the tweezer frequency around the $v'=0$ excited state,
-we can further observe a $1/\delta$ component and a constant component
-in the experimentally explored region.
+When we vary the tweezer frequency around the $v'=0$ intermediate state, we can further observe a $1/\Delta$ component and a constant background in the experimentally explored region.
 The background is caused by coupling to other excited states that are further away in energy.
-The $1/\Delta$ component, however, is predominantly due to the coupling between
-the molecular state and the $v'=0$ excited state.
-From this measurement, we can calculate a matrix element between the molecular state and
-the excited state, $\Omega_m$, of $2\pi\times36.162(20) \mathrm{MHz}/\sqrt{\mathrm{mW}}$
-or $2\pi\times140.056(78) \mathrm{MHz}$ for the $15 \mathrm{mW}$ tweezer power used above.
+The $1/\Delta$ component, however, is due to the coupling between the molecular state and the $v'=0$ intermediate state.
+From this measurement, we can calculate a  $\Omega_m$ of $2\pi\times36.162(20) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or $2\pi\times140.056(78) ~\mathrm{MHz}$ for the $15 ~\mathrm{mW}$ tweezer power used above.
 This number is consistent with the value of
@@
 
-In order to calculate the matrix element ratio, we now need to extract the matrix element between the atomic state and the excited molecular state, $ \Omega_a $.
+In order to calculate the matrix element ratio, we now need to extract the matrix element, $ \Omega_a $.
 We do this by measuring the dependencies of the Raman Rabi frequency, which depends on both $\Omega_m$ and $\Omega_a$.
-The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change
-in the atomic wavefunction caused by the change in confinement (Fig.~\ref{f-det}B).
-The atomic matrix element, $\Omega_a$,
-is proportional to the the short range atomic wavefunction amplitude,
-which scales as $P^{0.375}$ due to increasing density for weakly interacting particles.
+The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change in the atomic wavefunction caused by tighter confinement at higher power (Fig.~\ref{f-det}B).
+Thus, as discussed before, for weakly interacting particles, $\Omega_a$ scales as $ \omega_{\text{trap}}^{3/4}$ or $P^{0.375}$.
 However, due to the strong interaction between the two atoms, this approximation breaks down.
-Instead, coupled-channel calculation shows that the scaling is very well approximated by $P^{0.29}$
-within the range of confinement in our experiment.
-Combined with the intensity factor, the Raman Rabi frequency should scale with $P^{1.29}$,
-which agrees with our experimental result.
-Similar to the light shift, there is also an offset and
-a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$.
-The $v'=0$ component of the Raman Rabi frequency is
-$2\pi\times161.8(22) \mathrm{Hz\cdot mW^{-1.29}}$,
-or $2\pi \times 5.324(73)\mathrm{kHz}$ at $15 \mathrm{mW}$ tweezer power.
+Instead, coupled-channel calculation shows that the scaling is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
+Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$, which agrees with our experimental result.
+Similar to the light shift, there is also a constant background component and a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$.
+The $v'=0$ component of the Raman Rabi frequency is $2\pi\times161.8(22) ~\mathrm{Hz\cdot mW^{-1.29}}$, or $2\pi \times 5.324(73)~\mathrm{kHz}$ at $15 ~\mathrm{mW}$ tweezer power.
 Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
 $2\pi \times 11.53(16)\mathrm{MHz}$.
-This gives a Rabi frequency, and therefore matrix element, ratio of $12.14(16)$,
-which is in fact better than the theory prediction of $23.7$
-and should not cause the scattering from the $v'=0$ state to be higher than expected.
+This gives a Rabi frequency, and therefore matrix element, ratio of $12.14(16)$, which is in fact better than the theory prediction of $23.7$ and should not cause the ratio of the Raman Rabi frequency to scattering rate from the $v'=0$ state to be higher than expected.
+Furthermore, based on measurements of the excited state using photoassociation (PA) spectroscopy, the natural linewidth of the $v'=0$ excited state is no larger than $20 \mathrm{MHz}$.
+This suggests that the excited state linewidth should not cause a stronger than expected scattering from $v'=0$ state either.
 
-Unfortunately, the offset in the Raman Rabi frequency fit cancels
-the Rabi frequency for red detuning Raman transition and reduces it by about $30\%$
-at the current detuning. However, this difference is not enough to explain
-the difference we observed in the experiment.
-The same offset will increase the Rabi frequency for blue detuning
-but we have observed additional excited states at slightly higher frequencies
-which prevent the blue side of the transition to be usable for the Raman transition.
+With the $ v' = 0 $ state ruled out as the source of discrepancy between experiment and theory, we now consider the background effects from other states with larger single photon detuning.
+Unfortunately, the background in the Raman Rabi frequency fit cancels the Rabi frequency for a single photon detuning that is red of the $ v' = 0 $ and reduces it by about $30\%$ at the current detuning.
+However, this difference is not enough to explain the over factor of 10 discrepancy present in the experiment.
+The same offset will increase the Rabi frequency for blue detuning, but we have observed additional excited states at slightly higher frequencies which prevent the blue side of the transition to be usable for the Raman transition.
 
-Based on our previous measurements of the excited state using photoassociation (PA) spectroscopy,
-the natural linewidth of the $v'=0$ excited state is no larger than $20 \mathrm{MHz}$.
-This suggests that the excited state linewidth should not cause a stronger than expected
-scattering from $v'=0$ state either.
+These results suggest that the decoherence or loss we observed during the the Raman transition comes from either a higher than expected background scattering rate or a different intrinsic or technical source that we have not accounted for.
+We have observed a significant decrease in the coherence time without the ASE filter, suggesting the spectral purity of the laser is a significant source of scattering.
+Another source of decoherence could result from fluctuations in the power ratio between the two beams resulting in a fluctuation in the resonance position.
+In the experiment, we only stabilize the total power of the tweezer.
 
-These results suggests that the decoherence or loss we observed during the the Raman transition
-comes from either a higher than expected background scattering rate
-or a different intrinsic or technical source that we have not accounted for.
-As mentioned above, we have observed significant improvment in the coherence time
-by filtering out most of the ASE from the laser suggesting the spectral purity of
-the laser is a significant source of scattering.
-Although we have good control on the total power of the tweezer and Raman beam to stabilize
-the light shift on the transition, the power ratio of the two frequencies within the beam
-is not yet controlled as tightly and may result in a residual resonance fluctuation.
-Finally, Fig.~\ref{f-det}C shows the two-body scattering rate for the atomic initial state.
-The scattering rate scales as $P_{tweezer}^{2.58}$ which is inconsistent with
-the prediction based on single photon scattering process.
-Although the absolute scattering rate is much lower than the total decoherence rate
-and we have not been able to observe a dependency on the detuning in order to
-verify if the scattering process is related to the $v'=0$ state, the power scaling
-strongly suggests the existence of a unknown two photon scattering process.
+Lastly, to confirm that the excess scattering does not come from the atomic state, we measure the two-body scattering rate without turning on the second frequency (Fig.~\ref{f-det}C).
+The scattering rate scales as $P_{tweezer}^{2.58}$ which is inconsistent with a single photon scattering process.
+We have not been able to observe a dependency on the detuning in order to verify if the scattering process is related to the $v'=0$ state, but the power scaling strongly suggests the existence of a unknown two photon scattering process.
+Nevertheless, the absolute scattering rate is much lower than the total scattering rate and is not the limiting factor in our experiment.
+% Although we have good control on the total power of the tweezer and Raman beam to stabilizethe light shift on the transition, the power ratio of the two frequencies within the beam is not yet controlled as tightly and may result in a residual resonance fluctuation.
 
@@
 In conclusion, we have formed a weakly bound NaCs molecule in an optical tweezer via an optical Raman transfer.
-A theoretical investigation including all excited states of $ c^3\Sigma^+(\Omega = 1)$ and coupled channel ground state wavefunctions indicated better transfer efficiency using a deeply bound intermediate state and the $ \ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}} } $ hyperfine state combination.
+A theoretical investigation including all excited states of $ c^3\Sigma^+(\Omega = 1)$, the excited atomic continuum and coupled channel ground state wavefunctions indicated better transfer efficiency using a deeply bound intermediate state and the $ \ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}} } $ hyperfine state combination.
 Using these theoretical insights, we located the weakly bound state and coherently associated the atoms into the weakly bound molecule.
@@
 There may also be a better choice of single photon detuning to increase the Raman Rabi frequency, since our location results in about 30\% cancellation of the Raman Rabi frequency due to an offset of unknown origin.
-(Do we want to mention also technical improvements as another way to potentially improve our signal?
-Though I guess that was mentioned directly in the paragraph above...) Nevertheless, our technique, with the right choice of parameters, can be used to form a more diverse set of molecular species, since it does not rely on a magnetic Feshbach resonance or a narrow excited state.
-The formation of a weakly bound molecule is also a key step in forming rovibrational ground state molecules.
+Nevertheless, our technique, with the right choice of parameters, can be used to form a more diverse set of molecular species, since it does not rely on a magnetic Feshbach resonance, bound states at the MHz-level or a narrow excited state.
+The formation of a weakly bound molecule is a key step in forming rovibrational ground state molecules.
 Combined with real time rearrangement \cite{Barredo2016, Endres2016}, defect free arrays of highly controlled molecules can be formed in arbitrary geometries.

### 2020-10-20 paper.tex
White space, remove duplicated reference entry, regenerate PDF
Clean up, breaking up long lines, remove molecule linetime from introduction

@@
   The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8~\mathrm{G}$
-  and lifetime up to $1 \mathrm{ms}$ \textcolor{blue}{(1~ms seems long here)} with more than $60\%$ of the molecule created in the
-  motional ground state.
+  with more than $60\%$ of the molecule created in the motional ground state.
   This technique is general without relying on narrow excited state lines or Feshbach resonances and could allow a wider range of molecular species to be assembled atom-by-atom.
@@
 Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$ which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning.
-%(We can maybe add information about the prediction here?)
+% (We can maybe add information about the prediction here?)
 %% Prediction
@@
 
-The ratio of the molecule scattering rate to the Rabi frequency is larger than the theory prediction by more than a factor of $10$.
-Based on the discussion above, if this discrepancy arises from the $v'=0$ excited state, it can be either due to a high ratio of $\Omega_m / \Omega_a$ or a large $\Gamma_e$.
-Additionally, coupling to other excited states can also add an offset to both the Raman Rabi frequency and the scattering rate which can affect the scattering rate to Rabi frequency ratio.
+The ratio of the molecule scattering rate to the Rabi frequency is larger than
+the theory prediction by more than a factor of $10$.
+Based on the discussion above, if this discrepancy arises from the $v'=0$ excited state,
+it can be either due to a high ratio of $\Omega_m / \Omega_a$ or a large $\Gamma_e$.
+Additionally, coupling to other excited states can also add an offset to
+both the Raman Rabi frequency and the scattering rate
+which can affect the scattering rate to Rabi frequency ratio.
 
-In order to verify whether any one of these known sources are the origin of the discrepancy, we measured the Raman resonance as a function of the tweezer power and single photon frequency.
-These dependencies allow us to experimentally determine the matrix elements, $ \Omega_a $, $\Omega_m $ and how much of the scattering, Stark shift, or Raman Rabi frequency comes from the $ v' = 0$ intermediate state.
+In order to verify whether any one of these known sources are the origin of the discrepancy,
+we measured the Raman resonance as a function of the tweezer power and single photon frequency.
+These dependencies allow us to experimentally determine the matrix elements,
+$ \Omega_a $, $\Omega_m $ and how much of the scattering, Stark shift,
+or Raman Rabi frequency comes from the $ v' = 0$ intermediate state.
 
-% From these fits, we extract the 2 photon resonance frequency, Raman Rabi frequency, atomic lifetime and molecular lifetime.
-%Each of these quantities provide us with information about a different combination of physical processes and the detuning dependency of them allows us to distinguish the contribution from the $v'=0$ excited states and other states.
-
-First we look at the change in resonance frequency. As a function of the tweezer power, we observe the expected linear dependency on the resonance frequency
+First we look at the change in resonance frequency.
+As a function of the tweezer power,
+we observe the expected linear dependency on the resonance frequency
 caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
-When we vary the tweezer frequency around the $v'=0$ intermediate state, we can further observe a $1/\Delta$ component and a constant background in the experimentally explored region.
+When we vary the tweezer frequency around the $v'=0$ intermediate state,
+we can further observe a $1/\Delta$ component
+and a constant background in the experimentally explored region.
 The background is caused by coupling to other excited states that are further away in energy.
-The $1/\Delta$ component, however, is due to the coupling between the molecular state and the $v'=0$ intermediate state.
-From this measurement, we can calculate a  $\Omega_m$ of $2\pi\times36.162(20) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or $2\pi\times140.056(78) ~\mathrm{MHz}$ for the $15 ~\mathrm{mW}$ tweezer power used above.
+The $1/\Delta$ component, however, is due to the coupling between the molecular state
+and the $v'=0$ intermediate state.
+From this measurement, we can calculate a $\Omega_m$ of
+$2\pi\times36.162(20) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or
+$2\pi\times140.056(78) ~\mathrm{MHz}$ for the $15 ~\mathrm{mW}$ tweezer power used above.
 This number is consistent with the value of
 $2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
-\todo{make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$,
-  also $\Omega$ vs $\Omega'$ for the single leg vs cross coupling number.}
 
@@
 
-In order to calculate the matrix element ratio, we now need to extract the matrix element, $ \Omega_a $.
-We do this by measuring the dependencies of the Raman Rabi frequency, which depends on both $\Omega_m$ and $\Omega_a$.
-The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change in the atomic wavefunction caused by tighter confinement at higher power (Fig.~\ref{f-det}B).
-Thus, as discussed before, for weakly interacting particles, $\Omega_a$ scales as $ \omega_{\text{trap}}^{3/4}$ or $P^{0.375}$.
+In order to calculate the matrix element ratio,
+we now need to extract the matrix element, $ \Omega_a $.
+We do this by measuring the dependencies of the Raman Rabi frequency,
+which depends on both $\Omega_m$ and $\Omega_a$.
+The Raman Rabi frequency shows a non-linear dependency on the tweezer power
+due to the change in the atomic wavefunction caused by
+tighter confinement at higher power (Fig.~\ref{f-det}B).
+Thus, as discussed before, for weakly interacting particles,
+$\Omega_a$ scales as $ \omega_{\text{trap}}^{3/4}$ or $P^{0.375}$.
 However, due to the strong interaction between the two atoms, this approximation breaks down.
-Instead, coupled-channel calculation shows that the scaling is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
-Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$, which agrees with our experimental result.
-Similar to the light shift, there is also a constant background component and a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$.
-The $v'=0$ component of the Raman Rabi frequency is $2\pi\times161.8(22) ~\mathrm{Hz\cdot mW^{-1.29}}$, or $2\pi \times 5.324(73)~\mathrm{kHz}$ at $15 ~\mathrm{mW}$ tweezer power.
+Instead, coupled-channel calculation shows that the scaling
+is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
+Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
+which agrees with our experimental result.
+Similar to the light shift, there is also a constant background component
+and a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$.
+The $v'=0$ component of the Raman Rabi frequency is
+$2\pi\times161.8(22) ~\mathrm{Hz\cdot mW^{-1.29}}$,
+or $2\pi \times 5.324(73)~\mathrm{kHz}$ at $15 ~\mathrm{mW}$ tweezer power.
 Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
 $2\pi \times 11.53(16)\mathrm{MHz}$.
-This gives a Rabi frequency, and therefore matrix element, ratio of $12.14(16)$, which is in fact better than the theory prediction of $23.7$ and should not cause the ratio of the Raman Rabi frequency to scattering rate from the $v'=0$ state to be higher than expected.
-Furthermore, based on measurements of the excited state using photoassociation (PA) spectroscopy, the natural linewidth of the $v'=0$ excited state is no larger than $20 \mathrm{MHz}$.
-This suggests that the excited state linewidth should not cause a stronger than expected scattering from $v'=0$ state either.
+This gives a Rabi frequency, and therefore matrix element, ratio of $12.14(16)$,
+which is in fact better than the theory prediction of $23.7$
+and should not cause the ratio of the Raman Rabi frequency to scattering rate
+from the $v'=0$ state to be higher than expected.
+Furthermore, based on measurements of the excited state using photoassociation (PA) spectroscopy,
+the natural linewidth of the $v'=0$ excited state is no larger than $20 \mathrm{MHz}$.
+This suggests that the excited state linewidth should not cause
+a stronger than expected scattering from $v'=0$ state either.
 
-With the $ v' = 0 $ state ruled out as the source of discrepancy between experiment and theory, we now consider the background effects from other states with larger single photon detuning.
-Unfortunately, the background in the Raman Rabi frequency fit cancels the Rabi frequency for a single photon detuning that is red of the $ v' = 0 $ and reduces it by about $30\%$ at the current detuning.
-However, this difference is not enough to explain the over factor of 10 discrepancy present in the experiment.
-The same offset will increase the Rabi frequency for blue detuning, but we have observed additional excited states at slightly higher frequencies which prevent the blue side of the transition to be usable for the Raman transition.
+With the $ v' = 0 $ state ruled out as the source of discrepancy between experiment and theory,
+we now consider the background effects from other states with larger single photon detuning.
+Unfortunately, the background in the Raman Rabi frequency fit cancels the Rabi frequency
+for a single photon detuning that is red of the $ v' = 0 $
+and reduces it by about $30\%$ at the current detuning.
+However, this difference is not enough to explain the over factor of $10$ discrepancy
+present in the experiment.
+The same offset will increase the Rabi frequency for blue detuning,
+but we have observed additional excited states at slightly higher frequencies
+which prevent the blue side of the transition to be usable for the Raman transition.
 
-These results suggest that the decoherence or loss we observed during the the Raman transition comes from either a higher than expected background scattering rate or a different intrinsic or technical source that we have not accounted for.
-We have observed a significant decrease in the coherence time without the ASE filter, suggesting the spectral purity of the laser is a significant source of scattering.
-Another source of decoherence could result from fluctuations in the power ratio between the two beams resulting in a fluctuation in the resonance position.
+These results suggest that the decoherence or loss we observed during the Raman transition
+comes from either a higher than expected background scattering rate
+or a different intrinsic or technical source that we have not accounted for.
+We have observed a significant decrease in the coherence time without the ASE filter,
+suggesting the spectral purity of the laser is a significant source of scattering.
+Another source of decoherence could result from fluctuations in the power ratio
+between the two beams resulting in a fluctuation in the resonance position.
 In the experiment, we only stabilize the total power of the tweezer.
 
-Lastly, to confirm that the excess scattering does not come from the atomic state, we measure the two-body scattering rate without turning on the second frequency (Fig.~\ref{f-det}C).
-The scattering rate scales as $P_{tweezer}^{2.58}$ which is inconsistent with a single photon scattering process.
-We have not been able to observe a dependency on the detuning in order to verify if the scattering process is related to the $v'=0$ state, but the power scaling strongly suggests the existence of a unknown two photon scattering process.
-Nevertheless, the absolute scattering rate is much lower than the total scattering rate and is not the limiting factor in our experiment.
-% Although we have good control on the total power of the tweezer and Raman beam to stabilizethe light shift on the transition, the power ratio of the two frequencies within the beam is not yet controlled as tightly and may result in a residual resonance fluctuation.
+Lastly, to confirm that the excess scattering does not come from the atomic state,
+we measure the two-body scattering rate
+without turning on the second frequency (Fig.~\ref{f-det}C).
+The scattering rate scales as $P_{tweezer}^{2.58}$ which is inconsistent
+with a single photon scattering process.
+We have not been able to observe a dependency on the detuning in order to verify
+if the scattering process is related to the $v'=0$ state,
+but the power scaling strongly suggests the existence of a unknown two photon scattering process.
+Nevertheless, the absolute scattering rate is much lower than the total scattering rate
+and is not the limiting factor in our experiment.
 
@@
 The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
-B field dependency $42.17(24) kHz/G$ which agrees with theory prediction of $... kHz/G$.
+B field dependency $42.17(24) kHz/G$.
 
@@
 \end{document}
+
+% Fig2 make vertical remove 2C
+% Bigger dots

### 2020-10-20 paper.tex
Mention molecular scattering scaling and mention longest lifetime measurement

@@
 
+\todo{change scattering to decoherence? since the fluctuation of light shift
+  does not lead to scattering but only decherence.}
 These results suggest that the decoherence or loss we observed during the Raman transition
@@
 In the experiment, we only stabilize the total power of the tweezer.
+
+In additional to calibrating the $\Omega_m$ and $\Omega_a$,
+the scattering rate of the molecule is also depend on the tweezer power and detuning.
+At $3\mathrm{mW}$ tweezer power, we have observed molecule lifetime as long as $1\mathrm{ms}$.
+However, since the technical noise that can lead to decoherence
+is not fully characterized in our experiment,
+we are unable to further identify the source of the discrepancy based on this dependency.
 

### 2020-10-20 plot_exp_data.jl
[imgs] update figure dot size

@@ -161,9 +161,9 @@ v00 = model_2d(0, 0, param_1)
 figure()
 errorbar([0.0], [ratio_00], [uncs_00], fmt="C0.", label="0.00 ms")
 plot([plot_freq_lo, plot_freq_hi] .- param_1[3], [v00, v00], "C0-")
-NaCsPlot.plot_survival_data(data_nacs_12′, fmt="C1.", label="0.12 ms")
+NaCsPlot.plot_survival_data(data_nacs_12′, fmt="C1o", label="0.12 ms")
 plot(plot_freq .- param_1[3], model_2d.(0.12, plot_freq, (param_1,)), "C1")
-NaCsPlot.plot_survival_data(data_nacs_25′, fmt="C2.", label="0.25 ms")
+NaCsPlot.plot_survival_data(data_nacs_25′, fmt="C2o", label="0.25 ms")
 plot(plot_freq .- param_1[3], model_2d.(0.25, plot_freq, (param_1,)), "C2")
 legend(fontsize="x-small", loc="lower right")
 grid()
@@ -172,11 +172,11 @@ ylabel("Two-body survival")
 NaCsPlot.maybe_save("$(prefix)_raman_det")
 
 figure()
-errorbar([0.0], [ratio_00 * scale_1], [uncs_00 * scale_1], fmt="C0.", label="0.00 ms")
+errorbar([0.0], [ratio_00 * scale_1], [uncs_00 * scale_1], fmt="C0o", label="0.00 ms")
 plot([plot_freq_lo, plot_freq_hi] .- param_1[3], [v00 * scale_1, v00 * scale_1], "C0-")
-NaCsPlot.plot_survival_data(data_nacs_12′, scale_1, fmt="C1.", label="0.12 ms")
+NaCsPlot.plot_survival_data(data_nacs_12′, scale_1, fmt="C1o", label="0.12 ms")
 plot(plot_freq .- param_1[3], model_2d.(0.12, plot_freq, (param_1,)) .* scale_1, "C1")
-NaCsPlot.plot_survival_data(data_nacs_25′, scale_1, fmt="C2.", label="0.25 ms")
+NaCsPlot.plot_survival_data(data_nacs_25′, scale_1, fmt="C2o", label="0.25 ms")
[…]

### 2020-10-20 paper.tex
Remove figure 2c (merged into 3a)

@@
 % In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
-\begin{figure*}[ht!]
-  \includegraphics[height=4.5cm]{fig2.pdf}
+\begin{figure}[ht!]
+  \includegraphics[width=0.45\textwidth]{fig2.pdf}
   \caption{
@@
     with maximum Raman Rabi frequency when the up and down leg powers are equal.
-    (C) Raman resonance from atomic state $Na(2,2)\ Cs(3,3)$ to the first molecular bound state
-    using a $0.12\mathrm{ms}$ pulse.
-    The full width half maximum (FWHM) of $7.56(82) \mathrm{kHz}$ of the resonance
-    is consistent with the FWHM for a coherent $0.12\mathrm{ms}$ $\pi$ pulse $6.7 \mathrm{kHz}$.
-    (D) Raman pulse time scan on resonance. A decaying Rabi oscillation can be observed
+    (C) Raman pulse time scan on resonance. A decaying Rabi oscillation can be observed
     proving the coherence of the Raman transfer process.
     \label{f-raman}}
-\end{figure*}
+\end{figure}
 
@@
 
-Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$ which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning.
+Guided by coupled channel calculations,
+we locate the Raman resonance for the atom to molecule transition at
+$770.59430(17) ~\mathrm{MHz}$ (Fig.~\ref{f-lifetime}A)
+with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$
+which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning.
 % (We can maybe add information about the prediction here?)
@@
 % directly detected by our imaging step.
-The molecular state is dark to the imaging step, so successful transfer of the atoms to the molecular state will be detected as loss of atoms in the post experiment image when compared to the initial image.
-We observed the narrowest linewidth of $7.56(82) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.12 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.907(98)$.
-This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is evidence of a coherent transfer.
-In order to verify the coherence of the transfer directly, we fix the two photon detuning on resonance and scan the pulse time.
-Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states.
-Fitting the data with a decaying Rabi oscillation suggests that $69\%$ of initial ground state atoms are transferred into the molecular state.
+The molecular state is dark to the imaging step,
+so successful transfer of the atoms to the molecular state will be detected as loss of atoms
+in the post experiment image when compared to the initial image.
+We observed a Fourier limited linewidth which is evidence of a coherent transfer.
+In order to verify the coherence of the transfer directly,
+we fix the two photon detuning on resonance and scan the pulse time.
+Fig.~\ref{f-raman}C shows the observed Rabi oscillation between the atomic and molecular states.
+Fitting the data with a decaying Rabi oscillation suggests that
+$69\%$ of initial ground state atoms are transferred into the molecular state.
 

### 2020-10-20 plot_exp_data.jl
Adjust figure sizes

@@ -266,7 +266,7 @@ xlabel("Raman time (ms)")
 ylabel("Two-body survival")
 NaCsPlot.maybe_save("$(prefix)_t")
 
-figure()
+figure(figsize=[7.2, 5.4])
 NaCsPlot.plot_survival_data(data_nacs_t, scale_2,
                             fmt="C0o", label="770.5704 MHz")
 plot(plot_time, model_2d.(plot_time, 570.4, (param_2,)) .* scale_2, "C0")

### 2020-10-20 paper.tex
Adjust figure sizes
Update figure 4

@@
 \begin{figure*}
-  \includegraphics[height=5cm]{fig1.pdf}
+  \includegraphics[width=\textwidth]{fig1.pdf}
   \caption{Optical creation of single molecule from single atoms in tweezer.
@@
 \begin{figure*}[t!]
-  \includegraphics[height=4.5cm]{fig3.pdf}
+  \includegraphics[width=\textwidth]{fig3.pdf}
   \caption{
@@
 \begin{figure*}
-  \includegraphics[height=4.5cm]{fig4.pdf}
+  \includegraphics[width=\textwidth]{fig4.pdf}
   \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
@@
 The $v'=0$ component of the Raman Rabi frequency is
-$2\pi\times161.8(22) ~\mathrm{Hz\cdot mW^{-1.29}}$,
-or $2\pi \times 5.324(73)~\mathrm{kHz}$ at $15 ~\mathrm{mW}$ tweezer power.
+$2\pi\times170.0(39) ~\mathrm{Hz\cdot mW^{-1.29}}$,
+or $2\pi \times 5.59(13)~\mathrm{kHz}$ at $15 ~\mathrm{mW}$ tweezer power.
 Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
-$2\pi \times 11.53(16)\mathrm{MHz}$.
-This gives a Rabi frequency, and therefore matrix element, ratio of $12.14(16)$,
+$2\pi \times 12.11(28)\mathrm{MHz}$.
+This gives a Rabi frequency, and therefore matrix element, ratio of $11.59(26)$,
 which is in fact better than the theory prediction of $23.7$
@@
 \end{document}
-
-% Fig2 make vertical remove 2C
-% Bigger dots

### 2020-10-20 plot_atomic_loss_scaling.jl

@@ -28,7 +28,7 @@ fit_gamma_a2 = fit_data(gen_power_model(2.58), rates[:, 1], rates[:, 2], rates[:
 const prefix = joinpath(@__DIR__, "imgs", "atomic_loss_scaling")
 
 figure()
-errorbar(rates[:, 1], rates[:, 2], rates[:, 3], fmt="C0.")
+errorbar(rates[:, 1], rates[:, 2], rates[:, 3], fmt="C0o")
 plot(fit_gamma_a2.plotx, fit_gamma_a2.ploty, "C0")
 xscale("log")
 yscale("log")

### 2020-10-20 plot_rabi_scaling.jl

@@ -121,7 +121,7 @@ end
 
 const model = gen_model(705)
 const data = gen_data(freqs)
-const fit1 = fit_data(model, data.x, data.y, data.unc, [0.1, 0.1], plotx=false)
+const fit1 = fit_data(model, data.x, data.y, [0.1, 0.1], plotx=false)
 @show fit1.uncs
 
 const prefix = joinpath(@__DIR__, "imgs", "rabi_scaling")
@@ -133,7 +133,7 @@ for i in 1:length(powers_plot)
     power = powers_plot[i]
     pd = get_plot_data_power(data, fit1, model, power)
     plot(pd.plotx .+ 288000, pd.ploty, "C$(i - 1)", label="$(power) mW")
-    errorbar(pd.x .+ 288000, pd.y, pd.unc, fmt="C$(i - 1).")
+    errorbar(pd.x .+ 288000, pd.y, pd.unc, fmt="C$(i - 1)o")
 end
 xticks([288500, 288530, 288560, 288590, 288620])
 # p: offset, strength

### 2020-10-20 plot_res_scaling.jl

@@ -170,7 +170,7 @@ for i in 1:length(powers_plot)
     power = powers_plot[i]
     plot1 = get_plot_data_power(data, fit1, model1, power)
     errorbar(plot1.x .+ 288000, (plot1.y .- fit1.param[1]) .* 1000,
-             plot1.unc .* 1000, fmt="C$(i - 1).")
+             plot1.unc .* 1000, fmt="C$(i - 1)o")
     plot(plot1.plotx .+ 288000, (plot1.ploty .- fit1.param[1]) .* 1000,
          "C$(i - 1)", label="$(power) mW")
 end

### 2020-10-20 plot_exp_data.jl
Fix figures

@@ -66,10 +66,10 @@ const data_pa_m = datas_nacs[4][1]
 
 const data_nacs_m = datas_nacs[2][3]
 
-const data_fit = [NaCsData.map_params((i, v) -> (1, 570.4, v, 2), data_nacs_00);
-                  NaCsData.map_params((i, v) -> (1, v, 0.12, 2), data_nacs_12);
-                  NaCsData.map_params((i, v) -> (1, v, 0.25, 2), data_nacs_25);
-                  NaCsData.map_params((i, v) -> (1, 570.4, v, 1), data_nacs_t);
+const data_fit = [NaCsData.map_params((i, v) -> (1, 570.4, v, 1), data_nacs_00);
+                  NaCsData.map_params((i, v) -> (1, v, 0.12, 1), data_nacs_12);
+                  NaCsData.map_params((i, v) -> (1, v, 0.25, 1), data_nacs_25);
+                  NaCsData.map_params((i, v) -> (1, 570.4, v, 2), data_nacs_t);
                   NaCsData.map_params((i, v) -> (2, v, 0.0, 3), data_pa_na);
                   NaCsData.map_params((i, v) -> (3, v, 0.0, 4), data_pa_cs);
                   NaCsData.map_params((i, v) -> (4, v, 0.0, 5), data_pa_a);

### 2020-10-20 paper.tex

@@
 The only exceptions are Sr$_2$ where narrow linewidth excited states are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb where weakly bound molecules of a binding energy of a couple MHz exists~\cite{He331}.
-These requirements greatly limit the generality of previous association techniques.
+These requirements  limit the generality of previous association techniques.
 % The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques.
@@
 The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.
-Our scheme is based on a choice of vibrational state of the electronic excited state $c^3\Sigma^+(\Omega = 1)$ that has the theoretical best raman Rabi frequency to photon scattering ratio.
+Our scheme is based on a choice of vibrational state of the electronic excited state $c^3\Sigma^+(\Omega = 1)$ that has the theoretical best Raman Rabi frequency to photon scattering ratio.
 To further increase this ratio and reduce technical requirements such as intensity stability, we choose an initial and final state where the matrix elements with the excited state are as balanced as possible.
@@
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
-The transfer Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate that is a sum of all coupling sources%,
+The transfer Raman Rabi Rate, $\Omega_R=\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_s$ that is a sum of all coupling sources%,
 % $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
@@
 Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally.
-Thus, the scattering is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power.
+Thus, the scattering is given by $ \Gamma_s=\Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power.
 Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.

### 2020-10-20 paper.tex
Update on Overleaf.

@@
 %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
-With the multiple excited vibrational states present in a molecular potential as intermediate states, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual intermediate states.
+
+Pioneering experiments used weakly-bound excited states as the intermediate state in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
+However, for a complete picture, the many excited vibrational states in a molecular potential as well as the excited atomic continuum need to be considered.
+The total scattering rate and Raman Rabi rate become a sum of the scattering rates and Raman Rabi rates over all possible intermediate states.
+With these considerations, using a weakly-bound excited state as the intermeidate state suffers from strong scattering of the nearby excited atomic continuum rendering it incoherent, resulting in molecule loss.
+This scattering is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can  be made smaller by detuning away from the dissociation threshold.
+%With the multiple excited vibrational states present in a molecular potential as intermediate states, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual intermediate states.
 Furthermore, for a more complete calculation, we also need to account for the effects of the excited atomic continuum, which is particularly important for the target molecular state.
@@
 (See SM)
-
-Pioneering experiments used weakly-bound excited states as the intermediate state in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
-However, such choice of state suffers from strong scattering of the nearby excited atomic continuum to render it incoherent, resulting in molecule loss.
-This scattering is  proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can  be made smaller by detuning away from the dissociation threshold.
 
@@
 To find the optimal intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011} and the continuum~\cite{Liu2017}.
-As shown in Fig.~\ref{f-theory}B (full result in SM), the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency.
+The excited atomic continuum is particularly important for the target molecular state.
+The sum of the squares of the wavefunction overlap between the target weakly-bound molecular state and all the excited molecular intermediate states considered is only about 2\%, suggesting that there is significant matrix element between the target molecular state and the excited atomic continuum (See SM).
+This calculation shows that the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency (Fig.~\ref{f-theory}B, full result in SM)
 As a result, we choose %a deeply bound molecular excited state

### 2020-10-21 paper.tex
Consistent use of Omega_R and Gamma_s

@@
     as intermediate state for the Raman transition.
-    The deeply bound excited state (upper half $v'=0$) has a smaller Raman Rabi frequency ($\Omega_{Raman}$)
+    The deeply bound excited state (upper half $v'=0$)
+    has a smaller Raman Rabi frequency ($\Omega_{R}$)
     compared to the weakly bound excited state (lower half $v'=63$) at a given detuning.
-    However, the scattering rate ($\Gamma_{scatter}$) is also much lower,
+    However, the scattering rate ($\Gamma_{s}$) is also much lower,
     which results in a larger Raman Rabi frequency to scattering rate ratio.

### 2020-10-21 plot_rabi_scaling.jl

@@ -143,7 +143,7 @@ xticks([288500, 288530, 288560, 288590, 288620])
 legend(loc="upper center", fontsize="small")
 grid()
 xlabel("Tweezer Frequency (GHz)")
-ylabel("\$\\Omega_{Raman} (2\\pi\\cdot \\mathrm{kHz})\$")
+ylabel("\$\\Omega_{R} (2\\pi\\cdot \\mathrm{kHz})\$")
 NaCsPlot.maybe_save("$(prefix)")
 
 NaCsPlot.maybe_show()

### 2020-10-21 plot_raman.jl

@@ -34,7 +34,7 @@ ax0.spines["right"].set_color("none")
 ax0.set_xticks([])
 ax0.set_yticks([])
 ax0.tick_params(labelcolor="w", top="off", bottom="off", left="off", right="off")
-ylabel("\$\\Omega_{Raman}\$ and \$\\Gamma_{scatter}\$ (\$2\\pi\\cdot \\mathrm{kHz})\$", fontsize="small")
+ylabel("\$\\Omega_{R}\$ and \$\\Gamma_{s}\$ (\$2\\pi\\cdot \\mathrm{kHz})\$", fontsize="small")
 ax0.get_yaxis().set_label_coords(-0.13, 0.5)
 ax0.tick_params(axis="x", length=0)
 ax0.tick_params(axis="y", length=0)
@@ -45,19 +45,19 @@ tax0.tick_params(labelcolor="w", top="off", bottom="off", left="off", right="off
 tax0.tick_params(axis="x", length=0)
 tax0.tick_params(axis="y", length=0)
 tax0.get_yaxis().set_label_coords(1.118, 0.5)
-ylabel("\$\\Omega_{Raman}/\\Gamma_{scatter}\$", fontsize="small", color="C2")
+ylabel("\$\\Omega_{R}/\\Gamma_{s}\$", fontsize="small", color="C2")
 
 ax1 = fig.add_subplot(211)
 plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ 2π / 1000), "C0",
-     label="\$\\Omega_{Raman}\$")
+     label="\$\\Omega_{R}\$")
 plot(data[:, 1] .- 288625.081, abs.(data[:, 4] ./ 2π / 1000), "C1",
-     label="\$\\Gamma_{scatter}\$")
+     label="\$\\Gamma_{s}\$")
 text(-32, 2.5, "v'=0", fontsize="small")
 ylim([0, 30])
 grid()
 tax1 = ax1.twinx()
 tax1.plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ data[:, 4]), "C2",
-          label="\$\\frac{\\Omega_{Raman}}{\\Gamma_{scatter}}\$")
+          label="\$\\frac{\\Omega_{R}}{\\Gamma_{s}}\$")
 xlim([-35, 35])
 ylim([0, 60])
 tax1.tick_params(axis="y", labelcolor="C2")
[…]

### 2020-10-23 paper.tex
Mention Omega_R in fig 4 caption
Vertical apparatus plot
Update on Overleaf.

@@
 
-Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018, PhysRevLett.119.153001, hudson2011}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111}.
-While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016, Mitra1366}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the association of ultracold atoms.
+Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018, PhysRevLett.119.153001, hudson2011}, quantum simulations~\cite{Yao2018, Wall2015, Sundar2018, wall2015realizing}, quantum information processing~\cite{DeMille2002, Ni2018, Hudson2018, Lin2019}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111,Segev2019}.
+While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016,Anderegg2018, Mitra1366, PhysRevX.10.021049, PhysRevLett.121.013202, PhysRevLett.120.123201}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020,He331}  have been achieved through the association of ultracold atoms.
 % (any place to cite  molecular ion work?)
@@
 \begin{figure}[ht!]
-  \includegraphics[width=0.45\textwidth]{fig2.pdf}
+  \includegraphics[width=0.48\textwidth]{fig2.pdf}
   \caption{
@@
     perpendicular to the real magnetic field.
-    (B) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\Delta$ with an offset.
+    (B) Raman Rabi frequency ($\Omega_R$) scales as $P_{tweezer}^{1.29}$
+    and follows $1/\Delta$ with an offset.
     From these results we can confirm the theory prediction of

### 2020-10-23 plot_exp_data.jl
Inset for Fig 2C

@@ -181,8 +181,25 @@ plot(plot_freq .- param_1[3], model_2d.(0.25, plot_freq, (param_1,)) .* scale_1,
 legend(fontsize="x-small", loc="lower right")
 grid()
 xlabel("Detuning from resonance (kHz)")
-ylabel("% Atomic Ground State")
+ylabel("Fraction of Atomic Ground State")
 NaCsPlot.maybe_save("$(prefix)_norm_raman_det")
+
+figure(figsize=[3.6, 3.0])
+bg = matplotlib.patches.Rectangle((-13, 0.08), 24, 0.98, facecolor="white", alpha=0.9)
+gca().add_patch(bg)
+NaCsPlot.plot_survival_data(data_nacs_12′, scale_1, fmt="C1o", label="0.12 ms")
+plot(plot_freq .- param_1[3], model_2d.(0.12, plot_freq, (param_1,)) .* scale_1, "C1")
+NaCsPlot.plot_survival_data(data_nacs_25′, scale_1, fmt="C2o", label="0.25 ms")
+plot(plot_freq .- param_1[3], model_2d.(0.25, plot_freq, (param_1,)) .* scale_1, "C2")
+xticks([-10, 0, 10])
+yticks([0.2, 0.6, 1.0])
+xlim([-13, 11])
+ylim([0.08, 1.06])
+# legend(fontsize="x-small", loc="lower right")
+grid()
+# xlabel("Detuning from resonance (kHz)")
+# ylabel("Fraction of Atomic Ground State")
+NaCsPlot.maybe_save("$(prefix)_norm_raman_det_inset")
 
 function model_lorentzian(x, p)
     p[1] .- p[2] ./ (1 .+ ((x .- p[3]) ./ (p[4] / 2)).^2)
@@ -230,7 +247,7 @@ function plot_lorentz_norm()
          color="C0", fontsize="small")
     grid()
     xlabel("Detuning from resonance (kHz)")
-    ylabel("% Atomic Ground State")
+    ylabel("Fraction of Atomic Ground State")
 end
 
 figure()
@@ -257,7 +274,7 @@ xlim([0, 0.8])
 ylim([0, ylim()[2]])
 legend(fontsize="x-small", loc="upper right")
 annotate("Atom", (0.01, 0.27), xytext=(0.13, 0.26), arrowprops=Dict(:color=>"C3"), color="C3")
-annotate("Molecule", (0.155, 0.030),
[…]

### 2020-10-23 paper.tex
Inset for Fig 2C
Update plot using new molecular lifetime measurement

@@
     with maximum Raman Rabi frequency when the up and down leg powers are equal.
-    (C) Raman pulse time scan on resonance. A decaying Rabi oscillation can be observed
-    proving the coherence of the Raman transfer process.
+    (C) Raman pulse time scan on resonance.
+    A decaying Rabi oscillation can be observed proving the coherence of
+    the Raman transfer process.
     \label{f-raman}}
@@
     Molecule survival is detected by dissociating back to atoms using a second Raman transition.
-    The lifetime is consistent with the $0.204(13) \mathrm{ms}$
+    The lifetime is consistent with the $0.1990(90) \mathrm{ms}$
     measured from the Raman transition data.
@@
 we locate the Raman resonance for the atom to molecule transition at
-$770.59430(17) ~\mathrm{MHz}$ (Fig.~\ref{f-lifetime}A)
+$770.571504(85) ~\mathrm{MHz}$ (Fig.~\ref{f-lifetime}A)
 with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$
@@
 The fit shows that we have a Raman Rabi frequency of $2\pi\times3.282(42) ~\mathrm{kHz}$.
-The molecule we form has a lifetime of $0.204(13) ~\mathrm{ms}$ which is the main limitation on the fidelity of the transfer.
+The molecule we form has a lifetime of $0.1990(90) ~\mathrm{ms}$ which is the main limitation on the fidelity of the transfer.
 The molecule lifetime can be measured directly by preparing the molecule with a $\pi $ pulse and then using a second $\pi $ pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C).
@@
 \end{document}
+
+% Shift figure 4 x axis
+% Try to move 3C forward
+% Inset in 4AB
+% Inset in 2C (3A) (or as a separate figure)
+% Maybe remove 3A (move into supplemental material)
+% Arrow head for molecule overlaps the datapoint
+% 4C as inset to 2B

### 2020-10-23 plot_exp_data.jl

@@ -15,7 +15,7 @@ using DataStructures
 using LsqFit
 
 const inames = ["nacs_202010/data/data_20201001_203322.mat",
-                "nacs_202010/data/data_20201002_203848.mat",
+                "nacs_202010/data/data_20201006_190214.mat",
                 "nacs_202010/data/data_20201002_085901.mat",
                 "nacs_202010/data/data_20201003_102015.mat"]
 const datas = [NaCsData.load_striped_mat(joinpath(@__DIR__, "../../experiments/", iname)) for iname in inames]
@@ -92,14 +92,14 @@ end
 
 function get_model_param(p, idx)
     f0, Ω, Γ1, Γ2, Γ_na, Γ_cs, p0r = p
-    p1 = p[9 + idx]
+    p1 = p[8 + idx]
     p0 = p1 * p0r
     return (p0, p1, f0, Ω, Γ1 + Γ_na + Γ_cs, Γ2)
 end
 
 function gen_pa_param(p, typ, pidx)
     f0, Ω, Γ1, Γ2, Γ_na, Γ_cs, p0r = p
-    p1 = p[9 + pidx]
+    p1 = p[8 + pidx]
     if typ == 1
         return (p1, Γ_na)
     elseif typ == 2
@@ -112,9 +112,9 @@ function gen_pa_param(p, typ, pidx)
 end
 
 function gen_ramsey_param(p, pidx)
-    f0, Ω, Γ1, Γ2, Γ_na, Γ_cs, p0r, p0rm, df = p
-    p1 = p[9 + pidx]
-    return (p1, Γ2, p0rm * p1, f0 - 570.4 + df)
+    f0, Ω, Γ1, Γ2, Γ_na, Γ_cs, p0r, p0rm = p
+    p1 = p[8 + pidx]
+    return (p1, Γ2, p0rm * p1, 0)
 end
 
 function model(xs, p)
@@ -135,9 +135,9 @@ function model(xs, p)
     return wrapper.(xs)
 end
 
-fit = fit_survival(model, data_fit, [570.4, 2π * 1.5, 0, 2π / 0.2, 0, 0, 0.1, 0.2, 0,
+fit = fit_survival(model, data_fit, [570.4, 2π * 1.5, 0, 2π / 0.2, 0, 0, 0.1, 0.2,
                                      0.3, 0.3, 0.8, 0.3, 0.3, 0.3, 0.15],
-                   plotx=false, lower=[-Inf; zeros(15)])
[…]

### 2020-10-23 plot_exp_data.jl
fig3 update

@@ -304,7 +304,7 @@ NaCsPlot.maybe_save("$(prefix)_norm_t")
 figure()
 NaCsPlot.plot_survival_data(data_pa_m, fmt="C0o")
 plot(plot_pa_time, model_exp(plot_pa_time, gen_pa_param(fit.param, 4, 6)), "C0-")
-text(7, 0.12, "\$\\tau_{atom}=$(1 / uncs_1[5])\\ \\mathrm{ms}\$", color="C0")
+# text(7, 0.12, "\$\\tau_{atom}=$(1 / uncs_1[5])\\ \\mathrm{ms}\$", color="C0")
 xlim([0, 22])
 ylim([0, 0.3])
 grid()
@@ -317,7 +317,7 @@ const param_pa = gen_pa_param(fit.param, 4, 6)
 figure()
 NaCsPlot.plot_survival_data(data_pa_m, fmt="C0o")
 plot(plot_pa_time, model_exp(plot_pa_time, param_pa), "C0-")
-text(7, 0.12, "\$\\tau_{atom}=$(1 / uncs_1[5])\\ \\mathrm{ms}\$", color="C0")
+# text(7, 0.12, "\$\\tau_{atom}=$(1 / uncs_1[5])\\ \\mathrm{ms}\$", color="C0")
 xlim([0, 22])
 ylim([0, 0.3])
 grid()
@@ -325,10 +325,10 @@ xlabel("Atom hold time (ms)")
 ylabel("Two-body survival")
 NaCsPlot.maybe_save("$(prefix)_a_t")
 
-figure()
+figure(figsize=[7.2, 5.4])
 NaCsPlot.plot_survival_data(data_pa_m, 1 / param_pa[1], fmt="C0o")
 plot(plot_pa_time, model_exp(plot_pa_time, param_pa) ./ param_pa[1], "C0-")
-text(7, 0.12 / param_pa[1], "\$\\tau_{atom}=$(1 / uncs_1[5])\\ \\mathrm{ms}\$", color="C0")
+# text(7, 0.12 / param_pa[1], "\$\\tau_{atom}=$(1 / uncs_1[5])\\ \\mathrm{ms}\$", color="C0")
 xlim([0, 22])
 ylim([0, 1.05])
 grid()
@@ -342,18 +342,18 @@ const scale_ramsey = 1 / (param_ramsey[1] + param_ramsey[3])
 figure()
[…]

### 2020-10-23 plot_atomic_loss_scaling.jl
fig3 inset

@@ -39,4 +39,22 @@ xlabel("Tweezer Power (mW)")
 ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$")
 NaCsPlot.maybe_save("$(prefix)")
 
+figure(figsize=[4.8, 3.6])
+bg = matplotlib.patches.Rectangle((2.48, 0.31), 14.52, 39.69, facecolor="white", alpha=0.9)
+gca().add_patch(bg)
+errorbar(rates[:, 1], rates[:, 2], rates[:, 3], fmt="C0o")
+plot(fit_gamma_a2.plotx, fit_gamma_a2.ploty, "C0")
+xscale("log")
+yscale("log")
+grid()
+xlim([2.48, 17])
+ylim([0.31, 40])
+xticks([3, 6, 15], ["3", "6", "15"])
+yticks([1, 3, 10, 30], ["1", "3", "10", "30"])
+minorticks_off()
+xlabel("Tweezer Power (mW)", fontsize=15)
+ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$", fontsize=15)
+tight_layout()
+NaCsPlot.maybe_save("$(prefix)_inset")
+
 NaCsPlot.maybe_show()

### 2020-10-23 plot_rabi_scaling.jl
Shift fig4 x axis and prepare for adding inset

@@ -132,15 +132,15 @@ const powers_plot = [15, 6, 3]
 for i in 1:length(powers_plot)
     power = powers_plot[i]
     pd = get_plot_data_power(data, fit1, model, power)
-    plot(pd.plotx .+ 288000, pd.ploty, "C$(i - 1)", label="$(power) mW")
-    errorbar(pd.x .+ 288000, pd.y, pd.unc, fmt="C$(i - 1)o")
+    plot(pd.plotx .- 703.6, pd.ploty, "C$(i - 1)")
+    errorbar(pd.x .- 703.6, pd.y, pd.unc, fmt="C$(i - 1)o", label="$(power) mW")
 end
-xticks([288500, 288530, 288560, 288590, 288620])
+# xticks([288500, 288530, 288560, 288590, 288620])
 # p: offset, strength
 # text(500, 5.0, ("\$\\left(a-\\dfrac{b}{f-705 GHz}\\right)\\cdot P^{1.29}\$"))
 # text(500, 2.8, ("\$a=$(fit1.uncs[1] * 1000)\$ Hz/mW\$^{1.29}\$\n" *
 #               "\$b=$(fit1.uncs[2])\$ kHz\$\\cdot\$GHz/mW\$^{1.29}\$"), fontsize="small")
-legend(loc="upper center", fontsize="small")
+legend(loc=(0.74, 0.31), fontsize="small", handlelength=0.6, handletextpad=0.3)
 grid()
 xlabel("Tweezer Frequency (GHz)")
 ylabel("\$\\Omega_{R} (2\\pi\\cdot \\mathrm{kHz})\$")

### 2020-10-23 plot_res_scaling.jl

@@ -169,12 +169,12 @@ const plot_freqs = get_plot_range(data.freqs)
 for i in 1:length(powers_plot)
     power = powers_plot[i]
     plot1 = get_plot_data_power(data, fit1, model1, power)
-    errorbar(plot1.x .+ 288000, (plot1.y .- fit1.param[1]) .* 1000,
-             plot1.unc .* 1000, fmt="C$(i - 1)o")
-    plot(plot1.plotx .+ 288000, (plot1.ploty .- fit1.param[1]) .* 1000,
-         "C$(i - 1)", label="$(power) mW")
+    errorbar(plot1.x .- 703.6, (plot1.y .- fit1.param[1]) .* 1000,
+             plot1.unc .* 1000, fmt="C$(i - 1)o", label="$(power) mW")
+    plot(plot1.plotx .- 703.6, (plot1.ploty .- fit1.param[1]) .* 1000,
+         "C$(i - 1)")
 end
-xticks([288500, 288530, 288560, 288590, 288620])
+# xticks([288500, 288530, 288560, 288590, 288620])
 # p: framan0, fpa0, offset, strength, bs...
 # text(560, 1700, ("\$f_{Raman0} + a\\cdot P\$\n" *
 #                  "  \$-\\dfrac{b}{f-f_{PA0}}\\cdot P\$"))
@@ -182,9 +182,9 @@ xticks([288500, 288530, 288560, 288590, 288620])
 #                 "\$f_{PA0}=$(fit1.uncs[2] + 288000)\$ GHz\n" *
 #                 "\$a=$(fit1.uncs[3] * 1000)\$ kHz/mW\n" *
 #                 "\$b=$(fit1.uncs[4])\$ MHz\$\\cdot\$GHz/mW"), fontsize="small")
-legend(loc="upper center", fontsize="small")
+legend(loc=(0.74, 0.38), fontsize="small", handlelength=0.6, handletextpad=0.3)
 grid()
-xlabel("Tweezer Frequency (GHz)")
+xlabel("Detuning (GHz)")
 ylabel("Light Shift (kHz)")
 NaCsPlot.maybe_save("$(prefix)_fs")
 

### 2020-10-23 paper.tex
Remote notes..
fig3 update
Legend for inset

@@
 
-\begin{figure*}[t!]
-  \includegraphics[width=\textwidth]{fig3.pdf}
+\begin{figure}[t!]
+  \includegraphics[width=0.48\textwidth]{fig3.pdf}
   \caption{
@@
     both the Raman Rabi frequency and the loss rates.
-    (B) \todo{inset?} Two-body atom lifetime in $15 \mathrm{mW}$ of trap depth caused by
-    off-resonance photoassociation.
+    (B) Two-body atom lifetime of $5.1(11) \mathrm{ms}$
+    in $15 \mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
     This is used to improve the fitting of the Raman transfer data.
+    Inset: Atomic scattering rate scales as $P_{tweezer}^{2.58}$,
+    this is consistent with a two photon scattering process.
+    We have not measured a clear dependency of the loss rate on the tweezer detuning.
     (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
@@
     \label{f-lifetime}}
-\end{figure*}
+\end{figure}
 
@@
     the atom-molecule matrix element ratio.
-    (C) Atomic scattering rate scales as $P_{tweezer}^{2.58}$,
-    this is consistent with a two photon scattering process.
-    We have not measured a clear dependency of the loss rate on the tweezer detuning.
     \label{f-det}}
@@
 we measure the two-body scattering rate
-without turning on the second frequency (Fig.~\ref{f-det}C).
+without turning on the second frequency (Fig.~\ref{f-lifetime}B inset).
 The scattering rate scales as $P_{tweezer}^{2.58}$ which is inconsistent
@@
 \end{document}
-
-% Shift figure 4 x axis
-% Try to move 3C forward
-% Inset in 4AB
-% Inset in 2C (3A) (or as a separate figure)
-% Maybe remove 3A (move into supplemental material)
-% Arrow head for molecule overlaps the datapoint
-% 4C as inset to 2B

### 2020-10-23 plot_rabi_scaling.jl
Fix x axis

@@ -142,7 +142,7 @@ end
 #               "\$b=$(fit1.uncs[2])\$ kHz\$\\cdot\$GHz/mW\$^{1.29}\$"), fontsize="small")
 legend(loc=(0.74, 0.31), fontsize="small", handlelength=0.6, handletextpad=0.3)
 grid()
-xlabel("Tweezer Frequency (GHz)")
+xlabel("Detuning (GHz)")
 ylabel("\$\\Omega_{R} (2\\pi\\cdot \\mathrm{kHz})\$")
 NaCsPlot.maybe_save("$(prefix)")
 

### 2020-10-23 plot_rabi_scaling.jl
Fig 4 inset

@@ -76,29 +76,29 @@ end
 #     return fit_data(model, data.x, data.y, data.unc, p0, plotx=false)
 # end
 
-# function get_plot_data_freq(data, fit, model, freq)
-#     local freq_id
-#     xs = Float64[]
-#     ys = Float64[]
-#     uncs = Float64[]
-#     for i in 1:length(data.x)
-#         x = data.x[i]
-#         x[1] == freq || continue
-#         if !@isdefined(freq_id)
-#             freq_id = x[3]
-#         else
-#             @assert(freq_id == x[3])
-#         end
-#         push!(xs, x[2])
-#         push!(ys, data.y[i])
-#         push!(uncs, data.unc[i])
-#     end
-#     function plot_func(x)
-#         return model((freq, x, freq_id), fit.param)
-#     end
-#     plotx = get_plot_range(xs)
-#     return (x=xs, y=ys, unc=uncs, plotx=plotx, ploty=plot_func.(plotx))
-# end
+function get_plot_data_freq(data, fit, model, freq)
+    local freq_id
+    xs = Float64[]
+    ys = Float64[]
+    uncs = Float64[]
+    for i in 1:length(data.x)
+        x = data.x[i]
+        x[1] == freq || continue
+        if !@isdefined(freq_id)
+            freq_id = x[3]
+        else
+            @assert(freq_id == x[3])
+        end
+        push!(xs, x[2])
+        push!(ys, data.y[i])
+        push!(uncs, data.unc[i])
+    end
+    function plot_func(x)
+        return model((freq, x, freq_id), fit.param)
+    end
+    plotx = get_plot_range(xs)
+    return (x=xs, y=ys, unc=uncs, plotx=plotx, ploty=plot_func.(plotx))
+end
 
 function get_plot_data_power(data, fit, model, power)
     xs = Float64[]
@@ -126,7 +126,7 @@ const fit1 = fit_data(model, data.x, data.y, [0.1, 0.1], plotx=false)
 
 const prefix = joinpath(@__DIR__, "imgs", "rabi_scaling")
 
-figure()
+figure(figsize=[7.2, 5.4])
[…]

### 2020-10-23 plot_res_scaling.jl

@@ -163,9 +163,9 @@ const nploty = ceil(Int, nfreq / nplotx)
 function plot_freq_func(model, fit, power, x)
     return model((x, power, 0), fit.param)
 end
-figure()
+
+figure(figsize=[7.2, 5.4])
 const powers_plot = [15, 6, 3]
-const plot_freqs = get_plot_range(data.freqs)
 for i in 1:length(powers_plot)
     power = powers_plot[i]
     plot1 = get_plot_data_power(data, fit1, model1, power)
@@ -182,10 +182,36 @@ end
 #                 "\$f_{PA0}=$(fit1.uncs[2] + 288000)\$ GHz\n" *
 #                 "\$a=$(fit1.uncs[3] * 1000)\$ kHz/mW\n" *
 #                 "\$b=$(fit1.uncs[4])\$ MHz\$\\cdot\$GHz/mW"), fontsize="small")
-legend(loc=(0.74, 0.38), fontsize="small", handlelength=0.6, handletextpad=0.3)
+legend(loc=(0.74, 0.385), fontsize="small", handlelength=0.6, handletextpad=0.3)
 grid()
+xticks([-225, -175, -125, -75])
+yticks([200, 400, 600])
 xlabel("Detuning (GHz)")
 ylabel("Light Shift (kHz)")
 NaCsPlot.maybe_save("$(prefix)_fs")
+
+figure(figsize=[3.6, 3.0])
+freq = 560
+plot2 = get_plot_data_freq(data, fit1, model1, freq)
+bg = matplotlib.patches.Rectangle((2.5, 70), 4.0, 370, facecolor="white", alpha=0.9)
+gca().add_patch(bg)
+bg = matplotlib.patches.Rectangle((6.5, 160), 10.5, 280, facecolor="white", alpha=0.9)
+gca().add_patch(bg)
+errorbar(plot2.x[1], (plot2.y[1] .- fit1.param[1]) .* 1000, plot2.unc[1] .* 1000, fmt="C0o")
+errorbar(plot2.x[2], (plot2.y[2] .- fit1.param[1]) .* 1000, plot2.unc[2] .* 1000, fmt="C1o")
+errorbar(plot2.x[3], (plot2.y[3] .- fit1.param[1]) .* 1000, plot2.unc[3] .* 1000, fmt="C2o")
+plot(plot2.plotx, (plot2.ploty .- fit1.param[1]) .* 1000, "k")
+xscale("log")
+yscale("log")
[…]

### 2020-10-23 paper.tex
Update captions

@@
     the Raman transfer process.
+    Inset: Raman detuning scans at different times showing the resonance frequency.
+    This is also fitted to a model of Raman transition
+    with loss on the atom and molecule state and is used to determine
+    both the Raman Rabi frequency and the loss rates.
     \label{f-raman}}
@@
   \caption{
-    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
-    with loss on the atom and molecule state. The combined fit is used to determine
-    both the Raman Rabi frequency and the loss rates.
-    (B) Two-body atom lifetime of $5.1(11) \mathrm{ms}$
-    in $15 \mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
-    This is used to improve the fitting of the Raman transfer data.
-    Inset: Atomic scattering rate scales as $P_{tweezer}^{2.58}$,
-    this is consistent with a two photon scattering process.
-    We have not measured a clear dependency of the loss rate on the tweezer detuning.
-    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
+    (A) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
     Molecule survival is detected by dissociating back to atoms using a second Raman transition.
@@
     between the two Raman pulses with incomplete transfer.
+    (B) Two-body atom lifetime of $5.1(11) \mathrm{ms}$
+    in $15 \mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
+    This is used to improve the fitting of the Raman transfer data.
+    Inset: Atomic scattering rate scales as $P_{tweezer}^{2.58}$ on a log-log scale,
+    this is consistent with a two photon scattering process.
+    We have not measured a clear dependency of the loss rate on the tweezer detuning.
     \label{f-lifetime}}

### 2020-10-23 plot_exp_data.jl
Consistent label casing, add xlabel for inset

@@ -167,8 +167,8 @@ NaCsPlot.plot_survival_data(data_nacs_25′, fmt="C2o", label="0.25 ms")
 plot(plot_freq .- param_1[3], model_2d.(0.25, plot_freq, (param_1,)), "C2")
 legend(fontsize="x-small", loc="lower right")
 grid()
-xlabel("Detuning from resonance (kHz)")
-ylabel("Two-body survival")
+xlabel("Detuning From Resonance (kHz)")
+ylabel("Two-Body Survival")
 NaCsPlot.maybe_save("$(prefix)_raman_det")
 
 figure()
@@ -180,11 +180,11 @@ NaCsPlot.plot_survival_data(data_nacs_25′, scale_1, fmt="C2o", label="0.25 ms"
 plot(plot_freq .- param_1[3], model_2d.(0.25, plot_freq, (param_1,)) .* scale_1, "C2")
 legend(fontsize="x-small", loc="lower right")
 grid()
-xlabel("Detuning from resonance (kHz)")
+xlabel("Detuning From Resonance (kHz)")
 ylabel("Fraction of Atomic Ground State")
 NaCsPlot.maybe_save("$(prefix)_norm_raman_det")
 
-figure(figsize=[3.6, 3.0])
+figure(figsize=[3.6, 3.1])
 bg = matplotlib.patches.Rectangle((-13, 0.08), 24, 0.98, facecolor="white", alpha=0.9)
 gca().add_patch(bg)
 NaCsPlot.plot_survival_data(data_nacs_12′, scale_1, fmt="C1o", label="0.12 ms")
@@ -197,7 +197,7 @@ xlim([-13, 11])
 ylim([0.08, 1.06])
 # legend(fontsize="x-small", loc="lower right")
 grid()
-# xlabel("Detuning from resonance (kHz)")
+xlabel("Raman Detuning (kHz)", fontsize=15)
 # ylabel("Fraction of Atomic Ground State")
 NaCsPlot.maybe_save("$(prefix)_norm_raman_det_inset")
 
@@ -218,8 +218,8 @@ function plot_lorentz()
     text(-5.83, 0.27, "\$f_{Raman}=$(770 + fit_l12.uncs[3] / 1000) \\mathrm{MHz}\$",
          color="C0", fontsize="small")
     grid()
-    xlabel("Detuning from resonance (kHz)")
-    ylabel("Two-body survival")
[…]

### 2020-10-24 paper.tex
Update result discussion order

@@
 we locate the Raman resonance for the atom to molecule transition at
-$770.571504(85) ~\mathrm{MHz}$ (Fig.~\ref{f-lifetime}A)
+$770.571504(85) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}C inset)
 with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$
@@
 $69\%$ of initial ground state atoms are transferred into the molecular state.
-
-In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the molecular state (Fig.~\ref{f-lifetime}A).
-We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B) without turning on the second frequency.
+This transfer efficiency is mainly limited by the molecular lifetime
+which can be measured directly by preparing the molecule with a $\pi $ pulse
+and then using a second $\pi$ pulse to dissociate the molecule back to atoms
+after a variable wait time (Fig.~\ref{f-lifetime}A).
+The result shows a molecular lifetime of $0.1990(90) \mathrm{ms}$
+consistent with the decay of Rabi oscillation.
+We obtain the Raman Rabi frequency by fitting our measurements to a model
+that includes a Raman Rabi frequency and
+a finite lifetime for the molecular state (Fig.~\ref{f-raman}C and inset).
+We account for the effect of atomic state loss by measuring the single and
+two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B)
+without turning on the second frequency.
 The fit shows that we have a Raman Rabi frequency of $2\pi\times3.282(42) ~\mathrm{kHz}$.
-The molecule we form has a lifetime of $0.1990(90) ~\mathrm{ms}$ which is the main limitation on the fidelity of the transfer.
-The molecule lifetime can be measured directly by preparing the molecule with a $\pi $ pulse and then using a second $\pi $ pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C).
-The result shows a molecular lifetime consistent with our fitting of the decaying Rabi oscillation.
 
@@
   \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
+    The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6\mathrm{GHz}$.
     (A) The light shift of the Raman resonance scales as $P_{tweezer}$
@@
     the atom-molecule matrix element ratio.
+    Insets for (A) and (B), light shift and Raman Rabi frequency on a log-log plot
+    showing the power law scaling.
     \label{f-det}}
@@
 The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
-B field dependency $42.17(24) kHz/G$.
+\todo{}B field dependency $42.17(24) kHz/G$.
 

### 2020-10-25 paper.tex
Update on Overleaf.

@@
 Experimentally, we first prepare two atoms in a well-defined external and internal quantum state using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}.
-In brief, the experimental cycle begins by  loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom stochastically into separate optical tweezers.
-The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom, which is compared to the image at the end of the experiment.
-Raman sideband cooling is then applied to cool both atoms simultaneous into the 3-dimensional motional ground state of their optical tweezers.
+In brief, the experimental cycle begins by stochastically loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into separate optical tweezers.
+The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom to be able to post select the experimental result on the initial loading condition.
+Raman sideband cooling is then applied to cool both atoms simultaneously into the 3-dimensional motional ground state of their optical tweezers.
 After cooling, the Na and Cs atoms are in a spin state of $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}\equiv \ket{F=2,m_F=2}_{\text{Na}}\ket{F=4,m_F=4}_{\text{Cs}} $ %and are merged into the same tweezer~\cite{Liu2019}.
 %The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $.
-that has a low scattering length.
+which has a low scattering length.
 The small two atom interaction allows the two atoms to be merged into the same tweezer with minimum pertubation and remain in the motional ground state after the merge.
@@
 % After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
-Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7 kHz$ interaction shift~\cite{Hood2019}.
+Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination to use as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7 kHz$ interaction shift~\cite{Hood2019}.
 %using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\text{Cs}}}$ state.
@@
 
-Guided by coupled channel calculations,
+We choose the tweezer frequency to be far detuned ($145 ~\mathrm{GHz}$) from the $v' = 0$ line, and guided by coupled channel calculations,
 we locate the Raman resonance for the atom to molecule transition at
 $770.571504(85) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}C inset)
-with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$
-which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning.
+with $15 ~\mathrm{mW}$ tweezer power. 
 % (We can maybe add information about the prediction here?)
@@
 The molecular state is dark to the imaging step,
-so successful transfer of the atoms to the molecular state will be detected as loss of atoms
-in the post experiment image when compared to the initial image.
+so successful transfer of the atoms to the molecular state will be detected as loss.
 We observed a Fourier limited linewidth which is evidence of a coherent transfer.
@@
 we fix the two photon detuning on resonance and scan the pulse time.
-Fig.~\ref{f-raman}C shows the observed Rabi oscillation between the atomic and molecular states.
+Fig.~\ref{f-raman}C shows the observed coherent Rabi oscillation between the atomic and molecular states.
 Fitting the data with a decaying Rabi oscillation suggests that
@@
 a finite lifetime for the molecular state (Fig.~\ref{f-raman}C and inset).
-We account for the effect of atomic state loss by measuring the single and
+We account for the effect of atomic state loss by measuring the one and
 two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B)
@@
 
-The ratio of the molecule scattering rate to the Rabi frequency is larger than
-the theory prediction by more than a factor of $10$.
+The efficiency of the transfer is worse than expected from theory and arises from the ratio of the molecule scattering rate to the Rabi frequency being 10 times larger than predicted.
 Based on the discussion above, if this discrepancy arises from the $v'=0$ excited state,
@@
 and the $v'=0$ intermediate state.
-From this measurement, we can calculate a $\Omega_m$ of
+From this measurement, we can extract a $\Omega_m$ of
 $2\pi\times36.162(20) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or
@@
 from the $v'=0$ state to be higher than expected.
-Furthermore, based on measurements of the excited state using photoassociation (PA) spectroscopy,
-the natural linewidth of the $v'=0$ excited state is no larger than $20 \mathrm{MHz}$.
+Furthermore, we measure the natural linewidth of the $v'=0$ excited state to be no larger than $20 \mathrm{MHz}$ using photoassociation (PA) spectroscopy.
 This suggests that the excited state linewidth should not cause

### 2020-10-27 paper.tex
Update on Overleaf.

@@
   through an optical Raman transition without the use of a Feshbach resonance.
-Our scheme borrows transition dipole moment while reducing photon scattering by selecting a deeply bound electronic excited intermediate state.
+The Raman scheme uses a deeply bound electronic excited intermediate state to achieve a large transition dipole moment while reducing the photon scattering.
   Starting from two atoms in their relative motional ground state,
-  we achieve optical transfer efficiency of $69\%$.
-  The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8~\mathrm{G}$
+  we achieve an optical transfer efficiency of $69\%$.
+  The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8~\mathrm{G}$ (\textcolor{red}{Unresolved comment from Jon: with so many digits on the resonance frequency, we may need to mention more digits on the B field number and/or also state the tweezer power.
+We can state the tweezer power for where we measure it, but the transmission through the objective, etc.
+I believe is only estimated.})
   with more than $60\%$ of the molecule created in the motional ground state.
-  This technique is general without relying on narrow excited state lines or Feshbach resonances and could allow a wider range of molecular species to be assembled atom-by-atom.
+  This technique does not rely on narrow excited state lines or Feshbach resonances and will allow a wider range of molecular species to be assembled atom-by-atom.
 \end{abstract}
@@
 
-Such ultracold molecular association takes advantage of the much developed cooling and trapping techniques for atoms as a starting point.
-To overcome the challenges of small wavefunction overlap and the large release of binding energy of converting atoms to deeply-bound molecules, a  two-step approach has been established to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
-So far, all of such association processes utilized a magnetic Feshbach scattering resonance and have been applied to bialkali molecules.
-The only exceptions are Sr$_2$ where narrow linewidth excited states are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb where weakly bound molecules of a binding energy of a couple MHz exists~\cite{He331}.
-These requirements  limit the generality of previous association techniques.
+Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques that have been developed for atoms.
+Associating atoms into deeply-bound molecules is challenging because of the small wavefunction overlap between the free-atom and molecular state and the release of a large amount of binding energy.
+A two-step approach has been demonstrated to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state releasing the binding energy via stimulated emission~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
+So far, most molecular association has been achieved for bialkali molecules by magnetoassociation using a magnetic Feshbach scattering resonance.
+The only exceptions are Sr$_2,$ where narrow linewidth ($\sim 20 ~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly bound molecules with a couple MHz binding energy exists~\cite{He331}.
+With these requirements, dimers between alkali atoms and non-magnetic atoms, or molecules involving atoms without narrow intercombination lines remain difficult to associate.
+% These requirements limit the generality of previous association techniques.
 % The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques.
@@
 
-Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}A, neither using a Feshbach resonance, few MHz-level bound states, nor a narrow excited state.
-The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.
-Our scheme is based on a choice of vibrational state of the electronic excited state $c^3\Sigma^+(\Omega = 1)$ that has the theoretical best Raman Rabi frequency to photon scattering ratio.
-To further increase this ratio and reduce technical requirements such as intensity stability, we choose an initial and final state where the matrix elements with the excited state are as balanced as possible.
-This approach minimizes the reliance on system specific properties and could therefore be applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
+Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}A.
+The scheme does not rely on a Feshbach resonance, few MHz level bound states, or a narrow excited state.
+The resulting single molecule is in a well-defined internal quantum state and predominately in its motional ground state.
+A vibrational state of the electronic excited state $c^3\Sigma^+(\Omega = 1)$ is used as the intermediate state in the Raman scheme, and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation.
+To further reduce the photon scattering and sensitivity to laser intensity noise, we choose the initial and final state to balance the two Rabi frequencies as much as possible.
+This system-independent approach can be used for creating new molecules atom-by-atom with full quantum state control.
+% and could therefore be applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
 % (also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))
@@
 
-The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
+The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, and the target weakly-bound molecular state are coupled to an intermediate state by two laser frequencies with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
-The transfer Raman Rabi Rate, $\Omega_R=\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_s$ that is a sum of all coupling sources%,
+The transfer Raman Rabi Rate, $\Omega_R=\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_s$
 % $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
 ~\cite{Wineland2003}.
-Unlike for Raman transitions in atoms, the two coupling matrix elements here are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
+Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
 due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
@@
 
-Pioneering experiments used weakly-bound excited states as the intermediate state in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
+Early experiments used weakly-bound excited states as the intermediate state in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
 However, for a complete picture, the many excited vibrational states in a molecular potential as well as the excited atomic continuum need to be considered.

### 2020-10-29 plot_exp_data.jl
Use illustration instead of text in plot

@@ -299,6 +299,19 @@ grid()
 yticks([0.2, 0.6, 1.0])
 xlabel("Raman Time (ms)")
 ylabel("Fraction of Atomic Ground State")
+NaCsPlot.maybe_save("$(prefix)_norm_t_annotate")
+
+figure(figsize=[7.2, 5.4])
+NaCsPlot.plot_survival_data(data_nacs_t, scale_2,
+                            fmt="C0o", label="770.5704 MHz")
+plot(plot_time, model_2d.(plot_time, 570.4, (param_2,)) .* scale_2, "C0")
+xlim([0, 0.86])
+ylim([0.04, 1.08])
+# legend(fontsize="x-small", loc="upper right")
+grid()
+yticks([0.2, 0.6, 1.0])
+xlabel("Raman Time (ms)")
+ylabel("Fraction of Atomic Ground State")
 NaCsPlot.maybe_save("$(prefix)_norm_t")
 
 figure()

### 2020-10-29 plot_rabi_scaling.jl
Add X axis to figure 4 inset

@@ -152,10 +152,14 @@ NaCsPlot.maybe_save("$(prefix)")
 figure(figsize=[3.6, 3.0])
 freq = 560
 plot2 = get_plot_data_freq(data, fit1, model, freq)
-bg = matplotlib.patches.Rectangle((2.8, 0.42), 10.2, 3.78, facecolor="white", alpha=0.9)
-gca().add_patch(bg)
-bg = matplotlib.patches.Rectangle((13, 0.6), 4, 3.6, facecolor="white", alpha=0.9)
-gca().add_patch(bg)
+ax = gca()
+# bg = matplotlib.patches.Rectangle((2.8, 0.42), 10.2, 3.78, facecolor="white", alpha=0.9)
+# ax.add_patch(bg)
+# bg = matplotlib.patches.Rectangle((13, 0.6), 4, 3.6, facecolor="white", alpha=0.9)
+# ax.add_patch(bg)
+bg = matplotlib.patches.Polygon([2.8 0.42; 2.8 4.2; 17 4.2; 17 3.3; 3.2 0.42],
+                                facecolor="white", alpha=0.9)
+ax.add_patch(bg)
 # errorbar(plot2.x, plot2.y, plot2.unc, fmt="C0o")
 errorbar(plot2.x[1], plot2.y[1], plot2.unc[1], fmt="C0o")
 errorbar(plot2.x[2], plot2.y[2], plot2.unc[2], fmt="C1o")
@@ -164,14 +168,16 @@ plot(plot2.plotx, plot2.ploty, "k")
 xscale("log")
 yscale("log")
 minorticks_off()
-xticks([])
+xticks([3, 6, 15], ["3", "6", "15"])
 yticks([1, 4], ["1", "4"])
+xlabel("Tweezer Power (mW)", fontsize=15)
 xlim([2.8, 17])
 ylim([0.42, 4.2])
-ax = gca()
-ax.spines["top"].set_visible(false)
+# ax.spines["top"].set_visible(false)
 ax.spines["bottom"].set_visible(false)
 ax.spines["right"].set_visible(false)
+ax.xaxis.set_ticks_position("top")
+ax.xaxis.set_label_position("top")
 NaCsPlot.maybe_save("$(prefix)_560")
 
 NaCsPlot.maybe_show()

### 2020-10-29 plot_res_scaling.jl

@@ -182,21 +182,26 @@ end
 #                 "\$f_{PA0}=$(fit1.uncs[2] + 288000)\$ GHz\n" *
 #                 "\$a=$(fit1.uncs[3] * 1000)\$ kHz/mW\n" *
 #                 "\$b=$(fit1.uncs[4])\$ MHz\$\\cdot\$GHz/mW"), fontsize="small")
-legend(loc=(0.74, 0.385), fontsize="small", handlelength=0.6, handletextpad=0.3)
+legend(loc=(0.74, 0.372), fontsize="small", handlelength=0.6, handletextpad=0.3)
 grid()
 xticks([-225, -175, -125, -75])
 yticks([200, 400, 600])
+ylim([43, 798])
 xlabel("Detuning (GHz)")
 ylabel("Light Shift (kHz)")
 NaCsPlot.maybe_save("$(prefix)_fs")
 
-figure(figsize=[3.6, 3.0])
+figure(figsize=[3.8, 2.9])
 freq = 560
 plot2 = get_plot_data_freq(data, fit1, model1, freq)
-bg = matplotlib.patches.Rectangle((2.5, 70), 4.0, 370, facecolor="white", alpha=0.9)
-gca().add_patch(bg)
-bg = matplotlib.patches.Rectangle((6.5, 160), 10.5, 280, facecolor="white", alpha=0.9)
-gca().add_patch(bg)
+ax = gca()
+# bg = matplotlib.patches.Rectangle((2.5, 70), 4.0, 370, facecolor="red", alpha=0.9)
+# ax.add_patch(bg)
+# bg = matplotlib.patches.Rectangle((6.5, 160), 10.5, 280, facecolor="red", alpha=0.9)
+# ax.add_patch(bg)
+bg = matplotlib.patches.Polygon([2.5 70; 2.5 440; 17 440; 7.63 120],
+                                facecolor="white", alpha=0.9)
+ax.add_patch(bg)
 errorbar(plot2.x[1], (plot2.y[1] .- fit1.param[1]) .* 1000, plot2.unc[1] .* 1000, fmt="C0o")
 errorbar(plot2.x[2], (plot2.y[2] .- fit1.param[1]) .* 1000, plot2.unc[2] .* 1000, fmt="C1o")
 errorbar(plot2.x[3], (plot2.y[3] .- fit1.param[1]) .* 1000, plot2.unc[3] .* 1000, fmt="C2o")
[…]

### 2020-10-29 plot_exp_data.jl
[figure] consistent label casing

@@ -370,7 +370,7 @@ plot(plot_m_time, model_ramsey(plot_m_time, param_ramsey) .* scale_ramsey, "C0-"
 xlim([0, 0.9])
 grid()
 xlabel("Molecule Hold Time (ms)")
-ylabel("Molecule survival")
+ylabel("Molecule Survival")
 NaCsPlot.maybe_save("$(prefix)_norm_m_t")
 
 const img_freq = param_1[3] .+ linspace(-20, 20, 201)

### 2020-10-29 plot_wavefunction.jl

@@ -1,0 +1,48 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+# using DataStructures
+# using LsqFit
+using LibArchive
+
+using DelimitedFiles
+
+function read_csv_compressed(fname, args...; kwargs...)
+    LibArchive.Reader(fname) do reader
+        LibArchive.support_format_raw(reader)
+        LibArchive.support_filter_all(reader)
+        LibArchive.next_header(reader)
+        readdlm(reader, args...; kwargs...)
+    end
+end
+
+const fname31 = joinpath(@__DIR__, "../2020-postdoc/3311boundstate.csv.zst")
+const fname32 = joinpath(@__DIR__, "../2020-postdoc/3322boundstate.csv.zst")
+const fname42 = joinpath(@__DIR__, "../2020-postdoc/4422boundstate.csv.zst")
+const data31 = read_csv_compressed(fname31, ',', Float64)
+const data32 = read_csv_compressed(fname32, ',', Float64)
+const data42 = read_csv_compressed(fname42, ',', Float64)
+
+const prefix = joinpath(@__DIR__, "imgs", "wavefunction")
+
+figure()
+plot(data42[:, 1], data42[:, 2] .* 1e4, "C2", label="Na(2,2) Cs(4,4)")
+plot(data32[:, 1], data32[:, 2] .* 1e4, "C1", label="Na(2,2) Cs(3,3)")
+plot(data31[:, 1], data31[:, 2] .* 1e4, "C3--", label="Na(1,1) Cs(3,3)")
+grid()
+xlim([0, 3080])
+ylim([0, 7.3])
+ylabel("Probability Density")
+xlabel("R (Angstroms)")
+legend(fontsize="x-small")
+NaCsPlot.maybe_save("$(prefix)")
+
+NaCsPlot.maybe_show()

### 2020-10-29 paper.tex
White space, regenerate PDF
Reply to Jon
WIP: address Jons comments

@@
 \newcommand{\eff}{ef\! f}
+\newcommand{\Na}{\mathrm{Na}}
+\newcommand{\Cs}{\mathrm{Cs}}
 \newcommand{\fxnote}[1]{{\textbf{[#1]}}}
@@
   through an optical Raman transition without the use of a Feshbach resonance.
-The Raman scheme uses a deeply bound electronic excited intermediate state to achieve a large transition dipole moment while reducing the photon scattering.
+  The Raman scheme uses a deeply bound electronic excited intermediate state
+  to achieve a large transition dipole moment while reducing the photon scattering.
   Starting from two atoms in their relative motional ground state,
   we achieve an optical transfer efficiency of $69\%$.
-  The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8~\mathrm{G}$ (\textcolor{red}{Unresolved comment from Jon: with so many digits on the resonance frequency, we may need to mention more digits on the B field number and/or also state the tweezer power.
+  The molecule has a binding energy of $770.20052(2) \mathrm{MHz}$ at $8.8~\mathrm{G}$ (\textcolor{red}{Unresolved comment from Jon: with so many digits on the resonance frequency, we may need to mention more digits on the B field number and/or also state the tweezer power.
 We can state the tweezer power for where we measure it, but the transmission through the objective, etc.
-I believe is only estimated.})
+I believe is only estimated.
+(YYC: This is why the original number quoted was zero field.
+The current number is still for zero tweezer power)})
   with more than $60\%$ of the molecule created in the motional ground state.
-  This technique does not rely on narrow excited state lines or Feshbach resonances and will allow a wider range of molecular species to be assembled atom-by-atom.
+  This technique does not rely on narrow excited state lines or Feshbach resonances
+  and will allow a wider range of molecular species to be assembled atom-by-atom.
 \end{abstract}
@@
 So far, most molecular association has been achieved for bialkali molecules by magnetoassociation using a magnetic Feshbach scattering resonance.
-The only exceptions are Sr$_2,$ where narrow linewidth ($\sim 20 ~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly bound molecules with a couple MHz binding energy exists~\cite{He331}.
+The only exceptions are Sr$_2,$ where narrow linewidth ($\sim 20 ~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly-bound molecules with a couple MHz binding energy exists~\cite{He331}.
 With these requirements, dimers between alkali atoms and non-magnetic atoms, or molecules involving atoms without narrow intercombination lines remain difficult to associate.
@@
 
-Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}A.
+Here, we demonstrate coherent association of an atom pair to a weakly-bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}a.
 The scheme does not rely on a Feshbach resonance, few MHz level bound states, or a narrow excited state.
@@
 
-% The traditional choice for such an intermediate state is a weakly-bound Feshbach molecule, which can be coherently produced by ramping a magnetic field across the Feshbach resonance \todo{cite our FB result}.
+% The traditional choice for such an intermediate state is a weakly-bound Feshbach molecule, which can be coherently produced by ramping a magnetic field across the Feshbach resonance.
 However, this requires a suitable Feshbach resonance, which limits the generality of this technique.
-An alternative approach uses a weakly bound ground electronic molecular state as the intermediate state (I'm wondering how we can distinguish this weakly bound molecular state from the weakly-bound Feshbach molecule state, we can maybe specify typcial binding energies?
-"most weakly bound state of the low field ground state electronic potential" maybe?), populated by an optical Raman transition, schematically shown in figure \todo{}.
+An alternative approach uses a weakly-bound ground electronic molecular state as the intermediate state (I'm wondering how we can distinguish this weakly-bound molecular state from the weakly-bound Feshbach molecule state, we can maybe specify typcial binding energies?
+"most weakly-bound state of the low field ground state electronic potential" maybe?), populated by an optical Raman transition, schematically shown in figure.
 In this scheme, a pair of Raman beams is used to drive the unbound, but confined, atoms to a bound molecular state via an excited molecular state.
 This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules.
-Such a transfer using an optical transition has been observed in previous experiments \todo{cite}.
+Such a transfer using an optical transition has been observed in previous experiments.
 However, they either require the use of a narrow optical transition which limits the generality or were driving the transition incoherently due to scattering.
 
-% the requirement of a suitable FB resonance limits its generality. \todo{e.g. non-magnetic atoms?}
+% the requirement of a suitable FB resonance limits its generality.
 
@@
   \caption{Optical creation of single molecule from single atoms in tweezer.
-    (A) Schematics of the optical transition from an atom pair to a weakly bound molecule.
+    (a) Schematics of the optical transition from an atom pair to a weakly-bound molecule.
     The initial state is the relative motional ground state between the two atoms
@@
     by $\Delta$ in order to suppress the scattering during the transfer.
-    (B) Comparison between using a weakly bound and a deeply bound excited state
+    (b) Comparison between using a weakly-bound and a deeply bound excited state
     as intermediate state for the Raman transition.
@@
     has a smaller Raman Rabi frequency ($\Omega_{R}$)
-    compared to the weakly bound excited state (lower half $v'=63$) at a given detuning.
+    compared to the weakly-bound excited state (lower half $v'=63$) at a given detuning.
     However, the scattering rate ($\Gamma_{s}$) is also much lower,
     which results in a larger Raman Rabi frequency to scattering rate ratio.
-    (C) Enhancement of short range wavefunction.
-    The large scattering length for the $Na(2,2),Cs(3,3)$ state creates an interaction shift
+    (c) Enhancement of short range wavefunction.
+    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
     comparable to the axial trapping frequency.
@@
 
-% The optical transfer scheme we use is shown in figure \todo{}. To drive the atoms from
+% The optical transfer scheme we use is shown in figure. To drive the atoms from
 % We use an optical Raman transition to drive the system from the atomic initial state to a ground electronic molecular state.
-In order to reduce the size mismatch between the atomic and molecular states, we selected the first bound state for the 3322 spin state \todo{asymtopt to the 3322 threshold?} as our final state.
-\todo{move selection of intermediate state to intro?}.
+In order to reduce the size mismatch between the atomic and molecular states, we selected the first bound state for the 3322 spin state as our final state.
 For similar reason, the natural choice for the intermediate excited molecular state is one with highly excited motional level.However, from our calculation (and experiment?), the smaller level space for high vibrational state and the smaller detuning from the atomic threshold increases the scattering rate of the molecular state which causes a reduced Raman Rabi frequency to decoherence rate ratio and a lower transfer efficiency.
@@
 % The challenge of optical Raman association of molecules from atoms lies with achieving a high enough Raman Rabi frequency despite the wavefunction size mismatch between the atomic state and the excited molecular state.
-While pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
+While pioneering experiments used weakly-bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
 % Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with minimal loss is the first key task.
 
-The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, and the target weakly-bound molecular state are coupled to an intermediate state by two laser frequencies with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
+The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}a), where the initial atomic state, and the target weakly-bound molecular state are coupled to an intermediate state by two laser frequencies with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
@@
 
-Early experiments used weakly-bound excited states as the intermediate state in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
-However, for a complete picture, the many excited vibrational states in a molecular potential as well as the excited atomic continuum need to be considered.
-The total scattering rate and Raman Rabi rate become a sum of the scattering rates and Raman Rabi rates over all possible intermediate states.
-With these considerations, using a weakly-bound excited state as the intermeidate state suffers from strong scattering of the nearby excited atomic continuum rendering it incoherent, resulting in molecule loss.
-This scattering is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can  be made smaller by detuning away from the dissociation threshold.
-%With the multiple excited vibrational states present in a molecular potential as intermediate states, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual intermediate states.
+Early experiments used weakly-bound excited states as the intermediate state
+in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
+However, for a complete picture, the many excited vibrational states in a molecular potential
+as well as the excited atomic continuum need to be considered.
+The total scattering rate and Raman Rabi rate become a sum of the scattering rates
+and Raman Rabi rates over all possible intermediate states.
+With these considerations, using a weakly-bound excited state as the intermeidate state
+suffers from strong scattering of the nearby excited atomic continuum rendering it incoherent,
+resulting in molecule loss \todo{be more clear with "molecule loss". I think you mean:
+  resulting in large incoherence and loss to other molecular states.}.
+This scattering is proportional to $1/\delta_{thresh}^2$,
+where $\delta_{thresh}$ is the detuning from the dissociation threshold,
+and thus can be made smaller by using deeply bound vibrational states as the intermediate level.
+% With the multiple excited vibrational states present in a molecular potential as intermediate states, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual intermediate states.
 Furthermore, for a more complete calculation, we also need to account for the effects of the excited atomic continuum, which is particularly important for the target molecular state.
@@
 
-% For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
-% Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
+% For a weakly-bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
+% Furthermore, due to similarity in wavefunction size, the weakly-bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
 The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can also be made smaller by detuning away from the dissociation threshold.
@@
 
-To find the optimal intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011} and the continuum~\cite{Liu2017}.
+To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency
+and scattering rate at different detunings from the atomic threshold
+taking into account of all states of
+the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
+and the continuum~\cite{Liu2017}.
 The excited atomic continuum is particularly important for the target molecular state.
-The sum of the squares of the wavefunction overlap between the target weakly-bound molecular state and all the excited molecular intermediate states considered is only about 2\%, suggesting that there is significant matrix element between the target molecular state and the excited atomic continuum (See SM).
-This calculation shows that the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency (Fig.~\ref{f-theory}B, full result in SM)
-As a result, we choose %a deeply bound molecular excited state
-the $v'=0$ of $c^3\Sigma^+(\Omega = 1)$ as an intermediate state to drive the Raman transition. %(mention the trend, also v'=12 will work as similarly as v'=0)
+The sum of the squares of the wavefunction overlap
+between the target weakly-bound molecular state
+and all the excited molecular intermediate states considered
+\todo{all vibrational states} is only about $0.02$,
+suggesting that there is significant matrix element
+between the target molecular state and the excited atomic continuum (See SM).
+This calculation shows that the ratio of the Raman Rabi rate to scattering rate
+can be made larger for more deeply bound states compared to weakly-bound states
+at a cost of a smaller Raman Rabi frequency
+(Fig.~\ref{f-theory}b, full result in SM \todo{proper cite})
+As a result, we choose the $v'=0$ of $c^3\Sigma^+(\Omega = 1)$ as an intermediate state
+to drive the Raman transition. % (mention the trend, also v'=12 will work as similarly as v'=0)
 
-% higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states.
+% higher Raman Rabi frequency at the same detuning, using a weakly-bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states.
 As a result, we use a deeply bound molecular excited state to drive the Raman transition.
@@
 % In addition to the intermediate state, the choice of the initial and final states is also critical.
-In addition to the intermediate state, choosing an initial and a final state for a large $ \Omega_a/\Omega_m $ ratio would allow large Raman Rabi coupling at a given detuning.
-Furthermore, a larger ratio also relaxes the intensity stability requirement, because this is also the ratio between the Raman Rabi coupling and the AC Stark shift of the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2, with both beams at equal power, to account for the Stark shift caused by both beams.}.
+In addition to the intermediate state,
+choosing an initial and a final state for a large $ \Omega_a/\Omega_m $ ratio
+maximizes Raman Rabi coupling at a given detuning.
+Furthermore, a larger ratio also relaxes the intensity stability requirement,
+because this is also the ratio between the Raman Rabi coupling
+and the AC Stark shift of the molecular state, $\Omega_m^2 / 2\Delta$
+\footnote{There is an additional factor of 2, with both beams at equal power,
+  to account for the Stark shift caused by both beams.}.
 % and relax the intensity stability requirement due to the AC Stark shift of the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.}
@@
 % it can be made larger by increasing the coupling of the atomic state with the excited molecular state.
-Due to the small size of the intermediate state wavefunction, the coupling $\Omega_a$ is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential.
-To increase the amplitude within the molecular potential, one can increase the external confinement of atom pairs.
-Using a harmonic oscillator approximation, the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $, where $ \omega_{\text{trap}} $ is the trap frequency.
-Alternatively, one can choose an atomic pair state with a large scattering length (positive or negative).
-For these states, the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}C).
-%The increase in the coupling is proportional to (quote/cite Olive's equation?).
-For our system of Na and Cs atoms, we choose  a spin state combination $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}\equiv \ket{F=2,m_F=2}_{\text{Na}}\ket{F=3,m_F=3}_{\text{Cs}} $that has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0$~\cite{Hood2019}.
-We note that other stable spin combinations give smaller scattering lengths ($<~50~a_0$).
-% We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\text{Cs}}} = \ket{F=4,m_F=4}_{\text{Cs}}, \ket{\downarrow_{\text{Cs}}} = \ket{F=3,m_F=3}_{\text{Cs}}, \ket{\uparrow_{\text{Na}}} = \ket{F=2,m_F=2}_{\text{Na}}, $ and $ \ket{\downarrow_{\text{Na}}} = \ket{F=1,m_F=1}_{\text{Na}}$.
-Among the stable spin combinations, $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}} $ combination has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
-In addition to the increased atomic coupling, $ \Omega_a $, %with the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination,
-coupled channel calculations show that the target molecular state that is predominantly in this spin combination also has reduced coupling, $ \Omega_m $, with the intermediate state when compared to bound states of the other stable spin combinations % $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ bound states.
-Therefore, using an initial $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the other combinations, and thus only an required intensity stability of 5\% instead of 0.3\%.
+Due to the small size of the intermediate state wavefunction as compared to the trapped atoms,
+the coupling $\Omega_a$ is approximately proportional to
+the value of the relative atomic wavefunction at short distance
+within the molecular potential.
+To increase the amplitude within the molecular potential,
+one can increase the external confinement of atom pairs.
+Using a harmonic oscillator approximation,
+the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $,
+where $ \omega_{\text{trap}} $ is the trap frequency.
+Alternatively, one can choose an atomic pair state with a large scattering length
+(positive or negative).
+For these states, the phase shift in the relative wavefunction
+between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}c).
+% The increase in the coupling is proportional to (quote/cite Olive's equation?).
+For our system of Na and Cs atoms,
+we choose a spin state combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=3,m_F=3}_{\Cs}$ that has a large and negative scattering length of
+$ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0$~\cite{Hood2019}.
+All other stable spin combinations give smaller scattering lengths ($<~50~a_0$).
+% We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\Cs}} = \ket{F=4,m_F=4}_{\Cs}, \ket{\downarrow_{\Cs}} = \ket{F=3,m_F=3}_{\Cs}, \ket{\uparrow_{\Na}} = \ket{F=2,m_F=2}_{\Na}, $ and $ \ket{\downarrow_{\Na}} = \ket{F=1,m_F=1}_{\Na}$.
+Among the stable spin combinations, $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\Na} \downarrow_{\Cs}} $ combination has a large and negative scattering length of $ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
+For the target molecular state, we perform coupled-channel calculations
+to identify the Rabi frequencies $\Omega_m$ to different weakly-bound spin states.
+\text{red}{A target spin state is ideally similar to the initial spin state
+  in order to minimize sensitivity to the B-field.
+  We find a target spin state predominantly in the initial spin state
+  that also has the advantage of having a reduced sensitivity
+  to laser intensity noise because of a larger $\Omega_a/\Omega_b$ as compared to other states.
+  This reduces the intensity stability requirement to $5\%$
+  instead of $0.3\%$ which is typical for other states.}
+In addition to the increased atomic coupling, $ \Omega_a $,
+coupled channel calculations show that the target molecular state
+that is predominantly in this spin combination also has reduced coupling, $ \Omega_m $,
+with the intermediate state when compared to bound states of the other stable spin combinations
+% $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
+Therefore, using an initial $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination
+results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003
+with the other combinations,
+and thus only an required intensity stability of 5\% instead of 0.3\%.
 % Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
-% Thus, we choose the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination.
+% Thus, we choose the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination.
 \textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
@@
   \caption{
-    (A) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
+    (a) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
     The tweezer and Raman beam is focused through an objective to define the location of the
@@
     As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
-    (B) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
+    (b) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
     When driving the Raman transition, the up leg power is smoothly ramped down and
@@
     with maximum Raman Rabi frequency when the up and down leg powers are equal.
-    (C) Raman pulse time scan on resonance.
+    (c) Raman pulse time scan on resonance.
     A decaying Rabi oscillation can be observed proving the coherence of
@@
 Raman sideband cooling is then applied to cool both atoms simultaneously into the 3-dimensional motional ground state of their optical tweezers.
-After cooling, the Na and Cs atoms are in a spin state of $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}\equiv \ket{F=2,m_F=2}_{\text{Na}}\ket{F=4,m_F=4}_{\text{Cs}} $ %and are merged into the same tweezer~\cite{Liu2019}.
-%The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $.
-which has a low scattering length.
-The small two atom interaction allows the two atoms to be merged into the same tweezer with minimum pertubation and remain in the motional ground state after the merge.
+After cooling, the Na and Cs atoms are in a spin state of $\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=4,m_F=4}_{\Cs} $ %and are merged into the same tweezer~\cite{Liu2019}.
+%The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $.
+which has a small scattering length. The small two atom interaction allows the merging of the two atoms to be done with minimum pertubation so that they remain in the motional ground state.
 
 % After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
-Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination to use as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7 kHz$ interaction shift~\cite{Hood2019}.
-%using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\text{Cs}}}$ state.
+Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination to use as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7 \mathrm{kHz}$ interaction shift~\cite{Hood2019}.
+%using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\Cs}}$ state.
 The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
-This spin flip selectively transfers atoms in the relative motion ground state \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}, and for the experiment reported here, this is 31\% of the initial population of two atoms loaded in separate optical tweezers.
+This spin flip selectively transfers atoms in the relative motion ground state \text{red}{I'm a little confused.
+Aren't the atoms already in the motion ground state?} \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}, and for the experiment reported here, this is 31\% of the initial population of two atoms loaded in separate optical tweezers.\text{red}{I also find this part of the sentence confusing.
+can you say this more concisely?}
 % The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..
@@
 %% Transfer scheme
-% After the atoms are prepared in the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $ hyperfine combination, we then perform the Raman transfer.
-To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}A).
+% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
+To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}a).
 The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time.
 %to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
-The pulse sequence is shown in Fig.~\ref{f-raman}B. %Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal.
+The pulse sequence is shown in Fig.~\ref{f-raman}b. %Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal.
 % In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse.
@@
   \caption{
-    (A) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
+    (a) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
     Molecule survival is detected by dissociating back to atoms using a second Raman transition.
-    The lifetime is consistent with the $0.1990(90) \mathrm{ms}$
+    The lifetime is consistent with the $0.199(9) \mathrm{ms}$
     measured from the Raman transition data.
@@
     between the two Raman pulses with incomplete transfer.
-    (B) Two-body atom lifetime of $5.1(11) \mathrm{ms}$
+    (b) Two-body atom lifetime of $5(1) \mathrm{ms}$
     in $15 \mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
@@
 we locate the Raman resonance for the atom to molecule transition at
-$770.571504(85) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}C inset)
+$770.57150(9) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}c inset)
 with $15 ~\mathrm{mW}$ tweezer power.
@@
 Theory prediction was at $770.1 MHz$.
-\todo{more, mention/cite Jeremy}
 % The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
@@
 we fix the two photon detuning on resonance and scan the pulse time.
-Fig.~\ref{f-raman}C shows the observed coherent Rabi oscillation between the atomic and molecular states.
+Fig.~\ref{f-raman}c shows the observed coherent Rabi oscillation between the atomic and molecular states.
 Fitting the data with a decaying Rabi oscillation suggests that
@@
 and then using a second $\pi$ pulse to dissociate the molecule back to atoms
-after a variable wait time (Fig.~\ref{f-lifetime}A).
-The result shows a molecular lifetime of $0.1990(90) \mathrm{ms}$
+after a variable wait time (Fig.~\ref{f-lifetime}a).
+The result shows a molecular lifetime of $0.199(9) \mathrm{ms}$
 consistent with the decay of Rabi oscillation.
@@
 that includes a Raman Rabi frequency and
-a finite lifetime for the molecular state (Fig.~\ref{f-raman}C and inset).
+a finite lifetime for the molecular state (Fig.~\ref{f-raman}c and inset).
 We account for the effect of atomic state loss by measuring the one and
-two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B)
+two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}b)
 without turning on the second frequency.
-The fit shows that we have a Raman Rabi frequency of $2\pi\times3.282(42) ~\mathrm{kHz}$.
+The fit shows that we have a Raman Rabi frequency of $2\pi\times3.28(4) ~\mathrm{kHz}$.
 
@@
 we observe the expected linear dependency on the resonance frequency
-caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
+caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}a).
 When we vary the tweezer frequency around the $v'=0$ intermediate state,
@@
 From this measurement, we can extract a $\Omega_m$ of
-$2\pi\times36.162(20) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or
-$2\pi\times140.056(78) ~\mathrm{MHz}$ for the $15 ~\mathrm{mW}$ tweezer power used above.
+$2\pi\times36.16(2) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or
+$2\pi\times140.06(8) ~\mathrm{MHz}$ for the $15 ~\mathrm{mW}$ tweezer power used above.
 This number is consistent with the value of
-$2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
+$2\pi\times27 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
 
@@
     The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6\mathrm{GHz}$.
-    (A) The light shift of the Raman resonance scales as $P_{tweezer}$
+    (a) The light shift of the Raman resonance scales as $P_{tweezer}$
     and follows $1/\Delta$ with an offset.
@@
     perpendicular to the real magnetic field.
-    (B) Raman Rabi frequency ($\Omega_R$) scales as $P_{tweezer}^{1.29}$
+    (b) Raman Rabi frequency ($\Omega_R$) scales as $P_{tweezer}^{1.29}$
     and follows $1/\Delta$ with an offset.
@@
     the atom-molecule matrix element ratio.
-    Insets for (A) and (B), light shift and Raman Rabi frequency on a log-log plot
+    Insets for (a) and (b), light shift and Raman Rabi frequency on a log-log plot
     showing the power law scaling.
@@
 In order to calculate the matrix element ratio,
-we now need to extract the matrix element, $ \Omega_a $.
+we now need to extract the up leg Rabi frequency, $ \Omega_a $.
 We do this by measuring the dependencies of the Raman Rabi frequency,
@@
 due to the change in the atomic wavefunction caused by
-tighter confinement at higher power (Fig.~\ref{f-det}B).
+tighter confinement at higher power (Fig.~\ref{f-det}b).
 Thus, as discussed before, for weakly interacting particles,
@@
 Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
-which agrees with our experimental result.
+which fits well to our experimental result.
 Similar to the light shift, there is also a constant background component
@@
 The $v'=0$ component of the Raman Rabi frequency is
-$2\pi\times170.0(39) ~\mathrm{Hz\cdot mW^{-1.29}}$,
-or $2\pi \times 5.59(13)~\mathrm{kHz}$ at $15 ~\mathrm{mW}$ tweezer power.
+$2\pi\times170(4) ~\mathrm{Hz\cdot mW^{-1.29}}$,
+or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $15 ~\mathrm{mW}$ tweezer power.
 Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
-$2\pi \times 12.11(28)\mathrm{MHz}$.
-This gives a Rabi frequency, and therefore matrix element, ratio of $11.59(26)$,
+$2\pi \times 12.1(3)\mathrm{MHz}$.
+This gives a Rabi frequency, and therefore matrix element ratio of $11.6(3)$,
 which is in fact better than the theory prediction of $23.7$
 and should not cause the ratio of the Raman Rabi frequency to scattering rate
-from the $v'=0$ state to be higher than expected.
+from the $v'=0$ state to be higher than expected. \todo{split into two sentence}
 Furthermore, we measure the natural linewidth of the $v'=0$ excited state to be no larger than $20 \mathrm{MHz}$ using photoassociation (PA) spectroscopy.
@@
 Unfortunately, the background in the Raman Rabi frequency fit cancels the Rabi frequency
-for a single photon detuning that is red of the $ v' = 0 $
+for a single photon detuning that is red of the $v' = 0$ transition
 and reduces it by about $30\%$ at the current detuning.
-However, this difference is not enough to explain the over factor of $10$ discrepancy
+However, this difference is not enough to explain the greater than a factor of $10$ discrepancy
 present in the experiment.
@@
 In additional to calibrating the $\Omega_m$ and $\Omega_a$,
-the scattering rate of the molecule is also depend on the tweezer power and detuning.
-At $3\mathrm{mW}$ tweezer power, we have observed molecule lifetime as long as $1\mathrm{ms}$.
+the scattering rate of the molecule depends on the tweezer power and detuning.
+At $3\mathrm{mW}$ tweezer power, we have observed a molecule lifetime as long as $1~\mathrm{ms}$.
 However, since the technical noise that can lead to decoherence
@@
 we measure the two-body scattering rate
-without turning on the second frequency (Fig.~\ref{f-lifetime}B inset).
-The scattering rate scales as $P_{tweezer}^{2.58}$ which is inconsistent
+without turning on the second frequency (Fig.~\ref{f-lifetime}b inset).
+The scattering rate scales as $P_{\mathrm{tweezer}}^{2.58}$ which is inconsistent
 with a single photon scattering process.
@@
 if the scattering process is related to the $v'=0$ state,
-but the power scaling strongly suggests the existence of a unknown two photon scattering process.
+but the power scaling strongly suggests the existence of an unknown two-photon scattering process.
 Nevertheless, the absolute scattering rate is much lower than the total scattering rate
@@
 The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
-\todo{}B field dependency $42.17(24) kHz/G$.
+\todo{}B field dependency $42.2(2) \mathrm{kHz/G}$.
 
-In conclusion, we have formed a weakly bound NaCs molecule in an optical tweezer via an optical Raman transfer.
-A theoretical investigation including all excited states of $ c^3\Sigma^+(\Omega = 1)$, the excited atomic continuum and coupled channel ground state wavefunctions indicated better transfer efficiency using a deeply bound intermediate state and the $ \ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}} } $ hyperfine state combination.
-Using these theoretical insights, we located the weakly bound state and coherently associated the atoms into the weakly bound molecule.
-Our transfer efficiency is limited by an unknown scattering source resulting in measured scattering rates over 10 times larger than theory predictions.
-Despite this limitation, the transfer efficiency may be further improved by increasing the $ \Omega_a/\Omega_m$ ratio by exploring the possibility of driving to more deeply bound states.
-There may also be a better choice of single photon detuning to increase the Raman Rabi frequency, since our location results in about 30\% cancellation of the Raman Rabi frequency due to an offset of unknown origin.
-Nevertheless, our technique, with the right choice of parameters, can be used to form a more diverse set of molecular species, since it does not rely on a magnetic Feshbach resonance, bound states at the MHz-level or a narrow excited state.
-The formation of a weakly bound molecule is a key step in forming rovibrational ground state molecules.
-Combined with real time rearrangement \cite{Barredo2016, Endres2016}, defect free arrays of highly controlled molecules can be formed in arbitrary geometries.
-These arrays are a promising and flexible platform for quantum simulation and quantum computing applications.
+In conclusion, we have formed a weakly-bound NaCs molecule in an optical tweezer
+via an optical Raman transfer.
+A theoretical investigation including all excited states of $ c^3\Sigma^+(\Omega = 1)$,
+the excited atomic continuum, and coupled-channel ground state wavefunctions indicated
+better transfer efficiency using a deeply bound intermediate state
+and the $\ket{\uparrow_{\Na} \downarrow_{\Cs} }$ hyperfine state as the initial and final states.
+Using these theoretical insights, we located the weakly-bound state
+and coherently associated the atoms into the weakly-bound molecule.
+Our transfer efficiency is limited by an unknown scattering source
+resulting in measured scattering rates over $10$ times larger than theoretical predictions.
+Despite this limitation, the transfer efficiency may be further improved
+by increasing the ratio of the up-leg to down-leg Rabi frequency
+$\Omega_a/\Omega_m$ by exploring the possibility of
+driving to more deeply bound states.
+There may also be a better choice of single photon detuning to increase the Raman Rabi frequency,
+since our location results in about 30\% cancellation of the Raman Rabi frequency
+due to an offset of unknown origin.
+
+Our technique can be used to form a more diverse set of molecular species,
+since it does not rely on a magnetic Feshbach resonance, bound states at the MHz-level,
+or a narrow excited state. The formation of a weakly-bound molecule is a key step
+in forming rovibrational ground state molecules.
+Combined with real time rearrangement \cite{Barredo2016, Endres2016},
+defect free arrays of highly controlled molecules are a promising
+and flexible platform for quantum simulation and quantum computing applications.
 

### 2020-10-30 paper.tex
WIP: address Jons comments
* Figure label position
* Word tweak
* Legend
* Y label for wavefunction probability density

@@
 between the target weakly-bound molecular state
-and all the excited molecular intermediate states considered
-\todo{all vibrational states} is only about $0.02$,
+and all the excited molecular bound states is only about $0.02$,
 suggesting that there is significant matrix element
-between the target molecular state and the excited atomic continuum (See SM).
+between the target molecular state and the excited atomic continuum (See SM \todo{proper cite}).
 This calculation shows that the ratio of the Raman Rabi rate to scattering rate
@@
 This gives a Rabi frequency, and therefore matrix element ratio of $11.6(3)$,
-which is in fact better than the theory prediction of $23.7$
-and should not cause the ratio of the Raman Rabi frequency to scattering rate
-from the $v'=0$ state to be higher than expected. \todo{split into two sentence}
+which is in fact better than the theory prediction of $23.7$.
+Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
+from the $v'=0$ state to be higher than expected.
 Furthermore, we measure the natural linewidth of the $v'=0$ excited state to be no larger than $20 \mathrm{MHz}$ using photoassociation (PA) spectroscopy.

### 2020-10-30 plot_exp_data.jl

@@ -193,9 +193,9 @@ NaCsPlot.plot_survival_data(data_nacs_25′, scale_1, fmt="C2o", label="0.25 ms"
 plot(plot_freq .- param_1[3], model_2d.(0.25, plot_freq, (param_1,)) .* scale_1, "C2")
 xticks([-10, 0, 10])
 yticks([0.2, 0.6, 1.0])
-xlim([-13, 11])
+xlim([-14, 11])
 ylim([0.08, 1.06])
-# legend(fontsize="x-small", loc="lower right")
+legend(fontsize=13, loc="lower left", handlelength=0.6, handletextpad=0.3)
 grid()
 xlabel("Raman Detuning (kHz)", fontsize=15)
 # ylabel("Fraction of Atomic Ground State")

### 2020-10-30 plot_wavefunction.jl

@@ -40,7 +40,7 @@ plot(data31[:, 1], data31[:, 2] .* 1e4, "C3--", label="Na(1,1) Cs(3,3)")
 grid()
 xlim([0, 3080])
 ylim([0, 7.3])
-ylabel("Probability Density")
+ylabel("\$\\left|\\psi(R)\\right|^2\$")
 xlabel("R (Angstroms)")
 legend(fontsize="x-small")
 NaCsPlot.maybe_save("$(prefix)")

### 2020-10-30 paper.tex
WIP: address Jons comments

@@
 (YYC: This is why the original number quoted was zero field.
-The current number is still for zero tweezer power)})
+The current number is still for zero tweezer power), May also need to quote tweezer waist for power dependency})
   with more than $60\%$ of the molecule created in the motional ground state.
@@
 $2\pi\times140.06(8) ~\mathrm{MHz}$ for the $15 ~\mathrm{mW}$ tweezer power used above.
-This number is consistent with the value of
+This number is closed to the value of
 $2\pi\times27 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}

### 2020-10-30 paper.tex
Clearify short range wavefunction enhancement plot

@@
     Compared to other spin states with weaker interaction,
-    the wavefunction at short distance ($R<100\mathrm{\AA}$) is significantly enhanced.
+    the wavefunction at short distance ($R<100\mathrm{\AA}$, left of the dotted line)
+    is significantly enhanced.
     \label{f-theory}

### 2020-10-30 plot_wavefunction.jl

@@ -37,6 +37,7 @@ figure()
 plot(data42[:, 1], data42[:, 2] .* 1e4, "C2", label="Na(2,2) Cs(4,4)")
 plot(data32[:, 1], data32[:, 2] .* 1e4, "C1", label="Na(2,2) Cs(3,3)")
 plot(data31[:, 1], data31[:, 2] .* 1e4, "C3--", label="Na(1,1) Cs(3,3)")
+axvline(100, color="C0", ls="dotted", linewidth=5)
 grid()
 xlim([0, 3080])
 ylim([0, 7.3])

### 2020-10-30 plot_rabi_scaling.jl
Fig 4 remove inset

@@ -1,183 +1,0 @@
-#!/usr/bin/julia
-
-push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
-
-import NaCsCalc.Format: Unc, Sci
-using NaCsCalc
-using NaCsCalc.Utils: interactive
-using NaCsData
-using NaCsData.Fitting: fit_data, fit_survival, get_plot_range
-using NaCsPlot
-using PyPlot
-using DataStructures
-using LsqFit
-
-const freqs = [560 15 3.282 0.042
-               560 6 1.182 0.033
-               560 3 0.488 0.015
-
-               503 15 2.073 0.051
-               503 9 1.074 0.036
-               503 6 0.680 0.022
-               503 3 0.2544 0.0077
-
-               605 15 6.39 0.15
-               605 6 1.985 0.043
-               605 3 0.845 0.042
-
-               625 15 8.35 0.25
-               625 6 2.513 0.036
-               625 3 0.996 0.029
-               ]
-
-function model_omega(x, p)
-    return p[1] .* x.^1.29
-end
-
-broacast_array(f, x) = f(x)
-broacast_array(f, x::AbstractArray) = f.(x)
-
-# x: freq, power
-# p: offset, strength
-function gen_model(fpa0)
-    function model(xs, p)
-        function real_model(x)
-            freq, power = x
-            offset, strength = p
-            p_omega = (offset - strength / (freq - fpa0),)
-            return model_omega(power, p_omega)
-        end
-        return broacast_array(real_model, xs)
-    end
-end
-
-function gen_data(data_in)
-    freq_ids = Dict{Float64,Int}()
-    xs = Tuple{Float64,Float64,Int}[]
-    ys = Float64[]
-    uncs = Float64[]
-    idmax = 0
-    for i in 1:size(data_in, 1)
-        freq = data_in[i, 1]
-        power = data_in[i, 2]
-        freq_id = get!(freq_ids, freq) do
-            idmax += 1
-            return idmax
-        end
-        push!(xs, (freq, power, freq_id))
-        push!(ys, data_in[i, 3])
-        push!(uncs, data_in[i, 4])
-    end
[…]

### 2020-10-30 plot_res_scaling.jl

@@ -1,224 +1,0 @@
-#!/usr/bin/julia
-
-push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
-
-import NaCsCalc.Format: Unc, Sci
-using NaCsCalc
-using NaCsCalc.Utils: interactive
-using NaCsData
-using NaCsData.Fitting: fit_data, fit_survival, get_plot_range
-using NaCsPlot
-using PyPlot
-using DataStructures
-using LsqFit
-
-const freqs = [668.35 21 772.1367 0.0082
-               668.35 21 772.1376 0.0049
-               668.35 21 772.1172 0.0048
-               668.35 18 771.924 0.033
-               668.35 12 771.323 0.050
-
-               560 15 770.59417 0.00013
-               560 6 770.369081 0.000037
-               560 3 770.287276 0.000015
-
-               565 15 770.61656 0.00021
-               565 6 770.378274 0.000080
-               565 3 770.291891 0.000038
-
-               555 15 770.57744 0.00013
-               555 6 770.362165 0.000043
-               555 3 770.283665 0.000017
-
-               503 15 770.483553 0.000049
-               503 12 770.43248 0.00011
-               503 9 770.379505 0.000028
-               503 6 770.324463 0.000019
-               503 3 770.2648307 0.0000084
-
-               492 15 770.47571 0.00010
-               492 12 770.42599 0.00032
-               492 9 770.375007 0.000069
-               492 6 770.321355 0.000037
-               492 3 770.263402 0.000028
-
-               510 15 770.50117 0.00083
-               510 12 770.44659 0.00021
-               510 9 770.390205 0.000079
-               510 6 770.331510 0.000057
-               510 3 770.258511 0.000023
-
-               605 15 770.76208 0.00027
-               605 12 770.65624 0.00046
-               605 9 770.54816 0.00058
-               605 6 770.437052 0.000072
-               605 3 770.321367 0.000038
-
-               625 15 770.89410 0.00024
-               625 6 770.490130 0.000059
-               625 3 770.347812 0.000022
[…]

### 2020-10-30 plot_scaling.jl

@@ -1,0 +1,290 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival, get_plot_range
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+
+const res_freqs = [668.35 21 772.1367 0.0082
+                   668.35 21 772.1376 0.0049
+                   668.35 21 772.1172 0.0048
+                   668.35 18 771.924 0.033
+                   668.35 12 771.323 0.050
+
+                   560 15 770.59417 0.00013
+                   560 6 770.369081 0.000037
+                   560 3 770.287276 0.000015
+
+                   565 15 770.61656 0.00021
+                   565 6 770.378274 0.000080
+                   565 3 770.291891 0.000038
+
+                   555 15 770.57744 0.00013
+                   555 6 770.362165 0.000043
+                   555 3 770.283665 0.000017
+
+                   503 15 770.483553 0.000049
+                   503 12 770.43248 0.00011
+                   503 9 770.379505 0.000028
+                   503 6 770.324463 0.000019
+                   503 3 770.2648307 0.0000084
+
+                   492 15 770.47571 0.00010
+                   492 12 770.42599 0.00032
+                   492 9 770.375007 0.000069
+                   492 6 770.321355 0.000037
+                   492 3 770.263402 0.000028
+
+                   510 15 770.50117 0.00083
+                   510 12 770.44659 0.00021
+                   510 9 770.390205 0.000079
+                   510 6 770.331510 0.000057
+                   510 3 770.258511 0.000023
+
+                   605 15 770.76208 0.00027
+                   605 12 770.65624 0.00046
+                   605 9 770.54816 0.00058
+                   605 6 770.437052 0.000072
[…]

### 2020-10-30 paper.tex
Fig 4 remove inset
Update on Overleaf.

@@
 This system-independent approach can be used for creating new molecules atom-by-atom with full quantum state control.
-% and could therefore be applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
-% (also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))
-
-% This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules.
-% electronic the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering.
-Using these parameters, we demonstrate coherent association of a electronic ground-state molecule from two atoms via an optical Raman transition in an optical tweezer.
-
-% Production of ultracold molecules in optical tweezers is challenging due to their internal degrees of freedom including rotation and vibration.
-In certain molecular species with relatively closed cycling transitions, direct laser cooling remains a viable option.
-However, for many species, including NaCs, the vibrational branching ratios are unfavorable, making direct laser cooling challenging.
-In these systems, a bottom-up approach of assembling the molecule from its constituent atoms has been demonstrated both in bulk gas and in optical tweezers.
-The challenge in a bottom-up approach is the vastly different length scales between the free atoms and a ground state molecule, leading to small coupling between them.
-For atoms in the motional ground state in the tweezer, the average distance between the two atoms is about $1000a_0$.
-However, for the ground rovibrational molecule, the bond length is only around $4a_0$.
-Because of this, it is necessary to use an intermediate state with a size in between the initial and final states, and accomplish the transfer in two steps in order to increase the coupling.
-
-% The traditional choice for such an intermediate state is a weakly-bound Feshbach molecule, which can be coherently produced by ramping a magnetic field across the Feshbach resonance.
-However, this requires a suitable Feshbach resonance, which limits the generality of this technique.
-An alternative approach uses a weakly-bound ground electronic molecular state as the intermediate state (I'm wondering how we can distinguish this weakly-bound molecular state from the weakly-bound Feshbach molecule state, we can maybe specify typcial binding energies?
-"most weakly-bound state of the low field ground state electronic potential" maybe?), populated by an optical Raman transition, schematically shown in figure.
-In this scheme, a pair of Raman beams is used to drive the unbound, but confined, atoms to a bound molecular state via an excited molecular state.
-This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules.
-Such a transfer using an optical transition has been observed in previous experiments.
-However, they either require the use of a narrow optical transition which limits the generality or were driving the transition incoherently due to scattering.
-
-% the requirement of a suitable FB resonance limits its generality.
-
-% The size mismatch between the initial and final states cause a very small coupling between them,
-% which poses the biggest challenge for for coherent creation of the molecule.
-
-% Because the electronic excited state we used are generic in most diatomic molecules, this technique is general....
 
@@
 
-% In this letter, we will present our result on coherent creation of a weakly bond molecule
-% using only optical transitions on a broad optical line for the first time.
-
-% The optical transfer scheme we use is shown in figure. To drive the atoms from
-% We use an optical Raman transition to drive the system from the atomic initial state to a ground electronic molecular state.
-In order to reduce the size mismatch between the atomic and molecular states, we selected the first bound state for the 3322 spin state as our final state.
-For similar reason, the natural choice for the intermediate excited molecular state is one with highly excited motional level.However, from our calculation (and experiment?), the smaller level space for high vibrational state and the smaller detuning from the atomic threshold increases the scattering rate of the molecular state which causes a reduced Raman Rabi frequency to decoherence rate ratio and a lower transfer efficiency.
-Therefore, in our experiment, we selected the v'=0 state as the intermediate state for our Raman transition.
-
-% While optical Raman transfers of atoms to molecules utilizing an electronic excited state have been shown previously, the transfers were incoherent  where the resulting molecules were lost~\cite{Wynar2000,Rom2004}.
-% For a given excited intermediate state,
-% This can be understood by using a three level model.
-% However, we are constrained by the multi-level of molecules.
-% A key difference in molecular association via a Raman process compared to Raman transfer between hyperfine states in atoms is that the matrix elements between the ground states and the excited state are greatly unbalanced.
-In particular, the matrix element between the molecule state and the excited state, $ \Omega_m $ is much larger than the matrix element between the free atom state and the excited state, $ \Omega_a $.
-To understand the effect of this imbalance, we consider a 3 level model, and ignore the presence of multiple excited states.
-
-% The challenge of optical Raman association of molecules from atoms lies with achieving a high enough Raman Rabi frequency despite the wavefunction size mismatch between the atomic state and the excited molecular state.
-While pioneering experiments used weakly-bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
-% Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with minimal loss is the first key task.
-
-The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}a), where the initial atomic state, and the target weakly-bound molecular state are coupled to an intermediate state by two laser frequencies with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
+The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}a), where the initial atomic state, and the target weakly-bound molecular state are coupled to an intermediate state by two laser  with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
@@
 and thus can be made smaller by using deeply bound vibrational states as the intermediate level.
-% With the multiple excited vibrational states present in a molecular potential as intermediate states, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual intermediate states.
-Furthermore, for a more complete calculation, we also need to account for the effects of the excited atomic continuum, which is particularly important for the target molecular state.
-The sum of the squares of the wavefunction overlap between the target weakly-bound molecular state and all the excited molecular intermediate states considered is only about 2\%, suggesting that there is significant matrix element between the target molecular state and the excited atomic continuum.
-(See SM)
-
-% For a weakly-bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
-% Furthermore, due to similarity in wavefunction size, the weakly-bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
-The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can also be made smaller by detuning away from the dissociation threshold.
-% (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
 
@@
 As a result, we choose the $v'=0$ of $c^3\Sigma^+(\Omega = 1)$ as an intermediate state
-to drive the Raman transition. % (mention the trend, also v'=12 will work as similarly as v'=0)
+to drive the Raman transition.
 
-% higher Raman Rabi frequency at the same detuning, using a weakly-bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states.
-As a result, we use a deeply bound molecular excited state to drive the Raman transition.
-
-% (goes to SM?)
-
-% (mention scattering/lightshift depends on up/down matrix element ratio?)
-
-% In addition to the intermediate state, the choice of the initial and final states are critical for both fundamental and technical reasons.
-Thus, a small $ \Omega_m/\Omega_a $ ratio is desired to be able to drive this transition coherently at smaller detunings where the Raman Rabi frequency will be larger.
-In addition to this fundamental reason, there is also a technical advantage for having a $ \Omega_m/\Omega_a $ ratio to be as small( KW: I think small, but open question whether we should always talk about $\Omega_m/\Omega_a$ or $ \Omega_a/\Omega_m$, KN: maybe $ \Omega_a/\Omega_m$ is better because it sounds more natural that we want to make it large?
-but either way.) as possible.
-The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $.
-The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser needs to be stabilized to better than the inverse of this ratio, $ \Omega_a/\Omega_m $, to fluctuate by less than a linewidth.
-This becomes technically easier wh So en $ \Omega_m/\Omega_a $ is smaller.
-% (for our choice of states, this mean intensity fluctuation of less than 1\% or 0.1\%. KW: I mentioned this in next paragraph, does it still need to be mentioned here?)
-
-% \textcolor{blue}{Main point here.
-Small $\Omega_a/\Omega_m$ ratio can be compensated by larger detuning, but Stark shift is problematic.} \textcolor{red}{KW: I agree Stark shift limitation is definitely pretty problematic, but I would also argue that larger detuning may not be able to save the day, because of the many vibrational states in a molecular potential, the lower Raman rabi frequency which results from detuning farther and possibly running into other limitations if you have to do that, such as the background off resonant scattering rate from near threshold states or technical background scattering.} \textcolor{blue}{yes, I agree.
-I want to layout the structure ....
-motivate for the better ratio first, than talk about choosing the state.} \textcolor{red}{KW: Okay, got it.
-Makes sense.
-}
-% In addition to the intermediate state, the choice of the initial and final states is also critical.
 In addition to the intermediate state,
@@
   to account for the Stark shift caused by both beams.}. 
-% and relax the intensity stability requirement due to the AC Stark shift of the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.}
-% As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio.
-The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate.
-In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation.
-The position of the two photon resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.}.
-The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process.
-The ratio, $ \Omega_a/\Omega_m $ can be changed through the choice of initial and final states.
-% Because of the large atom and molecule wavefunction mismatch, choosing an initial atomic state that has more amplitude at smaller internuclear distance can increase the coupling $\Omega_a$.
-\textcolor{blue}{(the two sentences have the same idea.)}
-% it can be made larger by increasing the coupling of the atomic state with the excited molecular state.
 Due to the small size of the intermediate state wavefunction as compared to the trapped atoms,
@@
 the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $,
-where $ \omega_{\text{trap}} $ is the trap frequency.
+where $ \omega_{\text{trap}} $ is the trap frequency\textcolor{blue}{(cite Julienne, a pra in 90s, check ref 43?)}.
 Alternatively, one can choose an atomic pair state with a large scattering length
@@
 to identify the Rabi frequencies $\Omega_m$ to different weakly-bound spin states.
-\text{red}{A target spin state is ideally similar to the initial spin state
+\textcolor{red}{A target spin state is ideally similar to the initial spin state
   in order to minimize sensitivity to the B-field.
@@
 The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
-This spin flip selectively transfers atoms in the relative motion ground state \text{red}{I'm a little confused.
-Aren't the atoms already in the motion ground state?} \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}, and for the experiment reported here, this is 31\% of the initial population of two atoms loaded in separate optical tweezers.\text{red}{I also find this part of the sentence confusing.
+This spin flip selectively transfers atoms in the relative motion ground state \textcolor{red}{I'm a little confused.
+Aren't the atoms already in the motion ground state?} \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}, and for the experiment reported here, this is 31\% of the initial population of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.
 can you say this more concisely?}
@@
 
-The efficiency of the transfer is worse than expected from theory and arises from the ratio of the molecule scattering rate to the Rabi frequency being 10 times larger than predicted.
+The efficiency of the transfer is lower than expected from theory and arises from the ratio of the molecule scattering rate to the Rabi frequency being 10 times larger than predicted.
 Based on the discussion above, if this discrepancy arises from the $v'=0$ excited state,
@@
     the atom-molecule matrix element ratio.
-    Insets for (a) and (b), light shift and Raman Rabi frequency on a log-log plot
-    showing the power law scaling.
+    (c) Tweezer power dependency of light shift (up) and Raman Rabi frequency (down)
+    on a log-log plot showing the power law scaling.
     \label{f-det}}

### 2020-10-30 paper.tex
Show an unaddressed comment from jon in the paper

--- 2020-10-30 paper.tex
@@
 suffers from strong scattering of the nearby excited atomic continuum rendering it incoherent,
-resulting in molecule loss \todo{be more clear with "molecule loss". I think you mean:
+resulting in molecule loss \text{red}{Jon: be more clear with "molecule loss". I think you mean:
   resulting in large incoherence and loss to other molecular states.}.

### 2020-10-30 plot_atomic_loss_scaling.jl
Tweak figures

@@ -40,8 +40,9 @@ ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$")
 NaCsPlot.maybe_save("$(prefix)")
 
 figure(figsize=[4.8, 3.6])
+ax = gca()
 bg = matplotlib.patches.Rectangle((2.48, 0.31), 14.52, 39.69, facecolor="white", alpha=0.9)
-gca().add_patch(bg)
+ax.add_patch(bg)
 errorbar(rates[:, 1], rates[:, 2], rates[:, 3], fmt="C0o")
 plot(fit_gamma_a2.plotx, fit_gamma_a2.ploty, "C0")
 xscale("log")
@@ -49,9 +50,11 @@ yscale("log")
 grid()
 xlim([2.48, 17])
 ylim([0.31, 40])
-xticks([3, 6, 15], ["3", "6", "15"])
+xticks([3, 6, 12], ["3", "6", "12"])
 yticks([1, 3, 10, 30], ["1", "3", "10", "30"])
-minorticks_off()
+ax.set_xticks([3, 6, 12], minor=true)
+ax.tick_params(axis="x", which="minor", bottom=false)
+# minorticks_off()
 xlabel("Tweezer Power (mW)", fontsize=15)
 ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$", fontsize=15)
 tight_layout()

### 2020-10-30 plot_scaling.jl

@@ -213,7 +213,7 @@ end
 #                 "\$f_{PA0}=$(fit_res.uncs[2] + 288000)\$ GHz\n" *
 #                 "\$a=$(fit_res.uncs[3] * 1000)\$ kHz/mW\n" *
 #                 "\$b=$(fit_res.uncs[4])\$ MHz\$\\cdot\$GHz/mW"), fontsize="small")
-legend(loc=(0.74, 0.355), fontsize="small", handlelength=0.6, handletextpad=0.3)
+legend(loc="upper left", fontsize="small", handlelength=0.6, handletextpad=0.3)
 grid()
 xticks([-225, -175, -125, -75])
 yticks([200, 400, 600])
@@ -235,7 +235,7 @@ end
 # text(500, 5.0, ("\$\\left(a-\\dfrac{b}{f-705 GHz}\\right)\\cdot P^{1.29}\$"))
 # text(500, 2.8, ("\$a=$(fit_rabi.uncs[1] * 1000)\$ Hz/mW\$^{1.29}\$\n" *
 #               "\$b=$(fit_rabi.uncs[2])\$ kHz\$\\cdot\$GHz/mW\$^{1.29}\$"), fontsize="small")
-legend(loc=(0.74, 0.300), fontsize="small", handlelength=0.6, handletextpad=0.3)
+legend(loc="upper left", fontsize="small", handlelength=0.6, handletextpad=0.3)
 grid()
 yticks([0, 4, 8])
 xticks([-200, -160, -120, -80])
@@ -258,7 +258,7 @@ xscale("log")
 yscale("log")
 minorticks_off()
 grid()
-xticks([3, 6, 15], ["3", "6", "15"])
+xticks([3, 6, 12], ["3", "6", "12"])
 yticks([100, 400], ["100", "400"])
 ylabel("Light Shift (kHz)")
 xlim([2.5, 17])
@@ -279,7 +279,7 @@ xscale("log")
 yscale("log")
 minorticks_off()
 grid()
-xticks([3, 6, 15], ["3", "6", "15"])
+xticks([3, 6, 12], ["3", "6", "12"])
 yticks([1, 4], ["1", "4"])
 xlabel("Tweezer Power (mW)")
 ylabel("\$\\Omega_{R} (2\\pi\\cdot \\mathrm{kHz})\$")

### 2020-10-30 plot_wavefunction.jl

@@ -37,7 +37,7 @@ figure()
 plot(data42[:, 1], data42[:, 2] .* 1e4, "C2", label="Na(2,2) Cs(4,4)")
 plot(data32[:, 1], data32[:, 2] .* 1e4, "C1", label="Na(2,2) Cs(3,3)")
 plot(data31[:, 1], data31[:, 2] .* 1e4, "C3--", label="Na(1,1) Cs(3,3)")
-axvline(100, color="C0", ls="dotted", linewidth=5)
+axvline(100, color="C0", ls="dashed", linewidth=3)
 grid()
 xlim([0, 3080])
 ylim([0, 7.3])

### 2020-10-30 plot_atomic_loss_scaling.jl
More plot tickmarks

@@ -35,6 +35,9 @@ yscale("log")
 grid()
 xticks([3, 4, 6, 8, 12], ["3", "4", "6", "8", "12"])
 yticks([1, 3, 10, 30], ["1", "3", "10", "30"])
+ax = gca()
+ax.xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
+ax.set_xticks(3:16, minor=true)
 xlabel("Tweezer Power (mW)")
 ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$")
 NaCsPlot.maybe_save("$(prefix)")
@@ -52,9 +55,8 @@ xlim([2.48, 17])
 ylim([0.31, 40])
 xticks([3, 6, 12], ["3", "6", "12"])
 yticks([1, 3, 10, 30], ["1", "3", "10", "30"])
-ax.set_xticks([3, 6, 12], minor=true)
-ax.tick_params(axis="x", which="minor", bottom=false)
-# minorticks_off()
+ax.xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
+ax.set_xticks(3:16, minor=true)
 xlabel("Tweezer Power (mW)", fontsize=15)
 ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$", fontsize=15)
 tight_layout()

### 2020-10-30 plot_scaling.jl

@@ -216,8 +216,8 @@ end
 legend(loc="upper left", fontsize="small", handlelength=0.6, handletextpad=0.3)
 grid()
 xticks([-225, -175, -125, -75])
-yticks([200, 400, 600])
-ylim([43, 798])
+yticks([0, 200, 400, 600])
+ylim([0, 790])
 xlabel("Detuning (GHz)")
 ylabel("Light Shift (kHz)")
 NaCsPlot.maybe_save("$(prefix)_light_shift")
@@ -237,7 +237,7 @@ end
 #               "\$b=$(fit_rabi.uncs[2])\$ kHz\$\\cdot\$GHz/mW\$^{1.29}\$"), fontsize="small")
 legend(loc="upper left", fontsize="small", handlelength=0.6, handletextpad=0.3)
 grid()
-yticks([0, 4, 8])
+yticks([0, 2, 4, 6, 8])
 xticks([-200, -160, -120, -80])
 ylim([0, 9.7])
 xlabel("Detuning (GHz)")
@@ -256,16 +256,16 @@ errorbar(plot2.x[3], (plot2.y[3] .- fit_res.param[1]) .* 1000, plot2.unc[3] .* 1
 plot(plot2.plotx, (plot2.ploty .- fit_res.param[1]) .* 1000, "k")
 xscale("log")
 yscale("log")
-minorticks_off()
+# minorticks_off()
 grid()
 xticks([3, 6, 12], ["3", "6", "12"])
-yticks([100, 400], ["100", "400"])
+yticks([100, 200, 400], ["100", "200", "400"])
 ylabel("Light Shift (kHz)")
 xlim([2.5, 17])
 ylim([77, 440])
 setp(ax1.get_xticklabels(), visible=false)
-setp(ax1.get_xticklabels(), visible=false)
 ax1.tick_params(axis="x", length=0)
+ax1.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 
 ax2 = fig.add_subplot(212)
 subplots_adjust(hspace=0.0)
@@ -277,10 +277,13 @@ errorbar(plot2.x[3], plot2.y[3], plot2.unc[3], fmt="C2o")
 plot(plot2.plotx, plot2.ploty, "k")
 xscale("log")
 yscale("log")
-minorticks_off()
+# minorticks_off()
 grid()
 xticks([3, 6, 12], ["3", "6", "12"])
[…]

### 2020-10-30 plot_scaling.jl
More fix of plot ticks

@@ -215,7 +215,7 @@ end
 #                 "\$b=$(fit_res.uncs[4])\$ MHz\$\\cdot\$GHz/mW"), fontsize="small")
 legend(loc="upper left", fontsize="small", handlelength=0.6, handletextpad=0.3)
 grid()
-xticks([-225, -175, -125, -75])
+xticks([-200, -160, -120, -80])
 yticks([0, 200, 400, 600])
 ylim([0, 790])
 xlabel("Detuning (GHz)")
@@ -264,8 +264,10 @@ ylabel("Light Shift (kHz)")
 xlim([2.5, 17])
 ylim([77, 440])
 setp(ax1.get_xticklabels(), visible=false)
-ax1.tick_params(axis="x", length=0)
+# ax1.tick_params(axis="x", length=0)
+ax1.set_xticks(3:16, minor=true)
 ax1.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
+ax1.xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 
 ax2 = fig.add_subplot(212)
 subplots_adjust(hspace=0.0)

### 2020-10-30 paper.tex
Typo and todo

--- 2020-10-30 paper.tex
@@
 (YYC: This is why the original number quoted was zero field.
-The current number is still for zero tweezer power), May also need to quote tweezer waist for power dependency})
+The current number is still for zero tweezer power), May also need to quote tweezer waist for power dependency}\todo{})
   with more than $60\%$ of the molecule created in the motional ground state.
@@
 suffers from strong scattering of the nearby excited atomic continuum rendering it incoherent,
-resulting in molecule loss \todo{be more clear with "molecule loss". I think you mean:
-  resulting in large incoherence and loss to other molecular states.}.
+resulting in molecule loss
+\textcolor{red}{Jon: be more clear with "molecule loss". I think you mean:
+  resulting in large incoherence and loss to other molecular states.}\todo{}.
 This scattering is proportional to $1/\delta_{thresh}^2$,
@@
   This reduces the intensity stability requirement to $5\%$
-  instead of $0.3\%$ which is typical for other states.}
+  instead of $0.3\%$ which is typical for other states.}\todo{}
 In addition to the increased atomic coupling, $ \Omega_a $,
@@
 Aren't the atoms already in the motion ground state?} \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}, and for the experiment reported here, this is 31\% of the initial population of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.
-can you say this more concisely?}
+can you say this more concisely?}\todo{}
 % The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

### 2020-11-02 paper.tex
Update on Overleaf.

@@
 With these considerations, using a weakly-bound excited state as the intermeidate state
-suffers from strong scattering of the nearby excited atomic continuum rendering it incoherent,
-resulting in molecule loss
-\textcolor{red}{Jon: be more clear with "molecule loss". I think you mean:
-  resulting in large incoherence and loss to other molecular states.}\todo{}.
+suffers from strong scattering of the nearby excited atomic continuum, resulting in large incoherence and loss to other molecular states.
 This scattering is proportional to $1/\delta_{thresh}^2$,
@@
 the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $,
-where $ \omega_{\text{trap}} $ is the trap frequency\textcolor{blue}{(cite Julienne, a pra in 90s, check ref 43?)}.
+where $ \omega_{\text{trap}} $ is the trap frequency\cite{Mies2000}.
 Alternatively, one can choose an atomic pair state with a large scattering length
@@
 For the target molecular state, we perform coupled-channel calculations
-to identify the Rabi frequencies $\Omega_m$ to different weakly-bound spin states.
-\textcolor{red}{A target spin state is ideally similar to the initial spin state
-  in order to minimize sensitivity to the B-field.
-  We find a target spin state predominantly in the initial spin state
-  that also has the advantage of having a reduced sensitivity
-  to laser intensity noise because of a larger $\Omega_a/\Omega_b$ as compared to other states.
-  This reduces the intensity stability requirement to $5\%$
-  instead of $0.3\%$ which is typical for other states.}\todo{}
-In addition to the increased atomic coupling, $ \Omega_a $,
-coupled channel calculations show that the target molecular state
-that is predominantly in this spin combination also has reduced coupling, $ \Omega_m $,
-with the intermediate state when compared to bound states of the other stable spin combinations
+to identify the Rabi frequencies $\Omega_m$ to different weakly-bound spin states. The target's spin state is ideally similar to the initial spin state in order to minimize sensitivity to the B-field.
+  % We find a target spin state predominantly in the initial spin state
+  %that also has the advantage of having a reduced sensitivity
+  %to laser intensity noise because of a larger %$\Omega_a/\Omega_b$ as compared to other states.
+  %This reduces the intensity stability requirement to $5\%$
+  %instead of $0.3\%$ which is typical for other states.
+% In addition to the increased atomic coupling, $ \Omega_a $,
+Coupled channel calculations show that this target molecular state also has reduced Rabi frequency, $ \Omega_m $,
+with the intermediate state when compared to bound states of the other stable spin combinations, thus further increasing the $\Omega_a/\Omega_m$ ratio.
 % $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
-Therefore, using an initial $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination
+Using an initial $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination
 results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003
 with the other combinations,
-and thus only an required intensity stability of 5\% instead of 0.3\%.
+and thus requiring an intensity stability of 5\% instead of 0.3\%.
 % Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
@@
 The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
-This spin flip selectively transfers atoms in the relative motion ground state \textcolor{red}{I'm a little confused.
-Aren't the atoms already in the motion ground state?} \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}, and for the experiment reported here, this is 31\% of the initial population of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.
-can you say this more concisely?}\todo{}
+This spin flip selectively transfers atoms in the relative motion ground state, removing any initial hot atom background from imperfect cooling \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}.
+For the experiment reported here, 31\% of our initial two atom population is successfully transferred.
+% of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
 % The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..
@@
 The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time.
+Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50 ~\mathrm{GHz}$ to filter the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
+We observed a reduction of the scattering rate by a factor of $2$ due to suppression of the broadband amplified spontaneous emission (ASE) from the laser that couples to other excited states.
 %to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
@@
 % In addition to reducing the number of laser beams during the Raman transition,
-Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50 ~\mathrm{GHz}$ to filter the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
-We observed a reduction of the scattering rate by a factor of $2$ due to suppression of the broadband amplified spontaneous emission (ASE) from the laser that couples to other excited states.
 
@@
 In order to verify whether any one of these known sources are the origin of the discrepancy,
-we measured the Raman resonance as a function of the tweezer power and single photon frequency.
+we measured the properties of the Raman resonance as a function of the tweezer power and single photon frequency.
 These dependencies allow us to experimentally determine the matrix elements,
@@
 $2\pi\times140.06(8) ~\mathrm{MHz}$ for the $15 ~\mathrm{mW}$ tweezer power used above.
-This number is closed to the value of
+This number is close to the value of
 $2\pi\times27 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
@@
 In order to calculate the matrix element ratio,
-we now need to extract the up leg Rabi frequency, $ \Omega_a $.
+we now need to extract the Rabi frequency between the atomic state and the intermediate state, $ \Omega_a $.
 We do this by measuring the dependencies of the Raman Rabi frequency,
@@
 tighter confinement at higher power (Fig.~\ref{f-det}b).
-Thus, as discussed before, for weakly interacting particles,
+As discussed before, for weakly interacting particles,
 $\Omega_a$ scales as $ \omega_{\text{trap}}^{3/4}$ or $P^{0.375}$.
 However, due to the strong interaction between the two atoms, this approximation breaks down.
-Instead, coupled-channel calculation shows that the scaling
+Instead, coupled-channel calculations show that the scaling
 is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
@@
 which fits well to our experimental result.
-Similar to the light shift, there is also a constant background component
-and a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$.
+Similar to the light shift, the Raman Rabi frequency's detuning dependence is determined by a constant background component and
+a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$.
 The $v'=0$ component of the Raman Rabi frequency is
@@
 or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $15 ~\mathrm{mW}$ tweezer power.
-Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
+Together with the $\Omega_m$ measured above, the matrix element, $ \Omega_a $, is
 $2\pi \times 12.1(3)\mathrm{MHz}$.
@@
 we now consider the background effects from other states with larger single photon detuning.
-Unfortunately, the background in the Raman Rabi frequency fit cancels the Rabi frequency
-for a single photon detuning that is red of the $v' = 0$ transition
-and reduces it by about $30\%$ at the current detuning.
+In the Raman Rabi frequency fit, the fitted background is of an opposite sign from the Raman Rabi frequency for single photon detunings red of the $v' = 0 $ transition.
+Thus, this background reduces the Raman Rabi frequency by about $30\%$ at the current detuning.
 However, this difference is not enough to explain the greater than a factor of $10$ discrepancy
 present in the experiment.
-The same offset will increase the Rabi frequency for blue detuning,
-but we have observed additional excited states at slightly higher frequencies
+Due to the change in sign of the Raman Rabi frequency, the same background will increase the Raman Rabi frequency for detunings blue of the $v' = 0$ transition, which increases the Raman Rabi frequency.
+Unfortunately, we have observed additional nearby excited states at higher frequencies
 which prevent the blue side of the transition to be usable for the Raman transition.
@@
 is not fully characterized in our experiment,
-we are unable to further identify the source of the discrepancy based on this dependency.
+we are unable to further identify the sources of the measured scattering rate based on our measured detuning and power dependencies.
+%the discrepancy based on the dependency.
 
@@
 but the power scaling strongly suggests the existence of an unknown two-photon scattering process.
-Nevertheless, the absolute scattering rate is much lower than the total scattering rate
-and is not the limiting factor in our experiment.
+Nevertheless, the absolute scattering rate from the atomic state is much lower than the total scattering rate
+and is not the limiting factor in this experiment.
 

### 2020-11-03 paper.tex
Update on Overleaf.

@@
 results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003
-with the other combinations,
-and thus requiring an intensity stability of 5\% instead of 0.3\%.
+with the other combinations, and thus relaxing the intensity stability requirement to the few percent level.
 % Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
 % Thus, we choose the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination.
-\textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
+% \textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
 

### 2020-11-03 sm.tex
Update on Overleaf.

--- 2020-10-30 paper.tex
@@
-\documentclass[aps,prl,twocolumn,superscriptaddress]{revtex4-1}
-% \documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4-1}
+\documentclass[aps,secnumarabic,amsmath,amssymb,superscriptaddress]{revtex4}
 \usepackage{amsmath}
@@
 \usepackage[colorlinks=true]{hyperref}
-\usepackage{footmisc}
-\usepackage{braket}
+\usepackage{listings}
 
@@
 \newcommand{\dprod}{\displaystyle\prod}
-\newcommand{\dlim}{\displaystyle\lim}
+\newcommand{\dlim}{\dispqlaystyle\lim}
 \newcommand{\dint}{\displaystyle\int}
@@
 \newcommand{\eff}{ef\! f}
-\newcommand{\Na}{\mathrm{Na}}
-\newcommand{\Cs}{\mathrm{Cs}}
-\newcommand{\fxnote}[1]{{\textbf{[#1]}}}
-
-\newcommand{\todo}[1]{}
-
-\ifpdf
-% Ensure reproducible output
-\pdfinfoomitdate=1
-\pdfsuppressptexinfo=-1
-\pdftrailerid{}
-\hypersetup{
-  pdfcreator={},
-  pdfproducer={}
-}
-\fi
 
@@
 
+% Add S1 to bibliography
+\bibliographystyle{apsrev4-2}
+\renewcommand*{\citenumfont}[1]{S#1}
+\renewcommand*{\bibnumfmt}[1]{[S#1]}
+
+%Add S to labels
+\setcounter{table}{0}
+\renewcommand{\thetable}{S\arabic{table}}%
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{S\arabic{figure}}%
+\renewcommand{\thepage}{S\arabic{page}}  
+\renewcommand{\thesection}{S\arabic{section}}   
+\renewcommand{\theequation}{S.\arabic{equation}}
+
 \begin{document}
-\title{Coherent optical association of a single molecule}
+\title{Coherent optical association of a single molecule -- Supplemental material}
 \author{Yichao~Yu}
@@
 
-\begin{abstract}
-  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
-  through an optical Raman transition without the use of a Feshbach resonance.
-  The Raman scheme uses a deeply bound electronic excited intermediate state
-  to achieve a large transition dipole moment while reducing the photon scattering.
-  Starting from two atoms in their relative motional ground state,
-  we achieve an optical transfer efficiency of $69\%$.
-  The molecule has a binding energy of $770.20052(2) \mathrm{MHz}$ at $8.8~\mathrm{G}$ (\textcolor{red}{Unresolved comment from Jon: with so many digits on the resonance frequency, we may need to mention more digits on the B field number and/or also state the tweezer power.
-We can state the tweezer power for where we measure it, but the transmission through the objective, etc.
-I believe is only estimated.
-(YYC: This is why the original number quoted was zero field.
-The current number is still for zero tweezer power), May also need to quote tweezer waist for power dependency}\todo{})
-  with more than $60\%$ of the molecule created in the motional ground state.
-  This technique does not rely on narrow excited state lines or Feshbach resonances
-  and will allow a wider range of molecular species to be assembled atom-by-atom.
-\end{abstract}
-
 \maketitle
 
-% Introduction
+\section{3 Level Raman Transfer with Cross Coupling}
 
-% 1.
-we want to have a diverse species to tailor to different applications including precision measurements and quantum engineering.
-2.
-for the technique of associating atoms to form molecules, but so far all has been done with Feshbach association (before STIRAP), or in the case of Sr2, a narrow excited state.
-Previous work on near-threshold Raman transfer has been incoherent.
-% (suggested referees: Florian Shreck and Immanual Bloch, Tanya, Deep Gupta, DeMille)
+Our Raman transfer scheme differs from typical Raman transfers, for instance between hyperfine states in atoms, in two key ways.
 
-% Trapped neutral molecules, assembled in an array of optical tweezers, are a promising platform to study quantum information and quantum simulation. (more detail to add here about applications?).
+Test Reference\cite{Liu2019}
 
-Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018, PhysRevLett.119.153001, hudson2011}, quantum simulations~\cite{Yao2018, Wall2015, Sundar2018, wall2015realizing}, quantum information processing~\cite{DeMille2002, Ni2018, Hudson2018, Lin2019}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111,Segev2019}.
-While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016,Anderegg2018, Mitra1366, PhysRevX.10.021049, PhysRevLett.121.013202, PhysRevLett.120.123201}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020,He331}  have been achieved through the association of ultracold atoms.
-% (any place to cite  molecular ion work?)
-% Citations are not complete. Add them as you see fit.
-
-Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques that have been developed for atoms.
-Associating atoms into deeply-bound molecules is challenging because of the small wavefunction overlap between the free-atom and molecular state and the release of a large amount of binding energy.
-A two-step approach has been demonstrated to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state releasing the binding energy via stimulated emission~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
-So far, most molecular association has been achieved for bialkali molecules by magnetoassociation using a magnetic Feshbach scattering resonance.
-The only exceptions are Sr$_2,$ where narrow linewidth ($\sim 20 ~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly-bound molecules with a couple MHz binding energy exists~\cite{He331}.
-With these requirements, dimers between alkali atoms and non-magnetic atoms, or molecules involving atoms without narrow intercombination lines remain difficult to associate.
-% These requirements limit the generality of previous association techniques.
-% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques.
-% to more diverse species.
-
-Here, we demonstrate coherent association of an atom pair to a weakly-bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}a.
-The scheme does not rely on a Feshbach resonance, few MHz level bound states, or a narrow excited state.
-The resulting single molecule is in a well-defined internal quantum state and predominately in its motional ground state.
-A vibrational state of the electronic excited state $c^3\Sigma^+(\Omega = 1)$ is used as the intermediate state in the Raman scheme, and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation.
-To further reduce the photon scattering and sensitivity to laser intensity noise, we choose the initial and final state to balance the two Rabi frequencies as much as possible.
-This system-independent approach can be used for creating new molecules atom-by-atom with full quantum state control.
-
-\begin{figure*}
-  \includegraphics[width=\textwidth]{fig1.pdf}
-  \caption{Optical creation of single molecule from single atoms in tweezer.
-    (a) Schematics of the optical transition from an atom pair to a weakly-bound molecule.
-    The initial state is the relative motional ground state between the two atoms
-    and the final state is the first molecular bound state.
-    The transition is driven by a pair of laser frequencies matching the binding energy
-    of the molecule.
-    The lasers are detuned from an excited molecular state in the $c^3\Sigma$ potential
-    by $\Delta$ in order to suppress the scattering during the transfer.
-    (b) Comparison between using a weakly-bound and a deeply bound excited state
-    as intermediate state for the Raman transition.
-    The deeply bound excited state (upper half $v'=0$)
-    has a smaller Raman Rabi frequency ($\Omega_{R}$)
-    compared to the weakly-bound excited state (lower half $v'=63$) at a given detuning.
-    However, the scattering rate ($\Gamma_{s}$) is also much lower,
-    which results in a larger Raman Rabi frequency to scattering rate ratio.
-    (c) Enhancement of short range wavefunction.
-    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
-    comparable to the axial trapping frequency.
-    This causes a significant change in the relative wavefunction especially at short
-    intranuclear distance ($R$).
-    Compared to other spin states with weaker interaction,
-    the wavefunction at short distance ($R<100\mathrm{\AA}$, left of the dotted line)
-    is significantly enhanced.
-    \label{f-theory}
-  }
-\end{figure*}
-
-The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}a), where the initial atomic state, and the target weakly-bound molecular state are coupled to an intermediate state by two laser  with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
-%(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
-The transfer Raman Rabi Rate, $\Omega_R=\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_s$
-% $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
-~\cite{Wineland2003}.
-Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
-due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
-and therefore the scattering is predominantly from the target molecular state.
-Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally.
-Thus, the scattering is given by $ \Gamma_s=\Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power.
-Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
-The ratio between the Raman Rabi frequency and the scattering rate is therefore $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $.
-%, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
-To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred.
-%However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
-
-Early experiments used weakly-bound excited states as the intermediate state
-in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
-However, for a complete picture, the many excited vibrational states in a molecular potential
-as well as the excited atomic continuum need to be considered.
-The total scattering rate and Raman Rabi rate become a sum of the scattering rates
-and Raman Rabi rates over all possible intermediate states.
-With these considerations, using a weakly-bound excited state as the intermeidate state
-suffers from strong scattering of the nearby excited atomic continuum rendering it incoherent,
-resulting in molecule loss
-\textcolor{red}{Jon: be more clear with "molecule loss". I think you mean:
-  resulting in large incoherence and loss to other molecular states.}\todo{}.
-This scattering is proportional to $1/\delta_{thresh}^2$,
-where $\delta_{thresh}$ is the detuning from the dissociation threshold,
-and thus can be made smaller by using deeply bound vibrational states as the intermediate level.
-
-To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency
-and scattering rate at different detunings from the atomic threshold
-taking into account of all states of
-the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
-and the continuum~\cite{Liu2017}.
-The excited atomic continuum is particularly important for the target molecular state.
-The sum of the squares of the wavefunction overlap
-between the target weakly-bound molecular state
-and all the excited molecular bound states is only about $0.02$,
-suggesting that there is significant matrix element
-between the target molecular state and the excited atomic continuum (See SM \todo{proper cite}).
-This calculation shows that the ratio of the Raman Rabi rate to scattering rate
-can be made larger for more deeply bound states compared to weakly-bound states
-at a cost of a smaller Raman Rabi frequency
-(Fig.~\ref{f-theory}b, full result in SM \todo{proper cite})
-As a result, we choose the $v'=0$ of $c^3\Sigma^+(\Omega = 1)$ as an intermediate state
-to drive the Raman transition.
-
-In addition to the intermediate state,
-choosing an initial and a final state for a large $ \Omega_a/\Omega_m $ ratio
-maximizes Raman Rabi coupling at a given detuning.
-Furthermore, a larger ratio also relaxes the intensity stability requirement,
-because this is also the ratio between the Raman Rabi coupling
-and the AC Stark shift of the molecular state, $\Omega_m^2 / 2\Delta$
-\footnote{There is an additional factor of 2, with both beams at equal power,
-  to account for the Stark shift caused by both beams.}.
-Due to the small size of the intermediate state wavefunction as compared to the trapped atoms,
-the coupling $\Omega_a$ is approximately proportional to
-the value of the relative atomic wavefunction at short distance
-within the molecular potential.
-To increase the amplitude within the molecular potential,
-one can increase the external confinement of atom pairs.
-Using a harmonic oscillator approximation,
-the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $,
-where $ \omega_{\text{trap}} $ is the trap frequency\textcolor{blue}{(cite Julienne, a pra in 90s, check ref 43?)}.
-Alternatively, one can choose an atomic pair state with a large scattering length
-(positive or negative).
-For these states, the phase shift in the relative wavefunction
-between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}c).
-% The increase in the coupling is proportional to (quote/cite Olive's equation?).
-For our system of Na and Cs atoms,
-we choose a spin state combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=3,m_F=3}_{\Cs}$ that has a large and negative scattering length of
-$ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0$~\cite{Hood2019}.
-All other stable spin combinations give smaller scattering lengths ($<~50~a_0$).
-% We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\Cs}} = \ket{F=4,m_F=4}_{\Cs}, \ket{\downarrow_{\Cs}} = \ket{F=3,m_F=3}_{\Cs}, \ket{\uparrow_{\Na}} = \ket{F=2,m_F=2}_{\Na}, $ and $ \ket{\downarrow_{\Na}} = \ket{F=1,m_F=1}_{\Na}$.
-Among the stable spin combinations, $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\Na} \downarrow_{\Cs}} $ combination has a large and negative scattering length of $ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
-For the target molecular state, we perform coupled-channel calculations
-to identify the Rabi frequencies $\Omega_m$ to different weakly-bound spin states.
-\textcolor{red}{A target spin state is ideally similar to the initial spin state
-  in order to minimize sensitivity to the B-field.
-  We find a target spin state predominantly in the initial spin state
-  that also has the advantage of having a reduced sensitivity
-  to laser intensity noise because of a larger $\Omega_a/\Omega_b$ as compared to other states.
-  This reduces the intensity stability requirement to $5\%$
-  instead of $0.3\%$ which is typical for other states.}\todo{}
-In addition to the increased atomic coupling, $ \Omega_a $,
-coupled channel calculations show that the target molecular state
-that is predominantly in this spin combination also has reduced coupling, $ \Omega_m $,
-with the intermediate state when compared to bound states of the other stable spin combinations
-% $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
-Therefore, using an initial $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination
-results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003
-with the other combinations,
-and thus only an required intensity stability of 5\% instead of 0.3\%.
-% Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
-% Thus, we choose the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination.
-\textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
-
-% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
-\begin{figure}[ht!]
-  \includegraphics[width=0.48\textwidth]{fig2.pdf}
-  \caption{
-    (a) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
-    The tweezer and Raman beam is focused through an objective to define the location of the
-    atoms and molecule.
-    We use a bias B field of $B_0=8.8 G$ alone the tweezer polarization
-    to define the quantization axis.
-    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
-    (b) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
-    When driving the Raman transition, the up leg power is smoothly ramped down and
-    the down leg power ramped up over $10\mu s$ while maintaining the total power of the tweezer.
-    This minimizes the heating on the atoms due to power fluctuation while maximizes the time
-    with maximum Raman Rabi frequency when the up and down leg powers are equal.
-    (c) Raman pulse time scan on resonance.
-    A decaying Rabi oscillation can be observed proving the coherence of
-    the Raman transfer process.
-    Inset: Raman detuning scans at different times showing the resonance frequency.
-    This is also fitted to a model of Raman transition
-    with loss on the atom and molecule state and is used to determine
-    both the Raman Rabi frequency and the loss rates.
-    \label{f-raman}}
-\end{figure}
-
-%% Preparation
-Experimentally, we first prepare two atoms in a well-defined external and internal quantum state using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}.
-In brief, the experimental cycle begins by stochastically loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into separate optical tweezers.
-The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom to be able to post select the experimental result on the initial loading condition.
-Raman sideband cooling is then applied to cool both atoms simultaneously into the 3-dimensional motional ground state of their optical tweezers.
-After cooling, the Na and Cs atoms are in a spin state of $\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=4,m_F=4}_{\Cs} $ %and are merged into the same tweezer~\cite{Liu2019}.
-%The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $.
-which has a small scattering length. The small two atom interaction allows the merging of the two atoms to be done with minimum pertubation so that they remain in the motional ground state.
-
-% After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
-Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination to use as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7 \mathrm{kHz}$ interaction shift~\cite{Hood2019}.
-%using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\Cs}}$ state.
-The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
-This spin flip selectively transfers atoms in the relative motion ground state \textcolor{red}{I'm a little confused.
-Aren't the atoms already in the motion ground state?} \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}, and for the experiment reported here, this is 31\% of the initial population of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.
-can you say this more concisely?}\todo{}
-% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..
-
-%% Transfer scheme
-% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
-To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}a).
-The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time.
-%to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
-The pulse sequence is shown in Fig.~\ref{f-raman}b. %Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal.
-% In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse.
-The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time.
-After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged.
-Both frequencies are kept on for a specified duration before the process is reversed and the tweezer returns to a single frequency.
-% In addition to reducing the number of laser beams during the Raman transition,
-Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50 ~\mathrm{GHz}$ to filter the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
-We observed a reduction of the scattering rate by a factor of $2$ due to suppression of the broadband amplified spontaneous emission (ASE) from the laser that couples to other excited states.
-
-% found the spectral purity of the laser for Raman beams to be critical for achieving a higher transfer efficiency.
-% The tweezer/Raman beams are generated by a fiber amplifier seeded with a $1037 \mathrm{nm}$ external cavity diode laser.
-% by amplifying a $1037 \mathrm{nm}$ external cavity diode laser (ECDL) with a fiber amplifier,
-% The diode laser produces the desired frequency on top of a broad band amplified spontaneous emission (ASE).
-We use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the laser spectrum and found it reduces the scattering rate by at least a factor of $2$
-% for a particular single photon detuning.
-
-% in addition to the desired frequency. This increases the scattering rate due to coupling to other excited states.
-
-\begin{figure}[t!]
-  \includegraphics[width=0.48\textwidth]{fig3.pdf}
-  \caption{
-    (a) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
-    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
-    The lifetime is consistent with the $0.199(9) \mathrm{ms}$
-    measured from the Raman transition data.
-    The oscillation in the survival is the result of the interference
-    between the two Raman pulses with incomplete transfer.
-    (b) Two-body atom lifetime of $5(1) \mathrm{ms}$
-    in $15 \mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
-    This is used to improve the fitting of the Raman transfer data.
-    Inset: Atomic scattering rate scales as $P_{tweezer}^{2.58}$ on a log-log scale,
-    this is consistent with a two photon scattering process.
-    We have not measured a clear dependency of the loss rate on the tweezer detuning.
-    \label{f-lifetime}}
-\end{figure}
-
-%% Experiment condition/resonance
-
-We choose the tweezer frequency to be far detuned ($145 ~\mathrm{GHz}$) from the $v' = 0$ line, and guided by coupled channel calculations,
-we locate the Raman resonance for the atom to molecule transition at
-$770.57150(9) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}c inset)
-with $15 ~\mathrm{mW}$ tweezer power.
-% (We can maybe add information about the prediction here?)
-%% Prediction
-% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state.
-The ground molecular state has not been observed previously in experimentally.
-Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state.
-Theory prediction was at $770.1 MHz$.
-% The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
-% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence.
-% directly detected by our imaging step.
-The molecular state is dark to the imaging step,
-so successful transfer of the atoms to the molecular state will be detected as loss.
-We observed a Fourier limited linewidth which is evidence of a coherent transfer.
-In order to verify the coherence of the transfer directly,
-we fix the two photon detuning on resonance and scan the pulse time.
-Fig.~\ref{f-raman}c shows the observed coherent Rabi oscillation between the atomic and molecular states.
-Fitting the data with a decaying Rabi oscillation suggests that
-$69\%$ of initial ground state atoms are transferred into the molecular state.
-This transfer efficiency is mainly limited by the molecular lifetime
-which can be measured directly by preparing the molecule with a $\pi $ pulse
-and then using a second $\pi$ pulse to dissociate the molecule back to atoms
-after a variable wait time (Fig.~\ref{f-lifetime}a).
-The result shows a molecular lifetime of $0.199(9) \mathrm{ms}$
-consistent with the decay of Rabi oscillation.
-We obtain the Raman Rabi frequency by fitting our measurements to a model
-that includes a Raman Rabi frequency and
-a finite lifetime for the molecular state (Fig.~\ref{f-raman}c and inset).
-We account for the effect of atomic state loss by measuring the one and
-two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}b)
-without turning on the second frequency.
-The fit shows that we have a Raman Rabi frequency of $2\pi\times3.28(4) ~\mathrm{kHz}$.
-
-The efficiency of the transfer is lower than expected from theory and arises from the ratio of the molecule scattering rate to the Rabi frequency being 10 times larger than predicted.
-Based on the discussion above, if this discrepancy arises from the $v'=0$ excited state,
-it can be either due to a high ratio of $\Omega_m / \Omega_a$ or a large $\Gamma_e$.
-Additionally, coupling to other excited states can also add an offset to
-both the Raman Rabi frequency and the scattering rate
-which can affect the scattering rate to Rabi frequency ratio.
-
-In order to verify whether any one of these known sources are the origin of the discrepancy,
-we measured the Raman resonance as a function of the tweezer power and single photon frequency.
-These dependencies allow us to experimentally determine the matrix elements,
-$ \Omega_a $, $\Omega_m $ and how much of the scattering, Stark shift,
-or Raman Rabi frequency comes from the $ v' = 0$ intermediate state.
-
-First we look at the change in resonance frequency.
-As a function of the tweezer power,
-we observe the expected linear dependency on the resonance frequency
-caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}a).
-When we vary the tweezer frequency around the $v'=0$ intermediate state,
-we can further observe a $1/\Delta$ component
-and a constant background in the experimentally explored region.
-The background is caused by coupling to other excited states that are further away in energy.
-The $1/\Delta$ component, however, is due to the coupling between the molecular state
-and the $v'=0$ intermediate state.
-From this measurement, we can extract a $\Omega_m$ of
-$2\pi\times36.16(2) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or
-$2\pi\times140.06(8) ~\mathrm{MHz}$ for the $15 ~\mathrm{mW}$ tweezer power used above.
-This number is closed to the value of
-$2\pi\times27 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
-
-\begin{figure*}
-  \includegraphics[width=\textwidth]{fig4.pdf}
-  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
-    The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6\mathrm{GHz}$.
-    (a) The light shift of the Raman resonance scales as $P_{tweezer}$
-    and follows $1/\Delta$ with an offset.
-    The fit also includes a small term that is proportional to $P_{tweezer}^2$
-    which is caused by the effective magnetic field generated by the tweezer which is
-    perpendicular to the real magnetic field.
-    (b) Raman Rabi frequency ($\Omega_R$) scales as $P_{tweezer}^{1.29}$
-    and follows $1/\Delta$ with an offset.
-    From these results we can confirm the theory prediction of
-    the atom-molecule matrix element ratio.
-    (c) Tweezer power dependency of light shift (up) and Raman Rabi frequency (down)
-    on a log-log plot showing the power law scaling.
-    \label{f-det}}
-\end{figure*}
-
-In order to calculate the matrix element ratio,
-we now need to extract the up leg Rabi frequency, $ \Omega_a $.
-We do this by measuring the dependencies of the Raman Rabi frequency,
-which depends on both $\Omega_m$ and $\Omega_a$.
-The Raman Rabi frequency shows a non-linear dependency on the tweezer power
-due to the change in the atomic wavefunction caused by
-tighter confinement at higher power (Fig.~\ref{f-det}b).
-Thus, as discussed before, for weakly interacting particles,
-$\Omega_a$ scales as $ \omega_{\text{trap}}^{3/4}$ or $P^{0.375}$.
-However, due to the strong interaction between the two atoms, this approximation breaks down.
-Instead, coupled-channel calculation shows that the scaling
-is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
-Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
-which fits well to our experimental result.
-Similar to the light shift, there is also a constant background component
-and a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$.
-The $v'=0$ component of the Raman Rabi frequency is
-$2\pi\times170(4) ~\mathrm{Hz\cdot mW^{-1.29}}$,
-or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $15 ~\mathrm{mW}$ tweezer power.
-Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
-$2\pi \times 12.1(3)\mathrm{MHz}$.
-This gives a Rabi frequency, and therefore matrix element ratio of $11.6(3)$,
-which is in fact better than the theory prediction of $23.7$.
-Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
-from the $v'=0$ state to be higher than expected.
-Furthermore, we measure the natural linewidth of the $v'=0$ excited state to be no larger than $20 \mathrm{MHz}$ using photoassociation (PA) spectroscopy.
-This suggests that the excited state linewidth should not cause
-a stronger than expected scattering from $v'=0$ state either.
-
-With the $ v' = 0 $ state ruled out as the source of discrepancy between experiment and theory,
-we now consider the background effects from other states with larger single photon detuning.
-Unfortunately, the background in the Raman Rabi frequency fit cancels the Rabi frequency
-for a single photon detuning that is red of the $v' = 0$ transition
-and reduces it by about $30\%$ at the current detuning.
-However, this difference is not enough to explain the greater than a factor of $10$ discrepancy
-present in the experiment.
-The same offset will increase the Rabi frequency for blue detuning,
-but we have observed additional excited states at slightly higher frequencies
-which prevent the blue side of the transition to be usable for the Raman transition.
-
-\todo{change scattering to decoherence? since the fluctuation of light shift
-  does not lead to scattering but only decherence.}
-These results suggest that the decoherence or loss we observed during the Raman transition
-comes from either a higher than expected background scattering rate
-or a different intrinsic or technical source that we have not accounted for.
-We have observed a significant decrease in the coherence time without the ASE filter,
-suggesting the spectral purity of the laser is a significant source of scattering.
-Another source of decoherence could result from fluctuations in the power ratio
-between the two beams resulting in a fluctuation in the resonance position.
-In the experiment, we only stabilize the total power of the tweezer.
-
-In additional to calibrating the $\Omega_m$ and $\Omega_a$,
-the scattering rate of the molecule depends on the tweezer power and detuning.
-At $3\mathrm{mW}$ tweezer power, we have observed a molecule lifetime as long as $1~\mathrm{ms}$.
-However, since the technical noise that can lead to decoherence
-is not fully characterized in our experiment,
-we are unable to further identify the source of the discrepancy based on this dependency.
-
-Lastly, to confirm that the excess scattering does not come from the atomic state,
-we measure the two-body scattering rate
-without turning on the second frequency (Fig.~\ref{f-lifetime}b inset).
-The scattering rate scales as $P_{\mathrm{tweezer}}^{2.58}$ which is inconsistent
-with a single photon scattering process.
-We have not been able to observe a dependency on the detuning in order to verify
-if the scattering process is related to the $v'=0$ state,
-but the power scaling strongly suggests the existence of an unknown two-photon scattering process.
-Nevertheless, the absolute scattering rate is much lower than the total scattering rate
-and is not the limiting factor in our experiment.
-
-%%%% Maybe this following section about the B field can be relegated to a figure caption?
-% Figure () shows the geometry of the experiment setup.
-A $8.8\mathrm{G}$ B field was used to defines the quantization axis in the experiment and is applied perpendicular to the tweezer axis.
-The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
-\todo{}B field dependency $42.2(2) \mathrm{kHz/G}$.
-
-In conclusion, we have formed a weakly-bound NaCs molecule in an optical tweezer
-via an optical Raman transfer.
-A theoretical investigation including all excited states of $ c^3\Sigma^+(\Omega = 1)$,
-the excited atomic continuum, and coupled-channel ground state wavefunctions indicated
-better transfer efficiency using a deeply bound intermediate state
-and the $\ket{\uparrow_{\Na} \downarrow_{\Cs} }$ hyperfine state as the initial and final states.
-Using these theoretical insights, we located the weakly-bound state
-and coherently associated the atoms into the weakly-bound molecule.
-Our transfer efficiency is limited by an unknown scattering source
-resulting in measured scattering rates over $10$ times larger than theoretical predictions.
-Despite this limitation, the transfer efficiency may be further improved
-by increasing the ratio of the up-leg to down-leg Rabi frequency
-$\Omega_a/\Omega_m$ by exploring the possibility of
-driving to more deeply bound states.
-There may also be a better choice of single photon detuning to increase the Raman Rabi frequency,
-since our location results in about 30\% cancellation of the Raman Rabi frequency
-due to an offset of unknown origin.
-
-Our technique can be used to form a more diverse set of molecular species,
-since it does not rely on a magnetic Feshbach resonance, bound states at the MHz-level,
-or a narrow excited state. The formation of a weakly-bound molecule is a key step
-in forming rovibrational ground state molecules.
-Combined with real time rearrangement \cite{Barredo2016, Endres2016},
-defect free arrays of highly controlled molecules are a promising
-and flexible platform for quantum simulation and quantum computing applications.
-
-\todo{sm: STIRAP vs Raman}
-
-\begin{acknowledgments}
-  We would like to thank Bo Gao and Paul Julienne, Rosario (?) (anybody else) for discussion.
-This work is supported by the NSF~(PHY-1806595), the AFOSR~(FA9550-19-1-0089), ARO DURIP (W911NF1810194) and the Arnold and Mabel Beckman foundation.
-J.~T.~Z.
-is supported by a National Defense Science and Engineering Graduate Fellowship.
-W.~C.
-is supported by a Max Planck-Harvard Research Center for Quantum Optics fellowship.
-K.~W.
-is supported by an NSF GRFP fellowship.
-J.~M.~H.
-is supported by the U.K.
-Engineering and Physical Sciences Research Council (EPSRC) Grants No.\ EP/N007085/1, EP/P008275/1 and EP/P01058X/1.
-\end{acknowledgments}
-
-\bibliography{master_ref}
-\bibliographystyle{apsrev4-2}
+\bibliography{master-ref}
 \end{document}

### 2020-11-03 sm.tex
Update on Overleaf.

@@
 
-Our Raman transfer scheme differs from typical Raman transfers, for instance between hyperfine states in atoms, in two key ways.
+In our system, the separation in energy between the initial and target state is much smaller than the single photon detuning $\Delta$ from the intermediate state.
+Thus, there is significant cross coupling for the scattering rate and light shift, where each state is coupled to the excited state by the power in both beams.
+Under these conditions, the scattering rate and light shift is proportional to the total power $P_{\text{tot}} = P_m + P_a$, where $P_{m} (P_{a})$ is the power in the beam that addresses the molecular (atomic) state.
+The Raman Rabi frequency is proportional to $\sqrt{P_mP_a} $.
+With a fixed total power and thus fixed scattering rate, the Raman Rabi frequency is maximized by maximizing $\sqrt{P_m(P_{\text{tot}} - P_m)}$, which is achieved when $ P_m = P_a = P_{\text{tot}}/2$.
+
+\section{Raman Transfer with Many Excited States}
+
+\section{Calculating Matrix Elements with Coupled Channel Ground State}
 
@@
 
-\bibliography{master-ref}
+\bibliography{master_ref}
 \end{document}

### 2020-11-04 paper.tex
Update on Overleaf.
White space, regenerate PDF
Fix latex and revtex warning

@@
-\documentclass[aps,prl,twocolumn,superscriptaddress]{revtex4-1}
+\documentclass[aps,prl,twocolumn,10pt,superscriptaddress]{revtex4-1}
 % \documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4-1}
@@
     Compared to other spin states with weaker interaction,
-    the wavefunction at short distance ($R<100\mathrm{\AA}$, left of the dotted line)
+    the wavefunction at short distance ($R<100\text{\AA}$, left of the dotted line)
     is significantly enhanced.
@@
 % We find a target spin state predominantly in the initial spin state
-  %that also has the advantage of having a reduced sensitivity
-  %to laser intensity noise because of a larger %$\Omega_a/\Omega_b$ as compared to other states.
-  %This reduces the intensity stability requirement to $5\%$
-  %instead of $0.3\%$ which is typical for other states.
+% that also has the advantage of having a reduced sensitivity
+% to laser intensity noise because of a larger %$\Omega_a/\Omega_b$ as compared to other states.
+% This reduces the intensity stability requirement to $5\%$
+% instead of $0.3\%$ which is typical for other states.
 % In addition to the increased atomic coupling, $ \Omega_a $,
@@
 we are unable to further identify the sources of the measured scattering rate based on our measured detuning and power dependencies.
-%the discrepancy based on the dependency.
+% the discrepancy based on the dependency.
 
@@
 \begin{acknowledgments}
-  We would like to thank Bo Gao and Paul Julienne, Rosario (?) (anybody else) for discussion.
+  We would like to thank Bo Gao,  Paul Julienne, and Rosario Gonzalez-Ferez for discussion.
 This work is supported by the NSF~(PHY-1806595), the AFOSR~(FA9550-19-1-0089), ARO DURIP (W911NF1810194) and the Arnold and Mabel Beckman foundation.

### 2020-11-04 paper.tex
Mention power/b field stability requirements

@@
 suggesting the spectral purity of the laser is a significant source of scattering.
-Another source of decoherence could result from fluctuations in the power ratio
-between the two beams resulting in a fluctuation in the resonance position.
-In the experiment, we only stabilize the total power of the tweezer.
+Other sources that can contribute to the decoherence includes
+the stability of the tweezer power and the magnetic field.
+Based on the Raman Rabi frequency to light shift ratio (Fig.~\ref{f-det}c),
+the requirement on the tweezer power stability is $0.8~\%$ at $15~\mathrm{mW}$.
+We stabilize the tweezer power to $0.1~\%$ so this should not be a major source
+of decoherence.
+Similarly, we measured a Zeeman shift of $42.2(2)~\mathrm{kHz/G}$
+which does not cause significant decoherence from the measured magnetic field
+fluctuation of $\sim1.5~\mathrm{mG}$.
 
@@
 is not fully characterized in our experiment,
-we are unable to further identify the sources of the measured scattering rate based on our measured detuning and power dependencies.
-% the discrepancy based on the dependency.
+we are unable to further identify the sources of the measured scattering rate
+based on our measured detuning and power dependencies.
 
@@
 but the power scaling strongly suggests the existence of an unknown two-photon scattering process.
-Nevertheless, the absolute scattering rate from the atomic state is much lower than the total scattering rate
+Nevertheless, the absolute scattering rate from the atomic state
+is much lower than the total scattering rate
 and is not the limiting factor in this experiment.
-
-%%%% Maybe this following section about the B field can be relegated to a figure caption?
-% Figure () shows the geometry of the experiment setup.
-A $8.8\mathrm{G}$ B field was used to defines the quantization axis in the experiment and is applied perpendicular to the tweezer axis.
-The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
-\todo{}B field dependency $42.2(2) \mathrm{kHz/G}$.
 

### 2020-11-04 paper.tex
Consistent unit/font

@@
   Starting from two atoms in their relative motional ground state,
-  we achieve an optical transfer efficiency of $69\%$.
-  The molecule has a binding energy of $770.20052(2) \mathrm{MHz}$ at $8.8~\mathrm{G}$ (\textcolor{red}{Unresolved comment from Jon: with so many digits on the resonance frequency, we may need to mention more digits on the B field number and/or also state the tweezer power.
+  we achieve an optical transfer efficiency of $69~\mathrm{\%}$.
+  The molecule has a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$ (\textcolor{red}{Unresolved comment from Jon: with so many digits on the resonance frequency, we may need to mention more digits on the B field number and/or also state the tweezer power.
 We can state the tweezer power for where we measure it, but the transmission through the objective, etc.
@@
 The current number is still for zero tweezer power), May also need to quote tweezer waist for power dependency}\todo{})
-  with more than $60\%$ of the molecule created in the motional ground state.
+  with more than $60~\mathrm{\%}$ of the molecule created in the motional ground state.
   This technique does not rely on narrow excited state lines or Feshbach resonances
@@
 So far, most molecular association has been achieved for bialkali molecules by magnetoassociation using a magnetic Feshbach scattering resonance.
-The only exceptions are Sr$_2,$ where narrow linewidth ($\sim 20 ~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly-bound molecules with a couple MHz binding energy exists~\cite{He331}.
+The only exceptions are Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly-bound molecules with a couple MHz binding energy exists~\cite{He331}.
 With these requirements, dimers between alkali atoms and non-magnetic atoms, or molecules involving atoms without narrow intercombination lines remain difficult to associate.
@@
 The resulting single molecule is in a well-defined internal quantum state and predominately in its motional ground state.
-A vibrational state of the electronic excited state $c^3\Sigma^+(\Omega = 1)$ is used as the intermediate state in the Raman scheme, and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation.
+A vibrational state of the electronic excited state $\mathrm{c^3\Sigma^+}(\Omega = 1)$ is used as the intermediate state in the Raman scheme, and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation.
 To further reduce the photon scattering and sensitivity to laser intensity noise, we choose the initial and final state to balance the two Rabi frequencies as much as possible.
@@
     of the molecule.
-    The lasers are detuned from an excited molecular state in the $c^3\Sigma$ potential
+    The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
     by $\Delta$ in order to suppress the scattering during the transfer.
@@
 suffers from strong scattering of the nearby excited atomic continuum, resulting in large incoherence and loss to other molecular states.
-This scattering is proportional to $1/\delta_{thresh}^2$,
-where $\delta_{thresh}$ is the detuning from the dissociation threshold,
+This scattering is proportional to $1/\delta_{\mathrm{thresh}}^2$,
+where $\delta_{\mathrm{thresh}}$ is the detuning from the dissociation threshold,
 and thus can be made smaller by using deeply bound vibrational states as the intermediate level.
@@
 % to laser intensity noise because of a larger %$\Omega_a/\Omega_b$ as compared to other states.
-% This reduces the intensity stability requirement to $5\%$
-% instead of $0.3\%$ which is typical for other states.
+% This reduces the intensity stability requirement to $5~\mathrm{\%}$
+% instead of $0.3~\mathrm{\%}$ which is typical for other states.
 % In addition to the increased atomic coupling, $ \Omega_a $,
@@
 with the other combinations, and thus relaxing the intensity stability requirement to the few percent level.
-% Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
+% Thus, instead of a required intensity stability of $0.3 ~\mathrm{\%} $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5~\mathrm{\%} $.
 % Thus, we choose the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination.
@@
     atoms and molecule.
-    We use a bias B field of $B_0=8.8 G$ alone the tweezer polarization
+    We use a bias B field of $B_0=8.8~\mathrm{G}$ alone the tweezer polarization
     to define the quantization axis.
@@
     When driving the Raman transition, the up leg power is smoothly ramped down and
-    the down leg power ramped up over $10\mu s$ while maintaining the total power of the tweezer.
+    the down leg power ramped up over $10~\mathrm{\mu s}$
+    while maintaining the total power of the tweezer.
     This minimizes the heating on the atoms due to power fluctuation while maximizes the time
@@
 Experimentally, we first prepare two atoms in a well-defined external and internal quantum state using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}.
-In brief, the experimental cycle begins by stochastically loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into separate optical tweezers.
+In brief, the experimental cycle begins by stochastically loading a single ${}^{23}\Na$ atom and a single ${}^{133}\Cs$ atom into separate optical tweezers.
 The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom to be able to post select the experimental result on the initial loading condition.
@@
 % After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
-Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination to use as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7 \mathrm{kHz}$ interaction shift~\cite{Hood2019}.
+Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination to use as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.
 %using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\Cs}}$ state.
@@
 This spin flip selectively transfers atoms in the relative motion ground state, removing any initial hot atom background from imperfect cooling \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}.
-For the experiment reported here, 31\% of our initial two atom population is successfully transferred.
+For the experiment reported here, $31~\mathrm{\%}$ of our initial two atom population is successfully transferred.
 % of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
@@
 % found the spectral purity of the laser for Raman beams to be critical for achieving a higher transfer efficiency.
-% The tweezer/Raman beams are generated by a fiber amplifier seeded with a $1037 \mathrm{nm}$ external cavity diode laser.
-% by amplifying a $1037 \mathrm{nm}$ external cavity diode laser (ECDL) with a fiber amplifier,
+% The tweezer/Raman beams are generated by a fiber amplifier seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
+% by amplifying a $1037~\mathrm{nm}$ external cavity diode laser (ECDL) with a fiber amplifier,
 % The diode laser produces the desired frequency on top of a broad band amplified spontaneous emission (ASE).
-We use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the laser spectrum and found it reduces the scattering rate by at least a factor of $2$
+We use a Bragg grating with a line width (FWHM) of $50~\mathrm{GHz}$ to clean up the laser spectrum and found it reduces the scattering rate by at least a factor of $2$
 % for a particular single photon detuning.
@@
   \caption{
-    (a) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
+    (a) Direct measurement of molecule lifetime in $15~\mathrm{mW}$ of trap depth.
     Molecule survival is detected by dissociating back to atoms using a second Raman transition.
-    The lifetime is consistent with the $0.199(9) \mathrm{ms}$
+    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
     measured from the Raman transition data.
@@
     between the two Raman pulses with incomplete transfer.
-    (b) Two-body atom lifetime of $5(1) \mathrm{ms}$
-    in $15 \mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
+    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
+    in $15~\mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
     This is used to improve the fitting of the Raman transfer data.
@@
 Theory prediction was at $770.1 MHz$.
-% The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
+% The background level of $31~\mathrm{\%}$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
 % When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence.
@@
 Fitting the data with a decaying Rabi oscillation suggests that
-$69\%$ of initial ground state atoms are transferred into the molecular state.
+$69~\mathrm{\%}$ of initial ground state atoms are transferred into the molecular state.
 This transfer efficiency is mainly limited by the molecular lifetime
@@
 after a variable wait time (Fig.~\ref{f-lifetime}a).
-The result shows a molecular lifetime of $0.199(9) \mathrm{ms}$
+The result shows a molecular lifetime of $0.199(9)~\mathrm{ms}$
 consistent with the decay of Rabi oscillation.
@@
   \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
-    The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6\mathrm{GHz}$.
+    The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6~\mathrm{GHz}$.
     (a) The light shift of the Raman resonance scales as $P_{tweezer}$
@@
 The $v'=0$ component of the Raman Rabi frequency is
-$2\pi\times170(4) ~\mathrm{Hz\cdot mW^{-1.29}}$,
-or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $15 ~\mathrm{mW}$ tweezer power.
+$2\pi\times170(4)~\mathrm{Hz\cdot mW^{-1.29}}$,
+or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $15~\mathrm{mW}$ tweezer power.
 Together with the $\Omega_m$ measured above, the matrix element, $ \Omega_a $, is
-$2\pi \times 12.1(3)\mathrm{MHz}$.
+$2\pi \times 12.1(3)~\mathrm{MHz}$.
 This gives a Rabi frequency, and therefore matrix element ratio of $11.6(3)$,
@@
 from the $v'=0$ state to be higher than expected.
-Furthermore, we measure the natural linewidth of the $v'=0$ excited state to be no larger than $20 \mathrm{MHz}$ using photoassociation (PA) spectroscopy.
+Furthermore, we measure the natural linewidth of the $v'=0$ excited state to be no larger than $20~\mathrm{MHz}$ using photoassociation (PA) spectroscopy.
 This suggests that the excited state linewidth should not cause
@@
 In the Raman Rabi frequency fit, the fitted background is of an opposite sign from the Raman Rabi frequency for single photon detunings red of the $v' = 0 $ transition.
-Thus, this background reduces the Raman Rabi frequency by about $30\%$ at the current detuning.
+Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$ at the current detuning.
 However, this difference is not enough to explain the greater than a factor of $10$ discrepancy
@@
 Based on the Raman Rabi frequency to light shift ratio (Fig.~\ref{f-det}c),
-the requirement on the tweezer power stability is $0.8~\%$ at $15~\mathrm{mW}$.
-We stabilize the tweezer power to $0.1~\%$ so this should not be a major source
+the requirement on the tweezer power stability is $0.8~\mathrm{\%}$ at $15~\mathrm{mW}$.
+We stabilize the tweezer power to $0.1~\mathrm{\%}$ so this should not be a major source
 of decoherence.
@@
 the scattering rate of the molecule depends on the tweezer power and detuning.
-At $3\mathrm{mW}$ tweezer power, we have observed a molecule lifetime as long as $1~\mathrm{ms}$.
+At $3~\mathrm{mW}$ tweezer power, we have observed a molecule lifetime as long as $1~\mathrm{ms}$.
 However, since the technical noise that can lead to decoherence
@@
 There may also be a better choice of single photon detuning to increase the Raman Rabi frequency,
-since our location results in about 30\% cancellation of the Raman Rabi frequency
+since our location results in about $30~\mathrm{\%}$ cancellation of the Raman Rabi frequency
 due to an offset of unknown origin.

### 2020-11-04 paper.tex
Change tweezer powers

@@
   \caption{
-    (a) Direct measurement of molecule lifetime in $15~\mathrm{mW}$ of trap depth.
+    (a) Direct measurement of molecule lifetime in $3.75~\mathrm{mW}$ of trap depth.
     Molecule survival is detected by dissociating back to atoms using a second Raman transition.
@@
     (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
-    in $15~\mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
+    in $3.75~\mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
     This is used to improve the fitting of the Raman transfer data.
@@
 $770.57150(9) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}c inset)
-with $15 ~\mathrm{mW}$ tweezer power.
+with $3.75~\mathrm{mW}$ tweezer power.
 % (We can maybe add information about the prediction here?)
@@
 From this measurement, we can extract a $\Omega_m$ of
-$2\pi\times36.16(2) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or
-$2\pi\times140.06(8) ~\mathrm{MHz}$ for the $15 ~\mathrm{mW}$ tweezer power used above.
+$2\pi\times72.32(4) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or
+$2\pi\times140.06(8) ~\mathrm{MHz}$ for the $3.75~\mathrm{mW}$ tweezer power used above.
 This number is close to the value of
-$2\pi\times27 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
+$2\pi\times54 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
 
@@
 The $v'=0$ component of the Raman Rabi frequency is
-$2\pi\times170(4)~\mathrm{Hz\cdot mW^{-1.29}}$,
-or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $15~\mathrm{mW}$ tweezer power.
+$2\pi\times1.02(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
+or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
 Together with the $\Omega_m$ measured above, the matrix element, $ \Omega_a $, is
@@
 Based on the Raman Rabi frequency to light shift ratio (Fig.~\ref{f-det}c),
-the requirement on the tweezer power stability is $0.8~\mathrm{\%}$ at $15~\mathrm{mW}$.
+the requirement on the tweezer power stability is $0.8~\mathrm{\%}$ at $3.75~\mathrm{mW}$.
 We stabilize the tweezer power to $0.1~\mathrm{\%}$ so this should not be a major source
@@
 the scattering rate of the molecule depends on the tweezer power and detuning.
-At $3~\mathrm{mW}$ tweezer power, we have observed a molecule lifetime as long as $1~\mathrm{ms}$.
+At $0.75~\mathrm{mW}$ tweezer power, we have observed
+a molecule lifetime as long as $1~\mathrm{ms}$.
 However, since the technical noise that can lead to decoherence

### 2020-11-04 plot_atomic_loss_scaling.jl

@@ -27,36 +27,36 @@ fit_gamma_a2 = fit_data(gen_power_model(2.58), rates[:, 1], rates[:, 2], rates[:
 
 const prefix = joinpath(@__DIR__, "imgs", "atomic_loss_scaling")
 
-figure()
-errorbar(rates[:, 1], rates[:, 2], rates[:, 3], fmt="C0o")
-plot(fit_gamma_a2.plotx, fit_gamma_a2.ploty, "C0")
-xscale("log")
-yscale("log")
-grid()
-xticks([3, 4, 6, 8, 12], ["3", "4", "6", "8", "12"])
-yticks([1, 3, 10, 30], ["1", "3", "10", "30"])
-ax = gca()
-ax.xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
-ax.set_xticks(3:16, minor=true)
-xlabel("Tweezer Power (mW)")
-ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$")
-NaCsPlot.maybe_save("$(prefix)")
+# figure()
+# errorbar(rates[:, 1], rates[:, 2], rates[:, 3], fmt="C0o")
+# plot(fit_gamma_a2.plotx, fit_gamma_a2.ploty, "C0")
+# xscale("log")
+# yscale("log")
+# grid()
+# xticks([3, 4, 6, 8, 12], ["3", "4", "6", "8", "12"])
+# yticks([1, 3, 10, 30], ["1", "3", "10", "30"])
+# ax = gca()
+# ax.xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
+# ax.set_xticks(3:16, minor=true)
+# xlabel("Tweezer Power (mW)")
+# ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$")
+# NaCsPlot.maybe_save("$(prefix)")
 
 figure(figsize=[4.8, 3.6])
 ax = gca()
-bg = matplotlib.patches.Rectangle((2.48, 0.31), 14.52, 39.69, facecolor="white", alpha=0.9)
+bg = matplotlib.patches.Rectangle((0.625, 0.31), 3.625, 39.69, facecolor="white", alpha=0.9)
 ax.add_patch(bg)
-errorbar(rates[:, 1], rates[:, 2], rates[:, 3], fmt="C0o")
[…]

### 2020-11-04 plot_scaling.jl

@@ -202,7 +202,7 @@ for i in 1:length(powers_plot)
     power = powers_plot[i]
     pd = get_plot_data_power(data_res, fit_res, model_res, power)
     errorbar(pd.x .- 703.6, (pd.y .- fit_res.param[1]) .* 1000,
-             pd.unc .* 1000, fmt="C$(i - 1)o", label="$(power) mW")
+             pd.unc .* 1000, fmt="C$(i - 1)o", label="$(power / 4) mW")
     plot(pd.plotx .- 703.6, (pd.ploty .- fit_res.param[1]) .* 1000, "C$(i - 1)")
 end
 # xticks([288500, 288530, 288560, 288590, 288620])
@@ -228,7 +228,7 @@ for i in 1:length(powers_plot)
     power = powers_plot[i]
     pd = get_plot_data_power(data_rabi, fit_rabi, model_rabi, power)
     plot(pd.plotx .- 703.6, pd.ploty, "C$(i - 1)")
-    errorbar(pd.x .- 703.6, pd.y, pd.unc, fmt="C$(i - 1)o", label="$(power) mW")
+    errorbar(pd.x .- 703.6, pd.y, pd.unc, fmt="C$(i - 1)o", label="$(power / 4) mW")
 end
 # xticks([288500, 288530, 288560, 288590, 288620])
 # p: offset, strength
@@ -250,22 +250,25 @@ fig = figure(figsize=[3.6, 5.4])
 
 ax1 = fig.add_subplot(211)
 plot2 = get_plot_data_freq(data_res, fit_res, model_res, freq)
-errorbar(plot2.x[1], (plot2.y[1] .- fit_res.param[1]) .* 1000, plot2.unc[1] .* 1000, fmt="C0o")
-errorbar(plot2.x[2], (plot2.y[2] .- fit_res.param[1]) .* 1000, plot2.unc[2] .* 1000, fmt="C1o")
-errorbar(plot2.x[3], (plot2.y[3] .- fit_res.param[1]) .* 1000, plot2.unc[3] .* 1000, fmt="C2o")
-plot(plot2.plotx, (plot2.ploty .- fit_res.param[1]) .* 1000, "k")
+errorbar(plot2.x[1] / 4, (plot2.y[1] .- fit_res.param[1]) .* 1000,
[…]

### 2020-11-04 paper.tex
Font

@@
 The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}a), where the initial atomic state, and the target weakly-bound molecular state are coupled to an intermediate state by two laser  with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
-%(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
+%(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
 The transfer Raman Rabi Rate, $\Omega_R=\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_s$
@@
 taking into account of all states of
-the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
+the $\mathrm{c^3\Sigma^+}(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
 and the continuum~\cite{Liu2017}.
@@
 (Fig.~\ref{f-theory}b, full result in SM \todo{proper cite})
-As a result, we choose the $v'=0$ of $c^3\Sigma^+(\Omega = 1)$ as an intermediate state
+As a result, we choose the $v'=0$ of $\mathrm{c^3\Sigma^+}(\Omega = 1)$ as an intermediate state
 to drive the Raman transition.
@@
 via an optical Raman transfer.
-A theoretical investigation including all excited states of $ c^3\Sigma^+(\Omega = 1)$,
+A theoretical investigation including all excited states of $\mathrm{c^3\Sigma^+}(\Omega = 1)$,
 the excited atomic continuum, and coupled-channel ground state wavefunctions indicated

### 2020-11-04 paper.tex
Update figure 2 to remove the sequence

@@
   \caption{
-    (a) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
+    (a) Raman detuning scans at different times showing the resonance frequency.
+    (b) Raman pulse time scan on resonance.
+    A decaying Rabi oscillation can be observed proving the coherence of
+    the Raman transfer process.
+    This is fitted together with (a) to a model of Raman transition
+    with loss on the atom and molecule state and is used to determine
+    both the Raman Rabi frequency and the loss rates.
+    Inset: Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
     The tweezer and Raman beam is focused through an objective to define the location of the
@@
     As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
-    (b) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
-    When driving the Raman transition, the up leg power is smoothly ramped down and
-    the down leg power ramped up over $10~\mathrm{\mu s}$
-    while maintaining the total power of the tweezer.
-    This minimizes the heating on the atoms due to power fluctuation while maximizes the time
-    with maximum Raman Rabi frequency when the up and down leg powers are equal.
-    (c) Raman pulse time scan on resonance.
-    A decaying Rabi oscillation can be observed proving the coherence of
-    the Raman transfer process.
-    Inset: Raman detuning scans at different times showing the resonance frequency.
-    This is also fitted to a model of Raman transition
-    with loss on the atom and molecule state and is used to determine
-    both the Raman Rabi frequency and the loss rates.
     \label{f-raman}}
@@
 % After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
-To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}a).
+To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}b inset).
 The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time.
@@
 We observed a reduction of the scattering rate by a factor of $2$ due to suppression of the broadband amplified spontaneous emission (ASE) from the laser that couples to other excited states.
-%to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
-The pulse sequence is shown in Fig.~\ref{f-raman}b. %Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal.
-% In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse.
-The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time.
+% to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
 After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged.
@@
 we locate the Raman resonance for the atom to molecule transition at
-$770.57150(9) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}c inset)
+$770.57150(9) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}a)
 with $3.75~\mathrm{mW}$ tweezer power.
@@
 we fix the two photon detuning on resonance and scan the pulse time.
-Fig.~\ref{f-raman}c shows the observed coherent Rabi oscillation between the atomic and molecular states.
+Fig.~\ref{f-raman}b shows the observed coherent Rabi oscillation between the atomic and molecular states.
 Fitting the data with a decaying Rabi oscillation suggests that
@@
 that includes a Raman Rabi frequency and
-a finite lifetime for the molecular state (Fig.~\ref{f-raman}c and inset).
+a finite lifetime for the molecular state (Fig.~\ref{f-raman}a and b).
 We account for the effect of atomic state loss by measuring the one and

### 2020-11-04 plot_exp_data.jl

@@ -171,7 +171,7 @@ xlabel("Detuning From Resonance (kHz)")
 ylabel("Two-Body Survival")
 NaCsPlot.maybe_save("$(prefix)_raman_det")
 
-figure()
+figure(figsize=[7.2, 5.4])
 errorbar([0.0], [ratio_00 * scale_1], [uncs_00 * scale_1], fmt="C0o", label="0.00 ms")
 plot([plot_freq_lo, plot_freq_hi] .- param_1[3], [v00 * scale_1, v00 * scale_1], "C0-")
 NaCsPlot.plot_survival_data(data_nacs_12′, scale_1, fmt="C1o", label="0.12 ms")
@@ -180,7 +180,7 @@ NaCsPlot.plot_survival_data(data_nacs_25′, scale_1, fmt="C2o", label="0.25 ms"
 plot(plot_freq .- param_1[3], model_2d.(0.25, plot_freq, (param_1,)) .* scale_1, "C2")
 legend(fontsize="x-small", loc="lower right")
 grid()
-xlabel("Detuning From Resonance (kHz)")
+xlabel("Raman Detuning (kHz)")
 ylabel("Fraction of Atomic Ground State")
 NaCsPlot.maybe_save("$(prefix)_norm_raman_det")
 

### 2020-11-05 paper.tex
Mention tweezer waist
Update on Overleaf.

@@
     Inset: Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
-    The tweezer and Raman beam is focused through an objective to define the location of the
-    atoms and molecule.
+    The tweezer and Raman beam is focused through an objective to a waist of $0.9~\mathrm{\mu m}$
+    which defines the location of the atoms and molecule.
     We use a bias B field of $B_0=8.8~\mathrm{G}$ alone the tweezer polarization
@@
 % After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
-To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}b inset).
+To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer beam itself as the Raman beams by turning on two frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}b inset).
 The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time.

### 2020-11-05 sm.tex
White space, regenerate PDF
Reproducible SM
[sm] todo
Update on Overleaf.

@@
 
+\newcommand{\todo}[1]{}
+
 \newcommand{\harvardphysics}{\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}}
@@
 
-%Add S to labels
+% Add S to labels
 \setcounter{table}{0}
@@
 \renewcommand{\theequation}{S.\arabic{equation}}
+
+\ifpdf
+% Ensure reproducible output
+\pdfinfoomitdate=1
+\pdfsuppressptexinfo=-1
+\pdftrailerid{}
+\hypersetup{
+  pdfcreator={},
+  pdfproducer={}
+}
+\fi
 
@@
 
+For the purposes of this work, we denote $\Omega_a $($\Omega_m$) as the Rabi frequencies to drive a transition from the atom (target molecule) state to the intermediate state used in the Raman transition corresponding to the power in a single beam, $P_a$ ($P_m$).
+Thus, the Raman Rabi frequency remains $\Omega_a\Omega_m/2\Delta$.
+Cross coupling affects the scattering rate and light shift, and assuming equal powers in both beams, these quantities become $ \Gamma_e \Omega_m^2 / 2\Delta^2 + \Gamma_e \Omega_a^2 / 2\Delta^2 $ and $ \Omega_m^2/2\Delta - \Omega_a^2/2\Delta $, where $\Gamma_e$ is the excited state linewidth.
+
 \section{Raman Transfer with Many Excited States}
@@
 
+\todo{
+  Power/intensity calibration
+}
+
 \bibliography{master_ref}

### 2020-11-06 sm.tex
Update on Overleaf.

@@
 \usepackage{listings}
+\usepackage{braket}
 
@@
 For the purposes of this work, we denote $\Omega_a $($\Omega_m$) as the Rabi frequencies to drive a transition from the atom (target molecule) state to the intermediate state used in the Raman transition corresponding to the power in a single beam, $P_a$ ($P_m$).
-Thus, the Raman Rabi frequency remains $\Omega_a\Omega_m/2\Delta$.
+Thus, the Raman Rabi frequency remains $\Omega_a\Omega_m/2\Delta$, where $ \Delta $ is the single photon detuning.
 Cross coupling affects the scattering rate and light shift, and assuming equal powers in both beams, these quantities become $ \Gamma_e \Omega_m^2 / 2\Delta^2 + \Gamma_e \Omega_a^2 / 2\Delta^2 $ and $ \Omega_m^2/2\Delta - \Omega_a^2/2\Delta $, where $\Gamma_e$ is the excited state linewidth.
+Since $ \Omega_m >> \Omega_a $, the scattering rate and light shift can be approximated as $ \Gamma_e \Omega_m^2/2\Delta^2$ and $\Omega_m^2/2\Delta$.
 
-\section{Raman Transfer with Many Excited States}
+\section{Raman Transfer with Many Intermediate States}
+With multiple intermediate states, the total Raman Rabi frequency, scattering rate, and light shift become a sum over all these possible states.
+In our model, we consider all vibrational states of $ c^3\Sigma^+(\Omega = 1) $ as intermediate states, as well as states in the atomic continuum.
+The Rabi frequency between two states is proportional to the electronic dipole moment, arising from the electronic wavefunctions, and the vibrational wavefunction (in the relative motion coordinate of the two atoms) overlap between the two states.
+Under the assumption that the electronic dipole moment $ d $ is the same for all transitions between the ground state and the excited electronic state, the total Raman Rabi frequency becomes:
+
+\begin{equation}
+\Omega_R = \frac{d^2E^2}{2\hbar^2} \displaystyle\sum_{v'} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}}
+\end{equation}
+
+where $\ket{a}$ ($\ket{m}$) are the relative coordinate wavefunctions for the trapped atom (target-molecule) state, and $\ket{v'}$ is the relative coordinate wavefunction for the excited state which includes both bound molecule states and the atomic continuum.
+$\Delta_{v'}$ is a single photon detuning with respect to the $\ket{v'}$ state, $ E $ is the electric field for the power in the single beam given a waist size.
+We can divide this sum into a sum over all the bound molecular states, and a sum over atomic continuum states.
+
+\begin{equation}
+\Omega_R = \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' > v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}}
+\end{equation}
+
+where $ v'_{\text{max}}$ corresponds to the most weakly bound electronically excited molecular state.
+The first term can be calculated numerically given an excited state potential.
+To calculate the second term, we first make an assumption that we are far enough detuned from the contributing continuum states that they are all at approximately the same detuning, $ \delta_{\text{thresh}}$.
+This allows us to pull it out of the sum, and we obtain:
+
+\begin{equation}
+\Omega_R \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\delta_{\text{thresh}}}\displaystyle\sum_{v' > v'_{\text{max}}} \braket{a|v'}\braket{v'|m}  \label{rabifreq}
+\end{equation}
+
+From requiring orthogonality,
+
+\begin{equation}
+    \displaystyle\sum_{v'} \braket{a|v'}\braket{v'|m} = \braket{a|m} = 0
+\end{equation}
+
+we derive an expression for the second sum in equation \ref{rabifreq}
+
+\begin{equation}
+    \displaystyle\sum_{v'> v'_{\text{max}}} \braket{a|v'}\braket{v'|m} = -\displaystyle\sum_{v' \leq v'_{\text{max}}} \braket{a|v'}\braket{v'|m}
+\end{equation}
+
+which can be calculated from the vibrational states of the excited state potential. Thus, the Raman Rabi frequency can be approximated as:
+
+\begin{equation}
+\Omega_R \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} -  \frac{d^2E^2}{2\hbar^2\delta_{\text{thresh}}}\displaystyle\sum_{v' \leq v'_{\text{max}}} \braket{a|v'}\braket{v'|m}
+\end{equation}
+
+We can account for the atomic continuum in the scattering rate in a similar way.
+
+\begin{align}
+    \Gamma_s &= \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} + \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' > v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} \\
+     &\approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} + \frac{d^2E^2\Gamma}{2\hbar^2\delta_{\text{thresh}}^2}\displaystyle\sum_{v' > v'_{\text{max}}}\braket{m|v'}\braket{v'|m}
+\end{align}
+
+where $\Gamma_{v'}$ is the excited state linewidth for the $\ket{v'}$ state, and we have assumed the atomic continuum states all have the same linewidth $\Gamma$.
+Using normalization, we derive an expression for the sum in the second term
+
+\begin{equation}
+    \displaystyle\sum_{v' > v'_{\text{max}}}\braket{m|v'}\braket{v'|m} = 1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}
+\end{equation}
+
+We then arrive at an expression for the scattering rate, accounting for the atomic continuum,
+
+\begin{equation}
+    \Gamma_s \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} +  \frac{d^2E^2\Gamma}{2\hbar^2\delta_{\text{thresh}}^2}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right)
+\end{equation}
+
+The effect of the continuum is to add an extra state at the atomic threshold with strength proportional to the amount of wavefunction overlap between the target-molecular state and all atomic continuum states.
+This term is especially important for our target-molecule state, because the square of the wavefunction overlap between the target-molecule state and all excited vibrational states is only 0.02
+
+\begin{equation}
+\displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m} = 0.02
+\end{equation}
+
+leading to strong scattering from the atomic continuum.
+We note that this model also leads to a component in the scattering rate that is proportional to $ 1/\delta_{\text{thresh}}^2$ and is smaller as one detunes farther from the threshold.
+
+A very similar result holds for the light shift and is written here for completeness
+
+\begin{equation}
+    \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\delta_{\text{thresh}}}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right)
+\end{equation}
 

### 2020-11-07 paper.tex
Update on Overleaf.

@@
 \begin{abstract}
-  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
+  Fully controlled single molecules provide a promising platform for a variety of quantum science applications.
+As a step towards this goal, we report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
   through an optical Raman transition without the use of a Feshbach resonance.
@@
   we achieve an optical transfer efficiency of $69~\mathrm{\%}$.
-  The molecule has a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$ (\textcolor{red}{Unresolved comment from Jon: with so many digits on the resonance frequency, we may need to mention more digits on the B field number and/or also state the tweezer power.
-We can state the tweezer power for where we measure it, but the transmission through the objective, etc.
-I believe is only estimated.
-(YYC: This is why the original number quoted was zero field.
-The current number is still for zero tweezer power), May also need to quote tweezer waist for power dependency}\todo{})
+  The molecule has a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$ 
   with more than $60~\mathrm{\%}$ of the molecule created in the motional ground state.
@@
 
-Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018, PhysRevLett.119.153001, hudson2011}, quantum simulations~\cite{Yao2018, Wall2015, Sundar2018, wall2015realizing}, quantum information processing~\cite{DeMille2002, Ni2018, Hudson2018, Lin2019}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111,Segev2019}.
-While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016,Anderegg2018, Mitra1366, PhysRevX.10.021049, PhysRevLett.121.013202, PhysRevLett.120.123201}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020,He331}  have been achieved through the association of ultracold atoms.
+Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018, PhysRevLett.119.153001, hudson2011}, quantum simulations~\cite{Micheli2006, Yao2018, Wall2015, wall2015realizing}, quantum information processing~\cite{DeMille2002, Ni2018, Hudson2018, Lin2019}, and studies of ultracold chemistry~\cite{Bala2016,Hu1111,Segev2019,deJongh626}.
+While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016,Anderegg2018, Mitra1366, PhysRevX.10.021049, PhysRevLett.121.013202, Truppe2017}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020,He331}  have been achieved through the association of ultracold atoms.
 % (any place to cite  molecular ion work?)
@@
 Associating atoms into deeply-bound molecules is challenging because of the small wavefunction overlap between the free-atom and molecular state and the release of a large amount of binding energy.
-A two-step approach has been demonstrated to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state releasing the binding energy via stimulated emission~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
+A two step approach has been demonstrated to associate atom pairs into weakly bound molecules first, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state releasing the binding energy via stimulated emission~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
 So far, most molecular association has been achieved for bialkali molecules by magnetoassociation using a magnetic Feshbach scattering resonance.
 The only exceptions are Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly-bound molecules with a couple MHz binding energy exists~\cite{He331}.
-With these requirements, dimers between alkali atoms and non-magnetic atoms, or molecules involving atoms without narrow intercombination lines remain difficult to associate.
+With these requirements, molecules involving non-magnetic atoms or atoms without narrow intercombination lines remain difficult to associate.
 % These requirements limit the generality of previous association techniques.
@@
 
-Here, we demonstrate coherent association of an atom pair to a weakly-bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}a.
+Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}a.
 The scheme does not rely on a Feshbach resonance, few MHz level bound states, or a narrow excited state.
@@
   \caption{Optical creation of single molecule from single atoms in tweezer.
-    (a) Schematics of the optical transition from an atom pair to a weakly-bound molecule.
+    (a) Schematic of the optical transition from an atom pair to a weakly-bound molecule.
     The initial state is the relative motional ground state between the two atoms
@@
     which results in a larger Raman Rabi frequency to scattering rate ratio.
-    (c) Enhancement of short range wavefunction.
+    (c) Enhancement of the short range wavefunction.
     The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
@@
 
-The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}a), where the initial atomic state, and the target weakly-bound molecular state are coupled to an intermediate state by two laser  with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
+The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}a), where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
-The transfer Raman Rabi Rate, $\Omega_R=\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_s$
+The transfer Raman Rabi Rate, $\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
 % $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
@@
 Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally.
-Thus, the scattering is given by $ \Gamma_s=\Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power.
+Thus, the scattering rate is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power.
 Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
@@
 
-Early experiments used weakly-bound excited states as the intermediate state
+Early experiments used weakly bound excited states as the intermediate state
 in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
@@
 and Raman Rabi rates over all possible intermediate states.
-With these considerations, using a weakly-bound excited state as the intermeidate state
+With these considerations, using a weakly bound excited state as the intermediate state
 suffers from strong scattering of the nearby excited atomic continuum, resulting in large incoherence and loss to other molecular states.
@@
 
-To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency
-and scattering rate at different detunings from the atomic threshold
+To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency $\Omega_R$
+and scattering rate $\Gamma_s$ at different detunings from the atomic threshold
 taking into account of all states of
@@
 suggesting that there is significant matrix element
-between the target molecular state and the excited atomic continuum (See SM \todo{proper cite}).
+between the target molecular state and the excited atomic continuum (See Supplementary Material\todo{proper cite}).
 This calculation shows that the ratio of the Raman Rabi rate to scattering rate
-can be made larger for more deeply bound states compared to weakly-bound states
+can be made larger for more deeply bound states compared to weakly bound states
 at a cost of a smaller Raman Rabi frequency
-(Fig.~\ref{f-theory}b, full result in SM \todo{proper cite})
+(Fig.~\ref{f-theory}b, full result in Supplementary Material \todo{proper cite})
 As a result, we choose the $v'=0$ of $\mathrm{c^3\Sigma^+}(\Omega = 1)$ as an intermediate state
@@
 choosing an initial and a final state for a large $ \Omega_a/\Omega_m $ ratio
-maximizes Raman Rabi coupling at a given detuning.
+maximizes the Raman Rabi frequency at a given detuning.
 Furthermore, a larger ratio also relaxes the intensity stability requirement,
@@
 Due to the small size of the intermediate state wavefunction as compared to the trapped atoms,
-the coupling $\Omega_a$ is approximately proportional to
+$\Omega_a$ is approximately proportional to
 the value of the relative atomic wavefunction at short distance
@@
 Using a harmonic oscillator approximation,
-the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $,
-where $ \omega_{\text{trap}} $ is the trap frequency\cite{Mies2000}.
+the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $ or $P^{3/8}$,
+where $ \omega_{\text{trap}} $ is the trap frequency and $P$ is the power in the trap\cite{Mies2000}.
+However, additional power may not always be available, and will also lead to additional undesired scattering.
 Alternatively, one can choose an atomic pair state with a large scattering length
@@
 Among the stable spin combinations, $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\Na} \downarrow_{\Cs}} $ combination has a large and negative scattering length of $ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
-For the target molecular state, we perform coupled-channel calculations
-to identify the Rabi frequencies $\Omega_m$ to different weakly-bound spin states. The target's spin state is ideally similar to the initial spin state in order to minimize sensitivity to the B-field.
+For the target molecular state, the spin state is ideally similar to the initial spin state in order to minimize sensitivity to the magnetic field.
 % We find a target spin state predominantly in the initial spin state
@@
 % In addition to the increased atomic coupling, $ \Omega_a $,
-Coupled channel calculations show that this target molecular state also has reduced Rabi frequency, $ \Omega_m $,
-with the intermediate state when compared to bound states of the other stable spin combinations, thus further increasing the $\Omega_a/\Omega_m$ ratio.
+Coupled channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $,
+with the intermediate state when compared to bound states of the other spin compositions.
+This further increases the $\Omega_a/\Omega_m$ ratio when using the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.
 % $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
-Using an initial $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination
+This combination
 results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003
-with the other combinations, and thus relaxing the intensity stability requirement to the few percent level.
+with the other combinations, thus relaxing the intensity stability requirement to the few percent level.
 % Thus, instead of a required intensity stability of $0.3 ~\mathrm{\%} $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5~\mathrm{\%} $.
@@
     the Raman transfer process.
-    This is fitted together with (a) to a model of Raman transition
-    with loss on the atom and molecule state and is used to determine
+    This is fitted together with (a) to a model of the Raman transition including loss of the atom and molecule state and is used to determine
     both the Raman Rabi frequency and the loss rates.
@@
     which defines the location of the atoms and molecule.
-    We use a bias B field of $B_0=8.8~\mathrm{G}$ alone the tweezer polarization
+    We use a bias B field of $B_0=8.8~\mathrm{G}$ along the tweezer polarization
     to define the quantization axis.
@@
 The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom to be able to post select the experimental result on the initial loading condition.
-Raman sideband cooling is then applied to cool both atoms simultaneously into the 3-dimensional motional ground state of their optical tweezers.
+Raman sideband cooling is then applied to prepare both atoms simultaneously into the 3-dimensional motional ground state of their optical tweezers.
 After cooling, the Na and Cs atoms are in a spin state of $\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=4,m_F=4}_{\Cs} $ %and are merged into the same tweezer~\cite{Liu2019}.
@@
 The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
-This spin flip selectively transfers atoms in the relative motion ground state, removing any initial hot atom background from imperfect cooling \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}.
+This spin flip selectively transfers atoms in the relative motional ground state, removing any initial hot atom background from imperfect cooling \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motional ground state.}.
 For the experiment reported here, $31~\mathrm{\%}$ of our initial two atom population is successfully transferred.
@@
 % After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
-To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer beam itself as the Raman beams by turning on two frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}b inset).
+To perform the Raman transfer of an atom pair to the target weakly bound molecular state, we use the tweezer beam itself as the Raman beams by turning on two frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}b inset).
 The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time.
@@
     measured from the Raman transition data.
-    The oscillation in the survival is the result of the interference
-    between the two Raman pulses with incomplete transfer.
     (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
@@
     Inset: Atomic scattering rate scales as $P_{tweezer}^{2.58}$ on a log-log scale,
-    this is consistent with a two photon scattering process.
+    this is consistent with a two-photon scattering process.
     We have not measured a clear dependency of the loss rate on the tweezer detuning.
@@
 In order to verify the coherence of the transfer directly,
-we fix the two photon detuning on resonance and scan the pulse time.
+we fix the two-photon detuning on resonance and scan the pulse time.
 Fig.~\ref{f-raman}b shows the observed coherent Rabi oscillation between the atomic and molecular states.
 Fitting the data with a decaying Rabi oscillation suggests that
-$69~\mathrm{\%}$ of initial ground state atoms are transferred into the molecular state.
+$69~\mathrm{\%}$ of initial ground state atoms are transferred into the molecular state after a $\pi$ pulse.
 This transfer efficiency is mainly limited by the molecular lifetime
@@
 both the Raman Rabi frequency and the scattering rate
-which can affect the scattering rate to Rabi frequency ratio.
+which can affect the scattering rate to Raman Rabi frequency ratio.
 
 In order to verify whether any one of these known sources are the origin of the discrepancy,
-we measured the properties of the Raman resonance as a function of the tweezer power and single photon frequency.
+we measured the properties of the Raman resonance as a function of the tweezer power and single photon detuning.
 These dependencies allow us to experimentally determine the matrix elements,
@@
 we observe the expected linear dependency on the resonance frequency
-caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}a).
+caused by the differential light shift between the atomic and molecular state.
 When we vary the tweezer frequency around the $v'=0$ intermediate state,
 we can further observe a $1/\Delta$ component
-and a constant background in the experimentally explored region.
+and a constant background in the experimentally explored region (Fig.~\ref{f-det}a).
 The background is caused by coupling to other excited states that are further away in energy.
@@
 This number is close to the value of
-$2\pi\times54 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
+$2\pi\times40.7 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
 
@@
     The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6~\mathrm{GHz}$.
-    (a) The light shift of the Raman resonance scales as $P_{tweezer}$
-    and follows $1/\Delta$ with an offset.
-    The fit also includes a small term that is proportional to $P_{tweezer}^2$
+    (a) The light shift of the Raman resonance scales as $P$
+    and follows $1/\Delta$ with an offset, where $ P$ is the power in the tweezer.
+    The fit also includes a small term that is proportional to $P^2$
     which is caused by the effective magnetic field generated by the tweezer which is
     perpendicular to the real magnetic field.
-    (b) Raman Rabi frequency ($\Omega_R$) scales as $P_{tweezer}^{1.29}$
+    (b) Raman Rabi frequency ($\Omega_R$) scales as $P^{1.29}$
     and follows $1/\Delta$ with an offset.
-    From these results we can confirm the theory prediction of
-    the atom-molecule matrix element ratio.
     (c) Tweezer power dependency of light shift (up) and Raman Rabi frequency (down)
@@
 
-In order to calculate the matrix element ratio,
-we now need to extract the Rabi frequency between the atomic state and the intermediate state, $ \Omega_a $.
+In order to calculate the $\Omega_m/\Omega_a$ ratio,
+we now need to extract $ \Omega_a $.
 We do this by measuring the dependencies of the Raman Rabi frequency,
@@
 As discussed before, for weakly interacting particles,
-$\Omega_a$ scales as $ \omega_{\text{trap}}^{3/4}$ or $P^{0.375}$.
+$\Omega_a$ scales as $P^{0.375}$.
 However, due to the strong interaction between the two atoms, this approximation breaks down.
@@
 Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
-which fits well to our experimental result.
+which fits well to our experimental result (Fig.~\ref{f-det}c).
 Similar to the light shift, the Raman Rabi frequency's detuning dependence is determined by a constant background component and
@@
 or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
-Together with the $\Omega_m$ measured above, the matrix element, $ \Omega_a $, is
+Together with the $\Omega_m$ measured above, the Rabi frequency, $ \Omega_a $, is
 $2\pi \times 12.1(3)~\mathrm{MHz}$.
-This gives a Rabi frequency, and therefore matrix element ratio of $11.6(3)$,
-which is in fact better than the theory prediction of $23.7$.
+This gives a matrix element ratio of $11.6(3)$,
+which is in fact better than the theory prediction of $23.8$ (Table \ref{tab:rabi_freqs}).
 Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
 from the $v'=0$ state to be higher than expected.
-Furthermore, we measure the natural linewidth of the $v'=0$ excited state to be no larger than $20~\mathrm{MHz}$ using photoassociation (PA) spectroscopy.
+Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $20~\mathrm{MHz}$ using photoassociation (PA) spectroscopy.
 This suggests that the excited state linewidth should not cause
 a stronger than expected scattering from $v'=0$ state either.
+
+\begin{table}[h]
+    \centering
+    \begin{tabular}{c|c|c}
+         & Experiment & Theory \\ \hline
+         $ \Omega_m $ & $2\pi \times 140.06(8) ~\mathrm{MHz} $ & $2\pi \times 78.9 ~\mathrm{MHz}$ \\
+       $\Omega_a$ & $2\pi \times 12.1(3) ~\mathrm{MHz}$ & $2\pi \times 3.32 ~\mathrm{MHz}$ \\
+       $\Omega_m/\Omega_a$ & $11.6(3)$ & $ 23.8$
+    \end{tabular}
+    \caption{Comparison between theory and experiment of the Rabi frequencies $\Omega_m$ and $\Omega_a$ at $3.75$ mW tweezer power.
+The experimentally measured $\Omega_m/\Omega_a$ ratio is smaller than the theory prediction.}
+    \label{tab:rabi_freqs}
+\end{table}
 
@@
 present in the experiment.
-Due to the change in sign of the Raman Rabi frequency, the same background will increase the Raman Rabi frequency for detunings blue of the $v' = 0$ transition, which increases the Raman Rabi frequency.
-Unfortunately, we have observed additional nearby excited states at higher frequencies
+Due to the change in sign of the Raman Rabi frequency as a function of detuning when crossing a resonance, the same background will increase the Raman Rabi frequency for detunings blue of the $v' = 0$ transition, which increases the Raman Rabi frequency.
+Unfortunately, we have observed additional nearby excited states belonging to a different excited state potential at higher frequencies
 which prevent the blue side of the transition to be usable for the Raman transition.
@@
 or a different intrinsic or technical source that we have not accounted for.
-We have observed a significant decrease in the coherence time without the ASE filter,
+We have observed a decrease in the coherence time by a factor of 2 without the ASE filter,
 suggesting the spectral purity of the laser is a significant source of scattering.
@@
 Based on the Raman Rabi frequency to light shift ratio (Fig.~\ref{f-det}c),
-the requirement on the tweezer power stability is $0.8~\mathrm{\%}$ at $3.75~\mathrm{mW}$.
-We stabilize the tweezer power to $0.1~\mathrm{\%}$ so this should not be a major source
+the requirement on the tweezer power stability is $0.8~\mathrm{\%}$ at $3.75~\mathrm{mW}$, which we stabilize to $0.1~\mathrm{\%}$ so this should not be a major source
 of decoherence.
@@
 
-In additional to calibrating the $\Omega_m$ and $\Omega_a$,
-the scattering rate of the molecule depends on the tweezer power and detuning.
+The scattering rate of the molecule also depends on the tweezer power and detuning, and becomes smaller when the power is lowered.
 At $0.75~\mathrm{mW}$ tweezer power, we have observed
@@
 if the scattering process is related to the $v'=0$ state,
-but the power scaling strongly suggests the existence of an unknown two-photon scattering process.
+but the power scaling strongly suggests the existence of an unknown two-photon process.
 Nevertheless, the absolute scattering rate from the atomic state
@@
 
-In conclusion, we have formed a weakly-bound NaCs molecule in an optical tweezer
+In conclusion, we have formed a weakly bound NaCs molecule in an optical tweezer
 via an optical Raman transfer.
 A theoretical investigation including all excited states of $\mathrm{c^3\Sigma^+}(\Omega = 1)$,
-the excited atomic continuum, and coupled-channel ground state wavefunctions indicated
+the excited atomic continuum, and coupled channel ground state wavefunctions indicated
 better transfer efficiency using a deeply bound intermediate state
-and the $\ket{\uparrow_{\Na} \downarrow_{\Cs} }$ hyperfine state as the initial and final states.
-Using these theoretical insights, we located the weakly-bound state
-and coherently associated the atoms into the weakly-bound molecule.
+and the $\ket{\uparrow_{\Na} \downarrow_{\Cs} }$ spin state as the initial and final states.
+Using these theoretical insights, we located the weakly bound state
+and coherently associated the atoms into a weakly bound molecule.
 Our transfer efficiency is limited by an unknown scattering source
@@
 
-Our technique can be used to form a more diverse set of molecular species,
+Our technique can be applied to form a more diverse set of molecular species,
 since it does not rely on a magnetic Feshbach resonance, bound states at the MHz-level,
@@
 Combined with real time rearrangement \cite{Barredo2016, Endres2016},
-defect free arrays of highly controlled molecules are a promising
+defect free arrays of highly controlled molecules comprise a promising
 and flexible platform for quantum simulation and quantum computing applications.

### 2020-11-09 sm.tex
Update on Overleaf.

@@
 \section{Calculating Matrix Elements with Coupled Channel Ground State}
-
-Test Reference\cite{Liu2019}
+The free atom state (with spherically symmetric harmonic confinement) and target weakly-bound molecular state are calculated using coupled-channel methods.
+With the cylindrical symmetry present at non-zero magnetic field, the magnetic quantum number is a good quantum number.
+We use the $ \ket{F_{\text{Na}} = 2, m_{F_{\text{Na}}} = 2, F_{\text{Cs}} = 3, m_{F_{\text{Cs}}} = 3}$ spin combination, so states with total $ m_F = 5 $ are included.
+These states, written in the basis $ \ket{S, m_S, I, m_I}$, include $ \ket{0,0,5,5}, \ket{1,0$
 

### 2020-11-09 paper.tex
Format and whitespace
Minor comments from Jeremy

@@
 \begin{abstract}
-  Fully controlled single molecules provide a promising platform for a variety of quantum science applications.
-As a step towards this goal, we report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
+  Fully controlled single molecules provide a promising platform
+  for a variety of quantum science applications.
+  As a step towards this goal, we report on coherent association
+  of a single weakly bound NaCs molecule in an optical tweezer
   through an optical Raman transition without the use of a Feshbach resonance.
@@
   with more than $60~\mathrm{\%}$ of the molecule created in the motional ground state.
-  This technique does not rely on narrow excited state lines or Feshbach resonances
+  This technique does not rely on narrow excited-state lines or Feshbach resonances
   and will allow a wider range of molecular species to be assembled atom-by-atom.
@@
 
-Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018, PhysRevLett.119.153001, hudson2011}, quantum simulations~\cite{Micheli2006, Yao2018, Wall2015, wall2015realizing}, quantum information processing~\cite{DeMille2002, Ni2018, Hudson2018, Lin2019}, and studies of ultracold chemistry~\cite{Bala2016,Hu1111,Segev2019,deJongh626}.
-While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016,Anderegg2018, Mitra1366, PhysRevX.10.021049, PhysRevLett.121.013202, Truppe2017}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020,He331}  have been achieved through the association of ultracold atoms.
+Diverse species of fully quantum controlled  ultracold molecules are desired
+for a wide variety of applications including precision measurements~\cite{
+  Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018,
+  PhysRevLett.119.153001, hudson2011},
+quantum simulations~\cite{Micheli2006, Yao2018, Wall2015, wall2015realizing},
+quantum information processing~\cite{DeMille2002, Ni2018, Hudson2018, Lin2019},
+and studies of ultracold chemistry~\cite{Bala2016,Hu1111,Segev2019,deJongh626}.
+While many innovative approaches demonstrated in the last few years
+have directly cooled different species of diatomic or polyatomic molecules
+below 1~mK~\cite{Norrgard2016,Anderegg2018, Mitra1366, PhysRevX.10.021049,
+  PhysRevLett.121.013202, Truppe2017},
+the highest phase-space-density gas~\cite{Demarco2018} and
+the coldest individual molecules~\cite{Zhang2020,He331}
+have been achieved through the association of ultracold atoms.
 % (any place to cite molecular ion work?)
@@
 
-Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques that have been developed for atoms.
-Associating atoms into deeply-bound molecules is challenging because of the small wavefunction overlap between the free-atom and molecular state and the release of a large amount of binding energy.
-A two step approach has been demonstrated to associate atom pairs into weakly bound molecules first, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state releasing the binding energy via stimulated emission~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
-So far, most molecular association has been achieved for bialkali molecules by magnetoassociation using a magnetic Feshbach scattering resonance.
-The only exceptions are Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly-bound molecules with a couple MHz binding energy exists~\cite{He331}.
-With these requirements, molecules involving non-magnetic atoms or atoms without narrow intercombination lines remain difficult to associate.
+Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques
+that have been developed for atoms.
+Associating atoms into deeply-bound molecules is challenging
+because of the small wavefunction overlap between the free-atom and molecular states
+and the release of a large amount of binding energy.
+A two-step approach has been demonstrated to associate atom pairs
+into weakly bound molecules first,
+and then transfer the molecules from this single internal state
+to a desired rovibrational and electronic state,
+releasing the binding energy by stimulated emission~\cite{Danzl2008, Ni2008, Lang2008,
+  Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
+So far, most molecular association has been achieved for bialkali molecules
+by magnetoassociation using a magnetic Feshbach scattering resonance.
+The only exceptions are Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states
+are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012},
+and $^{87}$Rb$^{85}$Rb,
+where there are molecular states bound by $1\sim2~\mathrm{MHz}$~\cite{He331}.
+With these requirements, molecules involving non-magnetic atoms
+or atoms without narrow intercombination lines remain difficult to associate.
 % These requirements limit the generality of previous association techniques.
-% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques.
+% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited-state lines limits the generality of previous association techniques.
 % to more diverse species.
 
-Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}a.
-The scheme does not rely on a Feshbach resonance, few MHz level bound states, or a narrow excited state.
-The resulting single molecule is in a well-defined internal quantum state and predominately in its motional ground state.
-A vibrational state of the electronic excited state $\mathrm{c^3\Sigma^+}(\Omega = 1)$ is used as the intermediate state in the Raman scheme, and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation.
-To further reduce the photon scattering and sensitivity to laser intensity noise, we choose the initial and final state to balance the two Rabi frequencies as much as possible.
-This system-independent approach can be used for creating new molecules atom-by-atom with full quantum state control.
+Here, we demonstrate coherent association of an atom pair to a weakly bound molecule
+using a two-photon optical Raman transfer via an electronic excited state,
+schematically shown in Fig.~\ref{f-theory}a.
+The scheme does not rely on a Feshbach resonance,
+molecular states bound by a few MHz, or a narrow excited state.
+The resulting single molecule is in a well-defined internal quantum state
+and predominantly in its motional ground state.
+A vibrational state of the electronic excited state $\mathrm{c^3\Sigma^+}(\Omega = 1)$
+is used as the intermediate state in the Raman scheme,
+and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation.
+To reduce the photon scattering and sensitivity to laser intensity noise further,
+we choose the initial and final state to balance the two Rabi frequencies as much as possible.
+This system-independent approach can be used for creating new molecules atom-by-atom
+with full quantum state control.
 
@@
   \caption{Optical creation of single molecule from single atoms in tweezer.
-    (a) Schematic of the optical transition from an atom pair to a weakly-bound molecule.
+    (a) Schematic of the optical transition from an atom pair to a weakly bound molecule.
     The initial state is the relative motional ground state between the two atoms
@@
     by $\Delta$ in order to suppress the scattering during the transfer.
-    (b) Comparison between using a weakly-bound and a deeply bound excited state
+    (b) Comparison between using a weakly bound and a deeply bound excited state
     as intermediate state for the Raman transition.
@@
     has a smaller Raman Rabi frequency ($\Omega_{R}$)
-    compared to the weakly-bound excited state (lower half $v'=63$) at a given detuning.
+    compared to the weakly bound excited state (lower half $v'=63$) at a given detuning.
     However, the scattering rate ($\Gamma_{s}$) is also much lower,
     which results in a larger Raman Rabi frequency to scattering rate ratio.
-    (c) Enhancement of the short range wavefunction.
+    (c) Enhancement of the short-range wavefunction.
     The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
@@
 
-The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}a), where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
+The essence of an optical Raman transfer can be illustrated
+using a three-level system shown in Fig.~\ref{f-theory}a,
+where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
@@
 and therefore the scattering is predominantly from the target molecular state.
-Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally.
-Thus, the scattering rate is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power.
+Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally.
+Thus, the scattering rate is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited-state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power.
 Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
@@
 in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
-However, for a complete picture, the many excited vibrational states in a molecular potential
-as well as the excited atomic continuum need to be considered.
+However, a complete picture must include both the many vibrational levels
+of the excited electronic state and the atomic continuum.
 The total scattering rate and Raman Rabi rate become a sum of the scattering rates
@@
 With these considerations, using a weakly bound excited state as the intermediate state
-suffers from strong scattering of the nearby excited atomic continuum, resulting in large incoherence and loss to other molecular states.
+suffers from strong scattering due to the nearby excited atomic continuum,
+resulting in large incoherence and loss to other molecular states.
 This scattering is proportional to $1/\delta_{\mathrm{thresh}}^2$,
@@
 The sum of the squares of the wavefunction overlap
-between the target weakly-bound molecular state
+between the target weakly bound molecular state
 and all the excited molecular bound states is only about $0.02$,
-suggesting that there is significant matrix element
-between the target molecular state and the excited atomic continuum (See Supplementary Material\todo{proper cite}).
+suggesting that there are significant matrix elements
+between the target molecular state and the excited atomic continuum.
 This calculation shows that the ratio of the Raman Rabi rate to scattering rate
 can be made larger for more deeply bound states compared to weakly bound states
-at a cost of a smaller Raman Rabi frequency
-(Fig.~\ref{f-theory}b, full result in Supplementary Material \todo{proper cite})
-As a result, we choose the $v'=0$ of $\mathrm{c^3\Sigma^+}(\Omega = 1)$ as an intermediate state
-to drive the Raman transition.
+at a cost of a smaller Raman Rabi frequency, as shown in Fig.~\ref{f-theory}b;
+see Supplementary Material for details.
+As a result, we choose the $v'=0$ level of $\mathrm{c^3\Sigma^+}(\Omega = 1)$
+as an intermediate state to drive the Raman transition.
 
 In addition to the intermediate state,
-choosing an initial and a final state for a large $ \Omega_a/\Omega_m $ ratio
+choosing an initial and a final state for a large ratio $\Omega_a/\Omega_m$
 maximizes the Raman Rabi frequency at a given detuning.
@@
   to account for the Stark shift caused by both beams.}.
-Due to the small size of the intermediate state wavefunction as compared to the trapped atoms,
+Due to the small extent of the intermediate-state wavefunction
+compared to that of the trapped atoms,
 $\Omega_a$ is approximately proportional to
-the value of the relative atomic wavefunction at short distance
-within the molecular potential.
-To increase the amplitude within the molecular potential,
-one can increase the external confinement of atom pairs.
-Using a harmonic oscillator approximation,
-the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $ or $P^{3/8}$,
+the amplitude of the relative atomic wavefunction at short distance,
+within the range of the molecular potential.
+To increase this amplitude, one can increase the external confinement of atom pairs.
+Using a harmonic approximation,
+the short-range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $ or $P^{3/8}$,
 where $ \omega_{\text{trap}} $ is the trap frequency and $P$ is the power in the trap\cite{Mies2000}.
@@
 (positive or negative).
-For these states, the phase shift in the relative wavefunction
-between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}c).
+For such states, the amplitude of the relative atomic wavefunction is substantially enhanced
+at short range, as shown in Fig.~\ref{f-theory}c.
 % The increase in the coupling is proportional to (quote/cite Olive's equation?).
 For our system of Na and Cs atoms,
-we choose a spin state combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=3,m_F=3}_{\Cs}$ that has a large and negative scattering length of
-$ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0$~\cite{Hood2019}.
+we choose a spin-state combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=3,m_F=3}_{\Cs}$ that has a large and negative scattering length of
+$a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0$~\cite{Hood2019}.
 All other stable spin combinations give smaller scattering lengths ($<~50~a_0$).
@@
 % In addition to the increased atomic coupling, $ \Omega_a $,
-Coupled channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $,
+coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $,
 with the intermediate state when compared to bound states of the other spin compositions.
-This further increases the $\Omega_a/\Omega_m$ ratio when using the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.
+This further increases the ratio $\Omega_a/\Omega_m$ when using the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.
 % $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
 This combination
-results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003
+results in a ratio $\Omega_a/\Omega_m$ of about 0.05 instead of a ratio of about 0.003
 with the other combinations, thus relaxing the intensity stability requirement to the few percent level.
@@
 % Thus, we choose the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination.
-% \textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
+% \textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled-channel calculation anywhere...)
 
@@
     to define the quantization axis.
-    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
+    As a result, the atoms experiences predominantly $\pi$ polarization from the tweezer.
     \label{f-raman}}
@@
 %% Preparation
-Experimentally, we first prepare two atoms in a well-defined external and internal quantum state using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}.
-In brief, the experimental cycle begins by stochastically loading a single ${}^{23}\Na$ atom and a single ${}^{133}\Cs$ atom into separate optical tweezers.
-The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom to be able to post select the experimental result on the initial loading condition.
-Raman sideband cooling is then applied to prepare both atoms simultaneously into the 3-dimensional motional ground state of their optical tweezers.
-After cooling, the Na and Cs atoms are in a spin state of $\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=4,m_F=4}_{\Cs} $ %and are merged into the same tweezer~\cite{Liu2019}.
-%The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $.
-which has a small scattering length. The small two atom interaction allows the merging of the two atoms to be done with minimum pertubation so that they remain in the motional ground state.
+Experimentally, we first prepare two atoms in a well-defined external and internal quantum state
+using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}.
+In brief, the experimental cycle begins by stochastically loading a single ${}^{23}\Na$ atom
+and a single ${}^{133}\Cs$ atom into separate optical tweezers.
+The atoms are initially imaged to distinguish between loading of two atoms,
+one atom (Na or Cs), or no atom to be able to post-select from the experimental results
+based on the initial loading condition.
+Raman sideband cooling is then applied to prepare both atoms simultaneously
+in the 3-dimensional motional ground state of their optical tweezers.
+After cooling, the Na and Cs atoms are in the spin state~$\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=4,m_F=4}_{\Cs}$,
+which has a small scattering length.
+The weak two-atom interaction allows the merging of the two tweezers to be done
+with minimum pertubation so that they remain in the motional ground state.
 
 % After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
-Next, we drive the atoms into the large scattering length $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination to use as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.
-%using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\Cs}}$ state.
-The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
-This spin flip selectively transfers atoms in the relative motional ground state, removing any initial hot atom background from imperfect cooling \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motional ground state.}.
-For the experiment reported here, $31~\mathrm{\%}$ of our initial two atom population is successfully transferred.
+Next, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$,
+which has large scattering length,
+by performing a Cs spin flip while taking into account
+the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.
+We use this as the initial atomic state for Raman transfer.
+This spin flip selectively transfers atoms in the relative motional ground state,
+removing any background from atoms in excited motional states
+\footnote{This interaction shift is larger than the differential axial trapping frequency
+  between Na and Cs atoms, which decouples the relative and center of mass motional state
+  and improves the robustness of our preparation of the relative motional ground state.}.
+For the experiment reported here,
+$31~\mathrm{\%}$ of our initial two-atom population is transferred.
 % of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
@@
 % After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
-To perform the Raman transfer of an atom pair to the target weakly bound molecular state, we use the tweezer beam itself as the Raman beams by turning on two frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}b inset).
-The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time.
-Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50 ~\mathrm{GHz}$ to filter the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
-We observed a reduction of the scattering rate by a factor of $2$ due to suppression of the broadband amplified spontaneous emission (ASE) from the laser that couples to other excited states.
-% to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
-After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged.
-Both frequencies are kept on for a specified duration before the process is reversed and the tweezer returns to a single frequency.
-% In addition to reducing the number of laser beams during the Raman transition,
+To perform the Raman transfer of an atom pair to the target weakly bound molecular state,
+we use the tweezer beam itself as the Raman beams by turning on two frequencies
+in the tweezer during the Raman pulse, as shown in Fig.~\ref{f-raman}b inset.
+The dual use of the tweezer beam not only eliminates additional scattering sources
+or undesired laser frequencies,
+but also allows a tight focus to maximize the Raman Rabi frequency
+and minimize the transfer time.
+Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50~\mathrm{GHz}$
+to filter the laser spectrum generated by a fiber amplifier
+that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
+We observe a reduction of the scattering rate by a factor of $2$
+due to suppression of the broadband amplified spontaneous emission (ASE) from the laser
+that couples to other excited states.
+After the total tweezer power is set to the desired value,
+we smoothly ramp down the power of one frequency in the tweezer
+while simultaneously ramping up the power of a different frequency
+so that the total tweezer power remains unchanged.
+Both frequencies are kept on for a specified duration before the process is reversed
+and the tweezer returns to a single frequency.
 
@@
 We use a Bragg grating with a line width (FWHM) of $50~\mathrm{GHz}$ to clean up the laser spectrum and found it reduces the scattering rate by at least a factor of $2$
-% for a particular single photon detuning.
+% for a particular single-photon detuning.
 
@@
 
-We choose the tweezer frequency to be far detuned ($145 ~\mathrm{GHz}$) from the $v' = 0$ line, and guided by coupled channel calculations,
-we locate the Raman resonance for the atom to molecule transition at
-$770.57150(9) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}a)
-with $3.75~\mathrm{mW}$ tweezer power.
+We choose the tweezer frequency to be far detuned (by $145 ~\mathrm{GHz}$)
+from the $v' = 0$ line. Guided by coupled-channel calculations,
+we locate the Raman resonance for the atoms-to-molecule transition at
+$770.57150(9) ~\mathrm{MHz}$ with $3.75~\mathrm{mW}$ tweezer power,
+as shown in Fig.~\ref{f-raman}a.
 % (We can maybe add information about the prediction here?)
@@
 The molecular state is dark to the imaging step,
-so successful transfer of the atoms to the molecular state will be detected as loss.
-We observed a Fourier limited linewidth which is evidence of a coherent transfer.
+so successful transfer of the atoms to the molecular state is detected as loss.
+We observe a fourier-limited linewidth, which is evidence of a coherent transfer.
 In order to verify the coherence of the transfer directly,
@@
 Fitting the data with a decaying Rabi oscillation suggests that
-$69~\mathrm{\%}$ of initial ground state atoms are transferred into the molecular state after a $\pi$ pulse.
-This transfer efficiency is mainly limited by the molecular lifetime
+$69~\mathrm{\%}$ of atoms initially in the motional ground state are transferred into the molecular state after a $\pi$ pulse.
+This transfer efficiency is limited mainly by the molecular lifetime,
 which can be measured directly by preparing the molecule with a $\pi $ pulse
 and then using a second $\pi$ pulse to dissociate the molecule back to atoms
-after a variable wait time (Fig.~\ref{f-lifetime}a).
-The result shows a molecular lifetime of $0.199(9)~\mathrm{ms}$
+after a variable wait time.
+The result in Fig.~\ref{f-lifetime}a shows a molecular lifetime of $0.199(9)~\mathrm{ms}$
 consistent with the decay of Rabi oscillation.
@@
 that includes a Raman Rabi frequency and
-a finite lifetime for the molecular state (Fig.~\ref{f-raman}a and b).
-We account for the effect of atomic state loss by measuring the one and
-two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}b)
-without turning on the second frequency.
-The fit shows that we have a Raman Rabi frequency of $2\pi\times3.28(4) ~\mathrm{kHz}$.
+a finite lifetime for the molecular state, as shown in Fig.~\ref{f-raman}a and b.
+We account for the effect of atomic state loss by measuring the one-body and
+two-body lifetime of the atoms directly without turning on the second frequency,
+as shown in Fig.~\ref{f-lifetime}b.
+The fit gives a Raman Rabi frequency of $2\pi\times3.28(4)~\mathrm{kHz}$.
 
-The efficiency of the transfer is lower than expected from theory and arises from the ratio of the molecule scattering rate to the Rabi frequency being 10 times larger than predicted.
+The efficiency of the transfer is lower than expected
+because the ratio of the molecular scattering rate to the Rabi frequency
+is 10 times larger than predicted.
 Based on the discussion above, if this discrepancy arises from the $v'=0$ excited state,
-it can be either due to a high ratio of $\Omega_m / \Omega_a$ or a large $\Gamma_e$.
-Additionally, coupling to other excited states can also add an offset to
-both the Raman Rabi frequency and the scattering rate
-which can affect the scattering rate to Raman Rabi frequency ratio.
+it can be due either to a high ratio $\Omega_m / \Omega_a$ or to a large $\Gamma_e$.
+Additionally, coupling to other excited states can add an offset to
+both the Raman Rabi frequency and the scattering rate and thus affect their ratio.
 
 In order to verify whether any one of these known sources are the origin of the discrepancy,
-we measured the properties of the Raman resonance as a function of the tweezer power and single photon detuning.
+we measured the properties of the Raman resonance as a function of the tweezer power and single-photon detuning.
 These dependencies allow us to experimentally determine the matrix elements,
@@
 we can further observe a $1/\Delta$ component
-and a constant background in the experimentally explored region (Fig.~\ref{f-det}a).
+and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a.
 The background is caused by coupling to other excited states that are further away in energy.
@@
 
-In order to calculate the $\Omega_m/\Omega_a$ ratio,
+In order to calculate the ratio $\Omega_m/\Omega_a$,
 we now need to extract $ \Omega_a $.
@@
 due to the change in the atomic wavefunction caused by
-tighter confinement at higher power (Fig.~\ref{f-det}b).
+tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
 As discussed before, for weakly interacting particles,
@@
 Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
-which fits well to our experimental result (Fig.~\ref{f-det}c).
-Similar to the light shift, the Raman Rabi frequency's detuning dependence is determined by a constant background component and
-a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$.
+which fits well to our experimental result, as shown in Fig.~\ref{f-det}c.
+Similar to the light shift, the detuning dependency of the Raman Rabi frequency
+is determined by a constant background component and
+a $v'=0$ component that scales as $1/\Delta$.
 The $v'=0$ component of the Raman Rabi frequency is
@@
 $2\pi \times 12.1(3)~\mathrm{MHz}$.
-This gives a matrix element ratio of $11.6(3)$,
+This gives a matrix-element ratio of $11.6(3)$,
 which is in fact better than the theory prediction of $23.8$ (Table \ref{tab:rabi_freqs}).
@@
 Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $20~\mathrm{MHz}$ using photoassociation (PA) spectroscopy.
-This suggests that the excited state linewidth should not cause
+This suggests that the excited-state linewidth should not cause
 a stronger than expected scattering from $v'=0$ state either.
@@
   \caption{Comparison between theory and experiment of the Rabi frequencies $\Omega_m$ and $\Omega_a$ at $3.75$ mW tweezer power.
-The experimentally measured $\Omega_m/\Omega_a$ ratio is smaller than the theory prediction.}
+The experimentally measured ratio $\Omega_m/\Omega_a$ is smaller than the theory prediction.}
   \label{tab:rabi_freqs}
@@
 With the $ v' = 0 $ state ruled out as the source of discrepancy between experiment and theory,
-we now consider the background effects from other states with larger single photon detuning.
-In the Raman Rabi frequency fit, the fitted background is of an opposite sign from the Raman Rabi frequency for single photon detunings red of the $v' = 0 $ transition.
-Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$ at the current detuning.
-However, this difference is not enough to explain the greater than a factor of $10$ discrepancy
+we now consider the background effects from other states with larger single-photon detuning.
+In the Raman Rabi frequency fit,
+the fitted background is of opposite sign from the Raman Rabi frequency
+for single-photon detunings red of the $v' = 0 $ transition.
+Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$
+at the current detuning.
+However, this difference is not enough to explain the discrapancy of more than a factor of $10$
 present in the experiment.
-Due to the change in sign of the Raman Rabi frequency as a function of detuning when crossing a resonance, the same background will increase the Raman Rabi frequency for detunings blue of the $v' = 0$ transition, which increases the Raman Rabi frequency.
-Unfortunately, we have observed additional nearby excited states belonging to a different excited state potential at higher frequencies
+Due to the change in sign of the Raman Rabi frequency as a function of detuning
+when crossing a resonance, the same background will increase the Raman Rabi frequency
+for positive detunings from the $v' = 0$ transition,
+which increases the Raman Rabi frequency.
+Unfortunately, we observe additional nearby excited states
+belonging to a different electronically excited state at higher frequencies
 which prevent the blue side of the transition to be usable for the Raman transition.
@@
   does not lead to scattering but only decherence.}
-These results suggest that the decoherence or loss we observed during the Raman transition
+These results suggest that the decoherence or loss we observe during the Raman transition
 comes from either a higher than expected background scattering rate
 or a different intrinsic or technical source that we have not accounted for.
-We have observed a decrease in the coherence time by a factor of 2 without the ASE filter,
+We observe a decrease in the coherence time by a factor of 2 without the ASE filter,
 suggesting the spectral purity of the laser is a significant source of scattering.
-Other sources that can contribute to the decoherence includes
+Other sources that can contribute to the decoherence include
 the stability of the tweezer power and the magnetic field.
-Based on the Raman Rabi frequency to light shift ratio (Fig.~\ref{f-det}c),
-the requirement on the tweezer power stability is $0.8~\mathrm{\%}$ at $3.75~\mathrm{mW}$, which we stabilize to $0.1~\mathrm{\%}$ so this should not be a major source
-of decoherence.
+Based on the ratio of the Raman Rabi frequency to light shift, shown in Fig.~\ref{f-det}c,
+the requirement on the tweezer power stability is $0.8~\mathrm{\%}$ at $3.75~\mathrm{mW}$,
+which we stabilize to $0.1~\mathrm{\%}$ so this should not be a major source of decoherence.
 Similarly, we measured a Zeeman shift of $42.2(2)~\mathrm{kHz/G}$
@@
 The scattering rate of the molecule also depends on the tweezer power and detuning, and becomes smaller when the power is lowered.
-At $0.75~\mathrm{mW}$ tweezer power, we have observed
-a molecule lifetime as long as $1~\mathrm{ms}$.
+At $0.75~\mathrm{mW}$ tweezer power, we observe a molecule lifetime as long as $1~\mathrm{ms}$.
 However, since the technical noise that can lead to decoherence
@@
 we measure the two-body scattering rate
-without turning on the second frequency (Fig.~\ref{f-lifetime}b inset).
-The scattering rate scales as $P_{\mathrm{tweezer}}^{2.58}$ which is inconsistent
-with a single photon scattering process.
+without turning on the second frequency, as shown in Fig.~\ref{f-lifetime}b inset.
+The scattering rate scales as $P_{\mathrm{tweezer}}^{2.58}$,
+which is inconsistent with a single-photon scattering process.
 We have not been able to observe a dependency on the detuning in order to verify
@@
 In conclusion, we have formed a weakly bound NaCs molecule in an optical tweezer
-via an optical Raman transfer.
+by optical Raman transfer.
 A theoretical investigation including all excited states of $\mathrm{c^3\Sigma^+}(\Omega = 1)$,
-the excited atomic continuum, and coupled channel ground state wavefunctions indicated
+the excited atomic continuum, and coupled-channel ground state wavefunctions indicated
 better transfer efficiency using a deeply bound intermediate state
@@
 by increasing the ratio of the up-leg to down-leg Rabi frequency
-$\Omega_a/\Omega_m$ by exploring the possibility of
-driving to more deeply bound states.
-There may also be a better choice of single photon detuning to increase the Raman Rabi frequency,
+$\Omega_a/\Omega_m$, for example by driving to more deeply bound states.
+There may also be a better choice of single-photon detuning to increase the Raman Rabi frequency,
 since our location results in about $30~\mathrm{\%}$ cancellation of the Raman Rabi frequency
@@
 Our technique can be applied to form a more diverse set of molecular species,
-since it does not rely on a magnetic Feshbach resonance, bound states at the MHz-level,
-or a narrow excited state. The formation of a weakly-bound molecule is a key step
+since it does not rely on a magnetic Feshbach resonance, states bound by a few MHz,
+or a narrow excited state. The formation of a weakly bound molecule is a key step
 in forming rovibrational ground state molecules.
-Combined with real time rearrangement \cite{Barredo2016, Endres2016},
-defect free arrays of highly controlled molecules comprise a promising
+Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},
+defect-free arrays of highly controlled molecules comprise a promising
 and flexible platform for quantum simulation and quantum computing applications.

### 2020-11-09 sm.tex
Update on Overleaf.

@@
 We use the $ \ket{F_{\text{Na}} = 2, m_{F_{\text{Na}}} = 2, F_{\text{Cs}} = 3, m_{F_{\text{Cs}}} = 3}$ spin combination, so states with total $ m_F = 5 $ are included.
-These states, written in the basis $ \ket{S, m_S, I, m_I}$, include $ \ket{0,0,5,5}, \ket{1,0$
+These states, written in the basis $ \ket{S, m_S, I, m_I}$, include $ \ket{0,0,5,5}, \ket{1,0,5,5}, \ket{1,1,5,4}, \ket{1,1,4,4} $, where $S = 0,1$ is the total electron sp and $ I = 2,3,4,5 $ is the total nuclear spin
 

### 2020-11-09 sm.tex

--- 2020-11-09 sm.tex
@@
 We use the $ \ket{F_{\text{Na}} = 2, m_{F_{\text{Na}}} = 2, F_{\text{Cs}} = 3, m_{F_{\text{Cs}}} = 3}$ spin combination, so states with total $ m_F = 5 $ are included.
-These states, written in the basis $ \ket{S, m_S, I, m_I}$, include $ \ket{0,0,5,5}, \ket{1,0$
+These states, written in the basis $ \ket{S, m_S, I, m_I}$, include $ \ket{0,0,5,5}, \ket{1,0,5,5}, \ket{1,1,5,4}, \ket{1,1,4,4} $, where $S = 0,1$ is the total electron spin and $ I = 2,3,4,5 $ is the total nuclear spin.
 

### 2020-11-09 plot_raman_full.jl
Wide Raman theory plot without ratio

@@ -22,51 +22,22 @@ const data = LibArchive.Reader(fname) do reader
     LibArchive.next_header(reader)
     readdlm(reader, ',', skipstart=1)
 end
-const prefix = joinpath(@__DIR__, "imgs", "raman_theory")
+const prefix = joinpath(@__DIR__, "imgs", "raman_theory_full")
 
-figure()
-l1 = plot(data[:, 1], abs.(data[:, 2] ./ 2π / 1000), "C0",
-          label="\$\\Omega_{Raman}\$")
-l2 = plot(data[:, 1], abs.(data[:, 4] ./ 2π / 1000), "C1",
-          label="\$\\Gamma_{scatter}\$")
+figure(figsize=[12.8, 4.8])
+l1 = plot(data[:, 1] ./ 1000, abs.(data[:, 2] ./ 2π / 1000), "C0",
+          label="\$\\Omega_{R}\$")
+l2 = plot(data[:, 1] ./ 1000, abs.(data[:, 4] ./ 2π / 1000), "C1",
+          label="\$\\Gamma_{s}\$")
 ylabel("\$2\\pi\\cdot \\mathrm{kHz}\$")
-xlabel("One-Photon Detuning (GHz)")
+xlabel("Raman Single-Photon Frequency (THz)")
 yscale("log")
-ylim([0.001, 10])
+ylim([0.003, 100])
+yticks([0.01, 0.1, 1, 10, 100], ["0.01", "0.1", "1", "10", "100"])
 grid()
-ax = gca()
-ax2 = ax.twinx()
-l3 = ax2.plot(data[:, 1], abs.(data[:, 2] ./ data[:, 4]), "C2",
-              label="\$\\frac{\\Omega_{Raman}}{\\Gamma_{scatter}}\$")
-ls = [l1; l2; l3]
-legend(ls, [l.get_label() for l in ls], fontsize="x-small",
-       loc="lower right", bbox_to_anchor=(1, 0.05))
-xlim([287500, 345000])
-yscale("log")
-ylim([0.1, 100])
-ax2.tick_params(axis="y", labelcolor="C2")
-# setp(ax2.get_yticklabels(), fontweight="bold")
+legend(ncol=2, loc="lower center", bbox_to_anchor=(0.5, 0.95), frameon=false)
+gca().yaxis.set_label_coords(-0.04, 0.55)
+xlim([287.5, 351.5])
[…]

### 2020-11-09 sm.tex

--- 2020-11-09 sm.tex
@@
 
-\section{Raman Transfer with Many Intermediate States}
+\section{Raman Transfer with Many Intermediate States} \label{sm:sect_2}
 With multiple intermediate states, the total Raman Rabi frequency, scattering rate, and light shift become a sum over all these possible states.
@@
 With the cylindrical symmetry present at non-zero magnetic field, the magnetic quantum number is a good quantum number.
-We use the $ \ket{F_{\text{Na}} = 2, m_{F_{\text{Na}}} = 2, F_{\text{Cs}} = 3, m_{F_{\text{Cs}}} = 3}$ spin combination, so states with total $ m_F = 5 $ are included.
-These states, written in the basis $ \ket{S, m_S, I, m_I}$, include $ \ket{0,0,5,5}, \ket{1,0$
+We use the $ \ket{F_{\text{Na}} = 2, m_{F_{\text{Na}}} = 2, F_{\text{Cs}} = 3, m_{F_{\text{Cs}}} = 3}$ spin combination, so channels with total $ m_F = 5 $ are included.
+These channels, written in the basis $ \ket{S, m_S, I, m_I}$, include $ \ket{0,0,5,5}, \ket{1,0,5,5}, \ket{1,1,5,4}, \ket{1,1,4,4} $, where $S = 0,1$ is the total electron spin and $ I = 2,3,4,5 $ is the total nuclear spin.
+For each of these channels, there is a different vibrational wavefunction.
+In this work, we assume the excited state wavefunction is a single-channel wavefunction, so that it is purely triplet.
+Thus, only the triplet component of the coupled-channel ground state wavefunction contributes to $\Omega_a$ and $ \Omega_m $.
+
+The full calculation using the methods in section \ref{sm:sect_2} is shown in figure XXX.
+The strong contribution from the atomic threshold arises from the large overlap between the weakly-bound molecular state and the atomic continuum.
+This leads to a $1/\delta_{\text{thresh}}^2$ dependence of the scattering rate and favors deeply bound states as the intermediate state.
+The Raman Rabi frequency is larger than the scattering rate only for these deeply bound states.
+
+Since our coupled-channel calculations include the harmonic confinement, we can calculate the enhancement in $\Omega_a$ with increasing confinement.
+Using two calculations with $ \omega_{\text{trap}} = 36.5~\mathrm{kHz}$ and $\omega_{\text{trap}} = 80~\mathrm{kHz}$ trapping frequencies, and assuming a power law scaling, we find $ \Omega_a \propto \omega_{\text{trap}}^{0.58} $.
+Thus, $\Omega_a \propto P^{0.29} $, which was also experimentally verified.
+However, we note that in the actual experiment, the radial and axial trapping frequencies differ
 

### 2020-11-09 sm.tex
Update on Overleaf.

@@
 The Raman Rabi frequency is proportional to $\sqrt{P_mP_a} $.
-With a fixed total power and thus fixed scattering rate, the Raman Rabi frequency is maximized by maximizing $\sqrt{P_m(P_{\text{tot}} - P_m)}$, which is achieved when $ P_m = P_a = P_{\text{tot}}/2$.
+With a fixed total power and thus fixed scattering rate, the Raman Rabi frequency is maximized when $ P_m = P_a = P_{\text{tot}}/2$.
 
 For the purposes of this work, we denote $\Omega_a $($\Omega_m$) as the Rabi frequencies to drive a transition from the atom (target molecule) state to the intermediate state used in the Raman transition corresponding to the power in a single beam, $P_a$ ($P_m$).
-Thus, the Raman Rabi frequency remains $\Omega_a\Omega_m/2\Delta$, where $ \Delta $ is the single photon detuning.
+Thus, the Raman Rabi frequency is $\Omega_a\Omega_m/2\Delta$, where $ \Delta $ is the single photon detuning.
 Cross coupling affects the scattering rate and light shift, and assuming equal powers in both beams, these quantities become $ \Gamma_e \Omega_m^2 / 2\Delta^2 + \Gamma_e \Omega_a^2 / 2\Delta^2 $ and $ \Omega_m^2/2\Delta - \Omega_a^2/2\Delta $, where $\Gamma_e$ is the excited state linewidth.
@@
 With multiple intermediate states, the total Raman Rabi frequency, scattering rate, and light shift become a sum over all these possible states.
-In our model, we consider all vibrational states of $ c^3\Sigma^+(\Omega = 1) $ as intermediate states, as well as states in the atomic continuum.
-The Rabi frequency between two states is proportional to the electronic dipole moment, arising from the electronic wavefunctions, and the vibrational wavefunction (in the relative motion coordinate of the two atoms) overlap between the two states.
+In our model, we consider all vibrational states of $ \mathrm{c^3\Sigma^+(\Omega = 1)} $ and states in the atomic continuum as intermediate states.
+The Rabi frequency between two states is proportional to the electronic dipole moment, arising from the electronic wavefunctions, and the overlap of the vibrational wavefunctions.
 Under the assumption that the electronic dipole moment $ d $ is the same for all transitions between the ground state and the excited electronic state, the total Raman Rabi frequency becomes:
@@
 
-where $\ket{a}$ ($\ket{m}$) are the relative coordinate wavefunctions for the trapped atom (target-molecule) state, and $\ket{v'}$ is the relative coordinate wavefunction for the excited state which includes both bound molecule states and the atomic continuum.
+where $\ket{a}$ ($\ket{m}$) are the relative coordinate wavefunctions for the trapped atomic (target molecular) state, and $\ket{v'}$ is the relative-coordinate wavefunction for the excited state which includes both bound molecular states and the atomic continuum.
 $\Delta_{v'}$ is a single photon detuning with respect to the $\ket{v'}$ state, $ E $ is the electric field for the power in the single beam given a waist size.
@@
 
-where $ v'_{\text{max}}$ corresponds to the most weakly bound electronically excited molecular state.
+where $ v'_{\text{max}}$ corresponds to the excited molecular state, which is most weakly bound.
 The first term can be calculated numerically given an excited state potential.
@@
 leading to strong scattering from the atomic continuum.
-We note that this model also leads to a component in the scattering rate that is proportional to $ 1/\delta_{\text{thresh}}^2$ and is smaller as one detunes farther from the threshold.
+We note that this model leads to a component in the scattering rate that is proportional to $ 1/\delta_{\text{thresh}}^2$ and is smaller as one detunes farther from the threshold.
 
@@
 \section{Calculating Matrix Elements with Coupled Channel Ground State}
-The free atom state (with spherically symmetric harmonic confinement) and target weakly-bound molecular state are calculated using coupled-channel methods.
+The free atom state (with spherically-symmetric harmonic confinement) and target weakly-bound molecular state are calculated using coupled-channel methods.
 With the cylindrical symmetry present at non-zero magnetic field, the magnetic quantum number is a good quantum number.
-We use the $ \ket{F_{\text{Na}} = 2, m_{F_{\text{Na}}} = 2, F_{\text{Cs}} = 3, m_{F_{\text{Cs}}} = 3}$ spin combination, so channels with total $ m_F = 5 $ are included.
+We use the spin combination $ \ket{F_{\text{Na}} = 2, m_{F_{\text{Na}}} = 2, F_{\text{Cs}} = 3, m_{F_{\text{Cs}}} = 3}$, so channels with total $ m_F = 5 $ are included.
 These channels, written in the basis $ \ket{S, m_S, I, m_I}$, include $ \ket{0,0,5,5}, \ket{1,0,5,5}, \ket{1,1,5,4}, \ket{1,1,4,4} $, where $S = 0,1$ is the total electron spin and $ I = 2,3,4,5 $ is the total nuclear spin.
@@
 
-The full calculation using the methods in section \ref{sm:sect_2} is shown in figure XXX.
+The full calculation using the methods in section \ref{sm:sect_2} is shown in figure \ref{f-sm}.
 The strong contribution from the atomic threshold arises from the large overlap between the weakly-bound molecular state and the atomic continuum.
@@
 
+\begin{figure}[ht!]
+  \includegraphics[width=\textwidth]{imgs/raman_theory_full.pdf}
+  \caption{ Full calculation of the Raman Rabi frequency and scattering rate as a function of the single-photon frequency including all vibrational states of $ \mathrm{c^3\Sigma^+(\Omega = 1)}$ and the atomic continuum.
+The second frequency in the Raman transition is offset by about $770~\mathrm{MHz}$ and resonant with the two photon transition.
+The assumed excited-state linewidth for all molecular lines is $20~\text{MHz} $.
+    \label{f-sm}}
+\end{figure}
+
 Since our coupled-channel calculations include the harmonic confinement, we can calculate the enhancement in $\Omega_a$ with increasing confinement.
@@
 Thus, $\Omega_a \propto P^{0.29} $, which was also experimentally verified.
-However, we note that in the actual experiment, the radial and axial trapping frequencies differ
-
+However, we note that in the actual experiment, our system does not have spherically symmetric confinement.
+The radial trapping frequency is about $5.7$ times larger than the axial trapping frequency.
 \todo{

### 2020-11-10 paper.tex
NFC: Fix latex warning about figure position specifier
Comments from Jeremy

@@
   The molecule has a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$
-  with more than $60~\mathrm{\%}$ of the molecule created in the motional ground state.
+  and are created with higher than $60~\mathrm{\%}$ probability in the motional ground state.
   This technique does not rely on narrow excited-state lines or Feshbach resonances
@@
 we choose a spin-state combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=3,m_F=3}_{\Cs}$ that has a large and negative scattering length of
-$a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0$~\cite{Hood2019}.
+$a(\uparrow_{\Na} \downarrow_{\Cs}) \approx -700a_0$~\cite{Hood2019}.
 All other stable spin combinations give smaller scattering lengths ($<~50~a_0$).
@@
 
-\begin{table}[h]
+\begin{table}[ht]
   \centering

### 2020-11-10 plot_wavefunction.jl
Explicitly set fontsize in plot_wavefunction. This will be used as reference to other plots

@@ -41,9 +41,10 @@ axvline(100, color="C0", ls="dashed", linewidth=3)
 grid()
 xlim([0, 3080])
 ylim([0, 7.3])
-ylabel("\$\\left|\\psi(R)\\right|^2\$")
-xlabel("R (Angstroms)")
-legend(fontsize="x-small")
+ylabel("\$\\left|\\psi(R)\\right|^2\$", fontsize=20)
+xlabel("R (Angstroms)", fontsize=20)
+gca().tick_params(axis="both", which="major", labelsize=15)
+legend(fontsize=13.88)
 NaCsPlot.maybe_save("$(prefix)")
 
 NaCsPlot.maybe_show()

### 2020-11-10 plot_raman.jl
Adjust fig1 font size

@@ -24,7 +24,7 @@ const data = LibArchive.Reader(fname) do reader
 end
 const prefix = joinpath(@__DIR__, "imgs", "raman")
 
-fig = figure(figsize=[1, 1] * 4.8)
+fig = figure(figsize=[1.11, 1.11] * 4.8)
 
 ax0 = fig.add_subplot(111)    # The big subplot
 ax0.spines["top"].set_color("none")
@@ -34,7 +34,7 @@ ax0.spines["right"].set_color("none")
 ax0.set_xticks([])
 ax0.set_yticks([])
 ax0.tick_params(labelcolor="w", top="off", bottom="off", left="off", right="off")
-ylabel("\$\\Omega_{R}\$ and \$\\Gamma_{s}\$ (\$2\\pi\\cdot \\mathrm{kHz})\$", fontsize="small")
+ylabel("\$\\Omega_{R}\$ and \$\\Gamma_{s}\$ (\$2\\pi\\cdot \\mathrm{kHz})\$")
 ax0.get_yaxis().set_label_coords(-0.13, 0.5)
 ax0.tick_params(axis="x", length=0)
 ax0.tick_params(axis="y", length=0)
@@ -45,7 +45,7 @@ tax0.tick_params(labelcolor="w", top="off", bottom="off", left="off", right="off
 tax0.tick_params(axis="x", length=0)
 tax0.tick_params(axis="y", length=0)
 tax0.get_yaxis().set_label_coords(1.118, 0.5)
-ylabel("\$\\Omega_{R}/\\Gamma_{s}\$", fontsize="small", color="C2")
+ylabel("\$\\Omega_{R}/\\Gamma_{s}\$", color="C2")
 
 ax1 = fig.add_subplot(211)
 plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ 2π / 1000), "C0",
@@ -80,7 +80,7 @@ tax2 = ax.twinx()
 l3 = tax2.plot(data[:, 1] .- 351271.53, abs.(data[:, 2] ./ data[:, 4]), "C2",
               label="\$\\frac{\\Omega_{R}}{\\Gamma_{s}}\$")
 ls = [l1; l2; l3]
-legend(ls, [l.get_label() for l in ls], fontsize="x-small", loc="upper right")
+legend(ls, [l.get_label() for l in ls], fontsize=13.88, loc="upper right")
 xlim([-35, 35])
 ylim([0, 1.49])
 tax2.tick_params(axis="y", labelcolor="C2")

### 2020-11-10 paper.tex
Add country to Purdue...
Association ...

@@
 \begin{document}
-\title{Coherent optical association of a single molecule}
+\title{Coherent optical association of atoms into a single molecule}
 \author{Yichao~Yu}
@@
 \author{Jonathan~D.~Hood}
-\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indianna, 47906}
+\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indianna, 47906, USA}
 \author{Lewis~R.~B.~Picard}
@@
   As a step towards this goal, we report on coherent association
-  of a single weakly bound NaCs molecule in an optical tweezer
+  of atoms into a single weakly bound NaCs molecule in an optical tweezer
   through an optical Raman transition without the use of a Feshbach resonance.

### 2020-11-10 sm.tex
format, regenerate pdf
Update on Overleaf.

@@
 Under the assumption that the electronic dipole moment $ d $ is the same for all transitions between the ground state and the excited electronic state, the total Raman Rabi frequency becomes:
-
 \begin{equation}
@@
 \end{equation}
-
 where $\ket{a}$ ($\ket{m}$) are the relative coordinate wavefunctions for the trapped atomic (target molecular) state, and $\ket{v'}$ is the relative-coordinate wavefunction for the excited state which includes both bound molecular states and the atomic continuum.
@@
 We can divide this sum into a sum over all the bound molecular states, and a sum over atomic continuum states.
-
 \begin{equation}
@@
 \end{equation}
-
 where $ v'_{\text{max}}$ corresponds to the excited molecular state, which is most weakly bound.
@@
 This allows us to pull it out of the sum, and we obtain:
-
 \begin{equation}
@@
 \end{equation}
-
 From requiring orthogonality,
-
 \begin{equation}
@@
 \end{equation}
-
 we derive an expression for the second sum in equation \ref{rabifreq}
-
 \begin{equation}
@@
 \end{equation}
-
 which can be calculated from the vibrational states of the excited state potential. Thus, the Raman Rabi frequency can be approximated as:
-
 \begin{equation}
@@
 \end{equation}
-
 We can account for the atomic continuum in the scattering rate in a similar way.
-
 \begin{align}
@@
 \end{align}
-
 where $\Gamma_{v'}$ is the excited state linewidth for the $\ket{v'}$ state, and we have assumed the atomic continuum states all have the same linewidth $\Gamma$.
 Using normalization, we derive an expression for the sum in the second term
-
 \begin{equation}
@@
 \end{equation}
-
 We then arrive at an expression for the scattering rate, accounting for the atomic continuum,
-
 \begin{equation}
@@
 \end{equation}
-
-The effect of the continuum is to add an extra state at the atomic threshold with strength proportional to the amount of wavefunction overlap between the target-molecular state and all atomic continuum states.
+We have replaced the full continuum with an effective state at the atomic threshold with strength proportional to the amount of wavefunction overlap between the target molecular state and all atomic continuum states.
 This term is especially important for our target-molecule state, because the square of the wavefunction overlap between the target-molecule state and all excited vibrational states is only 0.02
-
 \begin{equation}
@@
 \end{equation}
-
 leading to strong scattering from the atomic continuum.
@@
 The free atom state (with spherically-symmetric harmonic confinement) and target weakly-bound molecular state are calculated using coupled-channel methods.
-With the cylindrical symmetry present at non-zero magnetic field, the magnetic quantum number is a good quantum number.
-We use the spin combination $ \ket{F_{\text{Na}} = 2, m_{F_{\text{Na}}} = 2, F_{\text{Cs}} = 3, m_{F_{\text{Cs}}} = 3}$, so channels with total $ m_F = 5 $ are included.
+Due to the cylindrical symmetry of the system, the projection of the total spin $m_F \equiv m_{F_{\text{Na}}} + m_{F_{\text{Cs}}}$ is conserved in the transition.
+Since our initial spin state is $ \ket{F_{\text{Na}} = 2, m_{F_{\text{Na}}} = 2, F_{\text{Cs}} = 3, m_{F_{\text{Cs}}} = 3}$, we can couple to all channels with total $ m_F = 5 $.
 These channels, written in the basis $ \ket{S, m_S, I, m_I}$, include $ \ket{0,0,5,5}, \ket{1,0,5,5}, \ket{1,1,5,4}, \ket{1,1,4,4} $, where $S = 0,1$ is the total electron spin and $ I = 2,3,4,5 $ is the total nuclear spin.
-For each of these channels, there is a different vibrational wavefunction.
-In this work, we assume the excited state wavefunction is a single-channel wavefunction, so that it is purely triplet.
-Thus, only the triplet component of the coupled-channel ground state wavefunction contributes to $\Omega_a$ and $ \Omega_m $.
+The coupled-channel wavefunction contains a component in each of these channels .
+In this work, we assume the excited state wavefunction is a single-channel triplet wavefunction.
+Thus, only the triplet component of the coupled-channel ground state contributes to $\Omega_a$ and $ \Omega_m $.
 

### 2020-11-10 plot_atomic_loss_scaling.jl
Adjust fig2 and 3 font size

@@ -42,7 +42,7 @@ const prefix = joinpath(@__DIR__, "imgs", "atomic_loss_scaling")
 # ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$")
 # NaCsPlot.maybe_save("$(prefix)")
 
-figure(figsize=[4.8, 3.6])
+figure(figsize=[4.8, 3.6] .* 1.08792)
 ax = gca()
 bg = matplotlib.patches.Rectangle((0.625, 0.31), 3.625, 39.69, facecolor="white", alpha=0.9)
 ax.add_patch(bg)
@@ -57,8 +57,8 @@ xticks([1, 2, 4], ["1", "2", "4"])
 yticks([1, 3, 10, 30], ["1", "3", "10", "30"])
 ax.xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 ax.set_xticks(0.7:0.1:4, minor=true)
-xlabel("Tweezer Power (mW)", fontsize=15)
-ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$", fontsize=15)
+xlabel("Tweezer Power (mW)", fontsize=17)
+ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$", fontsize=17)
 tight_layout()
 NaCsPlot.maybe_save("$(prefix)_inset")
 

### 2020-11-10 plot_exp_data.jl

@@ -171,7 +171,7 @@ xlabel("Detuning From Resonance (kHz)")
 ylabel("Two-Body Survival")
 NaCsPlot.maybe_save("$(prefix)_raman_det")
 
-figure(figsize=[7.2, 5.4])
+figure(figsize=[7.2, 5.4] .* 1.263)
 errorbar([0.0], [ratio_00 * scale_1], [uncs_00 * scale_1], fmt="C0o", label="0.00 ms")
 plot([plot_freq_lo, plot_freq_hi] .- param_1[3], [v00 * scale_1, v00 * scale_1], "C0-")
 NaCsPlot.plot_survival_data(data_nacs_12′, scale_1, fmt="C1o", label="0.12 ms")
@@ -301,7 +301,7 @@ xlabel("Raman Time (ms)")
 ylabel("Fraction of Atomic Ground State")
 NaCsPlot.maybe_save("$(prefix)_norm_t_annotate")
 
-figure(figsize=[7.2, 5.4])
+figure(figsize=[7.2, 5.4] .* 1.263)
 NaCsPlot.plot_survival_data(data_nacs_t, scale_2,
                             fmt="C0o", label="770.5704 MHz")
 plot(plot_time, model_2d.(plot_time, 570.4, (param_2,)) .* scale_2, "C0")
@@ -338,7 +338,7 @@ xlabel("Atom Hold Time (ms)")
 ylabel("Two-Body Survival")
 NaCsPlot.maybe_save("$(prefix)_a_t")
 
-figure(figsize=[7.2, 5.4])
+figure(figsize=[7.2, 5.4] .* 1.26042)
 NaCsPlot.plot_survival_data(data_pa_m, 1 / param_pa[1], fmt="C0o")
 plot(plot_pa_time, model_exp(plot_pa_time, param_pa) ./ param_pa[1], "C0-")
 # text(7, 0.12 / param_pa[1], "\$\\tau_{atom}=$(1 / uncs_1[5])\\ \\mathrm{ms}\$", color="C0")
@@ -362,12 +362,12 @@ xlabel("Molecule Hold Time (ms)")
 ylabel("Two-Body Survival")
 NaCsPlot.maybe_save("$(prefix)_m_t")
 
-figure(figsize=[7.2, 5.4])
+figure(figsize=[7.2, 5.4] .* 1.26042)
[…]

### 2020-11-10 paper.tex
Other title option...

@@
 \title{Coherent optical association of atoms into a single molecule}
+% \title{Coherent optical creation of a single molecule}
 \author{Yichao~Yu}
@@
 the short-range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $ or $P^{3/8}$,
-where $ \omega_{\text{trap}} $ is the trap frequency and $P$ is the power in the trap\cite{Mies2000}.
+where $ \omega_{\text{trap}} $ is the trap frequency and $P$ is the power in the trap \cite{Mies2000}.
 However, additional power may not always be available, and will also lead to additional undesired scattering.
@@
 % In addition to the increased atomic coupling, $ \Omega_a $,
-coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $,
+Coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $,
 with the intermediate state when compared to bound states of the other spin compositions.

### 2020-11-10 plot_scaling.jl
Adjust fig4 font size

@@ -197,7 +197,7 @@ const prefix = joinpath(@__DIR__, "imgs", "scaling")
 
 const powers_plot = [15, 6, 3]
 
-figure()
+figure(figsize=[6.4, 4.8] * 1.11308)
 for i in 1:length(powers_plot)
     power = powers_plot[i]
     pd = get_plot_data_power(data_res, fit_res, model_res, power)
@@ -222,7 +222,7 @@ xlabel("Detuning (GHz)")
 ylabel("Light Shift (kHz)")
 NaCsPlot.maybe_save("$(prefix)_light_shift")
 
-figure()
+figure(figsize=[6.4, 4.8] * 1.11308)
 # const plot_freqs = get_plot_range(data_rabi.freqs)
 for i in 1:length(powers_plot)
     power = powers_plot[i]
@@ -246,7 +246,7 @@ NaCsPlot.maybe_save("$(prefix)_rabi")
 
 const freq = 560
 
-fig = figure(figsize=[3.6, 5.4])
+fig = figure(figsize=[3.6, 5.4] .* 1.0516)
 
 ax1 = fig.add_subplot(211)
 plot2 = get_plot_data_freq(data_res, fit_res, model_res, freq)

### 2020-11-12 paper.tex
Update on Overleaf.

@@
 \begin{abstract}
-  Fully controlled single molecules provide a promising platform
-  for a variety of quantum science applications.
-  As a step towards this goal, we report on coherent association
+  We report on coherent association
   of atoms into a single weakly bound NaCs molecule in an optical tweezer
@@
   The Raman scheme uses a deeply bound electronic excited intermediate state
-  to achieve a large transition dipole moment while reducing the photon scattering.
+  to achieve a large transition dipole moment while reducing photon scattering.
   Starting from two atoms in their relative motional ground state,
   we achieve an optical transfer efficiency of $69~\mathrm{\%}$.
-  The molecule has a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$
+  The molecules have a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$
   and are created with higher than $60~\mathrm{\%}$ probability in the motional ground state.
   This technique does not rely on narrow excited-state lines or Feshbach resonances
-  and will allow a wider range of molecular species to be assembled atom-by-atom.
+  and may allow a wide range of molecular species to be assembled atom-by-atom.
 \end{abstract}
@@
 by magnetoassociation using a magnetic Feshbach scattering resonance.
-The only exceptions are Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states
+Exceptions are Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states
 are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012},
 and $^{87}$Rb$^{85}$Rb,
-where there are molecular states bound by $1\sim2~\mathrm{MHz}$~\cite{He331}.
+where there are molecular states bound by $1-2~\mathrm{MHz}$~\cite{He331}.
 With these requirements, molecules involving non-magnetic atoms
@@
 Here, we demonstrate coherent association of an atom pair to a weakly bound molecule
-using a two-photon optical Raman transfer via an electronic excited state,
+by two-photon optical Raman transfer via an electronic excited state,
 schematically shown in Fig.~\ref{f-theory}a.
@@
 is used as the intermediate state in the Raman scheme,
-and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation.
-To reduce the photon scattering and sensitivity to laser intensity noise further,
-we choose the initial and final state to balance the two Rabi frequencies as much as possible.
-This system-independent approach can be used for creating new molecules atom-by-atom
+and is chosen to minimize theoretical photon scattering during Raman Rabi oscillations
+To reduce photon scattering and sensitivity to laser intensity noise further,
+we choose the initial and final states to balance the two Rabi frequencies as much as possible.
+This system-independent approach creates new molecules atom-by-atom
 with full quantum state control.
@@
     However, the scattering rate ($\Gamma_{s}$) is also much lower,
-    which results in a larger Raman Rabi frequency to scattering rate ratio.
+    which results in a larger ratio of Raman Rabi frequency to scattering rate.
     (c) Enhancement of the short-range wavefunction.
@@
     comparable to the axial trapping frequency.
-    This causes a significant change in the relative wavefunction especially at short
-    intranuclear distance ($R$).
+    This causes a significant change in the relative wavefunction, especially at short
+    internuclear distance ($R$).
     Compared to other spin states with weaker interaction,
-    the wavefunction at short distance ($R<100\text{\AA}$, left of the dotted line)
+    the wavefunction at short distance ($R<100\ \text{\AA}$, left of the dotted line)
     is significantly enhanced.
@@
 Among the stable spin combinations, $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\Na} \downarrow_{\Cs}} $ combination has a large and negative scattering length of $ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
-For the target molecular state, the spin state is ideally similar to the initial spin state in order to minimize sensitivity to the magnetic field.
+
+{\color{red} To identify a suitable target molecular state, we carry out coupled-channel calculations of the near-threshold bound states, as described in the Supplemental Material. 
+Choosing a bound state with similar spin character to the atomic state  minimizes the sensitivity of the transition frequency to magnetic field.
+A suitable state with this character is predicted about 763 MHz below the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ threshold.
+The coupled-channel calculations show that this target molecular state has lower overlap with the intermediate state, compared to bound states of other spin compositions.
+%For the target molecular state, the spin state is ideally similar to the initial spin state in order to minimize sensitivity to the magnetic field.
 % We find a target spin state predominantly in the initial spin state
@@
 % In addition to the increased atomic coupling, $ \Omega_a $,
-Coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $,
-with the intermediate state when compared to bound states of the other spin compositions.
-This further increases the ratio $\Omega_a/\Omega_m$ when using the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.
+%Coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $, with the intermediate state when compared to bound states of the other spin compositions.
+This further increases the ratio $\Omega_a/\Omega_m$ when starting from atoms in the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.}
 % $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
@@
     (a) Raman detuning scans at different times showing the resonance frequency.
-    (b) Raman pulse time scan on resonance.
-    A decaying Rabi oscillation can be observed proving the coherence of
+    (b) Raman pulse-time scan on resonance.
+    A decaying Rabi oscillation can be observed, proving the coherence of
     the Raman transfer process.
@@
     Inset: Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
-    The tweezer and Raman beam is focused through an objective to a waist of $0.9~\mathrm{\mu m}$
+    The tweezer and Raman beam is focused through an objective to a waist of $0.9~\mathrm{\mu m}$,
     which defines the location of the atoms and molecule.
-    We use a bias B field of $B_0=8.8~\mathrm{G}$ along the tweezer polarization
+    We use a bias magnetic field $B_0=8.8~\mathrm{G}$ along the tweezer polarization
     to define the quantization axis.
-    As a result, the atoms experiences predominantly $\pi$ polarization from the tweezer.
+    As a result, the atoms experience predominantly $\pi$ polarization from the tweezer.
     \label{f-raman}}
@@
   \caption{
-    (a) Direct measurement of molecule lifetime in $3.75~\mathrm{mW}$ of trap depth.
+    (a) Direct measurement of molecule lifetime in a trap of depth $3.75~\mathrm{mW}$.
     Molecule survival is detected by dissociating back to atoms using a second Raman transition.
@@
     (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
-    in $3.75~\mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
+    in a trap of depth $3.75~\mathrm{mW}$ caused by off-resonance photoassociation.
     This is used to improve the fitting of the Raman transfer data.
-    Inset: Atomic scattering rate scales as $P_{tweezer}^{2.58}$ on a log-log scale,
+    Inset: Atomic scattering rate scales as $P_\textrm{tweezer}^{2.58}$ on a log-log scale;
     this is consistent with a two-photon scattering process.
@@
 We choose the tweezer frequency to be far detuned (by $145 ~\mathrm{GHz}$)
-from the $v' = 0$ line. Guided by coupled-channel calculations,
+from the $v' = 0$ line. Guided by the coupled-channel calculations,
 we locate the Raman resonance for the atoms-to-molecule transition at
@@
     The fit also includes a small term that is proportional to $P^2$
-    which is caused by the effective magnetic field generated by the tweezer which is
-    perpendicular to the real magnetic field.
+    which is caused by the effective magnetic field generated by the tweezer, which is perpendicular to the real magnetic field.
     (b) Raman Rabi frequency ($\Omega_R$) scales as $P^{1.29}$
@@
     (c) Tweezer power dependency of light shift (up) and Raman Rabi frequency (down)
-    on a log-log plot showing the power law scaling.
+    on a log-log plot showing the power-law scaling.
     \label{f-det}}

### 2020-11-12 sm.tex
Update on Overleaf.

@@
 \usepackage{braket}
+\usepackage{xcolor}
+\newcommand\jmh[1]{{\color{magenta} #1}}
 
@@
 \author{Jonathan~D.~Hood}
-\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indianna, 47906, USA}
+\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indiana, 47906, USA}
 \author{Lewis~R.~B.~Picard}
@@
 
+\section{Computational methods for bound states and scattering}
+
+For scattering and near-threshold bound states, we solve the Schr\"odinger equation by
+coupled-channel methods \cite{HUTSON1994}, using a basis set in which the electron spins
+$s_{\rm Na}$ and $s_{\rm Cs}$ and the nuclear spins $i_{\rm Na}$ and $i_{\rm Cs}$ are separately
+coupled,
+\begin{equation}
+| (s_{\rm Na} s_{\rm Cs} S)
+(i_{\rm Na} i_{\rm Cs} I) F M_F\rangle.
+\label{eqbassif}
+\end{equation}
+Here $S$ and $I$ are the total electron and nuclear spins of the molecule or atomic pair. Their
+resultant $F$ is the total spin, with projection $M_F$ onto the axis of the magnetic field. In
+principle $F$ can be further coupled to the rotational angular momentum $L$, but in the present
+work only functions with $L=0$ are included. In the absence of a magnetic field, $F$ and $M_F$ are
+both good quantum numbers, but in a magnetic field only $M_F$ is conserved. The calculations in
+this paper use basis sets with all possible values of $S$, $I$ and $F$ (for the required value of
+$M_F$) that can be constructed with $s_{\rm Na} = s_{\rm Cs} = 1/2$, $i_{\rm Na} = 3/2$ and $i_{\rm
+Cs} = 7/2$.
+
+Scattering calculations are carried out using the MOLSCAT package \cite{molscat:2019,
+mbf-github:2020} and bound-state calculations using the related BOUND package
+\cite{bound+field:2019, mbf-github:2020}. The calculations use singlet and triplet interaction
+potentials for Na+Cs obtained by adjusting the potentials of Docenko \emph{et al.}\
+\cite{Docenko:2006} at short range, using the same procedure as for KCs \cite{Groebner2017},
+to reproduce the experimental binding energy of the least-bound triplet state \cite{Hood2019}
+and the position of the s-wave Feshbach resonance near 864~G \cite{Zhang2020}. The atomic
+nuclear hyperfine coupling and Zeeman effects are fully included, using the Hamiltonian described
+in \cite{Hutson2008}.
+
+The bound-state calculations were initially used to predict the binding energies of states that lie
+within about 1~GHz of each atomic threshold of interest. At zero magnetic field, the states fall
+into groups from each hyperfine state of the atomic pair, labeled by $(f_{\rm Na},f_{\rm Cs})$. For
+example, for the $(f_{\rm Na},f_{\rm Cs}) = (2,3)$ states that are of principal interest here, each
+group comprises 5 zero-field levels with $F=1,2,3,4$ and 5; one such group is spread out over a
+range of energies between 290 MHz and 770 MHz below the $(f_{\rm Na},f_{\rm Cs}) = (2,3)$
+threshold. In a magnetic field, each zero-field level splits into $2F+1$ Zeeman sublevels labeled
+by $M_F$. For each sublevel we can calculate the dependence of the energy on magnetic field, in
+order to choose a target state for which the Raman transition frequency depends only weakly on
+field.
+
+The state that we ultimately chose as the target state for Raman transfer is the least-bound
+$(F,M_F)=(5,5)$ sublevel with $(f_{\rm Na},f_{\rm Cs}) = (2,3)$, which was predicted at a binding
+energy 763 MHz below the $(f_{\rm Na},f_{\rm Cs}) = (2,3)$ threshold. As described in the text, it
+was subsequently located experimentally at a binding energy of 770.57150(9) MHz.
+
+Multichannel bound-state wavefunctions, with components labeled by $S$, $I$ and $F$, are calculated
+using the method of Thornley and Hutson \cite{Thornley1994}. For molecular bound states, they are
+obtained on a grid of internuclear distances from 2.4~\AA\ to 50~\AA. For states of confined atomic
+pairs, a harmonic confining potential is added to the molecular potentials and the grid is extended
+to 3000~\AA.
+
 \section{Calculating Matrix Elements with Coupled Channel Ground State}
-The free atom state (with spherically-symmetric harmonic confinement) and target weakly-bound molecular state are calculated using coupled-channel methods.
-Due to the cylindrical symmetry of the system, the projection of the total spin $m_F \equiv m_{F_{\text{Na}}} + m_{F_{\text{Cs}}}$ is conserved in the transition.
-Since our initial spin state is $ \ket{F_{\text{Na}} = 2, m_{F_{\text{Na}}} = 2, F_{\text{Cs}} = 3, m_{F_{\text{Cs}}} = 3}$, we can couple to all channels with total $ m_F = 5 $.
-These channels, written in the basis $ \ket{S, m_S, I, m_I}$, include $ \ket{0,0,5,5}, \ket{1,0,5,5}, \ket{1,1,5,4}, \ket{1,1,4,4} $, where $S = 0,1$ is the total electron spin and $ I = 2,3,4,5 $ is the total nuclear spin.
-The coupled-channel wavefunction contains a component in each of these channels .
-In this work, we assume the excited state wavefunction is a single-channel triplet wavefunction.
-Thus, only the triplet component of the coupled-channel ground state contributes to $\Omega_a$ and $ \Omega_m $.
+To calculate Rabi frequencies for transitions to intermediate vibrational levels of the c$^3\Sigma\ (\Omega=1)$ electronic state, we
+obtain their wavefunctions from a single-channel calculation using the potential curve of \cite{Grochola2011}. We
+then calculate overlap integrals between this function and the triplet ($S=1$) components of the
+coupled-channel wavefunctions for either the target molecular state or the confined atomic state.
+These calculations assume that the intermediate state has pure triplet character and neglect its
+nuclear spin character, which is unknown.
 
-The full calculation using the methods in section \ref{sm:sect_2} is shown in figure \ref{f-sm}.
-The strong contribution from the atomic threshold arises from the large overlap between the weakly-bound molecular state and the atomic continuum.
-This leads to a $1/\delta_{\text{thresh}}^2$ dependence of the scattering rate and favors deeply bound states as the intermediate state.
-The Raman Rabi frequency is larger than the scattering rate only for these deeply bound states.
+The full calculation of the Raman Rabi frequency and scattering rate using the methods in section \ref{sm:sect_2} is shown in figure \ref{f-sm}.
+The strong contribution from the atomic threshold arises from the large overlap between the target molecular state and the atomic continuum.
+This leads to a $1/\delta_{\text{thresh}}^2$ dependence of the scattering rate and favors using deeply bound states as the intermediate state for the Raman transfer.
+The Raman Rabi frequency is larger than the scattering rate only for the deeply bound states.
 

### 2020-11-12 paper.tex
F->f as per Jeremy's comment

@@
 For our system of Na and Cs atoms,
-we choose a spin-state combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=3,m_F=3}_{\Cs}$ that has a large and negative scattering length of
+we choose a spin-state combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}\equiv \ket{f=2,m_f=2}_{\Na}\ket{f=3,m_f=3}_{\Cs}$ that has a large and negative scattering length of
 $a(\uparrow_{\Na} \downarrow_{\Cs}) \approx -700a_0$~\cite{Hood2019}.
 All other stable spin combinations give smaller scattering lengths ($<~50~a_0$).
-% We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\Cs}} = \ket{F=4,m_F=4}_{\Cs}, \ket{\downarrow_{\Cs}} = \ket{F=3,m_F=3}_{\Cs}, \ket{\uparrow_{\Na}} = \ket{F=2,m_F=2}_{\Na}, $ and $ \ket{\downarrow_{\Na}} = \ket{F=1,m_F=1}_{\Na}$.
+% We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\Cs}} = \ket{f=4,m_f=4}_{\Cs}, \ket{\downarrow_{\Cs}} = \ket{f=3,m_f=3}_{\Cs}, \ket{\uparrow_{\Na}} = \ket{f=2,m_f=2}_{\Na}, $ and $ \ket{\downarrow_{\Na}} = \ket{f=1,m_f=1}_{\Na}$.
 Among the stable spin combinations, $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\Na} \downarrow_{\Cs}} $ combination has a large and negative scattering length of $ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
@@
   The coupled-channel calculations show that this target molecular state has lower overlap with the intermediate state, compared to bound states of other spin compositions.
-%For the target molecular state, the spin state is ideally similar to the initial spin state in order to minimize sensitivity to the magnetic field.
+  % For the target molecular state, the spin state is ideally similar to the initial spin state in order to minimize sensitivity to the magnetic field.
   % We find a target spin state predominantly in the initial spin state
@@
   % In addition to the increased atomic coupling, $ \Omega_a $,
-%Coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $, with the intermediate state when compared to bound states of the other spin compositions.
+  % Coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $, with the intermediate state when compared to bound states of the other spin compositions.
   This further increases the ratio $\Omega_a/\Omega_m$ when starting from atoms in the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.}
@@
 in the 3-dimensional motional ground state of their optical tweezers.
-After cooling, the Na and Cs atoms are in the spin state~$\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=4,m_F=4}_{\Cs}$,
+After cooling, the Na and Cs atoms are in the spin state~$\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{f=2,m_f=2}_{\Na}\ket{f=4,m_f=4}_{\Cs}$,
 which has a small scattering length.

### 2020-11-12 sm.tex

@@
 \section{Calculating Matrix Elements with Coupled Channel Ground State}
-To calculate Rabi frequencies for transitions to intermediate vibrational levels of the c$^3\Sigma\ (\Omega=1)$ electronic state, we
+To calculate Rabi frequencies for transitions to intermediate vibrational levels of the c$^3\Sigma^+ (\Omega=1)$ electronic state, we
 obtain their wavefunctions from a single-channel calculation using the potential curve of \cite{Grochola2011}. We

### 2020-11-14 paper.tex
Update on Overleaf.

@@
   of atoms into a single weakly bound NaCs molecule in an optical tweezer
-  through an optical Raman transition without the use of a Feshbach resonance.
+  through an optical Raman transition.
   The Raman scheme uses a deeply bound electronic excited intermediate state
@@
   Starting from two atoms in their relative motional ground state,
-  we achieve an optical transfer efficiency of $69~\mathrm{\%}$.
+  we achieve an optical transfer efficiency of $69\mathrm{\%}$.
   The molecules have a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$
-  and are created with higher than $60~\mathrm{\%}$ probability in the motional ground state.
+  and are created with higher than $60\mathrm{\%}$ probability in the motional ground state.
   This technique does not rely on narrow excited-state lines or Feshbach resonances
@@
 that have been developed for atoms.
-Associating atoms into deeply-bound molecules is challenging
+Associating atoms into deeply bound molecules is challenging
 because of the small wavefunction overlap between the free-atom and molecular states
 and the release of a large amount of binding energy.
-A two-step approach has been demonstrated to associate atom pairs
+A widely used method of overcoming these challenges is to associate atom pairs
 into weakly bound molecules first,
@@
   Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
-So far, most molecular association has been achieved for bialkali molecules
-by magnetoassociation using a magnetic Feshbach scattering resonance.
-Exceptions are Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states
+So far, molecular association has generally been achieved by magnetoassociation using a magnetic Feshbach scattering resonance.
+Exceptions include Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states
 are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012},
@@
 is used as the intermediate state in the Raman scheme,
-and is chosen to minimize theoretical photon scattering during Raman Rabi oscillations
+and is chosen to minimize photon scattering during Raman Rabi oscillations.
 To reduce photon scattering and sensitivity to laser intensity noise further,
@@
     The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
-    by $\Delta$ in order to suppress the scattering during the transfer.
+    by $\Delta$ in order to suppress scattering during the transfer.
     (b) Comparison between using a weakly bound and a deeply bound excited state
@@
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
-The transfer Raman Rabi Rate, $\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
+The transfer Raman Rabi Rate is given by $\Omega_a\Omega_m / 2\Delta$.
+%, is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
 % $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
@@
 
-Early experiments used weakly bound excited states as the intermediate state
+Earlier experiments used weakly bound excited states as the intermediate state
 in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
@@
 between the target molecular state and the excited atomic continuum.
-This calculation shows that the ratio of the Raman Rabi rate to scattering rate
+This calculation shows that $\Omega_R/\Gamma_s$
 can be made larger for more deeply bound states compared to weakly bound states
-at a cost of a smaller Raman Rabi frequency, as shown in Fig.~\ref{f-theory}b;
+at a cost of a smaller $\Omega_R$, as shown in Fig.~\ref{f-theory}b;
 see Supplementary Material for details.
@@
 choosing an initial and a final state for a large ratio $\Omega_a/\Omega_m$
-maximizes the Raman Rabi frequency at a given detuning.
-Furthermore, a larger ratio also relaxes the intensity stability requirement,
-because this is also the ratio between the Raman Rabi coupling
+maximizes $\Omega_R$ at a given detuning.
+Furthermore, a larger ratio also relaxes the intensity stability requirement for the Raman lasers,
+because this is also the ratio between $\Omega_R$
 and the AC Stark shift of the molecular state, $\Omega_m^2 / 2\Delta$
@@
 the short-range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $ or $P^{3/8}$,
-where $ \omega_{\text{trap}} $ is the trap frequency and $P$ is the power in the trap \cite{Mies2000}.
+where $ \omega_{\text{trap}} $ is the trap frequency and $P$ is the optical power in the tweezer trap \cite{Mies2000}.
 However, additional power may not always be available, and will also lead to additional undesired scattering.
@@
 
-{\color{red} To identify a suitable target molecular state, we carry out coupled-channel calculations of the near-threshold bound states, as described in the Supplemental Material.
+To identify a suitable target molecular state, we carry out coupled-channel calculations of the near-threshold bound states, as described in the Supplemental Material.
   Choosing a bound state with similar spin character to the atomic state  minimizes the sensitivity of the transition frequency to magnetic field.
   A suitable state with this character is predicted about 763 MHz below the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ threshold.
-  The coupled-channel calculations show that this target molecular state has lower overlap with the intermediate state, compared to bound states of other spin compositions.
+  The coupled-channel calculations show that this target molecular state has lower overlap with the intermediate state, compared to bound states from other hyperfine combinations.
   % For the target molecular state, the spin state is ideally similar to the initial spin state in order to minimize sensitivity to the magnetic field.
@@
   % Coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $, with the intermediate state when compared to bound states of the other spin compositions.
-  This further increases the ratio $\Omega_a/\Omega_m$ when starting from atoms in the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.}
+  This further increases the ratio $\Omega_a/\Omega_m$ to about 0.05 when starting from atoms in the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.
 % $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
-This combination
-results in a ratio $\Omega_a/\Omega_m$ of about 0.05 instead of a ratio of about 0.003
-with the other combinations, thus relaxing the intensity stability requirement to the few percent level.
+Compared to 0.003
+with the other combinations, this relaxes the intensity stability requirement to the few percent level.
 % Thus, instead of a required intensity stability of $0.3 ~\mathrm{\%} $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5~\mathrm{\%} $.
@@
 For the experiment reported here,
-$31~\mathrm{\%}$ of our initial two-atom population is transferred.
+$31\mathrm{\%}$ of our initial two-atom population is transferred.
 % of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
@@
 we smoothly ramp down the power of one frequency in the tweezer
-while simultaneously ramping up the power of a different frequency
+while simultaneously ramping up the power of the other frequency
 so that the total tweezer power remains unchanged.
@@
 we locate the Raman resonance for the atoms-to-molecule transition at
-$770.57150(9) ~\mathrm{MHz}$ with $3.75~\mathrm{mW}$ tweezer power,
+$770.57150(9) ~\mathrm{MHz}$ with about $3.75~\mathrm{mW}$ tweezer power,
 as shown in Fig.~\ref{f-raman}a.
@@
 so successful transfer of the atoms to the molecular state is detected as loss.
-We observe a fourier-limited linewidth, which is evidence of a coherent transfer.
+We observe a Fourier-limited linewidth, which is evidence of a coherent transfer.
 In order to verify the coherence of the transfer directly,
@@
 The result in Fig.~\ref{f-lifetime}a shows a molecular lifetime of $0.199(9)~\mathrm{ms}$
-consistent with the decay of Rabi oscillation.
+consistent with the decay of the Rabi oscillation.
 We obtain the Raman Rabi frequency by fitting our measurements to a model
@@
 
-In order to verify whether any one of these known sources are the origin of the discrepancy,
+In order to verify whether any one of these known sources are the origin of the reduced transfer efficiency,
 we measured the properties of the Raman resonance as a function of the tweezer power and single-photon detuning.
-These dependencies allow us to experimentally determine the matrix elements,
+These dependencies allow us to experimentally determine the Rabi frequencies,
 $ \Omega_a $, $\Omega_m $ and how much of the scattering, Stark shift,
 or Raman Rabi frequency comes from the $ v' = 0$ intermediate state.
+% KENNETH WILL RESUME EDITING FROM HERE BASED ON LEWIS AND WILL COMMENTS
 
-First we look at the change in resonance frequency.
-As a function of the tweezer power,
-we observe the expected linear dependency on the resonance frequency
-caused by the differential light shift between the atomic and molecular state.
+First we look at the change in resonance frequency to determine $\Omega_m$.
+We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
 When we vary the tweezer frequency around the $v'=0$ intermediate state,
@@
 From this measurement, we can extract a $\Omega_m$ of
-$2\pi\times72.32(4) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or
-$2\pi\times140.06(8) ~\mathrm{MHz}$ for the $3.75~\mathrm{mW}$ tweezer power used above.
+$2\pi\times72.32(4) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
+%or
+%$2\pi\times140.06(8) ~\mathrm{MHz}$ for the $3.75~\mathrm{mW}$ tweezer power used above.
 This number is close to the value of
@@
 we now need to extract $ \Omega_a $.
-We do this by measuring the dependencies of the Raman Rabi frequency,
-which depends on both $\Omega_m$ and $\Omega_a$.
+We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
+%which depends on both $\Omega_m$ and $\Omega_a$.
 The Raman Rabi frequency shows a non-linear dependency on the tweezer power
@@
 As discussed before, for weakly interacting particles,
-$\Omega_a$ scales as $P^{0.375}$.
-However, due to the strong interaction between the two atoms, this approximation breaks down.
+$\Omega_a$ scales as $P^{3/8}$.
+However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
 Instead, coupled-channel calculations show that the scaling
@@
 a $v'=0$ component that scales as $1/\Delta$.
-The $v'=0$ component of the Raman Rabi frequency is
+The $v'=0$ component of the Raman Rabi frequency at our detuning is
 $2\pi\times1.02(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
@@
 when crossing a resonance, the same background will increase the Raman Rabi frequency
-for positive detunings from the $v' = 0$ transition,
-which increases the Raman Rabi frequency.
+for positive detunings from the $v' = 0$ transition. 
 Unfortunately, we observe additional nearby excited states
 belonging to a different electronically excited state at higher frequencies
-which prevent the blue side of the transition to be usable for the Raman transition.
+which prevent the blue side of the transition from being be usable for the Raman transition.
 
@@
 comes from either a higher than expected background scattering rate
-or a different intrinsic or technical source that we have not accounted for.
+or a different intrinsic or technical source for which we have not accounted for.
 We observe a decrease in the coherence time by a factor of 2 without the ASE filter,
@@
 Based on the ratio of the Raman Rabi frequency to light shift, shown in Fig.~\ref{f-det}c,
-the requirement on the tweezer power stability is $0.8~\mathrm{\%}$ at $3.75~\mathrm{mW}$,
-which we stabilize to $0.1~\mathrm{\%}$ so this should not be a major source of decoherence.
+the requirement on the tweezer power stability is $0.8\mathrm{\%}$ at $3.75~\mathrm{mW}$. We stabilize the power to $0.1\mathrm{\%}$, so this should not be a major source of decoherence.
 Similarly, we measured a Zeeman shift of $42.2(2)~\mathrm{kHz/G}$
@@
 At $0.75~\mathrm{mW}$ tweezer power, we observe a molecule lifetime as long as $1~\mathrm{ms}$.
-However, since the technical noise that can lead to decoherence
+Since the technical noise that can lead to decoherence
 is not fully characterized in our experiment,
@@
 without turning on the second frequency, as shown in Fig.~\ref{f-lifetime}b inset.
-The scattering rate scales as $P_{\mathrm{tweezer}}^{2.58}$,
+The scattering rate scales as $P^{2.58}$,
 which is inconsistent with a single-photon scattering process.
-We have not been able to observe a dependency on the detuning in order to verify
-if the scattering process is related to the $v'=0$ state,
+We have not been able to observe a dependency on the detuning in order to verify whether the scattering process is related to the $v'=0$ state,
 but the power scaling strongly suggests the existence of an unknown two-photon process.

### 2020-11-14 sm.tex
Update on Overleaf.

@@
 potentials for Na+Cs obtained by adjusting the potentials of Docenko \emph{et al.}\
-\cite{Docenko:2006} at short range, using the same procedure as for KCs \cite{Groebner2017},
+\cite{Docenko2006} at short range, using the same procedure as for KCs \cite{Groebner2017},
 to reproduce the experimental binding energy of the least-bound triplet state \cite{Hood2019}

### 2020-11-14 paper.tex
Update on Overleaf.

@@
   and are created with higher than $60\mathrm{\%}$ probability in the motional ground state.
-  This technique does not rely on narrow excited-state lines or Feshbach resonances
+  This technique does not rely on Feshbach resonances or narrow excited-state lines 
   and may allow a wide range of molecular species to be assembled atom-by-atom.
@@
 
-\begin{figure}[t!]
-  \includegraphics[width=0.48\textwidth]{fig3.pdf}
-  \caption{
-    (a) Direct measurement of molecule lifetime in a trap of depth $3.75~\mathrm{mW}$.
-    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
-    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
-    measured from the Raman transition data.
-    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
-    in a trap of depth $3.75~\mathrm{mW}$ caused by off-resonance photoassociation.
-    This is used to improve the fitting of the Raman transfer data.
-    Inset: Atomic scattering rate scales as $P_\textrm{tweezer}^{2.58}$ on a log-log scale;
-    this is consistent with a two-photon scattering process.
-    We have not measured a clear dependency of the loss rate on the tweezer detuning.
-    \label{f-lifetime}}
-\end{figure}
-
 %% Experiment condition/resonance
@@
 both the Raman Rabi frequency and the scattering rate and thus affect their ratio.
+
+\begin{figure}[t!]
+  \includegraphics[width=0.48\textwidth]{fig3.pdf}
+  \caption{
+    (a) Direct measurement of molecule lifetime in a trap of depth $3.75~\mathrm{mW}$.
+    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
+    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
+    measured from the Raman transition data.
+    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
+    in a trap of depth $3.75~\mathrm{mW}$ caused by off-resonance photoassociation.
+    This is used to improve the fitting of the Raman transfer data.
+    Inset: Atomic scattering rate scales as $P_\textrm{tweezer}^{2.58}$ on a log-log scale;
+    this is consistent with a two-photon scattering process.
+    We have not measured a clear dependency of the loss rate on the tweezer detuning.
+    \label{f-lifetime}}
+\end{figure}
 

### 2020-11-16 paper.tex
Fix citation position
Whitespace, indent, regenerate PDF
Update on Overleaf.

@@
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
-The transfer Raman Rabi Rate is given by $\Omega_a\Omega_m / 2\Delta$.
-%, is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
+The transfer Raman Rabi Rate is given by $\Omega_a\Omega_m / 2\Delta$~\cite{Wineland2003}.
+% , is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
 % $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
-~\cite{Wineland2003}.
 Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
@@
 and Raman Rabi rates over all possible intermediate states.
-With these considerations, using a weakly bound excited state as the intermediate state
-suffers from strong scattering due to the nearby excited atomic continuum,
-resulting in large incoherence and loss to other molecular states.
-This scattering is proportional to $1/\delta_{\mathrm{thresh}}^2$,
+Since there is large overlap between the target molecular state and weakly bound excited states, using states that are closer to the dissociation threshold as the intermediate state results in a large scattering rate.
+%in large incoherence and loss to other molecular states.
+This scattering is approximately proportional to $1/\delta_{\mathrm{thresh}}^2$,
 where $\delta_{\mathrm{thresh}}$ is the detuning from the dissociation threshold,
-and thus can be made smaller by using deeply bound vibrational states as the intermediate level.
+and thus can be made smaller by using deeply bound vibrational states as the intermediate state.
 
@@
 and the continuum~\cite{Liu2017}.
-The excited atomic continuum is particularly important for the target molecular state.
-The sum of the squares of the wavefunction overlap
-between the target weakly bound molecular state
-and all the excited molecular bound states is only about $0.02$,
-suggesting that there are significant matrix elements
-between the target molecular state and the excited atomic continuum.
 This calculation shows that $\Omega_R/\Gamma_s$
@@
 or Raman Rabi frequency comes from the $ v' = 0$ intermediate state.
-% KENNETH WILL RESUME EDITING FROM HERE BASED ON LEWIS AND WILL COMMENTS
 
@@
 $2\pi\times72.32(4) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
-%or
-%$2\pi\times140.06(8) ~\mathrm{MHz}$ for the $3.75~\mathrm{mW}$ tweezer power used above.
+% or
+% $2\pi\times140.06(8) ~\mathrm{MHz}$ for the $3.75~\mathrm{mW}$ tweezer power used above.
 This number is close to the value of
@@
 We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
-%which depends on both $\Omega_m$ and $\Omega_a$.
+% which depends on both $\Omega_m$ and $\Omega_a$.
 The Raman Rabi frequency shows a non-linear dependency on the tweezer power

### 2020-11-16 sm.tex
Whitespace, indent, regenerate PDF
Update on Overleaf.

@@
-\documentclass[aps,secnumarabic,amsmath,amssymb,superscriptaddress]{revtex4}
+\documentclass[aps,secnumarabic,amsmath,amssymb,10pt,superscriptaddress]{revtex4}
 \usepackage{amsmath}
@@
 We have replaced the full continuum with an effective state at the atomic threshold with strength proportional to the amount of wavefunction overlap between the target molecular state and all atomic continuum states.
-This term is especially important for our target-molecule state, because the square of the wavefunction overlap between the target-molecule state and all excited vibrational states is only 0.02
-\begin{equation}
-  \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m} = 0.02
-\end{equation}
-leading to strong scattering from the atomic continuum.
-We note that this model leads to a component in the scattering rate that is proportional to $ 1/\delta_{\text{thresh}}^2$ and is smaller as one detunes farther from the threshold.
+This model leads to a component in the scattering rate that is proportional to $ 1/\delta_{\text{thresh}}^2$ and is smaller as one detunes farther from the threshold.
+We note that the first term can also scale nearly as $1/\delta_{\text{thresh}}^2 $, if, as in our case, the largest terms in the summation are from states near the threshold.
 
@@
 this paper use basis sets with all possible values of $S$, $I$ and $F$ (for the required value of
-$M_F$) that can be constructed with $s_{\rm Na} = s_{\rm Cs} = 1/2$, $i_{\rm Na} = 3/2$ and $i_{\rm
-Cs} = 7/2$.
+$M_F$) that can be constructed with $s_{\rm Na} = s_{\rm Cs} = 1/2$,
+$i_{\rm Na} = 3/2$ and $i_{\rm Cs} = 7/2$.
 
@@
 The full calculation of the Raman Rabi frequency and scattering rate using the methods in section \ref{sm:sect_2} is shown in figure \ref{f-sm}.
-The strong contribution from the atomic threshold arises from the large overlap between the target molecular state and the atomic continuum.
+The strong contribution from the atomic threshold arises from the large overlap near-threshold bound states.
 This leads to a $1/\delta_{\text{thresh}}^2$ dependence of the scattering rate and favors using deeply bound states as the intermediate state for the Raman transfer.

### 2020-11-19 plot_raman.jl
Update figures

@@ -24,66 +24,58 @@ const data = LibArchive.Reader(fname) do reader
 end
 const prefix = joinpath(@__DIR__, "imgs", "raman")
 
-fig = figure(figsize=[1.11, 1.11] * 4.8)
+fig = figure(figsize=[1.11, 1.4] * 4.8)
 
-ax0 = fig.add_subplot(111)    # The big subplot
-ax0.spines["top"].set_color("none")
-ax0.spines["bottom"].set_color("none")
-ax0.spines["left"].set_color("none")
-ax0.spines["right"].set_color("none")
-ax0.set_xticks([])
-ax0.set_yticks([])
-ax0.tick_params(labelcolor="w", top="off", bottom="off", left="off", right="off")
-ylabel("\$\\Omega_{R}\$ and \$\\Gamma_{s}\$ (\$2\\pi\\cdot \\mathrm{kHz})\$")
-ax0.get_yaxis().set_label_coords(-0.13, 0.5)
-ax0.tick_params(axis="x", length=0)
-ax0.tick_params(axis="y", length=0)
-tax0 = ax0.twinx()
-tax0.set_xticks([])
-tax0.set_yticks([])
-tax0.tick_params(labelcolor="w", top="off", bottom="off", left="off", right="off")
-tax0.tick_params(axis="x", length=0)
-tax0.tick_params(axis="y", length=0)
-tax0.get_yaxis().set_label_coords(1.118, 0.5)
-ylabel("\$\\Omega_{R}/\\Gamma_{s}\$", color="C2")
-
-ax1 = fig.add_subplot(211)
+ax1 = fig.add_subplot(311)
+plot(data[:, 1] .- 351271.53, abs.(data[:, 2] ./ 2π / 1000), "C1",
+     label="\$v'=63\$")
 plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ 2π / 1000), "C0",
-     label="\$\\Omega_{R}\$")
-plot(data[:, 1] .- 288625.081, abs.(data[:, 4] ./ 2π / 1000), "C1",
-     label="\$\\Gamma_{s}\$")
-text(-32, 2.5, "v'=0", fontsize="small")
-ylim([0, 30])
-grid()
-tax1 = ax1.twinx()
-tax1.plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ data[:, 4]), "C2",
[…]

### 2020-11-19 plot_scaling.jl

@@ -188,7 +188,7 @@ const data_res = gen_data(res_freqs)
 const fit_res = fit_freq_model_res(model_res, data_res, [770.202, 705, 0, 100])
 @show fit_res.uncs
 
-const model_rabi = gen_model_rabi(705)
+const model_rabi = gen_model_rabi(fit_res.param[2])
 const data_rabi = gen_data(rabi_freqs)
 const fit_rabi = fit_data(model_rabi, data_rabi.x, data_rabi.y, [0.1, 0.1], plotx=false)
 @show fit_rabi.uncs
@@ -201,9 +201,10 @@ figure(figsize=[6.4, 4.8] * 1.11308)
 for i in 1:length(powers_plot)
     power = powers_plot[i]
     pd = get_plot_data_power(data_res, fit_res, model_res, power)
-    errorbar(pd.x .- 703.6, (pd.y .- fit_res.param[1]) .* 1000,
+    errorbar(1000 ./ (pd.x .- fit_res.param[2]), (pd.y .- fit_res.param[1]) .* 1000,
              pd.unc .* 1000, fmt="C$(i - 1)o", label="$(power / 4) mW")
-    plot(pd.plotx .- 703.6, (pd.ploty .- fit_res.param[1]) .* 1000, "C$(i - 1)")
+    plot(1000 ./ (pd.plotx .- fit_res.param[2]), (pd.ploty .- fit_res.param[1]) .* 1000,
+         "C$(i - 1)")
 end
 # xticks([288500, 288530, 288560, 288590, 288620])
 # p: framan0, fpa0, offset, strength, bs...
@@ -213,12 +214,12 @@ end
 #                 "\$f_{PA0}=$(fit_res.uncs[2] + 288000)\$ GHz\n" *
 #                 "\$a=$(fit_res.uncs[3] * 1000)\$ kHz/mW\n" *
 #                 "\$b=$(fit_res.uncs[4])\$ MHz\$\\cdot\$GHz/mW"), fontsize="small")
-legend(loc="upper left", fontsize="small", handlelength=0.6, handletextpad=0.3)
+legend(loc="upper right", fontsize="small", handlelength=0.6, handletextpad=0.3)
 grid()
-xticks([-200, -160, -120, -80])
[…]

### 2020-11-19 plot_wavefunction.jl

@@ -34,15 +34,18 @@ const data42 = read_csv_compressed(fname42, ',', Float64)
 const prefix = joinpath(@__DIR__, "imgs", "wavefunction")
 
 figure()
-plot(data42[:, 1], data42[:, 2] .* 1e4, "C2", label="Na(2,2) Cs(4,4)")
-plot(data32[:, 1], data32[:, 2] .* 1e4, "C1", label="Na(2,2) Cs(3,3)")
-plot(data31[:, 1], data31[:, 2] .* 1e4, "C3--", label="Na(1,1) Cs(3,3)")
+plot(data42[:, 1], data42[:, 2] .* 2e6, "C2", label="Na(2,2) Cs(4,4)")
+plot(data32[:, 1], data32[:, 2] .* 2e6, "C1", label="Na(2,2) Cs(3,3)")
+plot(data31[:, 1], data31[:, 2] .* 2e6, "C3--", label="Na(1,1) Cs(3,3)")
 axvline(100, color="C0", ls="dashed", linewidth=3)
 grid()
-xlim([0, 3080])
-ylim([0, 7.3])
-ylabel("\$\\left|\\psi(R)\\right|^2\$", fontsize=20)
+xscale("log")
+yscale("log")
+xlim([2.7, 3000])
+ylim([0.0015, 1450])
+xticks([10, 100, 1000], ["10", "100", "1000"])
 xlabel("R (Angstroms)", fontsize=20)
+ylabel("\$\\left|\\psi(R)\\right|^2\$", fontsize=20)
 gca().tick_params(axis="both", which="major", labelsize=15)
 legend(fontsize=13.88)
 NaCsPlot.maybe_save("$(prefix)")

### 2020-11-19 imgs/raman_spectroscopy_raman_beampath.tex
Include ASE beam path

\documentclass{standalone}
\usepackage{tikz}
\usepackage[colorlinks=true]{hyperref}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes,
  arrows.meta
}
\tikzfading[name = lens fading,inner color = transparent!0,outer color = transparent!100]
\tikzfading[name = pbs fading,top color = transparent!0,bottom color = transparent!100]
\tikzset{
  mid arrow/.style={postaction={decorate,decoration={
        markings,
        mark=at position .5 with {\arrow[#1]{stealth}}
      }}},
  mid arrow2/.style={postaction={decorate,decoration={
        markings,
        mark=at position .5 with {\arrow[>=stealth]{><}}
      }}},
}

\newcommand\drawellipseshade[5][inner color=black,outer color=black]{
  % 1: shading option
  % 2: center (x, y)
  % 3: xsize
  % 4: ysize
  % 5: angle
  \begin{scope}
    \clip[rotate around={#5:#2}] #2 ellipse ({#3} and {#4});
    \begin{scope}[transform canvas={shift={#2}, rotate=#5}]
      \shade[shading=radial,path fading=lens fading, #1] (0, 0) ellipse ({#3} and {#4});
    \end{scope}
  \end{scope}
}
\newcommand\drawlens[3]{
  % 1: center (x, y)
  % 2: size
  % 3: angle
  \drawellipseshade[inner color=blue,outer color=blue!40!cyan]{#1}{#2}{{0.14 * #2}}{#3}
}
\newcommand\drawwaveplate[3]{
  % 1: center (x, y)
  % 2: size
  % 3: angle
  \drawellipseshade[inner color=blue!50!black,outer color=blue!80!black]{#1}{#2}{{0.07 * #2}}{#3}
}
\newcommand\drawaom[4]{
  % 1: center (x, y)
  % 2: xsize
  % 3: ysize
  % 4: angle
  \drawellipseshade[inner color=orange,outer color=orange]{#1}{#2}{#3}{#4}
  \begin{scope}[rotate around={#4:#1}]
    \fill[orange, even odd rule, opacity=0.8]
    ($#1 + ({#2}, 0)$) arc (0:360:{#2} and {#3})
    -- ($#1 + ({#2}, {#3})$) -- ($#1 + (-{#2}, {#3})$) -- ($#1 + (-{#2}, -{#3})$)
    -- ($#1 + ({#2}, -{#3})$) --cycle;
    \draw ($#1 + ({#2}, {#3})$) -- ($#1 + (-{#2}, {#3})$) -- ($#1 + (-{#2}, -{#3})$)
    -- ($#1 + ({#2}, -{#3})$) --cycle;
  \end{scope}
}
\newcommand\drawpbs[3]{
  % 1: center (x, y)
  % 2: size
  % 3: angle
  \begin{scope}
    \begin{scope}
      \clip[rotate around={#3:#1}] ($#1 - ({#2}, {#2})$) rectangle ($#1 + ({#2}, {#2})$);
      \begin{scope}[transform canvas={shift={#1}, rotate=#3}]
        \shade[bottom color=blue!60!cyan, top color=blue!50!cyan, path fading=pbs fading]
        (-{#2}, -{#2}) rectangle ({#2}, {#2});
        \draw[line width=1] (-{#2}, -{#2}) -- ({#2}, {#2});
      \end{scope}
    \end{scope}
    % Make sure the frame is not clipped
    \draw[rotate around={#3:#1}] ($#1 - ({#2}, {#2})$) rectangle ($#1 + ({#2}, {#2})$);
  \end{scope}
}

\ifpdf
% Ensure reproducible output
\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}
\hypersetup{
  pdfcreator={},
  pdfproducer={}
}
\fi

\begin{document}

\begin{tikzpicture}
  % Input
  \node[red,above] at (2, 0) {\large\textbf{From Laser}};
  \draw[red,line width=1.6,mid arrow] (2, 0) -- (0, 0);
  % Wavemeter
  \draw[red,line width=1.6] (0, 0) -- (0, -1);
  \draw[red,line width=1.6,mid arrow] (0, -1) -- (0, -2);
  \node[red,below] at (0, -2) {\large\textbf{To wavemeter}};
  % Between PBS and DP AOM
  \draw[red,line width=1.6,mid arrow2] (-2, 0) -- (0, 0);
  \begin{scope}
    % Clip off one arrow
    \clip (-1.23, 0) rectangle (-2, 1);
    \draw[blue,line width=1.6,mid arrow2] (-2, 0) -- (0, 0);
  \end{scope}
  \begin{scope}
    % Redraw the clipped line
    \clip (0, 0) rectangle (-2, 1);
    \draw[blue,line width=1.6] (-2, 0) -- (0, 0);
  \end{scope}
  % Output
  \draw[red,line width=1.6] (0, 0) -- (0, 1);
  \draw[red,line width=1.6,mid arrow] (0, 1) -- (0, 2);
  \begin{scope}
    \clip (0, 0) rectangle (-1, 3);
    \draw[blue,line width=1.6] (0, 0) -- (0, 1);
    \draw[blue,line width=1.6,mid arrow] (0, 1) -- (0, 2);
  \end{scope}
  \node[red] at (0, 2.3) {\large\textbf{To Experiment}};
  \begin{scope}
    \clip (-2, 2.3) rectangle (2, 3.5);
    \node[blue] at (0, 2.3) {\large\textbf{To Experiment}};
  \end{scope}
  \draw[red,line width=1.6,mid arrow2] (-2, 0) -- (-6, 0);
  \draw[blue,line width=1.6,mid arrow2] (-2, 0) -- (-6 - 0.3, 0 + 0.3);
  \draw[blue,line width=1.6,mid arrow2] (-6 - 0.3, 0 + 0.3) -- (-6 - 0.4, 2.5 + 0.05);
  \draw[red,line width=1.6,mid arrow2] (-6, 0) -- (-6, 5);
  \draw[red,line width=1.6,mid arrow2] (-7.5, 5) -- (-6, 5);
  \draw[red,line width=1.6] (-7.5, 5) -- (-9, 5);
  \draw[red,line width=1.6] (-9, 5) -- (-10, 5);
  \draw[red,line width=1.6,mid arrow] (-10, 5) -- (-11.5, 5);
  \draw[red,line width=1.6] (-11.5, 5) -- (-11.5, 3.3);
  \draw[red,line width=1.6,mid arrow] (-11.5, 3.3) -- (-11.5 - 0.2, 0 + 0.2);
  \draw[red,line width=1.6,mid arrow] (-11.5 - 0.2, 0 + 0.2) -- (-9, 0);
  \draw[red,line width=1.6,mid arrow] (-9, 0) -- (-9, 5);
  % Input PBS
  \drawpbs{(0, 0)}{0.7}{0}
  \node[blue!40!cyan,below right] at (0 + 0.7, 0 - 0.7) {\large PBS 1};
  % DP AOM
  \drawaom{(-2, 0)}{1}{0.5}{90}
  \node[rotate=-90] at (-2, 0) {\large DP AOM};
  % DP Lens
  \drawlens{(-4.5, 0)}{1}{90}
  \node[blue!80!cyan,below] at (-4.5, -1) {\large L1};
  \draw[line width=3] (-6 - 0.7, 0 + 0.7) -- (-6 + 0.7, 0 - 0.7);
  % DP QWP
  \drawwaveplate{(-6, 1.5)}{1}{0}
  \node[blue!80!black,right] at (-5.1, 1.5) {\large $\lambda/4$};
  \draw[line width=3] (-6 - 0.7, 2.5) -- (-6 - 0.1, 2.5 + 0.1);
  % Post DP QWP
  \drawwaveplate{(-6, 3.5)}{1}{0}
  \node[blue!80!black,right] at (-5.1, 3.5) {\large $\lambda/4$};
  \draw[line width=3] (-6 - 0.7, 5 + 0.7) -- (-6 + 0.7, 5 - 0.7);
  % Post DP Lens
  \drawlens{(-7.5, 5)}{1}{90}
  \node[blue!80!cyan,above] at (-7.5, 6) {\large L2};
  % SP PBS
  \drawpbs{(-9, 5)}{0.7}{0}
  \node[blue!40!cyan,above] at (-9, 5 + 0.7) {\large PBS 2};
  \draw[line width=3] (-11.5 - 0.7, 5 - 0.7) -- (-11.5 + 0.7, 5 + 0.7);
  % SP AOM
  \drawaom{(-11.5, 3.3)}{1}{0.5}{0}
  \node at (-11.5, 3.3) {\large SP AOM};
  \draw[line width=3] (-11.5 - 0.7, 0 + 0.7) -- (-11.5 + 0.7, 0 - 0.7);
  \draw[line width=3] (-9 - 0.7, 0 - 0.7) -- (-9 + 0.7, 0 + 0.7);
  % SP HWP
  \drawwaveplate{(-9, 1.7)}{1}{0}
  \node[blue!80!black,left] at (-9.9, 1.7) {\large $\lambda/2$};

  \draw[gray,opacity=0.8,line width=1,dashed] (-4, 6) |- (2.8, 2.8);

  \begin{scope}[shift={(-1.4, 4)}]
    \draw[red,line width=1.6,mid arrow] (3, 0) node[below] {\large\textbf{Input}} -- (0, 0);
    \draw[red,line width=1.6,mid arrow] (0, 0) -- ({3 * cos(40)}, {3 * sin(40)})
    node[left] {\large\textbf{Output}};
    \draw[gray,line width=6] ({-0.7 * tan(20)}, 0.7) --
    node[black,left] {\large ASE Filter} ({0.7 * tan(20)}, -0.7);
  \end{scope}
\end{tikzpicture}

\end{document}

### 2020-11-20 plot_raman.jl
Tweak plot spacing

@@ -24,7 +24,7 @@ const data = LibArchive.Reader(fname) do reader
 end
 const prefix = joinpath(@__DIR__, "imgs", "raman")
 
-fig = figure(figsize=[1.11, 1.4] * 4.8)
+fig = figure(figsize=[1.11, 1.5] * 4.8)
 
 ax1 = fig.add_subplot(311)
 plot(data[:, 1] .- 351271.53, abs.(data[:, 2] ./ 2π / 1000), "C1",
@@ -34,7 +34,7 @@ plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ 2π / 1000), "C0",
 legend(fontsize=13.88, loc="upper right")
 ylabel("\$\\Gamma_{s}~(2\\pi\\!\\cdot\\!\\mathrm{kHz})\$")
 xlim([-35, 35])
-ylim([0.5, 600])
+ylim([0.3, 600])
 yscale("log")
 yticks([1, 10, 100], ["1", "10", "100"])
 ax1.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
@@ -44,14 +44,14 @@ setp(ax1.get_xticklabels(), visible=false)
 ax1.tick_params(axis="x", length=0)
 
 ax2 = fig.add_subplot(312)
-subplots_adjust(hspace=0.0)
+subplots_adjust(hspace=0.018)
 plot(data[:, 1] .- 288625.081, abs.(data[:, 4] ./ 2π / 1000), "C0",
      label="\$v'=0\$")
 plot(data[:, 1] .- 351271.53, abs.(data[:, 4] ./ 2π / 1000), "C1",
      label="\$v'=63\$")
 ylabel("\$\\Omega_{R}~(2\\pi\\!\\cdot\\!\\mathrm{kHz})\$")
 xlim([-35, 35])
-ylim([0.012, 600])
+ylim([0.01, 600])
 yscale("log")
 yticks([0.1, 1, 10, 100], ["0.1", "1", "10", "100"])
 ax2.set_yticks([0.02:0.01:0.09; 0.2:0.1:0.9; 2:1:9;
@@ -63,7 +63,7 @@ setp(ax2.get_xticklabels(), visible=false)
 ax2.tick_params(axis="x", length=0)
 
 ax3 = fig.add_subplot(313)
-subplots_adjust(hspace=0.0)
+subplots_adjust(hspace=0.018)
[…]

### 2020-11-23 paper.tex
Update on Overleaf.

@@
 we choose the initial and final states to balance the two Rabi frequencies as much as possible.
-This system-independent approach creates new molecules atom-by-atom
+This system-independent approach creates molecules atom-by-atom
 with full quantum state control.
@@
 taking into account of all states of
-the $\mathrm{c^3\Sigma^+}(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
+8 excited molecular state potentials~\cite{Korek2007, Grochola2011, Zaharova2009, Grochola2010, Zabawa2012}
 and the continuum~\cite{Liu2017}.
@@
 As a result, we choose the $v'=0$ level of $\mathrm{c^3\Sigma^+}(\Omega = 1)$
-as an intermediate state to drive the Raman transition.
+as the closest intermediate state to drive the Raman transition.
 
@@
 A suitable state with this character is predicted about 763 MHz below the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ threshold.
-The coupled-channel calculations show that this target molecular state has lower overlap with the intermediate state, compared to bound states from other hyperfine combinations.
+%The coupled-channel calculations show that this target molecular state has lower overlap with the intermediate state, compared to bound states from other hyperfine combinations.
 % For the target molecular state, the spin state is ideally similar to the initial spin state in order to minimize sensitivity to the magnetic field.
@@
 % Coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $, with the intermediate state when compared to bound states of the other spin compositions.
-This further increases the ratio $\Omega_a/\Omega_m$ to about 0.05 when starting from atoms in the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.
+The ratio $\Omega_a/\Omega_m$ increases to about 0.013 when starting from atoms in the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.
 % $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
 Compared to 0.003
-with the other combinations, this relaxes the intensity stability requirement to the few percent level.
+with the other combinations, this relaxes the intensity stability requirement to the percent level.
 % Thus, instead of a required intensity stability of $0.3 ~\mathrm{\%} $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5~\mathrm{\%} $.
@@
 and minimize the transfer time.
-Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50~\mathrm{GHz}$
+Furthermore, we use two Bragg gratings, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
 to filter the laser spectrum generated by a fiber amplifier
@@
 we locate the Raman resonance for the atoms-to-molecule transition at
-$770.57150(9) ~\mathrm{MHz}$ with about $3.75~\mathrm{mW}$ tweezer power,
+$770.57150(9) ~\mathrm{MHz}$ with about $3.75~\mathrm{mW}$ tweezer power focused down to a waist of $ 0.9~\mathrm{\mu m}$,
 as shown in Fig.~\ref{f-raman}a.
@@
 The molecular state is dark to the imaging step,
-so successful transfer of the atoms to the molecular state is detected as loss.
+so successful transfer of the atoms to the molecular state is detected as loss of atoms.
 We observe a Fourier-limited linewidth, which is evidence of a coherent transfer.
@@
 a finite lifetime for the molecular state, as shown in Fig.~\ref{f-raman}a and b.
-We account for the effect of atomic state loss by measuring the one-body and
+We account for the small effect of atomic state loss by measuring the one-body and
 two-body lifetime of the atoms directly without turning on the second frequency,
 as shown in Fig.~\ref{f-lifetime}b.
-The fit gives a Raman Rabi frequency of $2\pi\times3.28(4)~\mathrm{kHz}$.
+The fit including all these effects gives a Raman Rabi frequency of $2\pi\times3.28(4)~\mathrm{kHz}$.
 
@@
 because the ratio of the molecular scattering rate to the Rabi frequency
-is 10 times larger than predicted.
-Based on the discussion above, if this discrepancy arises from the $v'=0$ excited state,
+is 10 times larger than predicted. If this discrepancy arises from the $v'=0$ excited state,
 it can be due either to a high ratio $\Omega_m / \Omega_a$ or to a large $\Gamma_e$.
@@
 
-In order to verify whether any one of these known sources are the origin of the reduced transfer efficiency,
+In order to verify whether any one of these sources are the origin of the reduced transfer efficiency,
 we measured the properties of the Raman resonance as a function of the tweezer power and single-photon detuning.
@@
 This number is close to the value of
-$2\pi\times40.7 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
+$2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
 
@@
 from the $v'=0$ state to be higher than expected.
-Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $20~\mathrm{MHz}$ using photoassociation (PA) spectroscopy.
-This suggests that the excited-state linewidth should not cause
-a stronger than expected scattering from $v'=0$ state either.
+Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $20~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.
 
@@
     & Experiment & Theory \\ \hline
-    $ \Omega_m $ & $2\pi \times 140.06(8) ~\mathrm{MHz} $ & $2\pi \times 78.9 ~\mathrm{MHz}$ \\
-    $\Omega_a$ & $2\pi \times 12.1(3) ~\mathrm{MHz}$ & $2\pi \times 3.32 ~\mathrm{MHz}$ \\
-    $\Omega_m/\Omega_a$ & $11.6(3)$ & $ 23.8$
+    $ \Omega_m $ & $2\pi \times 140.06(8) ~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
+    $\Omega_a$ & $2\pi \times 12.1(3) ~\mathrm{MHz}$ & $2\pi \times 7.37 ~\mathrm{MHz}$ \\
+    $\Omega_m/\Omega_a$ & $11.6(3)$ & $ 77.7$
   \end{tabular}
@@
 
-With the $ v' = 0 $ state ruled out as the source of discrepancy between experiment and theory,
+With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
 we now consider the background effects from other states with larger single-photon detuning.
@@
 These results suggest that the decoherence or loss we observe during the Raman transition
-comes from either a higher than expected background scattering rate
+comes from either a higher background scattering rate of an unknown source
 or a different intrinsic or technical source for which we have not accounted for.
-We observe a decrease in the coherence time by a factor of 2 without the ASE filter,
-suggesting the spectral purity of the laser is a significant source of scattering.
+We observe a decrease in the coherence time by a factor of 2 without the ASE filters. This
+suggests the spectral purity of the laser is a significant source of scattering, but does not explain the full amount. 
 Other sources that can contribute to the decoherence include
@@
 by optical Raman transfer.
-A theoretical investigation including all excited states of $\mathrm{c^3\Sigma^+}(\Omega = 1)$,
+A theoretical investigation including 8 excited state potentials,
 the excited atomic continuum, and coupled-channel ground state wavefunctions indicated
@@
 Using these theoretical insights, we located the weakly bound state
-and coherently associated the atoms into a weakly bound molecule.
+and coherently associated the atoms into a weakly bound molecule. Currently, 
 Our transfer efficiency is limited by an unknown scattering source
@@
 $\Omega_a/\Omega_m$, for example by driving to more deeply bound states.
-There may also be a better choice of single-photon detuning to increase the Raman Rabi frequency,
-since our location results in about $30~\mathrm{\%}$ cancellation of the Raman Rabi frequency
-due to an offset of unknown origin.
 
@@
 or a narrow excited state. The formation of a weakly bound molecule is a key step
-in forming rovibrational ground state molecules.
-Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},
-defect-free arrays of highly controlled molecules comprise a promising
-and flexible platform for quantum simulation and quantum computing applications.
+in forming rovibrational ground state molecules. By scaling up to many optical tweezers, large arrays with arbitrary geometry of highly controlled molecules can be achieved.
+%Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},
+%defect-free arrays of highly controlled molecules comprise a promising
+%and flexible platform for quantum simulation and quantum computing applications.
 
@@
 \begin{acknowledgments}
-  We would like to thank Bo Gao,  Paul Julienne, and Rosario Gonzalez-Ferez for discussion.
+  We would like to thank Rosario Gonzalez-Ferez, Bo Gao, and Paul Julienne \textcolor{red}{acknowledge getting TDM} for discussion.
 This work is supported by the NSF~(PHY-1806595), the AFOSR~(FA9550-19-1-0089), ARO DURIP (W911NF1810194) and the Arnold and Mabel Beckman foundation.

### 2020-11-24 paper.tex
Format and regenerate PDF
Fix B field

@@
   we achieve an optical transfer efficiency of $69\mathrm{\%}$.
-  The molecules have a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$
+  The molecules have a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.83(2)~\mathrm{G}$
   and are created with higher than $60\mathrm{\%}$ probability in the motional ground state.
@@
 Since there is large overlap between the target molecular state and weakly bound excited states, using states that are closer to the dissociation threshold as the intermediate state results in a large scattering rate.
-%in large incoherence and loss to other molecular states.
+% in large incoherence and loss to other molecular states.
 This scattering is approximately proportional to $1/\delta_{\mathrm{thresh}}^2$,
@@
 A suitable state with this character is predicted about 763 MHz below the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ threshold.
-%The coupled-channel calculations show that this target molecular state has lower overlap with the intermediate state, compared to bound states from other hyperfine combinations.
+% The coupled-channel calculations show that this target molecular state has lower overlap with the intermediate state, compared to bound states from other hyperfine combinations.
 % For the target molecular state, the spin state is ideally similar to the initial spin state in order to minimize sensitivity to the magnetic field.
@@
     which defines the location of the atoms and molecule.
-    We use a bias magnetic field $B_0=8.8~\mathrm{G}$ along the tweezer polarization
+    We use a bias magnetic field $B_0=8.83(2)~\mathrm{G}$ along the tweezer polarization
     to define the quantization axis.
@@
 in forming rovibrational ground state molecules. By scaling up to many optical tweezers, large arrays with arbitrary geometry of highly controlled molecules can be achieved.
-%Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},
-%defect-free arrays of highly controlled molecules comprise a promising
-%and flexible platform for quantum simulation and quantum computing applications.
+% Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},
+% defect-free arrays of highly controlled molecules comprise a promising
+% and flexible platform for quantum simulation and quantum computing applications.
 

### 2020-11-24 plot_raman_full.jl
Update full Raman plot

@@ -15,7 +15,8 @@ using LibArchive
 
 using DelimitedFiles
 
-const fname = joinpath(@__DIR__, "../damop-2020/20MHz_linewidth_c3SigmaOnly_3322_80kHzConfinement.csv.zst")
+# const fname = joinpath(@__DIR__, "../damop-2020/20MHz_linewidth_c3SigmaOnly_3322_80kHzConfinement.csv.zst")
+const fname = joinpath(@__DIR__, "data/50MHz_linewidth_8TotalExcitedStates_3322_80kHzConfinement_3.75mWPowerAtAtom.csv.zst")
 const data = LibArchive.Reader(fname) do reader
     LibArchive.support_format_raw(reader)
     LibArchive.support_filter_all(reader)
@@ -24,20 +25,32 @@ const data = LibArchive.Reader(fname) do reader
 end
 const prefix = joinpath(@__DIR__, "imgs", "raman_theory_full")
 
-figure(figsize=[12.8, 4.8])
+figure(figsize=[13.8, 4.8])
 l1 = plot(data[:, 1] ./ 1000, abs.(data[:, 2] ./ 2π / 1000), "C0",
           label="\$\\Omega_{R}\$")
 l2 = plot(data[:, 1] ./ 1000, abs.(data[:, 4] ./ 2π / 1000), "C1",
           label="\$\\Gamma_{s}\$")
+# plot(data[:, 1] ./ 1000, abs.(data[:, 2] ./ data[:, 4]), "C2")
+# es = [2.8863, 2.9026, 2.9184, 2.9339, 2.9492, 2.9643, 2.9792, 2.9939, 3.0084, 3.0227,
+#       3.0369, 3.0510, 3.0649, 3.0787, 3.0925, 3.1062, 3.1198, 3.1334, 3.1469, 3.1603,
+#       3.1736, 3.1868, 3.1999, 3.2129, 3.2258, 3.2385, 3.2511, 3.2635, 3.2757, 3.2876,
+#       3.2993, 3.3106, 3.3215, 3.3322, 3.3425, 3.3525, 3.3621, 3.3714, 3.3803, 3.3889,
+#       3.3972, 3.4052, 3.4129, 3.4204, 3.4276, 3.4345, 3.4412, 3.4475, 3.4537, 3.4597,
[…]

### 2020-11-24 paper.tex
Update excited state linewidth

@@
 from the $v'=0$ state to be higher than expected.
-Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $20~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.
+Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.
 

### 2020-11-24 paper.tex
WIP: comments from Kang-Kuen

@@
 \begin{document}
-\title{Coherent optical association of atoms into a single molecule}
-% \title{Coherent optical creation of a single molecule}
+% \title{Coherent optical association of atoms into a single molecule}
+\title{Coherent optical creation of a single molecule}
 \author{Yichao~Yu}
@@
 we choose the initial and final states to balance the two Rabi frequencies as much as possible.
-This system-independent approach creates molecules atom-by-atom
-with full quantum state control.
+This system-independent approach creates molecules atom-by-atom with full quantum state control.
 
@@
 based on the initial loading condition.
+After imaging, we turn on a $8.83(2)~\mathrm{G}$ magnetic field to define the quantization axis
+for the state preparation and molecule formation steps.
 Raman sideband cooling is then applied to prepare both atoms simultaneously
@@
 
-We choose the tweezer frequency to be far detuned (by $145 ~\mathrm{GHz}$)
-from the $v' = 0$ line. Guided by the coupled-channel calculations,
+We choose the tweezer frequency to be $288560~\mathrm{GHz}$
+which is far detuned (by $\approx\!145~\mathrm{GHz}$) from the $v' = 0$ line.
+Guided by the coupled-channel calculations,
 we locate the Raman resonance for the atoms-to-molecule transition at
-$770.57150(9) ~\mathrm{MHz}$ with about $3.75~\mathrm{mW}$ tweezer power focused down to a waist of $ 0.9~\mathrm{\mu m}$,
-as shown in Fig.~\ref{f-raman}a.
+$770.57150(9) ~\mathrm{MHz}$ with about $3.75~\mathrm{mW}$ tweezer power
+focused down to a waist of $ 0.9~\mathrm{\mu m}$, as shown in Fig.~\ref{f-raman}a.
 % (We can maybe add information about the prediction here?)
@@
 as shown in Fig.~\ref{f-lifetime}b.
-The fit including all these effects gives a Raman Rabi frequency of $2\pi\times3.28(4)~\mathrm{kHz}$.
+The fit including all these effects gives a Raman Rabi frequency
+of $2\pi\times3.28(4)~\mathrm{kHz}$.
 
 The efficiency of the transfer is lower than expected
-because the ratio of the molecular scattering rate to the Rabi frequency
+because we found the ratio of the molecular scattering rate to the Rabi frequency
 is 10 times larger than predicted. If this discrepancy arises from the $v'=0$ excited state,

### 2020-11-24 plot_raman.jl
new v0 vs vhi comparisons

@@ -15,7 +15,8 @@ using LibArchive
 
 using DelimitedFiles
 
-const fname = joinpath(@__DIR__, "../damop-2020/20MHz_linewidth_c3SigmaOnly_3322_80kHzConfinement.csv.zst")
+# const fname = joinpath(@__DIR__, "../damop-2020/20MHz_linewidth_c3SigmaOnly_3322_80kHzConfinement.csv.zst")
+const fname = joinpath(@__DIR__, "data/50MHz_linewidth_8TotalExcitedStates_3322_80kHzConfinement_3.75mWPowerAtAtom.csv.zst")
 const data = LibArchive.Reader(fname) do reader
     LibArchive.support_format_raw(reader)
     LibArchive.support_filter_all(reader)
@@ -27,16 +28,15 @@ const prefix = joinpath(@__DIR__, "imgs", "raman")
 fig = figure(figsize=[1.11, 1.5] * 4.8)
 
 ax1 = fig.add_subplot(311)
-plot(data[:, 1] .- 351271.53, abs.(data[:, 2] ./ 2π / 1000), "C1",
-     label="\$v'=63\$")
+plot(data[:, 1] .- 339724.57, abs.(data[:, 2] ./ 2π / 1000), "C1",
+     label="\$v'=40\$")
 plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ 2π / 1000), "C0",
      label="\$v'=0\$")
-legend(fontsize=13.88, loc="upper right")
-ylabel("\$\\Gamma_{s}~(2\\pi\\!\\cdot\\!\\mathrm{kHz})\$")
-xlim([-35, 35])
-ylim([0.3, 600])
+ylabel("\$\\Omega_{R}~(2\\pi\\!\\cdot\\!\\mathrm{kHz})\$")
+xlim([-300, 300])
+ylim([6, 20000])
 yscale("log")
-yticks([1, 10, 100], ["1", "10", "100"])
+# yticks([10, 100, 1000, 10000], ["10", "100", "1000", "10000"])
 ax1.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 grid()
 setp(ax1.get_xticklabels(), visible=false)
@@ -47,15 +47,14 @@ ax2 = fig.add_subplot(312)
 subplots_adjust(hspace=0.018)
[…]

### 2020-11-24 plot_scaling.jl
Use one ASE filter data for the scaling plot

@@ -59,7 +59,7 @@ const res_freqs = [668.35 21 772.1367 0.0082
                    625 3 770.347812 0.000022
                    ]
 
-const rabi_freqs = [560 15 3.282 0.042
+const rabi_freqs = [560 15 3.971 0.089
                     560 6 1.182 0.033
                     560 3 0.488 0.015
 

### 2020-11-24 imgs/AOM.tex
Make images compatible with old PDF viewers...

--- 2020-11-19 imgs/raman_spectroscopy_raman_beampath.tex
@@
 \begin{tikzpicture}
-  % Input
-  \node[red,above] at (2, 0) {\large\textbf{From Laser}};
-  \draw[red,line width=1.6,mid arrow] (2, 0) -- (0, 0);
-  % Wavemeter
-  \draw[red,line width=1.6] (0, 0) -- (0, -1);
-  \draw[red,line width=1.6,mid arrow] (0, -1) -- (0, -2);
-  \node[red,below] at (0, -2) {\large\textbf{To wavemeter}};
-  % Between PBS and DP AOM
-  \draw[red,line width=1.6,mid arrow2] (-2, 0) -- (0, 0);
-  \begin{scope}
-    % Clip off one arrow
-    \clip (-1.23, 0) rectangle (-2, 1);
-    \draw[blue,line width=1.6,mid arrow2] (-2, 0) -- (0, 0);
-  \end{scope}
-  \begin{scope}
-    % Redraw the clipped line
-    \clip (0, 0) rectangle (-2, 1);
-    \draw[blue,line width=1.6] (-2, 0) -- (0, 0);
-  \end{scope}
-  % Output
-  \draw[red,line width=1.6] (0, 0) -- (0, 1);
-  \draw[red,line width=1.6,mid arrow] (0, 1) -- (0, 2);
-  \begin{scope}
-    \clip (0, 0) rectangle (-1, 3);
-    \draw[blue,line width=1.6] (0, 0) -- (0, 1);
-    \draw[blue,line width=1.6,mid arrow] (0, 1) -- (0, 2);
-  \end{scope}
-  \node[red] at (0, 2.3) {\large\textbf{To Experiment}};
-  \begin{scope}
-    \clip (-2, 2.3) rectangle (2, 3.5);
-    \node[blue] at (0, 2.3) {\large\textbf{To Experiment}};
-  \end{scope}
-  \draw[red,line width=1.6,mid arrow2] (-2, 0) -- (-6, 0);
-  \draw[blue,line width=1.6,mid arrow2] (-2, 0) -- (-6 - 0.3, 0 + 0.3);
-  \draw[blue,line width=1.6,mid arrow2] (-6 - 0.3, 0 + 0.3) -- (-6 - 0.4, 2.5 + 0.05);
-  \draw[red,line width=1.6,mid arrow2] (-6, 0) -- (-6, 5);
-  \draw[red,line width=1.6,mid arrow2] (-7.5, 5) -- (-6, 5);
-  \draw[red,line width=1.6] (-7.5, 5) -- (-9, 5);
-  \draw[red,line width=1.6] (-9, 5) -- (-10, 5);
-  \draw[red,line width=1.6,mid arrow] (-10, 5) -- (-11.5, 5);
-  \draw[red,line width=1.6] (-11.5, 5) -- (-11.5, 3.3);
-  \draw[red,line width=1.6,mid arrow] (-11.5, 3.3) -- (-11.5 - 0.2, 0 + 0.2);
-  \draw[red,line width=1.6,mid arrow] (-11.5 - 0.2, 0 + 0.2) -- (-9, 0);
-  \draw[red,line width=1.6,mid arrow] (-9, 0) -- (-9, 5);
-  % Input PBS
-  \drawpbs{(0, 0)}{0.7}{0}
-  \node[blue!40!cyan,below right] at (0 + 0.7, 0 - 0.7) {\large PBS 1};
-  % DP AOM
-  \drawaom{(-2, 0)}{1}{0.5}{90}
-  \node[rotate=-90] at (-2, 0) {\large DP AOM};
-  % DP Lens
-  \drawlens{(-4.5, 0)}{1}{90}
-  \node[blue!80!cyan,below] at (-4.5, -1) {\large L1};
-  \draw[line width=3] (-6 - 0.7, 0 + 0.7) -- (-6 + 0.7, 0 - 0.7);
-  % DP QWP
-  \drawwaveplate{(-6, 1.5)}{1}{0}
-  \node[blue!80!black,right] at (-5.1, 1.5) {\large $\lambda/4$};
-  \draw[line width=3] (-6 - 0.7, 2.5) -- (-6 - 0.1, 2.5 + 0.1);
-  % Post DP QWP
-  \drawwaveplate{(-6, 3.5)}{1}{0}
-  \node[blue!80!black,right] at (-5.1, 3.5) {\large $\lambda/4$};
-  \draw[line width=3] (-6 - 0.7, 5 + 0.7) -- (-6 + 0.7, 5 - 0.7);
-  % Post DP Lens
-  \drawlens{(-7.5, 5)}{1}{90}
-  \node[blue!80!cyan,above] at (-7.5, 6) {\large L2};
-  % SP PBS
-  \drawpbs{(-9, 5)}{0.7}{0}
-  \node[blue!40!cyan,above] at (-9, 5 + 0.7) {\large PBS 2};
-  \draw[line width=3] (-11.5 - 0.7, 5 - 0.7) -- (-11.5 + 0.7, 5 + 0.7);
-  % SP AOM
-  \drawaom{(-11.5, 3.3)}{1}{0.5}{0}
-  \node at (-11.5, 3.3) {\large SP AOM};
-  \draw[line width=3] (-11.5 - 0.7, 0 + 0.7) -- (-11.5 + 0.7, 0 - 0.7);
-  \draw[line width=3] (-9 - 0.7, 0 - 0.7) -- (-9 + 0.7, 0 + 0.7);
-  % SP HWP
-  \drawwaveplate{(-9, 1.7)}{1}{0}
-  \node[blue!80!black,left] at (-9.9, 1.7) {\large $\lambda/2$};
-
-  \draw[gray,opacity=0.8,line width=1,dashed] (-4, 6) |- (2.8, 2.8);
-
-  \begin{scope}[shift={(-1.4, 4)}]
-    \draw[red,line width=1.6,mid arrow] (3, 0) node[below] {\large\textbf{Input}} -- (0, 0);
-    \draw[red,line width=1.6,mid arrow] (0, 0) -- ({3 * cos(40)}, {3 * sin(40)})
-    node[left] {\large\textbf{Output}};
-    \draw[gray,line width=6] ({-0.7 * tan(20)}, 0.7) --
-    node[black,left] {\large ASE Filter} ({0.7 * tan(20)}, -0.7);
-  \end{scope}
+  \drawaom{(0, 0)}{1}{0.5}{0}
 \end{tikzpicture}

### 2020-11-24 imgs/PBS.tex
Make images compatible with old PDF viewers...

--- 2020-11-19 imgs/raman_spectroscopy_raman_beampath.tex
@@
 \begin{tikzpicture}
-  % Input
-  \node[red,above] at (2, 0) {\large\textbf{From Laser}};
-  \draw[red,line width=1.6,mid arrow] (2, 0) -- (0, 0);
-  % Wavemeter
-  \draw[red,line width=1.6] (0, 0) -- (0, -1);
-  \draw[red,line width=1.6,mid arrow] (0, -1) -- (0, -2);
-  \node[red,below] at (0, -2) {\large\textbf{To wavemeter}};
-  % Between PBS and DP AOM
-  \draw[red,line width=1.6,mid arrow2] (-2, 0) -- (0, 0);
-  \begin{scope}
-    % Clip off one arrow
-    \clip (-1.23, 0) rectangle (-2, 1);
-    \draw[blue,line width=1.6,mid arrow2] (-2, 0) -- (0, 0);
-  \end{scope}
-  \begin{scope}
-    % Redraw the clipped line
-    \clip (0, 0) rectangle (-2, 1);
-    \draw[blue,line width=1.6] (-2, 0) -- (0, 0);
-  \end{scope}
-  % Output
-  \draw[red,line width=1.6] (0, 0) -- (0, 1);
-  \draw[red,line width=1.6,mid arrow] (0, 1) -- (0, 2);
-  \begin{scope}
-    \clip (0, 0) rectangle (-1, 3);
-    \draw[blue,line width=1.6] (0, 0) -- (0, 1);
-    \draw[blue,line width=1.6,mid arrow] (0, 1) -- (0, 2);
-  \end{scope}
-  \node[red] at (0, 2.3) {\large\textbf{To Experiment}};
-  \begin{scope}
-    \clip (-2, 2.3) rectangle (2, 3.5);
-    \node[blue] at (0, 2.3) {\large\textbf{To Experiment}};
-  \end{scope}
-  \draw[red,line width=1.6,mid arrow2] (-2, 0) -- (-6, 0);
-  \draw[blue,line width=1.6,mid arrow2] (-2, 0) -- (-6 - 0.3, 0 + 0.3);
-  \draw[blue,line width=1.6,mid arrow2] (-6 - 0.3, 0 + 0.3) -- (-6 - 0.4, 2.5 + 0.05);
-  \draw[red,line width=1.6,mid arrow2] (-6, 0) -- (-6, 5);
-  \draw[red,line width=1.6,mid arrow2] (-7.5, 5) -- (-6, 5);
-  \draw[red,line width=1.6] (-7.5, 5) -- (-9, 5);
-  \draw[red,line width=1.6] (-9, 5) -- (-10, 5);
-  \draw[red,line width=1.6,mid arrow] (-10, 5) -- (-11.5, 5);
-  \draw[red,line width=1.6] (-11.5, 5) -- (-11.5, 3.3);
-  \draw[red,line width=1.6,mid arrow] (-11.5, 3.3) -- (-11.5 - 0.2, 0 + 0.2);
-  \draw[red,line width=1.6,mid arrow] (-11.5 - 0.2, 0 + 0.2) -- (-9, 0);
-  \draw[red,line width=1.6,mid arrow] (-9, 0) -- (-9, 5);
-  % Input PBS
   \drawpbs{(0, 0)}{0.7}{0}
-  \node[blue!40!cyan,below right] at (0 + 0.7, 0 - 0.7) {\large PBS 1};
-  % DP AOM
-  \drawaom{(-2, 0)}{1}{0.5}{90}
-  \node[rotate=-90] at (-2, 0) {\large DP AOM};
-  % DP Lens
-  \drawlens{(-4.5, 0)}{1}{90}
-  \node[blue!80!cyan,below] at (-4.5, -1) {\large L1};
-  \draw[line width=3] (-6 - 0.7, 0 + 0.7) -- (-6 + 0.7, 0 - 0.7);
-  % DP QWP
-  \drawwaveplate{(-6, 1.5)}{1}{0}
-  \node[blue!80!black,right] at (-5.1, 1.5) {\large $\lambda/4$};
-  \draw[line width=3] (-6 - 0.7, 2.5) -- (-6 - 0.1, 2.5 + 0.1);
-  % Post DP QWP
-  \drawwaveplate{(-6, 3.5)}{1}{0}
-  \node[blue!80!black,right] at (-5.1, 3.5) {\large $\lambda/4$};
-  \draw[line width=3] (-6 - 0.7, 5 + 0.7) -- (-6 + 0.7, 5 - 0.7);
-  % Post DP Lens
-  \drawlens{(-7.5, 5)}{1}{90}
-  \node[blue!80!cyan,above] at (-7.5, 6) {\large L2};
-  % SP PBS
-  \drawpbs{(-9, 5)}{0.7}{0}
-  \node[blue!40!cyan,above] at (-9, 5 + 0.7) {\large PBS 2};
-  \draw[line width=3] (-11.5 - 0.7, 5 - 0.7) -- (-11.5 + 0.7, 5 + 0.7);
-  % SP AOM
-  \drawaom{(-11.5, 3.3)}{1}{0.5}{0}
-  \node at (-11.5, 3.3) {\large SP AOM};
-  \draw[line width=3] (-11.5 - 0.7, 0 + 0.7) -- (-11.5 + 0.7, 0 - 0.7);
-  \draw[line width=3] (-9 - 0.7, 0 - 0.7) -- (-9 + 0.7, 0 + 0.7);
-  % SP HWP
-  \drawwaveplate{(-9, 1.7)}{1}{0}
-  \node[blue!80!black,left] at (-9.9, 1.7) {\large $\lambda/2$};
-
-  \draw[gray,opacity=0.8,line width=1,dashed] (-4, 6) |- (2.8, 2.8);
-
-  \begin{scope}[shift={(-1.4, 4)}]
-    \draw[red,line width=1.6,mid arrow] (3, 0) node[below] {\large\textbf{Input}} -- (0, 0);
-    \draw[red,line width=1.6,mid arrow] (0, 0) -- ({3 * cos(40)}, {3 * sin(40)})
-    node[left] {\large\textbf{Output}};
-    \draw[gray,line width=6] ({-0.7 * tan(20)}, 0.7) --
-    node[black,left] {\large ASE Filter} ({0.7 * tan(20)}, -0.7);
-  \end{scope}
 \end{tikzpicture}

### 2020-11-24 imgs/raman_spectroscopy_raman_beampath.tex
Mark AOM frequency shifts
Make images compatible with old PDF viewers...

@@
 }
+% \newcommand\drawlens[3]{
+%   % 1: center (x, y)
+%   % 2: size
+%   % 3: angle
+%   \drawellipseshade[inner color=blue,outer color=blue!40!cyan]{#1}{#2}{{0.14 * #2}}{#3}
+% }
+% \newcommand\drawwaveplate[3]{
+%   % 1: center (x, y)
+%   % 2: size
+%   % 3: angle
+%   \drawellipseshade[inner color=blue!50!black,outer color=blue!80!black]{#1}{#2}{{0.07 * #2}}{#3}
+% }
+% \newcommand\drawaom[4]{
+%   % 1: center (x, y)
+%   % 2: xsize
+%   % 3: ysize
+%   % 4: angle
+%   \drawellipseshade[inner color=orange,outer color=orange]{#1}{#2}{#3}{#4}
+%   \begin{scope}[rotate around={#4:#1}]
+%     \fill[orange, even odd rule, opacity=0.8]
+%     ($#1 + ({#2}, 0)$) arc (0:360:{#2} and {#3})
+%     -- ($#1 + ({#2}, {#3})$) -- ($#1 + (-{#2}, {#3})$) -- ($#1 + (-{#2}, -{#3})$)
+%     -- ($#1 + ({#2}, -{#3})$) --cycle;
+%     \draw ($#1 + ({#2}, {#3})$) -- ($#1 + (-{#2}, {#3})$) -- ($#1 + (-{#2}, -{#3})$)
+%     -- ($#1 + ({#2}, -{#3})$) --cycle;
+%   \end{scope}
+% }
+% \newcommand\drawpbs[3]{
+%   % 1: center (x, y)
+%   % 2: size
+%   % 3: angle
+%   \begin{scope}
+%     \begin{scope}
+%       \clip[rotate around={#3:#1}] ($#1 - ({#2}, {#2})$) rectangle ($#1 + ({#2}, {#2})$);
+%       \begin{scope}[transform canvas={shift={#1}, rotate=#3}]
+%         \shade[bottom color=blue!60!cyan, top color=blue!50!cyan, path fading=pbs fading]
+%         (-{#2}, -{#2}) rectangle ({#2}, {#2});
+%         \draw[line width=1] (-{#2}, -{#2}) -- ({#2}, {#2});
+%       \end{scope}
+%     \end{scope}
+%     % Make sure the frame is not clipped
+%     \draw[rotate around={#3:#1}] ($#1 - ({#2}, {#2})$) rectangle ($#1 + ({#2}, {#2})$);
+%   \end{scope}
+% }
 \newcommand\drawlens[3]{
@@
   % 3: angle
-  \drawellipseshade[inner color=blue,outer color=blue!40!cyan]{#1}{#2}{{0.14 * #2}}{#3}
+  \begin{scope}[shift={#1}]
+    \node[rotate={#3}] at (0, 0) {\scalebox{#2}{\includegraphics[width=2cm]{lens.png}}};
+  \end{scope}
 }
@@
   % 3: angle
-  \drawellipseshade[inner color=blue!50!black,outer color=blue!80!black]{#1}{#2}{{0.07 * #2}}{#3}
+  \begin{scope}[shift={#1}]
+    \node[rotate={#3}] at (0, 0) {\scalebox{#2}{\includegraphics[width=2cm]{wp.png}}};
+  \end{scope}
 }
@@
   % 4: angle
-  \drawellipseshade[inner color=orange,outer color=orange]{#1}{#2}{#3}{#4}
-  \begin{scope}[rotate around={#4:#1}]
-    \fill[orange, even odd rule, opacity=0.8]
-    ($#1 + ({#2}, 0)$) arc (0:360:{#2} and {#3})
-    -- ($#1 + ({#2}, {#3})$) -- ($#1 + (-{#2}, {#3})$) -- ($#1 + (-{#2}, -{#3})$)
-    -- ($#1 + ({#2}, -{#3})$) --cycle;
-    \draw ($#1 + ({#2}, {#3})$) -- ($#1 + (-{#2}, {#3})$) -- ($#1 + (-{#2}, -{#3})$)
-    -- ($#1 + ({#2}, -{#3})$) --cycle;
+  \begin{scope}[shift={#1}]
+    \node[rotate={#4}] at (0, 0)
+    {\scalebox{#2}[#3]{\includegraphics[width=2cm,height=2cm]{AOM.png}}};
   \end{scope}
@@
   % 3: angle
-  \begin{scope}
-    \begin{scope}
-      \clip[rotate around={#3:#1}] ($#1 - ({#2}, {#2})$) rectangle ($#1 + ({#2}, {#2})$);
-      \begin{scope}[transform canvas={shift={#1}, rotate=#3}]
-        \shade[bottom color=blue!60!cyan, top color=blue!50!cyan, path fading=pbs fading]
-        (-{#2}, -{#2}) rectangle ({#2}, {#2});
-        \draw[line width=1] (-{#2}, -{#2}) -- ({#2}, {#2});
-      \end{scope}
-    \end{scope}
-    % Make sure the frame is not clipped
-    \draw[rotate around={#3:#1}] ($#1 - ({#2}, {#2})$) rectangle ($#1 + ({#2}, {#2})$);
+  \begin{scope}[shift={#1}]
+    \node[rotate={#3}] at (0, 0)
+    {\scalebox{#2}{\includegraphics[width=1.4285714285714286cm]{PBS.png}}};
   \end{scope}
@@
   \draw[red,line width=1.6,mid arrow2] (-2, 0) -- (-6, 0);
-  \draw[blue,line width=1.6,mid arrow2] (-2, 0) -- (-6 - 0.3, 0 + 0.3);
+  \draw[blue,line width=1.6,mid arrow2] (-2, 0) --
+  node[above,pos=0.34,rotate=-5] {\small $\approx\!+345~\mathrm{MHz}$} (-6 - 0.3, 0 + 0.3);
   \draw[blue,line width=1.6,mid arrow2] (-6 - 0.3, 0 + 0.3) -- (-6 - 0.4, 2.5 + 0.05);
@@
   \draw[red,line width=1.6] (-11.5, 5) -- (-11.5, 3.3);
-  \draw[red,line width=1.6,mid arrow] (-11.5, 3.3) -- (-11.5 - 0.2, 0 + 0.2);
+  \draw[red,line width=1.6,mid arrow] (-11.5, 3.3) --
+  node[above,rotate=86,pos=0.45] {\small $-80~\mathrm{MHz}$} (-11.5 - 0.2, 0 + 0.2);
   \draw[red,line width=1.6,mid arrow] (-11.5 - 0.2, 0 + 0.2) -- (-9, 0);
@@
   % DP Lens
+  % \node[rotate=90] at (-4.5, 0) {\includegraphics[width={2 cm}]{lens.pdf}};
   \drawlens{(-4.5, 0)}{1}{90}
@@
   \node[blue!80!black,right] at (-5.1, 1.5) {\large $\lambda/4$};
-  \draw[line width=3] (-6 - 0.7, 2.5) -- (-6 - 0.1, 2.5 + 0.1);
+  \draw[line width=3,shift={(-6 - 0.4, 2.5 + 0.05)}] (-0.3, -0.02) -- (0.3, 0.02);
   % Post DP QWP

### 2020-11-24 sm.tex
Update on Overleaf.

@@
 
+\section{Excited Molecular States} 
+The lowest eight molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P.
+These eight potentials can be written in the Hund's case (a) basis as $ \mathrm{c^3\Sigma^+_{\Omega = 0^-},c^3\Sigma^+_{\Omega = 1}, b^3\Pi_{\Omega = 0^-}, b^3\Pi_{\Omega = 0^+}, b^3\Pi_{\Omega = 1}, b^3\Pi_{\Omega = 2}, B^1\Pi_{\Omega = 1}, A^1\Sigma^+_{\Omega = 0^+}}$ \cite{Korek2007}.
+Potential energy curves for $\mathrm{c^3\Sigma^+_{\Omega = 1}}$ and $  B^1\Pi_{\Omega = 1} $ have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
+Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed \mathrm{b-A} complex.
+
 \section{Calculating Matrix Elements with Coupled Channel Ground State}

### 2020-11-24 imgs/raman_spectroscopy_raman_beampath.tex
name coordinates

@@
 }
+\newcommand\drawmirror[3]{
+  % 1: center (x, y)
+  % 2: size
+  % 3: angle
+  \draw[line width=3] ($#1 + ({#2 * cos(#3)}, {#2 * sin(#3)})$) --
+  ($#1 - ({#2 * cos(#3)}, {#2 * sin(#3)})$);
+}
 
@@
 \begin{tikzpicture}
+  \coordinate (Raman Input) at (2, 0);
+  \coordinate (Raman Output) at (0, 2);
+  \coordinate (DP PBS) at (0, 0);
+  \coordinate (Wavemeter) at (0, -2);
+  \coordinate (DP AOM) at (-2, 0);
+  \coordinate (DP lens) at (-4.5, 0);
+  \coordinate (DP M1) at (-6, 0);
+  \coordinate (DP QWP) at (-6, 1.5);
+  \coordinate (DP M2) at (-6 - 0.4, 2.5 + 0.05);
+  \coordinate (SP QWP) at (-6, 3.5);
+  \coordinate (SP IM1) at (-6, 5);
+  \coordinate (SP lens) at (-7.5, 5);
+  \coordinate (SP PBS) at (-9, 5);
+  \coordinate (SP IM2) at (-11.5, 5);
+  \coordinate (SP AOM) at (-11.5, 3.3);
+  \coordinate (SP M1) at (-11.5, 0);
+  \coordinate (SP M2) at (-9, 0);
+  \coordinate (SP HWP) at (-9, 1.7);
+
   % Input
-  \node[red,above] at (2, 0) {\large\textbf{From Laser}};
-  \draw[red,line width=1.6,mid arrow] (2, 0) -- (0, 0);
+  \node[red,above] at (Raman Input) {\large\textbf{From Laser}};
+  \draw[red,line width=1.6,mid arrow] (Raman Input) -- (DP PBS);
   % Wavemeter
-  \draw[red,line width=1.6] (0, 0) -- (0, -1);
-  \draw[red,line width=1.6,mid arrow] (0, -1) -- (0, -2);
-  \node[red,below] at (0, -2) {\large\textbf{To wavemeter}};
+  \draw[red,line width=1.6] (DP PBS) -- ($(DP PBS) + (0, -1)$);
+  \draw[red,line width=1.6,mid arrow] ($(DP PBS) + (0, -1)$) -- (Wavemeter);
+  \node[red,below] at (Wavemeter) {\large\textbf{To wavemeter}};
   % Between PBS and DP AOM
-  \draw[red,line width=1.6,mid arrow2] (-2, 0) -- (0, 0);
+  \draw[red,line width=1.6,mid arrow2] (DP AOM) -- (DP PBS);
   \begin{scope}
     % Clip off one arrow
-    \clip (-1.23, 0) rectangle (-2, 1);
-    \draw[blue,line width=1.6,mid arrow2] (-2, 0) -- (0, 0);
+    \clip ($(DP AOM) + (0.77, 0)$) rectangle ($(DP AOM) + (0, 1)$);
+    \draw[blue,line width=1.6,mid arrow2] (DP AOM) -- (DP PBS);
   \end{scope}
@@
     % Redraw the clipped line
-    \clip (0, 0) rectangle (-2, 1);
-    \draw[blue,line width=1.6] (-2, 0) -- (0, 0);
+    \clip (DP PBS) rectangle ($(DP AOM) + (0, 1)$);
+    \draw[blue,line width=1.6] (DP AOM) -- (DP PBS);
   \end{scope}
   % Output
-  \draw[red,line width=1.6] (0, 0) -- (0, 1);
-  \draw[red,line width=1.6,mid arrow] (0, 1) -- (0, 2);
+  \draw[red,line width=1.6] (DP PBS) -- ($(DP PBS) + (0, 1)$);
+  \draw[red,line width=1.6,mid arrow] ($(DP PBS) + (0, 1)$) -- (Raman Output);
   \begin{scope}
-    \clip (0, 0) rectangle (-1, 3);
-    \draw[blue,line width=1.6] (0, 0) -- (0, 1);
-    \draw[blue,line width=1.6,mid arrow] (0, 1) -- (0, 2);
+    \clip (DP PBS) rectangle (-1, 3);
+    \draw[blue,line width=1.6] (DP PBS) -- ($(DP PBS) + (0, 1)$);
+    \draw[blue,line width=1.6,mid arrow] ($(DP PBS) + (0, 1)$) -- (Raman Output);
   \end{scope}
-  \node[red] at (0, 2.3) {\large\textbf{To Experiment}};
+  \node[red] at ($(Raman Output) + (0, 0.3)$) {\large\textbf{To Experiment}};
   \begin{scope}
-    \clip (-2, 2.3) rectangle (2, 3.5);
-    \node[blue] at (0, 2.3) {\large\textbf{To Experiment}};
+    \clip ($(Raman Output) + (-2, 0.3)$) rectangle ($(Raman Output) + (2, 1.5)$);
+    \node[blue] at ($(Raman Output) + (0, 0.3)$) {\large\textbf{To Experiment}};
   \end{scope}
-  \draw[red,line width=1.6,mid arrow2] (-2, 0) -- (-6, 0);
-  \draw[blue,line width=1.6,mid arrow2] (-2, 0) --
-  node[above,pos=0.34,rotate=-5] {\small $\approx\!+345~\mathrm{MHz}$} (-6 - 0.3, 0 + 0.3);
-  \draw[blue,line width=1.6,mid arrow2] (-6 - 0.3, 0 + 0.3) -- (-6 - 0.4, 2.5 + 0.05);
-  \draw[red,line width=1.6,mid arrow2] (-6, 0) -- (-6, 5);
-  \draw[red,line width=1.6,mid arrow2] (-7.5, 5) -- (-6, 5);
-  \draw[red,line width=1.6] (-7.5, 5) -- (-9, 5);
-  \draw[red,line width=1.6] (-9, 5) -- (-10, 5);
-  \draw[red,line width=1.6,mid arrow] (-10, 5) -- (-11.5, 5);
-  \draw[red,line width=1.6] (-11.5, 5) -- (-11.5, 3.3);
-  \draw[red,line width=1.6,mid arrow] (-11.5, 3.3) --
-  node[above,rotate=86,pos=0.45] {\small $-80~\mathrm{MHz}$} (-11.5 - 0.2, 0 + 0.2);
-  \draw[red,line width=1.6,mid arrow] (-11.5 - 0.2, 0 + 0.2) -- (-9, 0);
-  \draw[red,line width=1.6,mid arrow] (-9, 0) -- (-9, 5);
+  \draw[red,line width=1.6,mid arrow2] (DP AOM) -- (DP M1);
+  \draw[blue,line width=1.6,mid arrow2] (DP AOM) --
+  node[above,pos=0.34,rotate=-5] {\small $\approx\!+345~\mathrm{MHz}$} ($(DP M1) + (-0.3, 0.3)$);
+  \draw[blue,line width=1.6,mid arrow2] ($(DP M1) + (-0.3, 0.3)$) -- (DP M2);
+  \draw[red,line width=1.6,mid arrow2] (DP M1) -- (SP IM1);
+  \draw[red,line width=1.6,mid arrow2] (SP lens) -- (SP IM1);
+  \draw[red,line width=1.6] (SP lens) -- (SP PBS);
+  \draw[red,line width=1.6] (SP PBS) -- ($(SP PBS) + (-1, 0)$);
+  \draw[red,line width=1.6,mid arrow] ($(SP PBS) + (-1, 0)$) -- (SP IM2);
+  \draw[red,line width=1.6] (SP IM2) -- (SP AOM);
+  \draw[red,line width=1.6,mid arrow] (SP AOM) --
+  node[above,rotate=86,pos=0.45] {\small $-80~\mathrm{MHz}$} ($(SP M1) + (-0.2, 0.2)$);
+  \draw[red,line width=1.6,mid arrow] ($(SP M1) + (-0.2, 0.2)$) -- (SP M2);
+  \draw[red,line width=1.6,mid arrow] (SP M2) -- (SP PBS);
   % Input PBS
-  \drawpbs{(0, 0)}{0.7}{0}
-  \node[blue!40!cyan,below right] at (0 + 0.7, 0 - 0.7) {\large PBS 1};
+  \drawpbs{(DP PBS)}{0.7}{0}
+  \node[blue!40!cyan,below right] at ($(DP PBS) + (0.7, -0.7)$) {\large PBS 1};
   % DP AOM
-  \drawaom{(-2, 0)}{1}{0.5}{90}
-  \node[rotate=-90] at (-2, 0) {\large DP AOM};
+  \drawaom{(DP AOM)}{1}{0.5}{90}
+  \node[rotate=-90] at (DP AOM) {\large DP AOM};
   % DP Lens
-  % \node[rotate=90] at (-4.5, 0) {\includegraphics[width={2 cm}]{lens.pdf}};
-  \drawlens{(-4.5, 0)}{1}{90}
-  \node[blue!80!cyan,below] at (-4.5, -1) {\large L1};
-  \draw[line width=3] (-6 - 0.7, 0 + 0.7) -- (-6 + 0.7, 0 - 0.7);
+  \drawlens{(DP lens)}{1}{90}
+  \node[blue!80!cyan,below] at ($(DP lens) + (0, -1)$-4.5, -1) {\large L1};
+  \drawmirror{(DP M1)}{0.9}{-45}
   % DP QWP
-  \drawwaveplate{(-6, 1.5)}{1}{0}
-  \node[blue!80!black,right] at (-5.1, 1.5) {\large $\lambda/4$};
-  \draw[line width=3,shift={(-6 - 0.4, 2.5 + 0.05)}] (-0.3, -0.02) -- (0.3, 0.02);
+  \drawwaveplate{(DP QWP)}{1}{0}
+  \node[blue!80!black,right] at ($(DP QWP) + (0.9, 0)$) {\large $\lambda/4$};
+  \drawmirror{(DP M2)}{0.3}{3.8}
   % Post DP QWP
-  \drawwaveplate{(-6, 3.5)}{1}{0}
-  \node[blue!80!black,right] at (-5.1, 3.5) {\large $\lambda/4$};
-  \draw[line width=3] (-6 - 0.7, 5 + 0.7) -- (-6 + 0.7, 5 - 0.7);
+  \drawwaveplate{(SP QWP)}{1}{0}
+  \node[blue!80!black,right] at ($(SP QWP) + (0.9, 0)$) {\large $\lambda/4$};
+  \drawmirror{(SP IM1)}{0.9}{-45}
   % Post DP Lens
-  \drawlens{(-7.5, 5)}{1}{90}
-  \node[blue!80!cyan,above] at (-7.5, 6) {\large L2};
+  \drawlens{(SP lens)}{1}{90}
+  \node[blue!80!cyan,above] at ($(SP lens) + (0, 1)$) {\large L2};
   % SP PBS
-  \drawpbs{(-9, 5)}{0.7}{0}
-  \node[blue!40!cyan,above] at (-9, 5 + 0.7) {\large PBS 2};
-  \draw[line width=3] (-11.5 - 0.7, 5 - 0.7) -- (-11.5 + 0.7, 5 + 0.7);
+  \drawpbs{(SP PBS)}{0.7}{0}
+  \node[blue!40!cyan,above] at ($(SP PBS) + (0, 0.7)$) {\large PBS 2};
+  \drawmirror{(SP IM2)}{0.9}{45}
   % SP AOM
-  \drawaom{(-11.5, 3.3)}{1}{0.5}{0}
-  \node at (-11.5, 3.3) {\large SP AOM};
-  \draw[line width=3] (-11.5 - 0.7, 0 + 0.7) -- (-11.5 + 0.7, 0 - 0.7);
-  \draw[line width=3] (-9 - 0.7, 0 - 0.7) -- (-9 + 0.7, 0 + 0.7);
+  \drawaom{(SP AOM)}{1}{0.5}{0}
+  \node at (SP AOM) {\large SP AOM};
+  \drawmirror{(SP M1)}{0.9}{-45}
+  \drawmirror{(SP M2)}{0.9}{45}
   % SP HWP
-  \drawwaveplate{(-9, 1.7)}{1}{0}
-  \node[blue!80!black,left] at (-9.9, 1.7) {\large $\lambda/2$};
-
-  \draw[gray,opacity=0.8,line width=1,dashed] (-4, 6) |- (2.8, 2.8);
-
-  \begin{scope}[shift={(-1.4, 4)}]
-    \draw[red,line width=1.6,mid arrow] (3, 0) node[below] {\large\textbf{Input}} -- (0, 0);
-    \draw[red,line width=1.6,mid arrow] (0, 0) -- ({3 * cos(40)}, {3 * sin(40)})
-    node[left] {\large\textbf{Output}};
-    \draw[gray,line width=6] ({-0.7 * tan(20)}, 0.7) --
-    node[black,left] {\large ASE Filter} ({0.7 * tan(20)}, -0.7);
-  \end{scope}
+  \drawwaveplate{(SP HWP)}{1}{0}
+  \node[blue!80!black,left] at ($(SP HWP) + (-0.9, 0)$) {\large $\lambda/2$};
 \end{tikzpicture}

### 2020-11-24 sm.tex
Update on Overleaf.

@@
 Potential energy curves for $\mathrm{c^3\Sigma^+_{\Omega = 1}}$ and $  B^1\Pi_{\Omega = 1} $ have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
-Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed \mathrm{b-A} complex.
+Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed \mathrm{A-b} complex \cite{Zaharova2009}.
+Since we are most closely detuned from the $  $
 

### 2020-11-24 sm.tex
Update on Overleaf.

@@
 These eight potentials can be written in the Hund's case (a) basis as $ \mathrm{c^3\Sigma^+_{\Omega = 0^-},c^3\Sigma^+_{\Omega = 1}, b^3\Pi_{\Omega = 0^-}, b^3\Pi_{\Omega = 0^+}, b^3\Pi_{\Omega = 1}, b^3\Pi_{\Omega = 2}, B^1\Pi_{\Omega = 1}, A^1\Sigma^+_{\Omega = 0^+}}$ \cite{Korek2007}.
-Potential energy curves for $\mathrm{c^3\Sigma^+_{\Omega = 1}}$ and $  B^1\Pi_{\Omega = 1} $ have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
+Potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
 Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed \mathrm{A-b} complex \cite{Zaharova2009}.
-Since we are most closely detuned from the $  $
+Since our experiment attempts to work in a regime where the predominant coupling and scattering comes from the $ c^3\Sigma^+_1 v'$
 

### 2020-11-24 sm.tex
Update on Overleaf.

@@
 Potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
-Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed \mathrm{A-b} complex \cite{Zaharova2009}.
-Since our experiment attempts to work in a regime where the predominant coupling and scattering comes from the $ c^3\Sigma^+_1 v'$
+Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed A-b complex \cite{Zaharova2009}.
+Since our experiment attempts to work in a regime where the predominant coupling and scattering comes from the $v' = 0$ state of the $ \mathrm{c^3\Sigma^+_1} $
 

### 2020-11-24 sm.tex
Update on Overleaf.

--- 2020-11-24 sm.tex
@@
 Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed \mathrm{A-b} complex \cite{Zaharova2009}.
-Since our experiment attempts to work in a regime where the predominant coupling and scattering comes from the $ c^3\Sigma^+_1 v'$
+Since our experiment attempts to work in a regime where the predominant Raman coupling and scattering comes from the $v' = 0$ state of the $ \mathrm{c^3\Sigma^+_1} $, the contribution
 

### 2020-11-24 sm.tex

@@
 Potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
-Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed \mathrm{A-b} complex \cite{Zaharova2009}.
+Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed A-b complex \cite{Zaharova2009}.
 Since our experiment attempts to work in a regime where the predominant Raman coupling and scattering comes from the $v' = 0$ state of the $ \mathrm{c^3\Sigma^+_1} $, the contribution

### 2020-11-24 sm.tex
Update on Overleaf.

--- 2020-11-24 sm.tex
@@
 \section{Excited Molecular States} 
-The lowest eight molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P.
+To obtain a full calculation for the expected Raman Rabi frequency, light shift and scattering, we need to account for all molecular stThe lowest eight molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P.
 These eight potentials can be written in the Hund's case (a) basis as $ \mathrm{c^3\Sigma^+_{\Omega = 0^-},c^3\Sigma^+_{\Omega = 1}, b^3\Pi_{\Omega = 0^-}, b^3\Pi_{\Omega = 0^+}, b^3\Pi_{\Omega = 1}, b^3\Pi_{\Omega = 2}, B^1\Pi_{\Omega = 1}, A^1\Sigma^+_{\Omega = 0^+}}$ \cite{Korek2007}.

### 2020-11-24 sm.tex
Update on Overleaf.

--- 2020-11-24 sm.tex
@@
 \section{Excited Molecular States} 
+To obtain a full calculation for the expected Raman Rabi frequency, light shift and scattering, we need to account for all the excited molecular states.
 The lowest eight molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P.

### 2020-11-24 sm.tex
Update on Overleaf.

@@
 These eight potentials can be written in the Hund's case (a) basis as $ \mathrm{c^3\Sigma^+_{\Omega = 0^-},c^3\Sigma^+_{\Omega = 1}, b^3\Pi_{\Omega = 0^-}, b^3\Pi_{\Omega = 0^+}, b^3\Pi_{\Omega = 1}, b^3\Pi_{\Omega = 2}, B^1\Pi_{\Omega = 1}, A^1\Sigma^+_{\Omega = 0^+}}$ \cite{Korek2007}.
-Potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
-Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed A-b complex \cite{Zaharova2009}.
+We use potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ that have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
+Unfortunately, simple single-channel Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed \mathrm{A-b} complex \cite{Zaharova2009}.
 Since our experiment attempts to work in a regime where the predominant Raman coupling and scattering comes from the $v' = 0$ state of the $ \mathrm{c^3\Sigma^+_1} $, the contribution

### 2020-11-24 sm.tex
Update on Overleaf.

@@
 We use potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ that have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
-Unfortunately, simple single-channel Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed \mathrm{A-b} complex \cite{Zaharova2009}.
+Unfortunately, simple single-channel potentials Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed $\mathrm{A-b}$ complex \cite{Zaharova2009}.
 Since our experiment attempts to work in a regime where the predominant Raman coupling and scattering comes from the $v' = 0$ state of the $ \mathrm{c^3\Sigma^+_1} $, the contribution

### 2020-11-24 sm.tex

--- 2020-11-24 sm.tex
@@
 We use potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ that have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
-Unfortunately, simple single-channel Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed \mathrm{A-b} complex \cite{Zaharova2009}.
+Unfortunately, simple single-channel Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed A-b complex \cite{Zaharova2009}.
 Since our experiment attempts to work in a regime where the predominant Raman coupling and scattering comes from the $v' = 0$ state of the $ \mathrm{c^3\Sigma^+_1} $, the contribution

### 2020-11-24 imgs/raman_spectroscopy_raman_beampath.tex
Compact figure

@@
   \coordinate (Wavemeter) at (0, -2);
-  \coordinate (DP AOM) at (-2, 0);
-  \coordinate (DP lens) at (-4.5, 0);
-  \coordinate (DP M1) at (-6, 0);
-  \coordinate (DP QWP) at (-6, 1.5);
-  \coordinate (DP M2) at (-6 - 0.4, 2.5 + 0.05);
-  \coordinate (SP QWP) at (-6, 3.5);
-  \coordinate (SP IM1) at (-6, 5);
-  \coordinate (SP lens) at (-7.5, 5);
-  \coordinate (SP PBS) at (-9, 5);
-  \coordinate (SP IM2) at (-11.5, 5);
-  \coordinate (SP AOM) at (-11.5, 3.3);
-  \coordinate (SP M1) at (-11.5, 0);
-  \coordinate (SP M2) at (-9, 0);
-  \coordinate (SP HWP) at (-9, 1.7);
+  \coordinate (DP AOM) at (-1.7, 0);
+  \coordinate (DP lens) at (-4.2, 0);
+  \coordinate (DP M1) at (-5.2, 0);
+  \coordinate (DP QWP) at (-5.2, 1.4);
+  \coordinate (DP M2) at (-5.2 - 0.4, 2.0 + 0.05);
+  \coordinate (SP QWP) at (-5.2, 2.9);
+  \coordinate (SP IM1) at (-5.2, 4);
+  \coordinate (SP lens) at (-6.5, 4);
+  \coordinate (SP PBS) at (-7.5, 4);
+  \coordinate (SP IM2) at (-10, 4);
+  \coordinate (SP AOM) at (-10, 2.7);
+  \coordinate (SP M1) at (-10, 0);
+  \coordinate (SP M2) at (-7.5, 0);
+  \coordinate (SP HWP) at (-7.5, 1.7);
 
@@
   % Between PBS and DP AOM
-  \draw[red,line width=1.6,mid arrow2] (DP AOM) -- (DP PBS);
+  \draw[red,line width=1.6] ($(DP PBS) + (-1.2, 0)$) -- (DP AOM);
+  \draw[red,line width=1.6,mid arrow2] ($(DP PBS) + (-1.2, 0)$) -- (DP PBS);
   \begin{scope}
     % Clip off one arrow
-    \clip ($(DP AOM) + (0.77, 0)$) rectangle ($(DP AOM) + (0, 1)$);
-    \draw[blue,line width=1.6,mid arrow2] (DP AOM) -- (DP PBS);
+    \clip ($(DP AOM) + (0.9, 0)$) rectangle ($(DP AOM) + (0, 1)$);
+    \draw[blue,line width=1.6] ($(DP PBS) + (-1.2, 0)$) -- (DP AOM);
+    \draw[blue,line width=1.6,mid arrow2] ($(DP PBS) + (-1.2, 0)$) -- (DP PBS);
   \end{scope}
@@
   \draw[blue,line width=1.6,mid arrow2] (DP AOM) --
-  node[above,pos=0.34,rotate=-5] {\small $\approx\!+345~\mathrm{MHz}$} ($(DP M1) + (-0.3, 0.3)$);
+  node[above,pos=0.38,rotate=-6] {\small $\approx\!+345~\mathrm{MHz}$} ($(DP M1) + (-0.3, 0.3)$);
   \draw[blue,line width=1.6,mid arrow2] ($(DP M1) + (-0.3, 0.3)$) -- (DP M2);
@@
   \draw[red,line width=1.6,mid arrow] (SP AOM) --
-  node[above,rotate=86,pos=0.45] {\small $-80~\mathrm{MHz}$} ($(SP M1) + (-0.2, 0.2)$);
+  node[above,rotate=86,pos=0.5] {\small $-80~\mathrm{MHz}$} ($(SP M1) + (-0.2, 0.2)$);
   \draw[red,line width=1.6,mid arrow] ($(SP M1) + (-0.2, 0.2)$) -- (SP M2);

### 2020-11-24 sm.tex

@@
 
-\section{Excited Molecular States}
+\section{Excited Molecular States} \label{sm:excited_states}
 To obtain a full calculation for the expected Raman Rabi frequency, light shift and scattering, we need to account for all the excited molecular states. 
@@
 These eight potentials can be written in the Hund's case (a) basis as $ \mathrm{c^3\Sigma^+_{\Omega = 0^-},c^3\Sigma^+_{\Omega = 1}, b^3\Pi_{\Omega = 0^-}, b^3\Pi_{\Omega = 0^+}, b^3\Pi_{\Omega = 1}, b^3\Pi_{\Omega = 2}, B^1\Pi_{\Omega = 1}, A^1\Sigma^+_{\Omega = 0^+}}$ \cite{Korek2007}.
-We use potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ that have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
-Unfortunately, simple single-channel Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed A-b complex \cite{Zaharova2009}.
-Since our experiment attempts to work in a regime where the predominant Raman coupling and scattering comes from the $v' = 0$ state of the $ \mathrm{c^3\Sigma^+_1} $, the contribution
+Due to spin-orbit coupling, especially large in Cs, the excited molecular states are mixed, containing components in multiple potentials. 
+Fortunately, single-channel potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
+Since there is only one $ \Omega = 2$ potential at this dissociation limit, a single-channel potential has been determined for $ b^3\Pi_2$ as well \cite{Zabawa2012}.
+Unfortunately, single-channel potentials for the other electronic states do not exist. 
+A deperturbation analysis was required for states belonging to the mixed $\mathrm{A-b}$ complex, 
+and the fitted potentials and spin-orbit coupling coefficients are only accurate within the energy range of the measured experimental data \cite{Zaharova2009}. 
+Since our experiment attempts to work in a regime where the predominant Raman coupling comes from the $v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $, 
+the contribution of the other seven potentials is mainly to a background that is nearly detuning independent. 
+Thus, for computational ease, we use the diabatic potentials for $ \mathrm{b^3\Pi_{0}, b^3\Pi_{1}} $ and $ \mathrm{A^1\Sigma^+_{0^+}}$, and remove the states nearest to the $ v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $.
+Lastly, to our knowledge, no potential fit to experimental data exists for the $ c^3\Sigma^+_{0^-}$ state.
+Assuming that its contribution is only to the background, as an approximation, we simply double the contribution of all states except $v' = 0$ from $ c^3\Sigma^+_1$.
 
 \section{Calculating Matrix Elements with Coupled Channel Ground State}
-To calculate Rabi frequencies for transitions to intermediate vibrational levels of the c$^3\Sigma^+ (\Omega=1)$ electronic state, we
-obtain their wavefunctions from a single-channel calculation using the potential curve of \cite{Grochola2011}. We
-then calculate overlap integrals between this function and the triplet ($S=1$) components of the
+To calculate Rabi frequencies for transitions to the eight excited molecular potentials, we
+obtain their wavefunctions from a single-channel calculation \cite{Fattal1996} using the potential energy curves described in section \ref{sm:excited_states}. We
+then calculate overlap integrals between these functions and either the triplet ($S=1$) or singlet ($S=0$) components of the
 coupled-channel wavefunctions for either the target molecular state or the confined atomic state.
-These calculations assume that the intermediate state has pure triplet character and neglect its
+These calculations assume that the intermediate states have pure singlet or triplet character and neglect its
 nuclear spin character, which is unknown.
@@
 The full calculation of the Raman Rabi frequency and scattering rate using the methods in section \ref{sm:sect_2} is shown in figure \ref{f-sm}.
-The strong contribution from the atomic threshold arises from the large overlap near-threshold bound states.
+The strong contribution from the atomic threshold arises from the large overlap to the near-threshold bound states.
 This leads to a $1/\delta_{\text{thresh}}^2$ dependence of the scattering rate and favors using deeply bound states as the intermediate state for the Raman transfer.
-The Raman Rabi frequency is larger than the scattering rate only for the deeply bound states.
 
@@
 The second frequency in the Raman transition is offset by about $770~\mathrm{MHz}$ and resonant with the two photon transition.
-The assumed excited-state linewidth for all molecular lines is $20~\text{MHz} $.
+The assumed excited-state linewidth for all molecular lines is $50~\text{MHz} $.
     \label{f-sm}}

### 2020-11-24 plot_fcf.jl
[imgs] Plot FCFs

@@ -1,0 +1,32 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+# using DataStructures
+# using LsqFit
+using LibArchive
+
+using DelimitedFiles
+
+# const fname = joinpath(@__DIR__, "../damop-2020/20MHz_linewidth_c3SigmaOnly_3322_80kHzConfinement.csv.zst")
+const fname = joinpath(@__DIR__, "data/FCFtoc3Sigma.csv")
+const data = readdlm(fname, ',', skipstart=1)
+const prefix = joinpath(@__DIR__, "imgs", "fcf")
+
+figure(figsize=[13.8, 4.8])
+plot(data, "C0o-")
+xlabel("\$v'\$")
+ylabel("FCF")
+yscale("log")
+xlim([0, 73])
+grid()
+NaCsPlot.maybe_save("$(prefix)_c3sigma")
+
+NaCsPlot.maybe_show()

### 2020-11-24 plot_fcf.jl
... clean up

@@ -15,7 +15,6 @@ using LibArchive
 
 using DelimitedFiles
 
-# const fname = joinpath(@__DIR__, "../damop-2020/20MHz_linewidth_c3SigmaOnly_3322_80kHzConfinement.csv.zst")
 const fname = joinpath(@__DIR__, "data/FCFtoc3Sigma.csv")
 const data = readdlm(fname, ',', skipstart=1)
 const prefix = joinpath(@__DIR__, "imgs", "fcf")

### 2020-11-25 paper.tex
Update on Overleaf.

@@
     & Experiment & Theory \\ \hline
+    $\Omega_R $ & & $2\pi \times 15.3~\mathrm{kHz}$ \\
+    $\Gamma_S$ & & $ 2\pi \times 533~\mathrm{Hz}$ \\
     $ \Omega_m $ & $2\pi \times 140.06(8) ~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
@@
   \end{tabular}
-  \caption{Comparison between theory and experiment of the Rabi frequencies $\Omega_m$ and $\Omega_a$ at $3.75$ mW tweezer power.
-The experimentally measured ratio $\Omega_m/\Omega_a$ is smaller than the theory prediction.}
+  \caption{Comparison between theory and experiment of $\Omega_R,\Gamma_S, \Omega_m, \Omega_a$.
+$\Omega_R$ and $ \Gamma_S $ are reported at $145~\mathrm{GHz}$ detuned from the $v' = 0$ state.
+All numbers are reported at $3.75$ mW tweezer power.
+}
   \label{tab:rabi_freqs}
@@
 or a narrow excited state. The formation of a weakly bound molecule is a key step
-in forming rovibrational ground state molecules. By scaling up to many optical tweezers, large arrays with arbitrary geometry of highly controlled molecules can be achieved.
+in forming rovibrational ground state molecules.
+By scaling up to many optical tweezers\cite{Endres2016, Barredo2018, PhysRevX.8.041055, PhysRevLett.122.203601}, large arrays with arbitrary geometry of highly controlled molecules can be achieved.
 % Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},

### 2020-11-25 sm.tex
Update on Overleaf.

@@
 To obtain a full calculation for the expected Raman Rabi frequency, light shift and scattering, we need to account for all the excited molecular states.
-The lowest eight molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P. 
+The lowest eight excited molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P.
 These eight potentials can be written in the Hund's case (a) basis as $ \mathrm{c^3\Sigma^+_{\Omega = 0^-},c^3\Sigma^+_{\Omega = 1}, b^3\Pi_{\Omega = 0^-}, b^3\Pi_{\Omega = 0^+}, b^3\Pi_{\Omega = 1}, b^3\Pi_{\Omega = 2}, B^1\Pi_{\Omega = 1}, A^1\Sigma^+_{\Omega = 0^+}}$ \cite{Korek2007}.
@@
 nuclear spin character, which is unknown.
+These calculations include electronic transition dipole moments, calculated ab initio by \textcolor{red}{Should we just mention Mosynski or Rosario?
+or say something about the ab initio method and give a citation.}
 
 The full calculation of the Raman Rabi frequency and scattering rate using the methods in section \ref{sm:sect_2} is shown in figure \ref{f-sm}.
-The strong contribution from the atomic threshold arises from the large overlap to the near-threshold bound states.
+The strong contribution from the atomic threshold arises from the large overlap to the near-threshold bound states shown in figure \ref{f-smfcf} for the $c^3\Sigma^+_1$ state.
 This leads to a $1/\delta_{\text{thresh}}^2$ dependence of the scattering rate and favors using deeply bound states as the intermediate state for the Raman transfer.
+A similar result holds for the other excited state potentials.
 
@@
     \label{f-sm}}
+\end{figure}
+
+\begin{figure}[ht!]
+  \includegraphics[width=\textwidth]{imgs/fcf_c3sigma.pdf}
+  \caption{The Franck-Condon Factor (FCF) between the target molecular state and vibrational state $v'$ of $c^3\Sigma^+_1$.
+The potential supports 74 bound states, and the predominant contribution arises from the near-threshold bound states.
+The total overlap with all the bound states is $0.4822$, which is $96.8\%$ of the total triplet fraction of the target molecular state.
+    \label{f-smfcf}}
 \end{figure}

### 2020-11-25 imgs/raman_spectroscopy_raman_beampath.tex
Beam path figure

@@
 \usepackage[colorlinks=true]{hyperref}
-\usetikzlibrary{
+\usetikzlibrary{decorations.pathreplacing,
   arrows,
@@
         markings,
-        mark=at position .5 with {\arrow[#1]{stealth}}
+        mark=at position #1 with {\arrow[>=stealth]{>}}
       }}},
+  mid arrow/.default=0.5,
   mid arrow2/.style={postaction={decorate,decoration={
         markings,
-        mark=at position .5 with {\arrow[>=stealth]{><}}
+        mark=at position #1 with {\arrow[>=stealth]{><}}
       }}},
+  mid arrow2/.default=0.5,
 }
@@
 }
-\newcommand\drawmirror[3]{
-  % 1: center (x, y)
-  % 2: size
-  % 3: angle
-  \draw[line width=3] ($#1 + ({#2 * cos(#3)}, {#2 * sin(#3)})$) --
-  ($#1 - ({#2 * cos(#3)}, {#2 * sin(#3)})$);
+\newcommand\drawmirror[4][line width=3]{
+  % 1: draw option
+  % 2: center (x, y)
+  % 3: size
+  % 4: angle
+  \draw[#1] ($#2 + ({#3 * cos(#4)}, {#3 * sin(#4)})$) --
+  ($#2 - ({#3 * cos(#4)}, {#3 * sin(#4)})$);
 }
@@
 \begin{tikzpicture}
-  \coordinate (Raman Input) at (2, 0);
-  \coordinate (Raman Output) at (0, 2);
+  \coordinate (Fiber 1 Out) at (1.3, 0);
+  \coordinate (Fiber 1 In) at ($(Fiber 1 Out) + (1.3, 0)$);
+  \coordinate (Filter 1) at ($(Fiber 1 In) + (1.6, 0)$);
+  \coordinate (Input) at ($(Filter 1) + ({-2 * cos(44)}, {2 * sin(44)})$);
+
   \coordinate (DP PBS) at (0, 0);
@@
   \coordinate (DP M2) at (-5.2 - 0.4, 2.0 + 0.05);
-  \coordinate (SP QWP) at (-5.2, 2.9);
+  \coordinate (SP QWP) at (-5.2, 2.4);
   \coordinate (SP IM1) at (-5.2, 4);
@@
 
+  \coordinate (Servo AOM) at (0, 1.8);
+  \coordinate (Fiber 2 In) at (0.3, 3.2);
+  \coordinate (Fiber 2 Out) at ($(Fiber 2 In) + (0.5, 0.65) + (-1.7, 0.7)$);
+  \coordinate (Pick Off) at ($(Fiber 2 Out) + (-0.5, 0)$);
+  \coordinate (Servo PD) at ($(Pick Off) + ({0.8 * cos(30)}, {0.8 * sin(30)})$);
+  \coordinate (Filter 2) at ($(Pick Off) + (-1.5, 0)$);
+  \coordinate (Output) at ($(Filter 2) + ({2 * cos(44)}, {2 * sin(44)})$);
+
+  \draw[gray!30!white,line width=2] (-4.2, 5.6) |- (-1, 3.3);
+  \draw[gray!30!white,line width=2] (2.0, 5.6) |- (2.0, 1.3);
+
   % Input
-  \node[red,above] at (Raman Input) {\large\textbf{From Laser}};
-  \draw[red,line width=1.6,mid arrow] (Raman Input) -- (DP PBS);
+  \draw[red,line width=1.6,mid arrow] (Fiber 1 Out) -- (DP PBS);
+  % Filter 1
+  \draw[red,line width=1.6,mid arrow=0.6] (Filter 1) -- (Fiber 1 In);
+  \draw[red,line width=1.6,mid arrow=0.6] (Input) -- (Filter 1);
+  \node[red,above] at ($(Input) + (0.6, 0)$) {\large\textbf{From Laser}};
+
   % Wavemeter
-  \draw[red,line width=1.6] (DP PBS) -- ($(DP PBS) + (0, -1)$);
-  \draw[red,line width=1.6,mid arrow] ($(DP PBS) + (0, -1)$) -- (Wavemeter);
-  \node[red,below] at (Wavemeter) {\large\textbf{To wavemeter}};
+  \draw[red,line width=1.6,mid arrow=0.7] (DP PBS) -- (Wavemeter);
+  \node[red,below] at (Wavemeter) {\large\textbf{To Wavemeter}};
   % Between PBS and DP AOM
-  \draw[red,line width=1.6] ($(DP PBS) + (-1.2, 0)$) -- (DP AOM);
-  \draw[red,line width=1.6,mid arrow2] ($(DP PBS) + (-1.2, 0)$) -- (DP PBS);
+  \draw[red,line width=1.6,mid arrow2=0.6] (DP AOM) -- (DP PBS);
+  \draw[blue,dashed,line width=1.6] (DP AOM) -- (DP PBS);
   \begin{scope}
     % Clip off one arrow
-    \clip ($(DP AOM) + (0.9, 0)$) rectangle ($(DP AOM) + (0, 1)$);
-    \draw[blue,line width=1.6] ($(DP PBS) + (-1.2, 0)$) -- (DP AOM);
-    \draw[blue,line width=1.6,mid arrow2] ($(DP PBS) + (-1.2, 0)$) -- (DP PBS);
-  \end{scope}
-  \begin{scope}
-    % Redraw the clipped line
-    \clip (DP PBS) rectangle ($(DP AOM) + (0, 1)$);
-    \draw[blue,line width=1.6] (DP AOM) -- (DP PBS);
+    \clip ($(DP AOM) + (0.85cm, 0.81pt)$) rectangle ($(DP AOM) + (0, 1)$);
+    \draw[blue,dashed,line width=1.6,mid arrow2=0.6] (DP AOM) -- (DP PBS);
   \end{scope}
   % Output
-  \draw[red,line width=1.6] (DP PBS) -- ($(DP PBS) + (0, 1)$);
-  \draw[red,line width=1.6,mid arrow] ($(DP PBS) + (0, 1)$) -- (Raman Output);
-  \begin{scope}
-    \clip (DP PBS) rectangle (-1, 3);
-    \draw[blue,line width=1.6] (DP PBS) -- ($(DP PBS) + (0, 1)$);
-    \draw[blue,line width=1.6,mid arrow] ($(DP PBS) + (0, 1)$) -- (Raman Output);
-  \end{scope}
-  \node[red] at ($(Raman Output) + (0, 0.3)$) {\large\textbf{To Experiment}};
-  \begin{scope}
-    \clip ($(Raman Output) + (-2, 0.3)$) rectangle ($(Raman Output) + (2, 1.5)$);
-    \node[blue] at ($(Raman Output) + (0, 0.3)$) {\large\textbf{To Experiment}};
-  \end{scope}
+  \draw[red,line width=1.6,mid arrow=0.65] (DP PBS) -- (Servo AOM);
+  \draw[blue,dashed,line width=1.6] (DP PBS) -- (Servo AOM);
   \draw[red,line width=1.6,mid arrow2] (DP AOM) -- (DP M1);
@@
   \draw[red,line width=1.6] (SP lens) -- (SP PBS);
-  \draw[red,line width=1.6] (SP PBS) -- ($(SP PBS) + (-1, 0)$);
-  \draw[red,line width=1.6,mid arrow] ($(SP PBS) + (-1, 0)$) -- (SP IM2);
+  \draw[red,line width=1.6,mid arrow=0.6] (SP PBS) -- (SP IM2);
   \draw[red,line width=1.6] (SP IM2) -- (SP AOM);
@@
   \draw[red,line width=1.6,mid arrow] (SP M2) -- (SP PBS);
+
+  % Servo AOM
+  \draw[red,line width=1.6,mid arrow=0.65] (Servo AOM) -- (Fiber 2 In);
+  \draw[blue,dashed,line width=1.6] (Servo AOM) -- (Fiber 2 In);
+  % Pick Off
+  \draw[red,line width=1.6] (Fiber 2 Out) -- (Pick Off);
+  \draw[blue,dashed,line width=1.6] (Fiber 2 Out) -- (Pick Off);
+  \draw[red!50!white,line width=1.2] (Pick Off) -- (Servo PD);
+  \draw[blue!50!white,dashed,line width=1.2] (Pick Off) -- (Servo PD);
+  \node[right] (Servo Pickoff Node) at (Servo PD) {Servo Pickoff};
+  % Filter 2
+  \draw[red,line width=1.6,mid arrow] (Pick Off) -- (Filter 2);
+  \draw[blue,dashed,line width=1.6] (Pick Off) -- (Filter 2);
+  % Output
+  \draw[red,line width=1.6,mid arrow=0.6] (Filter 2) -- (Output);
+  \draw[blue,dashed,line width=1.6] (Filter 2) -- (Output);
+  \node[red,right] at (Output) {\large\textbf{To Tweezer}};
+  \begin{scope}
+    \clip ($(Output) + (0, 0)$) rectangle ($(Output) + (4, 0.2)$);
+    \node[blue,right] at (Output) {\large\textbf{To Tweezer}};
+  \end{scope}
+
+  %% Components
+  \begin{scope}[shift={($(Fiber 1 Out) + (0.65, 0.5)$)}]
+    \draw[line width=1.2]
+    (Fiber 1 Out) --
+    plot[domain={(-180 - 360 + 90):(180 + 360 + 90)},smooth,variable=\x,samples=2000]
+    ({0.5 * cos(\x) + 0.0003 * \x}, {0.5 * sin(\x)}) -- (Fiber 1 In);
+    \node[below] at (0, -0.5) {Fiber 1};
+  \end{scope}
+  \drawmirror[line width=8,gray!60!white]{(Filter 1)}{0.5}{68};
+  \node[below] at ($(Filter 1) + (-0.4, -0.45)$) {ASE Filter 1};
+
   % Input PBS
   \drawpbs{(DP PBS)}{0.7}{0}
-  \node[blue!40!cyan,below right] at ($(DP PBS) + (0.7, -0.7)$) {\large PBS 1};
+  \node[blue!40!cyan,below right] at ($(DP PBS) + (0.2, -0.5)$) {\large PBS 1};
   % DP AOM
-  \drawaom{(DP AOM)}{1}{0.5}{90}
+  \drawaom{(DP AOM)}{1}{0.4}{90}
   \node[rotate=-90] at (DP AOM) {\large DP AOM};
@@
   \drawwaveplate{(DP QWP)}{1}{0}
-  \node[blue!80!black,right] at ($(DP QWP) + (0.9, 0)$) {\large $\lambda/4$};
+  \node[blue!80!black,right] at ($(DP QWP) + (0.8, 0)$) {\large $\lambda/4$};
   \drawmirror{(DP M2)}{0.3}{3.8}
@@
   \drawwaveplate{(SP QWP)}{1}{0}
-  \node[blue!80!black,right] at ($(SP QWP) + (0.9, 0)$) {\large $\lambda/4$};
+  \node[blue!80!black,right] at ($(SP QWP) + (0.8, 0)$) {\large $\lambda/4$};
   \drawmirror{(SP IM1)}{0.9}{-45}
@@
   \drawpbs{(SP PBS)}{0.7}{0}
-  \node[blue!40!cyan,above] at ($(SP PBS) + (0, 0.7)$) {\large PBS 2};
+  \node[blue!40!cyan,above] at ($(SP PBS) + (0, 0.5)$) {\large PBS 2};
   \drawmirror{(SP IM2)}{0.9}{45}
   % SP AOM
-  \drawaom{(SP AOM)}{1}{0.5}{0}
+  \drawaom{(SP AOM)}{1}{0.4}{0}
   \node at (SP AOM) {\large SP AOM};
@@
   \drawwaveplate{(SP HWP)}{1}{0}
-  \node[blue!80!black,left] at ($(SP HWP) + (-0.9, 0)$) {\large $\lambda/2$};
+  \node[blue!80!black,left] at ($(SP HWP) + (-0.8, 0)$) {\large $\lambda/2$};
+
+  % SP AOM
+  \drawaom{(Servo AOM)}{1.2}{0.4}{0}
+  \node (Servo AOM Node) at (Servo AOM) {\large Servo AOM};
+
+  \draw[->,>=stealth,green!70!black,line width=0.8,dashed]
+  (Servo Pickoff Node) -| (1.7, 2) |- (Servo AOM Node);
+
+  \begin{scope}[shift={($(Fiber 2 In) + (0.5, 0.65)$)}]
+    \draw[line width=1.2]
+    (-0.5, -0.65) --
+    plot[domain={(-180 - 360):(180 + 360 + 90)},smooth,variable=\x,samples=2000]
+    ({0.5 * (-cos(\x)-2)}, {0.5 * sin(-\x) + 0.0003 * \x})
+    -- (Fiber 2 Out);
+    \node[right] at (-0.5, 0) {Fiber 2};
+  \end{scope}
+
+  \drawmirror[line width=2,gray!70!white]{(Pick Off)}{0.5}{105};
+  \drawmirror[line width=8,gray!60!white]{(Filter 2)}{0.5}{112};
+  \node[below] at ($(Filter 2) + (0, -0.45)$) {ASE Filter 2};
 \end{tikzpicture}

### 2020-11-25 imgs/fig-lifetime.tex
Rename figure files...

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes,
  arrows.meta
}
\pgfdeclareradialshading{glow}{\pgfpoint{0cm}{0cm}}{
  color(0mm)=(white);
  color(5mm)=(white);
  color(9mm)=(black);
  color(10mm)=(black)
}

\begin{tikzfadingfrompicture}[name=glow fading]
  \shade [shading=glow] (0,0) circle (1);
\end{tikzfadingfrompicture}

\ifpdf
% Ensure reproducible output
\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}
\fi

\begin{document}

\begin{tikzpicture}[scale=1.5391]
  \node at (0, 0) {\includegraphics[width=7.6958cm]{exp_data_norm_m_t.pdf}};
  \node at (-2.35, 1.7) {\footnotesize (\textbf{a})};

  \node at (0.77, 0.5) {$t_{\mathrm{hold}}$};
  \draw[->,>=stealth,line width=1] (0.4, 0.5) -- (0, 0.5);
  \draw[->,>=stealth,line width=1] (1.1, 0.5) -- (1.5, 0.5);
  \draw[orange!80!white,line width=1,fill=orange!50!white]
  (-0.3, 0.2) -- (-0.3, 0.8) -- node[above,orange!90!black] {\small $\pi$-pulse}
  (0, 0.8) -- (0, 0.2);
  \draw[orange!80!white,line width=1,fill=orange!50!white,shift={(1.8, 0)}]
  (-0.3, 0.2) -- (-0.3, 0.8) -- node[above,orange!90!black] {\small $\pi$-pulse}
  (0, 0.8) -- (0, 0.2);
  \draw[->,>=stealth,line width=1] (-0.5, 0.2) -- (2, 0.2);

  \node at (0, -3.9) {\includegraphics[width=7.6958cm]{exp_data_norm_a_t.pdf}};
  \node at (-2.35, 1.5 - 3.9) {\footnotesize (\textbf{b})};
  % strength = 2pi 29.3(17) mHz/mW^2.58
  \node at (0.85, -3.25) {\includegraphics[width=4.6175cm]{atomic_loss_scaling_inset.pdf}};
\end{tikzpicture}

\end{document}

### 2020-11-25 paper.tex
Tweak figure and include beampath
Rename figure files...
Copy caption from thesis

@@
 \begin{figure*}
-  \includegraphics[width=\textwidth]{fig1.pdf}
+  \includegraphics[width=\textwidth]{imgs/fig-theory.pdf}
   \caption{Optical creation of single molecule from single atoms in tweezer.
@@
 \end{figure*}
+
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{imgs/raman_spectroscopy_raman_beampath.pdf}
+  \caption{
+    Beampath for generating the frequency for Raman transition in the tweezer.
+    (Some mirrors and other optics used for alignment are not included.)
+    The two ASE filters before and after the fibers are also shown.
+    The red beam path is the $0$-th order of the double pass~(DP) AOM
+    which is used for the tweezer.
+    When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
+    (blue beam path) which generates the required frequency different to drive
+    the Raman transition. The two frequencies are recombined on the DP AOM.
+    The $0$-th order light is shifted by another single pass~(SP) AOM
+    running on a different frequency before recombining.
+    Without this AOM, the leak light from the DP AOM will be at the same frequency
+    as the $0$-th order light which can cause a significant power fluctuation
+    due to interference.
+    The experiment typically start with the SP AOM on and the DP AOM off.
+    When driving the Raman transition, the powers on both AOMs are ramped simultaneously
+    to achieve the desired power at both frequencies.
+    \label{f-beampath}
+  }
+\end{figure}
 
@@
 \begin{figure}[ht!]
-  \includegraphics[width=0.48\textwidth]{fig2.pdf}
+  \includegraphics[width=0.48\textwidth]{imgs/fig-raman.pdf}
   \caption{
@@
 \begin{figure}[t!]
-  \includegraphics[width=0.48\textwidth]{fig3.pdf}
+  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
   \caption{
@@
 \begin{figure*}
-  \includegraphics[width=\textwidth]{fig4.pdf}
+  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
   \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.

### 2020-11-25 paper.tex
Add - for empty entries in the table
Consistent case

@@
     & Experiment & Theory \\ \hline
-    $\Omega_R $ & & $2\pi \times 15.3~\mathrm{kHz}$ \\
-    $\Gamma_S$ & & $ 2\pi \times 533~\mathrm{Hz}$ \\
+    $\Omega_R $ & $-$ & $2\pi \times 15.3~\mathrm{kHz}$ \\
+    $\Gamma_s$ & $-$ & $ 2\pi \times 533~\mathrm{Hz}$ \\
     $ \Omega_m $ & $2\pi \times 140.06(8) ~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
@@
   \end{tabular}
-  \caption{Comparison between theory and experiment of $\Omega_R,\Gamma_S, \Omega_m, \Omega_a$.
-$\Omega_R$ and $ \Gamma_S $ are reported at $145~\mathrm{GHz}$ detuned from the $v' = 0$ state.
+  \caption{Comparison between theory and experiment of $\Omega_R,\Gamma_s, \Omega_m, \Omega_a$.
+$\Omega_R$ and $ \Gamma_s $ are reported at $145~\mathrm{GHz}$ detuned from the $v' = 0$ state.
 All numbers are reported at $3.75$ mW tweezer power.

### 2020-11-25 plot_raman_full.jl
Update Full Raman theory plot for SM

@@ -1,56 +1,0 @@
-#!/usr/bin/julia
-
-push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
-
-import NaCsCalc.Format: Unc, Sci
-using NaCsCalc
-using NaCsCalc.Utils: interactive
-using NaCsData
-using NaCsData.Fitting: fit_data, fit_survival
-using NaCsPlot
-using PyPlot
-# using DataStructures
-# using LsqFit
-using LibArchive
-
-using DelimitedFiles
-
-# const fname = joinpath(@__DIR__, "../damop-2020/20MHz_linewidth_c3SigmaOnly_3322_80kHzConfinement.csv.zst")
-const fname = joinpath(@__DIR__, "data/50MHz_linewidth_8TotalExcitedStates_3322_80kHzConfinement_3.75mWPowerAtAtom.csv.zst")
-const data = LibArchive.Reader(fname) do reader
-    LibArchive.support_format_raw(reader)
-    LibArchive.support_filter_all(reader)
-    LibArchive.next_header(reader)
-    readdlm(reader, ',', skipstart=1)
-end
-const prefix = joinpath(@__DIR__, "imgs", "raman_theory_full")
-
-figure(figsize=[13.8, 4.8])
-l1 = plot(data[:, 1] ./ 1000, abs.(data[:, 2] ./ 2π / 1000), "C0",
-          label="\$\\Omega_{R}\$")
-l2 = plot(data[:, 1] ./ 1000, abs.(data[:, 4] ./ 2π / 1000), "C1",
-          label="\$\\Gamma_{s}\$")
-# plot(data[:, 1] ./ 1000, abs.(data[:, 2] ./ data[:, 4]), "C2")
-# es = [2.8863, 2.9026, 2.9184, 2.9339, 2.9492, 2.9643, 2.9792, 2.9939, 3.0084, 3.0227,
-#       3.0369, 3.0510, 3.0649, 3.0787, 3.0925, 3.1062, 3.1198, 3.1334, 3.1469, 3.1603,
-#       3.1736, 3.1868, 3.1999, 3.2129, 3.2258, 3.2385, 3.2511, 3.2635, 3.2757, 3.2876,
-#       3.2993, 3.3106, 3.3215, 3.3322, 3.3425, 3.3525, 3.3621, 3.3714, 3.3803, 3.3889,
[…]

### 2020-11-25 scripts/plot_raman_full.jl

@@ -1,0 +1,59 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+# using DataStructures
+# using LsqFit
+using LibArchive
+
+using DelimitedFiles
+
+read_zst_csv(fname) = LibArchive.Reader(fname) do reader
+    LibArchive.support_format_raw(reader)
+    LibArchive.support_filter_all(reader)
+    LibArchive.next_header(reader)
+    readdlm(reader, ',', skipstart=1)
+end
+
+# const fname = joinpath(@__DIR__, "../../damop-2020/20MHz_linewidth_c3SigmaOnly_3322_80kHzConfinement.csv.zst")
+const fname = joinpath(@__DIR__, "../data/50MHz_linewidth_8TotalExcitedStates_3322_80kHzConfinement_3.75mWPowerAtAtom.csv.zst")
+const fname2 = joinpath(@__DIR__, "../data/50MHz_linewidth_8TotalExcitedStates_3322_80kHzConfinement_3.75mWPowerAtAtom_ThresholdContribution.csv.zst")
+const data = read_zst_csv(fname)
+const data2 = read_zst_csv(fname2)
+const prefix = joinpath(@__DIR__, "../imgs", "raman_theory_full")
+
+figure(figsize=[13.8, 4.8])
+plot(data[:, 1] ./ 1000, abs.(data[:, 2] ./ 2π / 1000), "C0", label="\$\\Omega_{R}\$")
+plot(data2[:, 1] ./ 1000, abs.(data2[:, 4] ./ 2π / 1000), "r", linewidth=4, alpha=0.7)
+plot(data[:, 1] ./ 1000, abs.(data[:, 4] ./ 2π / 1000), "C1", label="\$\\Gamma_{s}\$")
+# plot(data[:, 1] ./ 1000, abs.(data[:, 2] ./ data[:, 4]), "C2")
[…]

### 2020-11-25 paper.tex
Update captions and include fitting parameters

@@
     as intermediate state for the Raman transition.
-    The deeply bound excited state (upper half $v'=0$)
+    The deeply bound excited state (blue lines $v'=0$)
     has a smaller Raman Rabi frequency ($\Omega_{R}$)
-    compared to the weakly bound excited state (lower half $v'=63$) at a given detuning.
+    compared to the weakly bound excited state (orange lines $v'=40$) at a most detuning.
     However, the scattering rate ($\Gamma_{s}$) is also much lower,
@@
     measured from the Raman transition data.
+    Inset: pulse sequence for the lifetime measurement.
     (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
@@
     This is used to improve the fitting of the Raman transfer data.
-    Inset: Atomic scattering rate scales as $P_\textrm{tweezer}^{2.58}$ on a log-log scale;
+    Inset: Atomic scattering rate scales as
+    $P_\textrm{tweezer}^{2.58}\cdot\!2\pi\!\cdot29.3(17)~\mathrm{mHz/mW^{2.58}}$ on a log-log scale;
     this is consistent with a two-photon scattering process.
@@
     The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6~\mathrm{GHz}$.
-    (a) The light shift of the Raman resonance scales as $P$
-    and follows $1/\Delta$ with an offset, where $ P$ is the power in the tweezer.
-    The fit also includes a small term that is proportional to $P^2$
-    which is caused by the effective magnetic field generated by the tweezer, which is perpendicular to the real magnetic field.
-    (b) Raman Rabi frequency ($\Omega_R$) scales as $P^{1.29}$
-    and follows $1/\Delta$ with an offset.
-    (c) Tweezer power dependency of light shift (up) and Raman Rabi frequency (down)
+    (a) The light shift of the Raman resonance fitted to
+    $(f_{R0}+a\cdot P+b\cdot P^2)+c\cdot P/\Delta$
+    where $P$ is the power in the tweezer,
+    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweer}}$ is the detuning from
+    the PA resonance frequency $f_{\mathrm{PA}0}$.
+    The small $P^2$ term included in the fit is caused by the effective magnetic field
+    generated by the tweezer, which is perpendicular to the real magnetic field.
+    The fitting results are $f_{\mathrm{PA}0}=288711~\mathrm{GHz}$,
+    $f_{R0}=770.20052(2)~\mathrm{MHz}$, $a=8.78(7)~\mathrm{kHz/mW}$,
+    $b=-3.186(9)~\mathrm{kHz/mW^2}$
+    and $c=16.43(2)~\mathrm{MHz\cdot GHz/mW}$.
+    (b) Raman Rabi frequency ($\Omega_R$) fitted to $(a + b/\Delta)\cdot P^{1.29}$.
+    The detuning is calculated using the PA frequency fitted in (a).
+    The fitting results are $a=-2\pi\cdot\!0.41(2)~\mathrm{kHz/mW^{1.29}}$
+    $b=4\pi^2\cdot\!167(2)~\mathrm{kHz\cdot\!GHz/mW^{1.29}}$.
+    (c) Tweezer power dependency of light shift (top) and Raman Rabi frequency (bottom)
     on a log-log plot showing the power-law scaling.

### 2020-11-25 sm.tex
Update SM caption

@@
   \includegraphics[width=\textwidth]{imgs/raman_theory_full.pdf}
-  \caption{ Full calculation of the Raman Rabi frequency and scattering rate as a function of the single-photon frequency including all vibrational states of $ \mathrm{c^3\Sigma^+(\Omega = 1)}$ and the atomic continuum.
-The second frequency in the Raman transition is offset by about $770~\mathrm{MHz}$ and resonant with the two photon transition.
-The assumed excited-state linewidth for all molecular lines is $50~\text{MHz} $.
+  \caption{Full calculation of the Raman Rabi frequency and scattering rate
+    as a function of the single-photon frequency
+    including all vibrational states of $ \mathrm{c^3\Sigma^+(\Omega = 1)}$
+    and the atomic continuum.
+    The second frequency in the Raman transition is offset by about $770~\mathrm{MHz}$
+    and resonant with the two photon transition.
+    The assumed excited-state linewidth for all molecular lines is $50~\text{MHz}$.
+    The thick red line shows the contribution that comes only from the near-threshold states.
     \label{f-sm}}

### 2020-11-25 paper.tex
Move figures up a little
Update experimental numbers

@@
 
+\begin{figure}[t!]
+  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
+  \caption{
+    (a) Direct measurement of molecule lifetime in a trap of depth $3.75~\mathrm{mW}$.
+    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
+    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
+    measured from the Raman transition data.
+    Inset: pulse sequence for the lifetime measurement.
+    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
+    in a trap of depth $3.75~\mathrm{mW}$ caused by off-resonance photoassociation.
+    This is used to improve the fitting of the Raman transfer data.
+    Inset: Atomic scattering rate scales as
+    $P_\textrm{tweezer}^{2.58}\times\!2\pi\!\times29.3(17)~\mathrm{mHz/mW^{2.58}}$ on a log-log scale;
+    this is consistent with a two-photon scattering process.
+    We have not measured a clear dependency of the loss rate on the tweezer detuning.
+    \label{f-lifetime}}
+\end{figure}
+
 We choose the tweezer frequency to be $288560~\mathrm{GHz}$
@@
 
-\begin{figure}[t!]
-  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
-  \caption{
-    (a) Direct measurement of molecule lifetime in a trap of depth $3.75~\mathrm{mW}$.
-    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
-    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
-    measured from the Raman transition data.
-    Inset: pulse sequence for the lifetime measurement.
-    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
-    in a trap of depth $3.75~\mathrm{mW}$ caused by off-resonance photoassociation.
-    This is used to improve the fitting of the Raman transfer data.
-    Inset: Atomic scattering rate scales as
-    $P_\textrm{tweezer}^{2.58}\cdot\!2\pi\!\cdot29.3(17)~\mathrm{mHz/mW^{2.58}}$ on a log-log scale;
-    this is consistent with a two-photon scattering process.
-    We have not measured a clear dependency of the loss rate on the tweezer detuning.
-    \label{f-lifetime}}
-\end{figure}
-
 In order to verify whether any one of these sources are the origin of the reduced transfer efficiency,
@@
 or Raman Rabi frequency comes from the $ v' = 0$ intermediate state.
-
-First we look at the change in resonance frequency to determine $\Omega_m$.
-We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
-When we vary the tweezer frequency around the $v'=0$ intermediate state,
-we can further observe a $1/\Delta$ component
-and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a.
-The background is caused by coupling to other excited states that are further away in energy.
-The $1/\Delta$ component, however, is due to the coupling between the molecular state
-and the $v'=0$ intermediate state.
-From this measurement, we can extract a $\Omega_m$ of
-$2\pi\times72.32(4) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
-% or
-% $2\pi\times140.06(8) ~\mathrm{MHz}$ for the $3.75~\mathrm{mW}$ tweezer power used above.
-This number is close to the value of
-$2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
 
@@
     The detuning is calculated using the PA frequency fitted in (a).
-    The fitting results are $a=-2\pi\cdot\!0.41(2)~\mathrm{kHz/mW^{1.29}}$
-    $b=4\pi^2\cdot\!167(2)~\mathrm{kHz\cdot\!GHz/mW^{1.29}}$.
+    The fitting results are $a=-2\pi\times\!0.41(2)~\mathrm{kHz/mW^{1.29}}$
+    $b=4\pi^2\times\!167(2)~\mathrm{kHz\cdot\!GHz/mW^{1.29}}$.
     (c) Tweezer power dependency of light shift (top) and Raman Rabi frequency (bottom)
@@
 \end{figure*}
+
+First we look at the change in resonance frequency to determine $\Omega_m$.
+We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
+When we vary the tweezer frequency around the $v'=0$ intermediate state,
+we can further observe a $1/\Delta$ component
+and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a.
+The background is caused by coupling to other excited states that are further away in energy.
+The $1/\Delta$ component, however, is due to the coupling between the molecular state
+and the $v'=0$ intermediate state.
+From this measurement, we can extract a $\Omega_m$ of
+$2\pi\times181.3(1)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
+This number is within $50~\mathrm{\%}$
+of the value $2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory.
 
@@
 The $v'=0$ component of the Raman Rabi frequency at our detuning is
-$2\pi\times1.02(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
-or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
-Together with the $\Omega_m$ measured above, the Rabi frequency, $ \Omega_a $, is
-$2\pi \times 12.1(3)~\mathrm{MHz}$.
-This gives a matrix-element ratio of $11.6(3)$,
-which is in fact better than the theory prediction of $23.8$ (Table \ref{tab:rabi_freqs}).
+$2\pi\times1.15(1)~\mathrm{kHz\cdot mW^{-1.29}}$,
+or $2\pi \times 6.34(8)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
+Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
+$2\pi\times 5.23(6)~\mathrm{MHz}$.
+This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $67.1(8)$,
+which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
 Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
@@
     $\Gamma_s$ & $-$ & $ 2\pi \times 533~\mathrm{Hz}$ \\
-    $ \Omega_m $ & $2\pi \times 140.06(8) ~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
-    $\Omega_a$ & $2\pi \times 12.1(3) ~\mathrm{MHz}$ & $2\pi \times 7.37 ~\mathrm{MHz}$ \\
-    $\Omega_m/\Omega_a$ & $11.6(3)$ & $ 77.7$
+    $\Omega_m$ & $2\pi \times 351.1(2)~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
+    $\Omega_a$ & $2\pi \times 5.23(6)~\mathrm{MHz}$ & $2\pi \times 7.37 ~\mathrm{MHz}$ \\
+    $\Omega_m/\Omega_a$ & $67.1(8)$ & $77.7$
   \end{tabular}

### 2020-11-25 paper.tex
Clarify relation between lifetime and scattering rate

@@
   Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
-So far, molecular association has generally been achieved by magnetoassociation using a magnetic Feshbach scattering resonance.
+So far, molecular association has generally been achieved by magnetoassociation
+using a magnetic Feshbach scattering resonance.
 Exceptions include Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states
@@
 The efficiency of the transfer is lower than expected
-because we found the ratio of the molecular scattering rate to the Rabi frequency
-is 10 times larger than predicted. If this discrepancy arises from the $v'=0$ excited state,
+because we found the ratio of the molecular scattering rate~(i.e. inverse of lifetime)
+to the Rabi frequency is 10 times larger than predicted.
+If this discrepancy arises from the $v'=0$ excited state,
 it can be due either to a high ratio $\Omega_m / \Omega_a$ or to a large $\Gamma_e$.
@@
 
-The scattering rate of the molecule also depends on the tweezer power and detuning, and becomes smaller when the power is lowered.
+The scattering rate of the molecule also depends on the tweezer power and detuning,
+and becomes smaller when the power is lowered.
 At $0.75~\mathrm{mW}$ tweezer power, we observe a molecule lifetime as long as $1~\mathrm{ms}$.

### 2020-11-25 paper.tex
Fix caption

@@
     Compared to other spin states with weaker interaction,
-    the wavefunction at short distance ($R<100\ \text{\AA}$, left of the dotted line)
+    the wavefunction at short distance ($R<100\ \text{\AA}$, left of the dashed line)
     is significantly enhanced.

### 2020-11-25 scripts/plot_atomic_loss_scaling.jl
Move scripts, cdot -> times

@@ -1,6 +1,6 @@
 #!/usr/bin/julia
 
-push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
 
 import NaCsCalc.Format: Unc, Sci
 using NaCsCalc
@@ -25,7 +25,7 @@ fit_gamma_a2 = fit_data(gen_power_model(2.58), rates[:, 1], rates[:, 2], rates[:
                         [1.0]; plot_lo=2.7)
 @show fit_gamma_a2.uncs
 
-const prefix = joinpath(@__DIR__, "imgs", "atomic_loss_scaling")
+const prefix = joinpath(@__DIR__, "../imgs", "atomic_loss_scaling")
 
 # figure()
 # errorbar(rates[:, 1], rates[:, 2], rates[:, 3], fmt="C0o")
@@ -39,7 +39,7 @@ const prefix = joinpath(@__DIR__, "imgs", "atomic_loss_scaling")
 # ax.xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 # ax.set_xticks(3:16, minor=true)
 # xlabel("Tweezer Power (mW)")
-# ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$")
+# ylabel("\$\\Gamma_{atom} (2\\pi\\times \\mathrm{Hz})\$")
 # NaCsPlot.maybe_save("$(prefix)")
 
 figure(figsize=[4.8, 3.6] .* 1.08792)
@@ -58,7 +58,7 @@ yticks([1, 3, 10, 30], ["1", "3", "10", "30"])
 ax.xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 ax.set_xticks(0.7:0.1:4, minor=true)
 xlabel("Tweezer Power (mW)", fontsize=17)
-ylabel("\$\\Gamma_{atom} (2\\pi\\cdot \\mathrm{Hz})\$", fontsize=17)
+ylabel("\$\\Gamma_{atom} (2\\pi\\times \\mathrm{Hz})\$", fontsize=17)
 tight_layout()
 NaCsPlot.maybe_save("$(prefix)_inset")
 

### 2020-11-25 scripts/plot_exp_data.jl

@@ -1,8 +1,8 @@
 #!/usr/bin/julia
 
-push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
 
-include("../../experiments/nacs_202003/molecular_raman_model.jl")
+include("../../../experiments/nacs_202003/molecular_raman_model.jl")
 
 import NaCsCalc.Format: Unc, Sci
 using NaCsCalc
@@ -18,7 +18,7 @@ const inames = ["nacs_202010/data/data_20201001_203322.mat",
                 "nacs_202010/data/data_20201006_190214.mat",
                 "nacs_202010/data/data_20201002_085901.mat",
                 "nacs_202010/data/data_20201003_102015.mat"]
-const datas = [NaCsData.load_striped_mat(joinpath(@__DIR__, "../../experiments/", iname)) for iname in inames]
+const datas = [NaCsData.load_striped_mat(joinpath(@__DIR__, "../../../experiments/", iname)) for iname in inames]
 const maxcnts = [typemax(Int),
                  typemax(Int),
                  typemax(Int),
@@ -76,7 +76,7 @@ const data_fit = [NaCsData.map_params((i, v) -> (1, 570.4, v, 1), data_nacs_00);
                   NaCsData.map_params((i, v) -> (5, v, 0.0, 6), data_pa_m);
                   NaCsData.map_params((i, v) -> (6, v, 0.0, 7), data_nacs_m)]
 
-const prefix = joinpath(@__DIR__, "imgs", "exp_data")
+const prefix = joinpath(@__DIR__, "../imgs", "exp_data")
 
 function model_exp(x, p)
     if length(p) > 2

### 2020-11-25 scripts/plot_fcf.jl

@@ -1,6 +1,6 @@
 #!/usr/bin/julia
 
-push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
 
 import NaCsCalc.Format: Unc, Sci
 using NaCsCalc
@@ -15,9 +15,9 @@ using LibArchive
 
 using DelimitedFiles
 
-const fname = joinpath(@__DIR__, "data/FCFtoc3Sigma.csv")
+const fname = joinpath(@__DIR__, "../data/FCFtoc3Sigma.csv")
 const data = readdlm(fname, ',', skipstart=1)
-const prefix = joinpath(@__DIR__, "imgs", "fcf")
+const prefix = joinpath(@__DIR__, "../imgs", "fcf")
 
 figure(figsize=[13.8, 4.8])
 plot(data, "C0o-")

### 2020-11-25 scripts/plot_raman.jl

@@ -1,6 +1,6 @@
 #!/usr/bin/julia
 
-push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
 
 import NaCsCalc.Format: Unc, Sci
 using NaCsCalc
@@ -15,15 +15,15 @@ using LibArchive
 
 using DelimitedFiles
 
-# const fname = joinpath(@__DIR__, "../damop-2020/20MHz_linewidth_c3SigmaOnly_3322_80kHzConfinement.csv.zst")
-const fname = joinpath(@__DIR__, "data/50MHz_linewidth_8TotalExcitedStates_3322_80kHzConfinement_3.75mWPowerAtAtom.csv.zst")
+# const fname = joinpath(@__DIR__, "../../damop-2020/20MHz_linewidth_c3SigmaOnly_3322_80kHzConfinement.csv.zst")
+const fname = joinpath(@__DIR__, "../data/50MHz_linewidth_8TotalExcitedStates_3322_80kHzConfinement_3.75mWPowerAtAtom.csv.zst")
 const data = LibArchive.Reader(fname) do reader
     LibArchive.support_format_raw(reader)
     LibArchive.support_filter_all(reader)
     LibArchive.next_header(reader)
     readdlm(reader, ',', skipstart=1)
 end
-const prefix = joinpath(@__DIR__, "imgs", "raman")
+const prefix = joinpath(@__DIR__, "../imgs", "raman")
 
 fig = figure(figsize=[1.11, 1.5] * 4.8)
 
@@ -32,7 +32,7 @@ plot(data[:, 1] .- 339724.57, abs.(data[:, 2] ./ 2π / 1000), "C1",
      label="\$v'=40\$")
 plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ 2π / 1000), "C0",
      label="\$v'=0\$")
-ylabel("\$\\Omega_{R}~(2\\pi\\!\\cdot\\!\\mathrm{kHz})\$")
+ylabel("\$\\Omega_{R}~(2\\pi\\!\\times\\!\\mathrm{kHz})\$")
 xlim([-300, 300])
 ylim([6, 20000])
 yscale("log")
[…]

### 2020-11-25 scripts/plot_scaling.jl

@@ -1,6 +1,6 @@
 #!/usr/bin/julia
 
-push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
 
 import NaCsCalc.Format: Unc, Sci
 using NaCsCalc
@@ -193,7 +193,7 @@ const data_rabi = gen_data(rabi_freqs)
 const fit_rabi = fit_data(model_rabi, data_rabi.x, data_rabi.y, [0.1, 0.1], plotx=false)
 @show fit_rabi.uncs
 
-const prefix = joinpath(@__DIR__, "imgs", "scaling")
+const prefix = joinpath(@__DIR__, "../imgs", "scaling")
 
 const powers_plot = [15, 6, 3]
 
@@ -243,7 +243,7 @@ yticks([0, 2, 4, 6, 8])
 # xticks([-200, -160, -120, -80])
 ylim([0, 9.7])
 xlabel("\$1 / \\Delta~(\\mathrm{THz^{-1}})\$")
-ylabel("\$\\Omega_{R}~(2\\pi\\cdot \\mathrm{kHz})\$")
+ylabel("\$\\Omega_{R}~(\\mathrm{2\\pi\\times kHz})\$")
 NaCsPlot.maybe_save("$(prefix)_rabi")
 
 const freq = 560
@@ -292,7 +292,7 @@ grid()
 # ax2.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 # ax2.set_xticks(0.7:0.1:4, minor=true)
 xlabel("Tweezer Power (mW)")
-ylabel("\$\\Omega_{R} (2\\pi\\cdot \\mathrm{kHz})\$")
+ylabel("\$\\Omega_{R} (\\mathrm{2\\pi\\times kHz})\$")
 xlim([0.625, 4.25])
 ylim([0.42, 4.2])
 NaCsPlot.maybe_save("$(prefix)_560")

### 2020-11-25 scripts/plot_wavefunction.jl

@@ -1,6 +1,6 @@
 #!/usr/bin/julia
 
-push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
 
 import NaCsCalc.Format: Unc, Sci
 using NaCsCalc
@@ -24,14 +24,14 @@ function read_csv_compressed(fname, args...; kwargs...)
     end
 end
 
-const fname31 = joinpath(@__DIR__, "../2020-postdoc/3311boundstate.csv.zst")
-const fname32 = joinpath(@__DIR__, "../2020-postdoc/3322boundstate.csv.zst")
-const fname42 = joinpath(@__DIR__, "../2020-postdoc/4422boundstate.csv.zst")
+const fname31 = joinpath(@__DIR__, "../../2020-postdoc/3311boundstate.csv.zst")
+const fname32 = joinpath(@__DIR__, "../../2020-postdoc/3322boundstate.csv.zst")
+const fname42 = joinpath(@__DIR__, "../../2020-postdoc/4422boundstate.csv.zst")
 const data31 = read_csv_compressed(fname31, ',', Float64)
 const data32 = read_csv_compressed(fname32, ',', Float64)
 const data42 = read_csv_compressed(fname42, ',', Float64)
 
-const prefix = joinpath(@__DIR__, "imgs", "wavefunction")
+const prefix = joinpath(@__DIR__, "../imgs", "wavefunction")
 
 figure()
 plot(data42[:, 1], data42[:, 2] .* 2e6, "C2", label="Na(2,2) Cs(4,4)")

### 2020-11-30 paper.tex
Remove out of date note about detuning
Non sense... I don't care anymore

@@
   we achieve an optical transfer efficiency of $69\mathrm{\%}$.
-  The molecules have a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.83(2)~\mathrm{G}$
+  The molecules have a binding energy of $770.1969(2)~\mathrm{MHz}$ at $8.83(2)~\mathrm{G}$
   and are created with higher than $60\mathrm{\%}$ probability in the motional ground state.
@@
 We choose the tweezer frequency to be $288560~\mathrm{GHz}$
-which is far detuned (by $\approx\!145~\mathrm{GHz}$) from the $v' = 0$ line.
+which is far detuned (by $\approx\!151~\mathrm{GHz}$) from the $v' = 0$ line.
 Guided by the coupled-channel calculations,
@@
   \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
-    The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6~\mathrm{GHz}$.
-    (a) The light shift of the Raman resonance fitted to
-    $(f_{R0}+a\cdot P+b\cdot P^2)+c\cdot P/\Delta$
-    where $P$ is the power in the tweezer,
+    (a) The light shift of the Raman resonance fitted to$a(P)+b(P)/\Delta$, where
+    $a(P)$ and $b(P)=(\Omega_a^2-\Omega_m^2)/2$
+    are tweezer power dependent background and $v'=0$ contribution
+    to the light shift,
     $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweer}}$ is the detuning from
     the PA resonance frequency $f_{\mathrm{PA}0}$.
-    The small $P^2$ term included in the fit is caused by the effective magnetic field
-    generated by the tweezer, which is perpendicular to the real magnetic field.
-    The fitting results are $f_{\mathrm{PA}0}=288711~\mathrm{GHz}$,
-    $f_{R0}=770.20052(2)~\mathrm{MHz}$, $a=8.78(7)~\mathrm{kHz/mW}$,
-    $b=-3.186(9)~\mathrm{kHz/mW^2}$
-    and $c=16.43(2)~\mathrm{MHz\cdot GHz/mW}$.
-    (b) Raman Rabi frequency ($\Omega_R$) fitted to $(a + b/\Delta)\cdot P^{1.29}$.
+    The $a(P)$s are fitted to a model including linear and small quadratic light shift
+    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
+    at zero tweezer power to be $f_{R0}=770.1969(2)~\mathrm{MHz}$.
+    (b) Raman Rabi frequency ($\Omega_R$) fitted to$c(P)+d(P)/\Delta$, where
+    $c(P)$ and $d(P)=\Omega_a\Omega_m/2$
+    are tweezer power dependent background and $v'=0$ contribution.
     The detuning is calculated using the PA frequency fitted in (a).
-    The fitting results are $a=-2\pi\times\!0.41(2)~\mathrm{kHz/mW^{1.29}}$
-    $b=4\pi^2\times\!167(2)~\mathrm{kHz\cdot\!GHz/mW^{1.29}}$.
-    (c) Tweezer power dependency of light shift (top) and Raman Rabi frequency (bottom)
-    on a log-log plot showing the power-law scaling.
+    The $c(P)$s and $d(P)$s are proportional to $P^{1.29}$
+    and the fit gives $c(P)/P^{1.29}=-2\pi\times0.41(2)~\mathrm{kHz/mW^{1.29}}$
+    and $d(P)/P^{1.29}=-4\pi^2\times167(2)~\mathrm{kHz/mW^{1.29}}$.
+    The fitting results for (a) and (b) are shown in table~\ref{tab:f-det:fit}.
+    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
+    $b(P)$ and $d(P)$ on a log-log scale showing the $P^{0.5}$ scaling of $\Omega_m$ and
+    the $P^{0.79}$ scaling of $\Omega_a$.
     \label{f-det}}
 \end{figure*}
+\begin{table}[ht]
+  \centering
+  \begin{tabular}{|c|c|}
+    $f_{\mathrm{PA}0}$&$288711.8~\mathrm{GHz}$\\\hline
+    $a(0.75~\mathrm{mW})$&$770.20452(6)~\mathrm{MHz}$\\
+    $b(0.75~\mathrm{mW})$&$-12.46(2)~\mathrm{MHz\cdot GHz}$\\
+    $a(1.5~\mathrm{mW})$&$770.2081(1)~\mathrm{MHz}$\\
+    $b(1.5~\mathrm{mW})$&$-24.44(3)~\mathrm{MHz\cdot GHz}$\\
+    $a(3.75~\mathrm{mW})$&$770.1943(3)~\mathrm{MHz}$\\
+    $b(3.75~\mathrm{mW})$&$-60.66(8)~\mathrm{MHz\cdot GHz}$\\\hline
+    $c(0.75~\mathrm{mW})$&$-2\pi\times0.29(2)~\mathrm{kHz}$\\
+    $d(0.75~\mathrm{mW})$&$-4\pi^2\times115(4)~\mathrm{kHz\cdot GHz}$\\
+    $c(1.5~\mathrm{mW})$&$-2\pi\times0.63(4)~\mathrm{kHz}$\\
+    $d(1.5~\mathrm{mW})$&$-4\pi^2\times275(6)~\mathrm{kHz\cdot GHz}$\\
+    $c(3.75~\mathrm{mW})$&$-2\pi\times2.4(2)~\mathrm{kHz}$\\
+    $d(3.75~\mathrm{mW})$&$-4\pi^2\times0.95(3)~\mathrm{MHz\cdot GHz}$\\
+  \end{tabular}
+  \caption{Fitting results for Fig.~\ref{f-det}(a,b).
+    \label{tab:f-det:fit}}
+\end{table}
 
@@
 From this measurement, we can extract a $\Omega_m$ of
-$2\pi\times181.3(1)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
-This number is within $50~\mathrm{\%}$
+$2\pi\times180.87(7)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
+This number is within $40~\mathrm{\%}$
 of the value $2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory.
@@
 The $v'=0$ component of the Raman Rabi frequency at our detuning is
-$2\pi\times1.15(1)~\mathrm{kHz\cdot mW^{-1.29}}$,
-or $2\pi \times 6.34(8)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
+$2\pi\times1.10(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
+or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
 Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
-$2\pi\times 5.23(6)~\mathrm{MHz}$.
-This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $67.1(8)$,
+$2\pi\times 5.5(2)~\mathrm{MHz}$.
+This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $63(3)$,
 which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
@@
     $\Gamma_s$ & $-$ & $ 2\pi \times 533~\mathrm{Hz}$ \\
-    $\Omega_m$ & $2\pi \times 351.1(2)~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
-    $\Omega_a$ & $2\pi \times 5.23(6)~\mathrm{MHz}$ & $2\pi \times 7.37 ~\mathrm{MHz}$ \\
-    $\Omega_m/\Omega_a$ & $67.1(8)$ & $77.7$
+    $\Omega_m$ & $2\pi \times 348.3(3)~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
+    $\Omega_a$ & $2\pi \times 5.5(2)~\mathrm{MHz}$ & $2\pi \times 7.37 ~\mathrm{MHz}$ \\
+    $\Omega_m/\Omega_a$ & $63(3)$ & $77.7$
   \end{tabular}
   \caption{Comparison between theory and experiment of $\Omega_R,\Gamma_s, \Omega_m, \Omega_a$.
-$\Omega_R$ and $ \Gamma_s $ are reported at $145~\mathrm{GHz}$ detuned from the $v' = 0$ state.
+$\Omega_R$ and $ \Gamma_s $ are reported at $151~\mathrm{GHz}$ detuned from the $v' = 0$ state.
 All numbers are reported at $3.75$ mW tweezer power.

### 2020-11-30 scripts/plot_scaling.jl

@@ -12,111 +12,117 @@ using PyPlot
 using DataStructures
 using LsqFit
 
-const res_freqs = [668.35 21 772.1367 0.0082
-                   668.35 21 772.1376 0.0049
-                   668.35 21 772.1172 0.0048
-                   668.35 18 771.924 0.033
-                   668.35 12 771.323 0.050
+# For anyone that see this script, the analysis done here makes no sense
+# See the version as of 8dc37f814f6978f9fe76c549cc75dfe4196fb6b9
+# for how this should be done correctly.
 
-                   560 15 770.59417 0.00013
-                   560 6 770.369081 0.000037
-                   560 3 770.287276 0.000015
+const res_freqs = [
+    # 668.35 21 772.1367 0.0082
+    # 668.35 21 772.1376 0.0049
+    # 668.35 21 772.1172 0.0048
+    # 668.35 18 771.924 0.033
+    668.35 12 771.323 0.050
 
-                   565 15 770.61656 0.00021
-                   565 6 770.378274 0.000080
-                   565 3 770.291891 0.000038
+    560 15 770.59417 0.00013
+    560 6 770.369081 0.000037
+    560 3 770.287276 0.000015
 
-                   555 15 770.57744 0.00013
-                   555 6 770.362165 0.000043
-                   555 3 770.283665 0.000017
+    565 15 770.61656 0.00021
+    565 6 770.378274 0.000080
+    565 3 770.291891 0.000038
 
-                   503 15 770.483553 0.000049
-                   503 12 770.43248 0.00011
-                   503 9 770.379505 0.000028
-                   503 6 770.324463 0.000019
-                   503 3 770.2648307 0.0000084
+    555 15 770.57744 0.00013
+    555 6 770.362165 0.000043
+    555 3 770.283665 0.000017
 
-                   492 15 770.47571 0.00010
-                   492 12 770.42599 0.00032
-                   492 9 770.375007 0.000069
-                   492 6 770.321355 0.000037
-                   492 3 770.263402 0.000028
+    503 15 770.483553 0.000049
+    503 12 770.43248 0.00011
+    503 9 770.379505 0.000028
+    503 6 770.324463 0.000019
+    503 3 770.2648307 0.0000084
 
-                   510 15 770.50117 0.00083
[…]

### 2020-11-30 paper.tex
Update on Overleaf.

@@
 \begin{acknowledgments}
-  We would like to thank Rosario Gonzalez-Ferez, Bo Gao, and Paul Julienne \textcolor{red}{acknowledge getting TDM} for discussion.
+  We would like to thank Rosario Gonzalez-Ferez, Olivier Dulieu, Bo Gao, and Paul Julienne \textcolor{red}{acknowledge getting TDM} for discussion.
 This work is supported by the NSF~(PHY-1806595), the AFOSR~(FA9550-19-1-0089), ARO DURIP (W911NF1810194) and the Arnold and Mabel Beckman foundation.

### 2020-12-01 paper.tex
Whatever

--- 2020-11-30 paper.tex
@@
   \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
-    (a) The light shift of the Raman resonance fitted to$a(P)+b(P)/\Delta$, where
-    $a(P)$ and $b(P)=(\Omega_a^2-\Omega_m^2)/2$
+    (a) The light shift of the Raman resonance fitted to$a_P+b_P/\Delta$, where
+    $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
     are tweezer power dependent background and $v'=0$ contribution
@@
     the PA resonance frequency $f_{\mathrm{PA}0}$.
-    The $a(P)$s are fitted to a model including linear and small quadratic light shift
+    The $a_P$s are fitted to a model including linear and small quadratic light shift
     \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
     at zero tweezer power to be $f_{R0}=770.1969(2)~\mathrm{MHz}$.
-    (b) Raman Rabi frequency ($\Omega_R$) fitted to$c(P)+d(P)/\Delta$, where
-    $c(P)$ and $d(P)=\Omega_a\Omega_m/2$
+    (b) Raman Rabi frequency ($\Omega_R$) fitted to$c_P+d_P/\Delta$, where
+    $c_P$ and $d_P=\Omega_a\Omega_m/2$
     are tweezer power dependent background and $v'=0$ contribution.
     The detuning is calculated using the PA frequency fitted in (a).
-    The $c(P)$s and $d(P)$s are proportional to $P^{1.29}$
-    and the fit gives $c(P)/P^{1.29}=-2\pi\times0.41(2)~\mathrm{kHz/mW^{1.29}}$
-    and $d(P)/P^{1.29}=-4\pi^2\times167(2)~\mathrm{kHz/mW^{1.29}}$.
+    The $c_P$s and $d_P$s are proportional to $P^{1.29}$
+    and the fit gives $c_P/P^{1.29}=-2\pi\times0.41(2)~\mathrm{kHz/mW^{1.29}}$
+    and $d_P/P^{1.29}=-4\pi^2\times167(2)~\mathrm{kHz/mW^{1.29}}$.
     The fitting results for (a) and (b) are shown in table~\ref{tab:f-det:fit}.
     (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
-    $b(P)$ and $d(P)$ on a log-log scale showing the $P^{0.5}$ scaling of $\Omega_m$ and
+    $b_P$ and $d_P$ on a log-log scale showing the $P^{0.5}$ scaling of $\Omega_m$ and
     the $P^{0.79}$ scaling of $\Omega_a$.
@@
   \centering
-  \begin{tabular}{|c|c|}
-    $f_{\mathrm{PA}0}$&$288711.8~\mathrm{GHz}$\\\hline
-    $a(0.75~\mathrm{mW})$&$770.20452(6)~\mathrm{MHz}$\\
-    $b(0.75~\mathrm{mW})$&$-12.46(2)~\mathrm{MHz\cdot GHz}$\\
-    $a(1.5~\mathrm{mW})$&$770.2081(1)~\mathrm{MHz}$\\
-    $b(1.5~\mathrm{mW})$&$-24.44(3)~\mathrm{MHz\cdot GHz}$\\
-    $a(3.75~\mathrm{mW})$&$770.1943(3)~\mathrm{MHz}$\\
-    $b(3.75~\mathrm{mW})$&$-60.66(8)~\mathrm{MHz\cdot GHz}$\\\hline
-    $c(0.75~\mathrm{mW})$&$-2\pi\times0.29(2)~\mathrm{kHz}$\\
-    $d(0.75~\mathrm{mW})$&$-4\pi^2\times115(4)~\mathrm{kHz\cdot GHz}$\\
-    $c(1.5~\mathrm{mW})$&$-2\pi\times0.63(4)~\mathrm{kHz}$\\
-    $d(1.5~\mathrm{mW})$&$-4\pi^2\times275(6)~\mathrm{kHz\cdot GHz}$\\
-    $c(3.75~\mathrm{mW})$&$-2\pi\times2.4(2)~\mathrm{kHz}$\\
-    $d(3.75~\mathrm{mW})$&$-4\pi^2\times0.95(3)~\mathrm{MHz\cdot GHz}$\\
+  \begin{tabular}{|c|c|c|c|}
+    $P~(\mathrm{mW})$&$0.75$&$1.5$&$3.75$\\\hline
+    $f_{\mathrm{PA}0}~(\mathrm{GHz})$&\multicolumn{3}{|c|}{$288711.8$}\\\hline
+    $a~(\mathrm{MHz})$&$770.20452(6)$&$770.2081(1)$&$770.1943(3)$\\
+    $b~(\mathrm{MHz\cdot GHz})$&$-12.46(2)$&$-24.44(3)$&$-60.66(8)$\\\hline
+    $c~(\mathrm{2\pi\times kHz})$&$0.29(2)$&$0.63(4)$&$2.4(2)$\\
+    $d~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$0.115(4)$&$0.275(6)$&$0.95(3)$\\
   \end{tabular}

### 2020-12-01 scripts/plot_raman.jl

@@ -28,7 +28,7 @@ const prefix = joinpath(@__DIR__, "../imgs", "raman")
 fig = figure(figsize=[1.11, 1.5] * 4.8)
 
 ax1 = fig.add_subplot(311)
-plot(data[:, 1] .- 339724.57, abs.(data[:, 2] ./ 2π / 1000), "C1",
+plot(data[:, 1] .- 339724.57, abs.(data[:, 2] ./ 2π / 1000), "C1--",
      label="\$v'=40\$")
 plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ 2π / 1000), "C0",
      label="\$v'=0\$")
@@ -45,10 +45,10 @@ ax1.tick_params(axis="x", length=0)
 
 ax2 = fig.add_subplot(312)
 subplots_adjust(hspace=0.018)
+plot(data[:, 1] .- 339724.57, abs.(data[:, 4] ./ 2π / 1000), "C1--",
+     label="\$v'=40\$")
 plot(data[:, 1] .- 288625.081, abs.(data[:, 4] ./ 2π / 1000), "C0",
      label="\$v'=0\$")
-plot(data[:, 1] .- 339724.57, abs.(data[:, 4] ./ 2π / 1000), "C1",
-     label="\$v'=40\$")
 ylabel("\$\\Gamma_{s}~(2\\pi\\!\\times\\!\\mathrm{kHz})\$")
 legend(fontsize=13.88, loc="upper left", handlelength=1, handletextpad=0.3)
 xlim([-300, 300])
@@ -65,7 +65,7 @@ ax3 = fig.add_subplot(313)
 subplots_adjust(hspace=0.018)
 plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ data[:, 4]), "C0",
      label="\$v'=0\$")
-plot(data[:, 1] .- 339724.57, abs.(data[:, 2] ./ data[:, 4]), "C1",
+plot(data[:, 1] .- 339724.57, abs.(data[:, 2] ./ data[:, 4]), "C1--",
      label="\$v'=40\$")
 xlabel("One-Photon Detuning (GHz)")
 ylabel("\$\\Omega_{R}/\\Gamma_{s}\$")

### 2020-12-01 two-photon.tex
WIP: two photon scattering

--- 2020-11-24 sm.tex
@@
 \newcommand{\todo}[1]{}
+\newcommand{\Na}{\mathrm{Na}}
+\newcommand{\Cs}{\mathrm{Cs}}
 
@@
 \begin{document}
-\title{Coherent optical association of a single molecule -- Supplemental material}
-\author{Yichao~Yu}
-\email{yichaoyu@g.harvard.edu}
-\gradstudent
-\author{Kenneth~Wang}
-\gradstudent
-\author{Jonathan~D.~Hood}
-\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indiana, 47906, USA}
-\author{Lewis~R.~B.~Picard}
-\gradstudent
-\author{Jessie~T.~Zhang}
-\gradstudent
-\author{William~B.~Cairncross}
-\harvardccb
-\harvardphysics
-\cua
-\author{Jeremy~M.~Hutson}
-\affiliation{Joint Quantum Centre Durham-Newcastle, Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
-\author{Till Rosenband}
-\harvardphysics
-\author{Kang-Kuen~Ni}
-\email{ni@chemistry.harvard.edu}
-\harvardccb
-\harvardphysics
-\cua
-
-\date{\today}
+\title{Two photon coupling to atomic relative motional continuum}
 
@@
 
-\section{3 Level Raman Transfer with Cross Coupling}
+As the reverse process of the Raman transition that forms the molecule,
+the ground molecular state can be driven to the atomic state as well.
+If the energy for such atomic state is above the trap depth of the tweezer,
+this can couple the molecule to a continuum and therefore lead to loss.
+Physically, this loss corresponds to a photodissociation process
+where the two atoms flies apart with high kinetic energy.
 
-In our system, the separation in energy between the initial and target state is much smaller than the single photon detuning $\Delta$ from the intermediate state.
-Thus, there is significant cross coupling for the scattering rate and light shift, where each state is coupled to the excited state by the power in both beams.
-Under these conditions, the scattering rate and light shift is proportional to the total power $P_{\text{tot}} = P_m + P_a$, where $P_{m} (P_{a})$ is the power in the beam that addresses the molecular (atomic) state.
-The Raman Rabi frequency is proportional to $\sqrt{P_mP_a} $.
-With a fixed total power and thus fixed scattering rate, the Raman Rabi frequency is maximized when $ P_m = P_a = P_{\text{tot}}/2$.
+The photodissociation rate is determined by the Fermi's golden rule,
+\[
+  \Gamma=2\pi\Omega_{if}^2\ \rho_f
+\]
+where $\Omega_{if}$ is the matrix element between the initial and final state
+and $\rho_f$ is the density of state near the final state.
+We calculate this by first discretizing the continuum and the rate becomes
+\[
+  \Gamma=2\pi\frac{{\Omega'_{if}}^2}{\delta}
+\]
+where $\Omega'_{if}$ is the Rabi frequency between the initial and final state
+and $\delta$ is the spacing between the discretized final states.
 
-For the purposes of this work, we denote $\Omega_a $($\Omega_m$) as the Rabi frequencies to drive a transition from the atom (target molecule) state to the intermediate state used in the Raman transition corresponding to the power in a single beam, $P_a$ ($P_m$).
-Thus, the Raman Rabi frequency is $\Omega_a\Omega_m/2\Delta$, where $ \Delta $ is the single photon detuning.
-Cross coupling affects the scattering rate and light shift, and assuming equal powers in both beams, these quantities become $ \Gamma_e \Omega_m^2 / 2\Delta^2 + \Gamma_e \Omega_a^2 / 2\Delta^2 $ and $ \Omega_m^2/2\Delta - \Omega_a^2/2\Delta $, where $\Gamma_e$ is the excited state linewidth.
-Since $ \Omega_m >> \Omega_a $, the scattering rate and light shift can be approximated as $ \Gamma_e \Omega_m^2/2\Delta^2$ and $\Omega_m^2/2\Delta$.
+The Rabi frequency $\Omega'_{if}$ is proportional to the square root of FCF,
+which we calculate for the atomic ground motional states by exactly diagonalization
+of the atomic wavefunction.
+However, due to the high energy~($\approx\!1~\mathrm{GHz}$) of the final state,
+calculating FCF for the target state using this method requires an unrealiztic number of
+states to be included.
+Instead, we approximate it using the results for the atomic ground state
+by assuming the FCF to be proportional to the probability density of non-interacting
+atomic wavefunction at zero relative distance so that,
+\[
+  \Omega'_{if}=\Omega_0\frac{\psi_f\paren{r_{rel}=0}}{\psi_0\paren{r_{rel}=0}}
+\]
+where $\Omega_0$ is the Rabi frequency between the excited state and
+the atomic motional ground state and $\psi_f$ and $\psi_0$ are the
+wavefunctions of the final and ground motional atomic state without the molecular potential.
+This approximation is justifed because,
+\begin{enumerate}
+\item The molecular potential is short ranged and the excited molecular state is small.
+\item Only the final atomic wavefunction within the molecular potential contributes to the FCF.
+  For relatively low motional energy
+  this wavefunction is proportional to the value of the wavefunction at
+  the edge of the molecular potential which is well approximated by
+  the atomic wavefunction without the molecular potential.
+\end{enumerate}
+This approximation remains valid until the de Broglie wavelength for the atomic state
+is comparable to the size of the molecular potential which corresponds to
+a motional energy of $\approx\!40~\mathrm{GHz}$.
+For atomic motional ground state, we have,
+\begin{align*}
+  \psi_0\paren{r_{rel}=0}=&\prod_{i=1}^{3}\paren{\frac{\mu\omega_i}{\pi}}^{1/4}\\
+  =&\paren{\frac{\mu^3\omega_1\omega_2\omega_3}{\pi^3}}^{1/4}
+\end{align*}
+where $\mu$ is the reduced mass $\mu\equiv m_\Na m_\Cs/\paren{m_\Na+m_\Cs}$,
+and $\omega_i$'s are the relative trapping frequencies along the three trap axis.
+We discretize the continuum state by adding an infinitely deep spherical potential well
+of radius $R$ around the center. The radial wavefunctions of the eigenstates
+within the well with quantum number $n=1,2,\dots$ is,
+\begin{align*}
+  \psi_n=&\frac{1}{\sqrt{4\pi}r_{rel}}\sqrt{\frac{2}{R}}\sin\paren{\frac{\pi nr_{rel}}{R}}
+\end{align*}
+and the corresponding energy,
+\begin{align*}
+  E_n=&\frac{\pi^2n^2}{2\mu R^2}
+\end{align*}
+The energy gap between neighboring states is
+\begin{align*}
+  \delta_n\approx&\frac{\pi^2n}{\mu R^2}
+\end{align*}
+and the wavefunction value at $r_{rel}=0$ is,
+\begin{align*}
+  \psi_n\paren{r_{rel}=0}=&\sqrt{\frac{1}{2\pi R}}\left.\frac{\ud}{\ud r_{rel}}\sin\paren{\frac{\pi nr_{rel}}{R}}\right|_{r_{rel}=0}\\
+  =&\frac{\pi n}{\sqrt{2\pi R}R}
+\end{align*}
+Substituting into $\Gamma$ and taking the limit of $R\rightarrow\infty$ we have
+\begin{align*}
+  \Gamma=&2\pi\frac{\Omega_0^2}{\delta}\frac{\psi_f^2\paren{r_{rel}=0}}{\psi_0^2\paren{r_{rel}=0}}\\
+  =&\Omega_0^2\frac{n}{R}\sqrt{\frac{\pi^3}{\mu\omega_1\omega_2\omega_3}}=\Omega_0^2\sqrt{\frac{2\pi E}{\omega_1\omega_2\omega_3}}
+\end{align*}
 
-\section{Raman Transfer with Many Intermediate States} \label{sm:sect_2}
-With multiple intermediate states, the total Raman Rabi frequency, scattering rate, and light shift become a sum over all these possible states.
-In our model, we consider all vibrational states of $ \mathrm{c^3\Sigma^+(\Omega = 1)} $ and states in the atomic continuum as intermediate states.
-The Rabi frequency between two states is proportional to the electronic dipole moment, arising from the electronic wavefunctions, and the overlap of the vibrational wavefunctions.
-Under the assumption that the electronic dipole moment $ d $ is the same for all transitions between the ground state and the excited electronic state, the total Raman Rabi frequency becomes:
-\begin{equation}
-  \Omega_R = \frac{d^2E^2}{2\hbar^2} \displaystyle\sum_{v'} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}}
-\end{equation}
-where $\ket{a}$ ($\ket{m}$) are the relative coordinate wavefunctions for the trapped atomic (target molecular) state, and $\ket{v'}$ is the relative-coordinate wavefunction for the excited state which includes both bound molecular states and the atomic continuum.
-$\Delta_{v'}$ is a single photon detuning with respect to the $\ket{v'}$ state, $ E $ is the electric field for the power in the single beam given a waist size.
-We can divide this sum into a sum over all the bound molecular states, and a sum over atomic continuum states.
-\begin{equation}
-  \Omega_R = \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' > v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}}
-\end{equation}
-where $ v'_{\text{max}}$ corresponds to the excited molecular state, which is most weakly bound.
-The first term can be calculated numerically given an excited state potential.
-To calculate the second term, we first make an assumption that we are far enough detuned from the contributing continuum states that they are all at approximately the same detuning, $ \delta_{\text{thresh}}$.
-This allows us to pull it out of the sum, and we obtain:
-\begin{equation}
-  \Omega_R \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\delta_{\text{thresh}}}\displaystyle\sum_{v' > v'_{\text{max}}} \braket{a|v'}\braket{v'|m}  \label{rabifreq}
-\end{equation}
-From requiring orthogonality,
-\begin{equation}
-  \displaystyle\sum_{v'} \braket{a|v'}\braket{v'|m} = \braket{a|m} = 0
-\end{equation}
-we derive an expression for the second sum in equation \ref{rabifreq}
-\begin{equation}
-  \displaystyle\sum_{v'> v'_{\text{max}}} \braket{a|v'}\braket{v'|m} = -\displaystyle\sum_{v' \leq v'_{\text{max}}} \braket{a|v'}\braket{v'|m}
-\end{equation}
-which can be calculated from the vibrational states of the excited state potential. Thus, the Raman Rabi frequency can be approximated as:
-\begin{equation}
-  \Omega_R \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} -  \frac{d^2E^2}{2\hbar^2\delta_{\text{thresh}}}\displaystyle\sum_{v' \leq v'_{\text{max}}} \braket{a|v'}\braket{v'|m}
-\end{equation}
-We can account for the atomic continuum in the scattering rate in a similar way.
-\begin{align}
-  \Gamma_s &= \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} + \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' > v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} \\
-           &\approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} + \frac{d^2E^2\Gamma}{2\hbar^2\delta_{\text{thresh}}^2}\displaystyle\sum_{v' > v'_{\text{max}}}\braket{m|v'}\braket{v'|m}
-\end{align}
-where $\Gamma_{v'}$ is the excited state linewidth for the $\ket{v'}$ state, and we have assumed the atomic continuum states all have the same linewidth $\Gamma$.
-Using normalization, we derive an expression for the sum in the second term
-\begin{equation}
-  \displaystyle\sum_{v' > v'_{\text{max}}}\braket{m|v'}\braket{v'|m} = 1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}
-\end{equation}
-We then arrive at an expression for the scattering rate, accounting for the atomic continuum,
-\begin{equation}
-  \Gamma_s \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} +  \frac{d^2E^2\Gamma}{2\hbar^2\delta_{\text{thresh}}^2}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right)
-\end{equation}
-We have replaced the full continuum with an effective state at the atomic threshold with strength proportional to the amount of wavefunction overlap between the target molecular state and all atomic continuum states.
-This model leads to a component in the scattering rate that is proportional to $ 1/\delta_{\text{thresh}}^2$ and is smaller as one detunes farther from the threshold.
-We note that the first term can also scale nearly as $1/\delta_{\text{thresh}}^2 $, if, as in our case, the largest terms in the summation are from states near the threshold.
+As shown in Fig.~\todo{}, since we only have the two Raman frequencies in the experiment,
+the energy of the final state is never higher than that of the initial atomic state
+and well below the corresponding trap depth.
+Therefore, in order to couple to the continuum,
+the final state must belong to a different atomic spin state with lower energy.
+For our initial spin state of $\Na(2,2),\Cs(3,3)$,
+the only candidate for such state is therefore $\Na(1,1),\Cs(3,3)$,
+which is lower in energy by $\approx\!1.77~\mathrm{GHz}$.
 
-A very similar result holds for the light shift and is written here for completeness
-
-\begin{equation}
-  \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\delta_{\text{thresh}}}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right)
-\end{equation}
-
-\section{Computational methods for bound states and scattering}
-
-For scattering and near-threshold bound states, we solve the Schr\"odinger equation by
-coupled-channel methods \cite{HUTSON1994}, using a basis set in which the electron spins
-$s_{\rm Na}$ and $s_{\rm Cs}$ and the nuclear spins $i_{\rm Na}$ and $i_{\rm Cs}$ are separately
-coupled,
-\begin{equation}
-  | (s_{\rm Na} s_{\rm Cs} S)
-  (i_{\rm Na} i_{\rm Cs} I) F M_F\rangle.
-  \label{eqbassif}
-\end{equation}
-Here $S$ and $I$ are the total electron and nuclear spins of the molecule or atomic pair. Their
-resultant $F$ is the total spin, with projection $M_F$ onto the axis of the magnetic field. In
-principle $F$ can be further coupled to the rotational angular momentum $L$, but in the present
-work only functions with $L=0$ are included. In the absence of a magnetic field, $F$ and $M_F$ are
-both good quantum numbers, but in a magnetic field only $M_F$ is conserved. The calculations in
-this paper use basis sets with all possible values of $S$, $I$ and $F$ (for the required value of
-$M_F$) that can be constructed with $s_{\rm Na} = s_{\rm Cs} = 1/2$,
-$i_{\rm Na} = 3/2$ and $i_{\rm Cs} = 7/2$.
-
-Scattering calculations are carried out using the MOLSCAT package \cite{molscat:2019,
-  mbf-github:2020} and bound-state calculations using the related BOUND package
-\cite{bound+field:2019, mbf-github:2020}. The calculations use singlet and triplet interaction
-potentials for Na+Cs obtained by adjusting the potentials of Docenko \emph{et al.}\
-\cite{Docenko2006} at short range, using the same procedure as for KCs \cite{Groebner2017},
-to reproduce the experimental binding energy of the least-bound triplet state \cite{Hood2019}
-and the position of the s-wave Feshbach resonance near 864~G \cite{Zhang2020}. The atomic
-nuclear hyperfine coupling and Zeeman effects are fully included, using the Hamiltonian described
-in \cite{Hutson2008}.
-
-The bound-state calculations were initially used to predict the binding energies of states that lie
-within about 1~GHz of each atomic threshold of interest. At zero magnetic field, the states fall
-into groups from each hyperfine state of the atomic pair, labeled by $(f_{\rm Na},f_{\rm Cs})$. For
-example, for the $(f_{\rm Na},f_{\rm Cs}) = (2,3)$ states that are of principal interest here, each
-group comprises 5 zero-field levels with $F=1,2,3,4$ and 5; one such group is spread out over a
-range of energies between 290 MHz and 770 MHz below the $(f_{\rm Na},f_{\rm Cs}) = (2,3)$
-threshold. In a magnetic field, each zero-field level splits into $2F+1$ Zeeman sublevels labeled
-by $M_F$. For each sublevel we can calculate the dependence of the energy on magnetic field, in
-order to choose a target state for which the Raman transition frequency depends only weakly on
-field.
-
-The state that we ultimately chose as the target state for Raman transfer is the least-bound
-$(F,M_F)=(5,5)$ sublevel with $(f_{\rm Na},f_{\rm Cs}) = (2,3)$, which was predicted at a binding
-energy 763 MHz below the $(f_{\rm Na},f_{\rm Cs}) = (2,3)$ threshold. As described in the text, it
-was subsequently located experimentally at a binding energy of 770.57150(9) MHz.
-
-Multichannel bound-state wavefunctions, with components labeled by $S$, $I$ and $F$, are calculated
-using the method of Thornley and Hutson \cite{Thornley1994}. For molecular bound states, they are
-obtained on a grid of internuclear distances from 2.4~\AA\ to 50~\AA. For states of confined atomic
-pairs, a harmonic confining potential is added to the molecular potentials and the grid is extended
-to 3000~\AA.
-
-\section{Excited Molecular States} \label{sm:excited_states}
-To obtain a full calculation for the expected Raman Rabi frequency, light shift and scattering, we need to account for all the excited molecular states. 
-The lowest eight molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P. 
-These eight potentials can be written in the Hund's case (a) basis as $ \mathrm{c^3\Sigma^+_{\Omega = 0^-},c^3\Sigma^+_{\Omega = 1}, b^3\Pi_{\Omega = 0^-}, b^3\Pi_{\Omega = 0^+}, b^3\Pi_{\Omega = 1}, b^3\Pi_{\Omega = 2}, B^1\Pi_{\Omega = 1}, A^1\Sigma^+_{\Omega = 0^+}}$ \cite{Korek2007}.
-Due to spin-orbit coupling, especially large in Cs, the excited molecular states are mixed, containing components in multiple potentials. 
-Fortunately, single-channel potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
-Since there is only one $ \Omega = 2$ potential at this dissociation limit, a single-channel potential has been determined for $ b^3\Pi_2$ as well \cite{Zabawa2012}.
-Unfortunately, single-channel potentials for the other electronic states do not exist. 
-A deperturbation analysis was required for states belonging to the mixed $\mathrm{A-b}$ complex, 
-and the fitted potentials and spin-orbit coupling coefficients are only accurate within the energy range of the measured experimental data \cite{Zaharova2009}. 
-Since our experiment attempts to work in a regime where the predominant Raman coupling comes from the $v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $, 
-the contribution of the other seven potentials is mainly to a background that is nearly detuning independent. 
-Thus, for computational ease, we use the diabatic potentials for $ \mathrm{b^3\Pi_{0}, b^3\Pi_{1}} $ and $ \mathrm{A^1\Sigma^+_{0^+}}$, and remove the states nearest to the $ v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $.
-Lastly, to our knowledge, no potential fit to experimental data exists for the $ c^3\Sigma^+_{0^-}$ state.
-Assuming that its contribution is only to the background, as an approximation, we simply double the contribution of all states except $v' = 0$ from $ c^3\Sigma^+_1$.
-
-\section{Calculating Matrix Elements with Coupled Channel Ground State}
-To calculate Rabi frequencies for transitions to the eight excited molecular potentials, we
-obtain their wavefunctions from a single-channel calculation \cite{Fattal1996} using the potential energy curves described in section \ref{sm:excited_states}. We
-then calculate overlap integrals between these functions and either the triplet ($S=1$) or singlet ($S=0$) components of the
-coupled-channel wavefunctions for either the target molecular state or the confined atomic state.
-These calculations assume that the intermediate states have pure singlet or triplet character and neglect its
-nuclear spin character, which is unknown.
-
-The full calculation of the Raman Rabi frequency and scattering rate using the methods in section \ref{sm:sect_2} is shown in figure \ref{f-sm}.
-The strong contribution from the atomic threshold arises from the large overlap to the near-threshold bound states.
-This leads to a $1/\delta_{\text{thresh}}^2$ dependence of the scattering rate and favors using deeply bound states as the intermediate state for the Raman transfer.
-
-\begin{figure}[ht!]
-  \includegraphics[width=\textwidth]{imgs/raman_theory_full.pdf}
-  \caption{ Full calculation of the Raman Rabi frequency and scattering rate as a function of the single-photon frequency including all vibrational states of $ \mathrm{c^3\Sigma^+(\Omega = 1)}$ and the atomic continuum.
-The second frequency in the Raman transition is offset by about $770~\mathrm{MHz}$ and resonant with the two photon transition.
-The assumed excited-state linewidth for all molecular lines is $50~\text{MHz} $.
-    \label{f-sm}}
-\end{figure}
-
-Since our coupled-channel calculations include the harmonic confinement, we can calculate the enhancement in $\Omega_a$ with increasing confinement.
-Using two calculations with $ \omega_{\text{trap}} = 36.5~\mathrm{kHz}$ and $\omega_{\text{trap}} = 80~\mathrm{kHz}$ trapping frequencies, and assuming a power law scaling, we find $ \Omega_a \propto \omega_{\text{trap}}^{0.58} $.
-Thus, $\Omega_a \propto P^{0.29} $, which was also experimentally verified.
-However, we note that in the actual experiment, our system does not have spherically symmetric confinement.
-The radial trapping frequency is about $5.7$ times larger than the axial trapping frequency.
-\todo{
-  Power/intensity calibration
-}
-
-\bibliography{master_ref}
 \end{document}

### 2020-12-01 two-photon.tex
WIP: two photon scattering

@@
 
-As shown in Fig.~\todo{}, since we only have the two Raman frequencies in the experiment,
+\begin{figure}[ht!]
+  \includegraphics[width=0.6\textwidth]{imgs/pa_two_photon_down_raman.pdf}
+  \caption{
+    Effect of two-photon coupling to atomic contimuum on molecular state.
+    (a) Raman transition from the atomic ground state $|g\rangle$
+    to the molecular bound state $|m\rangle$ using two Raman beams with frequencies
+    $\omega_1$ and $\omega_2$.
+    (b-e) Two photon transitions starting from the molecular state $|m\rangle$
+    with different frequency combinations without additional atomic spin states.
+    (b) This is the reverse Raman transition and reaches the initial atomic state.
+    (c,d) The frequency pairs couples back to $|m\rangle$.
+    (e) This couples to an energy below $|m\rangle$.
+    Note that none of the two-photon transitions from $|m\rangle$ in (b-e) ends up in
+    the atomic motional continuum (gray) for the spin state $|g\rangle$.
+    However, it is coupled to the motional continuum
+    for the spin state with lower energy $|g'\rangle$
+    and may be affected by the corresponding dissociative scattering.
+    \label{f-raman-continuum}}
+\end{figure}
+
+As shown in Fig.~\ref{f-raman-continuum},
+since we only have the two Raman frequencies in the experiment,
 the energy of the final state is never higher than that of the initial atomic state

### 2020-12-01 two-photon.tex
two photon scattering

@@
 the only candidate for such state is therefore $\Na(1,1),\Cs(3,3)$,
-which is lower in energy by $\approx\!1.77~\mathrm{GHz}$.
+which is lower in energy by $E_{\mathrm{HF}}\approx1.77~\mathrm{GHz}$.
+Due to the conservation of $m_f$, this coupling is forbidden if the tweezer is $\pi$-polarized.
+Therefore, such coupling can only be caused by impurity in the tweezer polarization.
+Using a previously measured tweezer polarization of $C=0.0545$,
+where $\mathbf{C}\equiv\abs{\Im\paren{\mathbf{\varepsilon}\times\mathbf{\varepsilon}^*}}$
+and $\mathbf{\varepsilon}$ is the polarization vector,
+we estimated the Raman Rabi frequency between the molecular state and the $\Na(1,1),\Cs(3,3)$
+ground state to be $\Omega_0\approx2\pi500~\mathrm{Hz}$.
+Combining the 4 different pathways in Fig.~\ref{f-raman-continuum}(b-e),
+the total scattering expected is,
+\begin{align*}
+  \Gamma=&\Omega_0^2\sqrt{\frac{2\pi}{\omega_1\omega_2\omega_3}}
+           \paren{\sqrt{E_{\mathrm{HF}}}+4\sqrt{E_{\mathrm{HF}}-E_b}+\sqrt{E_{\mathrm{HF}}-2E_b}}\\
+  \approx&2\pi\times200~\mathrm{Hz}
+\end{align*}
+where $E_b$ is the binding energy of the molecule.
+The order-of-magnitude agreement between this rough estimate and the observed loss rate
+of $2\pi\times800~\mathrm{Hz}$ suggests that this loss mechanism
+could potentially explain the loss we observe given the correct tweezer polarization.
 

### 2020-12-02 paper.tex
Update on Overleaf.

@@
 taking into account of all states of
-8 excited molecular state potentials~\cite{Korek2007, Grochola2011, Zaharova2009, Grochola2010, Zabawa2012}
+8 excited molecular potentials~\cite{Korek2007, Grochola2011, Zaharova2009, Grochola2010, Zabawa2012}
 and the continuum~\cite{Liu2017}.
@@
 we use the tweezer beam itself as the Raman beams by turning on two frequencies
-in the tweezer during the Raman pulse, as shown in Fig.~\ref{f-raman}b inset.
+in the tweezer during the Raman pulse using an acousto-optic modulator, as shown in Fig.~\ref{f-beampath}.
 The dual use of the tweezer beam not only eliminates additional scattering sources
@@
 Furthermore, we use two Bragg gratings, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
-to filter the laser spectrum generated by a fiber amplifier
-that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
+to filter the laser spectrum. 
+As shown in Fig.~\ref{f-beampath}, we place one filter directly after the laser, which is a fiber amplifer seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
+We place the second filter as close to the microscope objective as possible.
 We observe a reduction of the scattering rate by a factor of $2$
@@
 to the Rabi frequency is 10 times larger than predicted.
-If this discrepancy arises from the $v'=0$ excited state,
-it can be due either to a high ratio $\Omega_m / \Omega_a$ or to a large $\Gamma_e$.
+This discrepancy can arise from the $v'=0$ excited state, if the ratio $\Omega_m / \Omega_a$ or $\Gamma_e$ are larger than expected.
 Additionally, coupling to other excited states can add an offset to
@@
   \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
-    (a) The light shift of the Raman resonance fitted to$a_P+b_P/\Delta$, where
+    (a) The light shift of the Raman resonance fitted to $a_P+b_P/\Delta$, where
     $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
@@
     to the light shift,
-    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweer}}$ is the detuning from
+    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweezer}}$ is the detuning from
     the PA resonance frequency $f_{\mathrm{PA}0}$.
@@
     at zero tweezer power to be $f_{R0}=770.1969(2)~\mathrm{MHz}$.
-    (b) Raman Rabi frequency ($\Omega_R$) fitted to$c_P+d_P/\Delta$, where
+    (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
     $c_P$ and $d_P=\Omega_a\Omega_m/2$
@@
     and the fit gives $c_P/P^{1.29}=-2\pi\times0.41(2)~\mathrm{kHz/mW^{1.29}}$
-    and $d_P/P^{1.29}=-4\pi^2\times167(2)~\mathrm{kHz/mW^{1.29}}$.
-    The fitting results for (a) and (b) are shown in table~\ref{tab:f-det:fit}.
+    and $d_P/P^{1.29}=-4\pi^2\times167(2)~\mathrm{kHz\cdot GHz/mW^{1.29}}$.
+    The fitting results for (a) and (b) are shown in Table~\ref{tab:f-det:fit}.
     (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
@@
 
-First we look at the change in resonance frequency to determine $\Omega_m$.
-We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
-When we vary the tweezer frequency around the $v'=0$ intermediate state,
-we can further observe a $1/\Delta$ component
-and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a.
+To determine $\Omega_m$ and $ \Omega_a$, we measure the change in resonance frequency and Raman Rabi frequency as a function of the tweezer detuning. 
+For both these quantities, we observe a $1/\Delta$ component
+and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a, b.
 The background is caused by coupling to other excited states that are further away in energy.
-The $1/\Delta$ component, however, is due to the coupling between the molecular state
-and the $v'=0$ intermediate state.
-From this measurement, we can extract a $\Omega_m$ of
-$2\pi\times180.87(7)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
+The $1/\Delta$ component, however, is due to the coupling to the $v'=0$ intermediate state.
+Combining the fit coefficients, summarized in Table \ref{tab:f-det:fit}, for the $1/\Delta$ component, we can extract $\Omega_m $ and $ \Omega_a $.
+
+We perform the experiment at various tweezer powers to extract the power dependence of $ \Omega_m $ and $ \Omega_a $, as shown in Fig.~\ref{f-det}c.
+$ \Omega_m $ scales with $ P^{0.5} $ as expected, and we obtain a fit value of $2\pi\times180.87(7)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
 This number is within $40~\mathrm{\%}$
 of the value $2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory.
-
-In order to calculate the ratio $\Omega_m/\Omega_a$,
-we now need to extract $ \Omega_a $.
-We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
-% which depends on both $\Omega_m$ and $\Omega_a$.
-The Raman Rabi frequency shows a non-linear dependency on the tweezer power
-due to the change in the atomic wavefunction caused by
-tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
-As discussed before, for weakly interacting particles,
+The scaling of $ \Omega_a $ differs from $ P^{0.5} $, which is the expected scaling from the laser intensity, due to the change in the atomic wavefunction caused by tighter confinement at higher power.
+For weakly interacting particles,
 $\Omega_a$ scales as $P^{3/8}$.
@@
 Instead, coupled-channel calculations show that the scaling
-is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
-Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
-which fits well to our experimental result, as shown in Fig.~\ref{f-det}c.
-Similar to the light shift, the detuning dependency of the Raman Rabi frequency
-is determined by a constant background component and
-a $v'=0$ component that scales as $1/\Delta$.
-The $v'=0$ component of the Raman Rabi frequency at our detuning is
-$2\pi\times1.10(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
-or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
-Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
-$2\pi\times 5.5(2)~\mathrm{MHz}$.
-This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $63(3)$,
-which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
-Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
-from the $v'=0$ state to be higher than expected.
+is very well approximated by $P^{0.29}$ within the range of confinement in our experiment. Thus, $ \Omega_a $ scales as $ P^{0.79} $, which fits well to our experimental result.
+The fit value is $2\pi\times1.85(3)~\mathrm{MHz}/\mathrm{P^{0.79}}$.
+At $3.75~\mathrm{mW}$ tweezer power, we measured $ \Omega_m = 2\pi \times 348.3(3)~\mathrm{MHz}$ and $ \Omega_a = 2\pi\times 5.5(2)~\mathrm{MHz}$, resulting in a $ \Omega_m/\Omega_a$ ratio of about $ 63 $, which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
+Therefore, the matrix element ratio is not the cause of our lower than expected transfer efficiency.
 Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.
+%We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
+% From these measurements, we can extract a $\Omega_m$ of
+
+%In order to calculate the ratio $\Omega_m/\Omega_a$,
+%we now need to extract $ \Omega_a $.
+%We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
+% which depends on both $\Omega_m$ and $\Omega_a$.
+%The Raman Rabi frequency shows a non-linear dependency on the tweezer power
+%due to the change in the atomic wavefunction caused by
+%tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
+
+%Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
+%which fits well to our experimental result, as shown in Fig.~\ref{f-det}b.
+%Similar to the light shift, the detuning dependency of the Raman Rabi frequency
+%is determined by a constant background component and
+%a $v'=0$ component that scales as $1/\Delta$.
+%The $v'=0$ component of the Raman Rabi frequency at our detuning is
+%$2\pi\times1.10(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
+%or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ %tweezer power.
+%Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
+%$2\pi\times 5.5(2)~\mathrm{MHz}$.
+%This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $63(3)$,
+%which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
 
@@
     & Experiment & Theory \\ \hline
-    $\Omega_R $ & $-$ & $2\pi \times 15.3~\mathrm{kHz}$ \\
-    $\Gamma_s$ & $-$ & $ 2\pi \times 533~\mathrm{Hz}$ \\
+    $\Omega_R $ & $2\pi \times 3.28(4)~\mathrm{kHz}$ & $2\pi \times 15.3~\mathrm{kHz}$ \\
+    $\Gamma_s$ & $2\pi \times 0.80(4)~\mathrm{kHz}$ & $ 2\pi \times 533~\mathrm{Hz}$ \\
     $\Omega_m$ & $2\pi \times 348.3(3)~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
@@
 
-With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
-we now consider the background effects from other states with larger single-photon detuning.
+%With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
+We now consider the background effects from other states with larger single-photon detuning.
 In the Raman Rabi frequency fit,

### 2020-12-02 sm.tex
[sm] let's just call it red line...
Update on Overleaf.

@@
     The assumed excited-state linewidth for all molecular lines is $50~\text{MHz}$.
-    The thick red line shows the contribution that comes only from the near-threshold states.
+    The red line shows the contribution that comes only from the near-threshold states.
     \label{f-sm}}
@@
 \end{figure}
+\section{Effective Matrix Elements to a Single State}
+
+In this calculation, there is a matrix element, $\Omega_{ai}, \Omega_{mi}$ between each channel $ i $ of the coupled channel ground state and an excited state.
+The total Raman Rabi frequency $ \Omega_R$, light shift $ \delta$ and off-resonant scattering $ \Gamma_S $ contribution from this single excited state is calculated as
+
+\begin{align}
+    \Omega_{R} &= \displaystyle\sum_{i} \frac{\Omega_{ai} \Omega_{mi}}{2\Delta} \\
+    \delta &= \displaystyle\sum_{i} \frac{\Omega_{ai}^2 - \Omega_{mi}^2}{2\Delta} \\
+    \Gamma_S &= \displaystyle\sum_{i} \Gamma_e \frac{\Omega_{ai}^2 + \Omega_{mi}^2}{2\Delta^2}
+\end{align}
+
+where $ \Delta $ is the single photon detuning and $ \Gamma_e $ is the excited state linewidth.
+The experiment, through measuring the detuning dependence of the Raman Rabi frequency and the resonance frequency, extracts a single $ \Omega_m $ and $ \Omega_a $.
+In order to compare to the theory, we introduce effective $ \Omega_a', \Omega_m', \Gamma_e'$, so that $ \Omega_R = \Omega_a'\Omega_m'/2\Delta $, $\delta = (\Omega_{a}'^2 - \Omega_{m}'^2)/2\Delta $, and $\Gamma_S = \Gamma_e'(\Omega_{a}'^2 + \Omega_{m}'^2)/2\Delta^2 $.
+These effective Rabi frequencies are used to calculate the Rabi frequency ratio and are the quantities reported in the main text when compared to experiment.
+
+\section{Scaling of atomic matrix element with tweezer power}
 

### 2020-12-03 paper.tex
Regenerate PDF, whitespace
Update on Overleaf.

@@
 the highest phase-space-density gas~\cite{Demarco2018} and 
-the coldest individual molecules~\cite{Zhang2020,He331}
+%the coldest 
+trapped individual molecules~\cite{Zhang2020,He331}
 have been achieved through the association of ultracold atoms.
@@
 where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
+Note that we use the convention where the Rabi frequency describes the population oscillation between the two states.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
-The transfer Raman Rabi Rate is given by $\Omega_a\Omega_m / 2\Delta$~\cite{Wineland2003}.
+The transfer Raman Rabi Rate is given by $\Omega_a\Omega_m / (2\Delta)$~\cite{Wineland2003}.
 % , is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
@@
 Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally.
-Thus, the scattering rate is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited-state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power.
+Thus, the scattering rate is given by $ \Gamma_e \Omega_m^2 / (2\Delta^2)$, where $ \Gamma_e $ is the excited-state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power.
 Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
@@
 because this is also the ratio between $\Omega_R$
-and the AC Stark shift of the molecular state, $\Omega_m^2 / 2\Delta$
+and the AC Stark shift of the molecular state, $\Omega_m^2 / (2\Delta)$
 \footnote{There is an additional factor of 2, with both beams at equal power,
@@
 $ \Omega_m $ scales with $ P^{0.5} $ as expected, and we obtain a fit value of $2\pi\times180.87(7)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
-This number is within $40~\mathrm{\%}$
-of the value $2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory.
 The scaling of $ \Omega_a $ differs from $ P^{0.5} $, which is the expected scaling from the laser intensity, due to the change in the atomic wavefunction caused by tighter confinement at higher power.
@@
 Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.
-%We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
+% We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
 % From these measurements, we can extract a $\Omega_m$ of
 
-%In order to calculate the ratio $\Omega_m/\Omega_a$,
-%we now need to extract $ \Omega_a $.
-%We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
+% In order to calculate the ratio $\Omega_m/\Omega_a$,
+% we now need to extract $ \Omega_a $.
+% We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
 % which depends on both $\Omega_m$ and $\Omega_a$.
-%The Raman Rabi frequency shows a non-linear dependency on the tweezer power
-%due to the change in the atomic wavefunction caused by
-%tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
+% The Raman Rabi frequency shows a non-linear dependency on the tweezer power
+% due to the change in the atomic wavefunction caused by
+% tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
 
-%Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
-%which fits well to our experimental result, as shown in Fig.~\ref{f-det}b.
-%Similar to the light shift, the detuning dependency of the Raman Rabi frequency
-%is determined by a constant background component and
-%a $v'=0$ component that scales as $1/\Delta$.
-%The $v'=0$ component of the Raman Rabi frequency at our detuning is
-%$2\pi\times1.10(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
-%or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ %tweezer power.
-%Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
-%$2\pi\times 5.5(2)~\mathrm{MHz}$.
-%This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $63(3)$,
-%which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
+% Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
+% which fits well to our experimental result, as shown in Fig.~\ref{f-det}b.
+% Similar to the light shift, the detuning dependency of the Raman Rabi frequency
+% is determined by a constant background component and
+% a $v'=0$ component that scales as $1/\Delta$.
+% The $v'=0$ component of the Raman Rabi frequency at our detuning is
+% $2\pi\times1.10(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
+% or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ %tweezer power.
+% Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
+% $2\pi\times 5.5(2)~\mathrm{MHz}$.
+% This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $63(3)$,
+% which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
+
+% Theory numbers
+% $2\pi \times 15.3~\mathrm{kHz}$
+%  $ 2\pi \times 533~\mathrm{Hz}$
+% $2\pi \times 573 ~\mathrm{MHz}$
+% $2\pi \times 7.37 ~\mathrm{MHz}$
 
@@
   \centering
-  \begin{tabular}{c|c|c}
-    & Experiment & Theory \\ \hline
-    $\Omega_R $ & $2\pi \times 3.28(4)~\mathrm{kHz}$ & $2\pi \times 15.3~\mathrm{kHz}$ \\
-    $\Gamma_s$ & $2\pi \times 0.80(4)~\mathrm{kHz}$ & $ 2\pi \times 533~\mathrm{Hz}$ \\
-    $\Omega_m$ & $2\pi \times 348.3(3)~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
-    $\Omega_a$ & $2\pi \times 5.5(2)~\mathrm{MHz}$ & $2\pi \times 7.37 ~\mathrm{MHz}$ \\
-    $\Omega_m/\Omega_a$ & $63(3)$ & $77.7$
+  \begin{tabular}{c|c}
+    & Measured Values \\ \hline
+    $\Omega_R $ & $2\pi \times 3.28(4)~\mathrm{kHz}$ \\
+    $\Gamma_s$ & $2\pi \times 0.80(4)~\mathrm{kHz}$ \\
+    $\Omega_m$ & $2\pi \times 348.3(3)~\mathrm{MHz} $  \\
+    $\Omega_a$ & $2\pi \times 5.5(2)~\mathrm{MHz}$  \\
+    $\Omega_m/\Omega_a$ & $63(3)$ 
   \end{tabular}
-  \caption{Comparison between theory and experiment of $\Omega_R,\Gamma_s, \Omega_m, \Omega_a$.
+  \caption{Experimental values of $\Omega_R,\Gamma_s, \Omega_m, \Omega_a$.
 $\Omega_R$ and $ \Gamma_s $ are reported at $151~\mathrm{GHz}$ detuned from the $v' = 0$ state.
@@
 
-%With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
+% With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
 We now consider the background effects from other states with larger single-photon detuning.

### 2020-12-04 scripts/plot_raman.jl
Update figures
* consistent 2pi
* remove theory plot for absolute Omega_m and Omega_a

@@ -25,44 +25,46 @@ const data = LibArchive.Reader(fname) do reader
 end
 const prefix = joinpath(@__DIR__, "../imgs", "raman")
 
-fig = figure(figsize=[1.11, 1.5] * 4.8)
+# fig = figure(figsize=[1.11, 1.5] * 4.8)
+fig = figure()
 
-ax1 = fig.add_subplot(311)
-plot(data[:, 1] .- 339724.57, abs.(data[:, 2] ./ 2π / 1000), "C1--",
-     label="\$v'=40\$")
-plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ 2π / 1000), "C0",
-     label="\$v'=0\$")
-ylabel("\$\\Omega_{R}~(2\\pi\\!\\times\\!\\mathrm{kHz})\$")
-xlim([-300, 300])
-ylim([6, 20000])
-yscale("log")
-# yticks([10, 100, 1000, 10000], ["10", "100", "1000", "10000"])
-ax1.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
-grid()
-setp(ax1.get_xticklabels(), visible=false)
-setp(ax1.get_xticklabels(), visible=false)
-ax1.tick_params(axis="x", length=0)
+# ax1 = fig.add_subplot(311)
+# plot(data[:, 1] .- 339724.57, abs.(data[:, 2] ./ 2π / 1000), "C1--",
+#      label="\$v'=40\$")
+# plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ 2π / 1000), "C0",
+#      label="\$v'=0\$")
+# ylabel("\$\\Omega_{R}~(2\\pi\\!\\times\\!\\mathrm{kHz})\$")
+# xlim([-300, 300])
+# ylim([6, 20000])
+# yscale("log")
+# # yticks([10, 100, 1000, 10000], ["10", "100", "1000", "10000"])
+# ax1.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
+# grid()
+# setp(ax1.get_xticklabels(), visible=false)
+# setp(ax1.get_xticklabels(), visible=false)
+# ax1.tick_params(axis="x", length=0)
 
-ax2 = fig.add_subplot(312)
-subplots_adjust(hspace=0.018)
-plot(data[:, 1] .- 339724.57, abs.(data[:, 4] ./ 2π / 1000), "C1--",
[…]

### 2020-12-04 scripts/plot_scaling.jl

@@ -276,8 +276,8 @@ grid()
 # xticks([-200, -160, -120, -80])
 yticks([0, 200, 400, 600])
 ylim([0, 790])
-xlabel("\$1 / \\Delta~(\\mathrm{THz^{-1}})\$")
-ylabel("Light Shift (kHz)")
+xlabel("\$1 / \\Delta~(\\mathrm{THz^{-1}/(2\\pi)})\$")
+ylabel("\$\\omega_R-\\omega_{R0}\$ (\$\\mathrm{2\\pi\\times kHz}\$)")
 NaCsPlot.maybe_save("$(prefix)_light_shift")
 
 figure(figsize=[6.4, 4.8] * 1.11308)
@@ -298,7 +298,7 @@ grid()
 yticks([0, 2, 4, 6, 8])
 # xticks([-200, -160, -120, -80])
 ylim([0, 9.7])
-xlabel("\$1 / \\Delta~(\\mathrm{THz^{-1}})\$")
+xlabel("\$1 / \\Delta~(\\mathrm{THz^{-1}/(2\\pi)})\$")
 ylabel("\$\\Omega_{R}~(\\mathrm{2\\pi\\times kHz})\$")
 NaCsPlot.maybe_save("$(prefix)_rabi")
 

### 2020-12-04 paper.tex
Consistent 2pi in text

--- 2020-12-02 paper.tex
@@
   \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
-    (a) The light shift of the Raman resonance fitted to $a_P+b_P/\Delta$, where
+    (a) The Raman resonance fitted to $a_P+b_P/\Delta$, where
     $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
@@
     to the light shift,
-    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweezer}}$ is the detuning from
+    $\Delta\equiv2\pi\times\paren{f_{\mathrm{PA}0} - f_{\mathrm{tweezer}}}$ is the detuning from
     the PA resonance frequency $f_{\mathrm{PA}0}$.
@@
     \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
-    at zero tweezer power to be $f_{R0}=770.1969(2)~\mathrm{MHz}$.
+    at zero tweezer power to be $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$.
     (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
@@
     $f_{\mathrm{PA}0}~(\mathrm{GHz})$&\multicolumn{3}{|c|}{$288711.8$}\\\hline
-    $a~(\mathrm{MHz})$&$770.20452(6)$&$770.2081(1)$&$770.1943(3)$\\
-    $b~(\mathrm{MHz\cdot GHz})$&$-12.46(2)$&$-24.44(3)$&$-60.66(8)$\\\hline
+    $a~(\mathrm{2\pi\times MHz})$&$770.20452(6)$&$770.2081(1)$&$770.1943(3)$\\
+    $b~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$-12.46(2)$&$-24.44(3)$&$-60.66(8)$\\\hline
     $c~(\mathrm{2\pi\times kHz})$&$0.29(2)$&$0.63(4)$&$2.4(2)$\\
@@
 Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.
-%We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
+% We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
 % From these measurements, we can extract a $\Omega_m$ of
 
-%In order to calculate the ratio $\Omega_m/\Omega_a$,
-%we now need to extract $ \Omega_a $.
-%We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
+% In order to calculate the ratio $\Omega_m/\Omega_a$,
+% we now need to extract $ \Omega_a $.
+% We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
 % which depends on both $\Omega_m$ and $\Omega_a$.
-%The Raman Rabi frequency shows a non-linear dependency on the tweezer power
-%due to the change in the atomic wavefunction caused by
-%tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
+% The Raman Rabi frequency shows a non-linear dependency on the tweezer power
+% due to the change in the atomic wavefunction caused by
+% tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
 
-%Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
-%which fits well to our experimental result, as shown in Fig.~\ref{f-det}b.
-%Similar to the light shift, the detuning dependency of the Raman Rabi frequency
-%is determined by a constant background component and
-%a $v'=0$ component that scales as $1/\Delta$.
-%The $v'=0$ component of the Raman Rabi frequency at our detuning is
-%$2\pi\times1.10(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
-%or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ %tweezer power.
-%Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
-%$2\pi\times 5.5(2)~\mathrm{MHz}$.
-%This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $63(3)$,
-%which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
+% Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
+% which fits well to our experimental result, as shown in Fig.~\ref{f-det}b.
+% Similar to the light shift, the detuning dependency of the Raman Rabi frequency
+% is determined by a constant background component and
+% a $v'=0$ component that scales as $1/\Delta$.
+% The $v'=0$ component of the Raman Rabi frequency at our detuning is
+% $2\pi\times1.10(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
+% or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ %tweezer power.
+% Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
+% $2\pi\times 5.5(2)~\mathrm{MHz}$.
+% This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $63(3)$,
+% which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
 

### 2020-12-04 paper.tex
Tweak up Raman Rabi vs Scattering plot and caption

@@
     The deeply bound excited state (blue lines $v'=0$)
-    has a smaller Raman Rabi frequency ($\Omega_{R}$)
+    has a larger ratio of Raman Rabi frequency to scattering rate
     compared to the weakly bound excited state (orange lines $v'=40$) at a most detuning.
-    However, the scattering rate ($\Gamma_{s}$) is also much lower,
-    which results in a larger ratio of Raman Rabi frequency to scattering rate.
     (c) Enhancement of the short-range wavefunction.

### 2020-12-04 scripts/plot_raman.jl

@@ -75,6 +75,8 @@ xlim([-300, 300])
 ylim([0.02, 90])
 yscale("log")
 yticks([0.1, 1, 10], ["0.1", "1", "10"])
+legend(fontsize=13.88, loc="center left", bbox_to_anchor=(0.0, 0.6),
+       handlelength=1, handletextpad=0.3)
 ax3.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 grid()
 NaCsPlot.maybe_save("$(prefix)_v0_vhi")

### 2020-12-04 paper.tex

--- 2020-12-03 paper.tex
@@
 the highest phase-space-density gas~\cite{Demarco2018} and
-%the coldest 
+% the coldest
 trapped individual molecules~\cite{Zhang2020,He331}

### 2020-12-06 paper.tex
Update on Overleaf.

@@
 
+\usepackage{xcolor}
+\newcounter{TRC}
+\newcommand{\TR}[1]{\textcolor{violet}{[[\stepcounter{TRC} TR\arabic{TRC}: #1]]}}
+
 \begin{document}
@@
   we achieve an optical transfer efficiency of $69\mathrm{\%}$.
-  The molecules have a binding energy of $770.1969(2)~\mathrm{MHz}$ at $8.83(2)~\mathrm{G}$
-  and are created with higher than $60\mathrm{\%}$ probability in the motional ground state.
+  The molecules have a binding energy of $770.1969(2)~\mathrm{MHz}$ \TR{SYSTEMATICS?
+I doubt the optical power measurement is accurate enough to support light-shift corrections to 200~Hz accuracy.} at $8.83(2)~\mathrm{G}$
+  and are created with higher than $60\mathrm{\%}$ probability\textcolor{blue}{(KK: this was not mentioned anywhere in the main text)} in the motional ground state.
   This technique does not rely on Feshbach resonances or narrow excited-state lines
@@
 Diverse species of fully quantum controlled  ultracold molecules are desired
-for a wide variety of applications including precision measurements~\cite{
+for a variety of applications including precision measurements~\cite{
   Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018,
@@
 and studies of ultracold chemistry~\cite{Bala2016,Hu1111,Segev2019,deJongh626}.
-While many innovative approaches demonstrated in the last few years
+While many innovative approaches in the last few years
 have directly cooled different species of diatomic or polyatomic molecules
@@
 by two-photon optical Raman transfer via an electronic excited state,
-schematically shown in Fig.~\ref{f-theory}a.
+as shown in Fig.~\ref{f-theory}a.
 The scheme does not rely on a Feshbach resonance,
-molecular states bound by a few MHz, or a narrow excited state.
+molecular states bound by a few~MHz, or a narrow excited state.
 The resulting single molecule is in a well-defined internal quantum state
@@
 A vibrational state of the electronic excited state $\mathrm{c^3\Sigma^+}(\Omega = 1)$
-is used as the intermediate state in the Raman scheme,
-and is chosen to minimize photon scattering during Raman Rabi oscillations.
+serves as the intermediate state in the Raman scheme,
+and is chosen to minimize photon scattering during Raman Rabi \TR{Is Raman Rabi freq the best term?} oscillations.
 To reduce photon scattering and sensitivity to laser intensity noise further,
@@
 
-The essence of an optical Raman transfer can be illustrated
-using a three-level system shown in Fig.~\ref{f-theory}a,
-where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.
-Note that we use the convention where the Rabi frequency describes the population oscillation between the two states.
+The optical Raman transfer is illustrated
+by the idealized three-level system shown in Fig.~\ref{f-theory}a,
+where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies $\Omega_a$ and $\Omega_m$ with one-photon detuning $ \Delta $, and all Rabi frequencies are population oscillation frequencies.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
-The transfer Raman Rabi Rate is given by $\Omega_a\Omega_m / (2\Delta)$~\cite{Wineland2003}.
+The transfer Raman Rabi Rate is given by $\Omega_a\Omega_m / (2\Delta)$~\cite{Wineland2003}. \textcolor{blue}{[KK: is this the formula used in the citation?]}
 % , is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
 % $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
-Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
+Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced ($\Omega_a/\Omega_m \ll 1$) %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
 due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
-and therefore the scattering is predominantly from the target molecular state.
-Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally.
-Thus, the scattering rate is given by $ \Gamma_e \Omega_m^2 / (2\Delta^2)$, where $ \Gamma_e $ is the excited-state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power.
-Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
-The ratio between the Raman Rabi frequency and the scattering rate is therefore $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $.
+and scattering losses are dominated by the final state.
+Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning $ \Delta $ of $80$ to $200$~GHz, causing the target molecular state to scatter both beams nearly equally with a total rate $ \Gamma_e \Omega_m^2 / (2\Delta^2)$, where $ \Gamma_e $ is the excited-state linewidth~\footnote{The two beams have equal power to maximize the Raman Rabi rate at fixed total power, resulting in a factor of 2 for scattering two beams.}.
+In this idealized treatment, the ratio between the Raman Rabi frequency and the scattering rate is $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, which limits the transfer efficiency into the molecular state.
+At the same time, the intensity-stability requirement is determined by the ratio of Raman Rabi frequency to Stark shift ($4\Omega_a/\Omega_m$)~\footnote{There is an additional factor of 2, with both beams at equal power,
+  to account for the Stark shift caused by both beams.}.
+Notably, both figures of merit improve with a larger ratio $\Omega_a/\Omega_m$.
 %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
-To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred.
+To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred \TR{Mention 2-photon here?}.
 %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
@@
 in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
-However, a complete picture must include both the many vibrational levels
+However, a complete picture includes both the many vibrational levels
 of the excited electronic state and the atomic continuum.
@@
 and Raman Rabi rates over all possible intermediate states.
-Since there is large overlap between the target molecular state and weakly bound excited states, using states that are closer to the dissociation threshold as the intermediate state results in a large scattering rate.
+As there is large overlap between the target molecular state and weakly bound excited states, intermediate states that are closer to the dissociation threshold result in a large scattering rate.
 % in large incoherence and loss to other molecular states.
@@
 where $\delta_{\mathrm{thresh}}$ is the detuning from the dissociation threshold,
-and thus can be made smaller by using deeply bound vibrational states as the intermediate state.
+which can be made smaller by using deeply bound vibrational states as the intermediate state \TR{Cite supplement or maybe Fig.
+S1 can go into Fig.
+1b since it shows $\Gamma_s\sim \delta_{thresh}^{-2}$ nicely.}.
 
-To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency $\Omega_R$
-and scattering rate $\Gamma_s$ at different detunings from the atomic threshold
+We optimize over intermediate states by calculating the Raman Rabi frequency $\Omega_R$
+and scattering rate $\Gamma_s$ at different detunings from the atomic threshold,
 taking into account of all states of
@@
 and the continuum~\cite{Liu2017}.
-This calculation shows that $\Omega_R/\Gamma_s$
-can be made larger for more deeply bound states compared to weakly bound states
-at a cost of a smaller $\Omega_R$, as shown in Fig.~\ref{f-theory}b;
+This calculation shows that the figure of merit $\Omega_R/\Gamma_s$
+can be larger for more deeply bound states compared to weakly bound states
+at a cost of a smaller transfer rate $\Omega_R$, as shown in Fig.~\ref{f-theory}b;
 see Supplementary Material for details.
 As a result, we choose the $v'=0$ level of $\mathrm{c^3\Sigma^+}(\Omega = 1)$
-as the closest intermediate state to drive the Raman transition.
+as the intermediate state near which to drive Raman transitions.
 
 In addition to the intermediate state,
-choosing an initial and a final state for a large ratio $\Omega_a/\Omega_m$
-maximizes $\Omega_R$ at a given detuning.
-Furthermore, a larger ratio also relaxes the intensity stability requirement for the Raman lasers,
-because this is also the ratio between $\Omega_R$
-and the AC Stark shift of the molecular state, $\Omega_m^2 / (2\Delta)$
-\footnote{There is an additional factor of 2, with both beams at equal power,
-  to account for the Stark shift caused by both beams.}.
+the choice of initial and final Zeeman and hyperfine states affects the single-photon rates $\Omega_a$ and $\Omega_m$.
 Due to the small extent of the intermediate-state wavefunction
@@
 the short-range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $ or $P^{3/8}$,
-where $ \omega_{\text{trap}} $ is the trap frequency and $P$ is the optical power in the tweezer trap \cite{Mies2000}.
-However, additional power may not always be available, and will also lead to additional undesired scattering.
+where $ \omega_{\text{trap}} $ is the trap frequency and $P$ is the optical power in the tweezer trap \cite{Mies2000} with a fixed beam waist.
+However, additional power may not be available and also leads to additional undesired scattering.
 Alternatively, one can choose an atomic pair state with a large scattering length
@@
   \includegraphics[width=0.48\textwidth]{imgs/fig-raman.pdf}
-  \caption{
-    (a) Raman detuning scans at different times showing the resonance frequency.
+  \caption{Coherent transfer of atoms to molecules.  The molecular state is dark to the imaging step and corresponds to zero signal.
+    (a) Raman difference frequency scans at different times showing the resonance.
     (b) Raman pulse-time scan on resonance.
-    A decaying Rabi oscillation can be observed, proving the coherence of
+    A decaying Rabi oscillation shows the coherence of
     the Raman transfer process.
-    This is fitted together with (a) to a model of the Raman transition including loss of the atom and molecule state and is used to determine
+    A model is fitted to (a) and (b) to determine
     both the Raman Rabi frequency and the loss rates.
-    Inset: Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
-    The tweezer and Raman beam is focused through an objective to a waist of $0.9~\mathrm{\mu m}$,
-    which defines the location of the atoms and molecule.
-    We use a bias magnetic field $B_0=8.83(2)~\mathrm{G}$ along the tweezer polarization
-    to define the quantization axis.
-    As a result, the atoms experience predominantly $\pi$ polarization from the tweezer.
+    \emph{Inset:} Geometry and polarization of trap and Raman beam relative to the magnetic field.
+    The beam is focused to a waist of $0.9~\mathrm{\mu m}$
+    that confines the atoms and molecule.
+    A magnetic field of $B_0=8.83(2)~\mathrm{G}$ along the tweezer polarization
+    defines the quantization axis and the atoms experience predominantly $\pi$-polarized light.
     \label{f-raman}}
@@
 To perform the Raman transfer of an atom pair to the target weakly bound molecular state,
-we use the tweezer beam itself as the Raman beams by turning on two frequencies
-in the tweezer during the Raman pulse using an acousto-optic modulator, as shown in Fig.~\ref{f-beampath}.
-The dual use of the tweezer beam not only eliminates additional scattering sources
-or undesired laser frequencies,
-but also allows a tight focus to maximize the Raman Rabi frequency
-and minimize the transfer time.
-Furthermore, we use two Bragg gratings, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
-to filter the laser spectrum.
-As shown in Fig.~\ref{f-beampath}, we place one filter directly after the laser, which is a fiber amplifer seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
-We place the second filter as close to the microscope objective as possible.
-We observe a reduction of the scattering rate by a factor of $2$
-due to suppression of the broadband amplified spontaneous emission (ASE) from the laser
-that couples to other excited states.
+we use the tweezer beam itself with two frequencies, as shown in Fig.~\ref{f-beampath}.
+The dual use of the tweezer beam for confinement and Raman transfer not only minimizes photon scattering,
+but also allows a tight focus to minimize the transfer duration.
+Furthermore, two filters, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
+clean the laser spectrum and prevent broadband noise from causing unwanted excitation.
+As shown in Fig.~\ref{f-beampath}, one filter immediately follows the laser, which is a fiber amplifer seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
+The second filter precedes the microscope objective.
+\TR{Move some technical details to the figure caption.}
+The filters reduce photon scattering rate by a factor of $2$.  While we have not fully characterized the sources 
+of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities.
 After the total tweezer power is set to the desired value,
@@
 Both frequencies are kept on for a specified duration before the process is reversed
-and the tweezer returns to a single frequency.
+and the tweezer returns to a single frequency.~\TR{???}
 
@@
   \caption{
-    (a) Direct measurement of molecule lifetime in a trap of depth $3.75~\mathrm{mW}$.
+    (a) Direct measurement of molecule lifetime with about $3.75~\mathrm{mW}$ optical power.
     Molecule survival is detected by dissociating back to atoms using a second Raman transition.
@@
 
-We choose the tweezer frequency to be $288560~\mathrm{GHz}$
-which is far detuned (by $\approx\!151~\mathrm{GHz}$) from the $v' = 0$ line.
+\TR{``We" is overused in this paper and obscures more important subject-object relationships.
+Authorship already implies that ``we" did everything in the paper.} We choose a tweezer frequency far detuned (by $-151~\mathrm{GHz}$) from the $v' = 0$ line to reduce resonant scattering.
+\textcolor{blue}{[KK: mention there are 3 lines at v'=0, cite our ~\cite{Liu2019}]}
 Guided by the coupled-channel calculations,
-we locate the Raman resonance for the atoms-to-molecule transition at
-$770.57150(9) ~\mathrm{MHz}$ with about $3.75~\mathrm{mW}$ tweezer power
-focused down to a waist of $ 0.9~\mathrm{\mu m}$, as shown in Fig.~\ref{f-raman}a.
+we locate the Raman resonance as shown in Fig.~\ref{f-raman}, which shows a Fourier-limited resonance together with Rabi oscillations between the atomic and molecular states.
 % (We can maybe add information about the prediction here?)
@@
 % directly detected by our imaging step.
-The molecular state is dark to the imaging step,
-so successful transfer of the atoms to the molecular state is detected as loss of atoms.
-We observe a Fourier-limited linewidth, which is evidence of a coherent transfer.
-In order to verify the coherence of the transfer directly,
-we fix the two-photon detuning on resonance and scan the pulse time.
-Fig.~\ref{f-raman}b shows the observed coherent Rabi oscillation between the atomic and molecular states.
-Fitting the data with a decaying Rabi oscillation suggests that
+A decaying Rabi oscillation fitted to the data suggests that
 $69~\mathrm{\%}$ of atoms initially in the motional ground state are transferred into the molecular state after a $\pi$ pulse.
-This transfer efficiency is limited mainly by the molecular lifetime,
-which can be measured directly by preparing the molecule with a $\pi $ pulse
+
+\TR{combine with later} Raman transfer efficiency is limited mainly by the molecular lifetime,
+which is measured directly by preparing the molecule with a $\pi $ pulse
 and then using a second $\pi$ pulse to dissociate the molecule back to atoms
@@
 consistent with the decay of the Rabi oscillation.
-We obtain the Raman Rabi frequency by fitting our measurements to a model
+We obtain the Raman Rabi frequency by fitting to our measurements a model
 that includes a Raman Rabi frequency and
 a finite lifetime for the molecular state, as shown in Fig.~\ref{f-raman}a and b.
-We account for the small effect of atomic state loss by measuring the one-body and
+We account for the small effect of atom loss by measuring the one-body and
 two-body lifetime of the atoms directly without turning on the second frequency,
@@
 The fit including all these effects gives a Raman Rabi frequency
-of $2\pi\times3.28(4)~\mathrm{kHz}$.
-
-The efficiency of the transfer is lower than expected
-because we found the ratio of the molecular scattering rate~(i.e. inverse of lifetime)
-to the Rabi frequency is 10 times larger than predicted.
-This discrepancy can arise from the $v'=0$ excited state, if the ratio $\Omega_m / \Omega_a$ or $\Gamma_e$ are larger than expected.
-Additionally, coupling to other excited states can add an offset to
-both the Raman Rabi frequency and the scattering rate and thus affect their ratio.
-
-In order to verify whether any one of these sources are the origin of the reduced transfer efficiency,
-we measured the properties of the Raman resonance as a function of the tweezer power and single-photon detuning.
-These dependencies allow us to experimentally determine the Rabi frequencies,
-$ \Omega_a $, $\Omega_m $ and how much of the scattering, Stark shift,
-or Raman Rabi frequency comes from the $ v' = 0$ intermediate state.
+of $2\pi\times3.28(4)~\mathrm{kHz}$.~\TR{Why does Fig. 5b show about 4 kHz?}
 
@@
   \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
-  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
-    (a) The Raman resonance fitted to $a_P+b_P/\Delta$, where
+  \caption{Raman transition parameters as a function of tweezer power and detuning.
+    (a) The Raman resonance fitted by $a_P+b_P/\Delta$, where
     $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
-    are tweezer power dependent background and $v'=0$ contribution
-    to the light shift,
-    $\Delta\equiv2\pi\times\paren{f_{\mathrm{PA}0} - f_{\mathrm{tweezer}}}$ is the detuning from
-    the PA resonance frequency $f_{\mathrm{PA}0}$.
-    The $a_P$s are fitted to a model including linear and small quadratic light shift
+    are the power ($P$) dependent background and $v'=0$ contributions
+    to the light shift and
+    $\Delta\equiv2\pi\times\paren{f_0 - f_{\mathrm{tweezer}}}$ is the detuning from
+    the $v'=0$ resonance frequency $f_0$.
+    $a_P$ is fitted to a model including linear and small quadratic light shift
     \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
-    at zero tweezer power to be $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$.
+    at zero tweezer power $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$.
     (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
@@
     The detuning is calculated using the PA frequency fitted in (a).
-    The $c_P$s and $d_P$s are proportional to $P^{1.29}$
+    $c_P$ and $d_P$ are proportional to $P^{1.29}$
     and the fit gives $c_P/P^{1.29}=-2\pi\times0.41(2)~\mathrm{kHz/mW^{1.29}}$
@@
 \end{figure*}
+
+To better understand the details and limitations of the Raman transfer process, we measured the properties of the two-photon resonance as a function of tweezer power and single-photon detuning.
+Known dependencies of the light shift and Raman Rabi frequency on detuning $\Delta$ allow experimental determination of the Rabi frequencies
+$ \Omega_a $ and $\Omega_m$ whose ratio critically affects the transfer efficiency.
+Both the light shift and Raman Rabi frequency follow a $1/\Delta$ slope as shown in Fig.~\ref{f-det}a, b and include a constant offset that we attribute to coupling to other excited states that are further away in energy.
+The $1/\Delta$ components, due to the nearby $v'=0$ intermediate state, determine $\Omega_m $ and $ \Omega_a $ in Table~\ref{tab:rabi_freqs} from the fit coefficients in Table \ref{tab:f-det:fit}.
+
 \begin{table}[ht]
@@
 
-To determine $\Omega_m$ and $ \Omega_a$, we measure the change in resonance frequency and Raman Rabi frequency as a function of the tweezer detuning.
-For both these quantities, we observe a $1/\Delta$ component
-and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a, b.
-The background is caused by coupling to other excited states that are further away in energy.
-The $1/\Delta$ component, however, is due to the coupling to the $v'=0$ intermediate state.
-Combining the fit coefficients, summarized in Table \ref{tab:f-det:fit}, for the $1/\Delta$ component, we can extract $\Omega_m $ and $ \Omega_a $.
-
 We perform the experiment at various tweezer powers to extract the power dependence of $ \Omega_m $ and $ \Omega_a $, as shown in Fig.~\ref{f-det}c.
-$ \Omega_m $ scales with $ P^{0.5} $ as expected, and we obtain a fit value of $2\pi\times180.87(7)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
-The scaling of $ \Omega_a $ differs from $ P^{0.5} $, which is the expected scaling from the laser intensity, due to the change in the atomic wavefunction caused by tighter confinement at higher power.
-For weakly interacting particles,
-$\Omega_a$ scales as $P^{3/8}$.
+$ \Omega_m $ scales like $ P^{1/2} $ as expected.
+As discussed previously, the scaling of $ \Omega_a $ is $P^{7/8}$ for weakly interacting particles.
 However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
-Instead, coupled-channel calculations show that the scaling
-is very well approximated by $P^{0.29}$ within the range of confinement in our experiment. Thus, $ \Omega_a $ scales as $ P^{0.79} $, which fits well to our experimental result.
-The fit value is $2\pi\times1.85(3)~\mathrm{MHz}/\mathrm{P^{0.79}}$.
-At $3.75~\mathrm{mW}$ tweezer power, we measured $ \Omega_m = 2\pi \times 348.3(3)~\mathrm{MHz}$ and $ \Omega_a = 2\pi\times 5.5(2)~\mathrm{MHz}$, resulting in a $ \Omega_m/\Omega_a$ ratio of about $ 63 $, which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
-Therefore, the matrix element ratio is not the cause of our lower than expected transfer efficiency.
-Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.
+Coupled-channel calculations show that the wave-function scaling
+is well approximated by $P^{0.29}$ within the range of confinement in our experiment and the expected scaling of $ \Omega_a \propto P^{0.79} $ agrees with the data.
+%At $3.75~\mathrm{mW}$ tweezer power, we measured $ \Omega_m = 2\pi \times 348.3(3)~\mathrm{MHz}$ and $ \Omega_a = 2\pi\times 5.5(2)~\mathrm{MHz}$, resulting in a 
+%The measured $ \Omega_m/\Omega_a$ ratio of $ 63 $ is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
+%Therefore, the matrix element ratio is not the cause of our lower than expected transfer efficiency.
+Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy.
 % We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
@@
   \centering
-  \begin{tabular}{c|c}
-    & Measured Values \\ \hline
-    $\Omega_R $ & $2\pi \times 3.28(4)~\mathrm{kHz}$ \\
-    $\Gamma_s$ & $2\pi \times 0.80(4)~\mathrm{kHz}$ \\
-    $\Omega_m$ & $2\pi \times 348.3(3)~\mathrm{MHz} $  \\
-    $\Omega_a$ & $2\pi \times 5.5(2)~\mathrm{MHz}$  \\
-    $\Omega_m/\Omega_a$ & $63(3)$
+  \begin{tabular}{c|c|c|c|c}
+    $\Omega_R$ & $\Gamma_s$ & $\Omega_m$ & $\Omega_a$ & $\Omega_a/\Omega_m$ \\ 
+    ($2\pi\times$kHz) & ($2\pi\times$kHz) & ($2\pi\times$MHz) & ($2\pi\times$MHz) &  \\ \hline 
+    X.YY & 0.80(4) & 348.3(3) & 5.5(2) & 63(3) \\
   \end{tabular}
-  \caption{Experimental values of $\Omega_R,\Gamma_s, \Omega_m, \Omega_a$.
-$\Omega_R$ and $ \Gamma_s $ are reported at $151~\mathrm{GHz}$ detuned from the $v' = 0$ state.
-All numbers are reported at $3.75$ mW tweezer power.
-}
+  \caption{Experimentally determined coefficients at $3.75$~mW tweezer power.
+$\Omega_R$ and $ \Gamma_s $ are reported at $-151~\mathrm{GHz}$ detuning from the $v' = 0$ state.
+The coefficients $\Omega_m$ and $\Omega_a$ are in broad agreement with our calculation and their ratio is near the theory prediction of $78$.
+The measured Rabi rate $\Omega_R$ is ZZ~\% of $\Omega_m \Omega_a/2$ due to interference from further-detuned Raman processes.
+[[TR: Check all mentions of $P=3.75$~mW because they may negelect reduction from 2nd ASE filter.]]}
   \label{tab:rabi_freqs}
@@
 % With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
-We now consider the background effects from other states with larger single-photon detuning.
-In the Raman Rabi frequency fit,
-the fitted background is of opposite sign from the Raman Rabi frequency
-for single-photon detunings red of the $v' = 0 $ transition.
-Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$
-at the current detuning.
-However, this difference is not enough to explain the discrapancy of more than a factor of $10$
-present in the experiment.
-Due to the change in sign of the Raman Rabi frequency as a function of detuning
-when crossing a resonance, the same background will increase the Raman Rabi frequency
-for positive detunings from the $v' = 0$ transition.
-Unfortunately, we observe additional nearby excited states
-belonging to a different electronically excited state at higher frequencies
-which prevent the blue side of the transition from being be usable for the Raman transition.
+%We now consider the background effects from other states with larger single-photon detuning.
+%In the Raman Rabi frequency fit,
+%the fitted background is of opposite sign from the Raman Rabi frequency
+%for single-photon detunings red of the $v' = 0 $ transition.
+%Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$
+%at the current detuning.
+%However, this difference is not enough to explain the discrapancy of more than a factor of $10$
+%present in the experiment.
+%Due to the change in sign of the Raman Rabi frequency as a function of detuning
+%when crossing a resonance, the same background will increase the Raman Rabi frequency
+%for positive detunings from the $v' = 0$ transition.
+%Unfortunately, we observe additional nearby excited states
+%belonging to a different electronically excited state at higher frequencies
+%which prevent the blue side of the transition from being be usable for the Raman transition.
 
@@
   does not lead to scattering but only decherence.}
-These results suggest that the decoherence or loss we observe during the Raman transition
-comes from either a higher background scattering rate of an unknown source
-or a different intrinsic or technical source for which we have not accounted for.
-We observe a decrease in the coherence time by a factor of 2 without the ASE filters. This
-suggests the spectral purity of the laser is a significant source of scattering, but does not explain the full amount.
-Other sources that can contribute to the decoherence include
-the stability of the tweezer power and the magnetic field.
+%These results suggest that the decoherence or loss we observe during the Raman transition
+%comes from either a higher background scattering rate of an unknown source
+%or a different intrinsic or technical source for which we have not accounted for.
+\TR{combine this and next paragraph with earlier} The efficiency of the transfer is limited by the short lifetime of the molecular state~(Fig.~\ref{f-lifetime}a) together with a reduction in the Raman Rabi frequency due to intermediate states beyond v'=0 (see Table~~\ref{tab:rabi_freqs}).
+Preliminary experiments and theoretical considerations indicate that the molecular lifetime may be limited by two-photon coupling to the atomic continuum~\TR{Cite YY thesis.}.
+We also observe a decrease in the coherence time by a factor of 2 without laser spectrum filters,
+suggesting that spectral impurity of the laser can be a significant source of scattering.
+Other sources that can contribute to decoherence include
+the stability of the tweezer power and magnetic field.
 Based on the ratio of the Raman Rabi frequency to light shift, shown in Fig.~\ref{f-det}c,
@@
 which does not cause significant decoherence from the measured magnetic field
-fluctuation of $\sim1.5~\mathrm{mG}$.
+fluctuation of $\sim1.5~\mathrm{mG}$.~\TR{Mention somewhere that the shape of Fig. 3b Rabi flopping indicates molecular loss, not atomic loss or frequency fluctuation.}
 
-The scattering rate of the molecule also depends on the tweezer power and detuning,
-and becomes smaller when the power is lowered.
-At $0.75~\mathrm{mW}$ tweezer power, we observe a molecule lifetime as long as $1~\mathrm{ms}$.
-Since the technical noise that can lead to decoherence
-is not fully characterized in our experiment,
-we are unable to further identify the sources of the measured scattering rate
-based on our measured detuning and power dependencies.
+%The scattering rate of the molecule also depends on the tweezer power and detuning,
+%and becomes smaller when the power is lowered.
+%At $0.75~\mathrm{mW}$ tweezer power, we observe a molecule lifetime as long as $1~\mathrm{ms}$.
+%Since the technical noise that can lead to decoherence
+%is not fully characterized in our experiment,
+%we are unable to further identify the sources of the measured scattering rate
+%based on our measured detuning and power dependencies.
 
-Lastly, to confirm that the excess scattering does not come from the atomic state,
+To confirm that the observed loss of Rabi oscillation is not due to the atomic state,
 we measure the two-body scattering rate
 without turning on the second frequency, as shown in Fig.~\ref{f-lifetime}b inset.
-The scattering rate scales as $P^{2.58}$,
-which is inconsistent with a single-photon scattering process.
-We have not been able to observe a dependency on the detuning in order to verify whether the scattering process is related to the $v'=0$ state,
-but the power scaling strongly suggests the existence of an unknown two-photon process.
-Nevertheless, the absolute scattering rate from the atomic state
-is much lower than the total scattering rate
-and is not the limiting factor in this experiment.
+The scattering rate scales as $P^{2.58}$ and is too low to explain the Rabi oscillation decoherence.
+%We have not been able to observe a dependency on the detuning in order to verify whether the scattering process is related to the $v'=0$ state,
+%but the power scaling strongly suggests the existence of an unknown two-photon process.
+%Nevertheless, the absolute scattering rate from the atomic state
+%is much lower than the total scattering rate
+%and is not the limiting factor in this experiment.
 
-In conclusion, we have formed a weakly bound NaCs molecule in an optical tweezer
+In conclusion, we have coherently formed a weakly bound NaCs molecule in an optical tweezer
 by optical Raman transfer.
+This process is enabled by utilizing a deeply-bound intermediate state, as well as highly-interacting initial atomic states.
 A theoretical investigation including 8 excited state potentials,
-the excited atomic continuum, and coupled-channel ground state wavefunctions indicated
-better transfer efficiency using a deeply bound intermediate state
-and the $\ket{\uparrow_{\Na} \downarrow_{\Cs} }$ spin state as the initial and final states.
-Using these theoretical insights, we located the weakly bound state
-and coherently associated the atoms into a weakly bound molecule. Currently,
-Our transfer efficiency is limited by an unknown scattering source
-resulting in measured scattering rates over $10$ times larger than theoretical predictions.
-Despite this limitation, the transfer efficiency may be further improved
-by increasing the ratio of the up-leg to down-leg Rabi frequency
-$\Omega_a/\Omega_m$, for example by driving to more deeply bound states.
+the excited atomic continuum, and coupled-channel ground state wavefunctions indicates
+the potential for higher transfer efficiency than the observed value of $69$~\%.
+Future experiments may benefit from better balancing of the up-leg and down-leg Rabi frequencies, for example by driving to more deeply bound states.
+If possible, destructive interferences that reduce the two-photon Rabi rate should be avoided.
+Nonlinear optical effects that limit the molecular state lifetime can also be explored.
 
-Our technique can be applied to form a more diverse set of molecular species,
-since it does not rely on a magnetic Feshbach resonance, states bound by a few MHz,
-or a narrow excited state. The formation of a weakly bound molecule is a key step
+Our technique can be applied to form a diverse set of molecular species,
+because it does not rely on a magnetic Feshbach resonance, states bound by only a few MHz,
+or a narrow excited state. The formation of weakly bound molecules is a key step
 in forming rovibrational ground state molecules.
-By scaling up to many optical tweezers\cite{Endres2016, Barredo2018, PhysRevX.8.041055, PhysRevLett.122.203601}, large arrays with arbitrary geometry of highly controlled molecules can be achieved.
+By scaling up to many optical tweezers~\cite{Endres2016, Barredo2018,  PhysRevLett.122.203601}, large arrays with arbitrary geometry of highly controlled molecules can be achieved.
+
 % Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},
@@
 \begin{acknowledgments}
-  We would like to thank Rosario Gonzalez-Ferez, Olivier Dulieu, Bo Gao, and Paul Julienne \textcolor{red}{acknowledge getting TDM} for discussion.
+  We would like to thank Rosario Gonzalez-Ferez, Olivier Dulieu, Bo Gao, and Paul Julienne for discussion and Robert Moszynski for providing theoretical transition dipole moments of NaCs.
 This work is supported by the NSF~(PHY-1806595), the AFOSR~(FA9550-19-1-0089), ARO DURIP (W911NF1810194) and the Arnold and Mabel Beckman foundation.

### 2020-12-06 scripts/plot_scaling.jl
Plot label

@@ -276,7 +276,7 @@ grid()
 # xticks([-200, -160, -120, -80])
 yticks([0, 200, 400, 600])
 ylim([0, 790])
-xlabel("\$1 / \\Delta~(\\mathrm{THz^{-1}/(2\\pi)})\$")
+xlabel("\$2\\pi / \\Delta~(\\mathrm{THz^{-1}})\$")
 ylabel("\$\\omega_R-\\omega_{R0}\$ (\$\\mathrm{2\\pi\\times kHz}\$)")
 NaCsPlot.maybe_save("$(prefix)_light_shift")
 
@@ -298,7 +298,7 @@ grid()
 yticks([0, 2, 4, 6, 8])
 # xticks([-200, -160, -120, -80])
 ylim([0, 9.7])
-xlabel("\$1 / \\Delta~(\\mathrm{THz^{-1}/(2\\pi)})\$")
+xlabel("\$2\\pi / \\Delta~(\\mathrm{THz^{-1}})\$")
 ylabel("\$\\Omega_{R}~(\\mathrm{2\\pi\\times kHz})\$")
 NaCsPlot.maybe_save("$(prefix)_rabi")
 

### 2020-12-06 two-photon.tex
Avoid Im macro

@@
 Using a previously measured tweezer polarization of $C=0.0545$,
-where $\mathbf{C}\equiv\abs{\Im\paren{\mathbf{\varepsilon}\times\mathbf{\varepsilon}^*}}$
+where $\mathbf{C}\equiv\abs{\mathrm{Im}\paren{\mathbf{\varepsilon}\times\mathbf{\varepsilon}^*}}$
 and $\mathbf{\varepsilon}$ is the polarization vector,

### 2020-12-07 paper.tex
Update on Overleaf.

@@
   we achieve an optical transfer efficiency of $69\mathrm{\%}$.
-  The molecules have a binding energy of $770.1969(2)~\mathrm{MHz}$ \TR{SYSTEMATICS?
-I doubt the optical power measurement is accurate enough to support light-shift corrections to 200~Hz accuracy.} at $8.83(2)~\mathrm{G}$
-  and are created with higher than $60\mathrm{\%}$ probability\textcolor{blue}{(KK: this was not mentioned anywhere in the main text)} in the motional ground state.
+  The molecules have a binding energy of $770.2~\mathrm{MHz}$ at $8.83(2)~\mathrm{G}$.
   This technique does not rely on Feshbach resonances or narrow excited-state lines
@@
 So far, molecular association has generally been achieved by magnetoassociation
-using a magnetic Feshbach scattering resonance.
+through a magnetic Feshbach scattering resonance.
 Exceptions include Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states
@@
     and the final state is the first molecular bound state.
-    The transition is driven by a pair of laser frequencies matching the binding energy
+    The transition is driven by a pair of laser frequencies whose difference matches the binding energy
     of the molecule.
@@
     by $\Delta$ in order to suppress scattering during the transfer.
-    (b) Comparison between using a weakly bound and a deeply bound excited state
-    as intermediate state for the Raman transition.
+    (b) Comparison between weakly-bound and deeply-bound intermediate excited state
+    for the Raman transition.
     The deeply bound excited state (blue lines $v'=0$)
@@
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
-The transfer Raman Rabi Rate is given by $\Omega_a\Omega_m / (2\Delta)$~\cite{Wineland2003}. \textcolor{blue}{[KK: is this the formula used in the citation?]}
+The transfer Raman Rabi Rate is given by $\Omega_a\Omega_m / (2\Delta)$~\cite{Wineland2003}. 
 % , is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
@@
 In this idealized treatment, the ratio between the Raman Rabi frequency and the scattering rate is $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, which limits the transfer efficiency into the molecular state.
-At the same time, the intensity-stability requirement is determined by the ratio of Raman Rabi frequency to Stark shift ($4\Omega_a/\Omega_m$)~\footnote{There is an additional factor of 2, with both beams at equal power,
+At the same time, the intensity-stability requirement is determined by the ratio of Raman Rabi frequency to Stark shift ($\Omega_a/\Omega_m$)~\footnote{There is an additional factor of 2, with both beams at equal power,
   to account for the Stark shift caused by both beams.}.
@@
 where $\delta_{\mathrm{thresh}}$ is the detuning from the dissociation threshold,
-which can be made smaller by using deeply bound vibrational states as the intermediate state \TR{Cite supplement or maybe Fig.
+which is smaller for intermediate states that are deeply bound \footnote{See Supplementary Material}.
+\TR{Cite supplement or maybe Fig.
 S1 can go into Fig.
@@
 To increase this amplitude, one can increase the external confinement of atom pairs.
-Using a harmonic approximation,
+In a harmonic approximation
 the short-range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $ or $P^{3/8}$,
@@
   \caption{Coherent transfer of atoms to molecules.  The molecular state is dark to the imaging step and corresponds to zero signal.
-    (a) Raman difference frequency scans at different times showing the resonance.
-    (b) Raman pulse-time scan on resonance.
+    (a) Raman difference frequency scans for different durations showing the resonance.
+    (b) Raman pulse-length scan on resonance.
     A decaying Rabi oscillation shows the coherence of
@@
     \emph{Inset:} Geometry and polarization of trap and Raman beam relative to the magnetic field.
-    The beam is focused to a waist of $0.9~\mathrm{\mu m}$
+    The beam X.yy~mW beam is focused to a waist of $0.9~\mathrm{\mu m}$
     that confines the atoms and molecule.
@@
 Experimentally, we first prepare two atoms in a well-defined external and internal quantum state
-using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}.
+by using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}.
 In brief, the experimental cycle begins by stochastically loading a single ${}^{23}\Na$ atom
@@
 the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.
-We use this as the initial atomic state for Raman transfer.
+This is the initial atomic state for Raman transfer.
 This spin flip selectively transfers atoms in the relative motional ground state,
@@
 To perform the Raman transfer of an atom pair to the target weakly bound molecular state,
-we use the tweezer beam itself with two frequencies, as shown in Fig.~\ref{f-beampath}.
+we modulate the tweezer beam with a second frequency, as shown in Fig.~\ref{f-beampath}.
 The dual use of the tweezer beam for confinement and Raman transfer not only minimizes photon scattering,
@@
 clean the laser spectrum and prevent broadband noise from causing unwanted excitation.
-As shown in Fig.~\ref{f-beampath}, one filter immediately follows the laser, which is a fiber amplifer seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
-The second filter precedes the microscope objective.
-\TR{Move some technical details to the figure caption.}
+As shown in Fig.~\ref{f-beampath}, one filter immediately follows the laser, while the second filter precedes the microscope objective for final cleanup of the laser spectrum.
 The filters reduce photon scattering rate by a factor of $2$. While we have not fully characterized the sources
 of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities.
-After the total tweezer power is set to the desired value,
-we smoothly ramp down the power of one frequency in the tweezer
-while simultaneously ramping up the power of the other frequency
-so that the total tweezer power remains unchanged.
-Both frequencies are kept on for a specified duration before the process is reversed
-and the tweezer returns to a single frequency.~\TR{???}
+%After the total tweezer power is set to the desired value,
+%we smoothly ramp down the power of one frequency in the tweezer
+%while simultaneously ramping up the power of the other frequency
+%so that the total tweezer power remains unchanged.
+%Both frequencies are kept on for a specified duration before the process is reversed
+%and the tweezer returns to a single frequency.~\TR{???}
 
@@
     (a) Direct measurement of molecule lifetime with about $3.75~\mathrm{mW}$ optical power.
-    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
+    Molecule survival is detected by dissociating back to atoms via a second Raman transition.
     The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
@@
 \TR{``We" is overused in this paper and obscures more important subject-object relationships.
-Authorship already implies that ``we" did everything in the paper.} We choose a tweezer frequency far detuned (by $-151~\mathrm{GHz}$) from the $v' = 0$ line to reduce resonant scattering.
-\textcolor{blue}{[KK: mention there are 3 lines at v'=0, cite our ~\cite{Liu2019}]}
+Authorship already implies that ``we" did everything in the paper.} We choose a tweezer frequency far detuned (by $-151~\mathrm{GHz}$) from the 3 observed rotational lines at $v' = 0 $ to reduce resonant scattering~\cite{Liu2019}.
 Guided by the coupled-channel calculations,
@@
 A decaying Rabi oscillation fitted to the data suggests that
-$69~\mathrm{\%}$ of atoms initially in the motional ground state are transferred into the molecular state after a $\pi$ pulse.
-
-\TR{combine with later} Raman transfer efficiency is limited mainly by the molecular lifetime,
-which is measured directly by preparing the molecule with a $\pi $ pulse
-and then using a second $\pi$ pulse to dissociate the molecule back to atoms
-after a variable wait time.
-The result in Fig.~\ref{f-lifetime}a shows a molecular lifetime of $0.199(9)~\mathrm{ms}$
-consistent with the decay of the Rabi oscillation.
-We obtain the Raman Rabi frequency by fitting to our measurements a model
-that includes a Raman Rabi frequency and
-a finite lifetime for the molecular state, as shown in Fig.~\ref{f-raman}a and b.
-We account for the small effect of atom loss by measuring the one-body and
-two-body lifetime of the atoms directly without turning on the second frequency,
-as shown in Fig.~\ref{f-lifetime}b.
-The fit including all these effects gives a Raman Rabi frequency
-of $2\pi\times3.28(4)~\mathrm{kHz}$.~\TR{Why does Fig. 5b show about 4 kHz?}
+$69~\mathrm{\%}$ of atoms initially in the relative motional ground state are transferred into the molecular state after a $\pi$ pulse.
+Over $60\%$ of the created molecules are in the motional ground state (both relative motion and center of mass motion), inferred from independent Raman sideband thermometry measurements of the atoms.
+A fit including atomic and molecular losses (see below) yields a Raman Rabi frequency of $2\pi\times3.28(4)~\mathrm{kHz}$.
 
@@
     \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
-    at zero tweezer power $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$.
+    at zero tweezer power $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$ where the statistical uncertainty is shown.
     (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
     $c_P$ and $d_P=\Omega_a\Omega_m/2$
-    are tweezer power dependent background and $v'=0$ contribution.
-    The detuning is calculated using the PA frequency fitted in (a).
-    $c_P$ and $d_P$ are proportional to $P^{1.29}$
-    and the fit gives $c_P/P^{1.29}=-2\pi\times0.41(2)~\mathrm{kHz/mW^{1.29}}$
-    and $d_P/P^{1.29}=-4\pi^2\times167(2)~\mathrm{kHz\cdot GHz/mW^{1.29}}$.
-    The fitting results for (a) and (b) are shown in Table~\ref{tab:f-det:fit}.
+    are the background and $v'=0$ contributions that scale as $P^{1.29}$ with optical power.
+    The detuning is calculated from the PA frequency fitted in (a). Fit parameters are listed in Table~\ref{tab:f-det:fit}.
     (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
-    $b_P$ and $d_P$ on a log-log scale showing the $P^{0.5}$ scaling of $\Omega_m$ and
-    the $P^{0.79}$ scaling of $\Omega_a$.
+    $b_P$ and $d_P$ on a log-log scale showing approximate $P^{0.5}$ scaling of $\Omega_m$ and
+    $P^{0.79}$ scaling of $\Omega_a$. [[TR: There should be a gap between (c) top and bottom.]
     \label{f-det}}
@@
 Both the light shift and Raman Rabi frequency follow a $1/\Delta$ slope as shown in Fig.~\ref{f-det}a, b and include a constant offset that we attribute to coupling to other excited states that are further away in energy.
-The $1/\Delta$ components, due to the nearby $v'=0$ intermediate state, determine $\Omega_m $ and $ \Omega_a $ in Table~\ref{tab:rabi_freqs} from the fit coefficients in Table \ref{tab:f-det:fit}.
+The $1/\Delta$ components, due to the nearby $v'=0$ intermediate state, determine $\Omega_m $ and $ \Omega_a $ in from the fit coefficients, as shown in Table~\ref{tab:f-det:fit}.
 
@@
     $c~(\mathrm{2\pi\times kHz})$&$0.29(2)$&$0.63(4)$&$2.4(2)$\\
-    $d~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$0.115(4)$&$0.275(6)$&$0.95(3)$\\
+    $d~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$0.115(4)$&$0.275(6)$&$0.95(3)$\\ \hline
+    $\Omega_R$ ($2\pi\times$kHz) & & & X.YY \\
+    $\Omega_m$ ($2\pi\times$MHz) & & & 348.3(3) \\
+    $\Omega_a$ ($2\pi\times$kHz) & & & 5.5(2)
   \end{tabular}
   \caption{Fitting results for Fig.~\ref{f-det}(a,b).
+$\Omega_R$ is reported at $-151~\mathrm{GHz}$ detuning from the $v' = 0$ state.
+The coefficients $\Omega_m$ and $\Omega_a$ are in broad agreement with our calculation and their ratio $63$ is near the theory prediction of $78$.
+The measured Rabi rate $\Omega_R$ is ZZ~\% of $\Omega_m \Omega_a/2$ due to interference from further-detuned Raman processes.
     \label{tab:f-det:fit}}
@@
 However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
-Coupled-channel calculations show that the wave-function scaling
+Coupled-channel calculations show that the wavefunction scaling
 is well approximated by $P^{0.29}$ within the range of confinement in our experiment and the expected scaling of $ \Omega_a \propto P^{0.79} $ agrees with the data.
-%At $3.75~\mathrm{mW}$ tweezer power, we measured $ \Omega_m = 2\pi \times 348.3(3)~\mathrm{MHz}$ and $ \Omega_a = 2\pi\times 5.5(2)~\mathrm{MHz}$, resulting in a 
-%The measured $ \Omega_m/\Omega_a$ ratio of $ 63 $ is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
-%Therefore, the matrix element ratio is not the cause of our lower than expected transfer efficiency.
-Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy.
+% At $3.75~\mathrm{mW}$ tweezer power, we measured $ \Omega_m = 2\pi \times 348.3(3)~\mathrm{MHz}$ and $ \Omega_a = 2\pi\times 5.5(2)~\mathrm{MHz}$, resulting in a
+% The measured $ \Omega_m/\Omega_a$ ratio of $ 63 $ is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
+% Therefore, the matrix element ratio is not the cause of our lower than expected transfer efficiency.
+
 % We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
@@
 
-\begin{table}[ht]
-  \centering
-  \begin{tabular}{c|c|c|c|c}
-    $\Omega_R$ & $\Gamma_s$ & $\Omega_m$ & $\Omega_a$ & $\Omega_a/\Omega_m$ \\ 
-    ($2\pi\times$kHz) & ($2\pi\times$kHz) & ($2\pi\times$MHz) & ($2\pi\times$MHz) &  \\ \hline 
-    X.YY & 0.80(4) & 348.3(3) & 5.5(2) & 63(3) \\
-  \end{tabular}
-  \caption{Experimentally determined coefficients at $3.75$~mW tweezer power.
-$\Omega_R$ and $ \Gamma_s $ are reported at $-151~\mathrm{GHz}$ detuning from the $v' = 0$ state.
-The coefficients $\Omega_m$ and $\Omega_a$ are in broad agreement with our calculation and their ratio is near the theory prediction of $78$.
-The measured Rabi rate $\Omega_R$ is ZZ~\% of $\Omega_m \Omega_a/2$ due to interference from further-detuned Raman processes.
-[[TR: Check all mentions of $P=3.75$~mW because they may negelect reduction from 2nd ASE filter.]]}
-  \label{tab:rabi_freqs}
-\end{table}
+% With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
+% We now consider the background effects from other states with larger single-photon detuning.
+% In the Raman Rabi frequency fit,
+% the fitted background is of opposite sign from the Raman Rabi frequency
+% for single-photon detunings red of the $v' = 0 $ transition.
+% Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$
+% at the current detuning.
+% However, this difference is not enough to explain the discrapancy of more than a factor of $10$
+% present in the experiment.
+% Due to the change in sign of the Raman Rabi frequency as a function of detuning
+% when crossing a resonance, the same background will increase the Raman Rabi frequency
+% for positive detunings from the $v' = 0$ transition.
+% Unfortunately, we observe additional nearby excited states
+% belonging to a different electronically excited state at higher frequencies
+% which prevent the blue side of the transition from being be usable for the Raman transition.
 
-% With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
-%We now consider the background effects from other states with larger single-photon detuning.
-%In the Raman Rabi frequency fit,
-%the fitted background is of opposite sign from the Raman Rabi frequency
-%for single-photon detunings red of the $v' = 0 $ transition.
-%Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$
-%at the current detuning.
-%However, this difference is not enough to explain the discrapancy of more than a factor of $10$
-%present in the experiment.
-%Due to the change in sign of the Raman Rabi frequency as a function of detuning
-%when crossing a resonance, the same background will increase the Raman Rabi frequency
-%for positive detunings from the $v' = 0$ transition.
-%Unfortunately, we observe additional nearby excited states
-%belonging to a different electronically excited state at higher frequencies
-%which prevent the blue side of the transition from being be usable for the Raman transition.
+The measured single-photon Rabi frequencies of Table~I are in broad agreement with calculations (see Supplementary Materials).
+Known single-photon scattering rates of Na and Cs atoms together with an independent measurement (via photoassociation spectroscopy) of the $v'=0$ excited state natural linewidth of no more than $50~\mathrm{MHz}$ indicate that single-photon scattering from the molecular or atomic state do not explain the decoherence in Fig.
+3b~\TR{long sentence}.
+Below, we further investigate the loss of coherence.
 
@@
   does not lead to scattering but only decherence.}
-%These results suggest that the decoherence or loss we observe during the Raman transition
-%comes from either a higher background scattering rate of an unknown source
-%or a different intrinsic or technical source for which we have not accounted for.
-\TR{combine this and next paragraph with earlier} The efficiency of the transfer is limited by the short lifetime of the molecular state~(Fig.~\ref{f-lifetime}a) together with a reduction in the Raman Rabi frequency due to intermediate states beyond v'=0 (see Table~~\ref{tab:rabi_freqs}).
-Preliminary experiments and theoretical considerations indicate that the molecular lifetime may be limited by two-photon coupling to the atomic continuum~\TR{Cite YY thesis.}.
-We also observe a decrease in the coherence time by a factor of 2 without laser spectrum filters,
-suggesting that spectral impurity of the laser can be a significant source of scattering.
-Other sources that can contribute to decoherence include
-the stability of the tweezer power and magnetic field.
-Based on the ratio of the Raman Rabi frequency to light shift, shown in Fig.~\ref{f-det}c,
-the requirement on the tweezer power stability is $0.8\mathrm{\%}$ at $3.75~\mathrm{mW}$. We stabilize the power to $0.1\mathrm{\%}$, so this should not be a major source of decoherence.
-Similarly, we measured a Zeeman shift of $42.2(2)~\mathrm{kHz/G}$
-which does not cause significant decoherence from the measured magnetic field
-fluctuation of $\sim1.5~\mathrm{mG}$.~\TR{Mention somewhere that the shape of Fig. 3b Rabi flopping indicates molecular loss, not atomic loss or frequency fluctuation.}
+% These results suggest that the decoherence or loss we observe during the Raman transition
+% comes from either a higher background scattering rate of an unknown source
+% or a different intrinsic or technical source for which we have not accounted for.
+Raman transfer efficiency is limited by the molecular lifetime, together with a reduction in the Raman Rabi frequency due to destructive interference with intermediate states beyond v'=0 (see Table~~\ref{tab:f-det:fit}).
+The lifetime is measured directly by preparing the molecule with a $\pi$-pulse,
+followed after a variable delay by a second dissociating $\pi$-pulse.
+The result in Fig.~\ref{f-lifetime}a shows a molecular lifetime of $0.199(9)~\mathrm{ms}$,
+consistent with the decay of the Rabi oscillation in Fig.~\ref{f-raman}b.
+ Preliminary experiments and theoretical considerations indicate that the molecular lifetime may be limited by two-photon coupling to the atomic continuum~\cite{YichaoYu}.
+Atom loss is shown to be small in Fig.~\ref{f-lifetime} by measuring the one- and
+two-body lifetimes of the atoms directly without the second Raman frequency.
+In principle, destructive interference that reduces the Raman Rabi rate for negative detunings $\Delta$ changes to constructive interference for positive detunings, but additional molecular resonances made the positive region unusable.
+Separately we observe a decrease in coherence by a factor of 2 without laser spectrum filters,
+suggesting that spectral impurity of the laser can be a significant source of loss.
 
-%The scattering rate of the molecule also depends on the tweezer power and detuning,
-%and becomes smaller when the power is lowered.
-%At $0.75~\mathrm{mW}$ tweezer power, we observe a molecule lifetime as long as $1~\mathrm{ms}$.
-%Since the technical noise that can lead to decoherence
-%is not fully characterized in our experiment,
-%we are unable to further identify the sources of the measured scattering rate
-%based on our measured detuning and power dependencies.
+Other potential decoherence sources include
+fluctuations of the tweezer intensity and magnetic field.
+Based on the Rabi frequency ratio in Table~\ref{tab:f-det:fit}
+the requirement on the tweezer intensity stability is $0.8\mathrm{\%}$ at $3.75~\mathrm{mW}$ power.
+We stabilize the power to $0.1\mathrm{\%}$, indicating that in the absence of beam-waist fluctuations, light shift is not a major source of decoherence.
+Similarly, the measured Zeeman shift of $42.2(2)~\mathrm{kHz/G}$
+does not cause significant decoherence for the measured magnetic field
+fluctuation of $1.5~\mathrm{mG}$.
 
-To confirm that the observed loss of Rabi oscillation is not due to the atomic state,
-we measure the two-body scattering rate
-without turning on the second frequency, as shown in Fig.~\ref{f-lifetime}b inset.
-The scattering rate scales as $P^{2.58}$ and is too low to explain the Rabi oscillation decoherence.
-%We have not been able to observe a dependency on the detuning in order to verify whether the scattering process is related to the $v'=0$ state,
-%but the power scaling strongly suggests the existence of an unknown two-photon process.
-%Nevertheless, the absolute scattering rate from the atomic state
-%is much lower than the total scattering rate
-%and is not the limiting factor in this experiment.
+% The scattering rate of the molecule also depends on the tweezer power and detuning,
+% and becomes smaller when the power is lowered.
+% At $0.75~\mathrm{mW}$ tweezer power, we observe a molecule lifetime as long as $1~\mathrm{ms}$.
+% Since the technical noise that can lead to decoherence
+% is not fully characterized in our experiment,
+% we are unable to further identify the sources of the measured scattering rate
+% based on our measured detuning and power dependencies.
+
+%To confirm that the observed loss of Rabi oscillation is not due to the atomic state,
+%we measure the two-body scattering rate
+%without turning on the second frequency, as shown in Fig.~\ref{f-lifetime}b inset.
+%The scattering rate scales as $P^{2.58}$ and is too low to explain the Rabi oscillation decoherence.
+% We have not been able to observe a dependency on the detuning in order to verify whether the scattering process is related to the $v'=0$ state,
+% but the power scaling strongly suggests the existence of an unknown two-photon process.
+% Nevertheless, the absolute scattering rate from the atomic state
+% is much lower than the total scattering rate
+% and is not the limiting factor in this experiment.
 
@@
 Future experiments may benefit from better balancing of the up-leg and down-leg Rabi frequencies, for example by driving to more deeply bound states.
-If possible, destructive interferences that reduce the two-photon Rabi rate should be avoided.
+If possible, destructive interference that reduces the two-photon Rabi rate should be avoided.
 Nonlinear optical effects that limit the molecular state lifetime can also be explored.
@@
 By scaling up to many optical tweezers~\cite{Endres2016, Barredo2018,  PhysRevLett.122.203601}, large arrays with arbitrary geometry of highly controlled molecules can be achieved.
-
+These highly controlled molecules comprise a flexible platform for quantum simulation and quantum computing applications.
+\textcolor{blue}{(End with a sentence on molecules for future quantum applications?)}
 % Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},
@@
 \begin{acknowledgments}
-  We would like to thank Rosario Gonzalez-Ferez, Olivier Dulieu, Bo Gao, and Paul Julienne for discussion and Robert Moszynski for providing theoretical transition dipole moments of NaCs.
+  We thank Rosario Gonzalez-Ferez, Olivier Dulieu, Bo Gao, and Paul Julienne for discussion and Robert Moszynski for providing theoretical transition dipole moments of NaCs.
 This work is supported by the NSF~(PHY-1806595), the AFOSR~(FA9550-19-1-0089), ARO DURIP (W911NF1810194) and the Arnold and Mabel Beckman foundation.
@@
 
+\TR{Mention somewhere that the shape of Fig. 3b Rabi flopping indicates molecular loss, not atomic loss or frequency fluctuation.}
+\TR{Check all ``$P=3.75$~mW'' results because they may negelect reduction from 2nd ASE filter.  Better to quote the reduced power.}
+
 \bibliography{master_ref}

### 2020-12-07 sm.tex
Regenerate PDF, whitespace
Update on Overleaf.

@@
 In order to compare to the theory, we introduce effective $ \Omega_a', \Omega_m', \Gamma_e'$, so that $ \Omega_R = \Omega_a'\Omega_m'/2\Delta $, $\delta = (\Omega_{a}'^2 - \Omega_{m}'^2)/2\Delta $, and $\Gamma_S = \Gamma_e'(\Omega_{a}'^2 + \Omega_{m}'^2)/2\Delta^2 $.
-These effective Rabi frequencies are used to calculate the Rabi frequency ratio and are the quantities reported in the main text when compared to experiment.
+The effective Rabi frequencies for the $v' = 0$ state of $ c^3\Sigma^+_1$ and their ratio are reported in Table~\ref{tab:sm} at $3.75~\mathrm{mW}$ of tweezer power.
+
+% $2\pi \times 15.3~\mathrm{kHz}$
+% $ 2\pi \times 533~\mathrm{Hz}$
+% $2\pi \times 573 ~\mathrm{MHz}$
+% $2\pi \times 7.37 ~\mathrm{MHz}$
+
+\begin{table}[ht]
+  \centering
+  \begin{tabular}{|c|c|} \hline
+  $\Omega_m'$ &  $2\pi \times 573 ~\mathrm{MHz}$ \\
+  $\Omega_a'$ &  $2\pi \times 7.37 ~\mathrm{MHz}$ \\
+  $\Omega_m'/\Omega_a'$ & $ 78 $ \\ \hline
+  \end{tabular}
+  \caption{ The effective Rabi frequencies for the $v' = 0$ state of $c^3\Sigma^+_1$ at $ 3.75~\mathrm{mW}$ of tweezer power. 
+    \label{tab:sm}}
+\end{table}
 

### 2020-12-07 paper.tex
whitespace, regenerate pdf
Update on Overleaf.

@@
 serves as the intermediate state in the Raman scheme,
-and is chosen to minimize photon scattering during Raman Rabi \TR{Is Raman Rabi freq the best term?} oscillations.
+and is chosen to minimize photon scattering during Raman Rabi oscillations.
 To reduce photon scattering and sensitivity to laser intensity noise further,
@@
     (Some mirrors and other optics used for alignment are not included.)
-    The two ASE filters before and after the fibers are also shown.
+    The two ASE filters before and after the fibers are also shown. The laser source is a fiber amplifier seeded by a external cavity diode laser. 
     The red beam path is the $0$-th order of the double pass~(DP) AOM
@@
 Choosing a bound state with similar spin character to the atomic state  minimizes the sensitivity of the transition frequency to magnetic field.
-A suitable state with this character is predicted about 763 MHz below the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ threshold.
+A suitable state with this character is predicted about 763 MHz below the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ threshold and the ratio $\Omega_a/\Omega_m$ increases to about 0.013.
 % The coupled-channel calculations show that this target molecular state has lower overlap with the intermediate state, compared to bound states from other hyperfine combinations.
@@
 % Coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $, with the intermediate state when compared to bound states of the other spin compositions.
-The ratio $\Omega_a/\Omega_m$ increases to about 0.013 when starting from atoms in the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.
 % $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
-Compared to 0.003
-with the other combinations, this relaxes the intensity stability requirement to the percent level.
+Compared to $\Omega_a/\Omega_m \approx 0.003$
+for other combinations, this relaxes the intensity stability requirement to the percent level and enhances the Raman Rabi frequency.
 % Thus, instead of a required intensity stability of $0.3 ~\mathrm{\%} $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5~\mathrm{\%} $.
@@
   \caption{Coherent transfer of atoms to molecules.  The molecular state is dark to the imaging step and corresponds to zero signal.
-    (a) Raman difference frequency scans for different durations showing the resonance.
+    (a) Raman difference frequency scans for various durations showing the resonance as a frequency offset from $770.2$~MHz, near the calculated value of $763$~MHz.
     (b) Raman pulse-length scan on resonance.
@@
     A model is fitted to (a) and (b) to determine
-    both the Raman Rabi frequency and the loss rates.
+    the Raman Rabi frequency and loss rates.
     \emph{Inset:} Geometry and polarization of trap and Raman beam relative to the magnetic field.
-    The beam X.yy~mW beam is focused to a waist of $0.9~\mathrm{\mu m}$
+    The X.yy~mW beam is focused to a waist of $0.9~\mathrm{\mu m}$
     that confines the atoms and molecule.
-    A magnetic field of $B_0=8.83(2)~\mathrm{G}$ along the tweezer polarization
+    A perpendicular $B_0=8.83(2)~\mathrm{G}$ magnetic field 
     defines the quantization axis and the atoms experience predominantly $\pi$-polarized light.
@@
 Raman sideband cooling is then applied to prepare both atoms simultaneously
-in the 3-dimensional motional ground state of their optical tweezers.
-After cooling, the Na and Cs atoms are in the spin state~$\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{f=2,m_f=2}_{\Na}\ket{f=4,m_f=4}_{\Cs}$,
+in the 3-dimensional motional ground state of their optical tweezers, leaving the atoms in the spin state~$\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{f=2,m_f=2}_{\Na}\ket{f=4,m_f=4}_{\Cs}$,
 which has a small scattering length.
-The weak two-atom interaction allows the merging of the two tweezers to be done
-with minimum pertubation so that they remain in the motional ground state.
+The weak two-atom interaction allows merging of the two tweezers with minimum pertubation so that they remain in the motional ground state.
 
 % After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
-Next, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$,
-which has large scattering length,
+Next, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ with a large scattering length
 by performing a Cs spin flip while taking into account
@@
 This is the initial atomic state for Raman transfer.
-This spin flip selectively transfers atoms in the relative motional ground state,
+The spin flip selectively transfers atoms in the relative motional ground state,
 removing any background from atoms in excited motional states
@@
 For the experiment reported here,
-$31\mathrm{\%}$ of our initial two-atom population is transferred.
+$31\mathrm{\%}$ of initial two-atom population is transferred.
 % of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
@@
 % After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
-To perform the Raman transfer of an atom pair to the target weakly bound molecular state,
-we modulate the tweezer beam with a second frequency, as shown in Fig.~\ref{f-beampath}.
+To transfer the atom pair into the target weakly bound molecular state,
+we modulate the tweezer beam with a second frequency near $770$~MHz, as shown in Fig.~\ref{f-beampath}.
 The dual use of the tweezer beam for confinement and Raman transfer not only minimizes photon scattering,
 but also allows a tight focus to minimize the transfer duration.
-Furthermore, two filters, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
-clean the laser spectrum and prevent broadband noise from causing unwanted excitation.
-As shown in Fig.~\ref{f-beampath}, one filter immediately follows the laser, while the second filter precedes the microscope objective for final cleanup of the laser spectrum.
-The filters reduce photon scattering rate by a factor of $2$. While we have not fully characterized the sources
-of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities.
-%After the total tweezer power is set to the desired value,
-%we smoothly ramp down the power of one frequency in the tweezer
-%while simultaneously ramping up the power of the other frequency
-%so that the total tweezer power remains unchanged.
-%Both frequencies are kept on for a specified duration before the process is reversed
-%and the tweezer returns to a single frequency.~\TR{???}
+A tweezer frequency far detuned (by $-151~\mathrm{GHz}$) from the 3 observed rotational~\TR{spectral?} lines at $v' = 0 $ reduces resonant scattering~\cite{Liu2019}.
+%Furthermore, two filters, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
+%clean the laser spectrum and prevent broadband noise from causing unwanted excitation.
+%As shown in Fig.~\ref{f-beampath}, one filter immediately follows the laser, while the second filter precedes the microscope objective for final cleanup of the laser spectrum.
+%The filters reduce photon scattering rate by a factor of $2$ (\textcolor{red}{KW: Since we mention this again later when we explore the causes of our lower than expected transfer efficiency, do we need to mention this reduction here?
+or the possible causes?}).
+While we have not fully characterized the sources
+%of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities.
+% After the total tweezer power is set to the desired value,
+% we smoothly ramp down the power of one frequency in the tweezer
+% while simultaneously ramping up the power of the other frequency
+% so that the total tweezer power remains unchanged.
+% Both frequencies are kept on for a specified duration before the process is reversed
+% and the tweezer returns to a single frequency.~\TR{???}
 
@@
 
-\TR{``We" is overused in this paper and obscures more important subject-object relationships.
-Authorship already implies that ``we" did everything in the paper.} We choose a tweezer frequency far detuned (by $-151~\mathrm{GHz}$) from the 3 observed rotational lines at $v' = 0 $ to reduce resonant scattering~\cite{Liu2019}.
-Guided by the coupled-channel calculations,
-we locate the Raman resonance as shown in Fig.~\ref{f-raman}, which shows a Fourier-limited resonance together with Rabi oscillations between the atomic and molecular states.
+Figure~\ref{f-raman} shows a Fourier-limited resonance together with Rabi oscillations between the atomic and molecular states.
 % (We can maybe add information about the prediction here?)
@@
 % directly detected by our imaging step.
-A decaying Rabi oscillation fitted to the data suggests that
-$69~\mathrm{\%}$ of atoms initially in the relative motional ground state are transferred into the molecular state after a $\pi$ pulse.
-Over $60\%$ of the created molecules are in the motional ground state (both relative motion and center of mass motion), inferred from independent Raman sideband thermometry measurements of the atoms.
-A fit including atomic and molecular losses (see below) yields a Raman Rabi frequency of $2\pi\times3.28(4)~\mathrm{kHz}$.
+A decaying Rabi oscillation with frequency $2\pi\times3.28(4)~\mathrm{kHz}$ fitted to the data suggests that
+$69~\mathrm{\%}$ of atoms initially in the relative motional ground state are transferred into the molecular state after a $\pi$-pulse.
+Over $60\%$ of the molecules are in the motional ground state (both relative and center of mass), inferred from independent Raman sideband thermometry measurements of the atoms.
 
@@
     $d~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$0.115(4)$&$0.275(6)$&$0.95(3)$\\ \hline
-    $\Omega_R$ ($2\pi\times$kHz) & & & X.YY \\
-    $\Omega_m$ ($2\pi\times$MHz) & & & 348.3(3) \\
-    $\Omega_a$ ($2\pi\times$kHz) & & & 5.5(2)
+    $\Omega_R~(\mathrm{2\pi\times kHz})$ & & & X.YY \\
+    $\Omega_m~(\mathrm{2\pi\times MHz})$ & & & 348.3(3) \\
+    $\Omega_a~(\mathrm{2\pi\times kHz})$ & & & 5.5(2)
   \end{tabular}
@@
 The coefficients $\Omega_m$ and $\Omega_a$ are in broad agreement with our calculation and their ratio $63$ is near the theory prediction of $78$.
-The measured Rabi rate $\Omega_R$ is ZZ~\% of $\Omega_m \Omega_a/2$ due to interference from further-detuned Raman processes.
+The measured Rabi rate $\Omega_R$ is ZZ~\% of $\Omega_m \Omega_a/(2\Delta)$ due to interference from further-detuned Raman processes.
     \label{tab:f-det:fit}}
@@
 
-%To confirm that the observed loss of Rabi oscillation is not due to the atomic state,
-%we measure the two-body scattering rate
-%without turning on the second frequency, as shown in Fig.~\ref{f-lifetime}b inset.
-%The scattering rate scales as $P^{2.58}$ and is too low to explain the Rabi oscillation decoherence.
+% To confirm that the observed loss of Rabi oscillation is not due to the atomic state,
+% we measure the two-body scattering rate
+% without turning on the second frequency, as shown in Fig.~\ref{f-lifetime}b inset.
+% The scattering rate scales as $P^{2.58}$ and is too low to explain the Rabi oscillation decoherence.
 % We have not been able to observe a dependency on the detuning in order to verify whether the scattering process is related to the $v'=0$ state,
@@
 \TR{Mention somewhere that the shape of Fig. 3b Rabi flopping indicates molecular loss, not atomic loss or frequency fluctuation.}
+
 \TR{Check all ``$P=3.75$~mW'' results because they may negelect reduction from 2nd ASE filter.  Better to quote the reduced power.}
+
+\TR{``We" is overused in this paper and obscures more important subject-object relationships.  Authorship already implies that ``we" did everything in the paper.}
+
+\TR{Is Raman Rabi freq the best term for $\Omega_R$?}
 

### 2020-12-07 scripts/plot_scaling.jl
Add gap in figure

@@ -322,12 +322,12 @@ ylim([0.14, 0.39])
 ylabel("\$\\Omega_m\$ (\$\\mathrm{2\\pi\\times GHz}\$)")
 setp(ax1.get_xticklabels(), visible=false)
 ax1.tick_params(axis="x", length=0)
-ax1.set_xticks(0.7:0.1:4, minor=true)
+ax1.set_xticks([], minor=true)
 ax1.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 ax1.xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 
 ax2 = fig.add_subplot(212)
-subplots_adjust(hspace=0.0)
+subplots_adjust(hspace=0.018)
 errorbar(omegas.powers[1] ./ 4, omegas.omega_as[1] ./ 1e6,
          omegas.omega_as_unc[1] ./ 1e6, fmt="C0o")
 errorbar(omegas.powers[2] ./ 4, omegas.omega_as[2] ./ 1e6,

### 2020-12-07 paper.tex
Update on Overleaf.

@@
 we choose the initial and final states to balance the two Rabi frequencies as much as possible.
-This system-independent approach creates molecules atom-by-atom with full quantum state control.
+This approach applies to a variety of molecules that can be created atom-by-atom with full quantum state control.
 
@@
 In this idealized treatment, the ratio between the Raman Rabi frequency and the scattering rate is $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, which limits the transfer efficiency into the molecular state.
-At the same time, the intensity-stability requirement is determined by the ratio of Raman Rabi frequency to Stark shift ($\Omega_a/\Omega_m$)~\footnote{There is an additional factor of 2, with both beams at equal power,
+At the same time, the intensity-stability requirement is determined by the ratio of Raman Rabi frequency to light shift ($\Omega_a/\Omega_m$)~\footnote{There is an additional factor of 2, with both beams at equal power,
   to account for the Stark shift caused by both beams.}.
@@
 %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
-To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred \TR{Mention 2-photon here?}.
 %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
@@
 but also allows a tight focus to minimize the transfer duration.
-A tweezer frequency far detuned (by $-151~\mathrm{GHz}$) from the 3 observed rotational~\TR{spectral?} lines at $v' = 0 $ reduces resonant scattering~\cite{Liu2019}.
+A tweezer frequency far detuned (by $-151~\mathrm{GHz}$) from $v' = 0 $ ($<50$~MHz natural linewidth) reduces resonant scattering~\cite{Liu2019}.
 %Furthermore, two filters, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
@@
   \caption{
-    (a) Direct measurement of molecule lifetime with about $3.75~\mathrm{mW}$ optical power.
+    (a) Direct measurement of molecule lifetime with about $X.XX~\mathrm{mW}$ optical power.
     Molecule survival is detected by dissociating back to atoms via a second Raman transition.
@@
     (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
-    in a trap of depth $3.75~\mathrm{mW}$ caused by off-resonance photoassociation.
+    in a trap of depth $X.XX~\mathrm{mW}$ caused by off-resonance photoassociation.
     This is used to improve the fitting of the Raman transfer data.
@@
     $d~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$0.115(4)$&$0.275(6)$&$0.95(3)$\\ \hline
-    $\Omega_R~(\mathrm{2\pi\times kHz})$ & & & X.YY \\
+    $\Omega_R~(\mathrm{2\pi\times kHz})$ & 0.49(2) & 1.18(3) & 3.97(9) \\
     $\Omega_m~(\mathrm{2\pi\times MHz})$ & & & 348.3(3) \\
@@
 $\Omega_R$ is reported at $-151~\mathrm{GHz}$ detuning from the $v' = 0$ state.
-The coefficients $\Omega_m$ and $\Omega_a$ are in broad agreement with our calculation and their ratio $63$ is near the theory prediction of $78$.
+The coefficients $\Omega_m$ and $\Omega_a$ are in broad agreement with our calculation and their ratio at $3.75~\mathrm{mW}$ is $0.016$, which is near the theory prediction of $0.013$.
 The measured Rabi rate $\Omega_R$ is ZZ~\% of $\Omega_m \Omega_a/(2\Delta)$ due to interference from further-detuned Raman processes.
@@
 The measured single-photon Rabi frequencies of Table~I are in broad agreement with calculations (see Supplementary Materials).
-Known single-photon scattering rates of Na and Cs atoms together with an independent measurement (via photoassociation spectroscopy) of the $v'=0$ excited state natural linewidth of no more than $50~\mathrm{MHz}$ indicate that single-photon scattering from the molecular or atomic state do not explain the decoherence in Fig.
+From the full calculation of the expected scattering rate including all excited states
+%Known single-photon scattering rates of Na and Cs atoms together with an independent measurement (via photoassociation spectroscopy) of the $v'=0$ excited state natural linewidth of no more than $50~\mathrm{MHz}$ indicate that single-photon scattering from the molecular or atomic state do not explain the decoherence in Fig.
 3b~\TR{long sentence}.
@@
 By scaling up to many optical tweezers~\cite{Endres2016, Barredo2018,  PhysRevLett.122.203601}, large arrays with arbitrary geometry of highly controlled molecules can be achieved.
-These highly controlled molecules comprise a flexible platform for quantum simulation and quantum computing applications.
+These molecules comprise a flexible platform for quantum simulation and quantum computing applications.
 \textcolor{blue}{(End with a sentence on molecules for future quantum applications?)}
@@
 
+\TR{Broader statement on experimentally possible vs. theoretical detunings.}
+
 \bibliography{master_ref}

### 2020-12-07 scripts/plot_raman.jl
Update theory figure

@@ -26,7 +26,8 @@ end
 const prefix = joinpath(@__DIR__, "../imgs", "raman")
 
 # fig = figure(figsize=[1.11, 1.5] * 4.8)
-fig = figure()
+# fig = figure()
+fig = figure(figsize=[6.4, 2.6])
 
 # ax1 = fig.add_subplot(311)
 # plot(data[:, 1] .- 339724.57, abs.(data[:, 2] ./ 2π / 1000), "C1--",
@@ -75,7 +76,7 @@ xlim([-300, 300])
 ylim([0.02, 90])
 yscale("log")
 yticks([0.1, 1, 10], ["0.1", "1", "10"])
-legend(fontsize=13.88, loc="center left", bbox_to_anchor=(0.0, 0.6),
+legend(fontsize=13.88, loc="center left", bbox_to_anchor=(0.0, 0.67),
        handlelength=1, handletextpad=0.3)
 ax3.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 grid()

### 2020-12-07 scripts/plot_raman_full.jl

@@ -45,7 +45,7 @@ plot(data[:, 1] ./ 1000, abs.(data[:, 4] ./ 2π / 1000), "C1", label="\$\\Gamma_
 # for v in es
 #     axvline(v * 100, color="C3", linewidth=5)
 # end
-ylabel("\$2\\pi\\cdot \\mathrm{kHz}\$")
+ylabel("\$2\\pi\\times \\mathrm{kHz}\$")
 xlabel("Raman Single-Photon Frequency (THz)")
 yscale("log")
 ylim([0.12, 400])
@@ -55,5 +55,34 @@ legend(ncol=2, loc="lower center", bbox_to_anchor=(0.5, 0.95), frameon=false)
 gca().yaxis.set_label_coords(-0.034, 0.55)
 xlim([287, 340])
 NaCsPlot.maybe_save("$(prefix)")
+
+figure(figsize=[13.8, 2.6])
+plot(data2[:, 1] ./ 1000, abs.(data2[:, 4] ./ 2π / 1000), "r", linewidth=4, alpha=0.7, ls=":")
+plot(data[:, 1] ./ 1000, abs.(data[:, 4] ./ 2π / 1000), "r", alpha=0.4)
+axvline(288.625081, color="C0", ls="--", linewidth=2)
+axvline(339.724570, color="C0", ls="--", linewidth=2)
+text(288.625081, 10, "v'=0", rotation=90, va="center", ha="right", color="C0", fontsize=16)
+text(339.724570, 3, "v'=40", rotation=90, va="center", ha="right", color="C0", fontsize=16)
+# plot(data[:, 1] ./ 1000, abs.(data[:, 2] ./ data[:, 4]), "C2")
+# es = [2.8863, 2.9026, 2.9184, 2.9339, 2.9492, 2.9643, 2.9792, 2.9939, 3.0084, 3.0227,
+#       3.0369, 3.0510, 3.0649, 3.0787, 3.0925, 3.1062, 3.1198, 3.1334, 3.1469, 3.1603,
+#       3.1736, 3.1868, 3.1999, 3.2129, 3.2258, 3.2385, 3.2511, 3.2635, 3.2757, 3.2876,
+#       3.2993, 3.3106, 3.3215, 3.3322, 3.3425, 3.3525, 3.3621, 3.3714, 3.3803, 3.3889,
[…]

### 2020-12-07 scripts/plot_wavefunction.jl

@@ -33,9 +33,9 @@ const data42 = read_csv_compressed(fname42, ',', Float64)
 
 const prefix = joinpath(@__DIR__, "../imgs", "wavefunction")
 
-figure()
-plot(data42[:, 1], data42[:, 2] .* 2e6, "C2", label="Na(2,2) Cs(4,4)")
+fig = figure(figsize=[6.4, 2.6])
 plot(data32[:, 1], data32[:, 2] .* 2e6, "C1", label="Na(2,2) Cs(3,3)")
+plot(data42[:, 1], data42[:, 2] .* 2e6, "C2", label="Na(2,2) Cs(4,4)")
 plot(data31[:, 1], data31[:, 2] .* 2e6, "C3--", label="Na(1,1) Cs(3,3)")
 axvline(100, color="C0", ls="dashed", linewidth=3)
 grid()

### 2020-12-07 paper.tex
Update on Overleaf.

@@
   through an optical Raman transition.
-  The Raman scheme uses a deeply bound electronic excited intermediate state
+  The Raman technique uses a deeply bound electronic excited intermediate state
   to achieve a large transition dipole moment while reducing photon scattering.
@@
 because of the small wavefunction overlap between the free-atom and molecular states
-and the release of a large amount of binding energy.
+and the release of large binding energy.
 A widely used method of overcoming these challenges is to associate atom pairs
@@
 are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012},
-and $^{87}$Rb$^{85}$Rb,
-where there are molecular states bound by $1-2~\mathrm{MHz}$~\cite{He331}.
+and $^{87}$Rb$^{85}$Rb with molecular states bound by only $1-2~\mathrm{MHz}$~\cite{He331}.
 With these requirements, molecules involving non-magnetic atoms
@@
 as shown in Fig.~\ref{f-theory}a.
-The scheme does not rely on a Feshbach resonance,
-molecular states bound by a few~MHz, or a narrow excited state.
+The technique does not rely on a Feshbach resonance,
+molecular states bound by a only few~MHz, or a narrow excited state.
 The resulting single molecule is in a well-defined internal quantum state
@@
 A vibrational state of the electronic excited state $\mathrm{c^3\Sigma^+}(\Omega = 1)$
-serves as the intermediate state in the Raman scheme,
+serves as the intermediate state in the Raman technique,
 and is chosen to minimize photon scattering during Raman Rabi oscillations.
@@
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
-The transfer Raman Rabi Rate is given by $\Omega_a\Omega_m / (2\Delta)$~\cite{Wineland2003}.
+The transfer Raman Rabi frequency is given by $\Omega_a\Omega_m / (2\Delta)$~\cite{Wineland2003}.
 % , is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
@@
 %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
-%However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
+% However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
 
@@
 % In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
-\begin{figure}[ht!]
-  \includegraphics[width=0.48\textwidth]{imgs/fig-raman.pdf}
-  \caption{Coherent transfer of atoms to molecules.  The molecular state is dark to the imaging step and corresponds to zero signal.
-    (a) Raman difference frequency scans for various durations showing the resonance as a frequency offset from $770.2$~MHz, near the calculated value of $763$~MHz.
-    (b) Raman pulse-length scan on resonance.
-    A decaying Rabi oscillation shows the coherence of
-    the Raman transfer process.
-    A model is fitted to (a) and (b) to determine
-    the Raman Rabi frequency and loss rates.
-    \emph{Inset:} Geometry and polarization of trap and Raman beam relative to the magnetic field.
-    The X.yy~mW beam is focused to a waist of $0.9~\mathrm{\mu m}$
-    that confines the atoms and molecule.
-    A perpendicular $B_0=8.83(2)~\mathrm{G}$ magnetic field 
-    defines the quantization axis and the atoms experience predominantly $\pi$-polarized light.
-    \label{f-raman}}
-\end{figure}
 
@@
 The spin flip selectively transfers atoms in the relative motional ground state,
-removing any background from atoms in excited motional states
+removing any background from atoms in excited states of relative motion
 \footnote{This interaction shift is larger than the differential axial trapping frequency
@@
 $31\mathrm{\%}$ of initial two-atom population is transferred.
+Of this population, over $60\%$ is in the ground state of center of mass motion, inferred from Raman sideband thermometry~\cite{Zhang2020,He331}.
+%center-of-mass motional ground state.
 % of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
@@
 
+\begin{figure}[t!]
+  \includegraphics[width=0.48\textwidth]{imgs/fig-raman.pdf}
+  \caption{Coherent transfer of atoms to molecules.  The molecular state is dark to the imaging step and corresponds to zero signal.
+    (a) Raman difference frequency scans for various durations showing the resonance as a frequency offset from $770.2$~MHz, near the calculated value of $763$~MHz.
+    (b) Raman pulse-length scan on resonance.
+    A decaying Rabi oscillation shows the coherence of
+    the Raman transfer process.
+    A model is fitted to (a) and (b) to determine
+    the Raman Rabi frequency and loss rates.
+    \emph{Inset:} Geometry and polarization of trap and Raman beam relative to the magnetic field.
+    The X.yy~mW beam is focused to a waist of $0.9~\mathrm{\mu m}$
+    that confines the atoms and molecule.
+    A perpendicular $B_0=8.83(2)~\mathrm{G}$ magnetic field
+    defines the quantization axis and the atoms experience predominantly $\pi$-polarized light.
+    \label{f-raman}}
+\end{figure}
 %% Transfer scheme
@@
 A tweezer frequency far detuned (by $-151~\mathrm{GHz}$) from $v' = 0 $ ($<50$~MHz natural linewidth) reduces resonant scattering~\cite{Liu2019}.
-%Furthermore, two filters, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
-%clean the laser spectrum and prevent broadband noise from causing unwanted excitation.
-%As shown in Fig.~\ref{f-beampath}, one filter immediately follows the laser, while the second filter precedes the microscope objective for final cleanup of the laser spectrum.
-%The filters reduce photon scattering rate by a factor of $2$ (\textcolor{red}{KW: Since we mention this again later when we explore the causes of our lower than expected transfer efficiency, do we need to mention this reduction here?
+% Furthermore, two filters, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
+% clean the laser spectrum and prevent broadband noise from causing unwanted excitation.
+% As shown in Fig.~\ref{f-beampath}, one filter immediately follows the laser, while the second filter precedes the microscope objective for final cleanup of the laser spectrum.
+% The filters reduce photon scattering rate by a factor of $2$ (\textcolor{red}{KW: Since we mention this again later when we explore the causes of our lower than expected transfer efficiency, do we need to mention this reduction here?
 or the possible causes?}).
 While we have not fully characterized the sources
-%of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities.
+% of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities.
 % After the total tweezer power is set to the desired value,
@@
 
-\begin{figure}[t!]
-  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
-  \caption{
-    (a) Direct measurement of molecule lifetime with about $X.XX~\mathrm{mW}$ optical power.
-    Molecule survival is detected by dissociating back to atoms via a second Raman transition.
-    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
-    measured from the Raman transition data.
-    Inset: pulse sequence for the lifetime measurement.
-    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
-    in a trap of depth $X.XX~\mathrm{mW}$ caused by off-resonance photoassociation.
-    This is used to improve the fitting of the Raman transfer data.
-    Inset: Atomic scattering rate scales as
-    $P_\textrm{tweezer}^{2.58}\times\!2\pi\!\times29.3(17)~\mathrm{mHz/mW^{2.58}}$ on a log-log scale;
-    this is consistent with a two-photon scattering process.
-    We have not measured a clear dependency of the loss rate on the tweezer detuning.
-    \label{f-lifetime}}
-\end{figure}
-
-Figure~\ref{f-raman} shows a Fourier-limited resonance together with Rabi oscillations between the atomic and molecular states.
-% (We can maybe add information about the prediction here?)
-%% Prediction
-% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state.
-The ground molecular state has not been observed previously in experimentally.
-Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state.
-Theory prediction was at $770.1 MHz$.
-% The background level of $31~\mathrm{\%}$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
-% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence.
-% directly detected by our imaging step.
-A decaying Rabi oscillation with frequency $2\pi\times3.28(4)~\mathrm{kHz}$ fitted to the data suggests that
-$69~\mathrm{\%}$ of atoms initially in the relative motional ground state are transferred into the molecular state after a $\pi$-pulse.
-Over $60\%$ of the molecules are in the motional ground state (both relative and center of mass), inferred from independent Raman sideband thermometry measurements of the atoms.
-
-\begin{figure*}
+\begin{figure*}[t!]
   \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
@@
     $b_P$ and $d_P$ on a log-log scale showing approximate $P^{0.5}$ scaling of $\Omega_m$ and
-    $P^{0.79}$ scaling of $\Omega_a$. [[TR: There should be a gap between (c) top and bottom.]
+    $P^{0.79}$ scaling of $\Omega_a$. 
     \label{f-det}}
 \end{figure*}
+
+Figure~\ref{f-raman} shows a Fourier-limited resonance together with Rabi oscillations between the atomic and molecular states.
+% (We can maybe add information about the prediction here?)
+%% Prediction
+% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state.
+The ground molecular state has not been observed previously in experimentally.
+Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state.
+Theory prediction was at $770.1 MHz$.
+% The background level of $31~\mathrm{\%}$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
+% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence.
+% directly detected by our imaging step.
+A decaying Rabi oscillation with frequency $2\pi\times3.28(4)~\mathrm{kHz}$ fitted to the data suggests that
+$69~\mathrm{\%}$ of atoms are transferred into the molecular state after a $\pi$-pulse with the majority of molecules in the ground state of motion. 
+%Over $60\%$ of the molecules are in the motional ground state (both relative and center of mass), inferred from independent Raman sideband thermometry measurements of the atoms.
 
@@
 The measured single-photon Rabi frequencies of Table~I are in broad agreement with calculations (see Supplementary Materials). 
-From the full calculation of the expected scattering rate including all excited states
-%Known single-photon scattering rates of Na and Cs atoms together with an independent measurement (via photoassociation spectroscopy) of the $v'=0$ excited state natural linewidth of no more than $50~\mathrm{MHz}$ indicate that single-photon scattering from the molecular or atomic state do not explain the decoherence in Fig.
+The full calculation of the expected scattering rate of the molecular and atomic state including all excited states does not explain the decoherence in Fig.~\ref{f-raman}b. 
+% Known single-photon scattering rates of Na and Cs atoms together with an independent measurement (via photoassociation spectroscopy) of the $v'=0$ excited state natural linewidth of no more than $50~\mathrm{MHz}$ indicate that single-photon scattering from the molecular or atomic state do not explain the decoherence in Fig.
 3b~\TR{long sentence}.
 Below, we further investigate the loss of coherence.
-
-\todo{change scattering to decoherence? since the fluctuation of light shift
-  does not lead to scattering but only decherence.}
+%\todo{change scattering to decoherence? since the fluctuation of light shift
+%  does not lead to scattering but only decherence.}
 % These results suggest that the decoherence or loss we observe during the Raman transition
@@
 % or a different intrinsic or technical source for which we have not accounted for.
-Raman transfer efficiency is limited by the molecular lifetime, together with a reduction in the Raman Rabi frequency due to destructive interference with intermediate states beyond v'=0 (see Table~~\ref{tab:f-det:fit}).
+From experimental measurements, the Raman transfer efficiency is limited by the molecular lifetime, together with a reduction in the Raman Rabi frequency due to destructive interference with intermediate states beyond v'=0 (see Table~~\ref{tab:f-det:fit}).
 The lifetime is measured directly by preparing the molecule with a $\pi$-pulse,
@@
 
+\begin{figure}[t!]
+  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
+  \caption{
+    (a) Direct measurement of molecule lifetime with about $X.XX~\mathrm{mW}$ optical power.
+    Molecule survival is detected by dissociating back to atoms via a second Raman transition.
+    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
+    measured from the Raman transition data.
+    Inset: pulse sequence for the lifetime measurement.
+    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
+    in a trap of depth $X.XX~\mathrm{mW}$ caused by off-resonance photoassociation.
+    This is used to improve the fitting of the Raman transfer data.
+    Inset: Atomic scattering rate scales as
+    $P_\textrm{tweezer}^{2.58}\times\!2\pi\!\times29.3(17)~\mathrm{mHz/mW^{2.58}}$ on a log-log scale;
+    this is consistent with a two-photon scattering process.
+    We have not measured a clear dependency of the loss rate on the tweezer detuning.
+    \label{f-lifetime}}
+\end{figure}
 Other potential decoherence sources include
@@
 These molecules comprise a flexible platform for quantum simulation and quantum computing applications.
-\textcolor{blue}{(End with a sentence on molecules for future quantum applications?)}
+%\textcolor{blue}{(End with a sentence on molecules for future quantum applications?)}
 % Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},
@@
 
-\TR{Mention somewhere that the shape of Fig. 3b Rabi flopping indicates molecular loss, not atomic loss or frequency fluctuation.}
+\TR{Mention somewhere that the shape of Fig. 3b Rabi flopping indicates loss, not frequency fluctuation.}
 

### 2020-12-07 imgs/fig-lifetime.tex
squeeze figure...

@@
-\documentclass{standalone}
+\documentclass[border={-3pt -6pt -4pt -4pt}]{standalone} % left bottom right top
 \usepackage{tikz}
@@
   \node at (0, 0) {\includegraphics[width=7.6958cm]{exp_data_norm_m_t.pdf}};
-  \node at (-2.35, 1.7) {\footnotesize (\textbf{a})};
+  \node at (-2.4, 1.2) {\footnotesize (\textbf{a})};
 
+  \begin{scope}[shift={(0, 0.1)}]
     \node at (0.77, 0.5) {$t_{\mathrm{hold}}$};
@@
     \draw[->,>=stealth,line width=1] (-0.5, 0.2) -- (2, 0.2);
+  \end{scope}
 
-  \node at (0, -3.9) {\includegraphics[width=7.6958cm]{exp_data_norm_a_t.pdf}};
-  \node at (-2.35, 1.5 - 3.9) {\footnotesize (\textbf{b})};
+  \node at (0, -2.7) {\includegraphics[width=7.6958cm]{exp_data_norm_a_t.pdf}};
+  \node at (-2.4, 1.2 - 2.7) {\footnotesize (\textbf{b})};
   % strength = 2pi 29.3(17) mHz/mW^2.58
-  \node at (0.85, -3.25) {\includegraphics[width=4.6175cm]{atomic_loss_scaling_inset.pdf}};
+  \node at (0.8, -2.25) {\includegraphics[width=4.6175cm]{atomic_loss_scaling_inset.pdf}};
 \end{tikzpicture}

### 2020-12-07 scripts/plot_atomic_loss_scaling.jl

@@ -39,10 +39,10 @@ const prefix = joinpath(@__DIR__, "../imgs", "atomic_loss_scaling")
 # ax.xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 # ax.set_xticks(3:16, minor=true)
 # xlabel("Tweezer Power (mW)")
-# ylabel("\$\\Gamma_{atom} (2\\pi\\times \\mathrm{Hz})\$")
+# ylabel("\$\\Gamma_{\\mathrm{atom}} (2\\pi\\times \\mathrm{Hz})\$")
 # NaCsPlot.maybe_save("$(prefix)")
 
-figure(figsize=[4.8, 3.6] .* 1.08792)
+figure(figsize=[4.8, 3.6 * 0.7] .* 1.08792)
 ax = gca()
 bg = matplotlib.patches.Rectangle((0.625, 0.31), 3.625, 39.69, facecolor="white", alpha=0.9)
 ax.add_patch(bg)
@@ -58,7 +58,7 @@ yticks([1, 3, 10, 30], ["1", "3", "10", "30"])
 ax.xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 ax.set_xticks(0.7:0.1:4, minor=true)
 xlabel("Tweezer Power (mW)", fontsize=17)
-ylabel("\$\\Gamma_{atom} (2\\pi\\times \\mathrm{Hz})\$", fontsize=17)
+ylabel("\$\\Gamma_{\\mathrm{atom}} (2\\pi\\times \\mathrm{Hz})\$", fontsize=17)
 tight_layout()
 NaCsPlot.maybe_save("$(prefix)_inset")
 

### 2020-12-07 scripts/plot_exp_data.jl

@@ -338,7 +338,7 @@ xlabel("Atom Hold Time (ms)")
 ylabel("Two-Body Survival")
 NaCsPlot.maybe_save("$(prefix)_a_t")
 
-figure(figsize=[7.2, 5.4] .* 1.26042)
+figure(figsize=[7.2, 5.4 * 0.67] .* 1.26042)
 NaCsPlot.plot_survival_data(data_pa_m, 1 / param_pa[1], fmt="C0o")
 plot(plot_pa_time, model_exp(plot_pa_time, param_pa) ./ param_pa[1], "C0-")
 # text(7, 0.12 / param_pa[1], "\$\\tau_{atom}=$(1 / uncs_1[5])\\ \\mathrm{ms}\$", color="C0")
@@ -362,7 +362,7 @@ xlabel("Molecule Hold Time (ms)")
 ylabel("Two-Body Survival")
 NaCsPlot.maybe_save("$(prefix)_m_t")
 
-figure(figsize=[7.2, 5.4] .* 1.26042)
+figure(figsize=[7.2, 5.4 * 0.67] .* 1.26042)
 NaCsPlot.plot_survival_data(data_nacs_m[1:end - 1], scale_ramsey, fmt="C0o")
 plot(plot_m_time, model_ramsey(plot_m_time, param_ramsey) .* scale_ramsey, "C0-")
 # text(0.218, 0.07 * scale_ramsey,

### 2020-12-07 paper.tex
Update on Overleaf.

@@
 To reduce photon scattering and sensitivity to laser intensity noise further,
-we choose the initial and final states to balance the two Rabi frequencies as much as possible.
+we choose the initial and final states that balance the two Rabi frequencies as much as possible.
 This approach applies to a variety of molecules that can be created atom-by-atom with full quantum state control.
@@
 by the idealized three-level system shown in Fig.~\ref{f-theory}a,
-where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies $\Omega_a$ and $\Omega_m$ with one-photon detuning $ \Delta $, and all Rabi frequencies are population oscillation frequencies.
+where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies $\Omega_a$ and $\Omega_m$, one-photon detuning $ \Delta $, and all Rabi frequencies are population oscillation frequencies.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
@@
 % $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
-Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced ($\Omega_a/\Omega_m \ll 1$) %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
+Unlike Raman transitions in atoms, the one-photon Rabi frequencies are greatly imbalanced ($\Omega_a/\Omega_m \ll 1$) %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
 due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
 and scattering losses are dominated by the final state.
-Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning $ \Delta $ of $80$ to $200$~GHz, causing the target molecular state to scatter both beams nearly equally with a total rate $ \Gamma_e \Omega_m^2 / (2\Delta^2)$, where $ \Gamma_e $ is the excited-state linewidth~\footnote{The two beams have equal power to maximize the Raman Rabi rate at fixed total power, resulting in a factor of 2 for scattering two beams.}.
+Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning of $80$ to $200$~GHz, causing the target molecular state to scatter both beams nearly equally with a total rate $ \Gamma_e \Omega_m^2 / (2\Delta^2)$, where $ \Gamma_e $ is the excited-state linewidth~\footnote{The two beams have equal power to maximize the Raman Rabi rate at fixed total power, resulting in a factor of 2 for scattering two beams.}.
 In this idealized treatment, the ratio between the Raman Rabi frequency and the scattering rate is $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, which limits the transfer efficiency into the molecular state.
@@
 of the excited electronic state and the atomic continuum.
-The total scattering rate and Raman Rabi rate become a sum of the scattering rates
-and Raman Rabi rates over all possible intermediate states.
+Then the scattering and Raman Rabi rates are sums over all possible intermediate states.
 As there is large overlap between the target molecular state and weakly bound excited states, intermediate states that are closer to the dissociation threshold result in a large scattering rate.
@@
 A tweezer frequency far detuned (by $-151~\mathrm{GHz}$) from $v' = 0 $ ($<50$~MHz natural linewidth) reduces resonant scattering~\cite{Liu2019}.
-% Furthermore, two filters, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
-% clean the laser spectrum and prevent broadband noise from causing unwanted excitation.
-% As shown in Fig.~\ref{f-beampath}, one filter immediately follows the laser, while the second filter precedes the microscope objective for final cleanup of the laser spectrum.
+Furthermore, two filters, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
+ clean the laser spectrum and prevent broadband noise from causing unwanted excitation.
+ As shown in Fig.~\ref{f-beampath}, one filter immediately follows the laser, while the second filter precedes the focusing objective for final cleanup of the laser spectrum.
 % The filters reduce photon scattering rate by a factor of $2$ (\textcolor{red}{KW: Since we mention this again later when we explore the causes of our lower than expected transfer efficiency, do we need to mention this reduction here?

### 2020-12-07 paper.tex
Update on Overleaf.

@@
 consistent with the decay of the Rabi oscillation in Fig.~\ref{f-raman}b.
+
 Preliminary experiments and theoretical considerations indicate that the molecular lifetime may be limited by two-photon coupling to the atomic continuum~\cite{YichaoYu}.
@@
 two-body lifetimes of the atoms directly without the second Raman frequency.
-In principle, destructive interference that reduces the Raman Rabi rate for negative detunings $\Delta$ changes to constructive interference for positive detunings, but additional molecular resonances made the positive region unusable.
+In principle, destructive interference that reduces the Raman Rabi rate for negative detunings $\Delta$ changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.
 Separately we observe a decrease in coherence by a factor of 2 without laser spectrum filters,
-suggesting that spectral impurity of the laser can be a significant source of loss.
+suggesting that spectral impurity of the laser can be a significant source of loss.   While we have not fully characterized the sources
+of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities.
 

### 2020-12-07 paper.tex
Update fig 1 caption and reference

@@
     by $\Delta$ in order to suppress scattering during the transfer.
-    (b) Comparison between weakly-bound and deeply-bound intermediate excited state
+    (b) Full calculation of the scattering rate as a function of the single-photon frequency
+    including all vibrational states of $\mathrm{c^3\Sigma^+(\Omega = 1)}$
+    and the atomic continuum.
+    The assumed excited-state linewidth for all molecular lines is $50~\text{MHz}$.
+    The red line shows the contribution that comes only from the near-threshold states.
+    (c) Comparison between weakly-bound and deeply-bound intermediate excited state
     for the Raman transition.
@@
     compared to the weakly bound excited state (orange lines $v'=40$) at a most detuning.
-    (c) Enhancement of the short-range wavefunction.
+    (d) Enhancement of the short-range wavefunction.
     The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
@@
 can be larger for more deeply bound states compared to weakly bound states
-at a cost of a smaller transfer rate $\Omega_R$, as shown in Fig.~\ref{f-theory}b;
+at a cost of a smaller transfer rate $\Omega_R$, as shown in Fig.~\ref{f-theory}c;
 see Supplementary Material for details.
@@
 For such states, the amplitude of the relative atomic wavefunction is substantially enhanced
-at short range, as shown in Fig.~\ref{f-theory}c.
+at short range, as shown in Fig.~\ref{f-theory}d.
 % The increase in the coupling is proportional to (quote/cite Olive's equation?).
@@
 $69~\mathrm{\%}$ of atoms are transferred into the molecular state after a $\pi$-pulse with the majority of molecules in the ground state of motion.
-%Over $60\%$ of the molecules are in the motional ground state (both relative and center of mass), inferred from independent Raman sideband thermometry measurements of the atoms.
+% Over $60\%$ of the molecules are in the motional ground state (both relative and center of mass), inferred from independent Raman sideband thermometry measurements of the atoms.
 
@@
 Below, we further investigate the loss of coherence.
-%\todo{change scattering to decoherence? since the fluctuation of light shift
+% \todo{change scattering to decoherence? since the fluctuation of light shift
 % does not lead to scattering but only decherence.}

### 2020-12-07 paper.tex
Update on Overleaf.
Mention resonance frequency fit

@@
   \caption{Coherent transfer of atoms to molecules.  The molecular state is dark to the imaging step and corresponds to zero signal.
-    (a) Raman difference frequency scans for various durations showing the resonance as a frequency offset from $770.2$~MHz, near the calculated value of $763$~MHz.
+    (a) Raman difference frequency scans for various durations
+    showing the resonance as the detuning from
+    the fitted resonance at $770.5715(1)$~MHz, near the calculated value of $763$~MHz.
     (b) Raman pulse-length scan on resonance.

### 2020-12-08 paper.tex
Update on Overleaf.

@@
   \includegraphics[width=\textwidth]{imgs/fig-theory.pdf}
-  \caption{Optical creation of single molecule from single atoms in tweezer.
+  \caption{Optical creation of single molecule from single atoms in an optical tweezer.
     (a) Schematic of the optical transition from an atom pair to a weakly bound molecule.
@@
     (b) Full calculation of the scattering rate as a function of the single-photon frequency
-    including all vibrational states of $\mathrm{c^3\Sigma^+(\Omega = 1)}$
+    including all vibrational states of 8 excited state potentials
     and the atomic continuum.
     The assumed excited-state linewidth for all molecular lines is $50~\text{MHz}$.
-    The red line shows the contribution that comes only from the near-threshold states.
+    The dotted red line shows the contribution that comes only from the near-threshold states, which approximately scales as $1/\Delta_{\mathrm{thresh}}^2$.
     (c) Comparison between weakly-bound and deeply-bound intermediate excited state
     for the Raman transition.
-    The deeply bound excited state (blue lines $v'=0$)
+    The deeply bound excited state (blue line $v'=0$)
     has a larger ratio of Raman Rabi frequency to scattering rate
-    compared to the weakly bound excited state (orange lines $v'=40$) at a most detuning.
+    compared to the weakly bound excited state (orange line $v'=40$) at a best detuning.
     (d) Enhancement of the short-range wavefunction.
@@
   \caption{
-    Beampath for generating the frequency for Raman transition in the tweezer.
+    Beampath for generating two frequencies in the tweezer for the Raman transition
     (Some mirrors and other optics used for alignment are not included.)
-    The two ASE filters before and after the fibers are also shown. The laser source is a fiber amplifier seeded by a external cavity diode laser.
-    The red beam path is the $0$-th order of the double pass~(DP) AOM
-    which is used for the tweezer.
-    When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
-    (blue beam path) which generates the required frequency different to drive
-    the Raman transition. The two frequencies are recombined on the DP AOM.
-    The $0$-th order light is shifted by another single pass~(SP) AOM
-    running on a different frequency before recombining.
-    Without this AOM, the leak light from the DP AOM will be at the same frequency
-    as the $0$-th order light which can cause a significant power fluctuation
-    due to interference.
-    The experiment typically start with the SP AOM on and the DP AOM off.
-    When driving the Raman transition, the powers on both AOMs are ramped simultaneously
-    to achieve the desired power at both frequencies.
+    Two ASE filters, one directly after the laser source and one after both optical fibers, are used. The laser source is a fiber amplifier seeded by a external cavity diode laser.
+    The red beam path is the $0$-th order of the double pass~(DP) AOM which is used at all times. 
+    The blue beam path is the $1$-st order of the DP AOM, and generates the second frequency required to drive the Raman transition.
+    %When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
+    %(blue beam path) which generates the required frequency different to drive
+    %the Raman transition. 
+    %The two frequencies are recombined on the DP AOM.
+    The $0$-th order light is shifted by another single pass~(SP) AOM before recombining, which ensures that it will not interfere with the leak light from the DP AOM, resulting in power fluctuations.
+    %be at the same frequency
+    %as the $0$-th order light which can cause a significant power fluctuation
+    %due to interference.
+    The experiment typically starts with the SP AOM on and the DP AOM off.
+    When driving the Raman transition, the RF powers for both AOMs are ramped simultaneously
+    to achieve the desired power at both frequencies, while keeping the total power fixed. 
     \label{f-beampath}
@@
 % in large incoherence and loss to other molecular states.
-This scattering is approximately proportional to $1/\delta_{\mathrm{thresh}}^2$,
-where $\delta_{\mathrm{thresh}}$ is the detuning from the dissociation threshold,
-which is smaller for intermediate states that are deeply bound \footnote{See Supplementary Material}.
-\TR{Cite supplement or maybe Fig.
-S1 can go into Fig.
-1b since it shows $\Gamma_s\sim \delta_{thresh}^{-2}$ nicely.}.
+This scattering is approximately proportional to $1/\Delta_{\mathrm{thresh}}^2$,
+where $\Delta_{\mathrm{thresh}}$ is the detuning from the dissociation threshold,
+which is smaller for intermediate states that are deeply bound.
 
@@
 $31\mathrm{\%}$ of initial two-atom population is transferred.
-Of this population, over $60\%$ is in the ground state of center of mass motion, inferred from Raman sideband thermometry~\cite{Zhang2020,He331}.
+Of this population, over $60\%$ is in the ground state of center of mass motion, inferred from Raman sideband thermometry.
 %center-of-mass motional ground state.
@@
     \emph{Inset:} Geometry and polarization of trap and Raman beam relative to the magnetic field.
-    The X.yy~mW beam is focused to a waist of $0.9~\mathrm{\mu m}$
+    The 3.25~mW beam is focused to a waist of $0.9~\mathrm{\mu m}$
     that confines the atoms and molecule.
@@
 A decaying Rabi oscillation with frequency $2\pi\times3.28(4)~\mathrm{kHz}$ fitted to the data suggests that
-$69~\mathrm{\%}$ of atoms are transferred into the molecular state after a $\pi$-pulse with the majority of molecules in the ground state of motion.
+$69~\mathrm{\%}$ of atoms are transferred into the molecular state after a $\pi$-pulse with the majority of molecules in the ground state of motion~\cite{Zhang2020,He331}.
 % Over $60\%$ of the molecules are in the motional ground state (both relative and center of mass), inferred from independent Raman sideband thermometry measurements of the atoms.
+
+\begin{figure}[t!]
+  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
+  \caption{
+    (a) Direct measurement of molecule lifetime with about $3.25~\mathrm{mW}$ optical power.
+    Molecule survival is detected by dissociating back to atoms via a second Raman transition.
+    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
+    measured from the Raman transition data.
+    Inset: pulse sequence for the lifetime measurement.
+    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
+    in a trap of depth $3.25~\mathrm{mW}$ caused by off-resonance photoassociation.
+    This is used to improve the fitting of the Raman transfer data.
+    Inset: Atomic scattering rate scales as
+    $P_\textrm{tweezer}^{2.58}\times\!2\pi\!\times29.3(17)~\mathrm{mHz/mW^{2.58}}$ on a log-log scale;
+    this is consistent with a two-photon scattering process.
+    We have not measured a clear dependency of the loss rate on the tweezer detuning.
+    \label{f-lifetime}}
+\end{figure}
 
@@
 The coefficients $\Omega_m$ and $\Omega_a$ are in broad agreement with our calculation and their ratio at $3.75~\mathrm{mW}$ is $0.016$, which is near the theory prediction of $0.013$.
-The measured Rabi rate $\Omega_R$ is ZZ~\% of $\Omega_m \Omega_a/(2\Delta)$ due to interference from further-detuned Raman processes.
+The measured Rabi rate $\Omega_R$ is 62.6~\% of $\Omega_m \Omega_a/(2\Delta)$ due to interference from further-detuned Raman processes.
     \label{tab:f-det:fit}}
@@
 From experimental measurements, the Raman transfer efficiency is limited by the molecular lifetime, together with a reduction in the Raman Rabi frequency due to destructive interference with intermediate states beyond v'=0 (see Table~~\ref{tab:f-det:fit}).
+We now discuss both these observations.
+
 The lifetime is measured directly by preparing the molecule with a $\pi$-pulse,
@@
 consistent with the decay of the Rabi oscillation in Fig.~\ref{f-raman}b.
-
 Preliminary experiments and theoretical considerations indicate that the molecular lifetime may be limited by two-photon coupling to the atomic continuum~\cite{YichaoYu}.
-Atom loss is shown to be small in Fig.~\ref{f-lifetime} by measuring the one- and
+Atom loss is shown to be small in Fig.~\ref{f-lifetime}b by measuring the one- and
 two-body lifetimes of the atoms directly without the second Raman frequency.
 In principle, destructive interference that reduces the Raman Rabi rate for negative detunings $\Delta$ changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.
+
 Separately we observe a decrease in coherence by a factor of 2 without laser spectrum filters,
 suggesting that spectral impurity of the laser can be a significant source of loss.   While we have not fully characterized the sources
-of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities.
-
-\begin{figure}[t!]
-  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
-  \caption{
-    (a) Direct measurement of molecule lifetime with about $X.XX~\mathrm{mW}$ optical power.
-    Molecule survival is detected by dissociating back to atoms via a second Raman transition.
-    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
-    measured from the Raman transition data.
-    Inset: pulse sequence for the lifetime measurement.
-    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
-    in a trap of depth $X.XX~\mathrm{mW}$ caused by off-resonance photoassociation.
-    This is used to improve the fitting of the Raman transfer data.
-    Inset: Atomic scattering rate scales as
-    $P_\textrm{tweezer}^{2.58}\times\!2\pi\!\times29.3(17)~\mathrm{mHz/mW^{2.58}}$ on a log-log scale;
-    this is consistent with a two-photon scattering process.
-    We have not measured a clear dependency of the loss rate on the tweezer detuning.
-    \label{f-lifetime}}
-\end{figure}
-Other potential decoherence sources include
+of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities. Other potential decoherence sources include
 fluctuations of the tweezer intensity and magnetic field.

### 2020-12-08 sm.tex
Update on Overleaf.

@@
 For the purposes of this work, we denote $\Omega_a $($\Omega_m$) as the Rabi frequencies to drive a transition from the atom (target molecule) state to the intermediate state used in the Raman transition corresponding to the power in a single beam, $P_a$ ($P_m$).
-Thus, the Raman Rabi frequency is $\Omega_a\Omega_m/2\Delta$, where $ \Delta $ is the single photon detuning.
-Cross coupling affects the scattering rate and light shift, and assuming equal powers in both beams, these quantities become $ \Gamma_e \Omega_m^2 / 2\Delta^2 + \Gamma_e \Omega_a^2 / 2\Delta^2 $ and $ \Omega_m^2/2\Delta - \Omega_a^2/2\Delta $, where $\Gamma_e$ is the excited state linewidth.
-Since $ \Omega_m >> \Omega_a $, the scattering rate and light shift can be approximated as $ \Gamma_e \Omega_m^2/2\Delta^2$ and $\Omega_m^2/2\Delta$.
+Thus, the Raman Rabi frequency is $\Omega_a\Omega_m/(2\Delta)$, where $ \Delta $ is the single photon detuning. 
+Cross coupling affects the scattering rate and light shift, and assuming equal powers in both beams, these quantities become $ \Gamma_e \Omega_m^2 / (2\Delta^2) + \Gamma_e \Omega_a^2 / (2\Delta^2) $ and $ \Omega_m^2/(2\Delta) - \Omega_a^2/(2\Delta) $, where $\Gamma_e$ is the excited state linewidth.
+Since $ \Omega_m >> \Omega_a $, the scattering rate and light shift can be approximated as $ \Gamma_e \Omega_m^2/(2\Delta^2)$ and $\Omega_m^2/(2\Delta)$.
 
@@
 The first term can be calculated numerically given an excited state potential.
-To calculate the second term, we first make an assumption that we are far enough detuned from the contributing continuum states that they are all at approximately the same detuning, $ \delta_{\text{thresh}}$.
+To calculate the second term, we first make an assumption that we are far enough detuned from the contributing continuum states that they are all at approximately the same detuning, $ \Delta_{\text{thresh}}$.
 This allows us to pull it out of the sum, and we obtain:
 \begin{equation}
-  \Omega_R \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\delta_{\text{thresh}}}\displaystyle\sum_{v' > v'_{\text{max}}} \braket{a|v'}\braket{v'|m}  \label{rabifreq}
+  \Omega_R \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\displaystyle\sum_{v' > v'_{\text{max}}} \braket{a|v'}\braket{v'|m}  \label{rabifreq}
 \end{equation}
@@
 \begin{equation}
-  \Omega_R \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} -  \frac{d^2E^2}{2\hbar^2\delta_{\text{thresh}}}\displaystyle\sum_{v' \leq v'_{\text{max}}} \braket{a|v'}\braket{v'|m}
+  \Omega_R \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} -  \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\displaystyle\sum_{v' \leq v'_{\text{max}}} \braket{a|v'}\braket{v'|m}
 \end{equation}
@@
   \Gamma_s &= \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} + \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' > v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} \\
-           &\approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} + \frac{d^2E^2\Gamma}{2\hbar^2\delta_{\text{thresh}}^2}\displaystyle\sum_{v' > v'_{\text{max}}}\braket{m|v'}\braket{v'|m}
+           &\approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} + \frac{d^2E^2\Gamma}{2\hbar^2\Delta_{\text{thresh}}^2}\displaystyle\sum_{v' > v'_{\text{max}}}\braket{m|v'}\braket{v'|m}
 \end{align}
@@
 \begin{equation}
-  \Gamma_s \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} +  \frac{d^2E^2\Gamma}{2\hbar^2\delta_{\text{thresh}}^2}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right)
+  \Gamma_s \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} +  \frac{d^2E^2\Gamma}{2\hbar^2\Delta_{\text{thresh}}^2}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right)
 \end{equation}
 We have replaced the full continuum with an effective state at the atomic threshold with strength proportional to the amount of wavefunction overlap between the target molecular state and all atomic continuum states.
-This model leads to a component in the scattering rate that is proportional to $ 1/\delta_{\text{thresh}}^2$ and is smaller as one detunes farther from the threshold.
-We note that the first term can also scale nearly as $1/\delta_{\text{thresh}}^2 $, if, as in our case, the largest terms in the summation are from states near the threshold.
+This model leads to a component in the scattering rate that is proportional to $ 1/\Delta_{\text{thresh}}^2$ and is smaller as one detunes farther from the threshold.
+We note that the first term can also scale nearly as $1/\Delta_{\text{thresh}}^2 $, if, as in our case, the largest terms in the summation are from states near the threshold.
 
@@
 \begin{equation}
-  \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\delta_{\text{thresh}}}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right)
+  \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right)
 \end{equation}
@@
 These calculations assume that the intermediate states have pure singlet or triplet character and neglect its
-nuclear spin character, which is unknown.
-These calculations include electronic transition dipole moments, calculated ab initio by \textcolor{red}{Should we just mention Mosynski or Rosario?
-or say something about the ab initio method and give a citation.}
+nuclear spin character, which is unknown. These calculations include theoretical electronic transition dipole moments\footnote{Private communication with R. Gonzalez-Ferez and R. Moszynski}
 
@@
 The strong contribution from the atomic threshold arises from the large overlap to the near-threshold bound states shown in figure \ref{f-smfcf} for the $c^3\Sigma^+_1$ state.
-This leads to a $1/\delta_{\text{thresh}}^2$ dependence of the scattering rate and favors using deeply bound states as the intermediate state for the Raman transfer.
+This leads to a $1/\Delta_{\text{thresh}}^2$ dependence of the scattering rate and favors using deeply bound states as the intermediate state for the Raman transfer.
 A similar result holds for the other excited state potentials.
@@
 The experiment, through measuring the detuning dependence of the Raman Rabi frequency and the resonance frequency, extracts a single $ \Omega_m $ and $ \Omega_a $.
-In order to compare to the theory, we introduce effective $ \Omega_a', \Omega_m', \Gamma_e'$, so that $ \Omega_R = \Omega_a'\Omega_m'/2\Delta $, $\delta = (\Omega_{a}'^2 - \Omega_{m}'^2)/2\Delta $, and $\Gamma_S = \Gamma_e'(\Omega_{a}'^2 + \Omega_{m}'^2)/2\Delta^2 $.
+In order to compare to the theory, we introduce effective $ \Omega_a', \Omega_m', \Gamma_e'$, so that $ \Omega_R = \Omega_a'\Omega_m'/(2\Delta) $, $\delta = (\Omega_{a}'^2 - \Omega_{m}'^2)/(2\Delta) $, and $\Gamma_S = \Gamma_e'(\Omega_{a}'^2 + \Omega_{m}'^2)/(2\Delta^2) $.
 The effective Rabi frequencies for the $v' = 0$ state of $ c^3\Sigma^+_1$ and their ratio are reported in Table~\ref{tab:sm} at $3.75~\mathrm{mW}$ of tweezer power.
@@
   $\Omega_a'$ &  $2\pi \times 7.37 ~\mathrm{MHz}$ \\
-  $\Omega_m'/\Omega_a'$ & $ 78 $ \\ \hline
+  $\Omega_a'/\Omega_m'$ & $ 0.013 $ \\ \hline
   \end{tabular}

### 2020-12-08 scripts/plot_raman.jl
Update raman theory plot

@@ -73,10 +73,10 @@ plot(data[:, 1] .- 339724.57, abs.(data[:, 2] ./ data[:, 4]), "C1--",
 xlabel("One-Photon Detuning (GHz)")
 ylabel("\$\\Omega_{R}/\\Gamma_{s}\$")
 xlim([-300, 300])
-ylim([0.02, 90])
+ylim([0.02, 30])
 yscale("log")
 yticks([0.1, 1, 10], ["0.1", "1", "10"])
-legend(fontsize=13.88, loc="center left", bbox_to_anchor=(0.0, 0.67),
+legend(fontsize=13.88, loc="center left", bbox_to_anchor=(0.06, 0.66),
        handlelength=1, handletextpad=0.3)
 ax3.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 grid()

### 2020-12-08 paper.tex
Update on Overleaf.

@@
 While many innovative approaches in the last few years
-have directly cooled different species of diatomic or polyatomic molecules
-below 1~mK~\cite{Norrgard2016,Anderegg2018, Mitra1366, PhysRevX.10.021049,
-  PhysRevLett.121.013202, Truppe2017},
+have directly cooled different species of %diatomic or polyatomic
+molecules
+below 1~mK~\cite{Norrgard2016,Prehn2016,Truppe2017,Anderegg2018,  PhysRevX.10.021049,
+Mitra1366},
 the highest phase-space-density gas~\cite{Demarco2018} and
@@
 Exceptions include Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states
-are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012},
+are available and optical association can be driven coherently~\cite{Stellmer2012,Reinaudi2012},
 and $^{87}$Rb$^{85}$Rb with molecular states bound by only $1-2~\mathrm{MHz}$~\cite{He331}.
@@
   \includegraphics[width=\textwidth]{imgs/fig-theory.pdf}
-  \caption{Optical creation of single molecule from single atoms in an optical tweezer.
+  \caption{Optical creation of single molecules from single atoms in an optical tweezer.
     (a) Schematic of the optical transition from an atom pair to a weakly bound molecule.
@@
   \caption{
-    Beampath for generating two frequencies in the tweezer for the Raman transition
-    (Some mirrors and other optics used for alignment are not included.)
-    Two ASE filters, one directly after the laser source and one after both optical fibers, are used. The laser source is a fiber amplifier seeded by a external cavity diode laser.
+    Beampath for generating two frequencies in the tweezer for the Raman transition (only essential optics are shown.)
+    Two  filters, one directly after the laser source and one after both optical fibers, are used. The laser source is a fiber amplifier seeded by a external cavity diode laser.
     The red beam path is the $0$-th order of the double pass~(DP) AOM which is used at all times.
     The blue beam path is the $1$-st order of the DP AOM, and generates the second frequency required to drive the Raman transition.
-    %When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
-    %(blue beam path) which generates the required frequency different to drive
-    %the Raman transition. 
-    %The two frequencies are recombined on the DP AOM.
+    % When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
+    % (blue beam path) which generates the required frequency different to drive
+    % the Raman transition.
+    % The two frequencies are recombined on the DP AOM.
     The $0$-th order light is shifted by another single pass~(SP) AOM before recombining, which ensures that it will not interfere with the leak light from the DP AOM, resulting in power fluctuations.
-    %be at the same frequency
-    %as the $0$-th order light which can cause a significant power fluctuation
-    %due to interference.
+    % be at the same frequency
+    % as the $0$-th order light which can cause a significant power fluctuation
+    % due to interference.
     The experiment typically starts with the SP AOM on and the DP AOM off.
@@
 
-% After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
-Next, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ with a large scattering length
-by performing a Cs spin flip while taking into account
-the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.
-This is the initial atomic state for Raman transfer.
-The spin flip selectively transfers atoms in the relative motional ground state,
-removing any background from atoms in excited states of relative motion
-\footnote{This interaction shift is larger than the differential axial trapping frequency
-  between Na and Cs atoms, which decouples the relative and center of mass motional state
-  and improves the robustness of our preparation of the relative motional ground state.}.
-For the experiment reported here,
-$31\mathrm{\%}$ of initial two-atom population is transferred.
-Of this population, over $60\%$ is in the ground state of center of mass motion, inferred from Raman sideband thermometry.
-%center-of-mass motional ground state.
-% of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
-% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..
-
 \begin{figure}[t!]
@@
 \end{figure}
+Next, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ with a large scattering length
+by performing a Cs spin flip while taking into account
+the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.
+This is the initial atomic state for Raman transfer.
+The spin flip selectively transfers atoms in the relative motional ground state,
+removing any background from atoms in excited states of relative motion
+\footnote{This interaction shift is larger than the differential axial trapping frequency
+  between Na and Cs atoms, which decouples the relative and center of mass motional state
+  and improves the robustness of our preparation of the relative motional ground state.}.
+For the experiment reported here,
+$31\mathrm{\%}$ of initial two-atom population is transferred.
+Of this population, over $60\%$ is in the ground state of center of mass motion, inferred from Raman sideband thermometry.
+%center-of-mass motional ground state.
+% of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
+% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..
+
+\begin{figure*}[htb]
+  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
+  \caption{Raman transition parameters as a function of tweezer power and detuning.
+    (a) The Raman resonance fitted by $a_P+b_P/\Delta$, where
+    $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
+    are the power ($P$) dependent background and $v'=0$ contributions
+    to the light shift and
+    $\Delta\equiv2\pi\times\paren{f_0 - f_{\mathrm{tweezer}}}$ is the detuning from
+    the $v'=0$ resonance frequency $f_0$.
+    $a_P$ is fitted to a model including linear and small quadratic light shift
+    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
+    at zero tweezer power $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$ where the statistical uncertainty is shown.
+    (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
+    $c_P$ and $d_P=\Omega_a\Omega_m/2$
+    are the background and $v'=0$ contributions that scale as $P^{1.29}$ with optical power.
+    The detuning is calculated from the PA frequency fitted in (a). Fit parameters are listed in Table~\ref{tab:f-det:fit}.
+    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
+    $b_P$ and $d_P$ on a log-log scale showing approximate $P^{0.5}$ scaling of $\Omega_m$ and
+    $P^{0.79}$ scaling of $\Omega_a$.
+    \label{f-det}}
+\end{figure*}
+
 %% Transfer scheme
@@
 
-\begin{figure*}[t!]
-  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
-  \caption{Raman transition parameters as a function of tweezer power and detuning.
-    (a) The Raman resonance fitted by $a_P+b_P/\Delta$, where
-    $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
-    are the power ($P$) dependent background and $v'=0$ contributions
-    to the light shift and
-    $\Delta\equiv2\pi\times\paren{f_0 - f_{\mathrm{tweezer}}}$ is the detuning from
-    the $v'=0$ resonance frequency $f_0$.
-    $a_P$ is fitted to a model including linear and small quadratic light shift
-    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
-    at zero tweezer power $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$ where the statistical uncertainty is shown.
-    (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
-    $c_P$ and $d_P=\Omega_a\Omega_m/2$
-    are the background and $v'=0$ contributions that scale as $P^{1.29}$ with optical power.
-    The detuning is calculated from the PA frequency fitted in (a). Fit parameters are listed in Table~\ref{tab:f-det:fit}.
-    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
-    $b_P$ and $d_P$ on a log-log scale showing approximate $P^{0.5}$ scaling of $\Omega_m$ and
-    $P^{0.79}$ scaling of $\Omega_a$.
-    \label{f-det}}
-\end{figure*}
-
 Figure~\ref{f-raman} shows a Fourier-limited resonance together with Rabi oscillations between the atomic and molecular states.
@@
 
-\begin{figure}[t!]
+\begin{figure}[ht]
   \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
@@
 By scaling up to many optical tweezers~\cite{Endres2016, Barredo2018,  PhysRevLett.122.203601}, large arrays with arbitrary geometry of highly controlled molecules can be achieved.
-These molecules comprise a flexible platform for quantum simulation and quantum computing applications.
+These molecules comprise a flexible platform for quantum simulation,  quantum computing, precision measurements applications.
 %\textcolor{blue}{(End with a sentence on molecules for future quantum applications?)}

### 2020-12-08 paper.tex
Define omega_R

--- 2020-12-08 paper.tex
@@
     The blue beam path is the $1$-st order of the DP AOM, and generates the second frequency required to drive the Raman transition.
-    %When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
-    %(blue beam path) which generates the required frequency different to drive
-    %the Raman transition. 
-    %The two frequencies are recombined on the DP AOM.
+    % When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
+    % (blue beam path) which generates the required frequency different to drive
+    % the Raman transition.
+    % The two frequencies are recombined on the DP AOM.
     The $0$-th order light is shifted by another single pass~(SP) AOM before recombining, which ensures that it will not interfere with the leak light from the DP AOM, resulting in power fluctuations.
-    %be at the same frequency
-    %as the $0$-th order light which can cause a significant power fluctuation
-    %due to interference.
+    % be at the same frequency
+    % as the $0$-th order light which can cause a significant power fluctuation
+    % due to interference.
     The experiment typically starts with the SP AOM on and the DP AOM off.
@@
   \caption{Raman transition parameters as a function of tweezer power and detuning.
-    (a) The Raman resonance fitted by $a_P+b_P/\Delta$, where
+    (a) The Raman resonance~($\omega_R$) fitted by $a_P+b_P/\Delta$, where
     $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$

### 2020-12-08 paper.tex
TODO cleanup
Update on Overleaf.

@@
     and the final state is the first molecular bound state.
-    The transition is driven by a pair of laser frequencies whose difference matches the binding energy
-    of the molecule.
+    The transition is driven by a pair of laser frequencies whose difference ($< 1$~GHz) matches the molecular binding energy.
     The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
-    by $\Delta$ in order to suppress scattering during the transfer.
-    (b) Full calculation of the scattering rate as a function of the single-photon frequency
-    including all vibrational states of 8 excited state potentials
+    by $\Delta$ in order to reduce scattering during the transfer.
+    (b) Calculation of the scattering rate vs. laser frequency
+    including all vibrational states of 8 excited-state potentials
     and the atomic continuum.
-    The assumed excited-state linewidth for all molecular lines is $50~\text{MHz}$.
-    The dotted red line shows the contribution that comes only from the near-threshold states, which approximately scales as $1/\Delta_{\mathrm{thresh}}^2$.
-    (c) Comparison between weakly-bound and deeply-bound intermediate excited state
+    The assumed excited-state linewidth for molecular lines is $50~\text{MHz}$.
+    The dotted red line shows the contribution from the near-threshold states, which approximately scales as $1/\Delta_{\mathrm{thresh}}^2$.
+    (c) Comparison between vibrational sublevels of the intermediate excited state
     for the Raman transition.
-    The deeply bound excited state (blue line $v'=0$)
-    has a larger ratio of Raman Rabi frequency to scattering rate
-    compared to the weakly bound excited state (orange line $v'=40$) at a best detuning.
-    (d) Enhancement of the short-range wavefunction.
-    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
-    comparable to the axial trapping frequency.
-    This causes a significant change in the relative wavefunction, especially at short
+    The lowest sublevel (blue)
+    has a larger optimum ratio of Raman Rabi frequency to scattering rate
+    than the higher sublevel (orange).
+    (d) The large scattering length for $\Na(2,2),\Cs(3,3)$ is associated with enhancementment of the relative wavefunction at short
     internuclear distance ($R$).
-    Compared to other spin states with weaker interaction,
-    the wavefunction at short distance ($R<100\ \text{\AA}$, left of the dashed line)
-    is significantly enhanced.
     \label{f-theory}
@@
   \caption{
-    Beampath for generating two frequencies in the tweezer for the Raman transition (only essential optics are shown.)
-    Two  filters, one directly after the laser source and one after both optical fibers, are used. The laser source is a fiber amplifier seeded by a external cavity diode laser.
-    The red beam path is the $0$-th order of the double pass~(DP) AOM which is used at all times.
-    The blue beam path is the $1$-st order of the DP AOM, and generates the second frequency required to drive the Raman transition.
+    Beampath for generating two frequencies in the tweezer for the Raman transition (only essential optics shown.)
+    Two  filters, one directly after the laser source and one after both optical fibers clean the light from a fiber amplifier seeded by an external cavity diode laser.
+    The red beam path is the always-present $0^\mathrm{th}$ order of the double pass~(DP) AOM.
+    The blue beam path is the switchable $1^\mathrm{st}$ order of the DP AOM. It generates the second frequency for the Raman transition.
     % When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
@@
     % The two frequencies are recombined on the DP AOM.
-    The $0$-th order light is shifted by another single pass~(SP) AOM before recombining, which ensures that it will not interfere with the leak light from the DP AOM, resulting in power fluctuations.
+    To reduce power fluctuations, the $0^\mathrm{th}$ order light is shifted by another single pass~(SP) AOM before recombination, preventing interference with leakage light from the DP AOM~[[TR: What frequency is the leakage light?
+]].
     % be at the same frequency
@@
 and scattering losses are dominated by the final state.
-Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning of $80$ to $200$~GHz, causing the target molecular state to scatter both beams nearly equally with a total rate $ \Gamma_e \Omega_m^2 / (2\Delta^2)$, where $ \Gamma_e $ is the excited-state linewidth~\footnote{The two beams have equal power to maximize the Raman Rabi rate at fixed total power, resulting in a factor of 2 for scattering two beams.}.
+Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning of $80$ to $200$~GHz, causing the target molecular state to scatter both beams nearly equally with a total rate $ \Gamma_e \Omega_m^2 / (2\Delta^2)$, where $ \Gamma_e $ is the excited-state linewidth~\footnote{The two beams have equal power to maximize the Raman Rabi frequency at fixed total power, resulting in a factor of 2 for scattering two beams.}.
 In this idealized treatment, the ratio between the Raman Rabi frequency and the scattering rate is $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, which limits the transfer efficiency into the molecular state.
@@
 
-Earlier experiments used weakly bound excited states as the intermediate state
-in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
+Earlier experiments used excited states with high vibrational quantum number for the intermediate state
+of the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
 However, a complete picture includes both the many vibrational levels
@@
 Then the scattering and Raman Rabi rates are sums over all possible intermediate states.
-As there is large overlap between the target molecular state and weakly bound excited states, intermediate states that are closer to the dissociation threshold result in a large scattering rate.
+As there is large overlap between the target molecular state and other vibrationally excited states, intermediate states that are closer to the dissociation threshold result in a large scattering rate.
 % in large incoherence and loss to other molecular states.
@@
 This calculation shows that the figure of merit $\Omega_R/\Gamma_s$
-can be larger for more deeply bound states compared to weakly bound states
+can be larger for the lowest vibrational state compared to higher bound states
 at a cost of a smaller transfer rate $\Omega_R$, as shown in Fig.~\ref{f-theory}c;
@@
 and a single ${}^{133}\Cs$ atom into separate optical tweezers.
-The atoms are initially imaged to distinguish between loading of two atoms,
-one atom (Na or Cs), or no atom to be able to post-select from the experimental results
-based on the initial loading condition.
+The atoms are initially imaged to post-select loading of both atoms vs.
+none or one atom.
 After imaging, we turn on a $8.83(2)~\mathrm{G}$ magnetic field to define the quantization axis
 for the state preparation and molecule formation steps.
-Raman sideband cooling is then applied to prepare both atoms simultaneously
+Raman sideband cooling then prepares both atoms simultaneously
 in the 3-dimensional motional ground state of their optical tweezers, leaving the atoms in the spin state~$\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{f=2,m_f=2}_{\Na}\ket{f=4,m_f=4}_{\Cs}$,
@@
 \end{figure}
-Next, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ with a large scattering length
+Afr merging the tweezers, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ with a large scattering length
 by performing a Cs spin flip while taking into account
@@
 For the experiment reported here,
-$31\mathrm{\%}$ of initial two-atom population is transferred.
-Of this population, over $60\%$ is in the ground state of center of mass motion, inferred from Raman sideband thermometry.
-%center-of-mass motional ground state.
-% of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
-% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..
+$31\mathrm{\%}$ of initial two-atom population is transferred. Of this population, over $60\%$ is in the ground state of center-of-mass motion, inferred from Raman sideband thermometry.
 
@@
 A decaying Rabi oscillation with frequency $2\pi\times3.28(4)~\mathrm{kHz}$ fitted to the data suggests that
-$69~\mathrm{\%}$ of atoms are transferred into the molecular state after a $\pi$-pulse with the majority of molecules in the ground state of motion~\cite{Zhang2020,He331}.
+$69~\mathrm{\%}$ of atoms are transferred into the molecular state after a $\pi$-pulse, with the majority of molecules in the ground state of motion~\cite{Zhang2020,He331}.
 % Over $60\%$ of the molecules are in the motional ground state (both relative and center of mass), inferred from independent Raman sideband thermometry measurements of the atoms.
@@
   \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
-  \caption{
-    (a) Direct measurement of molecule lifetime with about $3.25~\mathrm{mW}$ optical power.
+  \caption{Lifetime measurements with about $3.25~\mathrm{mW}$ optical power.
+    (a) Direct measurement of molecule lifetime.
     Molecule survival is detected by dissociating back to atoms via a second Raman transition.
@@
     Inset: pulse sequence for the lifetime measurement.
-    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
-    in a trap of depth $3.25~\mathrm{mW}$ caused by off-resonance photoassociation.
+    (b)~Two-body atom lifetime of $5(1)~\mathrm{ms}$
+    limited by off-resonance photoassociation.
     This is used to improve the fitting of the Raman transfer data.
@@
     this is consistent with a two-photon scattering process.
-    We have not measured a clear dependency of the loss rate on the tweezer detuning.
     \label{f-lifetime}}
@@
 To better understand the details and limitations of the Raman transfer process, we measured the properties of the two-photon resonance as a function of tweezer power and single-photon detuning.
-Known dependencies of the light shift and Raman Rabi frequency on detuning $\Delta$ allow experimental determination of the Rabi frequencies
+Known dependencies of the light shift and Raman Rabi frequency ($\Omega_R$) on detuning ($\Delta$) allow experimental determination of the Rabi frequencies
 $ \Omega_a $ and $\Omega_m$ whose ratio critically affects the transfer efficiency.
-Both the light shift and Raman Rabi frequency follow a $1/\Delta$ slope as shown in Fig.~\ref{f-det}a, b and include a constant offset that we attribute to coupling to other excited states that are further away in energy.
-The $1/\Delta$ components, due to the nearby $v'=0$ intermediate state, determine $\Omega_m $ and $ \Omega_a $ in from the fit coefficients, as shown in Table~\ref{tab:f-det:fit}.
+Both the light shift and $\Omega_R$ follow a $1/\Delta$ slope as shown in Fig.~\ref{f-det}a, b and include a constant offset that we attribute to coupling to other excited states that are further away in energy.
+The $1/\Delta$ components due to the nearby $v'=0$ intermediate state determine $\Omega_m $ and $ \Omega_a $ in Table~\ref{tab:f-det:fit}.
 
@@
 $\Omega_R$ is reported at $-151~\mathrm{GHz}$ detuning from the $v' = 0$ state.
-The coefficients $\Omega_m$ and $\Omega_a$ are in broad agreement with our calculation and their ratio at $3.75~\mathrm{mW}$ is $0.016$, which is near the theory prediction of $0.013$.
-The measured Rabi rate $\Omega_R$ is 62.6~\% of $\Omega_m \Omega_a/(2\Delta)$ due to interference from further-detuned Raman processes.
+The coefficients $\Omega_m$ and $\Omega_a$ are in broad agreement with our calculation and their ratio at $3.75~\mathrm{mW}$ is $0.016$, near the theory prediction of $0.013$.
+The measured Rabi rate $\Omega_R$ is only 63~\% of $\Omega_m \Omega_a/(2\Delta)$ due to interference from further-detuned Raman processes.
     \label{tab:f-det:fit}}
@@
 
-We perform the experiment at various tweezer powers to extract the power dependence of $ \Omega_m $ and $ \Omega_a $, as shown in Fig.~\ref{f-det}c.
-$ \Omega_m $ scales like $ P^{1/2} $ as expected.
+Figure~\ref{f-det}c shows the power dependence of $ \Omega_m $ and $ \Omega_a $, where $ \Omega_m $ scales like $ P^{1/2} $ as expected.
 As discussed previously, the scaling of $ \Omega_a $ is $P^{7/8}$ for weakly interacting particles.
@@
 
-The measured single-photon Rabi frequencies of Table~I are in broad agreement with calculations (see Supplementary Materials).
-The full calculation of the expected scattering rate of the molecular and atomic state including all excited states does not explain the decoherence in Fig.~\ref{f-raman}b.
+While the measured single-photon Rabi frequencies of Table~I are in broad agreement with calculations (see Supplementary Materials), calculated scattering rates of the molecular and atomic state underestimate the decoherence in Fig.~\ref{f-raman}b.
 % Known single-photon scattering rates of Na and Cs atoms together with an independent measurement (via photoassociation spectroscopy) of the $v'=0$ excited state natural linewidth of no more than $50~\mathrm{MHz}$ indicate that single-photon scattering from the molecular or atomic state do not explain the decoherence in Fig.
@@
 Below, we further investigate the loss of coherence.
-% \todo{change scattering to decoherence? since the fluctuation of light shift
-% does not lead to scattering but only decherence.}
 % These results suggest that the decoherence or loss we observe during the Raman transition
@@
 From experimental measurements, the Raman transfer efficiency is limited by the molecular lifetime, together with a reduction in the Raman Rabi frequency due to destructive interference with intermediate states beyond v'=0 (see Table~~\ref{tab:f-det:fit}).
-We now discuss both these observations.
+We discuss loss and decoherence below.
 
-The lifetime is measured directly by preparing the molecule with a $\pi$-pulse,
+The molecular lifetime of $0.199(9)~\mathrm{ms}$ in Fig.~\ref{f-lifetime}a is measured by preparing the molecule with a $\pi$-pulse,
 followed after a variable delay by a second dissociating $\pi$-pulse.
-The result in Fig.~\ref{f-lifetime}a shows a molecular lifetime of $0.199(9)~\mathrm{ms}$,
+This result is
 consistent with the decay of the Rabi oscillation in Fig.~\ref{f-raman}b.
@@
 two-body lifetimes of the atoms directly without the second Raman frequency.
-In principle, destructive interference that reduces the Raman Rabi rate for negative detunings $\Delta$ changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.
+In principle, destructive interference that reduces the Raman Rabi rate ($\Omega_R$) for negative detunings ($\Delta$) changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.
+More negative detunings than XXX~GHz that might reduce the scattering rate were prevented by vanishing of $\Omega_R$.
 
@@
 of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities. Other potential decoherence sources include
-fluctuations of the tweezer intensity and magnetic field.
+fluctuations of the tweezer intensity and magnetic field, although the shape of the Rabi oscillation in Fig.~{f-raman}b indicates that loss rather than frequency fluctuations are responsible for decoherence.
 Based on the Rabi frequency ratio in Table~\ref{tab:f-det:fit}
@@
 
-\todo{sm: STIRAP vs Raman}
-
 \begin{acknowledgments}
@@
 
-\TR{Mention somewhere that the shape of Fig. 3b Rabi flopping indicates loss, not frequency fluctuation.}
+\TR{Freq./mechanism of leakage light in Fig. 2?}
 
-\TR{Check all ``$P=3.75$~mW'' results because they may negelect reduction from 2nd ASE filter.  Better to quote the reduced power.}
+\TR{Remove $\delta$ in Fig. 1a.}
 
-\TR{``We" is overused in this paper and obscures more important subject-object relationships.  Authorship already implies that ``we" did everything in the paper.}
+\TR{Change 1b horizontal axis to ``Laser frequency''?}
 
-\TR{Is Raman Rabi freq the best term for $\Omega_R$?}
-
-\TR{Broader statement on experimentally possible vs. theoretical detunings.}
+\TR{Insert lower practical limit for $\Delta$ as ``XXX GHz'' on last page.}
 

### 2020-12-08 paper.tex
Fix up

--- 2020-12-08 paper.tex
@@
 For the experiment reported here,
-$31\mathrm{\%}$ of initial two-atom population is transferred.
-Of this population, over $60\%$ is in the ground state of center of mass motion, inferred from Raman sideband thermometry.
-%center-of-mass motional ground state.
-% of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
-% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..
+$31\mathrm{\%}$ of initial two-atom population is transferred. Of this population, over $60\%$ is in the ground state of center of mass motion, inferred from Raman sideband thermometry.
 
@@
     Inset: Atomic scattering rate scales as
-    $P_\textrm{tweezer}^{2.58}\times\!2\pi\!\times29.3(17)~\mathrm{mHz/mW^{2.58}}$ on a log-log scale;
+    $P_\textrm{tweezer}^{2.58}\times\!2\pi\!\times1.05(6)~\mathrm{Hz/mW^{2.58}}$ on a log-log scale;
     this is consistent with a two-photon scattering process.
@@
 Preliminary experiments and theoretical considerations indicate that the molecular lifetime may be limited by two-photon coupling to the atomic continuum~\cite{YichaoYu}.
-Atom loss is shown to be small in Fig.~\ref{f-lifetime}b by measuring the one- and
-two-body lifetimes of the atoms directly without the second Raman frequency.
+Atom loss is shown to be small in Fig.~\ref{f-lifetime}b by measuring the two-body lifetimes of the atoms directly
+without the second Raman frequency.
 In principle, destructive interference that reduces the Raman Rabi rate for negative detunings $\Delta$ changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.
@@
 
-\TR{Check all ``$P=3.75$~mW'' results because they may negelect reduction from 2nd ASE filter.  Better to quote the reduced power.}
-
 \TR{``We" is overused in this paper and obscures more important subject-object relationships.  Authorship already implies that ``we" did everything in the paper.}

### 2020-12-08 paper.tex

--- 2020-12-08 paper.tex
@@
 Preliminary experiments and theoretical considerations indicate that the molecular lifetime may be limited by two-photon coupling to the atomic continuum~\cite{YichaoYu}.
-Atom loss is shown to be small in Fig.~\ref{f-lifetime}b by measuring the one- and
-two-body lifetimes of the atoms directly without the second Raman frequency.
+Atom loss is shown to be small in Fig.~\ref{f-lifetime}b by measuring the two-body lifetimes of the atoms directly without the second Raman frequency.
 In principle, destructive interference that reduces the Raman Rabi rate ($\Omega_R$) for negative detunings ($\Delta$) changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.

### 2020-12-09 paper.tex
Update on Overleaf.

@@
 \newcommand{\cua}{\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}}
+\newcommand{\agendile}{\affiliation{Agendile LLC, Cambridge, Massachusetts 02139, USA}}
 \newcommand{\gradstudent}{
@@
 \author{Till Rosenband}
-\harvardphysics
+\agendile
 \author{Kang-Kuen~Ni}
@@
 fluctuations of the tweezer intensity and magnetic field, although the shape of the Rabi oscillation in Fig.~{f-raman}b indicates that loss rather than frequency fluctuations are responsible for decoherence.
-Based on the Rabi frequency ratio in Table~\ref{tab:f-det:fit}
-the requirement on the tweezer intensity stability is $0.8\mathrm{\%}$ at $3.75~\mathrm{mW}$ power.
+Based on the ratio between $\Omega_R$ and the light shift, 
+the requirement on the tweezer intensity stability is $1\mathrm{\%}$ at $3.75~\mathrm{mW}$ power.
 We stabilize the power to $0.1\mathrm{\%}$, indicating that in the absence of beam-waist fluctuations, light shift is not a major source of decoherence.

### 2020-12-09 scripts/plot_raman_full.jl
Figure fixes

@@ -46,7 +46,7 @@ plot(data[:, 1] ./ 1000, abs.(data[:, 4] ./ 2π / 1000), "C1", label="\$\\Gamma_
 #     axvline(v * 100, color="C3", linewidth=5)
 # end
 ylabel("\$2\\pi\\times \\mathrm{kHz}\$")
-xlabel("Raman Single-Photon Frequency (THz)")
+xlabel("Tweezer Frequency (THz)")
 yscale("log")
 ylim([0.12, 400])
 yticks([1, 10, 100], ["1", "10", "100"])
@@ -76,7 +76,7 @@ text(339.724570, 3, "v'=40", rotation=90, va="center", ha="right", color="C0", f
 #     axvline(v * 100, color="C3", linewidth=5)
 # end
 ylabel("\$\\Gamma_{s}~(2\\pi\\times \\mathrm{kHz})\$")
-xlabel("Raman Single-Photon Frequency (THz)")
+xlabel("Tweezer Frequency (THz)")
 yscale("log")
 ylim([0.12, 400])
 yticks([1, 10, 100], ["1", "10", "100"])

### 2020-12-09 paper.tex
Figure fixes
subscript font

@@
 \begin{abstract}
-  We report on coherent association
+  We report coherent association
   of atoms into a single weakly bound NaCs molecule in an optical tweezer
@@
     Two  filters, one directly after the laser source and one after both optical fibers clean the light from a fiber amplifier seeded by an external cavity diode laser.
-    The red beam path is the always-present $0^\mathrm{th}$ order of the double pass~(DP) AOM.
-    The blue beam path is the switchable $1^\mathrm{st}$ order of the DP AOM. It generates the second frequency for the Raman transition.
+    The red beam path is the always-present $0^{\mathrm{th}}$ order of the double pass~(DP) AOM.
+    The blue beam path is the switchable $1^{\mathrm{st}}$ order of the DP AOM. It generates the second frequency for the Raman transition.
     % When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
@@
     % The two frequencies are recombined on the DP AOM.
-    To reduce power fluctuations, the $0^\mathrm{th}$ order light is shifted by another single pass~(SP) AOM before recombination, preventing interference with leakage light from the DP AOM~[[TR: What frequency is the leakage light?
+    To reduce power fluctuations, the $0^{\mathrm{th}}$ order light is shifted by another single pass~(SP) AOM before recombination, preventing interference with leakage light from the DP AOM~[[TR: What frequency is the leakage light?
 ]].
@@
 by the idealized three-level system shown in Fig.~\ref{f-theory}a,
-where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies $\Omega_a$ and $\Omega_m$, one-photon detuning $ \Delta $, and all Rabi frequencies are population oscillation frequencies.
+where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies $\Omega_{\rm a}$ and $\Omega_{\rm m}$, one-photon detuning $ \Delta $, and all Rabi frequencies are population oscillation frequencies.
 %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
-The transfer Raman Rabi frequency is given by $\Omega_a\Omega_m / (2\Delta)$~\cite{Wineland2003}.
-% , is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
-% $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
-Unlike Raman transitions in atoms, the one-photon Rabi frequencies are greatly imbalanced ($\Omega_a/\Omega_m \ll 1$) %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
-due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
+The transfer Raman Rabi frequency is given by $\Omega_{\rm a}\Omega_{\rm m} / (2\Delta)$~\cite{Wineland2003}.
+Unlike Raman transitions in atoms, the one-photon Rabi frequencies are greatly imbalanced ($\Omega_{\rm a}/\Omega_{\rm m} \ll 1$)
+due to the small wavefunction overlap between the atomic state and the intermediate state,
 and scattering losses are dominated by the final state.
-Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning of $80$ to $200$~GHz, causing the target molecular state to scatter both beams nearly equally with a total rate $ \Gamma_e \Omega_m^2 / (2\Delta^2)$, where $ \Gamma_e $ is the excited-state linewidth~\footnote{The two beams have equal power to maximize the Raman Rabi frequency at fixed total power, resulting in a factor of 2 for scattering two beams.}.
-In this idealized treatment, the ratio between the Raman Rabi frequency and the scattering rate is $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, which limits the transfer efficiency into the molecular state.
-At the same time, the intensity-stability requirement is determined by the ratio of Raman Rabi frequency to light shift ($\Omega_a/\Omega_m$)~\footnote{There is an additional factor of 2, with both beams at equal power,
+Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning of $80$ to $200$~GHz, causing the target molecular state to scatter both beams nearly equally with a total rate $ \Gamma_{\rm e} \Omega_{\rm m}^2 / (2\Delta^2)$, where $ \Gamma_{\rm e} $ is the excited-state linewidth~\footnote{The two beams have equal power to maximize the Raman Rabi frequency at fixed total power, resulting in a factor of 2 for scattering two beams.}.
+In this idealized treatment, the ratio between the Raman Rabi frequency and the scattering rate is $ \Omega_{\rm a}/\Omega_{\rm m} \times \Delta/\Gamma_{\rm e} $, which limits the transfer efficiency into the molecular state.
+At the same time, the intensity-stability requirement is determined by the ratio of Raman Rabi frequency to light shift ($\Omega_{\rm a}/\Omega_{\rm m}$)~\footnote{There is an additional factor of 2, with both beams at equal power,
   to account for the Stark shift caused by both beams.}.
-Notably, both figures of merit improve with a larger ratio $\Omega_a/\Omega_m$.
+Notably, both figures of merit improve with a larger ratio $\Omega_{\rm a}/\Omega_{\rm m}$.
 %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
@@
 
-We optimize over intermediate states by calculating the Raman Rabi frequency $\Omega_R$
-and scattering rate $\Gamma_s$ at different detunings from the atomic threshold,
+We optimize over intermediate states by calculating the Raman Rabi frequency $\Omega_{\rm R}$
+and scattering rate $\Gamma_{\rm s}$ at different detunings from the atomic threshold,
 taking into account of all states of
@@
 and the continuum~\cite{Liu2017}.
-This calculation shows that the figure of merit $\Omega_R/\Gamma_s$
+This calculation shows that the figure of merit $\Omega_{\rm R}/\Gamma_{\rm s}$
 can be larger for the lowest vibrational state compared to higher bound states
-at a cost of a smaller transfer rate $\Omega_R$, as shown in Fig.~\ref{f-theory}c;
+at a cost of a smaller transfer rate $\Omega_{\rm R}$, as shown in Fig.~\ref{f-theory}c;
 see Supplementary Material for details.
@@
 In addition to the intermediate state,
-the choice of initial and final Zeeman and hyperfine states affects the single-photon rates $\Omega_a$ and $\Omega_m$.
+the choice of initial and final Zeeman and hyperfine states affects the single-photon rates $\Omega_{\rm a}$ and $\Omega_{\rm m}$.
 Due to the small extent of the intermediate-state wavefunction
 compared to that of the trapped atoms,
-$\Omega_a$ is approximately proportional to
+$\Omega_{\rm a}$ is approximately proportional to
 the amplitude of the relative atomic wavefunction at short distance,
@@
 Choosing a bound state with similar spin character to the atomic state  minimizes the sensitivity of the transition frequency to magnetic field.
-A suitable state with this character is predicted about 763 MHz below the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ threshold and the ratio $\Omega_a/\Omega_m$ increases to about 0.013.
+A suitable state with this character is predicted about 763 MHz below the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ threshold and the ratio $\Omega_{\rm a}/\Omega_{\rm m}$ increases to about 0.013.
 % The coupled-channel calculations show that this target molecular state has lower overlap with the intermediate state, compared to bound states from other hyperfine combinations.
@@
 % that also has the advantage of having a reduced sensitivity
-% to laser intensity noise because of a larger %$\Omega_a/\Omega_b$ as compared to other states.
+% to laser intensity noise because of a larger %$\Omega_{\rm a}/\Omega_b$ as compared to other states.
 % This reduces the intensity stability requirement to $5~\mathrm{\%}$
 % instead of $0.3~\mathrm{\%}$ which is typical for other states.
-% In addition to the increased atomic coupling, $ \Omega_a $,
-% Coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $, with the intermediate state when compared to bound states of the other spin compositions.
+% In addition to the increased atomic coupling, $ \Omega_{\rm a} $,
+% Coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_{\rm m} $, with the intermediate state when compared to bound states of the other spin compositions.
 % $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
-Compared to $\Omega_a/\Omega_m \approx 0.003$
+Compared to $\Omega_{\rm a}/\Omega_{\rm m} \approx 0.003$
 for other combinations, this relaxes the intensity stability requirement to the percent level and enhances the Raman Rabi frequency.
@@
   \caption{Raman transition parameters as a function of tweezer power and detuning.
-    (a) The Raman resonance~($\omega_R$) fitted by $a_P+b_P/\Delta$, where
-    $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
+    (a) The Raman resonance~($\omega_{\rm R}$) fitted by $a_P+b_P/\Delta$, where
+    $a_P$ and $b_P=(\Omega_{\rm a}^2-\Omega_{\rm m}^2)/2$
     are the power ($P$) dependent background and $v'=0$ contributions
@@
     $a_P$ is fitted to a model including linear and small quadratic light shift
-    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
+    \todo{which assumes $\Omega_{\rm m}\gg\Omega_{\rm a}$} to obtain the Raman resonance frequency
     at zero tweezer power $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$ where the statistical uncertainty is shown.
-    (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
-    $c_P$ and $d_P=\Omega_a\Omega_m/2$
+    (b) Raman Rabi frequency ($\Omega_{\rm R}$) fitted to $c_P+d_P/\Delta$, where
+    $c_P$ and $d_P=\Omega_{\rm a}\Omega_{\rm m}/2$
     are the background and $v'=0$ contributions that scale as $P^{1.29}$ with optical power.
     The detuning is calculated from the PA frequency fitted in (a). Fit parameters are listed in Table~\ref{tab:f-det:fit}.
-    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
-    $b_P$ and $d_P$ on a log-log scale showing approximate $P^{0.5}$ scaling of $\Omega_m$ and
-    $P^{0.79}$ scaling of $\Omega_a$.
+    (c) Tweezer power dependency of $\Omega_{\rm m}$ (top) and $\Omega_{\rm a}$ (bottom) calculated from
+    $b_P$ and $d_P$ on a log-log scale showing approximate $P^{0.5}$ scaling of $\Omega_{\rm m}$ and
+    $P^{0.79}$ scaling of $\Omega_{\rm a}$.
     \label{f-det}}
@@
     Inset: Atomic scattering rate scales as
-    $P_\textrm{tweezer}^{2.58}\times\!2\pi\!\times1.05(6)~\mathrm{Hz/mW^{2.58}}$ on a log-log scale;
+    $P_{\mathrm{tweezer}}^{2.58}\times\!2\pi\!\times1.05(6)~\mathrm{Hz/mW^{2.58}}$ on a log-log scale;
     this is consistent with a two-photon scattering process.
@@
 To better understand the details and limitations of the Raman transfer process, we measured the properties of the two-photon resonance as a function of tweezer power and single-photon detuning.
-Known dependencies of the light shift and Raman Rabi frequency ($\Omega_R$) on detuning ($\Delta$) allow experimental determination of the Rabi frequencies
-$ \Omega_a $ and $\Omega_m$ whose ratio critically affects the transfer efficiency.
-Both the light shift and $\Omega_R$ follow a $1/\Delta$ slope as shown in Fig.~\ref{f-det}a, b and include a constant offset that we attribute to coupling to other excited states that are further away in energy.
-The $1/\Delta$ components due to the nearby $v'=0$ intermediate state determine $\Omega_m $ and $ \Omega_a $ in Table~\ref{tab:f-det:fit}.
+Known dependencies of the light shift and Raman Rabi frequency ($\Omega_{\rm R}$) on detuning ($\Delta$) allow experimental determination of the Rabi frequencies
+$ \Omega_{\rm a} $ and $\Omega_{\rm m}$ whose ratio critically affects the transfer efficiency.
+Both the light shift and $\Omega_{\rm R}$ follow a $1/\Delta$ slope as shown in Fig.~\ref{f-det}a, b and include a constant offset that we attribute to coupling to other excited states that are further away in energy.
+The $1/\Delta$ components due to the nearby $v'=0$ intermediate state determine $\Omega_{\rm m} $ and $ \Omega_{\rm a} $ in Table~\ref{tab:f-det:fit}.
 
@@
     $d~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$0.115(4)$&$0.275(6)$&$0.95(3)$\\ \hline
-    $\Omega_R~(\mathrm{2\pi\times kHz})$ & 0.49(2) & 1.18(3) & 3.97(9) \\
-    $\Omega_m~(\mathrm{2\pi\times MHz})$ & & & 348.3(3) \\
-    $\Omega_a~(\mathrm{2\pi\times kHz})$ & & & 5.5(2)
+    $\Omega_{\rm R}~(\mathrm{2\pi\times kHz})$ & 0.49(2) & 1.18(3) & 3.97(9) \\
+    $\Omega_{\rm m}~(\mathrm{2\pi\times MHz})$ & & & 348.3(3) \\
+    $\Omega_{\rm a}~(\mathrm{2\pi\times kHz})$ & & & 5.5(2)
   \end{tabular}
   \caption{Fitting results for Fig.~\ref{f-det}(a,b).
-$\Omega_R$ is reported at $-151~\mathrm{GHz}$ detuning from the $v' = 0$ state.
-The coefficients $\Omega_m$ and $\Omega_a$ are in broad agreement with our calculation and their ratio at $3.75~\mathrm{mW}$ is $0.016$, near the theory prediction of $0.013$.
-The measured Rabi rate $\Omega_R$ is only 63~\% of $\Omega_m \Omega_a/(2\Delta)$ due to interference from further-detuned Raman processes.
+$\Omega_{\rm R}$ is reported at $-151~\mathrm{GHz}$ detuning from the $v' = 0$ state.
+The coefficients $\Omega_{\rm m}$ and $\Omega_{\rm a}$ are in broad agreement with our calculation and their ratio at $3.75~\mathrm{mW}$ is $0.016$, near the theory prediction of $0.013$.
+The measured Rabi rate $\Omega_{\rm R}$ is only 63~\% of $\Omega_{\rm m} \Omega_{\rm a}/(2\Delta)$ due to interference from further-detuned Raman processes.
     \label{tab:f-det:fit}}
@@
 
-Figure~\ref{f-det}c shows the power dependence of $ \Omega_m $ and $ \Omega_a $, where $ \Omega_m $ scales like $ P^{1/2} $ as expected.
-As discussed previously, the scaling of $ \Omega_a $ is $P^{7/8}$ for weakly interacting particles.
+Figure~\ref{f-det}c shows the power dependence of $ \Omega_{\rm m} $ and $ \Omega_{\rm a} $, where $ \Omega_{\rm m} $ scales like $ P^{1/2} $ as expected.
+As discussed previously, the scaling of $ \Omega_{\rm a} $ is $P^{7/8}$ for weakly interacting particles.
 However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
 Coupled-channel calculations show that the wavefunction scaling
-is well approximated by $P^{0.29}$ within the range of confinement in our experiment and the expected scaling of $ \Omega_a \propto P^{0.79} $ agrees with the data.
-% At $3.75~\mathrm{mW}$ tweezer power, we measured $ \Omega_m = 2\pi \times 348.3(3)~\mathrm{MHz}$ and $ \Omega_a = 2\pi\times 5.5(2)~\mathrm{MHz}$, resulting in a
-% The measured $ \Omega_m/\Omega_a$ ratio of $ 63 $ is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
+is well approximated by $P^{0.29}$ within the range of confinement in our experiment and the expected scaling of $ \Omega_{\rm a} \propto P^{0.79} $ agrees with the data.
+% At $3.75~\mathrm{mW}$ tweezer power, we measured $ \Omega_{\rm m} = 2\pi \times 348.3(3)~\mathrm{MHz}$ and $ \Omega_{\rm a} = 2\pi\times 5.5(2)~\mathrm{MHz}$, resulting in a
+% The measured $ \Omega_{\rm m}/\Omega_{\rm a}$ ratio of $ 63 $ is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
 % Therefore, the matrix element ratio is not the cause of our lower than expected transfer efficiency.
@@
 % We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
-% From these measurements, we can extract a $\Omega_m$ of
+% From these measurements, we can extract a $\Omega_{\rm m}$ of
 
-% In order to calculate the ratio $\Omega_m/\Omega_a$,
-% we now need to extract $ \Omega_a $.
+% In order to calculate the ratio $\Omega_{\rm m}/\Omega_{\rm a}$,
+% we now need to extract $ \Omega_{\rm a} $.
 % We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
-% which depends on both $\Omega_m$ and $\Omega_a$.
+% which depends on both $\Omega_{\rm m}$ and $\Omega_{\rm a}$.
 % The Raman Rabi frequency shows a non-linear dependency on the tweezer power
@@
 % or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ %tweezer power.
-% Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
+% Together with the $\Omega_{\rm m}$ measured above, the Rabi frequency, $\Omega_{\rm a}$, is
 % $2\pi\times 5.5(2)~\mathrm{MHz}$.
-% This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $63(3)$,
+% This gives a matrix-element ratio $\Omega_{\rm m}/\Omega_{\rm a}$ of $63(3)$,
 % which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
@@
 Atom loss is shown to be small in Fig.~\ref{f-lifetime}b by measuring the two-body lifetimes of the atoms directly without the second Raman frequency.
-In principle, destructive interference that reduces the Raman Rabi rate ($\Omega_R$) for negative detunings ($\Delta$) changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.
-More negative detunings than XXX~GHz that might reduce the scattering rate were prevented by vanishing of $\Omega_R$.
+In principle, destructive interference that reduces the Raman Rabi rate ($\Omega_{\rm R}$) for negative detunings ($\Delta$) changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.
+More negative detunings than XXX~GHz that might reduce the scattering rate were prevented by vanishing of $\Omega_{\rm R}$.
 
@@
 fluctuations of the tweezer intensity and magnetic field, although the shape of the Rabi oscillation in Fig.~{f-raman}b indicates that loss rather than frequency fluctuations are responsible for decoherence.
-Based on the ratio between $\Omega_R$ and the light shift, 
+Based on the ratio between $\Omega_{\rm R}$ and the light shift,
 the requirement on the tweezer intensity stability is $1\mathrm{\%}$ at $3.75~\mathrm{mW}$ power.
@@
 
-\TR{Remove $\delta$ in Fig. 1a.}
-
-\TR{Change 1b horizontal axis to ``Laser frequency''?}
-
 \TR{Insert lower practical limit for $\Delta$ as ``XXX GHz'' on last page.}

### 2020-12-09 sm.tex
Update on Overleaf.
subscript font

@@
 \begin{document}
-\title{Coherent optical association of a single molecule -- Supplemental material}
+\title{Coherent optical creation of a single molecule -- Supplemental material}
 \author{Yichao~Yu}
@@
 Thus, there is significant cross coupling for the scattering rate and light shift, where each state is coupled to the excited state by the power in both beams.
-Under these conditions, the scattering rate and light shift is proportional to the total power $P_{\text{tot}} = P_m + P_a$, where $P_{m} (P_{a})$ is the power in the beam that addresses the molecular (atomic) state.
-The Raman Rabi frequency is proportional to $\sqrt{P_mP_a} $. 
-With a fixed total power and thus fixed scattering rate, the Raman Rabi frequency is maximized when $ P_m = P_a = P_{\text{tot}}/2$.
+Under these conditions, the scattering rate and light shift is proportional to the total power $P_{\text{tot}} = P_{\rm m} + P_{\rm a}$, where $P_{\rm m} (P_{\rm a})$ is the power in the beam that addresses the molecular (atomic) state.
+The Raman Rabi frequency is proportional to $\sqrt{P_{\rm m}P_{\rm a}} $.
+With a fixed total power and thus fixed scattering rate, the Raman Rabi frequency is maximized when $ P_{\rm m} = P_{\rm a} = P_{\text{tot}}/2$.
 
-For the purposes of this work, we denote $\Omega_a $($\Omega_m$) as the Rabi frequencies to drive a transition from the atom (target molecule) state to the intermediate state used in the Raman transition corresponding to the power in a single beam, $P_a$ ($P_m$).
-Thus, the Raman Rabi frequency is $\Omega_a\Omega_m/(2\Delta)$, where $ \Delta $ is the single photon detuning. 
-Cross coupling affects the scattering rate and light shift, and assuming equal powers in both beams, these quantities become $ \Gamma_e \Omega_m^2 / (2\Delta^2) + \Gamma_e \Omega_a^2 / (2\Delta^2) $ and $ \Omega_m^2/(2\Delta) - \Omega_a^2/(2\Delta) $, where $\Gamma_e$ is the excited state linewidth.
-Since $ \Omega_m >> \Omega_a $, the scattering rate and light shift can be approximated as $ \Gamma_e \Omega_m^2/(2\Delta^2)$ and $\Omega_m^2/(2\Delta)$.
+For the purposes of this work, we denote $\Omega_{\rm a} $($\Omega_{\rm m}$) as the Rabi frequencies to drive a transition from the atom (target molecule) state to the intermediate state used in the Raman transition corresponding to the power in a single beam, $P_{\rm a}$ ($P_{\rm m}$).
+Thus, the Raman Rabi frequency is $\Omega_{\rm a}\Omega_{\rm m}/(2\Delta)$, where $ \Delta $ is the single photon detuning.
+Cross coupling affects the scattering rate and light shift, and assuming equal powers in both beams, these quantities become $ \Gamma_{\rm e} \Omega_{\rm m}^2 / (2\Delta^2) + \Gamma_{\rm e} \Omega_{\rm a}^2 / (2\Delta^2) $ and $ \Omega_{\rm m}^2/(2\Delta) - \Omega_{\rm a}^2/(2\Delta) $, where $\Gamma_{\rm e}$ is the excited state linewidth.
+Since $ \Omega_{\rm m} >> \Omega_{\rm a} $, the scattering rate and light shift can be approximated as $ \Gamma_{\rm e} \Omega_{\rm m}^2/(2\Delta^2)$ and $\Omega_{\rm m}^2/(2\Delta)$.
 
@@
 \begin{equation}
-  \Omega_R = \frac{d^2E^2}{2\hbar^2} \displaystyle\sum_{v'} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}}
+  \Omega_{\rm R} = \frac{d^2E^2}{2\hbar^2} \displaystyle\sum_{v'} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}}
 \end{equation}
@@
 \begin{equation}
-  \Omega_R = \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' > v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}}
+  \Omega_{\rm R} = \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' > v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}}
 \end{equation}
@@
 \begin{equation}
-  \Omega_R \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\displaystyle\sum_{v' > v'_{\text{max}}} \braket{a|v'}\braket{v'|m}  \label{rabifreq}
+  \Omega_{\rm R} \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\displaystyle\sum_{v' > v'_{\text{max}}} \braket{a|v'}\braket{v'|m}  \label{rabifreq}
 \end{equation}
@@
 \begin{equation}
-  \Omega_R \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} -  \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\displaystyle\sum_{v' \leq v'_{\text{max}}} \braket{a|v'}\braket{v'|m}
+  \Omega_{\rm R} \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} -  \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\displaystyle\sum_{v' \leq v'_{\text{max}}} \braket{a|v'}\braket{v'|m}
 \end{equation}
@@
 \begin{align}
-  \Gamma_s &= \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} + \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' > v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} \\
+  \Gamma_{\rm s} &= \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} + \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' > v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} \\
            &\approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} + \frac{d^2E^2\Gamma}{2\hbar^2\Delta_{\text{thresh}}^2}\displaystyle\sum_{v' > v'_{\text{max}}}\braket{m|v'}\braket{v'|m}
@@
 \begin{equation}
-  \Gamma_s \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} +  \frac{d^2E^2\Gamma}{2\hbar^2\Delta_{\text{thresh}}^2}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right)
+  \Gamma_{\rm s} \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} +  \frac{d^2E^2\Gamma}{2\hbar^2\Delta_{\text{thresh}}^2}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right)
 \end{equation}
@@
 In this calculation, there is a matrix element, $\Omega_{ai}, \Omega_{mi}$ between each channel $ i $ of the coupled channel ground state and an excited state.
-The total Raman Rabi frequency $ \Omega_R$, light shift $ \delta$ and off-resonant scattering $ \Gamma_S $ contribution from this single excited state is calculated as
+The total Raman Rabi frequency $ \Omega_{\rm R}$, light shift $ \delta$ and off-resonant scattering $ \Gamma_{\rm s} $ contribution from this single excited state is calculated as
 
 \begin{align}
-  \Omega_{R} &= \displaystyle\sum_{i} \frac{\Omega_{ai} \Omega_{mi}}{2\Delta} \\
+  \Omega_{\rm R} &= \displaystyle\sum_{i} \frac{\Omega_{ai} \Omega_{mi}}{2\Delta} \\
   \delta &= \displaystyle\sum_{i} \frac{\Omega_{ai}^2 - \Omega_{mi}^2}{2\Delta} \\
-  \Gamma_S &= \displaystyle\sum_{i} \Gamma_e \frac{\Omega_{ai}^2 + \Omega_{mi}^2}{2\Delta^2}
+  \Gamma_{\rm s} &= \displaystyle\sum_{i} \Gamma_{\rm e} \frac{\Omega_{ai}^2 + \Omega_{mi}^2}{2\Delta^2}
 \end{align}
 
-where $ \Delta $ is the single photon detuning and $ \Gamma_e $ is the excited state linewidth.
-The experiment, through measuring the detuning dependence of the Raman Rabi frequency and the resonance frequency, extracts a single $ \Omega_m $ and $ \Omega_a $.
-In order to compare to the theory, we introduce effective $ \Omega_a', \Omega_m', \Gamma_e'$, so that $ \Omega_R = \Omega_a'\Omega_m'/(2\Delta) $, $\delta = (\Omega_{a}'^2 - \Omega_{m}'^2)/(2\Delta) $, and $\Gamma_S = \Gamma_e'(\Omega_{a}'^2 + \Omega_{m}'^2)/(2\Delta^2) $.
+where $ \Delta $ is the single photon detuning and $ \Gamma_{\rm e} $ is the excited state linewidth.
+The experiment, through measuring the detuning dependence of the Raman Rabi frequency and the resonance frequency, extracts a single $ \Omega_{\rm m} $ and $ \Omega_{\rm a} $.
+In order to compare to the theory, we introduce effective $ \Omega_{\rm a}', \Omega_{\rm m}', \Gamma_{\rm e}'$, so that $ \Omega_{\rm R} = \Omega_{\rm a}'\Omega_{\rm m}'/(2\Delta) $, $\delta = (\Omega_{\rm a}'^2 - \Omega_{\rm m}'^2)/(2\Delta) $, and $\Gamma_{\rm s} = \Gamma_{\rm e}'(\Omega_{\rm a}'^2 + \Omega_{\rm m}'^2)/(2\Delta^2) $.
 The effective Rabi frequencies for the $v' = 0$ state of $ c^3\Sigma^+_1$ and their ratio are reported in Table~\ref{tab:sm} at $3.75~\mathrm{mW}$ of tweezer power.
@@
   \begin{tabular}{|c|c|} \hline
-  $\Omega_m'$ &  $2\pi \times 573 ~\mathrm{MHz}$ \\
-  $\Omega_a'$ &  $2\pi \times 7.37 ~\mathrm{MHz}$ \\
-  $\Omega_a'/\Omega_m'$ & $ 0.013 $ \\ \hline
+    $\Omega_{\rm m}'$ &  $2\pi \times 573 ~\mathrm{MHz}$ \\
+    $\Omega_{\rm a}'$ &  $2\pi \times 7.37 ~\mathrm{MHz}$ \\
+    $\Omega_{\rm a}'/\Omega_{\rm m}'$ & $ 0.013 $ \\ \hline
   \end{tabular}
@@
 
-Since our coupled-channel calculations include the harmonic confinement, we can calculate the enhancement in $\Omega_a$ with increasing confinement.
-Using two calculations with $ \omega_{\text{trap}} = 36.5~\mathrm{kHz}$ and $\omega_{\text{trap}} = 80~\mathrm{kHz}$ trapping frequencies, and assuming a power law scaling, we find $ \Omega_a \propto \omega_{\text{trap}}^{0.58} $.
-Thus, $\Omega_a \propto P^{0.29} $, which was also experimentally verified.
+Since our coupled-channel calculations include the harmonic confinement, we can calculate the enhancement in $\Omega_{\rm a}$ with increasing confinement.
+Using two calculations with $ \omega_{\text{trap}} = 36.5~\mathrm{kHz}$ and $\omega_{\text{trap}} = 80~\mathrm{kHz}$ trapping frequencies, and assuming a power law scaling, we find $ \Omega_{\rm a} \propto \omega_{\text{trap}}^{0.58} $.
+Thus, $\Omega_{\rm a} \propto P^{0.29} $, which was also experimentally verified.
 However, we note that in the actual experiment, our system does not have spherically symmetric confinement.

### 2020-12-09 paper.tex
Jeremy comment

@@
 
-Diverse species of fully quantum controlled  ultracold molecules are desired
+Diverse species of fully quantum-controlled ultracold molecules are desired
 for a variety of applications including precision measurements~\cite{
@@
 through a magnetic Feshbach scattering resonance.
-Exceptions include Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states
+Exceptions include Sr$_2$, where narrow-linewidth ($\sim 20~\mathrm{kHz}$) excited states
 are available and optical association can be driven coherently~\cite{Stellmer2012,Reinaudi2012},
@@
 we choose the initial and final states that balance the two Rabi frequencies as much as possible.
-This approach applies to a variety of molecules that can be created atom-by-atom with full quantum state control.
+This approach applies to a variety of molecules that can be created atom-by-atom
+with full quantum-state control.
 
@@
     The transition is driven by a pair of laser frequencies whose difference ($< 1$~GHz) matches the molecular binding energy.
-    The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
-    by $\Delta$ in order to reduce scattering during the transfer.
+    The lasers are detuned by $\Delta$ from an excited molecular state
+    in the $\mathrm{c^3\Sigma}$ electronic state
+    in order to reduce scattering during the transfer.
     (b) Calculation of the scattering rate vs. laser frequency
@@
   \caption{
-    Beampath for generating two frequencies in the tweezer for the Raman transition (only essential optics shown.)
+    Beam path for generating two frequencies in the tweezer for the Raman transition (only essential optics shown.)
     Two  filters, one directly after the laser source and one after both optical fibers clean the light from a fiber amplifier seeded by an external cavity diode laser.
@@
 
-To better understand the details and limitations of the Raman transfer process, we measured the properties of the two-photon resonance as a function of tweezer power and single-photon detuning.
+To understand the details and limitations of the Raman transfer process better,
+we measured the properties of the two-photon resonance as a function of tweezer power and single-photon detuning.
 Known dependencies of the light shift and Raman Rabi frequency ($\Omega_{\rm R}$) on detuning ($\Delta$) allow experimental determination of the Rabi frequencies
@@
 
-Figure~\ref{f-det}c shows the power dependence of $ \Omega_{\rm m} $ and $ \Omega_{\rm a} $, where $ \Omega_{\rm m} $ scales like $ P^{1/2} $ as expected.
+Figure~\ref{f-det}c shows the power dependence of $ \Omega_{\rm m} $ and $ \Omega_{\rm a} $, where $ \Omega_{\rm m} $ scales as $ P^{1/2} $ as expected.
 As discussed previously, the scaling of $ \Omega_{\rm a} $ is $P^{7/8}$ for weakly interacting particles.
@@
 % or a different intrinsic or technical source for which we have not accounted for.
-From experimental measurements, the Raman transfer efficiency is limited by the molecular lifetime, together with a reduction in the Raman Rabi frequency due to destructive interference with intermediate states beyond v'=0 (see Table~~\ref{tab:f-det:fit}).
+From experimental measurements, the Raman transfer efficiency is limited by the molecular lifetime, together with a reduction in the Raman Rabi frequency due to destructive interference with intermediate states beyond $v'=0$ (see Table~~\ref{tab:f-det:fit}).
 We discuss loss and decoherence below.
@@
 A theoretical investigation including 8 excited state potentials,
-the excited atomic continuum, and coupled-channel ground state wavefunctions indicates
+the excited atomic continuum, and coupled-channel ground-state wavefunctions indicates
 the potential for higher transfer efficiency than the observed value of $69$~\%.
@@
 or a narrow excited state. The formation of weakly bound molecules is a key step
-in forming rovibrational ground state molecules.
+in forming rovibrational ground-state molecules.
 By scaling up to many optical tweezers~\cite{Endres2016, Barredo2018,  PhysRevLett.122.203601}, large arrays with arbitrary geometry of highly controlled molecules can be achieved.

### 2020-12-09 paper.tex
one more subscript font

@@
     \todo{which assumes $\Omega_{\rm m}\gg\Omega_{\rm a}$} to obtain the Raman resonance frequency
-    at zero tweezer power $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$ where the statistical uncertainty is shown.
+    at zero tweezer power $\omega_{\rm R0}=2\pi\times770.1969(2)~\mathrm{MHz}$ where the statistical uncertainty is shown.
     (b) Raman Rabi frequency ($\Omega_{\rm R}$) fitted to $c_P+d_P/\Delta$, where

### 2020-12-09 paper.tex
Update on Overleaf.

@@
     % The two frequencies are recombined on the DP AOM.
-    To reduce power fluctuations, the $0^{\mathrm{th}}$ order light is shifted by another single pass~(SP) AOM before recombination, preventing interference with leakage light from the DP AOM~[[TR: What frequency is the leakage light?
-]].
+    To reduce interferences that cause relative power fluctuation of the two frequencies, the $0^{\mathrm{th}}$ order is frequency shifted by $-80$~MHz before recombination.
     % be at the same frequency
@@
     % due to interference.
-    The experiment typically starts with the SP AOM on and the DP AOM off.
+    The experiment typically starts with the single-pass (SP) AOM on and the DP AOM off.
     When driving the Raman transition, the RF powers for both AOMs are ramped simultaneously
-    to achieve the desired power at both frequencies, while keeping the total power fixed.
+    to achieve the desired optical power at both frequencies, while keeping the total optical power fixed.
     \label{f-beampath}
@@
 In principle, destructive interference that reduces the Raman Rabi rate ($\Omega_{\rm R}$) for negative detunings ($\Delta$) changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.
-More negative detunings than XXX~GHz that might reduce the scattering rate were prevented by vanishing of $\Omega_{\rm R}$.
+More negative detunings that might reduce the scattering rate were prevented by vanishing of $\Omega_{\rm R}$.
 

### 2020-12-09 paper.tex
Typo

--- 2020-12-09 paper.tex
@@
 \end{figure}
-Afr merging the tweezers, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ with a large scattering length
+After merging the tweezers, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ with a large scattering length
 by performing a Cs spin flip while taking into account

### 2020-12-09 paper.tex
Update on Overleaf.

@@
     The transition is driven by a pair of laser frequencies whose difference ($< 1$~GHz) matches the molecular binding energy.
-    The lasers are detuned by $\Delta$ from an excited molecular state
-    in the $\mathrm{c^3\Sigma}$ electronic state
+    The lasers are detuned by $\Delta$ from an excited vibrational sublevel
+    in the $\mathrm{c^3\Sigma^+(\Omega = 1)}$ electronic state
     in order to reduce scattering during the transfer.
@@
     than the higher sublevel (orange).
-    (d) The large scattering length for $\Na(2,2),\Cs(3,3)$ is associated with enhancementment of the relative wavefunction at short
+    (d) The large scattering length for $\Na(2,2),\Cs(3,3)$ is associated with enhancement of the relative wavefunction at short
     internuclear distance ($R$).
@@
 and scattering losses are dominated by the final state.
-Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning of $80$ to $200$~GHz, causing the target molecular state to scatter both beams nearly equally with a total rate $ \Gamma_{\rm e} \Omega_{\rm m}^2 / (2\Delta^2)$, where $ \Gamma_{\rm e} $ is the excited-state linewidth~\footnote{The two beams have equal power to maximize the Raman Rabi frequency at fixed total power, resulting in a factor of 2 for scattering two beams.}.
+Because the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning of $80$ to $200$~GHz, both beams scatter nearly equally with a total rate $ \Gamma_{\rm e} \Omega_{\rm m}^2 / (2\Delta^2)$, where $ \Gamma_{\rm e} $ is the excited-state linewidth.
+The two beams have equal power to maximize the Raman Rabi frequency at fixed total power.
 In this idealized treatment, the ratio between the Raman Rabi frequency and the scattering rate is $ \Omega_{\rm a}/\Omega_{\rm m} \times \Delta/\Gamma_{\rm e} $, which limits the transfer efficiency into the molecular state.
-At the same time, the intensity-stability requirement is determined by the ratio of Raman Rabi frequency to light shift ($\Omega_{\rm a}/\Omega_{\rm m}$)~\footnote{There is an additional factor of 2, with both beams at equal power,
-  to account for the Stark shift caused by both beams.}.
+At the same time, the intensity-stability requirement is determined by the ratio of Raman Rabi frequency to light shift $\Omega_{\rm a}/\Omega_{\rm m}$.
 Notably, both figures of merit improve with a larger ratio $\Omega_{\rm a}/\Omega_{\rm m}$.
@@
     (a) Raman difference frequency scans for various durations
-    showing the resonance as the detuning from
+    showing the resonance as a function of the detuning from
     the fitted resonance at $770.5715(1)$~MHz, near the calculated value of $763$~MHz.
@@
   \caption{Raman transition parameters as a function of tweezer power and detuning.
-    (a) The Raman resonance~($\omega_{\rm R}$) fitted by $a_P+b_P/\Delta$, where
+    (a) The Raman resonance $\omega_{\rm R}$ fitted to $a_P+b_P/\Delta$, where
     $a_P$ and $b_P=(\Omega_{\rm a}^2-\Omega_{\rm m}^2)/2$
@@
     to the light shift and
-    $\Delta\equiv2\pi\times\paren{f_0 - f_{\mathrm{tweezer}}}$ is the detuning from
-    the $v'=0$ resonance frequency $f_0$.
+    $\Delta\equiv2\pi\times\paren{f_{\mathrm{PA}0} - f_{\mathrm{tweezer}}}$ is the detuning from
+    the $v'=0$ resonance frequency $f_{\mathrm{PA}0}$.
     $a_P$ is fitted to a model including linear and small quadratic light shift
@@
     at zero tweezer power $\omega_{\rm R0}=2\pi\times770.1969(2)~\mathrm{MHz}$ where the statistical uncertainty is shown.
-    (b) Raman Rabi frequency ($\Omega_{\rm R}$) fitted to $c_P+d_P/\Delta$, where
+    (b) Raman Rabi frequency $\Omega_{\rm R}$ fitted to $c_P+d_P/\Delta$, where
     $c_P$ and $d_P=\Omega_{\rm a}\Omega_{\rm m}/2$
-    are the background and $v'=0$ contributions that scale as $P^{1.29}$ with optical power.
-    The detuning is calculated from the PA frequency fitted in (a). Fit parameters are listed in Table~\ref{tab:f-det:fit}.
+    are the background and $v'=0$ contributions that scale as $P^{1.29}$.
+    The detuning is calculated from $f_{\mathrm{PA}0}$ fitted in (a). Fit parameters are listed in Table~\ref{tab:f-det:fit}.
     (c) Tweezer power dependency of $\Omega_{\rm m}$ (top) and $\Omega_{\rm a}$ (bottom) calculated from
@@
 we measured the properties of the two-photon resonance as a function of tweezer power and single-photon detuning.
-Known dependencies of the light shift and Raman Rabi frequency ($\Omega_{\rm R}$) on detuning ($\Delta$) allow experimental determination of the Rabi frequencies
+Known dependencies of the light shift and Raman Rabi frequency $\Omega_{\rm R}$ on detuning $\Delta$ allow experimental determination of the Rabi frequencies
 $ \Omega_{\rm a} $ and $\Omega_{\rm m}$ whose ratio critically affects the transfer efficiency.
@@
 $\Omega_{\rm R}$ is reported at $-151~\mathrm{GHz}$ detuning from the $v' = 0$ state.
-The coefficients $\Omega_{\rm m}$ and $\Omega_{\rm a}$ are in broad agreement with our calculation and their ratio at $3.75~\mathrm{mW}$ is $0.016$, near the theory prediction of $0.013$.
+At $3.75~\mathrm{mW}$, $\Omega_{\rm m}/\Omega_{\rm a}=0.016$, near the theory prediction of $0.013$.
 The measured Rabi rate $\Omega_{\rm R}$ is only 63~\% of $\Omega_{\rm m} \Omega_{\rm a}/(2\Delta)$ due to interference from further-detuned Raman processes.
@@
 Atom loss is shown to be small in Fig.~\ref{f-lifetime}b by measuring the two-body lifetimes of the atoms directly without the second Raman frequency.
-In principle, destructive interference that reduces the Raman Rabi rate ($\Omega_{\rm R}$) for negative detunings ($\Delta$) changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.
+In principle, destructive interference that reduces the Raman Rabi rate $\Omega_{\rm R}$ for negative detunings $\Delta$ changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.
 More negative detunings that might reduce the scattering rate were prevented by vanishing of $\Omega_{\rm R}$.
@@
 of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities. Other potential decoherence sources include
-fluctuations of the tweezer intensity and magnetic field, although the shape of the Rabi oscillation in Fig.~{f-raman}b indicates that loss rather than frequency fluctuations are responsible for decoherence.
+fluctuations of the tweezer intensity and magnetic field, although the shape of the Rabi oscillation in Fig.~\ref{f-raman}b indicates that loss rather than frequency fluctuations are responsible for decoherence.
 Based on the ratio between $\Omega_{\rm R}$ and the light shift,
@@
 
-\TR{Freq./mechanism of leakage light in Fig. 2?}
-
-\TR{Insert lower practical limit for $\Delta$ as ``XXX GHz'' on last page.}
+\TR{What is meant by ``result is consistent with the decay of the Rabi oscillation'' if independent fits not done?  See also Fig.~5 caption.}
 

### 2020-12-10 paper.tex
Revert discussion about the molecular lifetime fit

--- 2020-12-09 paper.tex
@@
     Molecule survival is detected by dissociating back to atoms via a second Raman transition.
-    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
-    measured from the Raman transition data.
+    The lifetime is consistent with the decay of the Rabi oscillation in Fig.~\ref{f-raman}b.
     Inset: pulse sequence for the lifetime measurement.
@@
 
-The molecular lifetime of $0.199(9)~\mathrm{ms}$ in Fig.~\ref{f-lifetime}a is measured by preparing the molecule with a $\pi$-pulse,
+The molecular lifetime measurement in Fig.~\ref{f-lifetime}a is performed
+by preparing the molecule with a $\pi$-pulse,
 followed after a variable delay by a second dissociating $\pi$-pulse.
-This result is
-consistent with the decay of the Rabi oscillation in Fig.~\ref{f-raman}b.
-Preliminary experiments and theoretical considerations indicate that the molecular lifetime may be limited by two-photon coupling to the atomic continuum~\cite{YichaoYu}.
-Atom loss is shown to be small in Fig.~\ref{f-lifetime}b by measuring the two-body lifetimes of the atoms directly without the second Raman frequency.
-In principle, destructive interference that reduces the Raman Rabi rate ($\Omega_{\rm R}$) for negative detunings ($\Delta$) changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.
-More negative detunings that might reduce the scattering rate were prevented by vanishing of $\Omega_{\rm R}$.
+Together with the Rabi oscillation in Fig.~\ref{f-raman}b,
+we obtain a molecule lifetime of $0.199(9)~\mathrm{ms}$.
+Preliminary experiments and theoretical considerations indicate that
+the molecular lifetime may be limited by two-photon coupling
+to the atomic continuum~\cite{YichaoYu}.
+Atom loss is shown to be small in Fig.~\ref{f-lifetime}b
+by measuring the two-body lifetimes of the atoms directly
+without the second Raman frequency.
+In principle, destructive interference that reduces the Raman Rabi rate~($\Omega_{\rm R}$)
+for negative detunings ($\Delta$) changes to constructive interference
+for positive detunings, but additional molecular resonances make the positive region unusable.
+More negative detunings that might reduce the scattering rate
+were prevented by vanishing of $\Omega_{\rm R}$.
 

### 2020-12-10 paper.tex

--- 2020-12-09 paper.tex
@@
 
-The molecular lifetime of $0.199(9)~\mathrm{ms}$ in Fig.~\ref{f-lifetime}a is measured by preparing the molecule with a $\pi$-pulse,
+The molecular lifetime measurement in Fig.~\ref{f-lifetime}a is performed
+by preparing the molecule with a $\pi$-pulse,
 followed after a variable delay by a second dissociating $\pi$-pulse.
-This result is
-consistent with the decay of the Rabi oscillation in Fig.~\ref{f-raman}b.
-Preliminary experiments and theoretical considerations indicate that the molecular lifetime may be limited by two-photon coupling to the atomic continuum~\cite{YichaoYu}.
-Atom loss is shown to be small in Fig.~\ref{f-lifetime}b by measuring the two-body lifetimes of the atoms directly without the second Raman frequency.
-In principle, destructive interference that reduces the Raman Rabi rate $\Omega_{\rm R}$ for negative detunings $\Delta$ changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.
-More negative detunings that might reduce the scattering rate were prevented by vanishing of $\Omega_{\rm R}$.
+Together with the Rabi oscillation in Fig.~\ref{f-raman}b,
+we obtain a molecule lifetime of $0.199(9)~\mathrm{ms}$.
+Preliminary experiments and theoretical considerations indicate that
+the molecular lifetime may be limited by two-photon coupling
+to the atomic continuum~\cite{YichaoYu}.
+Atom loss is shown to be small in Fig.~\ref{f-lifetime}b
+by measuring the two-body lifetimes of the atoms directly
+without the second Raman frequency.
+In principle, destructive interference that reduces the Raman Rabi rate $\Omega_{\rm R}$
+for negative detunings $\Delta$ changes to constructive interference
+for positive detunings, but additional molecular resonances make the positive region unusable.
+More negative detunings that might reduce the scattering rate
+were prevented by vanishing of $\Omega_{\rm R}$.
 

### 2020-12-10 sm.tex

@@
 the contribution of the other seven potentials is mainly to a background that is nearly detuning independent.
-Thus, for computational ease, we use the diabatic potentials for $ \mathrm{b^3\Pi_{0}, b^3\Pi_{1}} $ and $ \mathrm{A^1\Sigma^+_{0^+}}$, and remove the states nearest to the $ v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $.
+Thus, for computational ease, we use the diabatic potentials for $ \mathrm{b^3\Pi_{0}, b^3\Pi_{1}} $ and $ \mathrm{A^1\Sigma^+_{0^+}}$.
+%and remove the states nearest to the $ v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $.
 Lastly, to our knowledge, no potential fit to experimental data exists for the $ c^3\Sigma^+_{0^-}$ state.
@@
 These calculations assume that the intermediate states have pure singlet or triplet character and neglect its
-nuclear spin character, which is unknown. These calculations include theoretical electronic transition dipole moments\footnote{Private communication with R. Gonzalez-Ferez and R. Moszynski}
+nuclear spin character, which is unknown. These calculations include theoretical electronic transition dipole moments~\footnote{Private communication with R. Gonzalez-Ferez and R. Moszynski}.
 
@@
 
-In this calculation, there is a matrix element, $\Omega_{ai}, \Omega_{mi}$ between each channel $ i $ of the coupled channel ground state and an excited state.
+In this calculation, there is a matrix element, $\Omega_{\mathrm{a}i}, \Omega_{\mathrm{m}i}$ between each channel $ i $ of the coupled channel ground state and an excited state.
 The total Raman Rabi frequency $ \Omega_{\rm R}$, light shift $ \delta$ and off-resonant scattering $ \Gamma_{\rm s} $ contribution from this single excited state is calculated as
@@
 \begin{align}
-  \Omega_{\rm R} &= \displaystyle\sum_{i} \frac{\Omega_{ai} \Omega_{mi}}{2\Delta} \\
-  \delta &= \displaystyle\sum_{i} \frac{\Omega_{ai}^2 - \Omega_{mi}^2}{2\Delta} \\
-  \Gamma_{\rm s} &= \displaystyle\sum_{i} \Gamma_{\rm e} \frac{\Omega_{ai}^2 + \Omega_{mi}^2}{2\Delta^2}
+  \Omega_{\rm R} &= \displaystyle\sum_{i} \frac{\Omega_{\mathrm{a}i} \Omega_{\mathrm{m}i}}{2\Delta} \\
+  \delta &= \displaystyle\sum_{i} \frac{\Omega_{\mathrm{a}i}^2 - \Omega_{\mathrm{m}i}^2}{2\Delta} \\
+  \Gamma_{\rm s} &= \displaystyle\sum_{i} \Gamma_{\rm e} \frac{\Omega_{\mathrm{a}i}^2 + \Omega_{\mathrm{m}i}^2}{2\Delta^2}
 \end{align}
@@
 Since our coupled-channel calculations include the harmonic confinement, we can calculate the enhancement in $\Omega_{\rm a}$ with increasing confinement.
-Using two calculations with $ \omega_{\text{trap}} = 36.5~\mathrm{kHz}$ and $\omega_{\text{trap}} = 80~\mathrm{kHz}$ trapping frequencies, and assuming a power law scaling, we find $ \Omega_{\rm a} \propto \omega_{\text{trap}}^{0.58} $.
-Thus, $\Omega_{\rm a} \propto P^{0.29} $, which was also experimentally verified.
+Using two calculations with $ \omega_{\text{trap}} = 36.5~\mathrm{kHz}$ and $\omega_{\text{trap}} = 80~\mathrm{kHz}$ trapping frequencies, and assuming a power law scaling, we find that the wavefunction overlap scales as $ \omega_{\text{trap}}^{0.58} = P^{0.29} $.
+Thus, $\Omega_{\rm a} \propto P^{0.79} $, which was also experimentally verified.
 However, we note that in the actual experiment, our system does not have spherically symmetric confinement.

### 2020-12-11 paper.tex
Update on Overleaf.

@@
 \author{Yichao~Yu}
+\thanks{Y.Y.~and K.W.~contributed equally to this work.}
 \email{yichaoyu@g.harvard.edu}
@@
 \author{Kenneth~Wang}
+\thanks{Y.Y.~and K.W.~contributed equally to this work.}
 \gradstudent
@@
 \affiliation{Joint Quantum Centre Durham-Newcastle, Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
+\author{Rosario Gonzalez-Ferez}
+\affiliation{Instituto Carlos I de F\'{\i}sica Te\'orica y Computacional, and Departamento de F\'{\i}sica At\'omica, Molecular y Nuclear,  Universidad de Granada, 18071 Granada, Spain}
 \author{Till Rosenband}
@@
 and $^{87}$Rb$^{85}$Rb with molecular states bound by only $1-2~\mathrm{MHz}$~\cite{He331}.
-With these requirements, molecules involving non-magnetic atoms
+With these requirements, molecules involving non-magnetic atoms~\cite{PhysRevX.10.031037}
 or atoms without narrow intercombination lines remain difficult to associate.
@@
 \begin{acknowledgments}
-  We thank Rosario Gonzalez-Ferez, Olivier Dulieu, Bo Gao, and Paul Julienne for discussion and Robert Moszynski for providing theoretical transition dipole moments of NaCs.
+  We thank Bo Gao and Paul Julienne for discussion and Robert Moszynski for providing theoretical transition dipole moments of NaCs.
 This work is supported by the NSF~(PHY-1806595), the AFOSR~(FA9550-19-1-0089), ARO DURIP (W911NF1810194) and the Arnold and Mabel Beckman foundation.

### 2020-12-14 scripts/plot_exp_data.jl
....................

@@ -152,6 +152,10 @@ const plot_time = linspace(0, 0.79, 1000)
 const plot_pa_time = linspace(0, 21, 1000)
 const plot_m_time = linspace(0, 1.55, 1000)
 
+fit_m = fit_survival(model_exp, data_nacs_m[1:end - 1], [0.3, 5.0, 0],
+                     lower=zeros(3))
+@show fit_m.uncs
+
 const data_nacs_12′ = NaCsData.map_params((i, v)->v - param_1[3], data_nacs_12)
 const data_nacs_25′ = NaCsData.map_params((i, v)->v - param_1[3], data_nacs_25)
 

### 2020-12-15 paper.tex
Update on Overleaf.

@@
 \newcommand{\agendile}{\affiliation{Agendile LLC, Cambridge, Massachusetts 02139, USA}}
+\newcommand{\itamp}{\affiliation{ITAMP, Harvard-Smithsonian Center for Astrophysics, Cambridge, Massachusetts 02138, USA}}
 \newcommand{\gradstudent}{
@@
 \thanks{Y.Y.~and K.W.~contributed equally to this work.}
-\email{yichaoyu@g.harvard.edu}
 \gradstudent
@@
 \affiliation{Instituto Carlos I de F\'{\i}sica Te\'orica y Computacional, and Departamento de F\'{\i}sica At\'omica, Molecular y Nuclear,  Universidad de Granada, 18071 Granada, Spain}
+\itamp
 \author{Till Rosenband}
@@
 \author{Kang-Kuen~Ni}
-\email{ni@chemistry.harvard.edu}
+\email[To whom correspondence should be addressed: ]{ni@chemistry.harvard.edu}
 \harvardccb
@@
 by two-photon optical Raman transfer via an electronic excited state,
-as shown in Fig.~\ref{f-theory}a.
+as shown in Fig.~\ref{f-theory}a, taking NaCs as the prototype system.
 The technique does not rely on a Feshbach resonance,
@@
 
-\begin{figure}
-  \includegraphics[width=0.5\textwidth]{imgs/raman_spectroscopy_raman_beampath.pdf}
-  \caption{
-    Beam path for generating two frequencies in the tweezer for the Raman transition (only essential optics shown.)
-    Two filters, one directly after the laser source and one after both optical fibers clean the light from a fiber amplifier seeded by an external cavity diode laser.
-    The red beam path is the always-present $0^{\mathrm{th}}$ order of the double pass~(DP) AOM.
-    The blue beam path is the switchable $1^{\mathrm{st}}$ order of the DP AOM. It generates the second frequency for the Raman transition.
-    % When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
-    % (blue beam path) which generates the required frequency different to drive
-    % the Raman transition.
-    % The two frequencies are recombined on the DP AOM.
-    To reduce interferences that cause relative power fluctuation of the two frequencies, the $0^{\mathrm{th}}$ order is frequency shifted by $-80$~MHz before recombination.
-    % be at the same frequency
-    % as the $0$-th order light which can cause a significant power fluctuation
-    % due to interference.
-    The experiment typically starts with the single-pass (SP) AOM on and the DP AOM off.
-    When driving the Raman transition, the RF powers for both AOMs are ramped simultaneously
-    to achieve the desired optical power at both frequencies, while keeping the total optical power fixed.
-    \label{f-beampath}
-  }
-\end{figure}
-
 The optical Raman transfer is illustrated
@@
 
-We optimize over intermediate states by calculating the Raman Rabi frequency $\Omega_{\rm R}$
+We optimize over intermediate states by calculating the total Raman Rabi frequency $\Omega_{\rm R}$
 and scattering rate $\Gamma_{\rm s}$ at different detunings from the atomic threshold,
-taking into account of all states of
-8 excited molecular potentials~\cite{Korek2007, Grochola2011, Zaharova2009, Grochola2010, Zabawa2012}
-and the continuum~\cite{Liu2017}.
+taking into account all states of
+8 excited molecular electronic potentials~\cite{Korek2007, Grochola2011, Zaharova2009, Grochola2010, Zabawa2012}
+and the continuum~\cite{Liu2017}; 
+see Supplementary Material for details.
 This calculation shows that the figure of merit $\Omega_{\rm R}/\Gamma_{\rm s}$
 can be larger for the lowest vibrational state compared to higher bound states
-at a cost of a smaller transfer rate $\Omega_{\rm R}$, as shown in Fig.~\ref{f-theory}c;
-see Supplementary Material for details.
+at a cost of a smaller transfer rate $\Omega_{\rm R}$, as shown in Fig.~\ref{f-theory}c.
 As a result, we choose the $v'=0$ level of $\mathrm{c^3\Sigma^+}(\Omega = 1)$
@@
 
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{imgs/raman_spectroscopy_raman_beampath.pdf}
+  \caption{
+    Beam path for generating two frequencies in the tweezer for the Raman transition (only essential optics shown.)
+    Two filters, one directly after the laser source and one after both optical fibers clean the light from a fiber amplifier seeded by an external cavity diode laser.
+    The red beam path is the always-present $0^{\mathrm{th}}$ order of the double pass~(DP) AOM.
+    The blue beam path is the switchable $1^{\mathrm{st}}$ order of the DP AOM. It generates the second frequency for the Raman transition.
+    % When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
+    % (blue beam path) which generates the required frequency different to drive
+    % the Raman transition.
+    % The two frequencies are recombined on the DP AOM.
+    To reduce interferences that cause relative power fluctuation of the two frequencies, the $0^{\mathrm{th}}$ order is frequency shifted by $-80$~MHz before recombination.
+    % be at the same frequency
+    % as the $0$-th order light which can cause a significant power fluctuation
+    % due to interference.
+    The experiment typically starts with the single-pass (SP) AOM on and the DP AOM off.
+    When driving the Raman transition, the RF powers for both AOMs are ramped simultaneously
+    to achieve the desired optical power at both frequencies, while keeping the total optical power fixed.
+    \label{f-beampath}
+  }
+\end{figure}
+
 %% Preparation
@@
 \end{figure}
-After merging the tweezers, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ with a large scattering length
-by performing a Cs spin flip while taking into account
-the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.
-This is the initial atomic state for Raman transfer.
-The spin flip selectively transfers atoms in the relative motional ground state,
-removing any background from atoms in excited states of relative motion
-\footnote{This interaction shift is larger than the differential axial trapping frequency
-  between Na and Cs atoms, which decouples the relative and center of mass motional state
-  and improves the robustness of our preparation of the relative motional ground state.}.
-For the experiment reported here,
-$31\mathrm{\%}$ of initial two-atom population is transferred. Of this population, over $60\%$ is in the ground state of center-of-mass motion, inferred from Raman sideband thermometry.
 
@@
 \end{figure*}
+
+After merging the tweezers, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ with a large scattering length
+by performing a Cs spin flip while taking into account
+the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.
+This is the initial atomic state for Raman transfer.
+The spin flip selectively transfers atoms in the relative motional ground state,
+removing any background from atoms in excited states of relative motion
+\footnote{This interaction shift is larger than the differential axial trapping frequency
+  between Na and Cs atoms, which decouples the relative and center of mass motional state
+  and improves the robustness of our preparation of the relative motional ground state.}.
+For the experiment reported here,
+$31\mathrm{\%}$ of initial two-atom population is transferred. Of this population, over $60\%$ is in the ground state of center-of-mass motion, inferred from Raman sideband thermometry.
 
@@
 followed after a variable delay by a second dissociating $\pi$-pulse.
-Together with the Rabi oscillation in Fig.~\ref{f-raman}b,
-we obtain a molecule lifetime of $0.199(9)~\mathrm{ms}$.
+The measured lifetime of $0.196(14)~\mathrm{ms}$ is consistent with the decaying time scale of  $0.203(13)~\mathrm{ms}$ of the  Rabi oscillation
+ in Fig.~\ref{f-raman}b. %,we obtain a molecule lifetime of $0.199(9)~\mathrm{ms}$.
 Preliminary experiments and theoretical considerations indicate that
@@
 This process is enabled by utilizing a deeply-bound intermediate state, as well as highly-interacting initial atomic states.
-A theoretical investigation including 8 excited state potentials,
-the excited atomic continuum, and coupled-channel ground-state wavefunctions indicates
+A theoretical investigation including 8 excited molecular electronic potentials,
+the electronically excited atomic continuum, and coupled-channel ground-state wavefunctions indicates
 the potential for higher transfer efficiency than the observed value of $69$~\%.
@@
 Engineering and Physical Sciences Research Council (EPSRC) Grants No.\ EP/N007085/1, EP/P008275/1 and EP/P01058X/1.
+R.~G.~F.
+acknowledges financial support of the Spanish Project FIS2017-89349-P (MINECO), and the Andalusian research group FQM-207.
 \end{acknowledgments}
 
-\TR{What is meant by ``result is consistent with the decay of the Rabi oscillation'' if independent fits not done?  See also Fig.~5 caption.}
+%\TR{What is meant by ``result is consistent with the decay of the Rabi oscillation'' if independent fits not done?  See also Fig.~5 caption.}
 

### 2020-12-15 sm.tex
Update on Overleaf.

@@
 }
+\newcommand{\itamp}{\affiliation{ITAMP, Harvard-Smithsonian Center for Astrophysics, Cambridge, Massachusetts 02138, USA}}
 
@@
 \affiliation{Joint Quantum Centre Durham-Newcastle, Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
+\author{Rosario Gonzalez-Ferez}
+\affiliation{Instituto Carlos I de F\'{\i}sica Te\'orica y Computacional, and Departamento de F\'{\i}sica At\'omica, Molecular y Nuclear,  Universidad de Granada, 18071 Granada, Spain}
+\itamp
 \author{Till Rosenband}
-\harvardphysics
+\affiliation{Agendile LLC, Cambridge, Massachusetts 02139, USA}
 \author{Kang-Kuen~Ni}
@@
 
-In our system, the separation in energy between the initial and target state is much smaller than the single photon detuning $\Delta$ from the intermediate state.
+In our system, the separation in energy between the initial and target state is much smaller than the single photon detuning $\Delta$ from the intermediate state; see Fig.~1a in the main text.
 Thus, there is significant cross coupling for the scattering rate and light shift, where each state is coupled to the excited state by the power in both beams.
-Under these conditions, the scattering rate and light shift is proportional to the total power $P_{\text{tot}} = P_{\rm m} + P_{\rm a}$, where $P_{\rm m} (P_{\rm a})$ is the power in the beam that addresses the molecular (atomic) state.
+Under these conditions, the scattering rate and light shift are proportional to the total power $P_{\text{tot}} = P_{\rm m} + P_{\rm a}$, where $P_{\rm m} (P_{\rm a})$ is the power in the beam that addresses the molecular (atomic) state.
 The Raman Rabi frequency is proportional to $\sqrt{P_{\rm m}P_{\rm a}} $.
@@
 The Rabi frequency between two states is proportional to the electronic dipole moment, arising from the electronic wavefunctions, and the overlap of the vibrational wavefunctions.
-Under the assumption that the electronic dipole moment $ d $ is the same for all transitions between the ground state and the excited electronic state, the total Raman Rabi frequency becomes:
+Under the assumption that the electronic dipole moment $ d $ is the same for all transitions between the ground state and the excited electronic state, the total Raman Rabi frequency becomes
 \begin{equation}
-  \Omega_{\rm R} = \frac{d^2E^2}{2\hbar^2} \displaystyle\sum_{v'} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}}
+  \Omega_{\rm R} = \frac{d^2E^2}{2\hbar^2} \displaystyle\sum_{v'} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}},
 \end{equation}
@@
 $\Delta_{v'}$ is a single photon detuning with respect to the $\ket{v'}$ state, $ E $ is the electric field for the power in the single beam given a waist size.
-We can divide this sum into a sum over all the bound molecular states, and a sum over atomic continuum states.
+We can divide this sum into a sum over all the bound molecular states, and a sum over atomic continuum states,
 \begin{equation}
-  \Omega_{\rm R} = \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' > v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}}
+  \Omega_{\rm R} = \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' > v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}},
 \end{equation}
@@
 To calculate the second term, we first make an assumption that we are far enough detuned from the contributing continuum states that they are all at approximately the same detuning, $ \Delta_{\text{thresh}}$.
-This allows us to pull it out of the sum, and we obtain:
+This allows us to pull it out of the sum, and we obtain
 \begin{equation}
-  \Omega_{\rm R} \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\displaystyle\sum_{v' > v'_{\text{max}}} \braket{a|v'}\braket{v'|m}  \label{rabifreq}
+  \Omega_{\rm R} \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\displaystyle\sum_{v' > v'_{\text{max}}} \braket{a|v'}\braket{v'|m} .
+\label{rabifreq}
 \end{equation}
-From requiring orthogonality,
+From requiring completeness and orthogonality,
 \begin{equation}
-  \displaystyle\sum_{v'} \braket{a|v'}\braket{v'|m} = \braket{a|m} = 0
+  \displaystyle\sum_{v'} \braket{a|v'}\braket{v'|m} = \braket{a|m} = 0,
 \end{equation}
@@
 \begin{equation}
-  \displaystyle\sum_{v'> v'_{\text{max}}} \braket{a|v'}\braket{v'|m} = -\displaystyle\sum_{v' \leq v'_{\text{max}}} \braket{a|v'}\braket{v'|m}
+  \displaystyle\sum_{v'> v'_{\text{max}}} \braket{a|v'}\braket{v'|m} = -\displaystyle\sum_{v' \leq v'_{\text{max}}} \braket{a|v'}\braket{v'|m},
 \end{equation}
@@
 \begin{equation}
-  \Omega_{\rm R} \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} -  \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\displaystyle\sum_{v' \leq v'_{\text{max}}} \braket{a|v'}\braket{v'|m}
+  \Omega_{\rm R} \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} -  \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\displaystyle\sum_{v' \leq v'_{\text{max}}} \braket{a|v'}\braket{v'|m}.
 \end{equation}
-We can account for the atomic continuum in the scattering rate in a similar way.
+We can account for the atomic continuum in the scattering rate in a similar way
 \begin{align} 
-  \Gamma_{\rm s} &= \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} + \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' > v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} \\
-           &\approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} + \frac{d^2E^2\Gamma}{2\hbar^2\Delta_{\text{thresh}}^2}\displaystyle\sum_{v' > v'_{\text{max}}}\braket{m|v'}\braket{v'|m}
+            \Gamma_{\rm s} &\approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} + \frac{d^2E^2\Gamma}{2\hbar^2\Delta_{\text{thresh}}^2}\displaystyle\sum_{v' > v'_{\text{max}}}\braket{m|v'}\braket{v'|m},
 \end{align}
@@
 \begin{equation}
-  \displaystyle\sum_{v' > v'_{\text{max}}}\braket{m|v'}\braket{v'|m} = 1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}
+  \displaystyle\sum_{v' > v'_{\text{max}}}\braket{m|v'}\braket{v'|m} = 1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}.
 \end{equation}
@@
 \begin{equation}
-  \Gamma_{\rm s} \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} +  \frac{d^2E^2\Gamma}{2\hbar^2\Delta_{\text{thresh}}^2}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right)
+  \Gamma_{\rm s} \approx \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2} +  \frac{d^2E^2\Gamma}{2\hbar^2\Delta_{\text{thresh}}^2}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right).
 \end{equation}
@@
 
-A very similar result holds for the light shift and is written here for completeness
+A very similar result holds for the light shift $\delta$ and is written here for completeness
 
 \begin{equation}
-  \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right)
+  \delta = \frac{d^2E^2}{2\hbar^2}\displaystyle\sum_{v' \leq v'_{\text{max}}} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}} +  \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\left(1 - \displaystyle\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right).
 \end{equation}
 
-\section{Computational methods for bound states and scattering}
+\section{Computational methods for bound and scattering states}
 
@@
 These calculations assume that the intermediate states have pure singlet or triplet character and neglect its
-nuclear spin character, which is unknown. These calculations include theoretical electronic transition dipole moments~\footnote{Private communication with R. Gonzalez-Ferez and R. Moszynski}.
+nuclear spin character, which is unknown. These calculations include theoretical electronic transition dipole moments~\footnote{Private communication with R. Moszynski}.
 
@@
 
-In this calculation, there is a matrix element, $\Omega_{\mathrm{a}i}, \Omega_{\mathrm{m}i}$ between each channel $ i $ of the coupled channel ground state and an excited state.
+In this calculation, there is a matrix element, $\Omega_{\mathrm{a}ij}, \Omega_{\mathrm{m}ij}$ between each channel $ i $ of the coupled channel ground state and an excited state $ j $.
 The total Raman Rabi frequency $ \Omega_{\rm R}$, light shift $ \delta$ and off-resonant scattering $ \Gamma_{\rm s} $ contribution from this single excited state is calculated as
@@
 \begin{align}
-  \Omega_{\rm R} &= \displaystyle\sum_{i} \frac{\Omega_{\mathrm{a}i} \Omega_{\mathrm{m}i}}{2\Delta} \\
-  \delta &= \displaystyle\sum_{i} \frac{\Omega_{\mathrm{a}i}^2 - \Omega_{\mathrm{m}i}^2}{2\Delta} \\
-  \Gamma_{\rm s} &= \displaystyle\sum_{i} \Gamma_{\rm e} \frac{\Omega_{\mathrm{a}i}^2 + \Omega_{\mathrm{m}i}^2}{2\Delta^2}
+  \Omega_{\mathrm{R}j} &= \displaystyle\sum_{i} \frac{\Omega_{\mathrm{a}ij} \Omega_{\mathrm{m}ij}}{2\Delta}, \\
+  \delta_j &= \displaystyle\sum_{i} \frac{\Omega_{\mathrm{a}ij}^2 - \Omega_{\mathrm{m}ij}^2}{2\Delta}, \\
+  \Gamma_{\mathrm{s} j} &= \displaystyle\sum_{i} \Gamma_{\rm e} \frac{\Omega_{\mathrm{a}ij}^2 + \Omega_{\mathrm{m}ij}^2}{2\Delta^2},
 \end{align}
-
 where $ \Delta $ is the single photon detuning and $ \Gamma_{\rm e} $ is the excited state linewidth.

### 2020-12-15 paper.tex
Whitespace and regenerate PDF
Clean up comments

@@
 \documentclass[aps,prl,twocolumn,10pt,superscriptaddress]{revtex4-1}
-% \documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4-1}
 \usepackage{amsmath}
@@
 \begin{document}
-% \title{Coherent optical association of atoms into a single molecule}
 \title{Coherent optical creation of a single molecule}
@@
 
-% Introduction
-
-% 1.
-we want to have a diverse species to tailor to different applications including precision measurements and quantum engineering.
-2.
-for the technique of associating atoms to form molecules, but so far all has been done with Feshbach association (before STIRAP), or in the case of Sr2, a narrow excited state.
-Previous work on near-threshold Raman transfer has been incoherent.
-% (suggested referees: Florian Shreck and Immanual Bloch, Tanya, Deep Gupta, DeMille)
-
-% Trapped neutral molecules, assembled in an array of optical tweezers, are a promising platform to study quantum information and quantum simulation. (more detail to add here about applications?).
-
 Diverse species of fully quantum-controlled ultracold molecules are desired
@@
 While many innovative approaches in the last few years
-have directly cooled different species of %diatomic or polyatomic
+have directly cooled different species of
 molecules
@@
 the highest phase-space-density gas~\cite{Demarco2018} and
-% the coldest
 trapped individual molecules~\cite{Zhang2020,He331}
 have been achieved through the association of ultracold atoms.
-% (any place to cite molecular ion work?)
-% Citations are not complete. Add them as you see fit.
 
@@
 or atoms without narrow intercombination lines remain difficult to associate.
-% These requirements limit the generality of previous association techniques.
-% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited-state lines limits the generality of previous association techniques.
-% to more diverse species.
 
@@
 where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies $\Omega_{\rm a}$ and $\Omega_{\rm m}$, one-photon detuning $ \Delta $, and all Rabi frequencies are population oscillation frequencies.
-%(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
 The transfer Raman Rabi frequency is given by $\Omega_{\rm a}\Omega_{\rm m} / (2\Delta)$~\cite{Wineland2003}.
@@
 Notably, both figures of merit improve with a larger ratio $\Omega_{\rm a}/\Omega_{\rm m}$.
-%, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
-% However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
 
@@
 As there is large overlap between the target molecular state and other vibrationally excited states, intermediate states that are closer to the dissociation threshold result in a large scattering rate.
-% in large incoherence and loss to other molecular states.
 This scattering is approximately proportional to $1/\Delta_{\mathrm{thresh}}^2$,
@@
 at short range, as shown in Fig.~\ref{f-theory}d.
-% The increase in the coupling is proportional to (quote/cite Olive's equation?).
 For our system of Na and Cs atoms,
@@
 All other stable spin combinations give smaller scattering lengths ($<~50~a_0$).
-% We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\Cs}} = \ket{f=4,m_f=4}_{\Cs}, \ket{\downarrow_{\Cs}} = \ket{f=3,m_f=3}_{\Cs}, \ket{\uparrow_{\Na}} = \ket{f=2,m_f=2}_{\Na}, $ and $ \ket{\downarrow_{\Na}} = \ket{f=1,m_f=1}_{\Na}$.
-Among the stable spin combinations, $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\Na} \downarrow_{\Cs}} $ combination has a large and negative scattering length of $ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
 
@@
 A suitable state with this character is predicted about 763 MHz below the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ threshold and the ratio $\Omega_{\rm a}/\Omega_{\rm m}$ increases to about 0.013.
-% The coupled-channel calculations show that this target molecular state has lower overlap with the intermediate state, compared to bound states from other hyperfine combinations.
-% For the target molecular state, the spin state is ideally similar to the initial spin state in order to minimize sensitivity to the magnetic field.
-% We find a target spin state predominantly in the initial spin state
-% that also has the advantage of having a reduced sensitivity
-% to laser intensity noise because of a larger %$\Omega_{\rm a}/\Omega_b$ as compared to other states.
-% This reduces the intensity stability requirement to $5~\mathrm{\%}$
-% instead of $0.3~\mathrm{\%}$ which is typical for other states.
-% In addition to the increased atomic coupling, $ \Omega_{\rm a} $,
-% Coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_{\rm m} $, with the intermediate state when compared to bound states of the other spin compositions.
-% $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
 Compared to $\Omega_{\rm a}/\Omega_{\rm m} \approx 0.003$
 for other combinations, this relaxes the intensity stability requirement to the percent level and enhances the Raman Rabi frequency.
-% Thus, instead of a required intensity stability of $0.3 ~\mathrm{\%} $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5~\mathrm{\%} $.
-% Thus, we choose the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination.
-% \textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled-channel calculation anywhere...)
-
-% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
 
@@
     The blue beam path is the switchable $1^{\mathrm{st}}$ order of the DP AOM. It generates the second frequency for the Raman transition.
-    % When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
-    % (blue beam path) which generates the required frequency different to drive
-    % the Raman transition.
-    % The two frequencies are recombined on the DP AOM.
     To reduce interferences that cause relative power fluctuation of the two frequencies, the $0^{\mathrm{th}}$ order is frequency shifted by $-80$~MHz before recombination.
-    % be at the same frequency
-    % as the $0$-th order light which can cause a significant power fluctuation
-    % due to interference.
     The experiment typically starts with the single-pass (SP) AOM on and the DP AOM off.
@@
 
-%% Preparation
 Experimentally, we first prepare two atoms in a well-defined external and internal quantum state
@@
 
-%% Transfer scheme
-% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
 To transfer the atom pair into the target weakly bound molecular state,
@@
 As shown in Fig.~\ref{f-beampath}, one filter immediately follows the laser, while the second filter precedes the focusing objective for final cleanup of the laser spectrum.
-% The filters reduce photon scattering rate by a factor of $2$ (\textcolor{red}{KW: Since we mention this again later when we explore the causes of our lower than expected transfer efficiency, do we need to mention this reduction here?
-or the possible causes?}).
-While we have not fully characterized the sources
-% of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities.
-% After the total tweezer power is set to the desired value,
-% we smoothly ramp down the power of one frequency in the tweezer
-% while simultaneously ramping up the power of the other frequency
-% so that the total tweezer power remains unchanged.
-% Both frequencies are kept on for a specified duration before the process is reversed
-% and the tweezer returns to a single frequency.~\TR{???}
-
-% found the spectral purity of the laser for Raman beams to be critical for achieving a higher transfer efficiency.
-% The tweezer/Raman beams are generated by a fiber amplifier seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
-% by amplifying a $1037~\mathrm{nm}$ external cavity diode laser (ECDL) with a fiber amplifier,
-% The diode laser produces the desired frequency on top of a broad band amplified spontaneous emission (ASE).
-We use a Bragg grating with a line width (FWHM) of $50~\mathrm{GHz}$ to clean up the laser spectrum and found it reduces the scattering rate by at least a factor of $2$
-% for a particular single-photon detuning.
-
-% in addition to the desired frequency. This increases the scattering rate due to coupling to other excited states.
-
-%% Experiment condition/resonance
 
 Figure~\ref{f-raman} shows a Fourier-limited resonance together with Rabi oscillations between the atomic and molecular states.
-% (We can maybe add information about the prediction here?)
-%% Prediction
-% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state.
-The ground molecular state has not been observed previously in experimentally.
-Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state.
-Theory prediction was at $770.1 MHz$.
-% The background level of $31~\mathrm{\%}$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
-% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence.
-% directly detected by our imaging step.
 A decaying Rabi oscillation with frequency $2\pi\times3.28(4)~\mathrm{kHz}$ fitted to the data suggests that
 $69~\mathrm{\%}$ of atoms are transferred into the molecular state after a $\pi$-pulse, with the majority of molecules in the ground state of motion~\cite{Zhang2020,He331}.
-% Over $60\%$ of the molecules are in the motional ground state (both relative and center of mass), inferred from independent Raman sideband thermometry measurements of the atoms.
 
@@
 is well approximated by $P^{0.29}$ within the range of confinement in our experiment and the expected scaling of $ \Omega_{\rm a} \propto P^{0.79} $ agrees with the data.
-% At $3.75~\mathrm{mW}$ tweezer power, we measured $ \Omega_{\rm m} = 2\pi \times 348.3(3)~\mathrm{MHz}$ and $ \Omega_{\rm a} = 2\pi\times 5.5(2)~\mathrm{MHz}$, resulting in a
-% The measured $ \Omega_{\rm m}/\Omega_{\rm a}$ ratio of $ 63 $ is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
-% Therefore, the matrix element ratio is not the cause of our lower than expected transfer efficiency.
-
-% We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
-% From these measurements, we can extract a $\Omega_{\rm m}$ of
-
-% In order to calculate the ratio $\Omega_{\rm m}/\Omega_{\rm a}$,
-% we now need to extract $ \Omega_{\rm a} $.
-% We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
-% which depends on both $\Omega_{\rm m}$ and $\Omega_{\rm a}$.
-% The Raman Rabi frequency shows a non-linear dependency on the tweezer power
-% due to the change in the atomic wavefunction caused by
-% tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
-
-% Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
-% which fits well to our experimental result, as shown in Fig.~\ref{f-det}b.
-% Similar to the light shift, the detuning dependency of the Raman Rabi frequency
-% is determined by a constant background component and
-% a $v'=0$ component that scales as $1/\Delta$.
-% The $v'=0$ component of the Raman Rabi frequency at our detuning is
-% $2\pi\times1.10(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
-% or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ %tweezer power.
-% Together with the $\Omega_{\rm m}$ measured above, the Rabi frequency, $\Omega_{\rm a}$, is
-% $2\pi\times 5.5(2)~\mathrm{MHz}$.
-% This gives a matrix-element ratio $\Omega_{\rm m}/\Omega_{\rm a}$ of $63(3)$,
-% which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
-
-% Theory numbers
-% $2\pi \times 15.3~\mathrm{kHz}$
-% $ 2\pi \times 533~\mathrm{Hz}$
-% $2\pi \times 573 ~\mathrm{MHz}$
-% $2\pi \times 7.37 ~\mathrm{MHz}$
-
-% With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
-% We now consider the background effects from other states with larger single-photon detuning.
-% In the Raman Rabi frequency fit,
-% the fitted background is of opposite sign from the Raman Rabi frequency
-% for single-photon detunings red of the $v' = 0 $ transition.
-% Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$
-% at the current detuning.
-% However, this difference is not enough to explain the discrapancy of more than a factor of $10$
-% present in the experiment.
-% Due to the change in sign of the Raman Rabi frequency as a function of detuning
-% when crossing a resonance, the same background will increase the Raman Rabi frequency
-% for positive detunings from the $v' = 0$ transition.
-% Unfortunately, we observe additional nearby excited states
-% belonging to a different electronically excited state at higher frequencies
-% which prevent the blue side of the transition from being be usable for the Raman transition.
 
 While the measured single-photon Rabi frequencies of Table~I are in broad agreement with calculations (see Supplementary Materials), calculated scattering rates of the molecular and atomic state underestimate the decoherence in Fig.~\ref{f-raman}b.
-% Known single-photon scattering rates of Na and Cs atoms together with an independent measurement (via photoassociation spectroscopy) of the $v'=0$ excited state natural linewidth of no more than $50~\mathrm{MHz}$ indicate that single-photon scattering from the molecular or atomic state do not explain the decoherence in Fig.
-3b~\TR{long sentence}.
-Below, we further investigate the loss of coherence.
-% These results suggest that the decoherence or loss we observe during the Raman transition
-% comes from either a higher background scattering rate of an unknown source
-% or a different intrinsic or technical source for which we have not accounted for.
 From experimental measurements, the Raman transfer efficiency is limited by the molecular lifetime, together with a reduction in the Raman Rabi frequency due to destructive interference with intermediate states beyond $v'=0$ (see Table~~\ref{tab:f-det:fit}).
@@
 The measured lifetime of $0.196(14)~\mathrm{ms}$ is consistent with the decaying time scale of  $0.203(13)~\mathrm{ms}$ of the  Rabi oscillation
- in Fig.~\ref{f-raman}b. %,we obtain a molecule lifetime of $0.199(9)~\mathrm{ms}$.
+in Fig.~\ref{f-raman}b.
 Preliminary experiments and theoretical considerations indicate that
@@
 
-% The scattering rate of the molecule also depends on the tweezer power and detuning,
-% and becomes smaller when the power is lowered.
-% At $0.75~\mathrm{mW}$ tweezer power, we observe a molecule lifetime as long as $1~\mathrm{ms}$.
-% Since the technical noise that can lead to decoherence
-% is not fully characterized in our experiment,
-% we are unable to further identify the sources of the measured scattering rate
-% based on our measured detuning and power dependencies.
-
-% To confirm that the observed loss of Rabi oscillation is not due to the atomic state,
-% we measure the two-body scattering rate
-% without turning on the second frequency, as shown in Fig.~\ref{f-lifetime}b inset.
-% The scattering rate scales as $P^{2.58}$ and is too low to explain the Rabi oscillation decoherence.
-% We have not been able to observe a dependency on the detuning in order to verify whether the scattering process is related to the $v'=0$ state,
-% but the power scaling strongly suggests the existence of an unknown two-photon process.
-% Nevertheless, the absolute scattering rate from the atomic state
-% is much lower than the total scattering rate
-% and is not the limiting factor in this experiment.
-
 In conclusion, we have coherently formed a weakly bound NaCs molecule in an optical tweezer
@@
 These molecules comprise a flexible platform for quantum simulation,  quantum computing, precision measurements applications.
-%\textcolor{blue}{(End with a sentence on molecules for future quantum applications?)}
-% Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},
-% defect-free arrays of highly controlled molecules comprise a promising
-% and flexible platform for quantum simulation and quantum computing applications.
 
@@
 
-%\TR{What is meant by ``result is consistent with the decay of the Rabi oscillation'' if independent fits not done?  See also Fig.~5 caption.}
-
 \bibliography{master_ref}

### 2020-12-18 fig-lifetime.tex
Move figures since PRX doesn't like subdirectories

--- 2020-12-07 imgs/fig-lifetime.tex
@@
 \begin{tikzpicture}[scale=1.5391]
-  \node at (0, 0) {\includegraphics[width=7.6958cm]{exp_data_norm_m_t.pdf}};
+  \node at (0, 0) {\includegraphics[width=7.6958cm]{imgs/exp_data_norm_m_t.pdf}};
   \node at (-2.4, 1.2) {\footnotesize (\textbf{a})};
@@
 
-  \node at (0, -2.7) {\includegraphics[width=7.6958cm]{exp_data_norm_a_t.pdf}};
+  \node at (0, -2.7) {\includegraphics[width=7.6958cm]{imgs/exp_data_norm_a_t.pdf}};
   \node at (-2.4, 1.2 - 2.7) {\footnotesize (\textbf{b})};
   % strength = 2pi 29.3(17) mHz/mW^2.58
-  \node at (0.8, -2.25) {\includegraphics[width=4.6175cm]{atomic_loss_scaling_inset.pdf}};
+  \node at (0.8, -2.25) {\includegraphics[width=4.6175cm]{imgs/atomic_loss_scaling_inset.pdf}};
 \end{tikzpicture}

### 2020-12-18 fig-theory.tex
Move figures since PRX doesn't like subdirectories

--- 2020-11-25 imgs/fig-lifetime.tex
@@
-\documentclass{standalone}
+\documentclass[border={-3pt -5.5pt -5pt -4pt}]{standalone} % left bottom right top
+
+\usepackage{hyperref}
 \usepackage{tikz}
@@
 \pdftrailerid{}
+\hypersetup{
+  pdfcreator={},
+  pdfproducer={}
+}
 \fi
@@
 
-\begin{tikzpicture}[scale=1.5391]
-  \node at (0, 0) {\includegraphics[width=7.6958cm]{exp_data_norm_m_t.pdf}};
-  \node at (-2.35, 1.7) {\footnotesize (\textbf{a})};
-
-  \node at (0.77, 0.5) {$t_{\mathrm{hold}}$};
-  \draw[->,>=stealth,line width=1] (0.4, 0.5) -- (0, 0.5);
-  \draw[->,>=stealth,line width=1] (1.1, 0.5) -- (1.5, 0.5);
-  \draw[orange!80!white,line width=1,fill=orange!50!white]
-  (-0.3, 0.2) -- (-0.3, 0.8) -- node[above,orange!90!black] {\small $\pi$-pulse}
-  (0, 0.8) -- (0, 0.2);
-  \draw[orange!80!white,line width=1,fill=orange!50!white,shift={(1.8, 0)}]
-  (-0.3, 0.2) -- (-0.3, 0.8) -- node[above,orange!90!black] {\small $\pi$-pulse}
-  (0, 0.8) -- (0, 0.2);
-  \draw[->,>=stealth,line width=1] (-0.5, 0.2) -- (2, 0.2);
-
-  \node at (0, -3.9) {\includegraphics[width=7.6958cm]{exp_data_norm_a_t.pdf}};
-  \node at (-2.35, 1.5 - 3.9) {\footnotesize (\textbf{b})};
-  % strength = 2pi 29.3(17) mHz/mW^2.58
-  \node at (0.85, -3.25) {\includegraphics[width=4.6175cm]{atomic_loss_scaling_inset.pdf}};
+\begin{tikzpicture}
+  \node at (-9.8, 0) {\includegraphics[width=4.5cm]{imgs/RamanTransferScheme_v6.eps}};
+  \node at (-11.4, 2.2) {\footnotesize (\textbf{a})};
+  \node at (-1.35, 1.25) {\includegraphics[width=11.0cm]{imgs/raman_theory_full_gamma.pdf}};
+  \node at (-7.05, 2.35) {\footnotesize (\textbf{b})};
+  \node at (-4.35, -1.35) {\includegraphics[width=5.7cm]{imgs/raman_v0_vhi.pdf}};
+  \node at (-6.95, -0.35) {\footnotesize (\textbf{c})};
+  \node at (1.4, -1.35) {\includegraphics[width=5.7cm]{imgs/wavefunction.pdf}};
+  \node at (-1.2, -0.35) {\footnotesize (\textbf{d})};
 \end{tikzpicture}

### 2020-12-18 raman_spectroscopy_raman_beampath.tex
Move figures since PRX doesn't like subdirectories

--- 2020-11-25 imgs/raman_spectroscopy_raman_beampath.tex
@@
-\documentclass{standalone}
+\documentclass[border=-2pt]{standalone}
 \usepackage{tikz}
@@
   \begin{scope}[shift={#1}]
-    \node[rotate={#3}] at (0, 0) {\scalebox{#2}{\includegraphics[width=2cm]{lens.png}}};
+    \node[rotate={#3}] at (0, 0) {\scalebox{#2}{\includegraphics[width=2cm]{imgs/lens.png}}};
   \end{scope}
@@
   \begin{scope}[shift={#1}]
-    \node[rotate={#3}] at (0, 0) {\scalebox{#2}{\includegraphics[width=2cm]{wp.png}}};
+    \node[rotate={#3}] at (0, 0) {\scalebox{#2}{\includegraphics[width=2cm]{imgs/wp.png}}};
   \end{scope}
@@
     \node[rotate={#4}] at (0, 0)
-    {\scalebox{#2}[#3]{\includegraphics[width=2cm,height=2cm]{AOM.png}}};
+    {\scalebox{#2}[#3]{\includegraphics[width=2cm,height=2cm]{imgs/AOM.png}}};
   \end{scope}
@@
     \node[rotate={#3}] at (0, 0)
-    {\scalebox{#2}{\includegraphics[width=1.4285714285714286cm]{PBS.png}}};
+    {\scalebox{#2}{\includegraphics[width=1.4285714285714286cm]{imgs/PBS.png}}};
   \end{scope}
@@
 \begin{tikzpicture}
-  \coordinate (Fiber 1 Out) at (1.3, 0);
+  \coordinate (Fiber 1 Out) at (1.1, 0);
   \coordinate (Fiber 1 In) at ($(Fiber 1 Out) + (1.3, 0)$);
-  \coordinate (Filter 1) at ($(Fiber 1 In) + (1.6, 0)$);
-  \coordinate (Input) at ($(Filter 1) + ({-2 * cos(44)}, {2 * sin(44)})$);
+  \coordinate (Filter 1) at ($(Fiber 1 In) + (1.5, 0)$);
+  \coordinate (Input) at ($(Filter 1) + ({-1.93 * cos(44)}, {1.93 * sin(44)})$);
 
@@
   \coordinate (SP IM1) at (-5.2, 4);
-  \coordinate (SP lens) at (-6.5, 4);
-  \coordinate (SP PBS) at (-7.5, 4);
-  \coordinate (SP IM2) at (-10, 4);
-  \coordinate (SP AOM) at (-10, 2.7);
-  \coordinate (SP M1) at (-10, 0);
-  \coordinate (SP M2) at (-7.5, 0);
-  \coordinate (SP HWP) at (-7.5, 1.7);
+  \coordinate (SP lens) at (-6.1, 4);
+  \coordinate (SP PBS) at (-7.1, 4);
+  \coordinate (SP IM2) at (-9.0, 4);
+  \coordinate (SP AOM) at (-9.0, 2.7);
+  \coordinate (SP M1) at (-9.0, 0);
+  \coordinate (SP M2) at (-7.1, 0);
+  \coordinate (SP HWP) at (-7.1, 1.7);
 
@@
   \draw[gray!30!white,line width=2] (-4.2, 5.6) |- (-1, 3.3);
-  \draw[gray!30!white,line width=2] (2.0, 5.6) |- (2.0, 1.3);
+  \draw[gray!30!white,line width=2] (1.85, 5.6) -- (1.85, 1.3);
 
@@
   \draw[red,line width=1.6,mid arrow2] (DP M1) -- (SP IM1);
-  \draw[red,line width=1.6,mid arrow2] (SP lens) -- (SP IM1);
+  \draw[red,line width=1.6,mid arrow2=0.7] (SP lens) -- (SP IM1);
   \draw[red,line width=1.6] (SP lens) -- (SP PBS);
@@
   \draw[red,line width=1.6,mid arrow] ($(SP M1) + (-0.2, 0.2)$) -- (SP M2);
-  \draw[red,line width=1.6,mid arrow] (SP M2) -- (SP PBS);
+  \draw[red,line width=1.6,mid arrow=0.7] (SP M2) -- (SP PBS);
 
@@
   \drawmirror[line width=8,gray!60!white]{(Filter 1)}{0.5}{68};
-  \node[below] at ($(Filter 1) + (-0.4, -0.45)$) {ASE Filter 1};
+  \node[below] at ($(Filter 1) + (-0.7, -0.45)$) {Filter 1};
 
@@
   \drawmirror[line width=8,gray!60!white]{(Filter 2)}{0.5}{112};
-  \node[below] at ($(Filter 2) + (0, -0.45)$) {ASE Filter 2};
+  \node[below] at ($(Filter 2) + (0, -0.45)$) {Filter 2};
 \end{tikzpicture}

### 2021-03-02 sm.tex
Whitespace and regenerate PDF
Fix reference styles and fix unicode/quote in references titles
Update on Overleaf.

@@
-\documentclass[aps,secnumarabic,amsmath,amssymb,10pt,superscriptaddress]{revtex4}
+\documentclass[aps,prx,secnumarabic,amsmath,amssymb,10pt,superscriptaddress]{revtex4-2}
 \usepackage{amsmath}
@@
 % Add S1 to bibliography
-\bibliographystyle{apsrev4-2}
 \renewcommand*{\citenumfont}[1]{S#1}
@@
 energy 763 MHz below the $(f_{\rm Na},f_{\rm Cs}) = (2,3)$ threshold. As described in the text, it
-was subsequently located experimentally at a binding energy of 770.57150(9) MHz.
+was subsequently located experimentally at a binding energy of $ 770.1969(2) \mathrm{MHz} $ at $ 8.83(2) \mathrm{G} $.
 
@@
 Thus, for computational ease, we use the diabatic potentials for $ \mathrm{b^3\Pi_{0}, b^3\Pi_{1}} $ and $ \mathrm{A^1\Sigma^+_{0^+}}$.
-%and remove the states nearest to the $ v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $.
+% and remove the states nearest to the $ v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $.
 Lastly, to our knowledge, no potential fit to experimental data exists for the $ c^3\Sigma^+_{0^-}$ state.

### 2021-03-02 paper.tex
Move figures since PRX doesn't like subdirectories
Fix reference styles and fix unicode/quote in references titles
Update on Overleaf.
Clarify about coherence

@@
-\documentclass[aps,prl,twocolumn,10pt,superscriptaddress]{revtex4-1}
+\documentclass[aps,prx,twocolumn,10pt,superscriptaddress]{revtex4-2}
 \usepackage{amsmath}
@@
   Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
-So far, molecular association has generally been achieved by magnetoassociation
+So far, coherent molecular association has generally been achieved by magnetoassociation
 through a magnetic Feshbach scattering resonance.
+Optical transfer to these molecular state have also been demonstrated~\cite{Wynar2000,Rom2004}
+but the transition is generally incoherent,
+which limits their use to spectroscopic study of the molecular structure,
+rather than creating and controlling the molecules.
 Exceptions include Sr$_2$, where narrow-linewidth ($\sim 20~\mathrm{kHz}$) excited states
@@
 \begin{figure*}
-  \includegraphics[width=\textwidth]{imgs/fig-theory.pdf}
+  \includegraphics[width=\textwidth]{fig-theory.pdf}
   \caption{Optical creation of single molecules from single atoms in an optical tweezer.
@@
 \begin{figure}
-  \includegraphics[width=0.5\textwidth]{imgs/raman_spectroscopy_raman_beampath.pdf}
+  \includegraphics[width=0.5\textwidth]{raman_spectroscopy_raman_beampath.pdf}
   \caption{
@@
 \begin{figure}[t!]
-  \includegraphics[width=0.48\textwidth]{imgs/fig-raman.pdf}
+  \includegraphics[width=0.48\textwidth]{fig-raman.pdf}
   \caption{Coherent transfer of atoms to molecules.  The molecular state is dark to the imaging step and corresponds to zero signal.
@@
 \begin{figure*}[htb]
-  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
+  \includegraphics[width=\textwidth]{fig-det.pdf}
   \caption{Raman transition parameters as a function of tweezer power and detuning.
@@
 \begin{figure}[ht]
-  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
+  \includegraphics[width=0.48\textwidth]{fig-lifetime.pdf}
   \caption{Lifetime measurements with about $3.25~\mathrm{mW}$ optical power.
@@
     $f_{\mathrm{PA}0}~(\mathrm{GHz})$&\multicolumn{3}{|c|}{$288711.8$}\\\hline
-    $a~(\mathrm{2\pi\times MHz})$&$770.20452(6)$&$770.2081(1)$&$770.1943(3)$\\
-    $b~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$-12.46(2)$&$-24.44(3)$&$-60.66(8)$\\\hline
-    $c~(\mathrm{2\pi\times kHz})$&$0.29(2)$&$0.63(4)$&$2.4(2)$\\
-    $d~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$0.115(4)$&$0.275(6)$&$0.95(3)$\\ \hline
+    $a_P~(\mathrm{2\pi\times MHz})$&$770.20452(6)$&$770.2081(1)$&$770.1943(3)$\\
+    $b_P~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$-12.46(2)$&$-24.44(3)$&$-60.66(8)$\\\hline
+    $c_P~(\mathrm{2\pi\times kHz})$&$0.29(2)$&$0.63(4)$&$2.4(2)$\\
+    $d_P~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$0.115(4)$&$0.275(6)$&$0.95(3)$\\ \hline
     $\Omega_{\rm R}~(\mathrm{2\pi\times kHz})$ & 0.49(2) & 1.18(3) & 3.97(9) \\
@@
 \bibliography{master_ref}
-\bibliographystyle{apsrev4-2}
+% \bibliographystyle{apsrev4-2}
 \end{document}

### 2021-03-03 paper.tex
Update on Overleaf.

@@
 through a magnetic Feshbach scattering resonance.
-Optical transfer to these molecular state have also been demonstrated~\cite{Wynar2000,Rom2004}
-but the transition is generally incoherent,
+A recent work~\cite{He331} used a microwave transfer to create weakly bound $^{87}$Rb$^{85}$Rb with binding energy of only  $1-2~\mathrm{MHz}$.
+Optical transfer to these molecular states has also been demonstrated~\cite{Wynar2000,Rom2004,Liu2019}, but these attempts have been incoherent,
 which limits their use to spectroscopic study of the molecular structure,
-rather than creating and controlling the molecules.
-Exceptions include Sr$_2$, where narrow-linewidth ($\sim 20~\mathrm{kHz}$) excited states
-are available and optical association can be driven coherently~\cite{Stellmer2012,Reinaudi2012},
-and $^{87}$Rb$^{85}$Rb with molecular states bound by only $1-2~\mathrm{MHz}$~\cite{He331}.
+rather than as a resource for quantum computing or simulation.
+One exception is Sr$_2$, where narrow-linewidth ($\sim 20~\mathrm{kHz}$) excited states
+can be used to drive the optical association coherently~\cite{Stellmer2012,Reinaudi2012}.
 With these requirements, molecules involving non-magnetic atoms~\cite{PhysRevX.10.031037}
-or atoms without narrow intercombination lines remain difficult to associate.
+or atoms without narrow intercombination lines remain difficult to create.
 

### 2021-03-03 paper.tex
Reorder the discussion about other attempts

--- 2021-03-02 paper.tex
@@
 through a magnetic Feshbach scattering resonance.
-Optical transfer to these molecular state have also been demonstrated~\cite{Wynar2000,Rom2004}
-but the transition is generally incoherent,
-which limits their use to spectroscopic study of the molecular structure,
-rather than creating and controlling the molecules.
 Exceptions include Sr$_2$, where narrow-linewidth ($\sim 20~\mathrm{kHz}$) excited states
@@
 or atoms without narrow intercombination lines remain difficult to associate.
+Optical association that can be applied to a wider range of molecule
+have also been demonstrated~\cite{Wynar2000,Rom2004}
+but the transition is generally incoherent,
+which limits their use to spectroscopic study of the molecular structure,
+rather than creating and controlling the molecules.
 

### 2021-03-03 paper.tex
Update on Overleaf.

--- 2021-03-02 paper.tex
@@
 With these requirements, molecules involving non-magnetic atoms~\cite{PhysRevX.10.031037}
-or atoms without narrow intercombination lines remain difficult to associate.
+or atoms without narrow intercombination lines remain difficult to create.
+Optical association that can be applied to a wider range of molecules
+has also been demonstrated~\cite{Wynar2000,Rom2004,Liu2019}, but these attempts have been incoherent,
+which limits their use to spectroscopic study of the molecular structure, 
+rather than as a resource for quantum computing or simulation.
 

### 2021-03-03 paper.tex
Update PDF, whitespace
Update on Overleaf.

@@
 Optical association that can be applied to a wider range of molecules
-has also been demonstrated~\cite{Wynar2000,Rom2004,Liu2019}, but these attempts have been incoherent,
-which limits their use to spectroscopic study of the molecular structure, 
-rather than as a resource for quantum computing or simulation.
+has also been demonstrated~\cite{Wynar2000,Rom2004,Liu2019},
+but these attempts have been in the incoherent regime, which led to loss of the created molecule.
+This technique can be used for spectroscopic study of the molecular structure and interactions,
+but without control of the created molecule, further transfer to states of interest in quantum computing or simulation remains difficult.
 
@@
 by two-photon optical Raman transfer via an electronic excited state,
-as shown in Fig.~\ref{f-theory}a, taking NaCs as the prototype system.
+as shown in Fig.~\ref{f-theory}a, taking NaCs as the prototype system. We observe coherent Rabi oscillations between the free atoms and the weakly bound molecule.
 The technique does not rely on a Feshbach resonance,

### 2021-05-08 paper.tex
Update on Overleaf.

@@
 Optical association that can be applied to a wider range of molecules
-has also been demonstrated~\cite{Wynar2000,Rom2004,Liu2019},
-but these attempts have been in the incoherent regime, which led to loss of the created molecule.
+has also been attempted~\cite{Wynar2000,Rom2004,Liu2019}. Although these attempts use a pair of
+coherent laser beams to target a particular molecular state, the created molecule was lost quickly before any Rabi oscillations were observed.
 This technique can be used for spectroscopic study of the molecular structure and interactions,

### 2021-05-10 paper.tex
Update on Overleaf.

--- 2021-03-03 paper.tex
@@
 Optical association that can be applied to a wider range of molecules
-has also been demonstrated~\cite{Wynar2000,Rom2004,Liu2019},
-but these attempts have been in the incoherent regime, which led to loss of the created molecule.
+has also been demonstrated~\cite{Wynar2000,Rom2004,Liu2019}.
+Although these attempts use a pair of laser beams to target a particular molecular state, the created molecule was lost quickly before any coherent Rabi oscillations were observed.
 This technique can be used for spectroscopic study of the molecular structure and interactions,

### 2021-05-10 scripts/plot_tdm.jl
[scripts,data,imgs] TDM data and plots

@@ -1,0 +1,83 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+# using DataStructures
+# using LsqFit
+using LibArchive
+
+using DelimitedFiles
+
+function read_csv_compressed(fname, args...; kwargs...)
+    LibArchive.Reader(fname) do reader
+        LibArchive.support_format_raw(reader)
+        LibArchive.support_filter_all(reader)
+        LibArchive.next_header(reader)
+        readdlm(reader, args...; kwargs...)
+    end
+end
+
+const fname_a3b3 = joinpath(@__DIR__, "../data/TDM_Rosario/DM_a3S_b3P_Full.csv.zst")
+const fname_a3c3 = joinpath(@__DIR__, "../data/TDM_Rosario/DM_a3S_c3S_Full.csv.zst")
+const fname_X1A1 = joinpath(@__DIR__, "../data/TDM_Rosario/DM_X1S_A1S_Full.csv.zst")
+const fname_X1B1 = joinpath(@__DIR__, "../data/TDM_Rosario/DM_X1S_B1P_Full.csv.zst")
+const data_a3b3 = read_csv_compressed(fname_a3b3, ',', Float64)
+const data_a3c3 = read_csv_compressed(fname_a3c3, ',', Float64)
+const data_X1A1 = read_csv_compressed(fname_X1A1, ',', Float64)
+const data_X1B1 = read_csv_compressed(fname_X1B1, ',', Float64)
+
+const prefix = joinpath(@__DIR__, "../imgs", "TDM")
+
+figure(figsize=[13.8, 4.8])
+plot(data_a3b3[:, 1] .* 0.529177210903, data_a3b3[:, 2], "C1",
+     label="\$a^3\\Sigma\\rightarrow b^3\\Pi\$")
+plot(data_a3c3[:, 1] .* 0.529177210903, data_a3c3[:, 2], "C2",
+     label="\$a^3\\Sigma\\rightarrow b^3\\Pi\$")
[…]

### 2021-05-10 scripts/plot_tdm.jl
[imgs] .... fix legend

@@ -39,11 +39,11 @@ figure(figsize=[13.8, 4.8])
 plot(data_a3b3[:, 1] .* 0.529177210903, data_a3b3[:, 2], "C1",
      label="\$a^3\\Sigma\\rightarrow b^3\\Pi\$")
 plot(data_a3c3[:, 1] .* 0.529177210903, data_a3c3[:, 2], "C2",
-     label="\$a^3\\Sigma\\rightarrow b^3\\Pi\$")
+     label="\$a^3\\Sigma\\rightarrow c^3\\Sigma\$")
 plot(data_X1A1[:, 1] .* 0.529177210903, data_X1A1[:, 2], "C3",
-     label="\$a^3\\Sigma\\rightarrow b^3\\Pi\$")
+     label="\$X^1\\Sigma\\rightarrow A^1\\Sigma\$")
 plot(data_X1B1[:, 1] .* 0.529177210903, data_X1B1[:, 2], "C4",
-     label="\$a^3\\Sigma\\rightarrow b^3\\Pi\$")
+     label="\$X^1\\Sigma\\rightarrow B^1\\Pi\$")
 grid()
 xscale("log")
 xlim([2.7, 25])
@@ -62,11 +62,11 @@ figure(figsize=[6.4, 4.8])
 plot(data_a3b3[:, 1] .* 0.529177210903, data_a3b3[:, 2], "C1",
      label="\$a^3\\Sigma\\rightarrow b^3\\Pi\$")
 plot(data_a3c3[:, 1] .* 0.529177210903, data_a3c3[:, 2], "C2",
-     label="\$a^3\\Sigma\\rightarrow b^3\\Pi\$")
+     label="\$a^3\\Sigma\\rightarrow c^3\\Sigma\$")
 plot(data_X1A1[:, 1] .* 0.529177210903, data_X1A1[:, 2], "C3",
-     label="\$a^3\\Sigma\\rightarrow b^3\\Pi\$")
+     label="\$X^1\\Sigma\\rightarrow A^1\\Sigma\$")
 plot(data_X1B1[:, 1] .* 0.529177210903, data_X1B1[:, 2], "C4",
-     label="\$a^3\\Sigma\\rightarrow b^3\\Pi\$")
+     label="\$X^1\\Sigma\\rightarrow B^1\\Pi\$")
 grid()
 xscale("log")
 xlim([2.7, 25])

### 2021-05-10 sm.tex
Update on Overleaf.

@@
 These calculations assume that the intermediate states have pure singlet or triplet character and neglect its
-nuclear spin character, which is unknown. These calculations include theoretical electronic transition dipole moments~\footnote{Private communication with R. Moszynski}.
+nuclear spin character, which is unknown.
+These calculations include theoretical electronic transition dipole moments shown in figure \ref{tdm-sm} calculated with ab initio methods~\footnote{Private communication with R.
+Moszynski}.
 
@@
 A similar result holds for the other excited state potentials.
+
+\begin{figure}[ht!]
+  \includegraphics[width=\textwidth]{imgs/TDM_wide.pdf}
+  \caption{Electronic transition dipole moments calculated via ab initio methods between different electronic states of NaCs.
+These transition dipole moments are shown as a function of internuclear distance.
+    \label{tdm-sm}}
+\end{figure}
 

### 2021-05-10 sm.tex
Update on Overleaf.

--- 2021-03-02 sm.tex
@@
 These calculations assume that the intermediate states have pure singlet or triplet character and neglect its
-nuclear spin character, which is unknown. These calculations include theoretical electronic transition dipole moments~\footnote{Private communication with R. Moszynski}.
+nuclear spin character, which is unknown.
+These calculations include theoretical electronic transition dipole moments shown in figure \ref{tdm-sm} calculated with \textit{ab initio} methods~\footnote{Private communication with R.
+Moszynski}.
 
@@
 A similar result holds for the other excited state potentials.
+
+\begin{figure}[ht!]
+  \includegraphics[width=\textwidth]{imgs/TDM_wide.pdf}
+  \caption{Electronic transition dipole moments calculated via \textit{ab initio} methods between different electronic states of NaCs.
+These transition dipole moments are shown in units of $ea_0$, where $ e $ is the elementary charge and $a_0$ is the Bohr radius.
+They are plotted as a function of internuclear distance, $ R $.
+    \label{tdm-sm}}
+\end{figure}
 

### 2021-06-28 paper.tex
Move SM into appendix
Also apply the reference update from Rosario

@@
 8 excited molecular electronic potentials~\cite{Korek2007, Grochola2011, Zaharova2009, Grochola2010, Zabawa2012}
-and the continuum~\cite{Liu2017};
-see Supplementary Material for details.
+and the continuum~\cite{Liu2017}; see appendix~\ref{appendix:multi-state} for details.
 This calculation shows that the figure of merit $\Omega_{\rm R}/\Gamma_{\rm s}$
@@
 the short-range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $ or $P^{3/8}$,
-where $ \omega_{\text{trap}} $ is the trap frequency and $P$ is the optical power in the tweezer trap \cite{Mies2000} with a fixed beam waist.
+where $ \omega_{\text{trap}} $ is the trap frequency and $P$ is the optical power in the tweezer trap~\cite{Mies2000} with a fixed beam waist.
 However, additional power may not be available and also leads to additional undesired scattering.
@@
 
-To identify a suitable target molecular state, we carry out coupled-channel calculations of the near-threshold bound states, as described in the Supplemental Material.
+To identify a suitable target molecular state, we carry out coupled-channel calculations of the near-threshold bound states, as described in the appendix~\ref{appendix:coupled-channel-ground}.
 Choosing a bound state with similar spin character to the atomic state  minimizes the sensitivity of the transition frequency to magnetic field.
@@
 
-While the measured single-photon Rabi frequencies of Table~I are in broad agreement with calculations (see Supplementary Materials), calculated scattering rates of the molecular and atomic state underestimate the decoherence in Fig.~\ref{f-raman}b.
-From experimental measurements, the Raman transfer efficiency is limited by the molecular lifetime, together with a reduction in the Raman Rabi frequency due to destructive interference with intermediate states beyond $v'=0$ (see Table~~\ref{tab:f-det:fit}).
+While the measured single-photon Rabi frequencies of Table~\ref{tab:f-det:fit} are in broad agreement with calculations (see appendix~\ref{appendix:excited_states} and \ref{appendix:coupled-channel-ground}), calculated scattering rates of the molecular and atomic state underestimate the decoherence in Fig.~\ref{f-raman}b.
+From experimental measurements, the Raman transfer efficiency is limited by the molecular lifetime, together with a reduction in the Raman Rabi frequency due to destructive interference with intermediate states beyond $v'=0$ (see Table~\ref{tab:f-det:fit}).
 We discuss loss and decoherence below.
@@
 
+\appendix
+\section{3 Level Raman Transfer with Cross Coupling}
+
+In our system, the separation in energy between the initial and target state is much smaller than the single photon detuning $\Delta$ from the intermediate state; see Fig.~1a in the main text.
+Thus, there is significant cross coupling for the scattering rate and light shift, where each state is coupled to the excited state by the power in both beams.
+Under these conditions, the scattering rate and light shift are proportional to the total power $P_{\text{tot}} = P_{\rm m} + P_{\rm a}$, where $P_{\rm m} (P_{\rm a})$ is the power in the beam that addresses the molecular (atomic) state.
+The Raman Rabi frequency is proportional to $\sqrt{P_{\rm m}P_{\rm a}} $.
+With a fixed total power and thus fixed scattering rate, the Raman Rabi frequency is maximized when $ P_{\rm m} = P_{\rm a} = P_{\text{tot}}/2$.
+
+For the purposes of this work, we denote $\Omega_{\rm a} $($\Omega_{\rm m}$) as the Rabi frequencies to drive a transition from the atom (target molecule) state to the intermediate state used in the Raman transition corresponding to the power in a single beam, $P_{\rm a}$ ($P_{\rm m}$).
+Thus, the Raman Rabi frequency is $\Omega_{\rm a}\Omega_{\rm m}/(2\Delta)$, where $ \Delta $ is the single photon detuning.
+Cross coupling affects the scattering rate and light shift, and assuming equal powers in both beams, these quantities become $ \Gamma_{\rm e} \Omega_{\rm m}^2 / (2\Delta^2) + \Gamma_{\rm e} \Omega_{\rm a}^2 / (2\Delta^2) $ and $ \Omega_{\rm m}^2/(2\Delta) - \Omega_{\rm a}^2/(2\Delta) $, where $\Gamma_{\rm e}$ is the excited state linewidth.
+Since $ \Omega_{\rm m} >> \Omega_{\rm a} $, the scattering rate and light shift can be approximated as $ \Gamma_{\rm e} \Omega_{\rm m}^2/(2\Delta^2)$ and $\Omega_{\rm m}^2/(2\Delta)$.
+
+\section{Raman Transfer with Many Intermediate States} \label{appendix:multi-state}
+With multiple intermediate states, the total Raman Rabi frequency, scattering rate, and light shift become a sum over all these possible states.
+In our model, we consider all vibrational states of $ \mathrm{c^3\Sigma^+(\Omega = 1)} $ and states in the atomic continuum as intermediate states.
+The Rabi frequency between two states is proportional to the electronic dipole moment, arising from the electronic wavefunctions, and the overlap of the vibrational wavefunctions.
+Under the assumption that the electronic dipole moment $ d $ is the same for all transitions between the ground state and the excited electronic state, the total Raman Rabi frequency becomes
+\begin{equation}
+  \Omega_{\rm R} = \frac{d^2E^2}{2\hbar^2} \sum_{v'}\frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}},
+\end{equation}
+where $\ket{a}$ ($\ket{m}$) are the relative coordinate wavefunctions for the trapped atomic (target molecular) state, and $\ket{v'}$ is the relative-coordinate wavefunction for the excited state which includes both bound molecular states and the atomic continuum.
+$\Delta_{v'}$ is a single photon detuning with respect to the $\ket{v'}$ state, $ E $ is the electric field for the power in the single beam given a waist size.
+We can divide this sum into a sum over all the bound molecular states, and a sum over atomic continuum states,
+\begin{equation}
+  \begin{split}
+    \Omega_{\rm R} = &\frac{d^2E^2}{2\hbar^2}\sum_{v' \leq v'_{\text{max}}}\frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}}\\
+    &+\frac{d^2E^2}{2\hbar^2}\sum_{v' > v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}},
+  \end{split}
+\end{equation}
+where $ v'_{\text{max}}$ corresponds to the excited molecular state, which is most weakly bound.
+The first term can be calculated numerically given an excited state potential.
+To calculate the second term, we first make an assumption that we are far enough detuned from the contributing continuum states that they are all at approximately the same detuning, $ \Delta_{\text{thresh}}$.
+This allows us to pull it out of the sum, and we obtain
+\begin{equation}
+  \begin{split}
+    \Omega_{\rm R} \approx &\frac{d^2E^2}{2\hbar^2}\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} \\
+    & +\frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\sum_{v' > v'_{\text{max}}} \braket{a|v'}\braket{v'|m} . \label{rabifreq}
+  \end{split}
+\end{equation}
+From requiring completeness and orthogonality,
+\begin{equation}
+  \sum_{v'} \braket{a|v'}\braket{v'|m} = \braket{a|m} = 0,
+\end{equation}
+we derive an expression for the second sum in equation~\ref{rabifreq}
+\begin{equation}
+  \sum_{v'> v'_{\text{max}}}\!\!\braket{a|v'}\braket{v'|m} = -\!\!\!\!\sum_{v' \leq v'_{\text{max}}}\!\!\braket{a|v'}\braket{v'|m},
+\end{equation}
+which can be calculated from the vibrational states of the excited state potential. Thus, the Raman Rabi frequency can be approximated as:
+\begin{equation}
+  \begin{split}
+    \Omega_{\rm R} \approx &\frac{d^2E^2}{2\hbar^2}\sum_{v' \leq v'_{\text{max}}} \frac{\braket{a|v'}\braket{v'|m}}{\Delta_{v'}} \\
+    & - \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\sum_{v' \leq v'_{\text{max}}} \braket{a|v'}\braket{v'|m}.
+  \end{split}
+\end{equation}
+We can account for the atomic continuum in the scattering rate in a similar way
+\begin{equation}
+  \begin{split}
+    \Gamma_{\rm s} \approx &\frac{d^2E^2}{2\hbar^2}\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2}\\
+    & + \frac{d^2E^2\Gamma}{2\hbar^2\Delta_{\text{thresh}}^2}\sum_{v' > v'_{\text{max}}}\braket{m|v'}\braket{v'|m},
+  \end{split}
+\end{equation}
+where $\Gamma_{v'}$ is the excited state linewidth for the $\ket{v'}$ state, and we have assumed the atomic continuum states all have the same linewidth $\Gamma$.
+Using normalization, we derive an expression for the sum in the second term
+\begin{equation}
+  \sum_{v' > v'_{\text{max}}}\!\!\braket{m|v'}\braket{v'|m} = 1 -\!\!\!\!\sum_{v' \leq v'_{\text{max}}}\!\!\braket{m|v'}\braket{v'|m}.
+\end{equation}
+We then arrive at an expression for the scattering rate, accounting for the atomic continuum,
+\begin{equation}
+  \begin{split}
+    \Gamma_{\rm s} \approx &\frac{d^2E^2}{2\hbar^2}\sum_{v' \leq v'_{\text{max}}}\Gamma_{v'} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}^2}\\
+    &+ \frac{d^2E^2\Gamma}{2\hbar^2\Delta_{\text{thresh}}^2}\left(1 -\!\!\!\!\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right).
+  \end{split}
+\end{equation}
+We have replaced the full continuum with an effective state at the atomic threshold with strength proportional to the amount of wavefunction overlap between the target molecular state and all atomic continuum states.
+This model leads to a component in the scattering rate that is proportional to $ 1/\Delta_{\text{thresh}}^2$ and is smaller as one detunes farther from the threshold.
+We note that the first term can also scale nearly as $1/\Delta_{\text{thresh}}^2 $, if, as in our case, the largest terms in the summation are from states near the threshold.
+
+A very similar result holds for the light shift $\delta$ and is written here for completeness
+
+\begin{equation}
+  \begin{split}
+    \delta=&\frac{d^2E^2}{2\hbar^2}\sum_{v' \leq v'_{\text{max}}} \frac{\braket{m|v'}\braket{v'|m}}{\Delta_{v'}} \\
+    & + \frac{d^2E^2}{2\hbar^2\Delta_{\text{thresh}}}\left(1 - \!\!\!\!\sum_{v' \leq v'_{\text{max}}}\braket{m|v'}\braket{v'|m}\right).
+  \end{split}
+\end{equation}
+
+\section{Computational methods for bound and scattering states}
+
+For scattering and near-threshold bound states, we solve the Schr\"odinger equation by
+coupled-channel methods~\cite{HUTSON1994}, using a basis set in which the electron spins
+$s_{\rm Na}$ and $s_{\rm Cs}$ and the nuclear spins $i_{\rm Na}$ and $i_{\rm Cs}$ are separately
+coupled,
+\begin{equation}
+  | (s_{\rm Na} s_{\rm Cs} S)
+  (i_{\rm Na} i_{\rm Cs} I) F M_F\rangle.
+  \label{eqbassif}
+\end{equation}
+Here $S$ and $I$ are the total electron and nuclear spins of the molecule or atomic pair. Their
+resultant $F$ is the total spin, with projection $M_F$ onto the axis of the magnetic field. In
+principle $F$ can be further coupled to the rotational angular momentum $L$, but in the present
+work only functions with $L=0$ are included. In the absence of a magnetic field, $F$ and $M_F$ are
+both good quantum numbers, but in a magnetic field only $M_F$ is conserved. The calculations in
+this paper use basis sets with all possible values of $S$, $I$ and $F$ (for the required value of
+$M_F$) that can be constructed with $s_{\rm Na} = s_{\rm Cs} = 1/2$,
+$i_{\rm Na} = 3/2$ and $i_{\rm Cs} = 7/2$.
+
+Scattering calculations are carried out using the MOLSCAT package~\cite{molscat:2019,
+  mbf-github:2020} and bound-state calculations using the related BOUND package
+\cite{bound+field:2019, mbf-github:2020}. The calculations use singlet and triplet interaction
+potentials for Na+Cs obtained by adjusting the potentials of Docenko \emph{et al.}\
+\cite{Docenko2006} at short range, using the same procedure as for KCs~\cite{Groebner2017},
+to reproduce the experimental binding energy of the least-bound triplet state~\cite{Hood2019}
+and the position of the s-wave Feshbach resonance near 864~G~\cite{Zhang2020}. The atomic
+nuclear hyperfine coupling and Zeeman effects are fully included, using the Hamiltonian described
+in~\cite{Hutson2008}.
+
+The bound-state calculations were initially used to predict the binding energies of states that lie
+within about 1~GHz of each atomic threshold of interest. At zero magnetic field, the states fall
+into groups from each hyperfine state of the atomic pair, labeled by $(f_{\rm Na},f_{\rm Cs})$. For
+example, for the $(f_{\rm Na},f_{\rm Cs}) = (2,3)$ states that are of principal interest here, each
+group comprises 5 zero-field levels with $F=1,2,3,4$ and 5; one such group is spread out over a
+range of energies between 290 MHz and 770 MHz below the $(f_{\rm Na},f_{\rm Cs}) = (2,3)$
+threshold. In a magnetic field, each zero-field level splits into $2F+1$ Zeeman sublevels labeled
+by $M_F$. For each sublevel we can calculate the dependence of the energy on magnetic field, in
+order to choose a target state for which the Raman transition frequency depends only weakly on
+field.
+
+The state that we ultimately chose as the target state for Raman transfer is the least-bound
+$(F,M_F)=(5,5)$ sublevel with $(f_{\rm Na},f_{\rm Cs}) = (2,3)$, which was predicted at a binding
+energy 763 MHz below the $(f_{\rm Na},f_{\rm Cs}) = (2,3)$ threshold. As described in the text, it
+was subsequently located experimentally at a binding energy of $ 770.1969(2) \mathrm{MHz} $ at $ 8.83(2) \mathrm{G} $.
+
+Multichannel bound-state wavefunctions, with components labeled by $S$, $I$ and $F$, are calculated
+using the method of Thornley and Hutson~\cite{Thornley1994}. For molecular bound states, they are
+obtained on a grid of internuclear distances from 2.4~\AA\ to 50~\AA. For states of confined atomic
+pairs, a harmonic confining potential is added to the molecular potentials and the grid is extended
+to 3000~\AA.
+
+\section{Excited Molecular States} \label{appendix:excited_states}
+To obtain a full calculation for the expected Raman Rabi frequency, light shift and scattering, we need to account for all the excited molecular states.
+The lowest eight excited molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P.
+These eight potentials can be written in the Hund's case (a) basis as
+$\mathrm{c^3\Sigma^+_{\Omega = 0^-}}$, $\mathrm{c^3\Sigma^+_{\Omega = 1}}$,
+$\mathrm{b^3\Pi_{\Omega = 0^-}}$, $\mathrm{b^3\Pi_{\Omega = 0^+}}$,
+$\mathrm{b^3\Pi_{\Omega = 1}}$, $\mathrm{b^3\Pi_{\Omega = 2}}$,
+$\mathrm{B^1\Pi_{\Omega = 1}}$, $\mathrm{A^1\Sigma^+_{\Omega = 0^+}}$~\cite{Korek2007}.
+Due to spin-orbit coupling, especially large in Cs, the excited molecular states are mixed, containing components in multiple potentials.
+Fortunately, single-channel potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ have been experimentally determined, and are predictive across the entire energy range of the potential~\cite{Grochola2010, Grochola2011, Liu2017}.
+Since there is only one $ \Omega = 2$ potential at this dissociation limit, a single-channel potential has been determined for $ b^3\Pi_2$ as well~\cite{Zabawa2012}.
+Unfortunately, single-channel potentials for the other electronic states do not exist.
+A deperturbation analysis was required for states belonging to the mixed $\mathrm{A-b}$ complex,
+and the fitted potentials and spin-orbit coupling coefficients are only accurate within the energy range of the measured experimental data~\cite{Zaharova2009}.
+Since our experiment attempts to work in a regime where the predominant Raman coupling comes from the $v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $,
+the contribution of the other seven potentials is mainly to a background that is nearly detuning independent.
+Thus, for computational ease, we use the diabatic potentials for $ \mathrm{b^3\Pi_{0}, b^3\Pi_{1}} $ and $ \mathrm{A^1\Sigma^+_{0^+}}$.
+% and remove the states nearest to the $ v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $.
+Lastly, to our knowledge, no potential fit to experimental data exists for the $ c^3\Sigma^+_{0^-}$ state.
+Assuming that its contribution is only to the background, as an approximation, we simply double the contribution of all states except $v' = 0$ from $ c^3\Sigma^+_1$.
+
+\section{Calculating Matrix Elements with Coupled Channel Ground State}
+\label{appendix:coupled-channel-ground}
+To calculate Rabi frequencies for transitions to the eight excited molecular potentials, we
+obtain their wavefunctions from a single-channel calculation~\cite{Fattal1996} using the potential energy curves described in appendix~\ref{appendix:excited_states}. We
+then calculate overlap integrals between these functions and either the triplet ($S=1$) or singlet ($S=0$) components of the
+coupled-channel wavefunctions for either the target molecular state or the confined atomic state.
+These calculations assume that the intermediate states have pure singlet or triplet character and neglect its
+nuclear spin character, which is unknown. These calculations include theoretical electronic transition dipole moments shown in figure~\ref{tdm-ap} calculated with \textit{ab initio} methods.
+In the \textit{ab initio} calculations the same computational scheme
+as for Rb2 in Ref.~\cite{Tomza2013aa} was used.
+
+The full calculation of the Raman Rabi frequency and scattering rate using the methods in appendix~\ref{appendix:multi-state} is shown in figure~\ref{f-ap}.
+The strong contribution from the atomic threshold arises from the large overlap to the near-threshold bound states shown in figure~\ref{f-apfcf} for the $c^3\Sigma^+_1$ state.
+This leads to a $1/\Delta_{\text{thresh}}^2$ dependence of the scattering rate and favors using deeply bound states as the intermediate state for the Raman transfer.
+A similar result holds for the other excited state potentials.
+
+\begin{figure}[ht!]
+  \includegraphics[width=0.48\textwidth]{imgs/TDM.pdf}
+  \caption{Electronic transition dipole moments calculated via \textit{ab initio} methods between different electronic states of NaCs.
+These transition dipole moments are shown in units of $ea_0$, where $ e $ is the elementary charge and $a_0$ is the Bohr radius.
+They are plotted as a function of internuclear distance, $ R $.
+    \label{tdm-ap}}
+\end{figure}
+
+\begin{figure*}[ht!]
+  \includegraphics[width=0.98\textwidth]{imgs/raman_theory_full.pdf}
+  \caption{Full calculation of the Raman Rabi frequency and scattering rate
+    as a function of the single-photon frequency
+    including all vibrational states of $ \mathrm{c^3\Sigma^+(\Omega = 1)}$
+    and the atomic continuum.
+    The second frequency in the Raman transition is offset by about $770~\mathrm{MHz}$
+    and resonant with the two photon transition.
+    The assumed excited-state linewidth for all molecular lines is $50~\text{MHz}$.
+    The red line shows the contribution that comes only from the near-threshold states.
+    \label{f-ap}}
+\end{figure*}
+
+\begin{figure}[ht!]
+  \includegraphics[width=0.48\textwidth]{imgs/fcf_c3sigma.pdf}
+  \caption{The Franck-Condon Factor (FCF) between the target molecular state and vibrational state $v'$ of $c^3\Sigma^+_1$.
+The potential supports 74 bound states, and the predominant contribution arises from the near-threshold bound states.
+The total overlap with all the bound states is $0.4822$, which is $96.8\%$ of the total triplet fraction of the target molecular state.
+    \label{f-apfcf}}
+\end{figure}
+
+\section{Effective Matrix Elements to a Single State}
+
+In this calculation, there is a matrix element, $\Omega_{\mathrm{a}ij}, \Omega_{\mathrm{m}ij}$ between each channel $ i $ of the coupled channel ground state and an excited state $ j $.
+The total Raman Rabi frequency $ \Omega_{\rm R}$, light shift $ \delta$ and off-resonant scattering $ \Gamma_{\rm s}$ contribution from this single excited state is calculated as
+\begin{align}
+  \Omega_{\mathrm{R}j} &= \displaystyle\sum_{i} \frac{\Omega_{\mathrm{a}ij} \Omega_{\mathrm{m}ij}}{2\Delta}, \\
+  \delta_j &= \displaystyle\sum_{i} \frac{\Omega_{\mathrm{a}ij}^2 - \Omega_{\mathrm{m}ij}^2}{2\Delta}, \\
+  \Gamma_{\mathrm{s} j} &= \displaystyle\sum_{i} \Gamma_{\rm e} \frac{\Omega_{\mathrm{a}ij}^2 + \Omega_{\mathrm{m}ij}^2}{2\Delta^2},
+\end{align}
+where $ \Delta $ is the single photon detuning and $ \Gamma_{\rm e} $ is the excited state linewidth.
+\begin{table}[ht]
+  \begin{tabular}{|c|c|} \hline
+    $\Omega_{\rm m}'$ &  $2\pi \times 573 ~\mathrm{MHz}$ \\
+    $\Omega_{\rm a}'$ &  $2\pi \times 7.37 ~\mathrm{MHz}$ \\
+    $\Omega_{\rm a}'/\Omega_{\rm m}'$ & $ 0.013 $ \\ \hline
+  \end{tabular}
+  \caption{ The effective Rabi frequencies for the $v' = 0$ state of $c^3\Sigma^+_1$ at $ 3.75~\mathrm{mW}$ of tweezer power.
+    \label{tab:ap}}
+\end{table}
+The experiment, through measuring the detuning dependence of the Raman Rabi frequency and the resonance frequency, extracts a single $ \Omega_{\rm m} $ and $ \Omega_{\rm a} $.
+In order to compare to the theory, we introduce effective $ \Omega_{\rm a}', \Omega_{\rm m}', \Gamma_{\rm e}'$, so that $ \Omega_{\rm R} = \Omega_{\rm a}'\Omega_{\rm m}'/(2\Delta) $, $\delta = (\Omega_{\rm a}'^2 - \Omega_{\rm m}'^2)/(2\Delta) $, and $\Gamma_{\rm s} = \Gamma_{\rm e}'(\Omega_{\rm a}'^2 + \Omega_{\rm m}'^2)/(2\Delta^2) $.
+The effective Rabi frequencies for the $v' = 0$ state of $ c^3\Sigma^+_1$ and their ratio are reported in Table~\ref{tab:ap} at $3.75~\mathrm{mW}$ of tweezer power.
+
+% $2\pi \times 15.3~\mathrm{kHz}$
+% $2\pi \times 533~\mathrm{Hz}$
+% $2\pi \times 573 ~\mathrm{MHz}$
+% $2\pi \times 7.37 ~\mathrm{MHz}$
+
+\section{Scaling of atomic matrix element with tweezer power}
+
+Since our coupled-channel calculations include the harmonic confinement, we can calculate the enhancement in $\Omega_{\rm a}$ with increasing confinement.
+Using two calculations with $ \omega_{\text{trap}} = 36.5~\mathrm{kHz}$ and $\omega_{\text{trap}} = 80~\mathrm{kHz}$ trapping frequencies, and assuming a power law scaling, we find that the wavefunction overlap scales as $ \omega_{\text{trap}}^{0.58} = P^{0.29} $.
+Thus, $\Omega_{\rm a} \propto P^{0.79} $, which was also experimentally verified.
+However, we note that in the actual experiment, our system does not have spherically symmetric confinement.
+The radial trapping frequency is about $5.7$ times larger than the axial trapping frequency.
+\todo{
+  Power/intensity calibration
+}
+
 \bibliography{master_ref}

### 2021-06-28 scripts/plot_fcf.jl

@@ -19,7 +19,7 @@ const fname = joinpath(@__DIR__, "../data/FCFtoc3Sigma.csv")
 const data = readdlm(fname, ',', skipstart=1)
 const prefix = joinpath(@__DIR__, "../imgs", "fcf")
 
-figure(figsize=[13.8, 4.8])
+figure(figsize=[6.4, 4.8])
 plot(data, "C0o-")
 xlabel("\$v'\$")
 ylabel("FCF")
@@ -27,5 +27,14 @@ yscale("log")
 xlim([0, 73])
 grid()
 NaCsPlot.maybe_save("$(prefix)_c3sigma")
+
+figure(figsize=[13.8, 4.8])
+plot(data, "C0o-")
+xlabel("\$v'\$")
+ylabel("FCF")
+yscale("log")
+xlim([0, 73])
+grid()
+NaCsPlot.maybe_save("$(prefix)_c3sigma_wide")
 
 NaCsPlot.maybe_show()

### 2021-06-28 scripts/plot_tdm.jl

@@ -69,11 +69,11 @@ plot(data_X1B1[:, 1] .* 0.529177210903, data_X1B1[:, 2], "C4",
      label="\$X^1\\Sigma\\rightarrow B^1\\Pi\$")
 grid()
 xscale("log")
-xlim([2.7, 25])
-xticks([3, 4, 5, 6, 7, 8, 9, 10, 20], ["3", "4", "5", "6", "7", "8", "9", "10", "20"])
+xlim([2.7, 18])
+xticks([3, 4, 5, 6, 7, 8, 9, 10], ["3", "4", "5", "6", "7", "8", "9", "10"])
 # xticks([4, 6, 8, 10, 20], ["4", "6", "8", "10", "20"])
 # xticks([3, 10], ["3", "10"])
-gca().set_xticks([3:10; 20], minor=true)
+gca().set_xticks([3:10], minor=true)
 gca().xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 xlabel("R (Angstroms)")
 ylabel("Transition Dipole Moment (\$ea_0\$)")

### 2021-06-29 scripts/plot_tdm.jl
[imgs] TDM comparison

@@ -33,6 +33,15 @@ const data_a3c3 = read_csv_compressed(fname_a3c3, ',', Float64)
 const data_X1A1 = read_csv_compressed(fname_X1A1, ',', Float64)
 const data_X1B1 = read_csv_compressed(fname_X1B1, ',', Float64)
 
+const fname_S3P3 = joinpath(@__DIR__, "../data/TDM_Dulieu/Sigma3_Pi3_1_1-7.csv.zst")
+const fname_S3S3 = joinpath(@__DIR__, "../data/TDM_Dulieu/Sigma3_Sigma3_1_1-7.csv.zst")
+const fname_S1S1 = joinpath(@__DIR__, "../data/TDM_Dulieu/Sigma1_Sigma1_1_1-7.csv.zst")
+const fname_S1P1 = joinpath(@__DIR__, "../data/TDM_Dulieu/Sigma1_Pi1_1_1-7.csv.zst")
+const data_S3P3 = read_csv_compressed(fname_S3P3, ',', Float64)
+const data_S3S3 = read_csv_compressed(fname_S3S3, ',', Float64)
+const data_S1S1 = read_csv_compressed(fname_S1S1, ',', Float64)
+const data_S1P1 = read_csv_compressed(fname_S1P1, ',', Float64)
+
 const prefix = joinpath(@__DIR__, "../imgs", "TDM")
 
 figure(figsize=[13.8, 4.8])
@@ -79,5 +88,31 @@ xlabel("R (Angstroms)")
 ylabel("Transition Dipole Moment (\$ea_0\$)")
 legend(fontsize=13.88)
 NaCsPlot.maybe_save("$(prefix)")
+
+figure(figsize=[6.4, 4.8])
+plot(data_a3b3[:, 1] .* 0.529177210903, data_a3b3[:, 2], "C1",
+     label="\$a^3\\Sigma\\rightarrow b^3\\Pi\$")
+plot(data_S3P3[:, 1] .* 0.529177210903, data_S3P3[:, 2], "C1--")
+plot(data_a3c3[:, 1] .* 0.529177210903, data_a3c3[:, 2], "C2",
+     label="\$a^3\\Sigma\\rightarrow c^3\\Sigma\$")
+plot(data_S3S3[:, 1] .* 0.529177210903, data_S3S3[:, 3], "C2--")
+plot(data_X1A1[:, 1] .* 0.529177210903, data_X1A1[:, 2], "C3",
[…]

### 2021-07-05 paper.tex
Remove TODO
Update on Overleaf.

@@
 These calculations assume that the intermediate states have pure singlet or triplet character and neglect its
-nuclear spin character, which is unknown. These calculations include theoretical electronic transition dipole moments shown in figure~\ref{tdm-ap} calculated with \textit{ab initio} methods.
-In the \textit{ab initio} calculations the same computational scheme
-as for Rb2 in Ref.~\cite{Tomza2013aa} was used.
+nuclear spin character, which is unknown. These calculations include theoretical electronic transition dipole moments, shown in figure 6, calculated with the same ab initio methods as described in 
+in Ref.~\cite{Tomza2013aa} for Rb$_2$. Using previously calculated NaCs transition dipole moments \cite{klincare2007radiative, aymar2007calculations} would lead to similar qualitative results.
 
@@
 The radial trapping frequency is about $5.7$ times larger than the axial trapping frequency.
-\todo{
-  Power/intensity calibration
-}
 
